### 2021-10-06 esi.tex
added text

\documentclass{elsarticle}
\input{definitions.tex}
\usepackage[margin=2.5cm]{geometry}% by courtesy of Mico
\begin{document}

\title{Supporting information to the article\\
\mytitle}

%\title{The \PE{} hydrogels as draw agents for desalination of solutions with multivalent ions}

%\tnotetext[t1]{This document is a collaborative effort.}
%\tnotetext[t2]{The second title footnote which is a longer longer than the first one and with an intention to fill in up more than one line while formatting.}

    \author[cuni,imc]{Oleg V. Rud}
    \ead{oleg.rud@natur.cuni.cz}
    \ead[url]{http://www.physchem.cz/}
    \author[cuni]{Alexander~D.~Kazakov}
    \author[cuni]{Lucie~Nova}
    %\author[cuni]{Peter~Kosovan}
    \author[cuni]{Filip~Uhlik}

\maketitle

\section{Theory behind the simulation\label{sec: theory}}

\reffig{fig:diamond} presents a diamond-like polymer network inserted in a simple cubic simulation box of volume $V_{\mathrm{box}}$ with periodic boundaries.
The network consists of $16$ linear \PE{} chains, each chain comprising $30$ monomer units.
Each unit is able to change its ionization state from charged to neutral and vice versa according to the ionization equilibrium.
The mobile ions ($\na$, $\cl$ and $\ca$) are present in certain amount such that they fulfill the electroneutrality condition.

We model the network in equilibrium with the bulk of aqueous solution.
In order to keep the equilibrium conditions we consider three processes to occur:

\begin{enumerate}
	\item the thermal movement of all segments in simulation box (Langevin dynamics);
	\item the ionization reaction equilibrium of \PE{} segments:
   	\begin{equation}
        \mathrm{HA}\leftrightarrows\mathrm{A}^{-}+\h\label{eq: acid reaction}
    \end{equation}
    \item the exchange of ion pairs between the gel and the bath (in order to keep electroneutrality of simulation box):
        \begin{eqnarray}
            \varnothing&\leftrightarrows&\na+\cl\label{eq: nacl reaction}\\
            \varnothing&\leftrightarrows&\ca+2\cl\label{eq: cacl reaction}\\
            %\varnothing&\leftrightarrows&2\na+\so\label{eq: naso reaction}
        \end{eqnarray}
%\todoi{We shall get rid of $\so$ ions and mention it in the inroduction. The reason is that their concentration is small, and they do not enter the hydrogel }
\end{enumerate}

All three processes occur simultaneously in real systems, however, we simulate them alternating each other in stop-run mode in a random order.
\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\columnwidth]{{figures/vmdscene}.pdf}
    \caption{
       	Diamond-like network in the simulation box. 
	Color code represents the individual ion types
	(red: $\na$, blue: $\cl$, yellow: $\ca$) and
        the hydrogel (gray: neutral segment ($\AH$), cyan: charged segment ($\A$)).
    }
    \label{fig:diamond}
    %in order to make snapshot use file snapshot.py
    % in order to edit the existing snapshot use file data/gel_MPC30_box_l53.0_pK7.00_pH7.00_pCl2.00_pCa2.94_lB0.0.vmd
\end{figure}

\subsection{Langevin dynamics\label{MD}}

We use three types of interactions, \ie bonded interactions, short-range non-bonded interactions and electrostatic interactions.

We use Finite extension nonlinear elastic (FENE) potential~\refeq{eq:fene} to account for the bonding interactions.
%The potential accounts for nonlinear elastic extensions and as a consequence, the simulation is not constrained too much.
\begin{equation}\label{eq:fene}
    V_\mathrm{FENE}(r) = -\frac{1}{2} K \Delta r_\mathrm{max}^2\ln \left[ 1 - \left(\frac{r-r_0}{\Delta r_\mathrm{max}} \right)^2 \right ],
\end{equation}
where $K$ is the magnitude of symmetric interaction between two segments,
$\Delta r_{\mathrm{max}}$ is the maximal stretching length of the bond and $r_0$ is the equilibrium bond length.
In our simulations we set $K = 10 \kT/\sigma^{2}$, $\Delta r_{\mathrm{max}} = 2 \sigma$ and $r_0 = 1.0\sigma$~\cite{Jin2007}.

We model the non-bonded interactions using truncated Lennard-Jones interaction potential.
This potential imposes strong repulsion between all particles at short distances:
\begin{equation}
    \begin{split}\label{eq:LJ}
        V_\mathrm{LJ}(r) =
        \begin{cases}
            4 \varepsilon \left( \left(\cfrac{\sigma}{r}\right)^{12}
            - \left(\cfrac{\sigma}{r}\right)^6\right)
            & \mathrm{if~} r < r_\mathrm{cut}\\
            0
            & \mathrm{elsewhere}
        \end{cases},
    \end{split}
\end{equation}
where $r$ is the interparticle distance,
$\sigma = 0.35 \mathrm{nm}$ is the characteristic size of the particles,
$\varepsilon$ is the depth of the potential well in $\kT$ units and $r_\mathrm{cut}$ is the cut-off distance beyond which the potential is set zero.

We model the long range electrostatic interactions by the Coulomb potential:
\begin{equation}
    V_{\mathrm{EL}}=\lb\kT \cfrac{q_{1}q_{2}}{r},
\end{equation}
where $\lb$ is Bjerrum length. We set $\lb = 2\sigma = 0.7 \mathrm{nm}$ which corresponds to water at $T=300 \mathrm{K}$.

We use Langevin thermostat, \ie
we add two additional terms to force in equation of motion
\begin{equation}
f_i =  -\gamma v_i(t)+\sqrt{2\gamma \kT }\eta_i(t),
\end{equation}
where the first term correspond to constant friction with $\gamma$ being a friction coefficient, and the second one corresponds to random thermal force with $\eta_i$ being a normally distributed random number (see for details \cite{Grest1986}).

%where $\gamma$ is the friction coefficient and .
%\todo{there is friction and there is random force ballanced by fluctiation dissipation theorem so that it is stationary}
%which causes the decrease of the particles' velocities.
%This is implemented by addition of two corresponding terms to the particles' equations of motion, namely
%\todo{usually -gamma v to keep gamma>0}
%where the first term correspond to

%\paragraph{Units} % apart from cref reference all references are in the text. Do we need cref?
%By setting up the interaction potentials we defined the system of units.
%We have chosen the unit of length being based on the Bjerrum length in water at room temperature, $l_B \simeq 7$nm, and $\sigma=0.5l_B = 0.35$.
% % %Then the unit of concentration is $\cref=(\sigma^{3}\NA1000)^{-1}$mol/l. % % % do we need to say that?
%We set the energy unit to be $\varepsilon = \kT$.

\subsection{Sampling in the Gibbs ensemble\label{sec: sampling the gibbs ensemble}}
All thermal moves are frozen during the sampling of the ion pairs exchange.
The system represents the ensemble with constant number of particles distributed between two vessels (I) and (II).

In the following paragraph we derive the criteria for sampling of the ion exchange equilibrium.
\paragraph{Gibbs canonical ensemble}
Let us first consider the total free energy of both vesselsassuming that we have only particles of a single type:
\begin{equation}
    F=\left(E_{I}-TS_{I}\right) + \left(E_{II}-TS_{II}\right) \label{eq:F-gibbs}
\end{equation}
where $E$ is internal energy, $T$~--- temperature, $S$~--- entropy.

%Our model system represents a finite volume $V$ which exchanges particles with the bath of infinite volume.
%The infinity of the volume means, that the particle exchange between the system and the bath does not influence on the chemical potentials in the bath.
%Such ensemble is called grand canonical ensemble; the free energy in this ensemble, the Landau potential, is
The entropy $S$ is given by the Boltzmann formula~\cite{Nagle2004}:
\begin{equation}
    S=\kB\ln\frac{V^{N}}{N!}\label{eq:entropy}
\end{equation}
%\todo{for partiles without interactions}
where $N$ is a number of particles in corresponding vessel.
This formula accounts for two contributions:
\begin{enumerate}
    \item the combinatorial entropy $S_{c}=-\kB\ln N!$ which reflects the freedom of choice among $N$ particles
    \item the mixing entropy $S_{m}=\kB N\ln V$ which reflects the freedom to place the chosen particle randomly within the simulation box. 
\end{enumerate}
$V$ is the unitless volume, \ie the volume measured in units of $\sigma^3$. 
Thus \refeq{eq:F-gibbs} turns to 
%\todo{this is not reason, moreover A.10 is already wrong as for units}
\begin{equation}
    F=\EI-\kT\ln\frac{\VI^{\NI}}{\NI!}\ + \ \EII-\kT\ln\frac{\VII ^{\NII}}{{\NII} !}
\label{eq: F_gibbs}
\end{equation}
When a single particle transferred from the vessel (I) to the  vessel (II) the free energy in vessel (I) changes 
\begin{equation}
\Delta \FI = \Delta \EI+\kT\ln\frac{\VI^{\NI}}{\NI !} - \kT\ln\frac{\VI^{\NI-1}}{(\NI-1)!}=\Delta \EI + \kT\ln\frac{\VI}{\NI}
\end{equation}
whwereas the free energy change in (II) vessel is
\begin{equation}
\Delta \FII = \Delta \EII+\kT\ln\frac{\VII^{\NII}}{\NII !} - \kT\ln\frac{\VII^{\NII+1}}{(\NII+1)!}=\Delta \EII + \kT\ln\frac{\NII+1}{\VII}
\end{equation}
Thus the total change of free energy will be 
\begin{equation}
\Delta F = \Delta \EI+\Delta \EII+\kT\ln\frac{\VI}{\VII}\frac{\NII+1}{\NI}
\end{equation}
The change of free energy associated with a transfer of a single particle from vessel (I) to vessel (II)  is
\begin{equation}
    \Delta\Omega=\kT\ln\left(V^{\xi}\frac{N!}{\left(N+\xi\right)!}\right)+\Delta \EI+\Delta \EII
\label{eq: DeltaG GC}
\end{equation}
where $\xi=+1$ stands for insertion of a particle and $\xi=-1$ for deletion.

In order to simulate an ensemble which exchanges particles with the bath (bulk reservoir) we need to perform the following Monte Carlo procedure \cite{Frenlkel2002_book}
\begin{enumerate}
	\item we propose the new configuration of the system by insertion (or deletion) of a particle so that the total number of particles changes from $N$ to $N+\xi$, $\xi=\pm1$
	\item we accept the new configuration if
	\begin{equation}
        \mathcal{R}^{\xi}<e^{\Delta\Omega/\kT}=V^{\xi}\frac{N!}{(N+\xi)!}e^{\left(\Delta E+\xi\mu\right)/\kT}\label{eq: GC acceptance}
	\end{equation}
\end{enumerate}
where $\mathcal{R}$ is uniformly distributed random number in range between $0$ and $1$.

\paragraph{Sampling the ionization equilibrium}
We model the ionization equilibrium by means of sampling the reaction ensemble~\cite{Smith1994, Turner2008a}.
In the reaction ensemble we perform chemical reactions as simultaneous insertion, deletion or identity change of particles according to the reaction equation.
For example we assume the ionization of an acidic unit which proceeds according to the reaction equation
\begin{equation}
    \mathrm{AH}\stackrel{K}{\leftrightarrows}\A+\h\label{eq: acid reaction}
\end{equation}
We perform the forward direction of this reaction
by inserting a $\h$ particle and replacing $\AH$ by $\A$.
We perform the reverse direction of this reaction
by deleting a $\h$ particle and replacing $\A$ by $\AH$.

In order to account for the particles creation and deletion
we need to introduce standard states for individual reacting species.
The creation of a particle then means that the particle is removed from the standard state
and inserted into the studied system, and vice versa for deletion.
Each species in its standard state has the \emph{standard} chemical potential, $\mu^\ominus_i$.
The choice of standard state for each component is arbitrary
and we usually define it as pure component at standard pressure $10^5$ Pa
and concentration $1 \molperl$~\cite{IUPAC}.

Thus we rewrite the formula for free energy \refeq{eq:Omega-GC}
accounting for particles creation and deletion as
\begin{equation}
    \Omega=E-TS+\sum_i\left(\mu_i-\mu^\ominus_i\right) N_i\label{eq:Omega-RE}
\end{equation}
where the last term in \refeq{eq:Omega-RE} stands for the exchange of particles between the studied system and the standard states.

Let's have the reaction extent $\xi = (N_i - N_{i,0})/\nu_i$
where $N_i$, resp. $N_{i,0}$ is the actual, resp. initial number of the $i$-th particle species,
$\nu_i$ is its stoichiometric coefficient.
and $i$ runs over individual species involved
in the chemical reaction \refeq{eq: acid reaction} $i \in (\h,\ \A,\ \AH)$. 
The stoichiometric coefficients are positive for reaction products
and negative for reactants: $\nu_\h=1$, $\nu_\A=1$, $\nu_\AH=-1$.
Therefore we take $\xi = +1$ for the forward reaction direction
and $\xi = -1$ for the reverse reaction direction.
Then we can write the change of the free energy of the studied system during one reaction step as
\begin{equation}
\Delta\Omega_{\mathrm{re}}=\kT\ln\left(\prod_i V^{\nu_i\xi}\frac{N_i!}{\left(N_i+\nu_i\xi\right)!}\right)+
\xi\left(\sum_i\nu_i\mu_i-\sum_i\nu_i\mu_i^\ominus\right)+\Delta E
\label{eq: DeltaG RE one}
\end{equation}
%\begin{multline}
%    \Delta\Omega_{\mathrm{re}}=\kT\ln\left(\prod_i V^{\nu_i\xi}\frac{N_i!}{\left(N_i+\nu_i\xi\right)!}\right)+\\
%    \xi\left(\sum_i\nu_i\mu_i-\sum_i\nu_i\mu_i^\ominus\right)+\Delta E
%\label{eq: DeltaG RE one}
%\end{multline}

We write $\sum_i\nu_i \mu_i = 0$
for the chemical reaction in equilibrium.

The term $\sum_i\nu_i\mu_i^\ominus$ is the standard Gibbs free energy change
of the reaction \refeq{eq: acid reaction}.
which defines the equilibrium reaction constant \cite{Atkins} as
\begin{equation}
    K = e^{-\sum_i\nu_i \mu_i^\ominus / \kT}
\end{equation}

Finally, the \refeq{eq: DeltaG RE one} translates to
\begin{equation}
    \Delta\Omega_{\mathrm{re}}=\kT\ln\left(K^\xi\prod_i V^{\nu_i\xi}\frac{N_i!}{\left(N_i+\nu_i\xi\right)!}\right)+\Delta E
\label{eq: DeltaG RE two}
\end{equation}

\subsection{Ion pairs insertions\label{sec: ion insertions}}
We treat the exchange of mobile ions with the reservoir as simultaneous insertion or deletion
of ion pairs or sets in the simulation box.
We insert/delete either $\na$ and $\cl$ ion pair or the two $\cl$ ions together with one $\ca$ ion.
Thus we model the insertion as:
\begin{eqnarray}
    \na +  \cl &\leftrightarrows& \emptyset\label{eq:nacl} \\
    \ca + 2\cl &\leftrightarrows& \emptyset \label{eq:cacl}
\end{eqnarray}
with the corresponding equilibrium reaction constants, reflecting the free energy change during the insertion
\begin{eqnarray*}
    K_\mathrm{NaCl}     = \exp\left(\left(\mu_\na+ \mu_\cl \right) /\kT\right), \\
    K_{\mathrm{CaCl}_2} = \exp\left(\left(\mu_\ca+2\mu_\cl \right /\kT\right))
\end{eqnarray*}
%$K_\mathrm{NaCl}= \exp\left(\mu_\na+\mu_\cl \right)$, $K_{\mathrm{CaCl}_2} = \exp\left(\mu_\ca+2\mu_\cl \right)$

\paragraph{Moderate pH conditions\label{sec: moderate pH conditions}}
In our study we consider the chemical equilibrium between the gel system and reservoir at neutral pH,
which means that the concentration of $\h$ ions in the reservoir is $c_\h=\unit[10^{-7}]{mol/l}$.
At the same time we include rather high salinities \ie $\cs \gtrsim \unit[0.006]{mol/l}$,
so that the concentrations of $\h$ ions and salt ions, $\na$ and $\ca$, differ by at least three orders of magnitude.
%If one had have wanted to simulate a system with at least 10 $\h$ particles, he would have to include $10^5$ of $\na$ particles there,  and not to mention the amount of polymer needed.
Under such conditions the sampling of the reaction \refeq{eq: acid reaction}
is very difficult because of the lack of $\h$ ions.
Following the scheme proposed in \cite{Landsgesel2020} and \cite{Rud2020},
we sample this reaction assuming that
it is accompanied by simultaneous exchange of counterions $\na$ and $\ca$ by $\h$ ion
with corresponding Gibbs free energy changes\cite{Smith1991}:
\begin{eqnarray}
     \h&\leftrightarrows&\na, \quad \Delta\Omega' = \mu_\h-\mu_\na   \label{eq:hna} \\
    2\h&\leftrightarrows&\ca, \quad \Delta\Omega'' = 2\mu_\h-\mu_\ca \label{eq:cacl}
\end{eqnarray}

Summing up the reactions \refeq{eq: acid reaction} with \refeq{eq:hna} and with \refeq{eq:cacl}
we obtain two reactions
\begin{eqnarray}
    \mathrm{HA}&\stackrel{K'}{\leftrightarrows}&\mathrm{A}^{-}+\na\label{eq: acid reaction na}\\
    2\mathrm{HA}&\stackrel{K''}{\leftrightarrows}&2\mathrm{A}^{-}+\ca\label{eq: acid reaction ca}
\end{eqnarray}
where $K'$ and $K''$ are the modified reaction constants which account for the free energy costs caused by the ions exchange, $\Delta\Omega''$ and $\Delta\Omega'$
\begin{eqnarray}
    K' &=& K \exp\left((\mu_\h-\mu_\na)/\kT\right) \label{eq:Gamma'}\\
    K'' &=& K \exp\left((2\mu_\h-\mu_\ca)/\kT\right)\label{eq:Gamma''}
\end{eqnarray}
We sample these two reactions instead of \refeq{eq: acid reaction}.
Then the final equations for the reactions acceptance criteria are obtained by replacing $K$
in \refeq{eq: DeltaG RE two} by $K'$ and $K''$.

Note that we used the approximation of low concentration of $\h$,
which is valid in conditions close to neutral $\pH$,
and generalize the model considering only three types of ions, namely $\na$, $\cl$ and $\ca$.
The value of $\pH$ enters the model only through Equations \ref{eq:Gamma'} and \ref{eq:Gamma''}.

\bibliographystyle{plain}
\bibliography{gibbs}

\newpage
\pagebreak

\end{document}

### 2021-10-07 gibbs.tex
added text

--- 2021-10-06 esi.tex
@@
 \begin{document}
+\begin{frontmatter}{}
 
-\title{Supporting information to the article\\
-\mytitle}
+\title{\mytitle}
 
@@
 
-    \author[cuni,imc]{Oleg V. Rud}
-    \ead{oleg.rud@natur.cuni.cz}
+    \author[cuni,imc]{Michail Laktionov}
+    \ead{michail.laktionov@natur.cuni.cz}
     \ead[url]{http://www.physchem.cz/}
-    \author[cuni]{Alexander~D.~Kazakov}
+    \author[cuni]{Oleg V. Rud}
     \author[cuni]{Lucie~Nova}
@@
 
-\maketitle
+    \address[cuni]{Department of Physical and Macromolecular Chemistry, Faculty of Science, Charles University in Prague, Hlavova 8, Praha 2 128 00, Czech Republic}
+    \address[imc]{Institute of Macromolecular Compounds of Russian Academy of Sciences, 199004, Bolshoy pr. 31, Saint-Petersburg, Russia}
+
+\begin{abstract}
+By this article we model compression of \PE{} hydrogel in equilibrium with small volume of salty aqueous solution.
+We show that the the change of the hydrogel volume affects the salinity of the solution.
+The decrease of the gel volume decreases the solution and vice versa the swelling of the gel increases the surrounding solution.
+This effect can be employed for water desalination ...
+\end{abstract}
+
+\end{frontmatter}{}
 
@@
 	\item the thermal movement of all segments in simulation box (Langevin dynamics);
-	\item the ionization reaction equilibrium of \PE{} segments:
-   	\begin{equation}
-        \mathrm{HA}\leftrightarrows\mathrm{A}^{-}+\h\label{eq: acid reaction}
-    \end{equation}
-    \item the exchange of ion pairs between the gel and the bath (in order to keep electroneutrality of simulation box):
-        \begin{eqnarray}
-            \varnothing&\leftrightarrows&\na+\cl\label{eq: nacl reaction}\\
-            \varnothing&\leftrightarrows&\ca+2\cl\label{eq: cacl reaction}\\
-            %\varnothing&\leftrightarrows&2\na+\so\label{eq: naso reaction}
-        \end{eqnarray}
+	\item the transfer of ions between two vessels:
+        \item the change of ratio between volumes of the two vessels emulationg the piston applying certain pressure to one of the vessels:
 %\todoi{We shall get rid of $\so$ ions and mention it in the inroduction. The reason is that their concentration is small, and they do not enter the hydrogel }
@@
 \end{figure}
-
+\todo{remove $\ca$ ions from snapshot}
 \subsection{Langevin dynamics\label{MD}}
@@
 
-\subsection{Sampling in the Gibbs ensemble\label{sec: sampling the gibbs ensemble}}
+\section{Sampling in the Gibbs ensemble\label{sec: sampling the gibbs ensemble}}
 All thermal moves are frozen during the sampling of the ion pairs exchange.
@@
 \end{equation}
-The change of free energy associated with a transfer of a single particle from vessel (I) to vessel (II)  is
+Introducing $\xi=\pm 1$, which reflects the direction of movement of particle, $\xi$= +1 if the particles moves from vessel (I) to vessel (II), and $\xi=-1$ if the particles moves backwards, then the previous formula transfers to
+
 \begin{equation}
-    \Delta\Omega=\kT\ln\left(V^{\xi}\frac{N!}{\left(N+\xi\right)!}\right)+\Delta \EI+\Delta \EII
-\label{eq: DeltaG GC}
+\Delta F = \Delta E_{tot}+\kT\xi\ln\frac{\VI}{\VII}\frac{\NII+\theta(\xi)}{\NI+\theta(-\xi)}
 \end{equation}
-where $\xi=+1$ stands for insertion of a particle and $\xi=-1$ for deletion.
+where $\theta(x)$ is the Heaviside function.
 
-In order to simulate an ensemble which exchanges particles with the bath (bulk reservoir) we need to perform the following Monte Carlo procedure \cite{Frenlkel2002_book}
+In order to keep electroneutrality of the system we transfer particles by elctroneutral pairs. 
+Accounting for two types of particles which are moved all the time together the previous formula translates to the following
+\begin{equation}
+\Delta F = \Delta E_{tot}+\kT\xi\left(\ln\frac{\VI}{\VII}\frac{\nnaII+\theta(\xi)}{\nnaI+\theta(-\xi)}    + 
+							    \ln\frac{\VI}{\VII}\frac{\nclII+\theta(\xi)}{\nclI+\theta(-\xi)}             \right)
+\end{equation}
+or
+\begin{equation}
+\Delta F = \Delta E_{tot}+\kT\xi\ln\left(\left(\frac{\VI}{\VII}\right)^2\prod_{i}\frac{\NII^i+\theta(\xi)}{\NI^i+\theta(-\xi)}\right) 
+\end{equation}
+where $i$ runs over the ion types $i\in\{\na,\ \cl\}$.
+
+In order to simulate an ensemble composed of two vessels exchanging particles with each other we need to perform the following Monte Carlo procedure \cite{Frenlkel2002_book, SilvaFernandes2015a, Panagiotopoulos1988b}
 \begin{enumerate}
-	\item we propose the new configuration of the system by insertion (or deletion) of a particle so that the total number of particles changes from $N$ to $N+\xi$, $\xi=\pm1$
+	\item we propose the new configuration of the system by removing ion pair from one vessel and inserting it to another
 	\item we accept the new configuration if
 	\begin{equation}
-        \mathcal{R}^{\xi}<e^{\Delta\Omega/\kT}=V^{\xi}\frac{N!}{(N+\xi)!}e^{\left(\Delta E+\xi\mu\right)/\kT}\label{eq: GC acceptance}
+        \mathcal{R}^{\xi}<e^{\Delta F/\kT}\label{eq: GC acceptance}
 	\end{equation}
@@
 
-\paragraph{Sampling the ionization equilibrium}
-We model the ionization equilibrium by means of sampling the reaction ensemble~\cite{Smith1994, Turner2008a}.
-In the reaction ensemble we perform chemical reactions as simultaneous insertion, deletion or identity change of particles according to the reaction equation.
-For example we assume the ionization of an acidic unit which proceeds according to the reaction equation
-\begin{equation}
-    \mathrm{AH}\stackrel{K}{\leftrightarrows}\A+\h\label{eq: acid reaction}
-\end{equation}
-We perform the forward direction of this reaction
-by inserting a $\h$ particle and replacing $\AH$ by $\A$.
-We perform the reverse direction of this reaction
-by deleting a $\h$ particle and replacing $\A$ by $\AH$.
+\section*{Acknowledgments}
 
-In order to account for the particles creation and deletion
-we need to introduce standard states for individual reacting species.
-The creation of a particle then means that the particle is removed from the standard state
-and inserted into the studied system, and vice versa for deletion.
-Each species in its standard state has the \emph{standard} chemical potential, $\mu^\ominus_i$.
-The choice of standard state for each component is arbitrary
-and we usually define it as pure component at standard pressure $10^5$ Pa
-and concentration $1 \molperl$~\cite{IUPAC}.
-
-Thus we rewrite the formula for free energy \refeq{eq:Omega-GC}
-accounting for particles creation and deletion as
-\begin{equation}
-    \Omega=E-TS+\sum_i\left(\mu_i-\mu^\ominus_i\right) N_i\label{eq:Omega-RE}
-\end{equation}
-where the last term in \refeq{eq:Omega-RE} stands for the exchange of particles between the studied system and the standard states.
-
-Let's have the reaction extent $\xi = (N_i - N_{i,0})/\nu_i$
-where $N_i$, resp. $N_{i,0}$ is the actual, resp. initial number of the $i$-th particle species,
-$\nu_i$ is its stoichiometric coefficient.
-and $i$ runs over individual species involved
-in the chemical reaction \refeq{eq: acid reaction} $i \in (\h,\ \A,\ \AH)$. 
-The stoichiometric coefficients are positive for reaction products
-and negative for reactants: $\nu_\h=1$, $\nu_\A=1$, $\nu_\AH=-1$.
-Therefore we take $\xi = +1$ for the forward reaction direction
-and $\xi = -1$ for the reverse reaction direction.
-Then we can write the change of the free energy of the studied system during one reaction step as
-\begin{equation}
-\Delta\Omega_{\mathrm{re}}=\kT\ln\left(\prod_i V^{\nu_i\xi}\frac{N_i!}{\left(N_i+\nu_i\xi\right)!}\right)+
-\xi\left(\sum_i\nu_i\mu_i-\sum_i\nu_i\mu_i^\ominus\right)+\Delta E
-\label{eq: DeltaG RE one}
-\end{equation}
-%\begin{multline}
-%    \Delta\Omega_{\mathrm{re}}=\kT\ln\left(\prod_i V^{\nu_i\xi}\frac{N_i!}{\left(N_i+\nu_i\xi\right)!}\right)+\\
-%    \xi\left(\sum_i\nu_i\mu_i-\sum_i\nu_i\mu_i^\ominus\right)+\Delta E
-%\label{eq: DeltaG RE one}
-%\end{multline}
-
-We write $\sum_i\nu_i \mu_i = 0$
-for the chemical reaction in equilibrium.
-
-The term $\sum_i\nu_i\mu_i^\ominus$ is the standard Gibbs free energy change
-of the reaction \refeq{eq: acid reaction}.
-which defines the equilibrium reaction constant \cite{Atkins} as
-\begin{equation}
-    K = e^{-\sum_i\nu_i \mu_i^\ominus / \kT}
-\end{equation}
-
-Finally, the \refeq{eq: DeltaG RE one} translates to
-\begin{equation}
-    \Delta\Omega_{\mathrm{re}}=\kT\ln\left(K^\xi\prod_i V^{\nu_i\xi}\frac{N_i!}{\left(N_i+\nu_i\xi\right)!}\right)+\Delta E
-\label{eq: DeltaG RE two}
-\end{equation}
-
-\subsection{Ion pairs insertions\label{sec: ion insertions}}
-We treat the exchange of mobile ions with the reservoir as simultaneous insertion or deletion
-of ion pairs or sets in the simulation box.
-We insert/delete either $\na$ and $\cl$ ion pair or the two $\cl$ ions together with one $\ca$ ion.
-Thus we model the insertion as:
-\begin{eqnarray}
-    \na +  \cl &\leftrightarrows& \emptyset\label{eq:nacl} \\
-    \ca + 2\cl &\leftrightarrows& \emptyset \label{eq:cacl}
-\end{eqnarray}
-with the corresponding equilibrium reaction constants, reflecting the free energy change during the insertion
-\begin{eqnarray*}
-    K_\mathrm{NaCl}     = \exp\left(\left(\mu_\na+ \mu_\cl \right) /\kT\right), \\
-    K_{\mathrm{CaCl}_2} = \exp\left(\left(\mu_\ca+2\mu_\cl \right /\kT\right))
-\end{eqnarray*}
-%$K_\mathrm{NaCl}= \exp\left(\mu_\na+\mu_\cl \right)$, $K_{\mathrm{CaCl}_2} = \exp\left(\mu_\ca+2\mu_\cl \right)$
-
-\paragraph{Moderate pH conditions\label{sec: moderate pH conditions}}
-In our study we consider the chemical equilibrium between the gel system and reservoir at neutral pH,
-which means that the concentration of $\h$ ions in the reservoir is $c_\h=\unit[10^{-7}]{mol/l}$.
-At the same time we include rather high salinities \ie $\cs \gtrsim \unit[0.006]{mol/l}$,
-so that the concentrations of $\h$ ions and salt ions, $\na$ and $\ca$, differ by at least three orders of magnitude.
-%If one had have wanted to simulate a system with at least 10 $\h$ particles, he would have to include $10^5$ of $\na$ particles there,  and not to mention the amount of polymer needed.
-Under such conditions the sampling of the reaction \refeq{eq: acid reaction}
-is very difficult because of the lack of $\h$ ions.
-Following the scheme proposed in \cite{Landsgesel2020} and \cite{Rud2020},
-we sample this reaction assuming that
-it is accompanied by simultaneous exchange of counterions $\na$ and $\ca$ by $\h$ ion
-with corresponding Gibbs free energy changes\cite{Smith1991}:
-\begin{eqnarray}
-     \h&\leftrightarrows&\na, \quad \Delta\Omega' = \mu_\h-\mu_\na   \label{eq:hna} \\
-    2\h&\leftrightarrows&\ca, \quad \Delta\Omega'' = 2\mu_\h-\mu_\ca \label{eq:cacl}
-\end{eqnarray}
-
-Summing up the reactions \refeq{eq: acid reaction} with \refeq{eq:hna} and with \refeq{eq:cacl}
-we obtain two reactions
-\begin{eqnarray}
-    \mathrm{HA}&\stackrel{K'}{\leftrightarrows}&\mathrm{A}^{-}+\na\label{eq: acid reaction na}\\
-    2\mathrm{HA}&\stackrel{K''}{\leftrightarrows}&2\mathrm{A}^{-}+\ca\label{eq: acid reaction ca}
-\end{eqnarray}
-where $K'$ and $K''$ are the modified reaction constants which account for the free energy costs caused by the ions exchange, $\Delta\Omega''$ and $\Delta\Omega'$
-\begin{eqnarray}
-    K' &=& K \exp\left((\mu_\h-\mu_\na)/\kT\right) \label{eq:Gamma'}\\
-    K'' &=& K \exp\left((2\mu_\h-\mu_\ca)/\kT\right)\label{eq:Gamma''}
-\end{eqnarray}
-We sample these two reactions instead of \refeq{eq: acid reaction}.
-Then the final equations for the reactions acceptance criteria are obtained by replacing $K$
-in \refeq{eq: DeltaG RE two} by $K'$ and $K''$.
-
-Note that we used the approximation of low concentration of $\h$,
-which is valid in conditions close to neutral $\pH$,
-and generalize the model considering only three types of ions, namely $\na$, $\cl$ and $\ca$.
-The value of $\pH$ enters the model only through Equations \ref{eq:Gamma'} and \ref{eq:Gamma''}.
+This research was supported by the Czech Science Foundation (grant 19-17847Y) (OR, LN, AK),
+Government of Russian Federation, grant number 14.W03.31.0022. % is it really necessary to add this aknowledgement? Who is paid from this project?
+AK thanks the Grant Agency of Charles University for support (project 318120).
+Computational resources were supplied by the project "e-Infrastruktura CZ" (e-INFRA LM2018140) provided within the program Projects of Large Research, Development and Innovations Infrastructures.
 

### 2021-10-08 donnan_analytic.py
entropy change ion pair fixed wrong formulae

@@ -1,8 +1,9 @@
-def zeta(N,v,A_fix):
+def zeta(N_pairs,v,A_fix):
     import numpy as np
     sqrt = np.sqrt
-    return (-2*A_fix*v + A_fix + N*v**2 + v*sqrt(-2*A_fix**2*v + A_fix**2 + N**2*v**2) - sqrt(-2*A_fix**2*v + A_fix**2 + N**2*v**2))/(v*(N*v - N + sqrt(-2*A_fix**2*v + A_fix**2 + N**2*v**2)))
+    return v*(N_pairs - (A_fix*(1 - v)**2/2 + N_pairs*v**2 - (1 - v)*sqrt(A_fix**2*(1 - v)**2 + 4*A_fix*N_pairs*v**2 + 4*N_pairs**2*v**2)/2)/(v**2 - (1 - v)**2))/((1 - v)*(A_fix + (A_fix*(1 - v)**2/2 + N_pairs*v**2 - (1 - v)*sqrt(A_fix**2*(1 - v)**2 + 4*A_fix*N_pairs*v**2 + 4*N_pairs**2*v**2)/2)/(v**2 - (1 - v)**2)))
 #def zeta(N_pair,v,A_fix):
 #    import numpy as np
 #    sqrt = np.sqrt
 #    return (v - 1)*(A_fix*v**2 - 2*A_fix*v + A_fix + 2*N_pair*v**2 + (v - 1)*sqrt(A_fix**2*v**2 - 2*A_fix**2*v + A_fix**2 + 4*A_fix*N_pair*v**2 + 4*N_pair**2*v**2))/(v*(A_fix*v**2 - 2*A_fix*v + A_fix + 2*N_pair*v**2 - 2*N_pair*(2*v - 1) + (v - 1)*sqrt(A_fix**2*v**2 - 2*A_fix**2*v + A_fix**2 + 4*A_fix*N_pair*v**2 + 4*N_pair**2*v**2)))
+

### 2021-10-08 mcmd_polyelctrolyte/main.py

@@ -20,7 +20,7 @@ DIAMOND_PARTICLES = MPC*16+8
 PYTHON_EXECUTABLE = 'python'
 
 #set True to check pure Donnan
-NO_INTERACTION = True
+NO_INTERACTION = False
 
 def populate_boxes(server, N0_pairs, N1_pairs):
     #import particles attributes consistent with other parts of the program
@@ -152,7 +152,7 @@ def main(electrostatic, system_volume, N_pairs, v_gel, n_gel, alpha):
     
     save_fname = f'../data/{str_alpha}_{v_gel}_{N_pairs}_{system_volume}_{int(electrostatic)}_{int(NO_INTERACTION)}_'+str(uuid.uuid4())[:8]+'.json'
     with open(save_fname, 'w') as outfile:
-        json.dump(collected_data, outfile)
+        json.dump(collected_data, outfile, indent=4)
 
     return collected_data
 
@@ -160,10 +160,10 @@ if __name__=="__main__":
     from functools import partial
     from multiprocessing import Pool
     electrostatic = False
-    system_vol = 25**3*2 #two boxes 25^3
-    N_pairs=100 #number of ion pairs to add in both systems
+    system_vol = 20**3*2 #two boxes 25^3
+    N_pairs=200 #number of ion pairs to add in both systems
     v_gel = [0.4, 0.45, 0.5, 0.55, 0.6] #relative volume of the gel box
-    alpha = 0 #charged monomers ratio in the gel
+    alpha = 0.5 #charged monomers ratio in the gel
     #define one-variable func for multiprocessing pool
     def worker(v_gel):
         #relative amount of the pairs in the gel box is approximately its relative volume

### 2021-10-08 mcmd_polyelctrolyte/monte_carlo/ion_pair.py

@@ -1,3 +1,4 @@
+#%%
 from typing import Tuple
 import numpy as np
 import pandas as pd
@@ -37,19 +38,25 @@ def _rotate_velocities_randomly(velocities):
     rot = Rotation.random().as_matrix
     velocities_rotated = [list(rot().dot(velocity)) for velocity in velocities]
     return velocities_rotated
-def _entropy_change(N1, N2, V1, V2, n=1):
+#def _entropy_change(N1, N2, V1, V2, n=1):
     #N1, V1 - box we removing particle from
     #N2, V2 - box we adding to
     #n - number of particles 
-    if n==1:
-        return math.log((N1*V2)/((N2+1)*V1))
-    elif n==2:
-        return math.log((V2/V1)**2*(N1*(N1-1))/((N2+2)*(N2+1)))
+#    if n==1:
+#        return math.log((N1*V2)/((N2+1)*V1))
+#    elif n==2:
+#        return math.log((V2/V1)**2*(N1*(N1-1))/((N2+2)*(N2+1)))
 
-def _get_mobile_species_count(particles_info_df, grouper = ['side']):
-    return particles_info_df.loc[
-        particles_info_df.type.isin(MOBILE_SPECIES)
-        ].groupby(by='side').size().to_list()
+def _entropy_change(anion_0, anion_1, cation_0, cation_1, volume_0, volume_1, removed_from = 0):
+    if removed_from == 0:
+        return math.log((volume_1/volume_0)**2   *   (anion_0*cation_0)/((anion_1+1)*(cation_1+1)))
+    elif removed_from == 1:
+        return _entropy_change(anion_1, anion_0, cation_1, cation_0, volume_1, volume_0, 0)
+
+#def _get_mobile_species_count(particles_info_df, grouper = ['type','side']):
+#    return particles_info_df.loc[
+#        particles_info_df.type.isin(MOBILE_SPECIES)
+#        ].groupby(by=grouper).size()
 
 class MonteCarloPairs(AbstractMonteCarlo):
     def __init__(self, server):
@@ -77,13 +84,14 @@ class MonteCarloPairs(AbstractMonteCarlo):
                 item['side'] = side
         particles_df = pd.concat(pd.DataFrame(part_dict[side]) for side in SIDES)
 
-        n_mobile = _get_mobile_species_count(particles_df)
+        #n_mobile = _get_mobile_species_count(particles_df)
         
         new_state = StateData(
             energy = energy, 
             volume = volume, 
[…]

### 2021-10-08 mcmd_polyelctrolyte/monte_carlo/pure_donnan.py

@@ -1,4 +1,5 @@
 #%%
+from itertools import product
 from typing import Tuple
 import numpy as np
 import pandas as pd
@@ -12,14 +13,21 @@ from libmontecarlo import StateData, ReversalData, AcceptCriterion
 
 SIDES = [0,1]
 
-def _entropy_change(N1, N2, V1, V2, n=1):
-    #N1, V1 - box we removing particle from
-    #N2, V2 - box we adding to
-    #n - number of particles 
-    if n==1:
-        return math.log((N1*V2)/((N2+1)*V1))
-    elif n==2:
-        return math.log((V2/V1)**2*(N1*(N1-1))/((N2+2)*(N2+1)))
+#def _entropy_change(N1, N2, V1, V2, n=1):
+#    #N1, V1 - box we removing particle from
+#    #N2, V2 - box we adding to
+#    #n - number of particles 
+#    if n==1:
+#        return math.log((N1*V2)/((N2+1)*V1))
+#    elif n==2:
+#        return math.log((V2/V1)**2*(N1*(N1-1))/((N2+2)*(N2+1)))
+
+def _entropy_change(anion_0, anion_1, cation_0, cation_1, volume_0, volume_1, removed_from = 0):
+    if removed_from == 0:
+        return math.log((volume_1/volume_0)**2   *   (anion_0*cation_0)/((anion_1+1)*(cation_1+1)))
+    elif removed_from == 1:
+        return _entropy_change(anion_1, anion_0, cation_1, cation_0, volume_1, volume_0, 0)
+
 
 class MonteCarloDonnan(AbstractMonteCarlo):
 
@@ -31,18 +39,22 @@ class MonteCarloDonnan(AbstractMonteCarlo):
         self.v = Volumes[1]/sum(Volumes)
         self.current_state = dict(
             v = self.v,
-            zeta = (self.anion[0]/self.volume[0])/(self.anion[0]/self.volume[1])
+            zeta = (self.anion[0]/self.volume[0])/(self.anion[0]/self.volume[1]),
+            product = [anion*cation/volume**2 for anion, cation, volume in zip(self.anion, self.cation, self.volume)]
         )
 
     def move(self) -> Tuple[ReversalData, AcceptCriterion]:
+        #side = int(random.random()>(self.anion[0]+self.cation[0])/(sum(self.anion)+sum(self.cation)))
         side = random.choice(SIDES)
         other_side = int(not(side))
[…]

### 2021-10-08 mcmd_polyelctrolyte/tests.py

@@ -78,7 +78,7 @@ def collect_data(MC, pressure_target_error=2, mc_target_error=0.001, rounds : in
         'pressure_gel' : {k:v.tolist() for k,v in zip(keys,np.array(pressure_gel).T)}}
     return return_dict
 
-
+#%%
 def main(electrostatic, system_volume, N_particles, v_gel, n_gel, alpha):
     #box volumes and dimmensions
     V = [system_volume*(1-v_gel),system_volume*v_gel]

### 2021-10-08 plots.py

@@ -27,6 +27,8 @@ for file in json_files:
     print(file.name)
     with open(file, 'r') as f:
         dicts.append(flatten_dict(json.loads(f.read())))
+
+
 # %%
 df = pd.DataFrame(dicts)
 df=df.fillna(False)
@@ -39,8 +41,18 @@ df = df.apply(lambda x: x.explode() if x.name in arr_columns else x)
 df['anion_salt'] = df.n_mobile_salt_mean/2
 df['anion_gel'] = df.n_pairs - df.anion_salt 
 df['zeta'] = df.anion_gel/df.anion_salt*(1-df.v)/df.v
-df = df.loc[df['alpha'].isin([0.5])]
+df = df.loc[df['alpha'].isin([0.5, 0.1])]
 #df = df.loc[df['no_gel'] == True]
+#%%
+path = pathlib.Path('mcmd_polyelctrolyte/monte_carlo/data/')
+json_files = path.glob('*.json')
+
+dicts= []
+for file in json_files:
+    print(file.name)
+    with open(file, 'r') as f:
+        dicts.append(flatten_dict(json.loads(f.read())))
+pure_Donnan = dicts[0]
 # %% 
 import numpy as np
 import seaborn as sns
@@ -51,12 +63,12 @@ lvl0 = ['alpha', 'n_pairs', 'n_gel', 'system_volume', 'no_interaction']
 for idx, grouped in df.groupby(by = lvl0):
     print(idx)
     alpha = idx[0]
-    n_pair = np.mean(idx[1])*2
-    a_fix = np.mean(grouped.anion_fixed)
+    n_pair = 200
+    a_fix = 248*0.5
     v_ = grouped.v
-    plt.scatter(v_, grouped.zeta, label = idx)
-    #zeta_theory = [zeta(n_pair, v, a_fix) for v in vv]
-    #plt.plot(vv, zeta_theory, label = idx)
+    plt.scatter(v_, grouped.zeta)
+    zeta_theory = [zeta(n_pair, v, a_fix) for v in vv]
+    plt.plot(vv, zeta_theory, label = idx)
 plt.legend(title=lvl0, bbox_to_anchor=(1.1, 1.05))
 plt.arrow(0.3, 0.05, 0.3, 0.0, head_width = 0.02,  transform=ax.transAxes)
 plt.text(0.35,0.07, "compression",  transform=ax.transAxes, va='bottom')
[…]

### 2021-10-08 sympy_donnan.py

@@ -1,41 +1,38 @@
 #%%
-from donnan_analytic import zeta
-from sympy import Symbol, Eq, solve, sqrt
-#known
-N_pair= Symbol("N_pair", positive = True) #number of all particles
-v= Symbol("v", positive = True) #relative volume of the gel
-A_fixed = Symbol("A_fix", positive = True) #number of fixed anions
-#unknown
-A_salt = Symbol("A_salt", positive = True) #number of mobile anions in salt
-A_gel = Symbol("A_gel", positive = True) #number of mobile anions in gel
+from sympy import Symbol, Eq, solve
+#KNOWN
+N_pairs= Symbol("N_pairs", positive = True) #number of all particles
+#v= Symbol("v", positive = True) #relative volume of the gel
+A_fixed = Symbol("A_fix", positive = True) #fixed anion conc
+V_salt = Symbol("V_salt", positive = True) #salt box volume
+V_gel = Symbol("V_gel", positive = True) #gel box volume
+#UNKNOWN
+A_salt = Symbol("A_salt", positive = True) #salt anions conc
+A_gel = Symbol("A_gel", positive = True) #gel anions conc
 # %%
-mass_law = Eq(A_salt**2/(1-v)**2, A_gel*(A_gel+A_fixed)/v**2)
+x = Symbol('x')
+mass_law = Eq(((N_pairs-x)/V_salt)**2, x*(A_fixed+x)/V_gel**2)
 mass_law
 #%%
-number_of_particle_eq = Eq(N_pair, A_gel + A_salt)
-number_of_particle_eq
+x_solved = solve(mass_law, x)[0]
 #%%
-A_gel_root = solve(number_of_particle_eq, A_gel)[0]
-A_salt_root = solve(mass_law.subs(A_gel, A_gel_root), A_salt)[0]
+A_salt_conc = (N_pairs-x_solved)/V_salt
+A_gel_conc = (A_fixed+x_solved)/V_gel
+zeta = A_gel_conc/A_salt_conc
 #%%
-A_gel_root
-#%%
-result = solve([mass_law, number_of_particle_eq], A_salt, A_gel)
-#%%
-possible_zeta = [(result_[1]/result_[0]/(v/(1-v))).simplify() for result_ in result]
-#%%
-possible_zeta[0]
-#%%
-print(possible_zeta[0])
+v = Symbol('v')
[…]

### 2021-10-08 mcmd_polyelctrolyte/monte_carlo/ion_pair.py
sync

@@ -219,8 +219,8 @@ def MC_step_n_mobile_left(MC, n_steps):
     mobile_count = []
     for i in range(n_steps):
         MC.step()
-        particle_data = MC.current_state['particles_info'].groupby(by = ['type', 'side']).size()
-        mobile_count.append(particle_data[0][0])
+        particle_data = MC.current_state['particles_info'].groupby(by = ['side']).size()
+        mobile_count.append(particle_data[0])
     return mobile_count
         
 def auto_MC_collect(MC, target_error, initial_sample_size, ci = 0.95, tau = None, timeout = 30):

### 2021-10-08 plots.py

@@ -77,4 +77,7 @@ plt.xlabel('v')
 plt.ylabel('$\zeta$')
 plt.plot(pure_Donnan['v'], pure_Donnan['zeta'])
 plt.show()
+
+# %%
+
 # %%

### 2021-11-06 mcmd_polyelctrolyte/ion_pair_monte_carlo.py
no diamond template commented

@@ -2,6 +2,10 @@
 from typing import Tuple
 import numpy as np
 import random
+try:
+    from tqdm import trange
+except:
+    trange = range
 
 from montecarlo import AbstractMonteCarlo
 from montecarlo import StateData, ReversalData, AcceptCriterion
@@ -253,7 +257,7 @@ class MonteCarloPairs(AbstractMonteCarlo):
     
     def equilibrate(self, md_steps = 100000, mc_steps = 200, rounds=25):
         self.run_md(md_steps)
-        for ROUND in range(rounds):
+        for ROUND in trange(rounds):
             [self.step() for i in range(mc_steps)]
             self.run_md(md_steps)
         return True

### 2021-11-06 mcmd_polyelctrolyte/no_diamond_template.py

@@ -1,0 +1,61 @@
+"""
+Template script to call MCMD to sample particles count and pressures
+Change input_args and script name for the task
+Set n_steps, rounds, timeouts, etc. to low values for debugging
+
+Pickled results will be saved to ../data/script_name.pkl
+
+@author: Mikhail Laktionov
+"""
+from ion_pair_monte_carlo import build_no_gel
+from utils import sample_all
+import pickle
+import pathlib
+
+import os
+import sys
+os.chdir(os.path.dirname(sys.argv[0]))
+
+##INPUT##
+input_args = dict(
+    Volume=[20000,20000], 
+    N_pairs=[100,100], 
+    A_fixed = 50, 
+    log_names=['box_0.log', 'box_1.log'],
+    python_executable='pypresso',
+    )
+
+#build monte carlo class instance, with no gel created, only salt reservoirs
+MC = build_no_gel(**input_args)
+
+#equilibration steps
+MC.equilibrate(
+    rounds=3, #repeats mc and md steps, 10 rounds seems to be enough,
+    md_steps=100000, #call integrator.run(md_steps)
+    mc_steps=sum(input_args['N_pairs']) #the same as pairs count
+    )
+
+#sample number of particles of each mobile species and pressures in the boxes
+#by alternating number of particles sampling and pressure sampling routines
+result = sample_all(
+    MC,
+    sample_size=5, #number of samples   #|--------------------------------------
+    n_particle_sampling_kwargs = dict(  #| n_particle sampling routine settings
+        timeout = 10,                   #| omit or comment out to use defaults
+        initial_sample_size = 10        #| set target_error, timeout, 
+        ),                              #| initial_sample_size kwarg here
+                                        #|--------------------------------------
+    pressure_sampling_kwargs=dict(      #| pressures sampling routine settings
+        timeout = 10,                   #| see comment above
+        initial_sample_size = 10        #| set short timeout and  
+        )                               #| small initial_sample_size for debug
+    )                                   #|--------------------------------------
+
+#add inputs to output file and save the pickle to ../data/script_name.pkl
+result.update({'input':input_args})
+print(result)
+
+output_fname = pathlib.Path(__file__).stem+'.pkl'
+output_dir = pathlib.Path(__file__).parent.parent / 'data'
+with open(output_dir/output_fname, 'wb') as f:
+    pickle.dump(result, f)

### 2021-11-06 mcmd_polyelctrolyte/tests_no_diamond.py

@@ -1,23 +1,0 @@
-#%%
-from ion_pair_monte_carlo import build_no_gel
-from utils import sample_all
-import pickle
-import pathlib
-
-input_args = dict(
-    Volume=[20000,20000], 
-    N_pairs=[100,100], 
-    A_fixed = 50, 
-    log_names=['box_0.log', 'box_1.log'],
-    python_executable='pypresso',
-    )
-
-MC = build_no_gel(**input_args)
-#MC.equilibrate(rounds=5)
-result = sample_all(MC, sample_size=5)
-result.update({'input':input_args})
-
-output_fname = pathlib.Path(__file__).stem+'.pkl'
-output_dir = pathlib.Path(__file__).parent.parent / 'data'
-with open(output_dir/output_fname, 'wb') as f:
-    pickle.dump(result, f)

### 2021-11-06 mcmd_polyelctrolyte/utils.py

@@ -54,24 +54,43 @@ def mol_to_n(mol_conc, unit_length_nm=0.35):
     return n
 
 
-def sample_all(MC, sample_size):
+def sample_all(
+        MC, sample_size, 
+        n_particle_sampling_kwargs = None, pressure_sampling_kwargs = None):
     try:
         from tqdm import trange
     except:
         trange = range
     import numpy as np
+    
+    ###defaults
+    n_particle_sampling_kwargs_defaults = dict(
+            target_error = 1, 
+            #timeout = 10,
+            #initial_sample_size = 10
+            )
+    pressure_sampling_kwargs_defaults = dict(
+            target_error = 0.01, 
+            #timeout = 10,
+            #initial_sample_size = 10
+            )
+    
+    if n_particle_sampling_kwargs:
+        n_particle_sampling_kwargs_defaults.update(n_particle_sampling_kwargs)
+    if pressure_sampling_kwargs:
+        pressure_sampling_kwargs_defaults.update(pressure_sampling_kwargs)
+    
+    
     results_ld = [] #list of dicts
     for i in trange(sample_size):
         n_particles_sample = MC.sample_particle_count_to_target_error(
-            target_error = 1, timeout = 10,
-            initial_sample_size = 10 #uncomment for debug
-            )
+            **n_particle_sampling_kwargs_defaults
+        )
         
         #probably we can dry run some MD without collecting any data
         
         pressures_sample = MC.sample_pressures_to_target_error(
-            target_error = 0.01, timeout = 10,
-            initial_sample_size = 10 #uncomment for debug
+            **pressure_sampling_kwargs_defaults
             )
         
         #discard info about errors

### 2021-11-06 mcmd_polyelctrolyte/ion_pair_monte_carlo.py
old numpy fix

@@ -18,7 +18,10 @@ MOBILE_SPECIES = [0,1]
 
 def _rotate_velocities_randomly(velocities):
     from scipy.spatial.transform import Rotation
-    rot = Rotation.random().as_matrix
+    try:
+        rot = Rotation.random().as_matrix
+    except:#old numpy method
+        rot = Rotation.random().as_dcm
     velocities_rotated = [list(rot().dot(velocity)) for velocity in velocities]
     return velocities_rotated
 

### 2021-11-06 mcmd_polyelctrolyte/main.py

@@ -1,179 +1,0 @@
-#%%
-import numpy as np
-import json
-
-import socket_nodes
-
-from ion_pair_monte_carlo import MonteCarloPairs
-
-#change cwd to file location
-import os
-import sys
-os.chdir(os.path.dirname(sys.argv[0]))
-
-#particles between the nodes
-MPC = 15
-#all gel particles
-DIAMOND_PARTICLES = MPC*16+8
-
-#path to python executable, can be pypresso
-PYTHON_EXECUTABLE = 'python'
-
-#set True to check pure Donnan
-NO_INTERACTION = True
-
-def populate_boxes(server, N0_pairs, N1_pairs):
-    #import particles attributes consistent with other parts of the program
-    from espresso_nodes.shared import PARTICLE_ATTR
-    MOBILE_SPECIES_COUNT = [
-            {'anion' : int(N0_pairs), 'cation' : int(N0_pairs)}, #left side
-            {'anion' : int(N1_pairs), 'cation' : int(N1_pairs)}, #right side
-        ]
-    for i,side in enumerate(MOBILE_SPECIES_COUNT):
-        for species, count in side.items():
-            print(f'Added {count} of {species}', end = ' ')
-            print(*[f'{attr}={val}' for attr, val in PARTICLE_ATTR[species].items()], end = ' ')
-            print(f'to side {i} ')
-            server(f"populate({count}, **{PARTICLE_ATTR[species]})", i)
-    server('system.minimize_energy.minimize()', [0,1])
-    print('two box system with polyelectrolite (client 1) is initialized')
-    
-def enable_electrostatic(server):
-    SIDES = [0,1]#for readability e.g. in list comprehensions
-    l_bjerrum = 2.0
-    temp = 1
-    server.request(
-        f"system.actors.add(espressomd.electrostatics.P3M(prefactor={l_bjerrum * temp},accuracy=1e-3))",
-        SIDES
-    )
-    #minimize energy and run md
-    server([
-        "system.minimize_energy.init(f_max=50, gamma=30.0, max_steps=10000, max_displacement=0.001)",
-        "system.minimize_energy.minimize()",
-        f"system.integrator.run({10000})"
-        ],
-        SIDES
-    )
-    server('system.minimize_energy.minimize()', [0,1])
-    print("Electrostatic is enabled")
-
-def equilibration(MC, gel_md_steps : int, salt_md_steps : int, mc_steps : int, rounds : int = 10):
[…]

### 2021-11-06 mcmd_polyelctrolyte/no_diamond_template.py

@@ -18,11 +18,13 @@ os.chdir(os.path.dirname(sys.argv[0]))
 
 ##INPUT##
 input_args = dict(
+    
     Volume=[20000,20000], 
     N_pairs=[100,100], 
     A_fixed = 50, 
     log_names=['box_0.log', 'box_1.log'],
     python_executable='pypresso',
+    
     )
 
 #build monte carlo class instance, with no gel created, only salt reservoirs

### 2021-11-08 mcmd_polyelctrolyte/espresso_nodes/init_reservoir_system.py
donnan inf reservoir analyt

@@ -51,15 +51,15 @@ if __name__=='__main__':
     integrator_steps = 100000
     system.integrator.run(integrator_steps)
 
-    from espressomd import electrostatics
-    l_bjerrum = 2
-    p3m = electrostatics.P3M(prefactor=l_bjerrum, accuracy=1e-3)
-    system.actors.add(p3m)
-    p3m_params = p3m.get_params()
-    logging.debug(p3m_params)
-    _minimize_energy(system)
-    integrator_steps = 100000
-    system.integrator.run(integrator_steps)
+    #from espressomd import electrostatics
+    #l_bjerrum = 2
+    #p3m = electrostatics.P3M(prefactor=l_bjerrum, accuracy=1e-3)
+    #system.actors.add(p3m)
+    #p3m_params = p3m.get_params()
+    #logging.debug(p3m_params)
+    #_minimize_energy(system)
+    #integrator_steps = 100000
+    #system.integrator.run(integrator_steps)
     
     from espressomd.visualization_opengl import  openGLLive
     visualizer = openGLLive(system)

### 2021-11-08 sympy_donnan.py

@@ -15,33 +15,18 @@ mass_law = Eq(((N_pairs-x)/V_salt)**2, x*(A_fixed+x)/V_gel**2)
 #mass_law = mass_law.subs(V_gel, V_salt).simplify()
 mass_law
 #%%
-x_solved = solve(mass_law, x)[0]
-x_solved
+B_gel= solve(mass_law, x)[0]
+B_gel
+B_gel_05 = solve(mass_law.subs(V_salt, V_gel), x)[0]
+B_gel_05
 #%%
-A_salt_conc = (N_pairs-x_solved)/V_salt
-A_gel_conc = (A_fixed+x_solved)/V_gel
-zeta = A_gel_conc/A_salt_conc
-#%%
-v = Symbol('v')
-zeta = zeta.subs(V_salt, 1-v).subs(V_gel,v)
-#%%
-zeta
-#%%
-from sympy import limit
-limit(zeta, v, 0.5)
-#%%
-from sympy import lambdify
-f = lambdify([N_pairs, A_fixed, v], zeta, "numpy")
+B_gel
 # %%
-import sympy
-import matplotlib.pyplot as plt
-import numpy as np
-vv = np.linspace(0.01,0.99)
-V=1000
-zetas = [1/f(200, 124, v_) for v_ in vv]
-plt.plot(vv, zetas)
-# %%
-print(zeta)
-# %%
-print(zeta)
+c_s = Symbol("C_s", positive = True)
+#%%
+mass_law = Eq((c_s)**2, x*(A_fixed+x)/V_gel**2)
+mass_law
+#%%
+B_gel= solve(mass_law, x)[1]
+B_gel
 # %%

### 2022-06-15 gibbs.tex
lyx
Switched to tex

@@
-\documentclass{elsarticle}
-\input{definitions.tex}
-\usepackage[margin=2.5cm]{geometry}% by courtesy of Mico
+ %% LyX 2.3.4.2 created this file.  For more info, see http://www.lyx.org/.
+%% Do not edit unless you really know what you are doing.
+%\documentclass{achemso}
+\documentclass[journal=mamobx, layout=twocolumns,manuscript=article]{achemso}
+
+\usepackage[utf8]{inputenc}
+\usepackage{geometry}
+\geometry{verbose}
+\usepackage{xcolor}
+\usepackage{verbatim}
+\usepackage{multirow}
+\usepackage{amsmath}
+\usepackage{amsthm}
+\usepackage{graphicx}
+\usepackage[unicode=true,pdfusetitle,
+ bookmarks=false,
+ breaklinks=true,pdfborder={0 0 0},pdfborderstyle={},backref=false,colorlinks=true]
+ {hyperref}
+\usepackage[textsize=small]{todonotes}
+
+\makeatletter
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
+
+\title{Water desalination using polyelectrolyte hydrogel. Gibbs ensemble
+modelling}
+
+\author{Mikhail Laktionov}
+
+\affiliation[cuni]{Department of Physical and Macromolecular Chemistry, Faculty of Science,
+Charles University in Prague, Czech Republic}
+
+\alsoaffiliation[itmo]{St. Petersburg National Research University of Information Technologies,
+Mechanics and Optics, St. Petersburg, Russia.}
+
+\author{Lucie Nová}
+\author{Oleg V. Rud}
+
+\affiliation{Department of Physical and Macromolecular Chemistry, Faculty of Science,
+Charles University in Prague, Czech Republic}
+
+\alsoaffiliation[imc]{Institute of Macromolecular Compounds of Russian Academy of Sciences,
+Saint-Petersburg, Russia}
+
+\email{oleg.rud@natur.cuni.cz}
+
+\abbreviations{MC, MD, RO, FO}
+
+\keywords{polyelectrolye hydrogel, simulation, desalination}
+
+%% Because html converters don't know tabularnewline
+\providecommand{\tabularnewline}{\\}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
+%\usepackage[utf8]{inputenc}
+\usepackage{amssymb}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
+\newcommand{\ie}{\textit{i.~e.} }
+\newcommand{\cref}{c^{\ominus}}
+%\newcommand{\cs}{c_{s}}
+\newcommand{\kT}{k_\mathrm{B}T}
+\newcommand{\kB}{k_\mathrm{B}}
+\newcommand{\lb}{l_\mathrm{B}}
+\newcommand{\NA}{N_{\mathrm{A^-}}}
+\newcommand{\muna}{\mu_\mathrm{Na^+}}
+
+\newcommand{\mucl}{\mu_\mathrm{Cl^-}}
+\newcommand{\muca}{\mu_\mathrm{Ca^{2+}}}
+\newcommand{\muh}{\mu_\mathrm{H^+}}
+\newcommand{\mua}{\mu_\mathrm{A^-}}
+\newcommand{\muha}{\mu_\mathrm{HA}}
+\newcommand{\muoh}{\mu_\mathrm{OH}}
+
+\newcommand{\cna}{c_\mathrm{Na^+}}
+\newcommand{\ccl}{c_\mathrm{Cl^-}}
+\newcommand{\cca}{c_\mathrm{Ca^{2+}}}
+\newcommand{\ch}{c_\mathrm{H^+}}
+\newcommand{\cp}{c_\mathrm{p}}
+\newcommand{\nna}{N_\mathrm{Na^+}}
+\newcommand{\ncl}{N_\mathrm{Cl^-}}
+\newcommand{\ncleq}{\widetilde{N}_\mathrm{Cl^-}}
+\newcommand{\nca}{N_\mathrm{Ca^{2+}}}
+
+\newcommand{\superin}{^\mathrm{in}}
+\newcommand{\subin}{_\mathrm{in}}
+\newcommand{\subi}{_\mathrm{i}}
+
+\newcommand{\gel}{^\mathrm{gel}}
+\newcommand{\tot}{^\mathrm{tot}}
+\newcommand{\out}{^{out}}
+\newcommand{\coh}{c_\mathrm{OH}}
+\newcommand{\bulk}{^{\mathrm{b}}}
+\renewcommand{\H}{\mathrm{H^+}}
+\newcommand{\A}{\mathrm{A^-}}
+\newcommand{\AH}{\mathrm{AH}}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
+%% A simple dot to overcome graphicx limitations
+\newcommand{\lyxdot}{.}
+\newcommand{\todoi}[1]{\todo[inline]{#1}}
+\setuptodonotes{fancyline, color=blue!30, size=\tiny}
+
+\newcommand{\cl}{\mathrm{Cl^-}}
+\newcommand{\br}{\mathrm{Br^-}}
+\newcommand{\na}{\mathrm{Na^+}}
+\newcommand{\h}{\mathrm{H^+}}
+\newcommand{\ka}{\mathrm{K^+}}
+\newcommand{\oh}{\mathrm{OH^-}}
+\newcommand{\ca}{\mathrm{Ca^{2+}}}
+\newcommand{\mg}{\mathrm{Mg^{2+}}}
+\newcommand{\so}{\mathrm{SO_4^{2-}}}
+
+\newcommand{\EI}{E_{\mathrm{I}}}
+\newcommand{\EII}{E_{\mathrm{II}}}
+\newcommand{\SI}{S_{\mathrm{I}}}
+\newcommand{\SII}{S_{\mathrm{II}}}
+\newcommand{\NI}{N_{\mathrm{I}}}
+\newcommand{\NII}{N_{\mathrm{II}}}
+\newcommand{\VI}{V_{\mathrm{I}}}
+\newcommand{\VII}{V_{\mathrm{II}}}
+\newcommand{\FI}{F_{\mathrm{I}}}
+\newcommand{\FII}{F_{\mathrm{II}}}
+\newcommand{\nnaI}{N^{\na}_{\mathrm{I}}}
+\newcommand{\nclI}{N^{\cl}_{\mathrm{I}}}
+\newcommand{\nnaII}{N^{\na}_{\mathrm{II}}}
+\newcommand{\nclII}{N^{\cl}_{\mathrm{II}}}
+
+\newcommand{\Ka}{K_{\mathrm{A}}}
+\newcommand{\pKa}{\mathrm{p}\Ka}
+\newcommand{\pK}{\mathrm{p}K}
+\newcommand{\pH}{\mathrm{pH}}
+\newcommand{\mol}{\mathrm{mol}}
+\newcommand{\molperl}{\mathrm{mol/l}}
+\newcommand{\kg}{\mathrm{kg}}
+\newcommand{\res}{^{\mathrm{res}}}
+\newcommand{\pHres}{\pH\res}
+\newcommand{\pHgel}{\pH\gel}
+\newcommand{\cs}{c_{\mathrm{s}}}
+%\newcommand{\cs}{c_{\mathrm{salt}}}
+\newcommand{\csres}{\cs\res}
+\newcommand{\Vgel}{V\gel}
+\newcommand{\Vgeleq}{\widetilde{V}\gel}
+\newcommand{\Pgel}{P\gel}
+\newcommand{\Pres}{P\res}
+\newcommand{\Vout}{V\out}
+\newcommand{\Vbox}{V\tot}
+\newcommand{\PE}{polyelectrolyte{}}
+
+\newcommand{\reffig}[1]{Figure~\ref{#1}}
+\newcommand{\refeq}[1]{Equation~\ref{#1}{}}
+\usepackage{afterpage}
+\newcommand\blankpage{%
+    \null
+    \thispagestyle{empty}%
+    \addtocounter{page}{-1}%
+    \newpage}
+
+\newcommand{\mytitle}{Gibbs ensemble for \PE{} hydrogel}
+\newcommand{\etal}{\textit{et al.}{}}
+
+\@ifundefined{showcaptionsetup}{}{%
+ \PassOptionsToPackage{caption=false}{subfig}}
+\usepackage{subfig}
+\makeatother
+
 \begin{document}
-\begin{frontmatter}{}
+\begin{abstract}
+Recently polyelectrolyte hydrogels have been proposed as draw agents
+for reverse osmosis desalination techniques. Indeed, polyelectrolyte
+hydrogels have the ability to absorb a big amount of water across
+forward osmosis membrane as a result of their swelling pressure. The
+insoluble cross-linked network of the gel enables dewatering under
+the influence of a stimuli (thermal and/or mechanical). On the other
+hand, the network structure of a polymer hydrogel from a thermodynamic
+perspective is already an osmotic membrane. So hydrogel microparticles
+may allow to completely avoid the osmotic membranes in forward osmosis
+and use microfiltration instead. By this article, we present our recent
+theoretical study of the use of polyelectrolyte hydrogel for water
+desalination. We modeled the thermodynamic equilibrium of coexistence
+of the gel and the aqueous salt solution in the so-called closed ensemble,
+in which the total amount of ions is assumed to be constant. We modeled
+the compression of the gel and the associated with that release of
+the solution. We have shown that the squeezed out solution has a little
+lower salinity than that the gel was equilibrated with. Also, we performed
+a set of simulations modeling the process of continuous decrease of
+water salinity up to freshwater concentrations.
 
-\title{\mytitle}
-
-%\title{The \PE{} hydrogels as draw agents for desalination of solutions with multivalent ions}
-
-%\tnotetext[t1]{This document is a collaborative effort.}
-%\tnotetext[t2]{The second title footnote which is a longer longer than the first one and with an intention to fill in up more than one line while formatting.}
-
-    \author[cuni,imc]{Michail Laktionov}
-    \ead{michail.laktionov@natur.cuni.cz}
-    \ead[url]{http://www.physchem.cz/}
-    \author[cuni]{Oleg V. Rud}
-    \author[cuni]{Lucie~Nova}
-    %\author[cuni]{Peter~Kosovan}
-    \author[cuni]{Filip~Uhlik}
-
-    \address[cuni]{Department of Physical and Macromolecular Chemistry, Faculty of Science, Charles University in Prague, Hlavova 8, Praha 2 128 00, Czech Republic}
-    \address[imc]{Institute of Macromolecular Compounds of Russian Academy of Sciences, 199004, Bolshoy pr. 31, Saint-Petersburg, Russia}
-
-\begin{abstract}
-By this article we model compression of \PE{} hydrogel in equilibrium with small volume of salty aqueous solution.
-We show that the the change of the hydrogel volume affects the salinity of the solution.
-The decrease of the gel volume decreases the solution and vice versa the swelling of the gel increases the surrounding solution.
-This effect can be employed for water desalination ...
 \end{abstract}
 
-\end{frontmatter}{}
+\section{Introduction\label{sec: intro}}
+
+\paragraph{Water desalination technologies.}
+
+Two basic approaches for separating water from salt are present in
+modern desalination technology \cite{Miller2003,Curto2021}.
+
+The first approach~--- distillation. It uses thermal means to effect
+a phase change of the water to vapor (or solid), then to physically
+separate the vapor phase from the remaining salt solution, and then
+recover the thermal energy for reuse as the separated vapor reverts
+to liquid form. Distillation processes were the first desalination
+techniques conducted on a large commercial scale and still account
+for a large portion of the modern world’s desalination capacity.
+
+The second approach is to physically separate the brine components,
+generally with a membrane, as they move in response to an externally
+applied gradient. In the context of our study, we will mention the
+reverse osmosis process (RO) \textasciitilde -{}-{}- the major processes
+of all the modern desalination industry, and the new emerging membrane
+technology -{}-{}- forward osmosis (FO) \cite{Akther2015}. In RO,
+water passes through a membrane that is impermeable to the solute
+in response to a chemical potential gradient achieved through pressurization.
+In FO, a concentrated draw solution, with a lower water chemical potential,
+and a feed solution, with a higher water chemical potential, are separated
+by a membrane that rejects the salt but allows the passage of water.
+The water permeation from feed solution to draw solution is a spontaneous
+process driven by the chemical potential gradient.
+
+Distillation is easy and cheap technology but it is characterized
+by relatively high energy costs due to the dissipation of thermal
+energy. On the contrary, RO uses expensive osmotic membranes, which
+need to be replaced regularly because of scaling and fouling. Moreover,
+RO requires very high operating pressures, ranging from 20 to 200
+bar, to let the water pass through the membrane. But in terms of energy
+losses, it works close to the thermodynamic limit. Thus, theoretically,
+per one transferred from freshwater to salty water ion pair, it consumes
+only the energy of difference of those ions chemical potentials.
+
+The absence of large hydraulic pressure in FO process in comparison
+to RO allows to reduce the energy consumption in pumping, reduce membrane
+scaling and fouling, therefore significantly increase the lifetime
+of the membranes. In FO, the draw solutes (agents) dispersed and/or
+dissolved in water form homogeneous draw solutions. The correct choice
+of the draw agents is a task of paramount importance. As an osmotically
+driven process, the draw solute is expected to significantly reduce
+the water chemical potential, and consequently generate a high osmotic
+pressure. On the other hand, the diluted draw solution is also expected
+to be easily separated to fresh water and to concentrated draw solution
+for reuse \cite{Cai2016}.
+
+\paragraph{Hydrogels for desalination.}
+
+Hydrogels are three-dimensional networks of polymer chains that are
+crosslinked by either physical or chemical bonds. They are able to
+entrap large volumes of water attracted by the high concentration
+of hydrophilic groups. Hydrogels with ionic groups on the comonomer
+unit are able to reject salt ions from the solution, they absorb a
+solution of lower salinity than that they are equilibrated with. When
+a dehydrated or deswollen hydrogel uptakes water, its polymer chains
+extend, creating a swelling pressure. For example, as reported in
+\cite{Wack_2009} weakly crosslinked poly(acrylic acid)/poly(sodium
+acrylate) copolymers with polymer volume fractions between 0.03 and
+0.30 exhibit a swelling pressure ranging from 0.20--4.23 MPa.
+
+An important, advantageous aspect of polymer hydrogels is that they
+can undergo reversible volume change, \ie solution --- gel phase
+transitions in response to environmental stimuli. This aspect causes
+hydrogels to be labeled as ‘smart’ hydrogels. Many physical and chemical
+stimuli have been applied to induce various responses of such smart
+hydrogels, in particular, to change them from hydrophilic to hydrophobic,
+thereby releasing water. These stimuli include: temperature, solvent
+composition, light, mechanical pressure, sound, electric and/or magnetic
+field, whilst the chemical or biochemical stimuli include pH, ions,
+and specific molecular recognition events \cite{Tanaka_1982,Serizawa_2001,Lietor_Santos_2009,Qiu_2001}.
+
+The smart properties of hydrogels were utilized for desalination in
+a recent study by Li \etal \cite{Li2011}, where hydrogels have been
+considered as draw agents for FO. The main point of the cited article
+is that hydrogels, due to their swelling and osmotic pressure, were
+able to absorb water across the FO membrane. The insoluble cross-linked
+network of the gel enables dewatering under the influence of stimuli
+(thermal and/or mechanical). For instance, Li \etal proposed the
+use of hydrogel made of thermoresponsive polyelectrolyte~--- copolymer
+of poly-N-isopropyl acrylamide (p-NIPAAm) and polyacrylic acid (p-AA).
+Depending on the temperature the network of the gel may appear to
+be either hydrophilic or hydrophobic. In the hydrophilic state, the
+gel is used as a draw agent accumulating water inside, then in the
+hydrophobic state, the water releases out.
+
+Moreover the hydrogel can be as an osmotic membrane from a thermodynamics
+perspective \cite{Wang_2014}. Such a view on hydrogels was employed
+in a series of works by the group of prof. Wilhelm (see for example
+\cite{Arens_2017,Fengler_2020}). The authors proposed to get rid of
+the osmotic membrane and simply use only a micro filtration membrane
+to compress the hydrogel and separate it from the solution. In their
+method first, the deswollen hydrogel was equilibrated with saline
+water feed. During equilibration, the gel was swelling absorbing water.
+Then it was taken out from the feed solution and mechanically compressed
+by means of a microfiltration membrane. The squeezed out brine was
+obtained to have lower salinity than the feed water.
+
+A similar approach was used by Ali \etal \cite{Ali2015}. In their
+study the thermosensitive gel was used (based on copolymers p-NIPAAm
+and p-AA), so instead of physical compression, the dewatering was
+done by an external heating stimulus (sunlight). At night the gel
+was equilibrating with feed water and at daytime, under sunlight,
+the gel was shrinking and releasing the collected inside water.
+
+\paragraph{Physics behind the desalination process.}
+
+\begin{figure*}
+\centering 
+\includegraphics[width=0.5\textwidth]{figures/gc}\includegraphics[width=0.5\textwidth]{figures/gibbs}\caption{Diamond-like network in the simulation box. Color code represents
+the individual ion types (red: $\na$, blue: $\cl$, yellow: $\ca$)
+and the hydrogel (gray: neutral segment ($\AH$), cyan: charged segment
+($\A$)). \label{fig:open and closed}.}
+\end{figure*}
+
+The maximum entropy principle requires the density of charges to be
+more-less the same throughout the system medium. Since the polyelectrolyte
+gel has its own charges and its own neutralizing counterions, the
+density of mobile ions (which are able to freely enter and leave the
+gel) in gel appears to be smaller than their density outside the gel.
+Therefore the internal solution of the gel has lower density of mobile
+ions than the solution outside. In that sense, the gel acts as an
+osmotic membrane separating solutions \cite{Rud2020}. The driving
+force of the separation is the Donnan potential originated from the
+charges of the hydrogel network. The density of mobile ions difference
+between ions concentrations in the internal and external solutions
+is defined by Donnan law \cite{Rud2018}
+\[
+\frac{c_{-}^{in}}{\cs}=\frac{\cs}{c_{+}^{in}}=\sqrt{1+\left(\frac{\alpha\cp}{2\cs}\right)^{2}}\pm\frac{\alpha\cp}{2\cs}
+\]
+where $c_{-}^{in}$ and $c_{+}^{in}$ are the internal concentration
+of anions and cations, $\cs$ is the salinity of external solution
+$\cp$ and $\alpha$ are the gel molar density and the ionization
+degree. The $\pm$ sign in the formula depends on whether the gel
+is made of polyanion or polycation.
+
+The internal solution can be extracted by means of compression and/or
+other stimulus providing that the charge of the gel remains constant.
+In the case of gel made of weak (pH-sensitive) polyelectrolyte, the
+compression initiates discharging of the gel, therefore the neutralizing
+counterions may leave out the gel diminishing the desalination effect
+and affecting the pH of the extracted solution. Nevertheless, the
+release of counterions may be employed for desalination as well and
+the way how to do it is discussed in\cite{Rud2018}. 
+\begin{enumerate}
+\item However, one can argue that sole Donnan effect is insufficient to
+achieve a high salt rejection \cite{Cai2016} and the salinity of
+the water squeezed from hydrogel under a very high hydraulic pressure
+(up to 100 bar \cite{Fengler_2020}) turns to be not much different
+from the initial.
+\item Indeed, the use of high hydraulic pressure diminishes all the advantages
+of this method over the reverse osmosis. At the same time the reversibility
+of hydrogel swelling after such strong compression remains questionable. 
+\item Nevertheless by the current study we would like to model the compression
+of the gel limiting ourselves within low compression rates, less than
+5 bar. We will show how the compression of the gel affects the surrounding
+salinity and model the whole desalination process as a cascade of
+$c$. 
+\end{enumerate}
+In the current study we would like to concentrate on the use of gel
+made of strong polyelectrolyte for water desalination. Namely, to
+investigate how the compression of the gel affects the salinity of
+the surrounding the gel solution and to propose the way of water desalination
+employing the hydrogel swelling/deswelling set of processes.
+
+The target of our study is to model the thermodynamic equilibrium
+between the two boxes and to show how the compression of the gel affects
+the ion density in the outside solution.
 
@@
 
-\reffig{fig:diamond} presents a diamond-like polymer network inserted in a simple cubic simulation box of volume $V_{\mathrm{box}}$ with periodic boundaries.
-The network consists of $16$ linear \PE{} chains, each chain comprising $30$ monomer units.
-Each unit is able to change its ionization state from charged to neutral and vice versa according to the ionization equilibrium.
-The mobile ions ($\na$, $\cl$ and $\ca$) are present in certain amount such that they fulfill the electroneutrality condition.
+\begin{figure*}
+\centering \includegraphics[width=0.5\textwidth]{figures/simgibbs}\caption{Diamond-like network in the simulation box. Color code represents
+the individual ion types (red: $\na$, blue: $\cl$, yellow: $\ca$)
+and the hydrogel (gray: neutral segment ($\AH$), cyan: charged segment
+($\A$)). \label{fig:diamond}.}
+\end{figure*}
 
-We model the network in equilibrium with the bulk of aqueous solution.
-In order to keep the equilibrium conditions we consider three processes to occur:
+\subsection{Model}
 
+We model our gel as a network of 16 linear polymer chains, each by
+30 monomer units. The chains are connected to a diamond-like polymer
+network and put into a simulation box with periodic boundaries. Each
+unit of the network carries a negative electric charge, which is equal
+to the charge of electron. Except the particles of the network, the
+mobile monovalent ions, $\na$ and $\cl$, are present in simulation
+box. The total electric charge of all the particles in the box is
+zero, therefore the amount of $\na$ ions is bigger than that of $\cl$
+by the number of hydrogel units, $N\gel=16\cdot30=480$.
+
+The goal of this study is to simulate the process of water desalination
+by means of compression. In order to do it we simulate the gel in
+two ensembles.
 \begin{enumerate}
-	\item the thermal movement of all segments in simulation box (Langevin dynamics);
-	\item the transfer of ions between two vessels:
-        \item the change of ratio between volumes of the two vessels emulationg the piston applying certain pressure to one of the vessels:
-%\todoi{We shall get rid of $\so$ ions and mention it in the inroduction. The reason is that their concentration is small, and they do not enter the hydrogel }
+\item The first is so called \emph{open system}, when the simulation box
+with gel freely exchanges ions with a big amount of aqueous solution
+of certain constant salinity. 
+\item And in \emph{closed system}, when the gel is in equilibrium with a
+finite volume of aqueous solution.
+\end{enumerate}
+The compression of the gel in the open system does not affect the surrounding salinity, thus the chemical potential of ions remains constant $\muna=$ $\mucl=$ $\text{Const}$. 
+On the contrary, what remains constant in the closed system is total number of ions, that are contained in the gel and in the external volume, $\nna=\text{Const}$ and $\ncl=\text{Const}$.
+By $\nna$ and $\ncl$ we will understand the density of the corresponding ion in the compression volume
+\begin{equation}
+\ncl = \left(\ncl\gel + \cs\cdot(\Vbox - \Vgel)\right)/\Vbox
+\end{equation}
+\paragraph{Open system.}
+
+We simulate the open system using the grand reaction method \cite{Landsgesel2020a,Rud2020}.
+This method is a hybrid of molecular dynamics (MD) and Monte Carlo
+(MC). The whole simulation represents a chain of subsimulations of
+MD and MC followed one by each other. For MD simulation we used a
+standard Langevin dynamics \cite{Grest1986} which models the mechanical
+movement of all the system particles. Whereas MC simulates the thermodynamic
+equilibrium with reservoir, which exchanges ions with the simulation
+box. The insertion (and deletion) of ion pairs is considered as a
+reaction of creation (or annihilation) of an ion pair 
+\[
+\varnothing\stackrel{K}{\leftrightarrows}\na+\cl
+\]
+with a reaction constant defined by the chemical potential of ions,
+$K=\exp\left(\muna+\mucl\right).$
+
+\paragraph{Closed system.}
+
+The similar scheme we use to simulate the gel in closed system. The
+procedure represents a chain of subsequent MD and MC simulation, but
+now we run the molecular dynamics in two simulation boxes simultaneously.
+The first box of the volume $\Vgel$ contains the gel with ions, and
+the second box, $\Vout$--- contains only ions. These two boxes are
+represented in Figure~\ref{fig:diamond}. The total volume of both
+boxes is kept constant, $V=V_{\mathrm{gel}}+V_{\mathrm{out}}$, so
+the compression of the gel implies the decrease $\Vgel$ and increase
+$\Vout$.
+
+The thermodynamic equilibrium between the two volumes implies the
+exchange of the ion pairs between them, which is done by means of
+MC procedure in a way similar to described in \cite{Panagiotopoulos1988b}.
+
+\paragraph{Algorithm.}
+
+In general the simulation algorithm is following:
+\begin{enumerate}
+\item simulate molecular dynamics in both boxes; collect the observables,
+for examples pressure values $P$, to an array; 
+\item perform Monte-Carlo procedure simulating ion pair exchange; collect
+the arrays ofobservables sample : number of ions in both boxes, $\nna^{I}$,
+$\ncl^{I}$, $\nna^{II}$ and $\ncl^{II}$ ; 
+\item repeat the procedure until the desired length of sample arrays is
+reached.
 \end{enumerate}
 
-All three processes occur simultaneously in real systems, however, we simulate them alternating each other in stop-run mode in a random order.
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=0.5\columnwidth]{{figures/vmdscene}.pdf}
+\section{Results and discussion }
+
+\paragraph{Compression in open system.}
+
+First we run a set of simulations modeling the gel compression in \emph{open system}, \ie in equilibrium with big bath of certain salinity, $\cs$. 
+The simulations are run for a set of different simulation box volumes. 
+Each simulation returns the averaged pressure, $P$, and the number of $\cl$ ions present in the simulation box, $\ncl$.
+
+In order to get the partial pressure of the gel, we substitute from $P$ the osmotic pressure of ions in reservoir: $P^{gel}=P-P^{res}$.
+$P^{res}$, in turn, we calculate by running a separate simulation of a reservoir, containing ionic gas in equilibrium with the bath of the same salinity $\cs$. 
+The gel partial pressure, $\Pgel$, is the pressure which needs to be applied to the gel via solvent permeable filter to compress the gel to a molar specific volume, $V$.
+
+The dependencies of $\Pgel$ versus gel molar volume $\Vgel$ (the volume calculated per one mol of gel segment) are present in Figure \ref{fig: PV} for a set of different salinity. 
+These dependencies corresponding to \emph{open system} are represented here by solid lines. 
+For example, blue solid line illustrates the compression (or swelling) of the gel in equilibrium with a reservoir of salinity, $\cs=0.063$ mol/l. 
+The points where the pressure equals to zero, $\Pgel=0$, (indicated by filled circles) are the gel \emph{free swelling equilibrium} states. 
+It is seen, that the increase of salinity shifts the free swelling equilibrium towards smaller volumes, \ie the gel shrinks with increasing salinity. 
+In general, all the solid curves shift towards smaller volumes with increasing salinity. 
+This effect is well known, and is typical for all branched \emph{strong} polyelectrolytes. 
+It is caused by the decrease of ions osmotic pressure and by screening of electrostatic interactions \cite{Zhulina2000,Landsgesel2020a}.\footnote{The salinity dependence of the size of \emph{weak} polyelectrolyte gel is in general non-monotonic \cite{Rud2018} but the case of weak polyelectrolyte is beyond the scope of this study.
+} %
+
+\paragraph{Compression in closed system.}
+
+\begin{figure*}[t]
+\subfloat[Partial pressure of the gel versus gel molar volume \label{fig: PV}]
+{\includegraphics[width=0.48\textwidth]{figures/fig_PV_pub}}
+\hspace{0.02\textwidth}
+\subfloat[Supernatant salinity versus gel molar volume\label{fig: CV}]
+{\includegraphics[width=0.48\textwidth]{figures/fig_CV_pub}}
 \caption{
-       	Diamond-like network in the simulation box. 
-	Color code represents the individual ion types
-	(red: $\na$, blue: $\cl$, yellow: $\ca$) and
-        the hydrogel (gray: neutral segment ($\AH$), cyan: charged segment ($\A$)).
-    }
-    \label{fig:diamond}
-    %in order to make snapshot use file snapshot.py
-    % in order to edit the existing snapshot use file data/gel_MPC30_box_l53.0_pK7.00_pH7.00_pCl2.00_pCa2.94_lB0.0.vmd
-\end{figure}
-\todo{remove $\ca$ ions from snapshot}
-\subsection{Langevin dynamics\label{MD}}
+The compression of the gel in open system (solid lines) and in closed system (dotted lines). 
+Each solid curve corresponds to different salinity of the reservoir $\cs$ (see legend). Shadowed area limit the states with applied pressure below zero and above 5 bar.\label{fig: PV and CV}}
+\todoi{replace $V$ by $\Vgel$ in Figures}
+\end{figure*}
 
-We use three types of interactions, \ie bonded interactions, short-range non-bonded interactions and electrostatic interactions.
+Each set of simulations in an \emph{open system} defines the free swelling equilibrium state of the gel for each salinity. 
+Namely, each salinity correspond to a certain gel molar volume, and to a certain amount of ions in gel in equilibrium state, $\cs\longrightarrow$, $\left(\Vgeleq,\ \ncleq\right)$.
+These equilibrium states we use as starting ones for the gel compression in \emph{closed system}. 
+Thus, we simulate the compression of the gel in the closed volume, $\Vbox$, which is equal to $\Vgeleq$, and contains $\ncleq$ of ion pairs (apart from neutralizing counterions). 
+So, we prepare two systems, one~--- simulating the gel of the volume $\Vgel$, and another~--- simulating the supernatant solution of the volume $\Vout = \Vbox - \Vgel$; in this way the total volume containing the gel and the supernatant solution remains constant.
+Also, the ion pairs of the amount $\ncleq$ remain all the time constant and are shared between the two volumes.
+%For each different initial states we run a set of simulations emulating the compression of the gel, \ie varying simultaneously $\Vgel$ and $\Vout$.
+%At any all the ions are getting redistributed between the systems but their total amount remains constant and equal to $\ncl^{0}$.
 
-We use Finite extension nonlinear elastic (FENE) potential~\refeq{eq:fene} to account for the bonding interactions.
-%The potential accounts for nonlinear elastic extensions and as a consequence, the simulation is not constrained too much.
-\begin{equation}\label{eq:fene}
-    V_\mathrm{FENE}(r) = -\frac{1}{2} K \Delta r_\mathrm{max}^2\ln \left[ 1 - \left(\frac{r-r_0}{\Delta r_\mathrm{max}} \right)^2 \right ],
+The process of the gel compression in \emph{closed} system is depicted in Figure~\ref{fig: PV} (dotted lines). 
+There the gel partial pressure is depicted as function of the gel molar volume.
+In this plot, the blue dotted line, for example, illustrates the compression of the gel equilibrated with the solution of salinity $\cs=0.063$ mol/l, in a volume which gel has at zero pressure. 
+Since, in this case, the volumes of the gel $\Vgel$ and of the supernatant solution $\Vout$ are comparable, the compression of the gel affects the salinity of supernatant solution. 
+The salinity now decreases, changing from $\cs^{0}=0.063$ at free swelling equilibrium state to 0.045 mol/l at $P\gel=5$ bar.
+
+The change of salinity is seen from Figure~\ref{fig: CV}. 
+In this Figure the gel swelling/compression processes are illustrated in different coordinates, \ie salinity of supertnatant outside the gel versus the gel molar volume, $\cs(\Vgel)$.\todo{we should stick to only 'supernate' or 'supernatant'}
+%Similarly, as in Figure~\ref{fig:fig PV}, the solid lines correspond to compression in \emph{open} system and dotted lines~--- in \emph{closed} system. 
+In this coordinates, all the open system compressions turn to the horizontal lines, which reflects the constant salinity, but the compressions in closed system indicate the decrease of $\cs$s.
+% Maybe "In this coordinates, each open system compression turns to the horizontal line, which reflects the constant salinity, whereas each compression in closed system shows the decrease of $\cs$s." would be better
+
+Although the salinity during compression in \emph{open} system remains constant, the number of ions in a compression volume, i.e. in the volume where the gel is compressed, changes.
+As the compression volume $\Vbox$ we chose the volume of the free swelling equilibrium state of the gel, $\Vbox = \widetilde{\Vgel}$ 
+In the Figure \ref{fig: NV} we depicted the number of $\cl$ ions in the volume $\Vbox$, calculated per unit volume, $\ncl/\Vbox$, as a function of the gel molar volume. 
+The depicted value can be considered as the density of $\cl$ ions averaged out over the volume $\Vbox$.
+
+As it is expected in case of closed system these dependencies look like horizontal lines, whereas in open system, the amount of ions in compression volume increases with compression. 
+This implies, that the compression of the gel in open system pulls out the ions from the bath to the compression volume. 
+And vice versa, the swelling of the gel pushes ions out to the bath.
+
+Finally in Figure \ref{fig: CN} the same processes are depicted in coordinates number of particles in compression volume --- salinity of the outside solution. 
+In this coordinates both ways of the compression, in \emph{open} and in \emph{closed} system, appear as straight vertical and horizontal lines correspondingly.
+
+In our study we modeled the compression of the gel in equilibrium with reservoirs of 40 different salinities, ranging from 0.001 to 0.5 mol/l. 
+Every open system compression resulted a defined free swelling equilibrium state, \ie the the gel molar volume and the number of ions in gel $\left(\Vgeleq,\ \ncleq\right)$ at zero pressure.
+These states were used as the initial ones for the compression in closed systems. 
+All the corresponding dependencies are depicted in Figures~\ref{fig: PV and CV} and \ref{fig: NV and CN} as thin grey dashed lines. 
+The states corresponding to $P^{gel}=0$, 5 and 10 bar pressure are marked by open circles, squares and crosses respectively. 
+The non-shadowed areas on the Figures limit the states corresponding to gel partial pressure ranging between 0 and 5 bar.
+
+\begin{figure*}[t]
+\subfloat[Pressure vs gel density \label{fig: NV}]
+{\includegraphics[width=0.49\textwidth]{figures/fig_NV_pub}}
+\subfloat[Salinity vs gel density\label{fig: CN}]
+{\includegraphics[width=0.495\textwidth]{figures/fig_NVbox_mu_pub}}
+\caption{The compression of the gel in open system (solid lines) and in closed
+system (dotted lines). Each solid curve corresponds to different salinity
+of the reservoir $\cs$ (see legend). Shadowed area limit the states
+with applied pressure below zero and above 5 bar.\label{fig: NV and CN}}
+%\todoi{Replace y-axis labels by $\ncl$}
+\end{figure*}
+
+\paragraph{Desalination scheme.}
+
+As we have seen, the compression of the gel in a closed system affects the salinity, whereas the compression in an open system affects the amount of ions in a volume where the gel is compressed in. 
+Here we show how to employ these phenomena for water desalination. 
+The highlighted colored lines on plots of Figures \ref{fig: PV and CV} and \ref{fig: NV and CN} form a sequence of the following one by each other swellings and compressions of the hydrogel, correspondingly in \emph{open} and \emph{closed} systems.
+This sequence forms the water desalination process.
+Starting from swelling the gel in the \emph{open} system at high salinity ($\cs=0.091$ mol/l, solid black line), the gel gets compressed in \emph{closed} system until the pressure reaches 5 bar (dashed black line).
+Then the same gel swells in a reservoir of a bit lower salinity (\ie $\cs=0.064$ mol/l, light blue line). 
+After swelling, the gel is compressed again by the pressure of 5 bar in \emph{closed} system (dashed light blue line).  
+Then it is put swelling in a reservoir of even smaller salinity ($\cs=0.045$ mol/l, solid yellow line). 
+And so on. 
+The chain of alternating swelling and compression steps ends up when salinity gets equal to $\cs=4\cdot10^{-3}$ mol/l after compression in closed system (dashed magenta line).
+
+The plots of Figures \ref{fig: PV and CV} and \ref{fig: NV and CN} depict the whole process in all the possible coordinates
+In all the plots the whole process looks like a staircase, especially in the Figure~\ref{fig: CN}, where open system processes are horizontal lines and closed system are vertical ones, a 'staircase' has rectangular steps
+
+%\begin{enumerate}
+%    \item as gel partial pressure versus gel molar volume, $\Pgel(\Vgel)$ (\ref{fig: PV}), 
+%    \item as supernatant salinity versus gel molar volume, $\cs(\Vgel)$ (\ref{fig: CV}),
+%    \item the amount of $\cl$ ions in a compression volume versus gel volume, $\ncl(\Vgel)$ (\ref{fig: NV}), 
+%    \item $\ncl$ as function of supernatant salinity.
+%\end{enumerate}
+
+\todo{we could get rid of saying 'gel molar volume' if we state elsewhere that all the values are calculated per one mol of the gel}
+
+%Then we repeat the simulation of hydrogel swelling in open system but setting as a salinity of the reservoir the new, obtained from the previous process, value $\cs=$ 0.045 mol/l. 
+%Again, as soon as we obtain the free swelling equilibrium state (at new salinity), with corresponding new values of $V\gel$ and $\ncl$, we start simulating the compression in closed system.
+Now the salinity changes again, decreasing from 0.045 to 0.031 mol/l (at 5 bar).
+%These two processes are depicted by solid and dotted yellow lines in Figure~\ref{fig:fig_PV}.
+%The Figure shows also the repetition of this procedure three more times until the salinity reaches the value $\cs=0.01$ mol/l. 
+%The last dashed magenta line shows the compression in closed system which ends up with $\cs=4\cdot10^{-4}$ mol/l. 
+%Schematically this process is depicted in the inset to the plot.
+
+%The same process is depicted on Figure~\ref{fig:fig_CV} but in different coordinates: salinity versus volume. 
+%In this coordinates the swelling in open system appear to be horizontal line, since the salinity in this process is constant. 
+%Again we start from swelling in open system untill the gel reaches its free swelling equilibrium (solid blue line).
+%Then the gel is compressed in closed system (dashed blue line), ending up in a state with applied to the gel pressure 5 bar. 
+%In this process the surrounding solution salinitiy changes from 0.064 to 0.045 mol/l.
+%Then the gel again swells in open system, but at new salinity.
+
+\paragraph{The efficiency of desalination.}
+The theoretical minimum specific energy for seawater desalination ($\cs=35$ g/l, $\simeq0.6$ mol/l as for pure NaCl) is 1.1 kWh/m3 (3.9 kJ/L) for 50\% recovery \cite{Wang_2020}.
+This value is calculated as follows 
+\begin{equation}
+W=2RT\left(\frac{c_{f}}{R_{w}}\ln\frac{c_{b}}{c_{f}}-c_{p}\ln\frac{c_{b}}{c_{p}}\right)
+\label{eq:SEC}
 \end{equation}
-where $K$ is the magnitude of symmetric interaction between two segments,
-$\Delta r_{\mathrm{max}}$ is the maximal stretching length of the bond and $r_0$ is the equilibrium bond length.
-In our simulations we set $K = 10 \kT/\sigma^{2}$, $\Delta r_{\mathrm{max}} = 2 \sigma$ and $r_0 = 1.0\sigma$~\cite{Jin2007}.
+where $R$ is a universal gas constant, $c_{f}$ is the salinity of feed water, $c_p$~--- of product water and $c_b$~--- the salinity of the brine, which necessarily appears in any desalination process.
+$R_{w}$ is a recovery ratio, \ie the ratio between volume of produced water and the volume of the feed water. 
+50\% recovery ratio means that one part of feed water divides into two equal volume solutions of the product water and of the brine.
+Of course, a significant amount of additional energy is required to operate the system\cite{Kim_2019}. 
+It has been reported that the specific energy consumption (SEC) of reverse osmosis (RO) process is 2.5~-- 4.0 kWh/m3 (9~-- 14.4 kJ/l), which is significantly higher than its minimum specific energy.
+The SEC of a real-scale RO plant is even higher, approximately 3.5~-- 4.5 kWh/$m^{3}$ (12.6 - 16.2 kJ/L), including pre-treatment and post-treatment processes \cite{Kim_2018}. 
+%Because of the inherent high energy requirement for RO desalination, seawater is not commonly utilized over traditional surface water.
 
-We model the non-bonded interactions using truncated Lennard-Jones interaction potential.
-This potential imposes strong repulsion between all particles at short distances:
+In order to compare the efficiency of the process presented in \ref{fig: PV and CV} and \ref{fig: NV and CN} with provided values we collect the corresponding data to the Table~\ref{tab: table}.
+The presented desalination process is a cascade of six swellings in open system, at six different (constant) salinities $\cs$, each followed by six compressions in closed system, at six different (constant) $\ncl$.
+Each swelling and compression presented as a row of the Table~\ref{tab: table}, which is collored to matching to the lines on Figures.
+The first column of the table contains values $\cs^0$ and $\cs^5$, which stand for the supernatant salinity at 0 and 5 bar compression; in open system supernatant salinity does not change, so $\cs^0$ and $\cs^5$ are presented by a single number.
+The second column contains values of $n^0$ and $n^5$, which stand for the number of $\cl$ ions in compression volume at 0 and 5 bar pressure.
+\todo[fancyline]{it is not a number but a number in unit volume}
+The number of ion does not change in closed system compression, thus $n^0$ and $n^5$ are the same in corresponding row.
+The fourth column shows the change of the volume in corresponding process, $\Delta v$. 
+The fifth column contain the work needed for the compression in the corresponding process, calculated per volume of extracted solution. 
+This value is calculated as integral of corresponding $\Pgel(\Vgel)$ dependence
 \begin{equation}
-    \begin{split}\label{eq:LJ}
-        V_\mathrm{LJ}(r) =
-        \begin{cases}
-            4 \varepsilon \left( \left(\cfrac{\sigma}{r}\right)^{12}
-            - \left(\cfrac{\sigma}{r}\right)^6\right)
-            & \mathrm{if~} r < r_\mathrm{cut}\\
-            0
-            & \mathrm{elsewhere}
-        \end{cases},
-    \end{split}
+    W = \frac{\int_{v^0}^{v^5} \Pgel d\Vgel}{\Delta v}
 \end{equation}
-where $r$ is the interparticle distance,
-$\sigma = 0.35 \mathrm{nm}$ is the characteristic size of the particles,
-$\varepsilon$ is the depth of the potential well in $\kT$ units and $r_\mathrm{cut}$ is the cut-off distance beyond which the potential is set zero.
+Here, in the table we present the absolute value, whereas one should keep in mind that the compression implies the work which is done by external force, whereas the swelling implies the work which is done by gel.
+\todo{may be we return back the 'minuses' to the W values}
 
-We model the long range electrostatic interactions by the Coulomb potential:
-\begin{equation}
-    V_{\mathrm{EL}}=\lb\kT \cfrac{q_{1}q_{2}}{r},
-\end{equation}
-where $\lb$ is Bjerrum length. We set $\lb = 2\sigma = 0.7 \mathrm{nm}$ which corresponds to water at $T=300 \mathrm{K}$.
+\begin{table*}[h]
+\caption{\label{tab: table}All the units calculated per one mol of gel segments.}
+\begin{tabular*}{1\textwidth}{@{\extracolsep{\fill}}|ll|ll|l|l|ll|}
+\hline 
+\multicolumn{1}{|l|}{$c_{s}^{0}$, M} & $c_{s}^{5}$,M & \multicolumn{1}{l|}{$\ncl^{0}$} & $\ncl^{5}$ & $\Delta v$, l & $|W$\textbar , J/L & \multicolumn{2}{c|}{$W^{id}$, J/L}\tabularnewline
+\hline 
+\multirow{2}{*}{0.092} & \multirow{2}{*}{} & \multirow{2}{*}{0.057 $\rightarrow$} & \multirow{2}{*}{0.072} & \multirow{2}{*}{2.74} & \multirow{2}{*}{95.4} &  & \multirow{2}{*}{}\tabularnewline
+ &  &  &  &  &  & \multirow{8}{*}{\hspace{-1em}\textcolor{teal}{$\left.\begin{array}{l}
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\end{array}\right\rbrace $$\rotatebox{90}{\hspace{-3.8em}\ensuremath{\begin{array}{cc}
+W^{id}= & (52.9)\\
+R_{w}= & 0.54
+\end{array}}}$}} & \tabularnewline
+\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
+\multirow{2}{*}{0.089 $\rightarrow$} & \multirow{2}{*}{0.074} & \multirow{2}{*}{0.057} & \multirow{2}{*}{} & \multirow{2}{*}{2.72} & \multirow{2}{*}{109.1} &  & \multirow{2}{*}{}\tabularnewline
+ &  &  &  &  &  &  & \tabularnewline
+\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
+\multirow{2}{*}{\textcolor{teal}{0.064}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{teal}{0.037 $\rightarrow$}} & \multirow{2}{*}{\textcolor{teal}{0.051}} & \multirow{2}{*}{\textcolor{teal}{3.26}} & \multirow{2}{*}{\textcolor{teal}{100.9}} &  & \tabularnewline
+ &  &  &  &  &  &  & \multirow{8}{*}{\hspace{-1em}\textcolor{olive}{$\left.\begin{array}{l}
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\end{array}\right\rbrace $$\rotatebox{90}{\hspace{-3.8em}\ensuremath{\begin{array}{cc}
+W^{id}= & 38.2\\
+R_{w}= & 0.53
+\end{array}}}$}}\tabularnewline
+\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
+\multirow{2}{*}{\textcolor{teal}{0.062 $\rightarrow$}} & \multirow{2}{*}{\textcolor{teal}{0.048}} & \multirow{2}{*}{\textcolor{teal}{0.037}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{teal}{3.18}} & \multirow{2}{*}{\textcolor{teal}{107.4}} &  & \tabularnewline
+ &  &  &  &  &  &  & \tabularnewline
+\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
+\multirow{2}{*}{\textcolor{olive}{0.045}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{olive}{0.024 $\rightarrow$}} & \multirow{2}{*}{\textcolor{olive}{0.036}} & \multirow{2}{*}{\textcolor{olive}{3.82}} & \multirow{2}{*}{\textcolor{olive}{106.7}} &  & \tabularnewline
+ &  &  &  &  &  & \multirow{8}{*}{\hspace{-1em}\textcolor{red}{$\left.\begin{array}{l}
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\end{array}\right\rbrace \rotatebox{90}{\hspace{-3.8em}\ensuremath{\begin{array}{cc}
+W^{id}= & 43.8\ {\color{red}{\scriptstyle (41.0)}}\\
+R_{w}= & 0.52\ {\scriptstyle (0.46)}
+\end{array}}}$}} & \tabularnewline
+\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
+\multirow{2}{*}{\textcolor{olive}{0.044 $\rightarrow$}} & \multirow{2}{*}{\textcolor{olive}{0.031}} & \multirow{2}{*}{\textcolor{olive}{0.024}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{olive}{3.91}} & \multirow{2}{*}{\textcolor{olive}{106.4}} &  & \tabularnewline
+ &  &  &  &  &  &  & \tabularnewline
+\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
+\multirow{2}{*}{\textcolor{red}{0.032}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{red}{0.015 $\rightarrow$}} & \multirow{2}{*}{\textcolor{red}{0.025}} & \multirow{2}{*}{\textcolor{red}{4.20}} & \multirow{2}{*}{\textcolor{red}{107.9}} &  & \tabularnewline
+ &  &  &  &  &  &  & \multirow{8}{*}{\hspace{-1em}\textcolor{orange}{$\left.\begin{array}{l}
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\end{array}\right\rbrace \rotatebox{90}{\hspace{-3.8em}\ensuremath{\begin{array}{cc}
+W^{id}= & 66.6\ {\scriptstyle (22.0)}\\
+R_{w}= & 0.53\ {\scriptstyle (0.49)}
+\end{array}}}$}}\tabularnewline
+\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
+\multirow{2}{*}{\textcolor{red}{0.030 $\rightarrow$}} & \multirow{2}{*}{\textcolor{red}{$\begin{array}{c}
+0.019\\
+{\scriptstyle (0.022)}
+\end{array}$}} & \multirow{2}{*}{\textcolor{red}{0.015}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{red}{$\begin{array}{c}
+4.17\\
+{\scriptstyle (3.22)}
+\end{array}$}} & \multirow{2}{*}{\textcolor{red}{$\begin{array}{c}
+115.6\\
+{\scriptstyle (57.3)}
+\end{array}$}} &  & \tabularnewline
+ &  &  &  &  &  &  & \tabularnewline
+\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
+\multirow{2}{*}{\textcolor{orange}{0.022}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{orange}{0.009 $\rightarrow$}} & \multirow{2}{*}{\textcolor{orange}{$\begin{array}{c}
+0.018\\
+{\scriptstyle (0.015)}
+\end{array}$}} & \multirow{2}{*}{\textcolor{orange}{$\begin{array}{c}
+4.75\\
+{\scriptstyle (3.76)}
+\end{array}$}} & \multirow{2}{*}{\textcolor{orange}{$\begin{array}{c}
+108.1\\
+{\scriptstyle (68.3)}
+\end{array}$}} &  & \tabularnewline
+ &  &  &  &  &  & \multirow{7}{*}{\hspace{-1em}\textcolor{magenta}{$\left.\begin{array}{l}
+\\
+\\
+\\
+\\
+\\
+\\
+\end{array}\right\rbrace \rotatebox{90}{\hspace{-3em}\ensuremath{\begin{array}{cc}
+W^{id}= & 69.7\\
+R_{w}= & 0.55
+\end{array}}}$}} & \tabularnewline
+\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
+\multirow{2}{*}{\textcolor{orange}{0.021 $\rightarrow$}} & \multirow{2}{*}{\textcolor{orange}{0.011}} & \multirow{2}{*}{\textcolor{orange}{0.009}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{orange}{$4.71$}} & \multirow{2}{*}{\textcolor{orange}{110.8}} &  & \tabularnewline
+ &  &  &  &  &  &  & \tabularnewline
+\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
+\multirow{2}{*}{\textcolor{magenta}{0.011}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{magenta}{0.003 $\rightarrow$}} & \multirow{2}{*}{\textcolor{magenta}{0.009}} & \multirow{2}{*}{\textcolor{magenta}{6.08}} & \multirow{2}{*}{\textcolor{magenta}{106.9}} &  & \tabularnewline
+ &  &  &  &  &  &  & \tabularnewline
+\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
+\multirow{2}{*}{\textcolor{magenta}{0.010 $\rightarrow$}} & \multirow{2}{*}{\textcolor{magenta}{0.004}} & \multirow{2}{*}{\textcolor{magenta}{0.003}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{magenta}{5.78}} & \multirow{2}{*}{\textcolor{magenta}{119.4}} &  & \tabularnewline
+ &  &  &  &  &  &  & \tabularnewline
+\hline 
+\end{tabular*}
+\end{table*}
 
-We use Langevin thermostat, \ie
-we add two additional terms to force in equation of motion
-\begin{equation}
-f_i =  -\gamma v_i(t)+\sqrt{2\gamma \kT }\eta_i(t),
-\end{equation}
-where the first term correspond to constant friction with $\gamma$ being a friction coefficient, and the second one corresponds to random thermal force with $\eta_i$ being a normally distributed random number (see for details \cite{Grest1986}).
+The six column \todo{check if it is sixth column} contains the values of specific energy consumption, $W^\text{id}$, which are calculated as follows.
+We consider, for example, the solution of concentration $\cs^f=0.045$ M as a feed solution, and the solutions of $\cs^p=0.032M$ and $\cs^b=0.064M$ correspondingly as produced product and brine solutions.
+\begin{enumerate}
+    \item first the gel is equilibrated with feed solution is getting compressed in closed system. 
+    The salinity of supernatant decreases from $\cs^f$ to $\cs^p$.
+    The change of the gel volume equals to $\Delta v^p =$ 3.69 l, so does the  the volume of produced desalinated solution
+    \item Then the squeezed gel is put back to feed solution and getting equilibrated with it under pressure 5 bar, so that it does not swell. 
+    \item then the squeezed gel is let to swell in closed system such that the salinity of external solution increases reaching the value of $\cs^b$
+    \item finally, the gel is taken out and squeezed by 5 bar in open system in equilibrium with the bath of the brine. 
+    The change of the gel volume in this process is $\Delta v^b =$ 3.26 l, so that the volume of the produced brine. 
+\end{enumerate}
+The recovery ratio $R_w = \Delta v^p / (\Delta v^p + \Delta v^b) simeq $ 0.53
+The theoretical minimum specific energy of desalination with corresponding $\cs^f$, $\cs^p$ and $\cs^b$, according to \refeq{eq: SEC} is $W^{id} =$ 38.2 J/l
 
-%where $\gamma$ is the friction coefficient and .
-%\todo{there is friction and there is random force ballanced by fluctiation dissipation theorem so that it is stationary}
-%which causes the decrease of the particles' velocities.
-%This is implemented by addition of two corresponding terms to the particles' equations of motion, namely
-%\todo{usually -gamma v to keep gamma>0}
-%where the first term correspond to
+\todoi{Start from here next time}
 
-%\paragraph{Units} % apart from cref reference all references are in the text. Do we need cref?
-%By setting up the interaction potentials we defined the system of units.
-%We have chosen the unit of length being based on the Bjerrum length in water at room temperature, $l_B \simeq 7$nm, and $\sigma=0.5l_B = 0.35$.
-% % %Then the unit of concentration is $\cref=(\sigma^{3}\NA1000)^{-1}$mol/l. % % % do we need to say that?
-%We set the energy unit to be $\varepsilon = \kT$.
-
-\section{Sampling in the Gibbs ensemble\label{sec: sampling the gibbs ensemble}}
-All thermal moves are frozen during the sampling of the ion pairs exchange.
-The system represents the ensemble with constant number of particles distributed between two vessels (I) and (II).
-
-In the following paragraph we derive the criteria for sampling of the ion exchange equilibrium.
-\paragraph{Gibbs canonical ensemble}
-Let us first consider the total free energy of both vesselsassuming that we have only particles of a single type:
-\begin{equation}
-    F=\left(E_{I}-TS_{I}\right) + \left(E_{II}-TS_{II}\right) \label{eq:F-gibbs}
-\end{equation}
-where $E$ is internal energy, $T$~--- temperature, $S$~--- entropy.
-
-%Our model system represents a finite volume $V$ which exchanges particles with the bath of infinite volume.
-%The infinity of the volume means, that the particle exchange between the system and the bath does not influence on the chemical potentials in the bath.
-%Such ensemble is called grand canonical ensemble; the free energy in this ensemble, the Landau potential, is
-The entropy $S$ is given by the Boltzmann formula~\cite{Nagle2004}:
-\begin{equation}
-    S=\kB\ln\frac{V^{N}}{N!}\label{eq:entropy}
-\end{equation}
-%\todo{for partiles without interactions}
-where $N$ is a number of particles in corresponding vessel.
-This formula accounts for two contributions:
+\section{Conclusions}
 \begin{enumerate}
-    \item the combinatorial entropy $S_{c}=-\kB\ln N!$ which reflects the freedom of choice among $N$ particles
-    \item the mixing entropy $S_{m}=\kB N\ln V$ which reflects the freedom to place the chosen particle randomly within the simulation box. 
+\item We have modeled the compression of the gel in thermodynamic equilibrium
+with the reservoir of limited amount of water.
+\item We have shown that in case of gel made of strong polyelectrolyte,
+the compression always lead to decrease of the surrounding salinity.
+\item We have modeled the process of water desalination combining two processes:
+(1) the swelling of the gel in open system, exchanging ions with big
+reservoir at constant salinity. (2) the compression of the gel in
+closed system, when the gel affect the salinity in surrounding solution.
+\item We estimated the energy needed to produce one liter of water and have
+show that the method at least theoretically may compete with the modern
+technologies used in industry nowadays.
 \end{enumerate}
-$V$ is the unitless volume, \ie the volume measured in units of $\sigma^3$. 
-Thus \refeq{eq:F-gibbs} turns to 
-%\todo{this is not reason, moreover A.10 is already wrong as for units}
-\begin{equation}
-    F=\EI-\kT\ln\frac{\VI^{\NI}}{\NI!}\ + \ \EII-\kT\ln\frac{\VII ^{\NII}}{{\NII} !}
-\label{eq: F_gibbs}
-\end{equation}
-When a single particle transferred from the vessel (I) to the  vessel (II) the free energy in vessel (I) changes 
-\begin{equation}
-\Delta \FI = \Delta \EI+\kT\ln\frac{\VI^{\NI}}{\NI !} - \kT\ln\frac{\VI^{\NI-1}}{(\NI-1)!}=\Delta \EI + \kT\ln\frac{\VI}{\NI}
-\end{equation}
-whwereas the free energy change in (II) vessel is
-\begin{equation}
-\Delta \FII = \Delta \EII+\kT\ln\frac{\VII^{\NII}}{\NII !} - \kT\ln\frac{\VII^{\NII+1}}{(\NII+1)!}=\Delta \EII + \kT\ln\frac{\NII+1}{\VII}
-\end{equation}
-Thus the total change of free energy will be 
-\begin{equation}
-\Delta F = \Delta \EI+\Delta \EII+\kT\ln\frac{\VI}{\VII}\frac{\NII+1}{\NI}
-\end{equation}
-Introducing $\xi=\pm 1$, which reflects the direction of movement of particle, $\xi$= +1 if the particles moves from vessel (I) to vessel (II), and $\xi=-1$ if the particles moves backwards, then the previous formula transfers to
-
-\begin{equation}
-\Delta F = \Delta E_{tot}+\kT\xi\ln\frac{\VI}{\VII}\frac{\NII+\theta(\xi)}{\NI+\theta(-\xi)}
-\end{equation}
-where $\theta(x)$ is the Heaviside function.
-
-In order to keep electroneutrality of the system we transfer particles by elctroneutral pairs. 
-Accounting for two types of particles which are moved all the time together the previous formula translates to the following
-\begin{equation}
-\Delta F = \Delta E_{tot}+\kT\xi\left(\ln\frac{\VI}{\VII}\frac{\nnaII+\theta(\xi)}{\nnaI+\theta(-\xi)}    + 
-							    \ln\frac{\VI}{\VII}\frac{\nclII+\theta(\xi)}{\nclI+\theta(-\xi)}             \right)
-\end{equation}
-or
-\begin{equation}
-\Delta F = \Delta E_{tot}+\kT\xi\ln\left(\left(\frac{\VI}{\VII}\right)^2\prod_{i}\frac{\NII^i+\theta(\xi)}{\NI^i+\theta(-\xi)}\right) 
-\end{equation}
-where $i$ runs over the ion types $i\in\{\na,\ \cl\}$.
-
-In order to simulate an ensemble composed of two vessels exchanging particles with each other we need to perform the following Monte Carlo procedure \cite{Frenlkel2002_book, SilvaFernandes2015a, Panagiotopoulos1988b}
-\begin{enumerate}
-	\item we propose the new configuration of the system by removing ion pair from one vessel and inserting it to another
-	\item we accept the new configuration if
-	\begin{equation}
-        \mathcal{R}^{\xi}<e^{\Delta F/\kT}\label{eq: GC acceptance}
-	\end{equation}
-\end{enumerate}
-where $\mathcal{R}$ is uniformly distributed random number in range between $0$ and $1$.
 
@@
 
-This research was supported by the Czech Science Foundation (grant 19-17847Y) (OR, LN, AK),
-Government of Russian Federation, grant number 14.W03.31.0022. % is it really necessary to add this aknowledgement? Who is paid from this project?
-AK thanks the Grant Agency of Charles University for support (project 318120).
-Computational resources were supplied by the project "e-Infrastruktura CZ" (e-INFRA LM2018140) provided within the program Projects of Large Research, Development and Innovations Infrastructures.
+This research was supported by the Czech Science Foundation (grant
+19-17847Y) (OR, LN, AK), Government of Russian Federation, grant number
+14.W03.31.0022. AK thanks the Grant Agency of Charles University for
+support (project 318120). Computational resources were supplied by
+the project ``e-Infrastruktura CZ'' (e-INFRA LM2018140) provided
+within the program Projects of Large Research, Development and Innovations
+Infrastructures.
 
-\bibliographystyle{plain}
-\bibliography{gibbs}
+\bibliography{lit/gibbs}
 
 \newpage
-\pagebreak
+\listoftodos
+
+\newpage
+\section*{Supplementary Information}
+\subsection{Sampling routine}
+Data gained from Molecular Dynamics (MD) and Markov Chain Monte Carlo processes (MD) are highly autocorrelated, thus we can not imply statistic developed for uncorrelated data.
+We have written a small in-house python package to calculate the expected value, the margin of error and effective sample size of correlated data.
+
+The goal of the routine is to estimate mean and margins of error for an observable e.g.
+pressure, number of particles, end-to-end distance of a chain for a given confidence level or effective sample size.
+
+We also provided the way to limit sampling procedure with some timeout value. Our routine based on [] %[https://www.physik.uni-leipzig.de/~janke/Paper/nic10_423_2002.pdf]
+
+There are multiple sampling routines developed for autocorrelated data, i.e. binning analysis, ... %some notes what others do
+
+Expected value of the observable $X$ estimated as the mere mean of the sample $\overline{X}$, the same way one would do for uncorrelated data, whilst to estimate margins of error and \emph{effective} sample size $N_{eff}$ we used the next formulae.
+First of all we have to correct sample size to account that data is correlated:
+\begin{eqnarray}
+    N_{eff} = \frac{N}{2\tau}
+    \\
+    \tau  = \frac{1}{2} + \sum_{k=1}^{N} \text{acf} (k) (1-\frac{k}{N})
+\end{eqnarray}
+where $\tau$ is integrated autocorrelation time, $N$ size of autocorrelated data, $\text{acf} (k)$ is autocorrelation function on lag.
+
+Note that ideally integral of  $\text{acf} (k)$ monotonically approaches some finite value, but due to unavoidable errors in number representation in computer and numeric integration methods it does not hold.
+For that reason instead of $\text{acf} (k)$ integral we use the maximum of its cumulative sum.
+
+Margins of error (MOE) for a given confidence level $\gamma$ and effective sample size $N_{eff}$ is calculated using the next equation:
+\begin{eqnarray}
+    \text{MOE}(\gamma) = \frac{S_{N}}{\sqrt{N_{eff}}} t_{((1+\gamma)/2, N_{eff}-1)}
+\end{eqnarray}
+where $t_{(\alpha, \nu)}$ is percentile function (inverse cumulative distribution function) of Student’s distribution with $\nu$ degrees of freedom for $\alpha$ percentile,
+$S_N$ is standard deviation of the sample.
+
+The true mean of the observable $\mu_X$ lies inside the confidence interval with the confidence level $\gamma$.
+\begin{equation}
+    \Pr(\overline{X} - MOE(\gamma) \leq \mu_X \leq \overline{X} + MOE(\gamma)) = \gamma
+\end{equation}
+
+In our study we set $\gamma = 0.95$
+
+\subsubsection{Routine implementation details}
+%Probably we don't need this section
+
+The arguments of our sampling routine are a function to calculate next sample and one of the next arguments: margins of error, effective sample size and timeout.
+
+An observable is sampled in a loop till one of required targets is met (timeout, the margins of error or sample size). 
+In the each following iteration of the loop, mean value and the margins of error are calculated with ever increasing precision and sample size.
+
+The loop follows the next steps:
+\begin{itemize}
+    \item Sample new data to double the sample size
+    \item Recalculate $\tau$, $N_{eff}$, MOE
+    \item If MOE is less, or $N_{eff}$ is bigger than desired, or run time exceed timeout exit loop
+\end{itemize}
+
+The routine returns mean of the sample, margins of error that defines confidence interval where true mean of distribution lies and \emph{effective} sample size that accounts that data is autocorrelated.
+
+The routine is also described in Figure \ref{fig: sampling_diagram}
+
+\begin{figure*}[t]
+\includegraphics[width = 0.9\textwidth]{figures/sample_to_target_scheme.png}
+\caption{Sampling routine diagram}
+\label{fig: sampling_diagram}
+\end{figure*}
 

### 2022-06-27 gibbs.tex
LN: abstract

@@
 insoluble cross-linked network of the gel enables dewatering under
-the influence of a stimuli (thermal and/or mechanical). On the other
-hand, the network structure of a polymer hydrogel from a thermodynamic
-perspective is already an osmotic membrane. So hydrogel microparticles
+the influence of a stimulus (thermal and/or mechanical). On the other
+hand, the network structure of a polymer hydrogel, from a thermodynamic
+perspective, is already an osmotic membrane. So hydrogel microparticles
 may allow to completely avoid the osmotic membranes in forward osmosis
-and use microfiltration instead. By this article, we present our recent
+and use microfiltration instead.
+
+In this article, we present our recent
 theoretical study of the use of polyelectrolyte hydrogel for water
-desalination. We modeled the thermodynamic equilibrium of coexistence
-of the gel and the aqueous salt solution in the so-called closed ensemble,
+desalination. We modeled the thermodynamic equilibrium of coexisting
+gel and aqueous salt solution phases in the so-called closed ensemble,
 in which the total amount of ions is assumed to be constant. We modeled
-the compression of the gel and the associated with that release of
-the solution. We have shown that the squeezed out solution has a little
-lower salinity than that the gel was equilibrated with. Also, we performed
+the compression of the gel associated with the release of
+solution. We have shown that the squeezed out solution has a little
+lower salinity than the one the gel was equilibrated with. Finally, we performed
 a set of simulations modeling the process of continuous decrease of

### 2022-06-27 gibbs.tex
LN: water desalination technologies

@@
 
-The first approach~--- distillation. It uses thermal means to effect
-a phase change of the water to vapor (or solid), then to physically
-separate the vapor phase from the remaining salt solution, and then
-recover the thermal energy for reuse as the separated vapor reverts
-to liquid form. Distillation processes were the first desalination
+The first approach is distillation, which uses heat to cause
+a phase change of the water to vapor. Then we physically
+separate the vapor phase from the remaining salt solution, and after that we
+recover the thermal energy for reuse as the separated vapor reverts back
+to the liquid form. Distillation processes were the first desalination
 techniques conducted on a large commercial scale and still account
@@
 
-The second approach is to physically separate the brine components,
-generally with a membrane, as they move in response to an externally
-applied gradient. In the context of our study, we will mention the
+The second approach is to physically separate the brine components
+using a membrane, as they move in response to an externally
+\todoi{we need to rephrase this}
+applied gradient.
+In the context of our study, we will mention the
 reverse osmosis process (RO) \textasciitilde -{}-{}- the major processes
-of all the modern desalination industry, and the new emerging membrane
+of all the modern desalination industry, and the newly emerging membrane
 technology -{}-{}- forward osmosis (FO) \cite{Akther2015}. In RO,
@@
 bar, to let the water pass through the membrane. But in terms of energy
-losses, it works close to the thermodynamic limit. Thus, theoretically,
-per one transferred from freshwater to salty water ion pair, it consumes
-only the energy of difference of those ions chemical potentials.
+losses, it works close to the thermodynamic limit.
+Thus, theoretically,
+per one ion pair transferred from freshwater to salty water,
+it consumes only the energy equal to the difference between the chemical potentials of the transfered ions.
 
-The absence of large hydraulic pressure in FO process in comparison
-to RO allows to reduce the energy consumption in pumping, reduce membrane
-scaling and fouling, therefore significantly increase the lifetime
-of the membranes. In FO, the draw solutes (agents) dispersed and/or
+The absence of large hydraulic pressure in FO process (unlike in
+RO) allows to reduce the energy consumption in pumping, reduce membrane
+scaling and fouling, and therefore significantly increase the lifetime
+of the membranes. In FO, the draw solutes (agents) are dispersed and/or
 dissolved in water form homogeneous draw solutions. The correct choice
@@
 pressure. On the other hand, the diluted draw solution is also expected
-to be easily separated to fresh water and to concentrated draw solution
+to be easily separated from fresh water and concentrated draw solution
 for reuse \cite{Cai2016}.

### 2022-06-29 gibbs.tex
added errors to the table

--- 2022-06-15 gibbs.tex
@@
 \item perform Monte-Carlo procedure simulating ion pair exchange; collect
-the arrays ofobservables sample : number of ions in both boxes, $\nna^{I}$,
+the arrays of observables sample : number of ions in both boxes, $\nna^{I}$,
 $\ncl^{I}$, $\nna^{II}$ and $\ncl^{II}$ ; 
@@
 
-\begin{table*}[h]
-\caption{\label{tab: table}All the units calculated per one mol of gel segments.}
-\begin{tabular*}{1\textwidth}{@{\extracolsep{\fill}}|ll|ll|l|l|ll|}
+\begin{table}
+\begin{tabular*}{1\textwidth}{@{\extracolsep{\fill}}ll|lc|c|l|l|ll}
+\multicolumn{1}{l|}{$c_{s}^{0}$, mM} & $c_{s}^{5}$, mM & \multicolumn{1}{l|}{$n_{\cl}^{0}$, mM} & $n_{\cl}^{5}$, mM & $\Delta v$, l & $R_{w}$ & $|W$\textbar , J/L & \multicolumn{2}{c}{$W^{id}$, J/L}\tabularnewline
 \hline 
-\multicolumn{1}{|l|}{$c_{s}^{0}$, M} & $c_{s}^{5}$,M & \multicolumn{1}{l|}{$\ncl^{0}$} & $\ncl^{5}$ & $\Delta v$, l & $|W$\textbar , J/L & \multicolumn{2}{c|}{$W^{id}$, J/L}\tabularnewline
 \hline 
-\multirow{2}{*}{0.092} & \multirow{2}{*}{} & \multirow{2}{*}{0.057 $\rightarrow$} & \multirow{2}{*}{0.072} & \multirow{2}{*}{2.74} & \multirow{2}{*}{95.4} &  & \multirow{2}{*}{}\tabularnewline
- &  &  &  &  &  & \multirow{8}{*}{\hspace{-1em}\textcolor{teal}{$\left.\begin{array}{l}
+\multirow{2}{*}{{\small{}$91.47$}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{{\small{}$57.08\pm0.122\enskip\longrightarrow$}} & \multirow{2}{*}{{\small{}2.74}} & \multirow{2}{*}{} & \multirow{2}{*}{{\small{}$95.4\pm1.86$}} &  & \multirow{2}{*}{}\tabularnewline
+ &  & \multicolumn{2}{r|}{{\small{}$71.75\pm0.024$}} &  &  &  & \multirow{8}{*}{{\small{}\hspace{-1em}}\textcolor{teal}{\small{}$\left.\begin{array}{l}
 \\
@@
 \end{array}}}$}} & \tabularnewline
-\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
-\multirow{2}{*}{0.089 $\rightarrow$} & \multirow{2}{*}{0.074} & \multirow{2}{*}{0.057} & \multirow{2}{*}{} & \multirow{2}{*}{2.72} & \multirow{2}{*}{109.1} &  & \multirow{2}{*}{}\tabularnewline
- &  &  &  &  &  &  & \tabularnewline
-\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
-\multirow{2}{*}{\textcolor{teal}{0.064}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{teal}{0.037 $\rightarrow$}} & \multirow{2}{*}{\textcolor{teal}{0.051}} & \multirow{2}{*}{\textcolor{teal}{3.26}} & \multirow{2}{*}{\textcolor{teal}{100.9}} &  & \tabularnewline
- &  &  &  &  &  &  & \multirow{8}{*}{\hspace{-1em}\textcolor{olive}{$\left.\begin{array}{l}
+\cline{1-7} \cline{2-7} \cline{3-7} \cline{4-7} \cline{5-7} \cline{6-7} \cline{7-7} 
+\multicolumn{2}{l|}{{\small{}$89.41\pm0.229\enskip\longrightarrow$}} & \multirow{2}{*}{{\small{}56.90}} & \multirow{2}{*}{} & \multirow{2}{*}{{\small{}2.72}} & \multirow{2}{*}{} & \multirow{2}{*}{{\small{}$109.1\pm1.72$}} &  & \multirow{2}{*}{}\tabularnewline
+\multicolumn{2}{r|}{{\small{}$73.63\pm0.03$}} &  &  &  &  &  &  & \tabularnewline
+\cline{1-7} \cline{2-7} \cline{3-7} \cline{4-7} \cline{5-7} \cline{6-7} \cline{7-7} 
+\multirow{2}{*}{\textcolor{teal}{\small{}63.93}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{teal}{\small{}$37.28\pm0.083\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{teal}{\small{}3.26}} & \multirow{2}{*}{\textcolor{teal}{\small{}0.54}} & \multirow{2}{*}{\textcolor{teal}{\small{}$100.9\pm1.69$}} &  & \tabularnewline
+ &  & \multicolumn{2}{r|}{\textcolor{teal}{\small{}$50.58\pm0.013$}} &  &  &  &  & \multirow{8}{*}{{\small{}\hspace{-1em}}\textcolor{olive}{\small{}$\left.\begin{array}{l}
 \\
@@
 \end{array}}}$}}\tabularnewline
-\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
-\multirow{2}{*}{\textcolor{teal}{0.062 $\rightarrow$}} & \multirow{2}{*}{\textcolor{teal}{0.048}} & \multirow{2}{*}{\textcolor{teal}{0.037}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{teal}{3.18}} & \multirow{2}{*}{\textcolor{teal}{107.4}} &  & \tabularnewline
- &  &  &  &  &  &  & \tabularnewline
-\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
-\multirow{2}{*}{\textcolor{olive}{0.045}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{olive}{0.024 $\rightarrow$}} & \multirow{2}{*}{\textcolor{olive}{0.036}} & \multirow{2}{*}{\textcolor{olive}{3.82}} & \multirow{2}{*}{\textcolor{olive}{106.7}} &  & \tabularnewline
- &  &  &  &  &  & \multirow{8}{*}{\hspace{-1em}\textcolor{red}{$\left.\begin{array}{l}
+\cline{1-7} \cline{2-7} \cline{3-7} \cline{4-7} \cline{5-7} \cline{6-7} \cline{7-7} 
+\multicolumn{2}{l|}{\textcolor{teal}{\small{}$62.05\pm0.15\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{teal}{\small{}37.17}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{teal}{\small{}3.18}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{teal}{\small{}$107.4\pm1.37$}} &  & \tabularnewline
+\multicolumn{2}{r|}{\textcolor{teal}{\small{}$48.21\pm0.016$}} &  &  &  &  &  &  & \tabularnewline
+\cline{1-7} \cline{2-7} \cline{3-7} \cline{4-7} \cline{5-7} \cline{6-7} \cline{7-7} 
+\multirow{2}{*}{\textcolor{olive}{\small{}44.91}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{olive}{\small{}$23.75\pm0.057\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{olive}{\small{}3.82}} & \multirow{2}{*}{\textcolor{olive}{\small{}0.53}} & \multirow{2}{*}{\textcolor{olive}{\small{}$106.7\pm1.51$}} &  & \tabularnewline
+ &  & \multicolumn{2}{r|}{\textcolor{olive}{\small{}$35.91\pm0.010$}} &  &  &  & \multirow{8}{*}{{\small{}\hspace{-1em}}\textcolor{red}{\small{}$\left.\begin{array}{l}
 \\
@@
 \end{array}}}$}} & \tabularnewline
-\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
-\multirow{2}{*}{\textcolor{olive}{0.044 $\rightarrow$}} & \multirow{2}{*}{\textcolor{olive}{0.031}} & \multirow{2}{*}{\textcolor{olive}{0.024}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{olive}{3.91}} & \multirow{2}{*}{\textcolor{olive}{106.4}} &  & \tabularnewline
- &  &  &  &  &  &  & \tabularnewline
-\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
-\multirow{2}{*}{\textcolor{red}{0.032}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{red}{0.015 $\rightarrow$}} & \multirow{2}{*}{\textcolor{red}{0.025}} & \multirow{2}{*}{\textcolor{red}{4.20}} & \multirow{2}{*}{\textcolor{red}{107.9}} &  & \tabularnewline
- &  &  &  &  &  &  & \multirow{8}{*}{\hspace{-1em}\textcolor{orange}{$\left.\begin{array}{l}
+\cline{1-7} \cline{2-7} \cline{3-7} \cline{4-7} \cline{5-7} \cline{6-7} \cline{7-7} 
+\multicolumn{2}{l|}{\textcolor{olive}{\small{}$43.46\pm0.12\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{olive}{\small{}24.27}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{olive}{\small{}3.91}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{olive}{\small{}$106.4\pm1.13$}} &  & \tabularnewline
+\multicolumn{2}{r|}{\textcolor{olive}{\small{}$30.80\pm0.008$}} &  &  &  &  &  &  & \tabularnewline
+\cline{1-7} \cline{2-7} \cline{3-7} \cline{4-7} \cline{5-7} \cline{6-7} \cline{7-7} 
+\multirow{2}{*}{\textcolor{red}{\small{}31.93}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{red}{\small{}$14.66\pm0.037\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{red}{\small{}4.20}} & \multirow{2}{*}{\textcolor{red}{\small{}0.52}} & \multirow{2}{*}{\textcolor{red}{\small{}$107.9\pm1.42$}} &  & \tabularnewline
+ &  & \multicolumn{2}{r|}{\textcolor{red}{\small{}$25.30\pm0.006$}} &  &  &  &  & \multirow{8}{*}{{\small{}\hspace{-1em}}\textcolor{orange}{\small{}$\left.\begin{array}{l}
 \\
@@
 \end{array}}}$}}\tabularnewline
-\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
-\multirow{2}{*}{\textcolor{red}{0.030 $\rightarrow$}} & \multirow{2}{*}{\textcolor{red}{$\begin{array}{c}
-0.019\\
-{\scriptstyle (0.022)}
-\end{array}$}} & \multirow{2}{*}{\textcolor{red}{0.015}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{red}{$\begin{array}{c}
+\cline{1-7} \cline{2-7} \cline{3-7} \cline{4-7} \cline{5-7} \cline{6-7} \cline{7-7} 
+\multicolumn{2}{l|}{\textcolor{red}{\small{}$30.03\pm0.084\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{red}{\small{}14.55}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{red}{\small{}$\begin{array}{c}
 4.17\\
 {\scriptstyle (3.22)}
-\end{array}$}} & \multirow{2}{*}{\textcolor{red}{$\begin{array}{c}
-115.6\\
+\end{array}$}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{red}{\small{}$\begin{array}{c}
+115.6\pm0.92\\
 {\scriptstyle (57.3)}
 \end{array}$}} &  & \tabularnewline
- &  &  &  &  &  &  & \tabularnewline
-\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
-\multirow{2}{*}{\textcolor{orange}{0.022}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{orange}{0.009 $\rightarrow$}} & \multirow{2}{*}{\textcolor{orange}{$\begin{array}{c}
-0.018\\
-{\scriptstyle (0.015)}
-\end{array}$}} & \multirow{2}{*}{\textcolor{orange}{$\begin{array}{c}
+\multicolumn{2}{r|}{\textcolor{red}{\small{}$\begin{array}{c}
+18.59\pm0.004\,\\
+{\scriptstyle (22.32)}
+\end{array}$}} &  &  &  &  &  &  & \tabularnewline
+\cline{1-7} \cline{2-7} \cline{3-7} \cline{4-7} \cline{5-7} \cline{6-7} \cline{7-7} 
+\multirow{2}{*}{\textcolor{orange}{\small{}22.30}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{orange}{\small{}$8.84\pm0.026\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{orange}{\small{}$\begin{array}{c}
 4.75\\
 {\scriptstyle (3.76)}
-\end{array}$}} & \multirow{2}{*}{\textcolor{orange}{$\begin{array}{c}
-108.1\\
+\end{array}$}} & \multirow{2}{*}{\textcolor{orange}{\small{}0.53}} & \multirow{2}{*}{\textcolor{orange}{\small{}$\begin{array}{c}
+108.1\pm1.26\\
 {\scriptstyle (68.3)}
 \end{array}$}} &  & \tabularnewline
- &  &  &  &  &  & \multirow{7}{*}{\hspace{-1em}\textcolor{magenta}{$\left.\begin{array}{l}
+ &  & \multicolumn{2}{r|}{\textcolor{orange}{\small{}$\begin{array}{c}
+\text{17.95}\pm\text{0.004}\\
+{\scriptstyle (14.56)}
+\end{array}$}} &  &  &  & \multirow{7}{*}{{\small{}\hspace{-1em}}\textcolor{magenta}{\small{}$\left.\begin{array}{l}
 \\
@@
 \end{array}}}$}} & \tabularnewline
-\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
-\multirow{2}{*}{\textcolor{orange}{0.021 $\rightarrow$}} & \multirow{2}{*}{\textcolor{orange}{0.011}} & \multirow{2}{*}{\textcolor{orange}{0.009}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{orange}{$4.71$}} & \multirow{2}{*}{\textcolor{orange}{110.8}} &  & \tabularnewline
- &  &  &  &  &  &  & \tabularnewline
-\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
-\multirow{2}{*}{\textcolor{magenta}{0.011}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{magenta}{0.003 $\rightarrow$}} & \multirow{2}{*}{\textcolor{magenta}{0.009}} & \multirow{2}{*}{\textcolor{magenta}{6.08}} & \multirow{2}{*}{\textcolor{magenta}{106.9}} &  & \tabularnewline
- &  &  &  &  &  &  & \tabularnewline
-\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
-\multirow{2}{*}{\textcolor{magenta}{0.010 $\rightarrow$}} & \multirow{2}{*}{\textcolor{magenta}{0.004}} & \multirow{2}{*}{\textcolor{magenta}{0.003}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{magenta}{5.78}} & \multirow{2}{*}{\textcolor{magenta}{119.4}} &  & \tabularnewline
- &  &  &  &  &  &  & \tabularnewline
-\hline 
+\cline{1-7} \cline{2-7} \cline{3-7} \cline{4-7} \cline{5-7} \cline{6-7} \cline{7-7} 
+\multicolumn{2}{l|}{\textcolor{orange}{\small{}$20.74\pm0.064\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{orange}{\small{}8.83}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{orange}{\small{}$4.71$}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{orange}{\small{}$110.8\pm0.77$}} &  & \tabularnewline
+\multicolumn{2}{r|}{\textcolor{orange}{\small{}$11.08\pm0.002$}} &  &  &  &  &  &  & \tabularnewline
+\cline{1-7} \cline{2-7} \cline{3-7} \cline{4-7} \cline{5-7} \cline{6-7} \cline{7-7} 
+\multirow{2}{*}{\textcolor{magenta}{\small{}10.90}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{magenta}{\small{}$3.00\pm0.01\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{magenta}{\small{}6.08}} & \multirow{2}{*}{\textcolor{magenta}{\small{}0.55}} & \multirow{2}{*}{\textcolor{magenta}{\small{}$106.9\pm1.05$}} &  & \tabularnewline
+ &  & \multicolumn{2}{r|}{\textcolor{magenta}{\small{}9.01$\pm$0.002}} &  &  &  &  & \tabularnewline
+\cline{1-7} \cline{2-7} \cline{3-7} \cline{4-7} \cline{5-7} \cline{6-7} \cline{7-7} 
+\multicolumn{2}{l|}{\textcolor{magenta}{\small{}$9.83\pm0.046\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{magenta}{\small{}3.12}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{magenta}{\small{}5.78}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{magenta}{\small{}$119.4\pm0.97$}} &  & \tabularnewline
+\multicolumn{2}{r|}{\textcolor{magenta}{\small{}$3.86\pm0.001$}} &  &  &  &  &  &  & \tabularnewline
 \end{tabular*}
-\end{table*}
 
-The six column \todo{check if it is sixth column} contains the values of specific energy consumption, $W^\text{id}$, which are calculated as follows.
-We consider, for example, the solution of concentration $\cs^f=0.045$ M as a feed solution, and the solutions of $\cs^p=0.032M$ and $\cs^b=0.064M$ correspondingly as produced product and brine solutions.
+\caption{All the units calculated per one mol of gel segments. Values in brackets
+are the estimates corresponding to crossection of 'red' and 'orange'
+lines on the plots of figures \ref{fig: PV and CV} and \ref{fig: NV and CN}
+}
+\end{table}
+
+The fifth column \todo{check if it is fifth column} contains the values of specific energy consumption, $W^\text{id}$, which are calculated as follows.
+We consider, for example, the solution of concentration $\cs^f=0.045$ mol/l as a feed solution, and the solutions of $\cs^p=0.032M$ and $\cs^b = 0.064$ mol/l 
+correspondingly as produced product and brine solutions.
 \begin{enumerate}
-    \item first the gel is equilibrated with feed solution is getting compressed in closed system. 
-    The salinity of supernatant decreases from $\cs^f$ to $\cs^p$.
-    The change of the gel volume equals to $\Delta v^p =$ 3.69 l, so does the  the volume of produced desalinated solution
-    \item Then the squeezed gel is put back to feed solution and getting equilibrated with it under pressure 5 bar, so that it does not swell. 
+    \item first, the gel, equilibrated with feed solution, is getting compressed in a closed system.
+    while compression it changes its volume by $\Delta v^p = 3.69$  l/mol and the salinity of supernate decreases from $\cs^f$ to $\cs^p$.
+    The volume of product solution equals to $\Delta v^p$
+    \item Then the squeezed gel is put back to feed solution and is getting equilibrated there under pressure, so it does not swell. 
     \item then the squeezed gel is let to swell in closed system such that the salinity of external solution increases reaching the value of $\cs^b$
     \item finally, the gel is taken out and squeezed by 5 bar in open system in equilibrium with the bath of the brine. 
-    The change of the gel volume in this process is $\Delta v^b =$ 3.26 l, so that the volume of the produced brine. 
+    The change of the gel volume in this process is $\Delta v^b = 3.26$ l/mol, which equals to the volume of produced brine. 
 \end{enumerate}
-The recovery ratio $R_w = \Delta v^p / (\Delta v^p + \Delta v^b) simeq $ 0.53
-The theoretical minimum specific energy of desalination with corresponding $\cs^f$, $\cs^p$ and $\cs^b$, according to \refeq{eq: SEC} is $W^{id} =$ 38.2 J/l
+Thus the recovery ratio $R_w = \Delta v^p / (\Delta v^p + \Delta v^b) \simeq $ 0.53 and the theoretical minimum specific energy of desalination with corresponding $\cs^f$, $\cs^p$ and $\cs^b$ is $W^{id} =$ 38.2 J/l (\refeq{eq:SEC})
 
@@
 
+\subsection{Monte Carlo process}
+\subsubsection{Open system}
+Free energy in grand-cannonical ensemble
+\begin{equation}
+\Omega = E-TS + \mu N 
+\end{equation}
+where $S$ is the entropy. Boltzman formula
+\begin{equation}
+S= k_B \ln \frac{V^N}{N!}
+\end{equation}
+The change of free energy associated with insertion ($\xi=1$) or deletion ($\xi=-1$) a particle is
+\begin{equation}
+\Delta \Omega =\kT\ln\left(V^{\xi}\frac{N!}{ (N+\xi)!}\right)+\xi\mu+\Delta E
+\end{equation}
+\subsubsection{Closed system}
+In closed system ion pairs are exchanged between two finite volume boxes.
+
+\begin{equation}
+    \na_{I} + \cl_{I} \leftrightarrows \na_{II} + \cl_{II}
+\end{equation}
+
+Suppose an ion pair has been moved from box to another, then the change in entropy can be expressed as
+\begin{eqnarray}
+    \Delta S = 2 \log \left(\frac{V^{I}}{V^{II}} \right) ^ {\gamma}  \left(\frac{(N_{Na^{+}}^{I}+\mathcal{H}(\gamma))(N_{Cl^{-}}^{I}+\mathcal{H}(\gamma))}{(N_{Na^{+}}^{II}+\mathcal{H}(-\gamma))(N_{Cl^{-}}^{II}+\mathcal{H}(-\gamma))}\right)^{-\gamma}
+\end{eqnarray}
+where $\gamma$ defines the direction of the trial move, so that $\gamma_{I \rightarrow II} = -1$ when an ion pair moved from box I to box II and  $\gamma_{II \rightarrow I} = 1$ otherwise, $\mathcal{H}$ is the Heaviside step function.
+
+The probability that the move will be accepted is calculated from the free energy change as
+\begin{equation}
+    \mathcal{P} = \exp(-\beta (\Delta E_{pot} - k_B T \Delta S))
+\end{equation}
+
+Thus, moving an ion pair from box I to box II change the entropy
+\begin{equation}
+    \Delta S_{I \rightarrow II} = 2 \log \left(\frac{V^{II}}{V^{I}} \right)  \frac{N_{Na^{+}}^{I} N_{Cl^{-}}^{I}}{(N_{Na^{+}}^{II}+1)(N_{Cl^{-}}^{II}+1)}
+\end{equation}
+
+The probability of this move ${I \rightarrow II}$ to be accepted
+
+\begin{equation}
+    \mathcal{P}_{I \rightarrow II} = \exp\left(-\beta (\Delta E_{pot} - 2 k_B T \log \left(\frac{V^{II}}{V^{I}} \right)  \frac{N_{Na^{+}}^{I} N_{Cl^{-}}^{I}}{(N_{Na^{+}}^{II}+1)(N_{Cl^{-}}^{II}+1)})\right)
+\end{equation}
+
+\begin{itemize}
+\item perform a move of a random ion pair 
+    \begin{equation}
+    \left(\na +\cl\right)^{I} \leftrightarrows\left(\na +\cl\right)^{II}
+\end{equation}
+
+\item accept if 
+    \begin{equation}
+    \mathrm{rand}(0,1] < \left(\frac{V^{II}}{V^{I}}\right)^{\xi}\prod_{i=Na,\ Cl}\frac{N^I_i!}{(N^I_i+\xi)!}\frac{N^{II}_i!}{(N^{II}_i+\xi)!}\exp(-\beta\Delta E_{pot})
+\end{equation}
+\end{itemize}
+
+\subsection{Donnan equilibrium in finite volume reservoirs}
+Before we can explore any system properties and collect data the system has to be equilibrated.
+To achieve this we perform equilibration routine consist of sequence of Molecular Dynamics and Monte Carlo steps.
+%Here we describe our technique
+The result of equilibration is stationary of any observable such as pressure, end-to-end distance for polymer chains and ion distribution between reservoirs.
+
+The success and the cost in terms of computational time for the equilibration process heavily depend on initial guess.
+In our case we initialize the system with ion distribution corresponds to Donnan equilibrium.
+
+In closed system number of ions in the system is constant, so Donnan equilibrium can be formulated as follows
+\begin{equation}
+    \frac{\left(N_{pairs} - N_{Cl^{-}}^{(gel)}\right)^2}{V_{salt}^2} = \frac{N_{Cl^{-}}^{gel} (N^{{(gel)}}_{A^{-}} + N_{Cl^{-}}^{(gel)})}{V_{gel}^2}
+\end{equation}
+where $N^{{(gel)}}_{A^{-}}$ is number of fixed anions in the box with the gel \ie acetic groups in the polymer gel.
+Solving this equation with respect to $N^{{(gel)}}_{A^{-}}$ gives us the distribution of the ions between two boxes.
+
+%probably not needed
+\begin{eqnarray}
+    %N_{Cl^{-}}^{(gel)} = \frac{\frac{N^{{(gel)}}_{A^{-}} V_{salt}^{2}}{2} + N_{pairs} V_{gel}^{2} - \frac{V_{salt} \sqrt{N^{{(gel)}}_{A^{-}}^{2} V_{salt}^{2} + 4 N^{{(gel)}}_{A^{-}} N_{pairs} V_{gel}^{2} + 4 N_{pairs}^{2} V_{gel}^{2}}}{2}}{V_{gel}^{2} - V_{salt}^{2}}
+    \\
+    N_{Na^{+}}^{(gel)} = N^{{(gel)}}_{A^{-}} + N_{Cl^{-}}^{(gel)}
+    \\
+    N_{Cl^{-}}^{(salt)} = N_{Na^{+}}^{(gel)} = N_{pairs} - N_{Cl^{-}}^{(gel)}
+\end{eqnarray}
+
+\begin{table}
+\begin{tabular*}{1\textwidth}{@{\extracolsep{\fill}}ll|lc|c|l|l|ll}
+\multicolumn{1}{l|}{$c_{s}^{0}$, mM} & $c_{s}^{5}$, mM & \multicolumn{1}{l|}{$n_{\cl}^{0}$, mM} & $n_{\cl}^{5}$, mM & $\Delta v$, l & $R_{w}$ & $|W$\textbar , J/L & \multicolumn{2}{c}{$W^{id}$, J/L}\tabularnewline
+\hline 
+\hline 
+\multirow{2}{*}{{\small{}91.466}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{{\small{}$57.083\pm0.1215\quad\longrightarrow$}} & \multirow{2}{*}{{\small{}2.74}} & \multirow{2}{*}{} & \multirow{2}{*}{{\small{}$95.4\pm1.86$}} &  & \multirow{2}{*}{}\tabularnewline
+ &  & \multicolumn{2}{r|}{{\small{}$71.751\pm0.024$}} &  &  &  & \multirow{8}{*}{{\small{}\hspace{-1em}}\textcolor{teal}{\small{}$\left.\begin{array}{l}
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\end{array}\right\rbrace $$\rotatebox{90}{\hspace{-3.8em}\ensuremath{\begin{array}{cc}
+W^{id}= & (52.9)\\
+R_{w}= & 0.54
+\end{array}}}$}} & \tabularnewline
+\cline{1-7} \cline{2-7} \cline{3-7} \cline{4-7} \cline{5-7} \cline{6-7} \cline{7-7} 
+\multicolumn{2}{l|}{{\small{}$89.414\pm0.2286\quad\longrightarrow$}} & \multirow{2}{*}{{\small{}56.898}} & \multirow{2}{*}{} & \multirow{2}{*}{{\small{}2.72}} & \multirow{2}{*}{} & \multirow{2}{*}{{\small{}$109.1\pm1.72$}} &  & \multirow{2}{*}{}\tabularnewline
+\multicolumn{2}{r|}{{\small{}$73.633\pm0.029$}} &  &  &  &  &  &  & \tabularnewline
+\cline{1-7} \cline{2-7} \cline{3-7} \cline{4-7} \cline{5-7} \cline{6-7} \cline{7-7} 
+\multirow{2}{*}{\textcolor{teal}{\small{}63.93}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{teal}{\small{}$37.281\pm0.083\quad\longrightarrow$}} & \multirow{2}{*}{\textcolor{teal}{\small{}3.26}} & \multirow{2}{*}{\textcolor{teal}{\small{}0.54}} & \multirow{2}{*}{\textcolor{teal}{\small{}$100.9\pm1.69$}} &  & \tabularnewline
+ &  & \multicolumn{2}{r|}{\textcolor{teal}{\small{}$50.579\pm0.0134$}} &  &  &  &  & \multirow{8}{*}{{\small{}\hspace{-1em}}\textcolor{olive}{\small{}$\left.\begin{array}{l}
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\end{array}\right\rbrace $$\rotatebox{90}{\hspace{-3.8em}\ensuremath{\begin{array}{cc}
+W^{id}= & 38.2\\
+R_{w}= & 0.53
+\end{array}}}$}}\tabularnewline
+\cline{1-7} \cline{2-7} \cline{3-7} \cline{4-7} \cline{5-7} \cline{6-7} \cline{7-7} 
+\multicolumn{2}{l|}{\textcolor{teal}{\small{}$62.052\pm0.148\quad\longrightarrow$}} & \multirow{2}{*}{\textcolor{teal}{\small{}37.172}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{teal}{\small{}3.18}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{teal}{\small{}$107.4\pm1.37$}} &  & \tabularnewline
+\multicolumn{2}{r|}{\textcolor{teal}{\small{}$48.206\pm0.0157$}} &  &  &  &  &  &  & \tabularnewline
+\cline{1-7} \cline{2-7} \cline{3-7} \cline{4-7} \cline{5-7} \cline{6-7} \cline{7-7} 
+\multirow{2}{*}{\textcolor{olive}{\small{}44.915}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{olive}{\small{}$23.747\pm0.0572\quad\longrightarrow$}} & \multirow{2}{*}{\textcolor{olive}{\small{}3.82}} & \multirow{2}{*}{\textcolor{olive}{\small{}0.53}} & \multirow{2}{*}{\textcolor{olive}{\small{}$106.7\pm1.51$}} &  & \tabularnewline
+ &  & \multicolumn{2}{r|}{\textcolor{olive}{\small{}$35.911\pm0.0101$}} &  &  &  & \multirow{8}{*}{{\small{}\hspace{-1em}}\textcolor{red}{\small{}$\left.\begin{array}{l}
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\end{array}\right\rbrace \rotatebox{90}{\hspace{-3.8em}\ensuremath{\begin{array}{cc}
+W^{id}= & 43.8\ {\color{red}{\scriptstyle (41.0)}}\\
+R_{w}= & 0.52\ {\scriptstyle (0.46)}
+\end{array}}}$}} & \tabularnewline
+\cline{1-7} \cline{2-7} \cline{3-7} \cline{4-7} \cline{5-7} \cline{6-7} \cline{7-7} 
+\multicolumn{2}{l|}{\textcolor{olive}{\small{}$43.463\pm0.116\quad\longrightarrow$}} & \multirow{2}{*}{\textcolor{olive}{\small{}24.272}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{olive}{\small{}3.91}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{olive}{\small{}$106.4\pm1.13$}} &  & \tabularnewline
+\multicolumn{2}{r|}{\textcolor{olive}{\small{}$30.795\pm0.0078$}} &  &  &  &  &  &  & \tabularnewline
+\cline{1-7} \cline{2-7} \cline{3-7} \cline{4-7} \cline{5-7} \cline{6-7} \cline{7-7} 
+\multirow{2}{*}{\textcolor{red}{\small{}31.928}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{red}{\small{}$14.658\pm0.0368\quad\longrightarrow$}} & \multirow{2}{*}{\textcolor{red}{\small{}4.20}} & \multirow{2}{*}{\textcolor{red}{\small{}0.52}} & \multirow{2}{*}{\textcolor{red}{\small{}$107.9\pm1.42$}} &  & \tabularnewline
+ &  & \multicolumn{2}{r|}{\textcolor{red}{\small{}$25.297\pm0.0061$}} &  &  &  &  & \multirow{8}{*}{{\small{}\hspace{-1em}}\textcolor{orange}{\small{}$\left.\begin{array}{l}
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\end{array}\right\rbrace \rotatebox{90}{\hspace{-3.8em}\ensuremath{\begin{array}{cc}
+W^{id}= & 66.6\ {\scriptstyle (22.0)}\\
+R_{w}= & 0.53\ {\scriptstyle (0.49)}
+\end{array}}}$}}\tabularnewline
+\cline{1-7} \cline{2-7} \cline{3-7} \cline{4-7} \cline{5-7} \cline{6-7} \cline{7-7} 
+\multicolumn{2}{l|}{\textcolor{red}{\small{}$30.029\pm0.0839\quad\longrightarrow$}} & \multirow{2}{*}{\textcolor{red}{\small{}14.549}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{red}{\small{}$\begin{array}{c}
+4.17\\
+{\scriptstyle (3.22)}
+\end{array}$}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{red}{\small{}$\begin{array}{c}
+115.6\pm0.92\\
+{\scriptstyle (57.3)}
+\end{array}$}} &  & \tabularnewline
+\multicolumn{2}{r|}{\textcolor{red}{\small{}$\begin{array}{c}
+18.585\pm0.0036\,\\
+{\scriptstyle (22.32)}
+\end{array}$}} &  &  &  &  &  &  & \tabularnewline
+\cline{1-7} \cline{2-7} \cline{3-7} \cline{4-7} \cline{5-7} \cline{6-7} \cline{7-7} 
+\multirow{2}{*}{\textcolor{orange}{\small{}22.301}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{orange}{\small{}$8.838\pm0.0262\quad\longrightarrow$}} & \multirow{2}{*}{\textcolor{orange}{\small{}$\begin{array}{c}
+4.75\\
+{\scriptstyle (3.76)}
+\end{array}$}} & \multirow{2}{*}{\textcolor{orange}{\small{}0.53}} & \multirow{2}{*}{\textcolor{orange}{\small{}$\begin{array}{c}
+108.1\pm1.26\\
+{\scriptstyle (68.3)}
+\end{array}$}} &  & \tabularnewline
+ &  & \multicolumn{2}{r|}{\textcolor{orange}{\small{}$\begin{array}{c}
+\text{17.945}\pm\text{0.0041}\\
+{\scriptstyle (14.56)}
+\end{array}$}} &  &  &  & \multirow{7}{*}{{\small{}\hspace{-1em}}\textcolor{magenta}{\small{}$\left.\begin{array}{l}
+\\
+\\
+\\
+\\
+\\
+\\
+\end{array}\right\rbrace \rotatebox{90}{\hspace{-3em}\ensuremath{\begin{array}{cc}
+W^{id}= & 69.7\\
+R_{w}= & 0.55
+\end{array}}}$}} & \tabularnewline
+\cline{1-7} \cline{2-7} \cline{3-7} \cline{4-7} \cline{5-7} \cline{6-7} \cline{7-7} 
+\multicolumn{2}{l|}{\textcolor{orange}{\small{}$20.743\pm0.0638\quad\longrightarrow$}} & \multirow{2}{*}{\textcolor{orange}{\small{}8.827}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{orange}{\small{}$4.71$}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{orange}{\small{}$110.8\pm0.77$}} &  & \tabularnewline
+\multicolumn{2}{r|}{\textcolor{orange}{\small{}$11.082\pm0.002$}} &  &  &  &  &  &  & \tabularnewline
+\cline{1-7} \cline{2-7} \cline{3-7} \cline{4-7} \cline{5-7} \cline{6-7} \cline{7-7} 
+\multirow{2}{*}{\textcolor{magenta}{\small{}10.904}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{magenta}{\small{}$3.002\pm0.0098\quad\longrightarrow$}} & \multirow{2}{*}{\textcolor{magenta}{\small{}6.08}} & \multirow{2}{*}{\textcolor{magenta}{\small{}0.55}} & \multirow{2}{*}{\textcolor{magenta}{\small{}$106.9\pm1.05$}} &  & \tabularnewline
+ &  & \multicolumn{2}{r|}{\textcolor{magenta}{\small{}9.011$\pm$0.0019}} &  &  &  &  & \tabularnewline
+\cline{1-7} \cline{2-7} \cline{3-7} \cline{4-7} \cline{5-7} \cline{6-7} \cline{7-7} 
+\multicolumn{2}{l|}{\textcolor{magenta}{\small{}$9.834\pm0.0461\quad\longrightarrow$}} & \multirow{2}{*}{\textcolor{magenta}{\small{}3.119}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{magenta}{\small{}5.78}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{magenta}{\small{}$119.4\pm0.97$}} &  & \tabularnewline
+\multicolumn{2}{r|}{\textcolor{magenta}{\small{}$3.862\pm0.0014$}} &  &  &  &  &  &  & \tabularnewline
+\end{tabular*}
+
+\caption{ORIGINAL TABLE (to be removed)
+}
+\end{table}
 \end{document}

### 2022-06-30 gibbs.tex

@@
 \newcommand{\csres}{\cs\res}
-\newcommand{\Vgel}{V\gel}
-\newcommand{\Vgeleq}{\widetilde{V}\gel}
+%\newcommand{\Vgel}{V\gel}
+\newcommand{\Vgel}{v_\mathrm{gel}}
+\newcommand{\Vgeleq}{\widetilde{\Vgel}}
 \newcommand{\Pgel}{P\gel}
@@
 \begin{abstract}
-Recently polyelectrolyte hydrogels have been proposed as draw agents
-for reverse osmosis desalination techniques. Indeed, polyelectrolyte
-hydrogels have the ability to absorb a big amount of water across
-forward osmosis membrane as a result of their swelling pressure. The
-insoluble cross-linked network of the gel enables dewatering under
-the influence of a stimuli (thermal and/or mechanical). On the other
-hand, the network structure of a polymer hydrogel from a thermodynamic
-perspective is already an osmotic membrane. So hydrogel microparticles
+Recently polyelectrolyte hydrogels have been proposed as draw agents for reverse osmosis desalination techniques. 
+Indeed, polyelectrolyte hydrogels have the ability to absorb a big amount of water across forward osmosis membrane as a result of their swelling pressure. 
+The insoluble cross-linked network of the gel enables dewatering under the influence of a stimulus (thermal and/or mechanical) \todo{remove this sentence?}.
+On the other hand, the network structure of a polymer hydrogel, from a thermodynamic
+perspective, is already an osmotic membrane. So hydrogel microparticles
 may allow to completely avoid the osmotic membranes in forward osmosis
-and use microfiltration instead. By this article, we present our recent
-theoretical study of the use of polyelectrolyte hydrogel for water
-desalination. We modeled the thermodynamic equilibrium of coexistence
-of the gel and the aqueous salt solution in the so-called closed ensemble,
-in which the total amount of ions is assumed to be constant. We modeled
-the compression of the gel and the associated with that release of
-the solution. We have shown that the squeezed out solution has a little
-lower salinity than that the gel was equilibrated with. Also, we performed
-a set of simulations modeling the process of continuous decrease of
-water salinity up to freshwater concentrations.
+and use microfiltration instead.
 
+In this article, we present our recent theoretical study of the use of polyelectrolyte hydrogel for water desalination. 
+We modeled the thermodynamic equilibrium of coexisting gel and aqueous salt solution phases in the so-called `closed' ensemble, in which the total amount of ions is assumed to be constant. 
+We modeled the compression of the gel associated with the release of solution and have shown that the squeezed-out solution has a little lower salinity than the one the gel was equilibrated with. 
+Finally, we performed a set of simulations modeling the process of continuous decrease of water salinity up to freshwater concentrations.
 \end{abstract}
@@
 
-Two basic approaches for separating water from salt are present in
-modern desalination technology \cite{Miller2003,Curto2021}.
+Two basic approaches for separating water from salt are present in modern desalination technology \cite{Miller2003,Curto2021}.
 
-The first approach~--- distillation. It uses thermal means to effect
-a phase change of the water to vapor (or solid), then to physically
-separate the vapor phase from the remaining salt solution, and then
-recover the thermal energy for reuse as the separated vapor reverts
-to liquid form. Distillation processes were the first desalination
-techniques conducted on a large commercial scale and still account
-for a large portion of the modern world’s desalination capacity.
+The first approach is distillation, which uses heat to cause a phase change of the water to vapor. The vapor phase is separated from the brine and condenses to liquid fresh water. 
+The released condensation energy is directed back to heating the feed solution.
+Distillation processes were the first desalination techniques conducted on a large commercial scale and still account for a large portion of the modern world’s desalination capacity.
 
-The second approach is to physically separate the brine components,
-generally with a membrane, as they move in response to an externally
-applied gradient. In the context of our study, we will mention the
-reverse osmosis process (RO) \textasciitilde -{}-{}- the major processes
-of all the modern desalination industry, and the new emerging membrane
-technology -{}-{}- forward osmosis (FO) \cite{Akther2015}. In RO,
-water passes through a membrane that is impermeable to the solute
-in response to a chemical potential gradient achieved through pressurization.
-In FO, a concentrated draw solution, with a lower water chemical potential,
-and a feed solution, with a higher water chemical potential, are separated
-by a membrane that rejects the salt but allows the passage of water.
-The water permeation from feed solution to draw solution is a spontaneous
-process driven by the chemical potential gradient.
+The second approach is to physically separate the brine components using an osmotic membrane transparent only for water molecules, which move in response to a water chemical potential difference.
+In the context of our study, we will mention the reverse osmosis process (RO)~--- the major process of all the modern desalination industry, and the newly emerging membrane
+technology~--- forward osmosis (FO) \cite{Akther2015}. 
+In RO, the difference in water chemical potential originates from a difference in pressures applied to the feed and to product solutions. 
+In FO, the chemical potential difference is due to an addition to solution from one side of the membrane (draw solution) the so-called draw solutes, which are lowering the water chemical potential in draw solution.
 
-Distillation is easy and cheap technology but it is characterized
-by relatively high energy costs due to the dissipation of thermal
-energy. On the contrary, RO uses expensive osmotic membranes, which
-need to be replaced regularly because of scaling and fouling. Moreover,
-RO requires very high operating pressures, ranging from 20 to 200
-bar, to let the water pass through the membrane. But in terms of energy
-losses, it works close to the thermodynamic limit. Thus, theoretically,
-per one transferred from freshwater to salty water ion pair, it consumes
-only the energy of difference of those ions chemical potentials.
+Distillation is easy and cheap technology but it is characterized by relatively high energy costs due to the dissipation of thermal energy. 
+On the contrary, RO uses expensive osmotic membranes, which need to be replaced regularly because of scaling and fouling. 
+Moreover, RO requires very high operating pressures, ranging from 20 to 200 bar, to let the water pass through the membrane. 
+But in terms of energy losses, it works close to the thermodynamic limit.
+Thus, theoretically, per one ion pair transferred from freshwater to salty water, it consumes only the energy equal to the difference between the chemical potentials of the transfered ions.
 
-The absence of large hydraulic pressure in FO process in comparison
-to RO allows to reduce the energy consumption in pumping, reduce membrane
-scaling and fouling, therefore significantly increase the lifetime
-of the membranes. In FO, the draw solutes (agents) dispersed and/or
-dissolved in water form homogeneous draw solutions. The correct choice
-of the draw agents is a task of paramount importance. As an osmotically
-driven process, the draw solute is expected to significantly reduce
-the water chemical potential, and consequently generate a high osmotic
-pressure. On the other hand, the diluted draw solution is also expected
-to be easily separated to fresh water and to concentrated draw solution
-for reuse \cite{Cai2016}.
+The absence of large hydraulic pressure in FO process (unlike in RO) allows to reduce the energy consumption in pumping, reduce membrane scaling and fouling, and therefore significantly increase the lifetime of the membranes.
+In FO, the draw solutes (agents) are dispersed and/or dissolved in water form homogeneous draw solutions. 
+The correct choice of the draw agents is a task of paramount importance. 
+As an osmotically driven process, the draw solute is expected to significantly reduce the water chemical potential, and consequently generate a high osmotic pressure. 
+On the other hand, the draw solute is expected to be easily separated from water \cite{Cai2016}.
 
 \paragraph{Hydrogels for desalination.}
+Hydrogels are three-dimensional networks of polymer chains that are crosslinked by either physical or chemical bonds. 
+They are able to entrap large volumes of water attracted by the high concentration of hydrophilic groups. 
+When a dehydrated or deswollen hydrogel uptakes water, its polymer chains extend, creating a swelling pressure. 
+For example, as reported in \cite{Wack_2009} weakly crosslinked poly(acrylic acid) (PAA) copolymers with polymer volume fractions between 0.03 and 0.30 exhibit a swelling pressure ranging from 0.20--4.23 MPa.
+Polyelectrolyte hydrogels, which are carrying ionic groups on the comonomer units (like PAA), are able to reject salt ions from the solution, they absorb a solution of lower salinity than that they are equilibrated with.
 
-Hydrogels are three-dimensional networks of polymer chains that are
-crosslinked by either physical or chemical bonds. They are able to
-entrap large volumes of water attracted by the high concentration
-of hydrophilic groups. Hydrogels with ionic groups on the comonomer
-unit are able to reject salt ions from the solution, they absorb a
-solution of lower salinity than that they are equilibrated with. When
-a dehydrated or deswollen hydrogel uptakes water, its polymer chains
-extend, creating a swelling pressure. For example, as reported in
-\cite{Wack_2009} weakly crosslinked poly(acrylic acid)/poly(sodium
-acrylate) copolymers with polymer volume fractions between 0.03 and
-0.30 exhibit a swelling pressure ranging from 0.20--4.23 MPa.
+An important, advantageous aspect of polymer hydrogels is that they can undergo reversible volume change, \ie solution --- gel phase transitions in response to environmental stimuli. 
+This aspect causes hydrogels to be labeled as ‘smart’ hydrogels. 
+Many physical and chemical stimuli have been applied to induce various responses of such smart hydrogels, in particular, to change them from hydrophilic to hydrophobic, thereby releasing water. 
+The physical stimuli include: temperature, solvent composition, light, mechanical pressure, sound, electric and/or magnetic field, whilst the chemical (or biochemical) stimuli include pH, ionic strength, and specific molecular recognition \cite{Tanaka_1982,Serizawa_2001,Lietor_Santos_2009,Qiu_2001}.
 
-An important, advantageous aspect of polymer hydrogels is that they
-can undergo reversible volume change, \ie solution --- gel phase
-transitions in response to environmental stimuli. This aspect causes
-hydrogels to be labeled as ‘smart’ hydrogels. Many physical and chemical
-stimuli have been applied to induce various responses of such smart
-hydrogels, in particular, to change them from hydrophilic to hydrophobic,
-thereby releasing water. These stimuli include: temperature, solvent
-composition, light, mechanical pressure, sound, electric and/or magnetic
-field, whilst the chemical or biochemical stimuli include pH, ions,
-and specific molecular recognition events \cite{Tanaka_1982,Serizawa_2001,Lietor_Santos_2009,Qiu_2001}.
+The smart properties of hydrogels were utilized for desalination in a recent study by Li \etal \cite{Li2011}, where hydrogels have been considered as draw agents for FO. 
+In this study authors have shown, that hydrogels, 
+are able to absorb water across the FO membrane due to their swelling and osmotic pressure and
+allow dewatering under the influence of stimuli (thermal and/or mechanical), due to their insoluble cross-linked polymer network.
+For instance, Li \etal proposed the use of hydrogel made of thermoresponsive polyelectrolyte~--- copolymer of poly-N-isopropyl acrylamide (p-NIPAAm) and polyacrylic acid (p-AA).
+Depending on the temperature the network of the gel appears to be either hydrophilic or hydrophobic. 
+In the hydrophilic state, the gel is used as a draw solute accumulating water inside, then in the hydrophobic state, the water releases out.
 
-The smart properties of hydrogels were utilized for desalination in
-a recent study by Li \etal \cite{Li2011}, where hydrogels have been
-considered as draw agents for FO. The main point of the cited article
-is that hydrogels, due to their swelling and osmotic pressure, were
-able to absorb water across the FO membrane. The insoluble cross-linked
-network of the gel enables dewatering under the influence of stimuli
-(thermal and/or mechanical). For instance, Li \etal proposed the
-use of hydrogel made of thermoresponsive polyelectrolyte~--- copolymer
-of poly-N-isopropyl acrylamide (p-NIPAAm) and polyacrylic acid (p-AA).
-Depending on the temperature the network of the gel may appear to
-be either hydrophilic or hydrophobic. In the hydrophilic state, the
-gel is used as a draw agent accumulating water inside, then in the
-hydrophobic state, the water releases out.
+Moreover, from a thermodynamics perspective, the polyelectrolyte hydrogel itself is an osmotic membrane generating Donnan potential, which rejects ions between outer and inner solutions \cite{Wang_2014}.
+Such a view on hydrogels was employed in a series of works by the group of prof. Wilhelm (see for example \cite{Arens_2017,Fengler_2020}). 
+The authors of these works proposed to get rid of the osmotic membrane and simply use only micro filtration to compress the hydrogel squeezing out the accumulated inside the gel solution. 
+In their method first, the deswollen hydrogel was equilibrated with saline water feed. 
+During equilibration, the gel was swelling absorbing water. 
+Then it was taken out from the feed solution and mechanically squeezed by means of a microfiltration membrane. 
+The squeezed out brine was obtained to have lower salinity than the feed water.
 
-Moreover the hydrogel can be as an osmotic membrane from a thermodynamics
-perspective \cite{Wang_2014}. Such a view on hydrogels was employed
-in a series of works by the group of prof. Wilhelm (see for example
-\cite{Arens_2017,Fengler_2020}). The authors proposed to get rid of
-the osmotic membrane and simply use only a micro filtration membrane
-to compress the hydrogel and separate it from the solution. In their
-method first, the deswollen hydrogel was equilibrated with saline
-water feed. During equilibration, the gel was swelling absorbing water.
-Then it was taken out from the feed solution and mechanically compressed
-by means of a microfiltration membrane. The squeezed out brine was
-obtained to have lower salinity than the feed water.
-
-A similar approach was used by Ali \etal \cite{Ali2015}. In their
-study the thermosensitive gel was used (based on copolymers p-NIPAAm
-and p-AA), so instead of physical compression, the dewatering was
-done by an external heating stimulus (sunlight). At night the gel
-was equilibrating with feed water and at daytime, under sunlight,
-the gel was shrinking and releasing the collected inside water.
+A similar approach was used by Ali \etal \cite{Ali2015}. 
+In their study the thermosensitive gel was used (based on copolymers p-NIPAAm and p-AA), so instead of physical compression, the dewatering was done by an external heating stimulus (sunlight). 
+At night the gel was equilibrating with feed water and at daytime, under sunlight, the gel was shrinking and releasing the collected inside solution.
 
@@
 
-The maximum entropy principle requires the density of charges to be
-more-less the same throughout the system medium. Since the polyelectrolyte
-gel has its own charges and its own neutralizing counterions, the
-density of mobile ions (which are able to freely enter and leave the
-gel) in gel appears to be smaller than their density outside the gel.
-Therefore the internal solution of the gel has lower density of mobile
-ions than the solution outside. In that sense, the gel acts as an
-osmotic membrane separating solutions \cite{Rud2020}. The driving
-force of the separation is the Donnan potential originated from the
-charges of the hydrogel network. The density of mobile ions difference
-between ions concentrations in the internal and external solutions
+%The maximum entropy principle requires the density of charges to be more-less the same throughout the system medium. 
+Since the polyelectrolyte gel has its own charges and its own neutralizing counterions, the density of mobile ions (which are able to freely enter and leave the gel) in gel appears to be smaller than their density outside the gel.
+Therefore the internal solution of the gel has a lower density of mobile ions than that in the solution outside. 
+In that sense, the gel acts as an osmotic membrane separating solutions \cite{Rud2020}. 
+The driving force of the separation is the Donnan potential originated from the charges of the hydrogel network. 
+The density of mobile ions difference between ions concentrations in the internal and external solutions
 is defined by Donnan law \cite{Rud2018}
-\[
-\frac{c_{-}^{in}}{\cs}=\frac{\cs}{c_{+}^{in}}=\sqrt{1+\left(\frac{\alpha\cp}{2\cs}\right)^{2}}\pm\frac{\alpha\cp}{2\cs}
-\]
-where $c_{-}^{in}$ and $c_{+}^{in}$ are the internal concentration
-of anions and cations, $\cs$ is the salinity of external solution
-$\cp$ and $\alpha$ are the gel molar density and the ionization
-degree. The $\pm$ sign in the formula depends on whether the gel
-is made of polyanion or polycation.
+\begin{equation*}
+\frac{\ccl\gel}{\cs}=\frac{\cs}{\cna\gel}=\sqrt{1+\left(\frac{\alpha}{2\cs\Vgel}\right)^{2}}\pm\frac{\alpha}{2\cs\Vgel}
+\end{equation*}
+where $\ccl\gel$ and $\cna\gel$ are the internal concentration of monovalent anions and cations, $\cs$ is the salinity of external solution $\Vgel$ is the gel molar volume (inverse density of gel segments) and $\alpha$ is ionization degree.
+The $\pm$ sign in the formula accounts for the change between the cases of gel made of polyanion or polycation.
 
-The internal solution can be extracted by means of compression and/or
-other stimulus providing that the charge of the gel remains constant.
-In the case of gel made of weak (pH-sensitive) polyelectrolyte, the
-compression initiates discharging of the gel, therefore the neutralizing
-counterions may leave out the gel diminishing the desalination effect
-and affecting the pH of the extracted solution. Nevertheless, the
-release of counterions may be employed for desalination as well and
-the way how to do it is discussed in\cite{Rud2018}. 
-\begin{enumerate}
-\item However, one can argue that sole Donnan effect is insufficient to
-achieve a high salt rejection \cite{Cai2016} and the salinity of
-the water squeezed from hydrogel under a very high hydraulic pressure
-(up to 100 bar \cite{Fengler_2020}) turns to be not much different
-from the initial.
-\item Indeed, the use of high hydraulic pressure diminishes all the advantages
-of this method over the reverse osmosis. At the same time the reversibility
-of hydrogel swelling after such strong compression remains questionable. 
-\item Nevertheless by the current study we would like to model the compression
-of the gel limiting ourselves within low compression rates, less than
-5 bar. We will show how the compression of the gel affects the surrounding
-salinity and model the whole desalination process as a cascade of
-$c$. 
-\end{enumerate}
-In the current study we would like to concentrate on the use of gel
-made of strong polyelectrolyte for water desalination. Namely, to
-investigate how the compression of the gel affects the salinity of
-the surrounding the gel solution and to propose the way of water desalination
-employing the hydrogel swelling/deswelling set of processes.
+The lower salinity solution can be extracted from the gel by means of compression and/or other stimulus providing that the charge of the gel remains constant.
+In the case of gel made of weak (pH-sensitive) polyelectrolyte, the compression discharges the gel, therefore the neutralizing counterions leave out the gel diminishing the desalination effect \cite{Rud2018}.
+%Nevertheless, in\cite{Rud2018} we discussed how the release of counterions may be employed for desalination as well.
 
-The target of our study is to model the thermodynamic equilibrium
-between the two boxes and to show how the compression of the gel affects
-the ion density in the outside solution.
+One can argue that the sole Donnan effect is insufficient to achieve a high salt rejection \cite{Cai2016} and the salinity of the water squeezed from hydrogel under a very high hydraulic pressure (up to 100 bar \cite{Fengler_2020}) turns out to be not much different from the initial.
+Indeed, the use of high hydraulic pressure diminishes all the advantages of this method over RO, and the reversibility of hydrogel swelling after strong compression remains questionable. 
+Nevertheless, in the current study, we model the compression of the gel limiting ourselves to low compression rates, less than 5 bar, and studied how the compression of the gel affects the surrounding salinity.
+We demonstrated the desalination process composed of a cascade of following one by each other gel swellings and compressions driving the salinity of gel supernate down to drinkable water. 
+%In the current study we would like to concentrate on the use of gel made of strong polyelectrolyte for water desalination. 
+%Namely, to investigate how the compression of the gel affects the salinity of the surrounding the gel solution and to propose the way of water desalination employing the hydrogel swelling/deswelling set of processes.
+
+%The target of our study is to model the thermodynamic equilibrium between the two boxes and to show how the compression of the gel affects the ion density in the outside solution.
 
@@
 \begin{figure*}[t]
-\subfloat[Partial pressure of the gel versus gel molar volume \label{fig: PV}]
+\subfloat[The gel partial pressure vs gel molar volume \label{fig: PV}]
 {\includegraphics[width=0.48\textwidth]{figures/fig_PV_pub}}
 \hspace{0.02\textwidth}
-\subfloat[Supernatant salinity versus gel molar volume\label{fig: CV}]
+\subfloat[Supernate salinity vs gel molar volume\label{fig: CV}]
 {\includegraphics[width=0.48\textwidth]{figures/fig_CV_pub}}
@@
 \begin{figure*}[t]
-\subfloat[Pressure vs gel density \label{fig: NV}]
+\subfloat[Pressure vs gel molar volume \label{fig: NV}]
 {\includegraphics[width=0.49\textwidth]{figures/fig_NV_pub}}
-\subfloat[Salinity vs gel density\label{fig: CN}]
+\subfloat[Salinity vs gel molar volume\label{fig: CN}]
 {\includegraphics[width=0.495\textwidth]{figures/fig_NVbox_mu_pub}}
@@
 \end{table}
+
 \end{document}

### 2022-07-01 gibbs.tex
abstract

@@
 Indeed, polyelectrolyte hydrogels have the ability to absorb a big amount of water across forward osmosis membrane as a result of their swelling pressure. 
-The insoluble cross-linked network of the gel enables dewatering under the influence of a stimulus (thermal and/or mechanical) \todo{remove this sentence?}.
-On the other hand, the network structure of a polymer hydrogel, from a thermodynamic
-perspective, is already an osmotic membrane. So hydrogel microparticles
-may allow to completely avoid the osmotic membranes in forward osmosis
-and use microfiltration instead.
+On the other hand, the insoluble cross-linked network of the gel enables dewatering under the influence of a stimulus (thermal and/or mechanical).
+Moreover, from a thermodynamic perspective, the polyelectrolyte hydrogel is already an osmotic membrane rejecting ions between external and internal solutions.
+These three properties of the gels make it possible to use them for desalination and at the same time avoid the use of expensive membranes.
+In this article, we present our recent theoretical study of the use of polyelectrolyte hydrogel for water desalination. 
+We modeled the thermodynamic equilibrium between coexisting phases of the gel and supernate aqueous salt solution.
+We have shown that the salinity of the supernate phase decreases during compression of the gel due to the release of absorbed in gel solution of lower salinity. 
+Finally, we performed a set of simulations modeling the process of continuous decrease of solution salinity up to freshwater concentrations.
 
-In this article, we present our recent theoretical study of the use of polyelectrolyte hydrogel for water desalination. 
-We modeled the thermodynamic equilibrium of coexisting gel and aqueous salt solution phases in the so-called `closed' ensemble, in which the total amount of ions is assumed to be constant. 
-We modeled the compression of the gel associated with the release of solution and have shown that the squeezed-out solution has a little lower salinity than the one the gel was equilibrated with. 
-Finally, we performed a set of simulations modeling the process of continuous decrease of water salinity up to freshwater concentrations.
 \end{abstract}
@@
 \paragraph{Physics behind the desalination process.}
-
-\begin{figure*}
-\centering 
-\includegraphics[width=0.5\textwidth]{figures/gc}\includegraphics[width=0.5\textwidth]{figures/gibbs}\caption{Diamond-like network in the simulation box. Color code represents
-the individual ion types (red: $\na$, blue: $\cl$, yellow: $\ca$)
-and the hydrogel (gray: neutral segment ($\AH$), cyan: charged segment
-($\A$)). \label{fig:open and closed}.}
-\end{figure*}
-
 %The maximum entropy principle requires the density of charges to be more-less the same throughout the system medium. 
@@
 Nevertheless, in the current study, we model the compression of the gel limiting ourselves to low compression rates, less than 5 bar, and studied how the compression of the gel affects the surrounding salinity.
-We demonstrated the desalination process composed of a cascade of following one by each other gel swellings and compressions driving the salinity of gel supernate down to drinkable water. 
+We modelled also the desalination process, as a cascade of following one by each other gel swellings and compressions driving the salinity of supernate down to drinkable water. 
 %In the current study we would like to concentrate on the use of gel made of strong polyelectrolyte for water desalination. 
@@
 
-\begin{figure*}
+\begin{figure*}[t]
 \centering \includegraphics[width=0.5\textwidth]{figures/simgibbs}\caption{Diamond-like network in the simulation box. Color code represents
@@
 \end{equation}
+
+\begin{figure*}[t]
+\centering 
+\includegraphics[width=0.5\textwidth]{figures/gc}\includegraphics[width=0.5\textwidth]{figures/gibbs}\caption{Diamond-like network in the simulation box. Color code represents
+the individual ion types (red: $\na$, blue: $\cl$, yellow: $\ca$)
+and the hydrogel (gray: neutral segment ($\AH$), cyan: charged segment
+($\A$)). \label{fig:open and closed}.}
+\end{figure*}
+
 \paragraph{Open system.}
-
 We simulate the open system using the grand reaction method \cite{Landsgesel2020a,Rud2020}.

### 2022-07-01 gibbs.tex
theory part

@@
 \newcommand{\cp}{c_\mathrm{p}}
-\newcommand{\nna}{N_\mathrm{Na^+}}
-\newcommand{\ncl}{N_\mathrm{Cl^-}}
+\newcommand{\nna}{n_\mathrm{Na^+}}
+\newcommand{\ncl}{n_\mathrm{Cl^-}}
 \newcommand{\ncleq}{\widetilde{N}_\mathrm{Cl^-}}
@@
 %\newcommand{\Vgel}{V\gel}
-\newcommand{\Vgel}{v_\mathrm{gel}}
+\newcommand{\Vgel}{V_\mathrm{gel}}
+\newcommand{\Ngel}{N_\mathrm{gel}}
 \newcommand{\Vgeleq}{\widetilde{\Vgel}}
@@
 \newcommand{\Pres}{P\res}
-\newcommand{\Vout}{V\out}
-\newcommand{\Vbox}{V\tot}
+\newcommand{\Vout}{V_\mathrm{out}}
+\newcommand{\Vbox}{V_\mathrm{box}}
 \newcommand{\PE}{polyelectrolyte{}}
@@
 \begin{figure*}[t]
-\centering \includegraphics[width=0.5\textwidth]{figures/simgibbs}\caption{Diamond-like network in the simulation box. Color code represents
+\centering \includegraphics[width=0.7\textwidth]{figures/simgibbs}\caption{Diamond-like network in the simulation box. Color code represents
 the individual ion types (red: $\na$, blue: $\cl$, yellow: $\ca$)
@@
 
-We model our gel as a network of 16 linear polymer chains, each by
-30 monomer units. The chains are connected to a diamond-like polymer
-network and put into a simulation box with periodic boundaries. Each
-unit of the network carries a negative electric charge, which is equal
-to the charge of electron. Except the particles of the network, the
-mobile monovalent ions, $\na$ and $\cl$, are present in simulation
-box. The total electric charge of all the particles in the box is
-zero, therefore the amount of $\na$ ions is bigger than that of $\cl$
-by the number of hydrogel units, $N\gel=16\cdot30=480$.
+We model the gel as a network of 16 linear polymer chains, each by 30 monomer units. 
+The chains are connected to a diamond-like polymer network throught 8 crosslinking units, and put into a simulation box with periodic boundaries (see \reffig{fig:diamond}). 
+Each unit of the network carries a negative electric charge, which is equal to the charge of electron. 
+Except the particles of the network, the monovalent co- and counter-ions ions, $\cl$ and $\na$, are present in simulation box. 
+The total electric charge of all the particles in the box is zero, therefore the amount of $\na$ ions is bigger than that of $\cl$ by the number of hydrogel units, $\Ngel=16\cdot30 + 8=488$.
 
-The goal of this study is to simulate the process of water desalination
-by means of compression. In order to do it we simulate the gel in
-two ensembles.
+\begin{figure*}[t]
+\centering 
+\subfloat[Open system \label{fig: open}]
+{\includegraphics[width=0.5\textwidth]{figures/gc}}
+\subfloat[Closed system \label{fig: closed}]
+{\includegraphics[width=0.5\textwidth]{figures/gibbs}}
+\caption{Diamond-like network in the simulation box. Color code represents
+the individual ion types (red: $\na$, blue: $\cl$, yellow: $\ca$)
+and the hydrogel (gray: neutral segment ($\AH$), cyan: charged segment
+($\A$)). \label{fig:open and closed}.}
+\end{figure*}
+We simulate the compression of the gel in two ensembles.
 \begin{enumerate}
@@
 \end{enumerate}
-The compression of the gel in the open system does not affect the surrounding salinity, thus the chemical potential of ions remains constant $\muna=$ $\mucl=$ $\text{Const}$. 
-On the contrary, what remains constant in the closed system is total number of ions, that are contained in the gel and in the external volume, $\nna=\text{Const}$ and $\ncl=\text{Const}$.
-By $\nna$ and $\ncl$ we will understand the density of the corresponding ion in the compression volume
+The compression of the gel in the \emph{open} system does not affect the surrounding salinity, thus the density of ions outside the gel remains constant $\cs =$ $\cna=$ $\ccl=$ $\text{Const}$ (\reffig{fig: open}).
+On the contrary, what remains constant in the \emph{closed} system, is the total number of $\na$ and $\cl$ ions, that are contained in the gel and in the external volume, \ie in the volume $\Vbox$ (\reffig{fig: closed}).
+
+Let $\nna$ and $\ncl$ be the density of the corresponding ion in the compression volume, $\Vbox$ averaged over this volume
 \begin{equation}
-\ncl = \left(\ncl\gel + \cs\cdot(\Vbox - \Vgel)\right)/\Vbox
+n_i = \left(N_i\gel + \cs\cdot(\Vbox - \Vgel)\right) / \Vbox
 \end{equation}
-
-\begin{figure*}[t]
-\centering 
-\includegraphics[width=0.5\textwidth]{figures/gc}\includegraphics[width=0.5\textwidth]{figures/gibbs}\caption{Diamond-like network in the simulation box. Color code represents
-the individual ion types (red: $\na$, blue: $\cl$, yellow: $\ca$)
-and the hydrogel (gray: neutral segment ($\AH$), cyan: charged segment
-($\A$)). \label{fig:open and closed}.}
-\end{figure*}
+where $ i \in \{\na, \cl\}$,  $N_i$ is the amount of the corresponding ions in gel.
+Then in closed system $\nna$ and $\ncl$ remain constant, whereas the salinity of supernate, $\cs$, may change with the change of the gel volume.
 
@@
 
-The similar scheme we use to simulate the gel in closed system. The
-procedure represents a chain of subsequent MD and MC simulation, but
-now we run the molecular dynamics in two simulation boxes simultaneously.
-The first box of the volume $\Vgel$ contains the gel with ions, and
-the second box, $\Vout$--- contains only ions. These two boxes are
-represented in Figure~\ref{fig:diamond}. The total volume of both
-boxes is kept constant, $V=V_{\mathrm{gel}}+V_{\mathrm{out}}$, so
-the compression of the gel implies the decrease $\Vgel$ and increase
-$\Vout$.
-
-The thermodynamic equilibrium between the two volumes implies the
-exchange of the ion pairs between them, which is done by means of
-MC procedure in a way similar to described in \cite{Panagiotopoulos1988b}.
+The similar scheme we use to simulate the gel in closed system. 
+The procedure represents a chain of subsequent MD and MC simulation, but now the molecular dynamics is runing in two simulation boxes simultaneously.
+The first box of the volume $\Vgel$ contains the gel with ions, and the second box, $\Vout$--- contains only ions. 
+The total volume of both boxes is kept constant, $\Vbox=V_{\mathrm{gel}}+V_{\mathrm{out}}$, so the compression of the gel implies the decrease $\Vgel$ and increase $\Vout$.
+These two boxes are represented in \reffig{fig:diamond}.
 
 \paragraph{Algorithm.}
-
-In general the simulation algorithm is following:
+The thermodynamic equilibrium between the two volumes implies the exchange of the ion pairs between them, which is done by means of MC procedure in a way similar to described in \cite{Panagiotopoulos1988b}.
+The simulation algorithm is following:
 \begin{enumerate}
-\item simulate molecular dynamics in both boxes; collect the observables,
-for examples pressure values $P$, to an array; 
-\item perform Monte-Carlo procedure simulating ion pair exchange; collect
-the arrays of observables sample : number of ions in both boxes, $\nna^{I}$,
-$\ncl^{I}$, $\nna^{II}$ and $\ncl^{II}$ ; 
-\item repeat the procedure until the desired length of sample arrays is
-reached.
+\item Simulate molecular dynamics in both boxes; collect the observables, for examples, values of pressure $P$, to an array; 
+\item Perform Monte-Carlo procedure simulating ion pair exchange; collect the arrays of observables samples: number of ions in both boxes, $\nna\gel$,
+$\ncl\gel$, $\nna\out$ and $\ncl\out$ ; 
+\item Repeat the procedure until the desired length of sample arrays is reached.
 \end{enumerate}

### 2022-07-01 gibbs.tex
results up to desalination

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
-%\usepackage[utf8]{inputenc}
-\usepackage{amssymb}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
-\newcommand{\ie}{\textit{i.~e.} }
-\newcommand{\cref}{c^{\ominus}}
-%\newcommand{\cs}{c_{s}}
-\newcommand{\kT}{k_\mathrm{B}T}
-\newcommand{\kB}{k_\mathrm{B}}
-\newcommand{\lb}{l_\mathrm{B}}
-\newcommand{\NA}{N_{\mathrm{A^-}}}
-\newcommand{\muna}{\mu_\mathrm{Na^+}}
-
-\newcommand{\mucl}{\mu_\mathrm{Cl^-}}
-\newcommand{\muca}{\mu_\mathrm{Ca^{2+}}}
-\newcommand{\muh}{\mu_\mathrm{H^+}}
-\newcommand{\mua}{\mu_\mathrm{A^-}}
-\newcommand{\muha}{\mu_\mathrm{HA}}
-\newcommand{\muoh}{\mu_\mathrm{OH}}
-
-\newcommand{\cna}{c_\mathrm{Na^+}}
-\newcommand{\ccl}{c_\mathrm{Cl^-}}
-\newcommand{\cca}{c_\mathrm{Ca^{2+}}}
-\newcommand{\ch}{c_\mathrm{H^+}}
-\newcommand{\cp}{c_\mathrm{p}}
-\newcommand{\nna}{n_\mathrm{Na^+}}
-\newcommand{\ncl}{n_\mathrm{Cl^-}}
-\newcommand{\ncleq}{\widetilde{N}_\mathrm{Cl^-}}
-\newcommand{\nca}{N_\mathrm{Ca^{2+}}}
-
-\newcommand{\superin}{^\mathrm{in}}
-\newcommand{\subin}{_\mathrm{in}}
-\newcommand{\subi}{_\mathrm{i}}
-
-\newcommand{\gel}{^\mathrm{gel}}
-\newcommand{\tot}{^\mathrm{tot}}
-\newcommand{\out}{^{out}}
-\newcommand{\coh}{c_\mathrm{OH}}
-\newcommand{\bulk}{^{\mathrm{b}}}
-\renewcommand{\H}{\mathrm{H^+}}
-\newcommand{\A}{\mathrm{A^-}}
-\newcommand{\AH}{\mathrm{AH}}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
-%% A simple dot to overcome graphicx limitations
-\newcommand{\lyxdot}{.}
-\newcommand{\todoi}[1]{\todo[inline]{#1}}
-\setuptodonotes{fancyline, color=blue!30, size=\tiny}
-
-\newcommand{\cl}{\mathrm{Cl^-}}
-\newcommand{\br}{\mathrm{Br^-}}
-\newcommand{\na}{\mathrm{Na^+}}
-\newcommand{\h}{\mathrm{H^+}}
-\newcommand{\ka}{\mathrm{K^+}}
-\newcommand{\oh}{\mathrm{OH^-}}
-\newcommand{\ca}{\mathrm{Ca^{2+}}}
-\newcommand{\mg}{\mathrm{Mg^{2+}}}
-\newcommand{\so}{\mathrm{SO_4^{2-}}}
-
-\newcommand{\EI}{E_{\mathrm{I}}}
-\newcommand{\EII}{E_{\mathrm{II}}}
-\newcommand{\SI}{S_{\mathrm{I}}}
-\newcommand{\SII}{S_{\mathrm{II}}}
-\newcommand{\NI}{N_{\mathrm{I}}}
-\newcommand{\NII}{N_{\mathrm{II}}}
-\newcommand{\VI}{V_{\mathrm{I}}}
-\newcommand{\VII}{V_{\mathrm{II}}}
-\newcommand{\FI}{F_{\mathrm{I}}}
-\newcommand{\FII}{F_{\mathrm{II}}}
-\newcommand{\nnaI}{N^{\na}_{\mathrm{I}}}
-\newcommand{\nclI}{N^{\cl}_{\mathrm{I}}}
-\newcommand{\nnaII}{N^{\na}_{\mathrm{II}}}
-\newcommand{\nclII}{N^{\cl}_{\mathrm{II}}}
-
-\newcommand{\Ka}{K_{\mathrm{A}}}
-\newcommand{\pKa}{\mathrm{p}\Ka}
-\newcommand{\pK}{\mathrm{p}K}
-\newcommand{\pH}{\mathrm{pH}}
-\newcommand{\mol}{\mathrm{mol}}
-\newcommand{\molperl}{\mathrm{mol/l}}
-\newcommand{\kg}{\mathrm{kg}}
-\newcommand{\res}{^{\mathrm{res}}}
-\newcommand{\pHres}{\pH\res}
-\newcommand{\pHgel}{\pH\gel}
-\newcommand{\cs}{c_{\mathrm{s}}}
-%\newcommand{\cs}{c_{\mathrm{salt}}}
-\newcommand{\csres}{\cs\res}
-%\newcommand{\Vgel}{V\gel}
-\newcommand{\Vgel}{V_\mathrm{gel}}
-\newcommand{\Ngel}{N_\mathrm{gel}}
-\newcommand{\Vgeleq}{\widetilde{\Vgel}}
-\newcommand{\Pgel}{P\gel}
-\newcommand{\Pres}{P\res}
-\newcommand{\Vout}{V_\mathrm{out}}
-\newcommand{\Vbox}{V_\mathrm{box}}
-\newcommand{\PE}{polyelectrolyte{}}
-
-\newcommand{\reffig}[1]{Figure~\ref{#1}}
-\newcommand{\refeq}[1]{Equation~\ref{#1}{}}
-\usepackage{afterpage}
-\newcommand\blankpage{%
-    \null
-    \thispagestyle{empty}%
-    \addtocounter{page}{-1}%
-    \newpage}
-
-\newcommand{\mytitle}{Gibbs ensemble for \PE{} hydrogel}
-\newcommand{\etal}{\textit{et al.}{}}
-
-\@ifundefined{showcaptionsetup}{}{%
- \PassOptionsToPackage{caption=false}{subfig}}
-\usepackage{subfig}
+\input{definitions.tex}
 \makeatother
@@
 \paragraph{Compression in open system.}
-
-First we run a set of simulations modeling the gel compression in \emph{open system}, \ie in equilibrium with big bath of certain salinity, $\cs$. 
-The simulations are run for a set of different simulation box volumes. 
-Each simulation returns the averaged pressure, $P$, and the number of $\cl$ ions present in the simulation box, $\ncl$.
-
-In order to get the partial pressure of the gel, we substitute from $P$ the osmotic pressure of ions in reservoir: $P^{gel}=P-P^{res}$.
-$P^{res}$, in turn, we calculate by running a separate simulation of a reservoir, containing ionic gas in equilibrium with the bath of the same salinity $\cs$. 
-The gel partial pressure, $\Pgel$, is the pressure which needs to be applied to the gel via solvent permeable filter to compress the gel to a molar specific volume, $V$.
-
-The dependencies of $\Pgel$ versus gel molar volume $\Vgel$ (the volume calculated per one mol of gel segment) are present in Figure \ref{fig: PV} for a set of different salinity. 
-These dependencies corresponding to \emph{open system} are represented here by solid lines. 
-For example, blue solid line illustrates the compression (or swelling) of the gel in equilibrium with a reservoir of salinity, $\cs=0.063$ mol/l. 
-The points where the pressure equals to zero, $\Pgel=0$, (indicated by filled circles) are the gel \emph{free swelling equilibrium} states. 
-It is seen, that the increase of salinity shifts the free swelling equilibrium towards smaller volumes, \ie the gel shrinks with increasing salinity. 
-In general, all the solid curves shift towards smaller volumes with increasing salinity. 
-This effect is well known, and is typical for all branched \emph{strong} polyelectrolytes. 
-It is caused by the decrease of ions osmotic pressure and by screening of electrostatic interactions \cite{Zhulina2000,Landsgesel2020a}.\footnote{The salinity dependence of the size of \emph{weak} polyelectrolyte gel is in general non-monotonic \cite{Rud2018} but the case of weak polyelectrolyte is beyond the scope of this study.
-} %
-
-\paragraph{Compression in closed system.}
-
 \begin{figure*}[t]
@@
 \end{figure*}
+First, we run a set of simulations modeling the gel compression in \emph{open system}, \ie in equilibrium with a big bath of certain salinity, $\cs$. 
+The simulations are run for a set of different simulation box volumes. 
+Each simulation returns the averaged pressure, $P$, and the number of $\cl$ ions present in the simulation box, $\ncl$.
 
-Each set of simulations in an \emph{open system} defines the free swelling equilibrium state of the gel for each salinity. 
-Namely, each salinity correspond to a certain gel molar volume, and to a certain amount of ions in gel in equilibrium state, $\cs\longrightarrow$, $\left(\Vgeleq,\ \ncleq\right)$.
-These equilibrium states we use as starting ones for the gel compression in \emph{closed system}. 
-Thus, we simulate the compression of the gel in the closed volume, $\Vbox$, which is equal to $\Vgeleq$, and contains $\ncleq$ of ion pairs (apart from neutralizing counterions). 
-So, we prepare two systems, one~--- simulating the gel of the volume $\Vgel$, and another~--- simulating the supernatant solution of the volume $\Vout = \Vbox - \Vgel$; in this way the total volume containing the gel and the supernatant solution remains constant.
-Also, the ion pairs of the amount $\ncleq$ remain all the time constant and are shared between the two volumes.
-%For each different initial states we run a set of simulations emulating the compression of the gel, \ie varying simultaneously $\Vgel$ and $\Vout$.
-%At any all the ions are getting redistributed between the systems but their total amount remains constant and equal to $\ncl^{0}$.
+In order to get the partial pressure of the gel, we substitute from $P$ the osmotic pressure of ions in the reservoir: $P^{gel}=P - P^{res}$.
+$P^{res}$, in turn, we calculate by running a separate simulation of a reservoir, containing ionic gas in equilibrium with the bath of the same salinity $\cs$. 
+The gel partial pressure, $\Pgel$, is the pressure that needs to be applied to the gel via a solvent permeable filter to compress the gel to a molar-specific volume, $\Vgel$.
 
-The process of the gel compression in \emph{closed} system is depicted in Figure~\ref{fig: PV} (dotted lines). 
-There the gel partial pressure is depicted as function of the gel molar volume.
-In this plot, the blue dotted line, for example, illustrates the compression of the gel equilibrated with the solution of salinity $\cs=0.063$ mol/l, in a volume which gel has at zero pressure. 
-Since, in this case, the volumes of the gel $\Vgel$ and of the supernatant solution $\Vout$ are comparable, the compression of the gel affects the salinity of supernatant solution. 
-The salinity now decreases, changing from $\cs^{0}=0.063$ at free swelling equilibrium state to 0.045 mol/l at $P\gel=5$ bar.
-
-The change of salinity is seen from Figure~\ref{fig: CV}. 
-In this Figure the gel swelling/compression processes are illustrated in different coordinates, \ie salinity of supertnatant outside the gel versus the gel molar volume, $\cs(\Vgel)$.\todo{we should stick to only 'supernate' or 'supernatant'}
-%Similarly, as in Figure~\ref{fig:fig PV}, the solid lines correspond to compression in \emph{open} system and dotted lines~--- in \emph{closed} system. 
-In this coordinates, all the open system compressions turn to the horizontal lines, which reflects the constant salinity, but the compressions in closed system indicate the decrease of $\cs$s.
-% Maybe "In this coordinates, each open system compression turns to the horizontal line, which reflects the constant salinity, whereas each compression in closed system shows the decrease of $\cs$s." would be better
-
-Although the salinity during compression in \emph{open} system remains constant, the number of ions in a compression volume, i.e. in the volume where the gel is compressed, changes.
-As the compression volume $\Vbox$ we chose the volume of the free swelling equilibrium state of the gel, $\Vbox = \widetilde{\Vgel}$ 
-In the Figure \ref{fig: NV} we depicted the number of $\cl$ ions in the volume $\Vbox$, calculated per unit volume, $\ncl/\Vbox$, as a function of the gel molar volume. 
-The depicted value can be considered as the density of $\cl$ ions averaged out over the volume $\Vbox$.
-
-As it is expected in case of closed system these dependencies look like horizontal lines, whereas in open system, the amount of ions in compression volume increases with compression. 
-This implies, that the compression of the gel in open system pulls out the ions from the bath to the compression volume. 
-And vice versa, the swelling of the gel pushes ions out to the bath.
-
-Finally in Figure \ref{fig: CN} the same processes are depicted in coordinates number of particles in compression volume --- salinity of the outside solution. 
-In this coordinates both ways of the compression, in \emph{open} and in \emph{closed} system, appear as straight vertical and horizontal lines correspondingly.
-
-In our study we modeled the compression of the gel in equilibrium with reservoirs of 40 different salinities, ranging from 0.001 to 0.5 mol/l. 
-Every open system compression resulted a defined free swelling equilibrium state, \ie the the gel molar volume and the number of ions in gel $\left(\Vgeleq,\ \ncleq\right)$ at zero pressure.
-These states were used as the initial ones for the compression in closed systems. 
-All the corresponding dependencies are depicted in Figures~\ref{fig: PV and CV} and \ref{fig: NV and CN} as thin grey dashed lines. 
-The states corresponding to $P^{gel}=0$, 5 and 10 bar pressure are marked by open circles, squares and crosses respectively. 
-The non-shadowed areas on the Figures limit the states corresponding to gel partial pressure ranging between 0 and 5 bar.
+The dependencies of $\Pgel$ on the gel molar volume $\Vgel$ are present in Figure \ref{fig: PV} for a set of different salinities. 
+These dependencies (the case of \emph{open system}) are represented by solid lines. 
+For example, the blue solid line illustrates the compression (or swelling) of the gel in equilibrium with a reservoir of salinity, $\cs=0.063$ mol/l. 
+The points where the pressure equals zero, $\Pgel=0$, (indicated by filled circles) are the gel \emph{free swelling equilibrium} states. 
+It is seen, that the increase of salinity shifts the free swelling equilibrium towards smaller volumes, \ie the gel shrinks with increasing salinity. 
+In general, all the solid curves shift towards smaller volumes with increasing salinity. 
+This effect is well known and is typical for all branched \emph{strong} polyelectrolytes. 
+It is caused by the decrease of ions osmotic pressure and by a screening of electrostatic interactions \cite{Zhulina2000, Landsgesel2020a}.\footnote{The salinity dependence of the size of \emph{weak} polyelectrolyte gel is in general non-monotonic.
+We discuss this case in \cite{Rud2018}.
+} %
 
@@
 
+\paragraph{Compression in closed system.}
+Each set of simulations in an \emph{open system} defines the free swelling equilibrium states of the gel for each salinity, that is the state where the gel partial pressure equals zero. 
+These states are characterized by the corresponding molar volume of the gel, $\Vgel^0$ and the densities of ions in gel \{$\nna^0$, $\ncl^0$\} 
+(Index ``0'' stands for zero bar applied pressure).
+We use the free swelling equilibrium states as the starting ones for the gel compression in \emph{closed system}. 
+Thus, we simulate the compression of the gel in the closed volume, $\Vbox$, which is equal to $\Vgel^0$, and contains $\ncl^0$ of $\cl$ ions and the $\na$ ions in the amount neutralizing the system,$\ncl^0$.
+
+We prepare two systems, one~--- simulating the gel of the volume $\Vgel$, and another~--- simulating the supernatant solution of the volume $\Vout = \Vbox - \Vgel$.
+Also, the ions of the amount $\Ncl^0$ and $\Nna^0$ are shared between the two volumes.
+
+The process of the gel compression in the \emph{closed} system is depicted in Figure~\ref{fig: PV} (dotted lines) as the dependence of gel partial pressure versus the gel molar volume.
+In this plot, the blue dotted line, for example, illustrates the compression of the gel equilibrated with the solution of salinity $\cs=0.063$ mol/l, in a volume which gel has at zero pressure. 
+Since, in this case, the volumes of the gel $\Vgel$ and of the supernate $\Vout$ are comparable, the compression of the gel affects the salinity of supernate, $\cs$. 
+The supernate salinity now decreases, changing from $\cs^{0}=0.063$ at the free swelling equilibrium state to $\cs^{5}=0.045$ mol/l in the state with applied pressure $P\gel=5$ bar (index ``5'' stands for 5 bar).
+
+The \reffig{fig: CV} illustrates the same swelling/compression processes, but in different coordinates: \ie salinity of supernate versus the gel molar volume, $\cs(\Vgel)$.
+In these coordinates, all the open system compressions show up as horizontal lines, which reflects the constant salinity, whereas the compressions in the closed system demonstrate the decrease of $\cs$.
+
+Although the salinity during compression in \emph{open} system remains constant, the number of ions in a compression volume, i.e. in the volume where the gel is compressed (or swells), changes.
+As the compression volume $\Vbox$ we chose the volume of the free swelling equilibrium state of the gel, $\Vbox = \Vgel^0$.
+In the Figure \ref{fig: NV} we depicted the number of $\cl$ ions in the volume $\Vbox$, calculated per unit volume, $\ncl =$ $\Ncl/\Vbox$, as a function of the gel molar volume. 
+The depicted value can be considered as the density of $\cl$ ions averaged out over the volume $\Vbox$.
+
+As it is expected in case of closed system these dependencies look like horizontal lines, whereas in open system, the amount of ions in compression volume increases with compression. 
+This implies, that the compression of the gel in open system pulls out the ions from the bath to the compression volume, $\Vbox$. 
+And vice versa, the swelling of the gel pushes ions out to the bath.
+
+Finally, in Figure \ref{fig: CN} the same processes are depicted in coordinates $\ncl$ --- $\cs$. 
+In these coordinates, both ways of the compression, in \emph{open} and in \emph{closed} system, appear as straight vertical and horizontal lines correspondingly.
+
+In our study, we modeled the compression of the gel in equilibrium with reservoirs of 40 different salinities, ranging from 0.001 to 0.5 mol/l. 
+Every open system compression resulted in a defined free swelling equilibrium state, which we used as the initial ones for the compression in closed systems. 
+All the corresponding dependencies are depicted in Figures~\ref{fig: PV and CV} and \ref{fig: NV and CN} as thin grey dashed lines (some of them are highlighted and colored).
+The states corresponding to $P^{gel}=0$, 5 and 10 bar pressure are marked by open circles, squares, and crosses respectively. 
+The non-shadowed areas in the Figures highlight the states in which the gel partial pressure ranges between 0 and 5 bar.
+
 \paragraph{Desalination scheme.}
-
 As we have seen, the compression of the gel in a closed system affects the salinity, whereas the compression in an open system affects the amount of ions in a volume where the gel is compressed in. 

### 2022-07-01 diff.sh
diff.sh

@@ -1,0 +1,3 @@
+latexdiff gibbs_old.tex gibbs.tex  > diff.tex
+latexmk -pdf -f diff.tex
+evince diff.pdf

### 2022-07-04 gibbs.tex
edits

@@
 We simulate the open system using the grand reaction method \cite{Landsgesel2020a,Rud2020}.
-This method is a hybrid of molecular dynamics (MD) and Monte Carlo
-(MC). The whole simulation represents a chain of subsimulations of
-MD and MC followed one by each other. For MD simulation we used a
-standard Langevin dynamics \cite{Grest1986} which models the mechanical
-movement of all the system particles. Whereas MC simulates the thermodynamic
-equilibrium with reservoir, which exchanges ions with the simulation
-box. The insertion (and deletion) of ion pairs is considered as a
-reaction of creation (or annihilation) of an ion pair 
+This method is a hybrid of molecular dynamics (MD) and Monte Carlo (MC). 
+The whole simulation represents a chain of subsimulations of MD and MC followed one by each other.
+For MD simulation we used a standard Langevin dynamics \cite{Grest1986} which models the mechanical movement of all the system particles.
+Whereas MC simulates the thermodynamic equilibrium with reservoir, which exchanges ions with the simulation box. 
+The insertion (and deletion) of ion pairs is considered as a reaction of creation (or annihilation) of an ion pair 
 \[
@@
 \paragraph{Closed system.}
-
 The similar scheme we use to simulate the gel in closed system. 
@@
 The simulations are run for a set of different simulation box volumes. 
-Each simulation returns the averaged pressure, $P$, and the number of $\cl$ ions present in the simulation box, $\ncl$.
+Each simulation returns the averaged pressure, $P$, and the number of $\cl$ ions, which are present in the simulation box, $\ncl$.
 
-In order to get the partial pressure of the gel, we substitute from $P$ the osmotic pressure of ions in the reservoir: $P^{gel}=P - P^{res}$.
-$P^{res}$, in turn, we calculate by running a separate simulation of a reservoir, containing ionic gas in equilibrium with the bath of the same salinity $\cs$. 
+In order to get the partial pressure of the gel, we substitute from $P$ the osmotic pressure of ions in the reservoir: $\Pgel=P - \Pout$.
+$\Pout$, in turn, we calculate by running a separate simulation of a reservoir, containing ionic gas in equilibrium with the bath of the same salinity $\cs$. 
 The gel partial pressure, $\Pgel$, is the pressure that needs to be applied to the gel via a solvent permeable filter to compress the gel to a molar-specific volume, $\Vgel$.
@@
 The points where the pressure equals zero, $\Pgel=0$, (indicated by filled circles) are the gel \emph{free swelling equilibrium} states. 
-It is seen, that the increase of salinity shifts the free swelling equilibrium towards smaller volumes, \ie the gel shrinks with increasing salinity. 
-In general, all the solid curves shift towards smaller volumes with increasing salinity. 
+These states shift towards smaller volumes with increase of salinity. 
+It is seen, that the increase of salinity shifts the free swelling equilibrium towards smaller volumes. 
+In general, the increase of salinity shift all the $\Pgel(V)$ curves towards smaller volumes
+
 This effect is well known and is typical for all branched \emph{strong} polyelectrolytes. 

### 2022-07-04 gibbs.tex
changed n to N

@@
 with gel freely exchanges ions with a big amount of aqueous solution
-of certain constant salinity. 
+of certain constant salinity, $\cs$. 
 \item And in \emph{closed system}, when the gel is in equilibrium with a
@@
 
-Let $\nna$ and $\ncl$ be the density of the corresponding ion in the compression volume, $\Vbox$ averaged over this volume
+%Let $\nna$ and $\ncl$ be the density of the corresponding ion in the compression volume, $\Vbox$ averaged over this volume
 \begin{equation}
-n_i = \left(N_i\gel + \cs\cdot(\Vbox - \Vgel)\right) / \Vbox
+N_i = N_i\gel + \cs\cdot(\Vbox - \Vgel)
 \end{equation}
-where $ i \in \{\na, \cl\}$,  $N_i$ is the amount of the corresponding ions in gel.
-Then in closed system $\nna$ and $\ncl$ remain constant, whereas the salinity of supernate, $\cs$, may change with the change of the gel volume.
+where $i \in \{\na, \cl\}$,  $N_i$ is the amount of the corresponding ions in gel,
+
+%Then in closed system $\nna$ and $\ncl$ remain constant, whereas the salinity of supernate, $\cs$, may change with the change of the gel volume.
 
@@
 The first box of the volume $\Vgel$ contains the gel with ions, and the second box, $\Vout$--- contains only ions. 
-The total volume of both boxes is kept constant, $\Vbox=V_{\mathrm{gel}}+V_{\mathrm{out}}$, so the compression of the gel implies the decrease $\Vgel$ and increase $\Vout$.
+The total volume of both boxes is kept constant, $\Vbox=V_{\mathrm{gel}}+V_{\mathrm{out}}$, so the compression of the gel implies the decreasing $\Vgel$ and increasing $\Vout$.
 These two boxes are represented in \reffig{fig:diamond}.
@@
 These states shift towards smaller volumes with increase of salinity. 
-It is seen, that the increase of salinity shifts the free swelling equilibrium towards smaller volumes. 
-In general, the increase of salinity shift all the $\Pgel(V)$ curves towards smaller volumes
-
+In general, the increase of salinity shift all the $\Pgel(V)$ curves towards smaller volumes.
 This effect is well known and is typical for all branched \emph{strong} polyelectrolytes. 
-It is caused by the decrease of ions osmotic pressure and by a screening of electrostatic interactions \cite{Zhulina2000, Landsgesel2020a}.\footnote{The salinity dependence of the size of \emph{weak} polyelectrolyte gel is in general non-monotonic.
-We discuss this case in \cite{Rud2018}.
-} %
+It is caused by the decrease of ions osmotic pressure and by a screening of electrostatic interactions \cite{Zhulina2000, Landsgesel2020a}.
+\footnote{The salinity dependence of the size of \emph{weak} polyelectrolyte gel is in general non-monotonic. We discuss this case in \cite{Rud2018}.}
 
@@
 \paragraph{Compression in closed system.}
-Each set of simulations in an \emph{open system} defines the free swelling equilibrium states of the gel for each salinity, that is the state where the gel partial pressure equals zero. 
-These states are characterized by the corresponding molar volume of the gel, $\Vgel^0$ and the densities of ions in gel \{$\nna^0$, $\ncl^0$\} 
+Each set of simulations in \emph{open system} defines the free swelling equilibrium states of the gel for each salinity, \ie the state where the gel partial pressure equals zero. 
+These states are characterized by the corresponding molar volume of the gel, $\Vgel^0$ and the amount of ions in gel \{$\Nna^0$, $\Ncl^0$\} 
 (Index ``0'' stands for zero bar applied pressure).
 We use the free swelling equilibrium states as the starting ones for the gel compression in \emph{closed system}. 
-Thus, we simulate the compression of the gel in the closed volume, $\Vbox$, which is equal to $\Vgel^0$, and contains $\ncl^0$ of $\cl$ ions and the $\na$ ions in the amount neutralizing the system,$\ncl^0$.
+Thus, we simulate the compression of the gel in a closed volume, $\Vbox$, which is equal to $\Vgel^0$, and contains $\Ncl^0$ of $\cl$ ions and the $\na$ ions in the amount neutralizing the system, $\Nna^0 = $$\Ncl^0 + \Ngel$.
 
@@
 
-The process of the gel compression in the \emph{closed} system is depicted in Figure~\ref{fig: PV} (dotted lines) as the dependence of gel partial pressure versus the gel molar volume.
+The processes of the gel compression in \emph{closed} system are depicted in Figure~\ref{fig: PV} as dotted lines.
 In this plot, the blue dotted line, for example, illustrates the compression of the gel equilibrated with the solution of salinity $\cs=0.063$ mol/l, in a volume which gel has at zero pressure. 
 Since, in this case, the volumes of the gel $\Vgel$ and of the supernate $\Vout$ are comparable, the compression of the gel affects the salinity of supernate, $\cs$. 
-The supernate salinity now decreases, changing from $\cs^{0}=0.063$ at the free swelling equilibrium state to $\cs^{5}=0.045$ mol/l in the state with applied pressure $P\gel=5$ bar (index ``5'' stands for 5 bar).
+The supernate salinity now decreases with compression.
+This decrease is illustrated \reffig{fig: CV}, where the same swelling/compression processes are displayed in different coordinates: \ie salinity of supernate versus the gel molar volume, $\cs(\Vgel)$.
+In these coordinates, all the open system compressions show up as horizontal lines, which reflects the constant salinity, whereas the compressions in closed system demonstrate the change of $\cs$ from $\cs^{0}=0.063$ at zero pressure $\Pgel$ to $\cs^{5}=0.045$ mol/l at $P\gel=5$ bar (index ``5'' stands for 5 bar).
 
-The \reffig{fig: CV} illustrates the same swelling/compression processes, but in different coordinates: \ie salinity of supernate versus the gel molar volume, $\cs(\Vgel)$.
-In these coordinates, all the open system compressions show up as horizontal lines, which reflects the constant salinity, whereas the compressions in the closed system demonstrate the decrease of $\cs$.
-
-Although the salinity during compression in \emph{open} system remains constant, the number of ions in a compression volume, i.e. in the volume where the gel is compressed (or swells), changes.
-As the compression volume $\Vbox$ we chose the volume of the free swelling equilibrium state of the gel, $\Vbox = \Vgel^0$.
+Although the salinity during compression in \emph{open} system remains constant, the number of ions in a compression volume, \ie in the volume where the gel is compressed (or swells), changes.
+%As the compression volume $\Vbox$ we chose the volume of the free swelling equilibrium state of the gel, $\Vbox = \Vgel^0$.
 In the Figure \ref{fig: NV} we depicted the number of $\cl$ ions in the volume $\Vbox$, calculated per unit volume, $\ncl =$ $\Ncl/\Vbox$, as a function of the gel molar volume. 

### 2022-07-05 gibbs.tex
added W_sim to the table

@@
 \end{equation}
-where $i \in \{\na, \cl\}$,  $N_i$ is the amount of the corresponding ions in gel,
+where $i \in \{\na, \cl\}$,  $N_i$ is the amount of the corresponding ions in gel, $\Vgel$~--- volume of the gel, $\Vbox$~--- the volume in which the gel is compressed.
+As $\Vbox$ we choose the volume of the gel in the free swelling equilibrium state.
 
@@
 The similar scheme we use to simulate the gel in closed system. 
-The procedure represents a chain of subsequent MD and MC simulation, but now the molecular dynamics is runing in two simulation boxes simultaneously.
+The procedure represents a chain of subsequent MD and MC simulation, but now the molecular dynamics is running in two simulation boxes simultaneously.
 The first box of the volume $\Vgel$ contains the gel with ions, and the second box, $\Vout$--- contains only ions. 
@@
 \paragraph{Algorithm.}
-The thermodynamic equilibrium between the two volumes implies the exchange of the ion pairs between them, which is done by means of MC procedure in a way similar to described in \cite{Panagiotopoulos1988b}.
+The thermodynamic equilibrium between the two volumes implies the exchange of ion pairs between them, which is done by means of MC procedure in a way similar to described in \cite{Panagiotopoulos1988b}.
 The simulation algorithm is following:
 \begin{enumerate}
-\item Simulate molecular dynamics in both boxes; collect the observables, for examples, values of pressure $P$, to an array; 
-\item Perform Monte-Carlo procedure simulating ion pair exchange; collect the arrays of observables samples: number of ions in both boxes, $\nna\gel$,
-$\ncl\gel$, $\nna\out$ and $\ncl\out$ ; 
+\item Simulate molecular dynamics in both boxes; collect the observables, for example, values of pressure $P$, to an array; 
+\item Perform Monte-Carlo procedure simulating ion pair exchange; collect the arrays of observables samples: number of ions in both boxes, 
+%$\nna\gel$,
+$\Ncl\gel$ 
+%$\nna\out$ 
+and $\Ncl\out$ ; 
 \item Repeat the procedure until the desired length of sample arrays is reached.
@@
 
-The dependencies of $\Pgel$ on the gel molar volume $\Vgel$ are present in Figure \ref{fig: PV} for a set of different salinities. 
+The dependencies of $\Pgel$ on the gel molar volume $\Vgel$ are present in Figure \ref{fig: PV} for a set of different salinities. \todo{consider treplacing $\Pgel$ by $\Pi$}
 These dependencies (the case of \emph{open system}) are represented by solid lines. 
@@
 \paragraph{Compression in closed system.}
-Each set of simulations in \emph{open system} defines the free swelling equilibrium states of the gel for each salinity, \ie the state where the gel partial pressure equals zero. 
-These states are characterized by the corresponding molar volume of the gel, $\Vgel^0$ and the amount of ions in gel \{$\Nna^0$, $\Ncl^0$\} 
+%Each set of simulations in \emph{open system} defines the free swelling equilibrium states of the gel for each salinity, \ie the state where the gel partial pressure equals zero. 
+The free swelling equilibrium states are characterized by the corresponding molar volume of the gel, $\Vgel^0$ and the amount of ions in gel \{$\Nna^0$, $\Ncl^0$\} 
 (Index ``0'' stands for zero bar applied pressure).
-We use the free swelling equilibrium states as the starting ones for the gel compression in \emph{closed system}. 
+We use these states as the starting ones for the gel compression in \emph{closed system}. 
 Thus, we simulate the compression of the gel in a closed volume, $\Vbox$, which is equal to $\Vgel^0$, and contains $\Ncl^0$ of $\cl$ ions and the $\na$ ions in the amount neutralizing the system, $\Nna^0 = $$\Ncl^0 + \Ngel$.
@@
 In this plot, the blue dotted line, for example, illustrates the compression of the gel equilibrated with the solution of salinity $\cs=0.063$ mol/l, in a volume which gel has at zero pressure. 
-Since, in this case, the volumes of the gel $\Vgel$ and of the supernate $\Vout$ are comparable, the compression of the gel affects the salinity of supernate, $\cs$. 
-The supernate salinity now decreases with compression.
-This decrease is illustrated \reffig{fig: CV}, where the same swelling/compression processes are displayed in different coordinates: \ie salinity of supernate versus the gel molar volume, $\cs(\Vgel)$.
+Since, in this case, the volumes of the gel $\Vgel$ and of the supernate $\Vout$ are comparable, the compression of the gel decreases the salinity of supernate, $\cs$. 
+%The supernate salinity now decreases with compression.
+This dependence is illustrated \reffig{fig: CV}, where the same swelling/compression processes are displayed in different coordinates: \ie salinity of supernate versus the gel molar volume, $\cs(\Vgel)$.
 In these coordinates, all the open system compressions show up as horizontal lines, which reflects the constant salinity, whereas the compressions in closed system demonstrate the change of $\cs$ from $\cs^{0}=0.063$ at zero pressure $\Pgel$ to $\cs^{5}=0.045$ mol/l at $P\gel=5$ bar (index ``5'' stands for 5 bar).
@@
 In the Figure \ref{fig: NV} we depicted the number of $\cl$ ions in the volume $\Vbox$, calculated per unit volume, $\ncl =$ $\Ncl/\Vbox$, as a function of the gel molar volume. 
-The depicted value can be considered as the density of $\cl$ ions averaged out over the volume $\Vbox$.
+The depicted value can be considered as the density of $\cl$ ions averaged out over the compression volume $\Vbox$.
 
-As it is expected in case of closed system these dependencies look like horizontal lines, whereas in open system, the amount of ions in compression volume increases with compression. 
-This implies, that the compression of the gel in open system pulls out the ions from the bath to the compression volume, $\Vbox$. 
+As expected in the case of closed system compression these dependencies look like horizontal lines, whereas in an open system, the amount of ions in compression volume increases with compression. 
+This implies, that the compression of the gel in the open system pulls out the ions from the bath to the compression volume, $\Vbox$. 
 And vice versa, the swelling of the gel pushes ions out to the bath.
@@
 After swelling, the gel is compressed again by the pressure of 5 bar in \emph{closed} system (dashed light blue line).  
-Then it is put swelling in a reservoir of even smaller salinity ($\cs=0.045$ mol/l, solid yellow line). 
+Then the gel is put swelling in a reservoir of even smaller salinity ($\cs=0.045$ mol/l, solid yellow line). 
 And so on. 
@@
 \paragraph{The efficiency of desalination.}
-The theoretical minimum specific energy for seawater desalination ($\cs=35$ g/l, $\simeq0.6$ mol/l as for pure NaCl) is 1.1 kWh/m3 (3.9 kJ/L) for 50\% recovery \cite{Wang_2020}.
+The theoretical minimum specific energy for seawater desalination (
+%$\cs=35$ g/l, 
+$\cs\simeq0.6$ mol/l as for pure NaCl) is $\sim3.9$ kJ/l (1.1 kWh/m$^3$) for 50\% recovery \cite{Wang_2020}.
 This value is calculated as follows 
@@
 
-In order to compare the efficiency of the process presented in \ref{fig: PV and CV} and \ref{fig: NV and CN} with provided values we collect the corresponding data to the Table~\ref{tab: table}.
+In order to compare the efficiency of the process presented in \ref{fig: PV and CV} and \ref{fig: NV and CN} with provided values, we collect the corresponding data to the Table~\ref{tab: table}.
 The presented desalination process is a cascade of six swellings in open system, at six different (constant) salinities $\cs$, each followed by six compressions in closed system, at six different (constant) $\ncl$.
-Each swelling and compression presented as a row of the Table~\ref{tab: table}, which is collored to matching to the lines on Figures.
-The first column of the table contains values $\cs^0$ and $\cs^5$, which stand for the supernatant salinity at 0 and 5 bar compression; in open system supernatant salinity does not change, so $\cs^0$ and $\cs^5$ are presented by a single number.
-The second column contains values of $n^0$ and $n^5$, which stand for the number of $\cl$ ions in compression volume at 0 and 5 bar pressure.
-\todo[fancyline]{it is not a number but a number in unit volume}
-The number of ion does not change in closed system compression, thus $n^0$ and $n^5$ are the same in corresponding row.
-The fourth column shows the change of the volume in corresponding process, $\Delta v$. 
-The fifth column contain the work needed for the compression in the corresponding process, calculated per volume of extracted solution. 
-This value is calculated as integral of corresponding $\Pgel(\Vgel)$ dependence
+Each swelling and compression process is presented as a row of Table~\ref{tab: table}, which is colored by matching the lines in the Figures.
+The first column of the table contains values $\cs^0$ and $\cs^5$, which stand for the supernate salinity at 0 and 5 bar compression; in open system, supernate salinity does not change, so $\cs^0$ and $\cs^5$ are presented by a single number.
+The second column contains values of $n^0$ and $n^5$, which stand for the number of $\cl$ ions in compression volume $\Vbox$, at 0 and 5 bar pressure (divided by $\Vbox$). 
+The number of ion does not change in closed system compression, thus $n^0$ and $n^5$ are the same in the corresponding rows.
+The third column shows the change of the gel volume in corresponding process, $\Delta v$. 
+The fourth column contain the work needed for the compression in the corresponding process, calculated per volume of extracted solution. 
+This value is an integral of corresponding $\Pgel(\Vgel)$ dependence
 \begin{equation}
@@
 \end{equation}
-Here, in the table we present the absolute value, whereas one should keep in mind that the compression implies the work which is done by external force, whereas the swelling implies the work which is done by gel.
-\todo{may be we return back the 'minuses' to the W values}
+Here, in the table, we present the absolute values of the work, whereas one should keep in mind that the compression implies the work is done by external force and the swelling implies that the work is done by gel.
 
 \begin{table}
-\begin{tabular*}{1\textwidth}{@{\extracolsep{\fill}}ll|lc|c|l|l|ll}
-\multicolumn{1}{l|}{$c_{s}^{0}$, mM} & $c_{s}^{5}$, mM & \multicolumn{1}{l|}{$n_{\cl}^{0}$, mM} & $n_{\cl}^{5}$, mM & $\Delta v$, l & $R_{w}$ & $|W$\textbar , J/L & \multicolumn{2}{c}{$W^{id}$, J/L}\tabularnewline
+\begin{tabular*}{1\textwidth}{@{\extracolsep{\fill}}ll|lc|c|l|ll}
+\multicolumn{1}{l|}{$c_{s}^{0}$, mM} & $c_{s}^{5}$, mM & \multicolumn{1}{l|}{$n_{\cl}^{0}$, mM} & $n_{\cl}^{5}$, mM & $\Delta v$, l & $|W$\textbar , J/L & \multicolumn{2}{c}{$W^{id}$, J/L}\tabularnewline
 \hline 
 \hline 
-\multirow{2}{*}{{\small{}$91.47$}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{{\small{}$57.08\pm0.122\enskip\longrightarrow$}} & \multirow{2}{*}{{\small{}2.74}} & \multirow{2}{*}{} & \multirow{2}{*}{{\small{}$95.4\pm1.86$}} &  & \multirow{2}{*}{}\tabularnewline
- &  & \multicolumn{2}{r|}{{\small{}$71.75\pm0.024$}} &  &  &  & \multirow{8}{*}{{\small{}\hspace{-1em}}\textcolor{teal}{\small{}$\left.\begin{array}{l}
+\multirow{2}{*}{{\small{}$91.47$}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{{\small{}$57.08\pm0.122\enskip\longrightarrow$}} & \multirow{2}{*}{{\small{}2.74}} & \multirow{2}{*}{{\small{}$95.4\pm1.86$}} &  & \multirow{2}{*}{}\tabularnewline
+ &  & \multicolumn{2}{r|}{{\small{}$71.75\pm0.024$}} &  &  & \multirow{8}{*}{{\small{}\hspace{-1em}}\textcolor{teal}{\small{}$\left.\begin{array}{l}
 \\
@@
 \\
-\end{array}\right\rbrace $$\rotatebox{90}{\hspace{-3.8em}\ensuremath{\begin{array}{cc}
-W^{id}= & (52.9)\\
+\\
+\end{array}\right\rbrace $$\rotatebox{90}{\hspace{-5em}{\color{teal}\ensuremath{\begin{array}{cc}
+W^{\mathrm{sim}}= & 202.8\pm3.23\\
+W^{id}= & 52.9\\
 R_{w}= & 0.54
-\end{array}}}$}} & \tabularnewline
-\cline{1-7} \cline{2-7} \cline{3-7} \cline{4-7} \cline{5-7} \cline{6-7} \cline{7-7} 
-\multicolumn{2}{l|}{{\small{}$89.41\pm0.229\enskip\longrightarrow$}} & \multirow{2}{*}{{\small{}56.90}} & \multirow{2}{*}{} & \multirow{2}{*}{{\small{}2.72}} & \multirow{2}{*}{} & \multirow{2}{*}{{\small{}$109.1\pm1.72$}} &  & \multirow{2}{*}{}\tabularnewline
-\multicolumn{2}{r|}{{\small{}$73.63\pm0.03$}} &  &  &  &  &  &  & \tabularnewline
-\cline{1-7} \cline{2-7} \cline{3-7} \cline{4-7} \cline{5-7} \cline{6-7} \cline{7-7} 
-\multirow{2}{*}{\textcolor{teal}{\small{}63.93}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{teal}{\small{}$37.28\pm0.083\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{teal}{\small{}3.26}} & \multirow{2}{*}{\textcolor{teal}{\small{}0.54}} & \multirow{2}{*}{\textcolor{teal}{\small{}$100.9\pm1.69$}} &  & \tabularnewline
- &  & \multicolumn{2}{r|}{\textcolor{teal}{\small{}$50.58\pm0.013$}} &  &  &  &  & \multirow{8}{*}{{\small{}\hspace{-1em}}\textcolor{olive}{\small{}$\left.\begin{array}{l}
+\end{array}}}}$}} & \tabularnewline
+\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
+\multicolumn{2}{l|}{{\small{}$89.41\pm0.229\enskip\longrightarrow$}} & \multirow{2}{*}{{\small{}56.90}} & \multirow{2}{*}{} & \multirow{2}{*}{{\small{}2.72}} & \multirow{2}{*}{{\small{}$109.1\pm1.72$}} &  & \multirow{2}{*}{}\tabularnewline
+\multicolumn{2}{r|}{{\small{}$73.63\pm0.03$}} &  &  &  &  &  & \tabularnewline
+\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
+\multirow{2}{*}{\textcolor{teal}{\small{}63.93}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{teal}{\small{}$37.28\pm0.083\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{teal}{\small{}3.26}} & \multirow{2}{*}{\textcolor{teal}{\small{}$100.9\pm1.69$}} &  & \tabularnewline
+ &  & \multicolumn{2}{r|}{\textcolor{teal}{\small{}$50.58\pm0.013$}} &  &  &  & \multirow{8}{*}{{\small{}\hspace{-1em}}\textcolor{olive}{\small{}$\left.\begin{array}{l}
 \\
@@
 \\
-\end{array}\right\rbrace $$\rotatebox{90}{\hspace{-3.8em}\ensuremath{\begin{array}{cc}
+\\
+\end{array}\right\rbrace $$\rotatebox{90}{\hspace{-5em}\ensuremath{\begin{array}{cc}
+W^{\mathrm{sim}}= & 207.3\pm2.19\\
 W^{id}= & 38.2\\
@@
 \end{array}}}$}}\tabularnewline
-\cline{1-7} \cline{2-7} \cline{3-7} \cline{4-7} \cline{5-7} \cline{6-7} \cline{7-7} 
-\multicolumn{2}{l|}{\textcolor{teal}{\small{}$62.05\pm0.15\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{teal}{\small{}37.17}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{teal}{\small{}3.18}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{teal}{\small{}$107.4\pm1.37$}} &  & \tabularnewline
-\multicolumn{2}{r|}{\textcolor{teal}{\small{}$48.21\pm0.016$}} &  &  &  &  &  &  & \tabularnewline
-\cline{1-7} \cline{2-7} \cline{3-7} \cline{4-7} \cline{5-7} \cline{6-7} \cline{7-7} 
-\multirow{2}{*}{\textcolor{olive}{\small{}44.91}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{olive}{\small{}$23.75\pm0.057\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{olive}{\small{}3.82}} & \multirow{2}{*}{\textcolor{olive}{\small{}0.53}} & \multirow{2}{*}{\textcolor{olive}{\small{}$106.7\pm1.51$}} &  & \tabularnewline
- &  & \multicolumn{2}{r|}{\textcolor{olive}{\small{}$35.91\pm0.010$}} &  &  &  & \multirow{8}{*}{{\small{}\hspace{-1em}}\textcolor{red}{\small{}$\left.\begin{array}{l}
+\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
+\multicolumn{2}{l|}{\textcolor{teal}{\small{}$62.05\pm0.15\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{teal}{\small{}37.17}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{teal}{\small{}3.18}} & \multirow{2}{*}{\textcolor{teal}{\small{}$107.4\pm1.37$}} &  & \tabularnewline
+\multicolumn{2}{r|}{\textcolor{teal}{\small{}$48.21\pm0.016$}} &  &  &  &  &  & \tabularnewline
+\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
+\multirow{2}{*}{\textcolor{olive}{\small{}44.91}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{olive}{\small{}$23.75\pm0.057\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{olive}{\small{}3.82}} & \multirow{2}{*}{\textcolor{olive}{\small{}$106.7\pm1.51$}} &  & \tabularnewline
+ &  & \multicolumn{2}{r|}{\textcolor{olive}{\small{}$35.91\pm0.010$}} &  &  & \multirow{8}{*}{{\small{}\hspace{-1em}}\textcolor{red}{\small{}$\left.\begin{array}{l}
 \\
@@
 \\
-\end{array}\right\rbrace \rotatebox{90}{\hspace{-3.8em}\ensuremath{\begin{array}{cc}
-W^{id}= & 43.8\ {\color{red}{\scriptstyle (41.0)}}\\
+\\
+\\
+\end{array}\right\rbrace \rotatebox{90}{\hspace{-5em}\ensuremath{\begin{array}{cc}
+W^{\mathrm{sim}}= & 222.3\pm2.43\\
+W^{\mathrm{id}}= & 43.8\ {\color{red}{\scriptstyle (41.0)}}\\
 R_{w}= & 0.52\ {\scriptstyle (0.46)}
 \end{array}}}$}} & \tabularnewline
-\cline{1-7} \cline{2-7} \cline{3-7} \cline{4-7} \cline{5-7} \cline{6-7} \cline{7-7} 
-\multicolumn{2}{l|}{\textcolor{olive}{\small{}$43.46\pm0.12\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{olive}{\small{}24.27}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{olive}{\small{}3.91}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{olive}{\small{}$106.4\pm1.13$}} &  & \tabularnewline
-\multicolumn{2}{r|}{\textcolor{olive}{\small{}$30.80\pm0.008$}} &  &  &  &  &  &  & \tabularnewline
-\cline{1-7} \cline{2-7} \cline{3-7} \cline{4-7} \cline{5-7} \cline{6-7} \cline{7-7} 
-\multirow{2}{*}{\textcolor{red}{\small{}31.93}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{red}{\small{}$14.66\pm0.037\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{red}{\small{}4.20}} & \multirow{2}{*}{\textcolor{red}{\small{}0.52}} & \multirow{2}{*}{\textcolor{red}{\small{}$107.9\pm1.42$}} &  & \tabularnewline
- &  & \multicolumn{2}{r|}{\textcolor{red}{\small{}$25.30\pm0.006$}} &  &  &  &  & \multirow{8}{*}{{\small{}\hspace{-1em}}\textcolor{orange}{\small{}$\left.\begin{array}{l}
+\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
+\multicolumn{2}{l|}{\textcolor{olive}{\small{}$43.46\pm0.12\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{olive}{\small{}24.27}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{olive}{\small{}3.91}} & \multirow{2}{*}{\textcolor{olive}{\small{}$106.4\pm1.13$}} &  & \tabularnewline
+\multicolumn{2}{r|}{\textcolor{olive}{\small{}$30.80\pm0.008$}} &  &  &  &  &  & \tabularnewline
+\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
+\multirow{2}{*}{\textcolor{red}{\small{}31.93}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{red}{\small{}$14.66\pm0.037\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{red}{\small{}4.20}} & \multirow{2}{*}{\textcolor{red}{\small{}$107.9\pm1.42$}} &  & \tabularnewline
+ &  & \multicolumn{2}{r|}{\textcolor{red}{\small{}$25.30\pm0.006$}} &  &  &  & \multirow{8}{*}{{\small{}\hspace{-1em}}\textcolor{orange}{\small{}$\left.\begin{array}{l}
 \\
@@
 \\
-\end{array}\right\rbrace \rotatebox{90}{\hspace{-3.8em}\ensuremath{\begin{array}{cc}
+\\
+\\
+\end{array}\right\rbrace \rotatebox{90}{\hspace{-5em}\ensuremath{\begin{array}{cc}
+W^{\mathrm{sim}}= & 218.7\pm2.19\\
 W^{id}= & 66.6\ {\scriptstyle (22.0)}\\
@@
 \end{array}}}$}}\tabularnewline
-\cline{1-7} \cline{2-7} \cline{3-7} \cline{4-7} \cline{5-7} \cline{6-7} \cline{7-7} 
+\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
 \multicolumn{2}{l|}{\textcolor{red}{\small{}$30.03\pm0.084\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{red}{\small{}14.55}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{red}{\small{}$\begin{array}{c}
@@
 {\scriptstyle (3.22)}
-\end{array}$}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{red}{\small{}$\begin{array}{c}
+\end{array}$}} & \multirow{2}{*}{\textcolor{red}{\small{}$\begin{array}{c}
 115.6\pm0.92\\
@@
 {\scriptstyle (22.32)}
-\end{array}$}} &  &  &  &  &  &  & \tabularnewline
-\cline{1-7} \cline{2-7} \cline{3-7} \cline{4-7} \cline{5-7} \cline{6-7} \cline{7-7} 
+\end{array}$}} &  &  &  &  &  & \tabularnewline
+\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
 \multirow{2}{*}{\textcolor{orange}{\small{}22.30}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{orange}{\small{}$8.84\pm0.026\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{orange}{\small{}$\begin{array}{c}
@@
 {\scriptstyle (3.76)}
-\end{array}$}} & \multirow{2}{*}{\textcolor{orange}{\small{}0.53}} & \multirow{2}{*}{\textcolor{orange}{\small{}$\begin{array}{c}
+\end{array}$}} & \multirow{2}{*}{\textcolor{orange}{\small{}$\begin{array}{c}
 108.1\pm1.26\\
@@
 {\scriptstyle (14.56)}
-\end{array}$}} &  &  &  & \multirow{7}{*}{{\small{}\hspace{-1em}}\textcolor{magenta}{\small{}$\left.\begin{array}{l}
+\end{array}$}} &  &  & \multirow{7}{*}{{\small{}\hspace{-1em}}\textcolor{magenta}{\small{}$\left.\begin{array}{l}
 \\
@@
 \\
-\end{array}\right\rbrace \rotatebox{90}{\hspace{-3em}\ensuremath{\begin{array}{cc}
+\\
+\end{array}\right\rbrace \rotatebox{90}{\hspace{-5em}\ensuremath{\begin{array}{cc}
+W^{\mathrm{sim}}= & 227.5\pm2.23\\
 W^{id}= & 69.7\\
@@
 \end{array}}}$}} & \tabularnewline
-\cline{1-7} \cline{2-7} \cline{3-7} \cline{4-7} \cline{5-7} \cline{6-7} \cline{7-7} 
-\multicolumn{2}{l|}{\textcolor{orange}{\small{}$20.74\pm0.064\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{orange}{\small{}8.83}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{orange}{\small{}$4.71$}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{orange}{\small{}$110.8\pm0.77$}} &  & \tabularnewline
-\multicolumn{2}{r|}{\textcolor{orange}{\small{}$11.08\pm0.002$}} &  &  &  &  &  &  & \tabularnewline
-\cline{1-7} \cline{2-7} \cline{3-7} \cline{4-7} \cline{5-7} \cline{6-7} \cline{7-7} 
-\multirow{2}{*}{\textcolor{magenta}{\small{}10.90}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{magenta}{\small{}$3.00\pm0.01\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{magenta}{\small{}6.08}} & \multirow{2}{*}{\textcolor{magenta}{\small{}0.55}} & \multirow{2}{*}{\textcolor{magenta}{\small{}$106.9\pm1.05$}} &  & \tabularnewline
- &  & \multicolumn{2}{r|}{\textcolor{magenta}{\small{}9.01$\pm$0.002}} &  &  &  &  & \tabularnewline
-\cline{1-7} \cline{2-7} \cline{3-7} \cline{4-7} \cline{5-7} \cline{6-7} \cline{7-7} 
-\multicolumn{2}{l|}{\textcolor{magenta}{\small{}$9.83\pm0.046\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{magenta}{\small{}3.12}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{magenta}{\small{}5.78}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{magenta}{\small{}$119.4\pm0.97$}} &  & \tabularnewline
-\multicolumn{2}{r|}{\textcolor{magenta}{\small{}$3.86\pm0.001$}} &  &  &  &  &  &  & \tabularnewline
+\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
+\multicolumn{2}{l|}{\textcolor{orange}{\small{}$20.74\pm0.064\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{orange}{\small{}8.83}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{orange}{\small{}$4.71$}} & \multirow{2}{*}{\textcolor{orange}{\small{}$110.8\pm0.77$}} &  & \tabularnewline
+\multicolumn{2}{r|}{\textcolor{orange}{\small{}$11.08\pm0.002$}} &  &  &  &  &  & \tabularnewline
+\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
+\multirow{2}{*}{\textcolor{magenta}{\small{}10.90}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{magenta}{\small{}$3.00\pm0.01\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{magenta}{\small{}6.08}} & \multirow{2}{*}{\textcolor{magenta}{\small{}$106.9\pm1.05$}} &  & \tabularnewline
+ &  & \multicolumn{2}{r|}{\textcolor{magenta}{\small{}9.01$\pm$0.002}} &  &  &  & \tabularnewline
+\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
+\multicolumn{2}{l|}{\textcolor{magenta}{\small{}$9.83\pm0.046\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{magenta}{\small{}3.12}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{magenta}{\small{}5.78}} & \multirow{2}{*}{\textcolor{magenta}{\small{}$119.4\pm0.97$}} &  & \tabularnewline
+\multicolumn{2}{r|}{\textcolor{magenta}{\small{}$3.86\pm0.001$}} &  &  &  &  &  & \tabularnewline
 \end{tabular*}
 
-\caption{All the units calculated per one mol of gel segments. Values in brackets
-are the estimates corresponding to crossection of 'red' and 'orange'
-lines on the plots of figures \ref{fig: PV and CV} and \ref{fig: NV and CN}
+\caption{The estimates of the efficiency of the desalination process. All the units are calculated per one mol of gel segments. Values in brackets
+are the estimates corresponding to crossection of 'red' and 'orange' lines on the plots of figures \ref{fig: PV and CV} and \ref{fig: NV and CN}
 }
@@
 
-The fifth column \todo{check if it is fifth column} contains the values of specific energy consumption, $W^\text{id}$, which are calculated as follows.
-We consider, for example, the solution of concentration $\cs^f=0.045$ mol/l as a feed solution, and the solutions of $\cs^p=0.032M$ and $\cs^b = 0.064$ mol/l 
+To give a clue of comparison with ideal desalination process efficiency, in the fifth column we provided the values of specific energy consumption, $W^\text{id}$, which are calculated by means of \refeq{eq:SEC} as follows.
+We consider, for example, the solution of concentration $\cs^f=44.91$ mmol/l as a feed solution, and the solutions of $\cs^p=31.93$ mmol/l and $\cs^b = 63.93$ mmol/l 
 correspondingly as produced product and brine solutions.
@@
     \item first, the gel, equilibrated with feed solution, is getting compressed in a closed system.
-    while compression it changes its volume by $\Delta v^p = 3.69$  l/mol and the salinity of supernate decreases from $\cs^f$ to $\cs^p$.
-    The volume of product solution equals to $\Delta v^p$
-    \item Then the squeezed gel is put back to feed solution and is getting equilibrated there under pressure, so it does not swell. 
-    \item then the squeezed gel is let to swell in closed system such that the salinity of external solution increases reaching the value of $\cs^b$
-    \item finally, the gel is taken out and squeezed by 5 bar in open system in equilibrium with the bath of the brine. 
-    The change of the gel volume in this process is $\Delta v^b = 3.26$ l/mol, which equals to the volume of produced brine. 
+    The volume of the gel changes by $\Delta v^p = 3.69$ l  and the salinity of supernate decreases from $\cs^f$ to $\cs^p$.
+    The volume of product solution equals $\Delta v^p$
+    \item Then the squeezed gel is put back into the feed solution and is getting equilibrated there under pressure, so it does not swell. 
+    \item After equilibration the gel is let to swell in a closed system such that the salinity of the external solution increases reaching the value of $\cs^b$.
+    \item Finally, the gel is taken out and squeezed by 5 bar in an open system in equilibrium with the bath of the brine. 
+    The change of the gel volume in this process is $\Delta v^b = 3.26$ l/mol, which equals the volume of the produced brine. 
 \end{enumerate}
-Thus the recovery ratio $R_w = \Delta v^p / (\Delta v^p + \Delta v^b) \simeq $ 0.53 and the theoretical minimum specific energy of desalination with corresponding $\cs^f$, $\cs^p$ and $\cs^b$ is $W^{id} =$ 38.2 J/l (\refeq{eq:SEC})
+Thus the recovery ratio $R_w = \Delta v^p / (\Delta v^p + \Delta v^b) \simeq $ 0.53 and the theoretical minimum specific energy of desalination with corresponding $\cs^f$, $\cs^p$ and $\cs^b$ is $W^{id} =$ 38.2 J/l (\refeq{eq:SEC}).
 
-\todoi{Start from here next time}
+Such estimations are provided in the fifth column of the table, for five triplets of values $\cs^f$, $\cs^p$, and $\cs^b$.
+$W_{\mathrm{sim}}$ is the energy calculated by integration of $\Pgel(\Vgel)$ dependencies~--- sum of corresponding comressions in closed and open systems, $W_{\mathrm{id}}$~--- the estimate based on the equation \refeq{eq:SEC} and $R_w$~--- is the corresponding recovery ratio.
+Note that calculating the $W_{\mathrm{sim}}$ we accounted for only the work done on the gel during compression, whereas the work done by the gel itself during swelling was not taken into account.
 

### 2022-07-06 gibbs.tex
presubmission version

@@
 \begin{enumerate}
-\item The first is so called \emph{open system}, when the simulation box
-with gel freely exchanges ions with a big amount of aqueous solution
-of certain constant salinity, $\cs$. 
-\item And in \emph{closed system}, when the gel is in equilibrium with a
-finite volume of aqueous solution.
+\item The first is so called \emph{open system}, when the simulation box with gel freely exchanges ions with a big amount of aqueous solution of certain constant salinity, $\cs$. 
+\item And in \emph{closed system}, when the gel is in equilibrium with a finite volume of aqueous solution.
 \end{enumerate}
@@
 Each solid curve corresponds to different salinity of the reservoir $\cs$ (see legend). Shadowed area limit the states with applied pressure below zero and above 5 bar.\label{fig: PV and CV}}
-\todoi{replace $V$ by $\Vgel$ in Figures}
 \end{figure*}
@@
 $\Pout$, in turn, we calculate by running a separate simulation of a reservoir, containing ionic gas in equilibrium with the bath of the same salinity $\cs$. 
-The gel partial pressure, $\Pgel$, is the pressure that needs to be applied to the gel via a solvent permeable filter to compress the gel to a molar-specific volume, $\Vgel$.
+The gel partial pressure, $\Pgel$, is the pressure that needs to be applied to the gel via a solvent permeable filter to compress the gel to a specific molar volume, $\Vgel$. 
+By gel molar volume $\Vgel$ we assume the volume of the gel calculated per on mole of gel monomer units.
 
-The dependencies of $\Pgel$ on the gel molar volume $\Vgel$ are present in Figure \ref{fig: PV} for a set of different salinities. \todo{consider treplacing $\Pgel$ by $\Pi$}
+The dependencies of $\Pgel$ on $\Vgel$ are present in Figure \ref{fig: PV} for a set of different salinities. 
 These dependencies (the case of \emph{open system}) are represented by solid lines. 
@@
 {\includegraphics[width=0.495\textwidth]{figures/fig_NVbox_mu_pub}}
-\caption{The compression of the gel in open system (solid lines) and in closed
-system (dotted lines). Each solid curve corresponds to different salinity
-of the reservoir $\cs$ (see legend). Shadowed area limit the states
-with applied pressure below zero and above 5 bar.\label{fig: NV and CN}}
+\caption{The compression of the gel in \emph{open system} (solid lines) and in \emph{closed system} (dotted lines). 
+Shadowed area limit the states with applied pressure below zero and above 5 bar.
+The values $N_\cl$ are the virtual numbers of present $\cl$ ions in \emph{closed system} simulation boxes.
+\label{fig: NV and CN}}
+
 %\todoi{Replace y-axis labels by $\ncl$}
@@
 %\end{enumerate}
-
-\todo{we could get rid of saying 'gel molar volume' if we state elsewhere that all the values are calculated per one mol of the gel}
 
@@
 Note that calculating the $W_{\mathrm{sim}}$ we accounted for only the work done on the gel during compression, whereas the work done by the gel itself during swelling was not taken into account.
+The ratio between $W_{\mathrm{sim}}$ and $W_{\mathrm{id}}$ ranges from 3.26 to 5.43, which is comparable to that of RO.
 
 \section{Conclusions}
-\begin{enumerate}
-\item We have modeled the compression of the gel in thermodynamic equilibrium
-with the reservoir of limited amount of water.
-\item We have shown that in case of gel made of strong polyelectrolyte,
-the compression always lead to decrease of the surrounding salinity.
-\item We have modeled the process of water desalination combining two processes:
-(1) the swelling of the gel in open system, exchanging ions with big
-reservoir at constant salinity. (2) the compression of the gel in
-closed system, when the gel affect the salinity in surrounding solution.
-\item We estimated the energy needed to produce one liter of water and have
-show that the method at least theoretically may compete with the modern
-technologies used in industry nowadays.
-\end{enumerate}
+We have modeled the compression of the gel in thermodynamic equilibrium with the reservoir of limited amount of water.
+We have shown that in case of gel made of strong polyelectrolyte, the compression always lead to decrease of the surrounding salinity.
+We have modeled the process of water desalination combining two processes: 
+(1) the swelling of the gel in \emph{open} system, exchanging ions with big reservoir at constant salinity. 
+(2) the compression of the gel in \emph{closed} system, when the gel affect the salinity in surrounding solution.
+We estimated the energy needed to produce one liter of water and have show that the method 
+%at least theoretically 
+may compete with the modern technologies used in modern industry.
 
@@
 \newpage
-\listoftodos
+%\listoftodos
 
@@
 
-\begin{table}
-\begin{tabular*}{1\textwidth}{@{\extracolsep{\fill}}ll|lc|c|l|l|ll}
-\multicolumn{1}{l|}{$c_{s}^{0}$, mM} & $c_{s}^{5}$, mM & \multicolumn{1}{l|}{$n_{\cl}^{0}$, mM} & $n_{\cl}^{5}$, mM & $\Delta v$, l & $R_{w}$ & $|W$\textbar , J/L & \multicolumn{2}{c}{$W^{id}$, J/L}\tabularnewline
-\hline 
-\hline 
-\multirow{2}{*}{{\small{}91.466}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{{\small{}$57.083\pm0.1215\quad\longrightarrow$}} & \multirow{2}{*}{{\small{}2.74}} & \multirow{2}{*}{} & \multirow{2}{*}{{\small{}$95.4\pm1.86$}} &  & \multirow{2}{*}{}\tabularnewline
- &  & \multicolumn{2}{r|}{{\small{}$71.751\pm0.024$}} &  &  &  & \multirow{8}{*}{{\small{}\hspace{-1em}}\textcolor{teal}{\small{}$\left.\begin{array}{l}
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\end{array}\right\rbrace $$\rotatebox{90}{\hspace{-3.8em}\ensuremath{\begin{array}{cc}
-W^{id}= & (52.9)\\
-R_{w}= & 0.54
-\end{array}}}$}} & \tabularnewline
-\cline{1-7} \cline{2-7} \cline{3-7} \cline{4-7} \cline{5-7} \cline{6-7} \cline{7-7} 
-\multicolumn{2}{l|}{{\small{}$89.414\pm0.2286\quad\longrightarrow$}} & \multirow{2}{*}{{\small{}56.898}} & \multirow{2}{*}{} & \multirow{2}{*}{{\small{}2.72}} & \multirow{2}{*}{} & \multirow{2}{*}{{\small{}$109.1\pm1.72$}} &  & \multirow{2}{*}{}\tabularnewline
-\multicolumn{2}{r|}{{\small{}$73.633\pm0.029$}} &  &  &  &  &  &  & \tabularnewline
-\cline{1-7} \cline{2-7} \cline{3-7} \cline{4-7} \cline{5-7} \cline{6-7} \cline{7-7} 
-\multirow{2}{*}{\textcolor{teal}{\small{}63.93}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{teal}{\small{}$37.281\pm0.083\quad\longrightarrow$}} & \multirow{2}{*}{\textcolor{teal}{\small{}3.26}} & \multirow{2}{*}{\textcolor{teal}{\small{}0.54}} & \multirow{2}{*}{\textcolor{teal}{\small{}$100.9\pm1.69$}} &  & \tabularnewline
- &  & \multicolumn{2}{r|}{\textcolor{teal}{\small{}$50.579\pm0.0134$}} &  &  &  &  & \multirow{8}{*}{{\small{}\hspace{-1em}}\textcolor{olive}{\small{}$\left.\begin{array}{l}
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\end{array}\right\rbrace $$\rotatebox{90}{\hspace{-3.8em}\ensuremath{\begin{array}{cc}
-W^{id}= & 38.2\\
-R_{w}= & 0.53
-\end{array}}}$}}\tabularnewline
-\cline{1-7} \cline{2-7} \cline{3-7} \cline{4-7} \cline{5-7} \cline{6-7} \cline{7-7} 
-\multicolumn{2}{l|}{\textcolor{teal}{\small{}$62.052\pm0.148\quad\longrightarrow$}} & \multirow{2}{*}{\textcolor{teal}{\small{}37.172}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{teal}{\small{}3.18}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{teal}{\small{}$107.4\pm1.37$}} &  & \tabularnewline
-\multicolumn{2}{r|}{\textcolor{teal}{\small{}$48.206\pm0.0157$}} &  &  &  &  &  &  & \tabularnewline
-\cline{1-7} \cline{2-7} \cline{3-7} \cline{4-7} \cline{5-7} \cline{6-7} \cline{7-7} 
-\multirow{2}{*}{\textcolor{olive}{\small{}44.915}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{olive}{\small{}$23.747\pm0.0572\quad\longrightarrow$}} & \multirow{2}{*}{\textcolor{olive}{\small{}3.82}} & \multirow{2}{*}{\textcolor{olive}{\small{}0.53}} & \multirow{2}{*}{\textcolor{olive}{\small{}$106.7\pm1.51$}} &  & \tabularnewline
- &  & \multicolumn{2}{r|}{\textcolor{olive}{\small{}$35.911\pm0.0101$}} &  &  &  & \multirow{8}{*}{{\small{}\hspace{-1em}}\textcolor{red}{\small{}$\left.\begin{array}{l}
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\end{array}\right\rbrace \rotatebox{90}{\hspace{-3.8em}\ensuremath{\begin{array}{cc}
-W^{id}= & 43.8\ {\color{red}{\scriptstyle (41.0)}}\\
-R_{w}= & 0.52\ {\scriptstyle (0.46)}
-\end{array}}}$}} & \tabularnewline
-\cline{1-7} \cline{2-7} \cline{3-7} \cline{4-7} \cline{5-7} \cline{6-7} \cline{7-7} 
-\multicolumn{2}{l|}{\textcolor{olive}{\small{}$43.463\pm0.116\quad\longrightarrow$}} & \multirow{2}{*}{\textcolor{olive}{\small{}24.272}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{olive}{\small{}3.91}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{olive}{\small{}$106.4\pm1.13$}} &  & \tabularnewline
-\multicolumn{2}{r|}{\textcolor{olive}{\small{}$30.795\pm0.0078$}} &  &  &  &  &  &  & \tabularnewline
-\cline{1-7} \cline{2-7} \cline{3-7} \cline{4-7} \cline{5-7} \cline{6-7} \cline{7-7} 
-\multirow{2}{*}{\textcolor{red}{\small{}31.928}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{red}{\small{}$14.658\pm0.0368\quad\longrightarrow$}} & \multirow{2}{*}{\textcolor{red}{\small{}4.20}} & \multirow{2}{*}{\textcolor{red}{\small{}0.52}} & \multirow{2}{*}{\textcolor{red}{\small{}$107.9\pm1.42$}} &  & \tabularnewline
- &  & \multicolumn{2}{r|}{\textcolor{red}{\small{}$25.297\pm0.0061$}} &  &  &  &  & \multirow{8}{*}{{\small{}\hspace{-1em}}\textcolor{orange}{\small{}$\left.\begin{array}{l}
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\end{array}\right\rbrace \rotatebox{90}{\hspace{-3.8em}\ensuremath{\begin{array}{cc}
-W^{id}= & 66.6\ {\scriptstyle (22.0)}\\
-R_{w}= & 0.53\ {\scriptstyle (0.49)}
-\end{array}}}$}}\tabularnewline
-\cline{1-7} \cline{2-7} \cline{3-7} \cline{4-7} \cline{5-7} \cline{6-7} \cline{7-7} 
-\multicolumn{2}{l|}{\textcolor{red}{\small{}$30.029\pm0.0839\quad\longrightarrow$}} & \multirow{2}{*}{\textcolor{red}{\small{}14.549}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{red}{\small{}$\begin{array}{c}
-4.17\\
-{\scriptstyle (3.22)}
-\end{array}$}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{red}{\small{}$\begin{array}{c}
-115.6\pm0.92\\
-{\scriptstyle (57.3)}
-\end{array}$}} &  & \tabularnewline
-\multicolumn{2}{r|}{\textcolor{red}{\small{}$\begin{array}{c}
-18.585\pm0.0036\,\\
-{\scriptstyle (22.32)}
-\end{array}$}} &  &  &  &  &  &  & \tabularnewline
-\cline{1-7} \cline{2-7} \cline{3-7} \cline{4-7} \cline{5-7} \cline{6-7} \cline{7-7} 
-\multirow{2}{*}{\textcolor{orange}{\small{}22.301}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{orange}{\small{}$8.838\pm0.0262\quad\longrightarrow$}} & \multirow{2}{*}{\textcolor{orange}{\small{}$\begin{array}{c}
-4.75\\
-{\scriptstyle (3.76)}
-\end{array}$}} & \multirow{2}{*}{\textcolor{orange}{\small{}0.53}} & \multirow{2}{*}{\textcolor{orange}{\small{}$\begin{array}{c}
-108.1\pm1.26\\
-{\scriptstyle (68.3)}
-\end{array}$}} &  & \tabularnewline
- &  & \multicolumn{2}{r|}{\textcolor{orange}{\small{}$\begin{array}{c}
-\text{17.945}\pm\text{0.0041}\\
-{\scriptstyle (14.56)}
-\end{array}$}} &  &  &  & \multirow{7}{*}{{\small{}\hspace{-1em}}\textcolor{magenta}{\small{}$\left.\begin{array}{l}
-\\
-\\
-\\
-\\
-\\
-\\
-\end{array}\right\rbrace \rotatebox{90}{\hspace{-3em}\ensuremath{\begin{array}{cc}
-W^{id}= & 69.7\\
-R_{w}= & 0.55
-\end{array}}}$}} & \tabularnewline
-\cline{1-7} \cline{2-7} \cline{3-7} \cline{4-7} \cline{5-7} \cline{6-7} \cline{7-7} 
-\multicolumn{2}{l|}{\textcolor{orange}{\small{}$20.743\pm0.0638\quad\longrightarrow$}} & \multirow{2}{*}{\textcolor{orange}{\small{}8.827}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{orange}{\small{}$4.71$}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{orange}{\small{}$110.8\pm0.77$}} &  & \tabularnewline
-\multicolumn{2}{r|}{\textcolor{orange}{\small{}$11.082\pm0.002$}} &  &  &  &  &  &  & \tabularnewline
-\cline{1-7} \cline{2-7} \cline{3-7} \cline{4-7} \cline{5-7} \cline{6-7} \cline{7-7} 
-\multirow{2}{*}{\textcolor{magenta}{\small{}10.904}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{magenta}{\small{}$3.002\pm0.0098\quad\longrightarrow$}} & \multirow{2}{*}{\textcolor{magenta}{\small{}6.08}} & \multirow{2}{*}{\textcolor{magenta}{\small{}0.55}} & \multirow{2}{*}{\textcolor{magenta}{\small{}$106.9\pm1.05$}} &  & \tabularnewline
- &  & \multicolumn{2}{r|}{\textcolor{magenta}{\small{}9.011$\pm$0.0019}} &  &  &  &  & \tabularnewline
-\cline{1-7} \cline{2-7} \cline{3-7} \cline{4-7} \cline{5-7} \cline{6-7} \cline{7-7} 
-\multicolumn{2}{l|}{\textcolor{magenta}{\small{}$9.834\pm0.0461\quad\longrightarrow$}} & \multirow{2}{*}{\textcolor{magenta}{\small{}3.119}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{magenta}{\small{}5.78}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{magenta}{\small{}$119.4\pm0.97$}} &  & \tabularnewline
-\multicolumn{2}{r|}{\textcolor{magenta}{\small{}$3.862\pm0.0014$}} &  &  &  &  &  &  & \tabularnewline
-\end{tabular*}
-
-\caption{ORIGINAL TABLE (to be removed)
-}
-\end{table}
-
 \end{document}

### 2022-07-07 esi.tex
esi separated

@@
-\documentclass{elsarticle}
-\input{definitions.tex}
-\usepackage[margin=2.5cm]{geometry}% by courtesy of Mico
-\begin{document}
+\newpage
+\section*{Supplementary Information}
+\subsection{Sampling routine}
+Data gained from Molecular Dynamics (MD) and Markov Chain Monte Carlo processes (MD) are highly autocorrelated, thus we can not imply statistic developed for uncorrelated data.
+We have written a small in-house python package to calculate the expected value, the margin of error and effective sample size of correlated data.
 
-\title{Supporting information to the article\\
-\mytitle}
+The goal of the routine is to estimate mean and margins of error for an observable e.g.
+pressure, number of particles, end-to-end distance of a chain for a given confidence level or effective sample size.
 
-%\title{The \PE{} hydrogels as draw agents for desalination of solutions with multivalent ions}
+We also provided the way to limit sampling procedure with some timeout value. Our routine based on [] %[https://www.physik.uni-leipzig.de/~janke/Paper/nic10_423_2002.pdf]
 
-%\tnotetext[t1]{This document is a collaborative effort.}
-%\tnotetext[t2]{The second title footnote which is a longer longer than the first one and with an intention to fill in up more than one line while formatting.}
+There are multiple sampling routines developed for autocorrelated data, i.e. binning analysis, ... %some notes what others do
 
-    \author[cuni,imc]{Oleg V. Rud}
-    \ead{oleg.rud@natur.cuni.cz}
-    \ead[url]{http://www.physchem.cz/}
-    \author[cuni]{Alexander~D.~Kazakov}
-    \author[cuni]{Lucie~Nova}
-    %\author[cuni]{Peter~Kosovan}
-    \author[cuni]{Filip~Uhlik}
+Expected value of the observable $X$ estimated as the mere mean of the sample $\overline{X}$, the same way one would do for uncorrelated data, whilst to estimate margins of error and \emph{effective} sample size $N_{eff}$ we used the next formulae.
+First of all we have to correct sample size to account that data is correlated:
+\begin{eqnarray}
+    N_{eff} = \frac{N}{2\tau}
+    \\
+    \tau  = \frac{1}{2} + \sum_{k=1}^{N} \text{acf} (k) (1-\frac{k}{N})
+\end{eqnarray}
+where $\tau$ is integrated autocorrelation time, $N$ size of autocorrelated data, $\text{acf} (k)$ is autocorrelation function on lag.
 
-\maketitle
+Note that ideally integral of  $\text{acf} (k)$ monotonically approaches some finite value, but due to unavoidable errors in number representation in computer and numeric integration methods it does not hold.
+For that reason instead of $\text{acf} (k)$ integral we use the maximum of its cumulative sum.
 
-\section{Theory behind the simulation\label{sec: theory}}
+Margins of error (MOE) for a given confidence level $\gamma$ and effective sample size $N_{eff}$ is calculated using the next equation:
+\begin{eqnarray}
+    \text{MOE}(\gamma) = \frac{S_{N}}{\sqrt{N_{eff}}} t_{((1+\gamma)/2, N_{eff}-1)}
+\end{eqnarray}
+where $t_{(\alpha, \nu)}$ is percentile function (inverse cumulative distribution function) of Student’s distribution with $\nu$ degrees of freedom for $\alpha$ percentile,
+$S_N$ is standard deviation of the sample.
 
-\reffig{fig:diamond} presents a diamond-like polymer network inserted in a simple cubic simulation box of volume $V_{\mathrm{box}}$ with periodic boundaries.
-The network consists of $16$ linear \PE{} chains, each chain comprising $30$ monomer units.
-Each unit is able to change its ionization state from charged to neutral and vice versa according to the ionization equilibrium.
-The mobile ions ($\na$, $\cl$ and $\ca$) are present in certain amount such that they fulfill the electroneutrality condition.
-
-We model the network in equilibrium with the bulk of aqueous solution.
-In order to keep the equilibrium conditions we consider three processes to occur:
-
-\begin{enumerate}
-	\item the thermal movement of all segments in simulation box (Langevin dynamics);
-	\item the ionization reaction equilibrium of \PE{} segments:
+The true mean of the observable $\mu_X$ lies inside the confidence interval with the confidence level $\gamma$.
 \begin{equation}
-        \mathrm{HA}\leftrightarrows\mathrm{A}^{-}+\h\label{eq: acid reaction}
-    \end{equation}
-    \item the exchange of ion pairs between the gel and the bath (in order to keep electroneutrality of simulation box):
-        \begin{eqnarray}
-            \varnothing&\leftrightarrows&\na+\cl\label{eq: nacl reaction}\\
-            \varnothing&\leftrightarrows&\ca+2\cl\label{eq: cacl reaction}\\
-            %\varnothing&\leftrightarrows&2\na+\so\label{eq: naso reaction}
-        \end{eqnarray}
-%\todoi{We shall get rid of $\so$ ions and mention it in the inroduction. The reason is that their concentration is small, and they do not enter the hydrogel }
-\end{enumerate}
-
-All three processes occur simultaneously in real systems, however, we simulate them alternating each other in stop-run mode in a random order.
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=0.5\columnwidth]{{figures/vmdscene}.pdf}
-    \caption{
-       	Diamond-like network in the simulation box. 
-	Color code represents the individual ion types
-	(red: $\na$, blue: $\cl$, yellow: $\ca$) and
-        the hydrogel (gray: neutral segment ($\AH$), cyan: charged segment ($\A$)).
-    }
-    \label{fig:diamond}
-    %in order to make snapshot use file snapshot.py
-    % in order to edit the existing snapshot use file data/gel_MPC30_box_l53.0_pK7.00_pH7.00_pCl2.00_pCa2.94_lB0.0.vmd
-\end{figure}
-
-\subsection{Langevin dynamics\label{MD}}
-
-We use three types of interactions, \ie bonded interactions, short-range non-bonded interactions and electrostatic interactions.
-
-We use Finite extension nonlinear elastic (FENE) potential~\refeq{eq:fene} to account for the bonding interactions.
-%The potential accounts for nonlinear elastic extensions and as a consequence, the simulation is not constrained too much.
-\begin{equation}\label{eq:fene}
-    V_\mathrm{FENE}(r) = -\frac{1}{2} K \Delta r_\mathrm{max}^2\ln \left[ 1 - \left(\frac{r-r_0}{\Delta r_\mathrm{max}} \right)^2 \right ],
-\end{equation}
-where $K$ is the magnitude of symmetric interaction between two segments,
-$\Delta r_{\mathrm{max}}$ is the maximal stretching length of the bond and $r_0$ is the equilibrium bond length.
-In our simulations we set $K = 10 \kT/\sigma^{2}$, $\Delta r_{\mathrm{max}} = 2 \sigma$ and $r_0 = 1.0\sigma$~\cite{Jin2007}.
-
-We model the non-bonded interactions using truncated Lennard-Jones interaction potential.
-This potential imposes strong repulsion between all particles at short distances:
-\begin{equation}
-    \begin{split}\label{eq:LJ}
-        V_\mathrm{LJ}(r) =
-        \begin{cases}
-            4 \varepsilon \left( \left(\cfrac{\sigma}{r}\right)^{12}
-            - \left(\cfrac{\sigma}{r}\right)^6\right)
-            & \mathrm{if~} r < r_\mathrm{cut}\\
-            0
-            & \mathrm{elsewhere}
-        \end{cases},
-    \end{split}
-\end{equation}
-where $r$ is the interparticle distance,
-$\sigma = 0.35 \mathrm{nm}$ is the characteristic size of the particles,
-$\varepsilon$ is the depth of the potential well in $\kT$ units and $r_\mathrm{cut}$ is the cut-off distance beyond which the potential is set zero.
-
-We model the long range electrostatic interactions by the Coulomb potential:
-\begin{equation}
-    V_{\mathrm{EL}}=\lb\kT \cfrac{q_{1}q_{2}}{r},
-\end{equation}
-where $\lb$ is Bjerrum length. We set $\lb = 2\sigma = 0.7 \mathrm{nm}$ which corresponds to water at $T=300 \mathrm{K}$.
-
-We use Langevin thermostat, \ie
-we add two additional terms to force in equation of motion
-\begin{equation}
-f_i =  -\gamma v_i(t)+\sqrt{2\gamma \kT }\eta_i(t),
-\end{equation}
-where the first term correspond to constant friction with $\gamma$ being a friction coefficient, and the second one corresponds to random thermal force with $\eta_i$ being a normally distributed random number (see for details \cite{Grest1986}).
-
-%where $\gamma$ is the friction coefficient and .
-%\todo{there is friction and there is random force ballanced by fluctiation dissipation theorem so that it is stationary}
-%which causes the decrease of the particles' velocities.
-%This is implemented by addition of two corresponding terms to the particles' equations of motion, namely
-%\todo{usually -gamma v to keep gamma>0}
-%where the first term correspond to
-
-%\paragraph{Units} % apart from cref reference all references are in the text. Do we need cref?
-%By setting up the interaction potentials we defined the system of units.
-%We have chosen the unit of length being based on the Bjerrum length in water at room temperature, $l_B \simeq 7$nm, and $\sigma=0.5l_B = 0.35$.
-% % %Then the unit of concentration is $\cref=(\sigma^{3}\NA1000)^{-1}$mol/l. % % % do we need to say that?
-%We set the energy unit to be $\varepsilon = \kT$.
-
-\subsection{Sampling in the Gibbs ensemble\label{sec: sampling the gibbs ensemble}}
-All thermal moves are frozen during the sampling of the ion pairs exchange.
-The system represents the ensemble with constant number of particles distributed between two vessels (I) and (II).
-
-In the following paragraph we derive the criteria for sampling of the ion exchange equilibrium.
-\paragraph{Gibbs canonical ensemble}
-Let us first consider the total free energy of both vesselsassuming that we have only particles of a single type:
-\begin{equation}
-    F=\left(E_{I}-TS_{I}\right) + \left(E_{II}-TS_{II}\right) \label{eq:F-gibbs}
-\end{equation}
-where $E$ is internal energy, $T$~--- temperature, $S$~--- entropy.
-
-%Our model system represents a finite volume $V$ which exchanges particles with the bath of infinite volume.
-%The infinity of the volume means, that the particle exchange between the system and the bath does not influence on the chemical potentials in the bath.
-%Such ensemble is called grand canonical ensemble; the free energy in this ensemble, the Landau potential, is
-The entropy $S$ is given by the Boltzmann formula~\cite{Nagle2004}:
-\begin{equation}
-    S=\kB\ln\frac{V^{N}}{N!}\label{eq:entropy}
-\end{equation}
-%\todo{for partiles without interactions}
-where $N$ is a number of particles in corresponding vessel.
-This formula accounts for two contributions:
-\begin{enumerate}
-    \item the combinatorial entropy $S_{c}=-\kB\ln N!$ which reflects the freedom of choice among $N$ particles
-    \item the mixing entropy $S_{m}=\kB N\ln V$ which reflects the freedom to place the chosen particle randomly within the simulation box. 
-\end{enumerate}
-$V$ is the unitless volume, \ie the volume measured in units of $\sigma^3$. 
-Thus \refeq{eq:F-gibbs} turns to 
-%\todo{this is not reason, moreover A.10 is already wrong as for units}
-\begin{equation}
-    F=\EI-\kT\ln\frac{\VI^{\NI}}{\NI!}\ + \ \EII-\kT\ln\frac{\VII ^{\NII}}{{\NII} !}
-\label{eq: F_gibbs}
-\end{equation}
-When a single particle transferred from the vessel (I) to the  vessel (II) the free energy in vessel (I) changes 
-\begin{equation}
-\Delta \FI = \Delta \EI+\kT\ln\frac{\VI^{\NI}}{\NI !} - \kT\ln\frac{\VI^{\NI-1}}{(\NI-1)!}=\Delta \EI + \kT\ln\frac{\VI}{\NI}
-\end{equation}
-whwereas the free energy change in (II) vessel is
-\begin{equation}
-\Delta \FII = \Delta \EII+\kT\ln\frac{\VII^{\NII}}{\NII !} - \kT\ln\frac{\VII^{\NII+1}}{(\NII+1)!}=\Delta \EII + \kT\ln\frac{\NII+1}{\VII}
-\end{equation}
-Thus the total change of free energy will be 
-\begin{equation}
-\Delta F = \Delta \EI+\Delta \EII+\kT\ln\frac{\VI}{\VII}\frac{\NII+1}{\NI}
-\end{equation}
-The change of free energy associated with a transfer of a single particle from vessel (I) to vessel (II)  is
-\begin{equation}
-    \Delta\Omega=\kT\ln\left(V^{\xi}\frac{N!}{\left(N+\xi\right)!}\right)+\Delta \EI+\Delta \EII
-\label{eq: DeltaG GC}
-\end{equation}
-where $\xi=+1$ stands for insertion of a particle and $\xi=-1$ for deletion.
-
-In order to simulate an ensemble which exchanges particles with the bath (bulk reservoir) we need to perform the following Monte Carlo procedure \cite{Frenlkel2002_book}
-\begin{enumerate}
-	\item we propose the new configuration of the system by insertion (or deletion) of a particle so that the total number of particles changes from $N$ to $N+\xi$, $\xi=\pm1$
-	\item we accept the new configuration if
-	\begin{equation}
-        \mathcal{R}^{\xi}<e^{\Delta\Omega/\kT}=V^{\xi}\frac{N!}{(N+\xi)!}e^{\left(\Delta E+\xi\mu\right)/\kT}\label{eq: GC acceptance}
-	\end{equation}
-\end{enumerate}
-where $\mathcal{R}$ is uniformly distributed random number in range between $0$ and $1$.
-
-\paragraph{Sampling the ionization equilibrium}
-We model the ionization equilibrium by means of sampling the reaction ensemble~\cite{Smith1994, Turner2008a}.
-In the reaction ensemble we perform chemical reactions as simultaneous insertion, deletion or identity change of particles according to the reaction equation.
-For example we assume the ionization of an acidic unit which proceeds according to the reaction equation
-\begin{equation}
-    \mathrm{AH}\stackrel{K}{\leftrightarrows}\A+\h\label{eq: acid reaction}
-\end{equation}
-We perform the forward direction of this reaction
-by inserting a $\h$ particle and replacing $\AH$ by $\A$.
-We perform the reverse direction of this reaction
-by deleting a $\h$ particle and replacing $\A$ by $\AH$.
-
-In order to account for the particles creation and deletion
-we need to introduce standard states for individual reacting species.
-The creation of a particle then means that the particle is removed from the standard state
-and inserted into the studied system, and vice versa for deletion.
-Each species in its standard state has the \emph{standard} chemical potential, $\mu^\ominus_i$.
-The choice of standard state for each component is arbitrary
-and we usually define it as pure component at standard pressure $10^5$ Pa
-and concentration $1 \molperl$~\cite{IUPAC}.
-
-Thus we rewrite the formula for free energy \refeq{eq:Omega-GC}
-accounting for particles creation and deletion as
-\begin{equation}
-    \Omega=E-TS+\sum_i\left(\mu_i-\mu^\ominus_i\right) N_i\label{eq:Omega-RE}
-\end{equation}
-where the last term in \refeq{eq:Omega-RE} stands for the exchange of particles between the studied system and the standard states.
-
-Let's have the reaction extent $\xi = (N_i - N_{i,0})/\nu_i$
-where $N_i$, resp. $N_{i,0}$ is the actual, resp. initial number of the $i$-th particle species,
-$\nu_i$ is its stoichiometric coefficient.
-and $i$ runs over individual species involved
-in the chemical reaction \refeq{eq: acid reaction} $i \in (\h,\ \A,\ \AH)$. 
-The stoichiometric coefficients are positive for reaction products
-and negative for reactants: $\nu_\h=1$, $\nu_\A=1$, $\nu_\AH=-1$.
-Therefore we take $\xi = +1$ for the forward reaction direction
-and $\xi = -1$ for the reverse reaction direction.
-Then we can write the change of the free energy of the studied system during one reaction step as
-\begin{equation}
-\Delta\Omega_{\mathrm{re}}=\kT\ln\left(\prod_i V^{\nu_i\xi}\frac{N_i!}{\left(N_i+\nu_i\xi\right)!}\right)+
-\xi\left(\sum_i\nu_i\mu_i-\sum_i\nu_i\mu_i^\ominus\right)+\Delta E
-\label{eq: DeltaG RE one}
-\end{equation}
-%\begin{multline}
-%    \Delta\Omega_{\mathrm{re}}=\kT\ln\left(\prod_i V^{\nu_i\xi}\frac{N_i!}{\left(N_i+\nu_i\xi\right)!}\right)+\\
-%    \xi\left(\sum_i\nu_i\mu_i-\sum_i\nu_i\mu_i^\ominus\right)+\Delta E
-%\label{eq: DeltaG RE one}
-%\end{multline}
-
-We write $\sum_i\nu_i \mu_i = 0$
-for the chemical reaction in equilibrium.
-
-The term $\sum_i\nu_i\mu_i^\ominus$ is the standard Gibbs free energy change
-of the reaction \refeq{eq: acid reaction}.
-which defines the equilibrium reaction constant \cite{Atkins} as
-\begin{equation}
-    K = e^{-\sum_i\nu_i \mu_i^\ominus / \kT}
+    \Pr(\overline{X} - MOE(\gamma) \leq \mu_X \leq \overline{X} + MOE(\gamma)) = \gamma
 \end{equation}
 
-Finally, the \refeq{eq: DeltaG RE one} translates to
+In our study we set $\gamma = 0.95$
+
+\subsubsection{Routine implementation details}
+%Probably we don't need this section
+
+The arguments of our sampling routine are a function to calculate next sample and one of the next arguments: margins of error, effective sample size and timeout.
+
+An observable is sampled in a loop till one of required targets is met (timeout, the margins of error or sample size). 
+In the each following iteration of the loop, mean value and the margins of error are calculated with ever increasing precision and sample size.
+
+The loop follows the next steps:
+\begin{itemize}
+    \item Sample new data to double the sample size
+    \item Recalculate $\tau$, $N_{eff}$, MOE
+    \item If MOE is less, or $N_{eff}$ is bigger than desired, or run time exceed timeout exit loop
+\end{itemize}
+
+The routine returns mean of the sample, margins of error that defines confidence interval where true mean of distribution lies and \emph{effective} sample size that accounts that data is autocorrelated.
+
+The routine is also described in Figure \ref{fig: sampling_diagram}
+
+\begin{figure*}[t]
+\includegraphics[width = 0.9\textwidth]{figures/sample_to_target_scheme.png}
+\caption{Sampling routine diagram}
+\label{fig: sampling_diagram}
+\end{figure*}
+
+\subsection{Monte Carlo process}
+\subsubsection{Open system}
+Free energy in grand-cannonical ensemble
 \begin{equation}
-    \Delta\Omega_{\mathrm{re}}=\kT\ln\left(K^\xi\prod_i V^{\nu_i\xi}\frac{N_i!}{\left(N_i+\nu_i\xi\right)!}\right)+\Delta E
-\label{eq: DeltaG RE two}
+\Omega = E-TS + \mu N 
+\end{equation}
+where $S$ is the entropy. Boltzman formula
+\begin{equation}
+S= k_B \ln \frac{V^N}{N!}
+\end{equation}
+The change of free energy associated with insertion ($\xi=1$) or deletion ($\xi=-1$) a particle is
+\begin{equation}
+\Delta \Omega =\kT\ln\left(V^{\xi}\frac{N!}{ (N+\xi)!}\right)+\xi\mu+\Delta E
+\end{equation}
+\subsubsection{Closed system}
+In closed system ion pairs are exchanged between two finite volume boxes.
+
+\begin{equation}
+    \na_{I} + \cl_{I} \leftrightarrows \na_{II} + \cl_{II}
 \end{equation}
 
-\subsection{Ion pairs insertions\label{sec: ion insertions}}
-We treat the exchange of mobile ions with the reservoir as simultaneous insertion or deletion
-of ion pairs or sets in the simulation box.
-We insert/delete either $\na$ and $\cl$ ion pair or the two $\cl$ ions together with one $\ca$ ion.
-Thus we model the insertion as:
+Suppose an ion pair has been moved from box to another, then the change in entropy can be expressed as
 \begin{eqnarray}
-    \na +  \cl &\leftrightarrows& \emptyset\label{eq:nacl} \\
-    \ca + 2\cl &\leftrightarrows& \emptyset \label{eq:cacl}
+    \Delta S = 2 \log \left(\frac{V^{I}}{V^{II}} \right) ^ {\gamma}  \left(\frac{(N_{Na^{+}}^{I}+\mathcal{H}(\gamma))(N_{Cl^{-}}^{I}+\mathcal{H}(\gamma))}{(N_{Na^{+}}^{II}+\mathcal{H}(-\gamma))(N_{Cl^{-}}^{II}+\mathcal{H}(-\gamma))}\right)^{-\gamma}
 \end{eqnarray}
-with the corresponding equilibrium reaction constants, reflecting the free energy change during the insertion
-\begin{eqnarray*}
-    K_\mathrm{NaCl}     = \exp\left(\left(\mu_\na+ \mu_\cl \right) /\kT\right), \\
-    K_{\mathrm{CaCl}_2} = \exp\left(\left(\mu_\ca+2\mu_\cl \right /\kT\right))
-\end{eqnarray*}
-%$K_\mathrm{NaCl}= \exp\left(\mu_\na+\mu_\cl \right)$, $K_{\mathrm{CaCl}_2} = \exp\left(\mu_\ca+2\mu_\cl \right)$
+where $\gamma$ defines the direction of the trial move, so that $\gamma_{I \rightarrow II} = -1$ when an ion pair moved from box I to box II and  $\gamma_{II \rightarrow I} = 1$ otherwise, $\mathcal{H}$ is the Heaviside step function.
 
-\paragraph{Moderate pH conditions\label{sec: moderate pH conditions}}
-In our study we consider the chemical equilibrium between the gel system and reservoir at neutral pH,
-which means that the concentration of $\h$ ions in the reservoir is $c_\h=\unit[10^{-7}]{mol/l}$.
-At the same time we include rather high salinities \ie $\cs \gtrsim \unit[0.006]{mol/l}$,
-so that the concentrations of $\h$ ions and salt ions, $\na$ and $\ca$, differ by at least three orders of magnitude.
-%If one had have wanted to simulate a system with at least 10 $\h$ particles, he would have to include $10^5$ of $\na$ particles there,  and not to mention the amount of polymer needed.
-Under such conditions the sampling of the reaction \refeq{eq: acid reaction}
-is very difficult because of the lack of $\h$ ions.
-Following the scheme proposed in \cite{Landsgesel2020} and \cite{Rud2020},
-we sample this reaction assuming that
-it is accompanied by simultaneous exchange of counterions $\na$ and $\ca$ by $\h$ ion
-with corresponding Gibbs free energy changes\cite{Smith1991}:
+The probability that the move will be accepted is calculated from the free energy change as
+\begin{equation}
+    \mathcal{P} = \exp(-\beta (\Delta E_{pot} - k_B T \Delta S))
+\end{equation}
+
+Thus, moving an ion pair from box I to box II change the entropy
+\begin{equation}
+    \Delta S_{I \rightarrow II} = 2 \log \left(\frac{V^{II}}{V^{I}} \right)  \frac{N_{Na^{+}}^{I} N_{Cl^{-}}^{I}}{(N_{Na^{+}}^{II}+1)(N_{Cl^{-}}^{II}+1)}
+\end{equation}
+
+The probability of this move ${I \rightarrow II}$ to be accepted
+
+\begin{equation}
+    \mathcal{P}_{I \rightarrow II} = \exp\left(-\beta (\Delta E_{pot} - 2 k_B T \log \left(\frac{V^{II}}{V^{I}} \right)  \frac{N_{Na^{+}}^{I} N_{Cl^{-}}^{I}}{(N_{Na^{+}}^{II}+1)(N_{Cl^{-}}^{II}+1)})\right)
+\end{equation}
+
+\begin{itemize}
+\item perform a move of a random ion pair 
+    \begin{equation}
+    \left(\na +\cl\right)^{I} \leftrightarrows\left(\na +\cl\right)^{II}
+\end{equation}
+
+\item accept if 
+    \begin{equation}
+    \mathrm{rand}(0,1] < \left(\frac{V^{II}}{V^{I}}\right)^{\xi}\prod_{i=Na,\ Cl}\frac{N^I_i!}{(N^I_i+\xi)!}\frac{N^{II}_i!}{(N^{II}_i+\xi)!}\exp(-\beta\Delta E_{pot})
+\end{equation}
+\end{itemize}
+
+\subsection{Donnan equilibrium in finite volume reservoirs}
+Before we can explore any system properties and collect data the system has to be equilibrated.
+To achieve this we perform equilibration routine consist of sequence of Molecular Dynamics and Monte Carlo steps.
+%Here we describe our technique
+The result of equilibration is stationary of any observable such as pressure, end-to-end distance for polymer chains and ion distribution between reservoirs.
+
+The success and the cost in terms of computational time for the equilibration process heavily depend on initial guess.
+In our case we initialize the system with ion distribution corresponds to Donnan equilibrium.
+
+In closed system number of ions in the system is constant, so Donnan equilibrium can be formulated as follows
+\begin{equation}
+    \frac{\left(N_{pairs} - N_{Cl^{-}}^{(gel)}\right)^2}{V_{salt}^2} = \frac{N_{Cl^{-}}^{gel} (N^{{(gel)}}_{A^{-}} + N_{Cl^{-}}^{(gel)})}{V_{gel}^2}
+\end{equation}
+where $N^{{(gel)}}_{A^{-}}$ is number of fixed anions in the box with the gel \ie acetic groups in the polymer gel.
+Solving this equation with respect to $N^{{(gel)}}_{A^{-}}$ gives us the distribution of the ions between two boxes.
+
+%probably not needed
 \begin{eqnarray}
-     \h&\leftrightarrows&\na, \quad \Delta\Omega' = \mu_\h-\mu_\na   \label{eq:hna} \\
-    2\h&\leftrightarrows&\ca, \quad \Delta\Omega'' = 2\mu_\h-\mu_\ca \label{eq:cacl}
+    %N_{Cl^{-}}^{(gel)} = \frac{\frac{N^{{(gel)}}_{A^{-}} V_{salt}^{2}}{2} + N_{pairs} V_{gel}^{2} - \frac{V_{salt} \sqrt{N^{{(gel)}}_{A^{-}}^{2} V_{salt}^{2} + 4 N^{{(gel)}}_{A^{-}} N_{pairs} V_{gel}^{2} + 4 N_{pairs}^{2} V_{gel}^{2}}}{2}}{V_{gel}^{2} - V_{salt}^{2}}
+    \\
+    N_{Na^{+}}^{(gel)} = N^{{(gel)}}_{A^{-}} + N_{Cl^{-}}^{(gel)}
+    \\
+    N_{Cl^{-}}^{(salt)} = N_{Na^{+}}^{(gel)} = N_{pairs} - N_{Cl^{-}}^{(gel)}
 \end{eqnarray}
-
-Summing up the reactions \refeq{eq: acid reaction} with \refeq{eq:hna} and with \refeq{eq:cacl}
-we obtain two reactions
-\begin{eqnarray}
-    \mathrm{HA}&\stackrel{K'}{\leftrightarrows}&\mathrm{A}^{-}+\na\label{eq: acid reaction na}\\
-    2\mathrm{HA}&\stackrel{K''}{\leftrightarrows}&2\mathrm{A}^{-}+\ca\label{eq: acid reaction ca}
-\end{eqnarray}
-where $K'$ and $K''$ are the modified reaction constants which account for the free energy costs caused by the ions exchange, $\Delta\Omega''$ and $\Delta\Omega'$
-\begin{eqnarray}
-    K' &=& K \exp\left((\mu_\h-\mu_\na)/\kT\right) \label{eq:Gamma'}\\
-    K'' &=& K \exp\left((2\mu_\h-\mu_\ca)/\kT\right)\label{eq:Gamma''}
-\end{eqnarray}
-We sample these two reactions instead of \refeq{eq: acid reaction}.
-Then the final equations for the reactions acceptance criteria are obtained by replacing $K$
-in \refeq{eq: DeltaG RE two} by $K'$ and $K''$.
-
-Note that we used the approximation of low concentration of $\h$,
-which is valid in conditions close to neutral $\pH$,
-and generalize the model considering only three types of ions, namely $\na$, $\cl$ and $\ca$.
-The value of $\pH$ enters the model only through Equations \ref{eq:Gamma'} and \ref{eq:Gamma''}.
-
-\bibliographystyle{plain}
-\bibliography{gibbs}
-
-\newpage
-\pagebreak
-
-\end{document}

### 2022-07-07 gibbs.tex
esi separated

@@
 
-\title{Water desalination using polyelectrolyte hydrogel. Gibbs ensemble
-modelling}
+\title{Water desalination using polyelectrolyte hydrogel. Gibbs ensemble modeling}
 
@@
 
-\newpage
-\section*{Supplementary Information}
-\subsection{Sampling routine}
-Data gained from Molecular Dynamics (MD) and Markov Chain Monte Carlo processes (MD) are highly autocorrelated, thus we can not imply statistic developed for uncorrelated data.
-We have written a small in-house python package to calculate the expected value, the margin of error and effective sample size of correlated data.
-
-The goal of the routine is to estimate mean and margins of error for an observable e.g.
-pressure, number of particles, end-to-end distance of a chain for a given confidence level or effective sample size.
-
-We also provided the way to limit sampling procedure with some timeout value. Our routine based on [] %[https://www.physik.uni-leipzig.de/~janke/Paper/nic10_423_2002.pdf]
-
-There are multiple sampling routines developed for autocorrelated data, i.e. binning analysis, ... %some notes what others do
-
-Expected value of the observable $X$ estimated as the mere mean of the sample $\overline{X}$, the same way one would do for uncorrelated data, whilst to estimate margins of error and \emph{effective} sample size $N_{eff}$ we used the next formulae.
-First of all we have to correct sample size to account that data is correlated:
-\begin{eqnarray}
-    N_{eff} = \frac{N}{2\tau}
-    \\
-    \tau  = \frac{1}{2} + \sum_{k=1}^{N} \text{acf} (k) (1-\frac{k}{N})
-\end{eqnarray}
-where $\tau$ is integrated autocorrelation time, $N$ size of autocorrelated data, $\text{acf} (k)$ is autocorrelation function on lag.
-
-Note that ideally integral of  $\text{acf} (k)$ monotonically approaches some finite value, but due to unavoidable errors in number representation in computer and numeric integration methods it does not hold.
-For that reason instead of $\text{acf} (k)$ integral we use the maximum of its cumulative sum.
-
-Margins of error (MOE) for a given confidence level $\gamma$ and effective sample size $N_{eff}$ is calculated using the next equation:
-\begin{eqnarray}
-    \text{MOE}(\gamma) = \frac{S_{N}}{\sqrt{N_{eff}}} t_{((1+\gamma)/2, N_{eff}-1)}
-\end{eqnarray}
-where $t_{(\alpha, \nu)}$ is percentile function (inverse cumulative distribution function) of Student’s distribution with $\nu$ degrees of freedom for $\alpha$ percentile,
-$S_N$ is standard deviation of the sample.
-
-The true mean of the observable $\mu_X$ lies inside the confidence interval with the confidence level $\gamma$.
-\begin{equation}
-    \Pr(\overline{X} - MOE(\gamma) \leq \mu_X \leq \overline{X} + MOE(\gamma)) = \gamma
-\end{equation}
-
-In our study we set $\gamma = 0.95$
-
-\subsubsection{Routine implementation details}
-%Probably we don't need this section
-
-The arguments of our sampling routine are a function to calculate next sample and one of the next arguments: margins of error, effective sample size and timeout.
-
-An observable is sampled in a loop till one of required targets is met (timeout, the margins of error or sample size). 
-In the each following iteration of the loop, mean value and the margins of error are calculated with ever increasing precision and sample size.
-
-The loop follows the next steps:
-\begin{itemize}
-    \item Sample new data to double the sample size
-    \item Recalculate $\tau$, $N_{eff}$, MOE
-    \item If MOE is less, or $N_{eff}$ is bigger than desired, or run time exceed timeout exit loop
-\end{itemize}
-
-The routine returns mean of the sample, margins of error that defines confidence interval where true mean of distribution lies and \emph{effective} sample size that accounts that data is autocorrelated.
-
-The routine is also described in Figure \ref{fig: sampling_diagram}
-
-\begin{figure*}[t]
-\includegraphics[width = 0.9\textwidth]{figures/sample_to_target_scheme.png}
-\caption{Sampling routine diagram}
-\label{fig: sampling_diagram}
-\end{figure*}
-
-\subsection{Monte Carlo process}
-\subsubsection{Open system}
-Free energy in grand-cannonical ensemble
-\begin{equation}
-\Omega = E-TS + \mu N 
-\end{equation}
-where $S$ is the entropy. Boltzman formula
-\begin{equation}
-S= k_B \ln \frac{V^N}{N!}
-\end{equation}
-The change of free energy associated with insertion ($\xi=1$) or deletion ($\xi=-1$) a particle is
-\begin{equation}
-\Delta \Omega =\kT\ln\left(V^{\xi}\frac{N!}{ (N+\xi)!}\right)+\xi\mu+\Delta E
-\end{equation}
-\subsubsection{Closed system}
-In closed system ion pairs are exchanged between two finite volume boxes.
-
-\begin{equation}
-    \na_{I} + \cl_{I} \leftrightarrows \na_{II} + \cl_{II}
-\end{equation}
-
-Suppose an ion pair has been moved from box to another, then the change in entropy can be expressed as
-\begin{eqnarray}
-    \Delta S = 2 \log \left(\frac{V^{I}}{V^{II}} \right) ^ {\gamma}  \left(\frac{(N_{Na^{+}}^{I}+\mathcal{H}(\gamma))(N_{Cl^{-}}^{I}+\mathcal{H}(\gamma))}{(N_{Na^{+}}^{II}+\mathcal{H}(-\gamma))(N_{Cl^{-}}^{II}+\mathcal{H}(-\gamma))}\right)^{-\gamma}
-\end{eqnarray}
-where $\gamma$ defines the direction of the trial move, so that $\gamma_{I \rightarrow II} = -1$ when an ion pair moved from box I to box II and  $\gamma_{II \rightarrow I} = 1$ otherwise, $\mathcal{H}$ is the Heaviside step function.
-
-The probability that the move will be accepted is calculated from the free energy change as
-\begin{equation}
-    \mathcal{P} = \exp(-\beta (\Delta E_{pot} - k_B T \Delta S))
-\end{equation}
-
-Thus, moving an ion pair from box I to box II change the entropy
-\begin{equation}
-    \Delta S_{I \rightarrow II} = 2 \log \left(\frac{V^{II}}{V^{I}} \right)  \frac{N_{Na^{+}}^{I} N_{Cl^{-}}^{I}}{(N_{Na^{+}}^{II}+1)(N_{Cl^{-}}^{II}+1)}
-\end{equation}
-
-The probability of this move ${I \rightarrow II}$ to be accepted
-
-\begin{equation}
-    \mathcal{P}_{I \rightarrow II} = \exp\left(-\beta (\Delta E_{pot} - 2 k_B T \log \left(\frac{V^{II}}{V^{I}} \right)  \frac{N_{Na^{+}}^{I} N_{Cl^{-}}^{I}}{(N_{Na^{+}}^{II}+1)(N_{Cl^{-}}^{II}+1)})\right)
-\end{equation}
-
-\begin{itemize}
-\item perform a move of a random ion pair 
-    \begin{equation}
-    \left(\na +\cl\right)^{I} \leftrightarrows\left(\na +\cl\right)^{II}
-\end{equation}
-
-\item accept if 
-    \begin{equation}
-    \mathrm{rand}(0,1] < \left(\frac{V^{II}}{V^{I}}\right)^{\xi}\prod_{i=Na,\ Cl}\frac{N^I_i!}{(N^I_i+\xi)!}\frac{N^{II}_i!}{(N^{II}_i+\xi)!}\exp(-\beta\Delta E_{pot})
-\end{equation}
-\end{itemize}
-
-\subsection{Donnan equilibrium in finite volume reservoirs}
-Before we can explore any system properties and collect data the system has to be equilibrated.
-To achieve this we perform equilibration routine consist of sequence of Molecular Dynamics and Monte Carlo steps.
-%Here we describe our technique
-The result of equilibration is stationary of any observable such as pressure, end-to-end distance for polymer chains and ion distribution between reservoirs.
-
-The success and the cost in terms of computational time for the equilibration process heavily depend on initial guess.
-In our case we initialize the system with ion distribution corresponds to Donnan equilibrium.
-
-In closed system number of ions in the system is constant, so Donnan equilibrium can be formulated as follows
-\begin{equation}
-    \frac{\left(N_{pairs} - N_{Cl^{-}}^{(gel)}\right)^2}{V_{salt}^2} = \frac{N_{Cl^{-}}^{gel} (N^{{(gel)}}_{A^{-}} + N_{Cl^{-}}^{(gel)})}{V_{gel}^2}
-\end{equation}
-where $N^{{(gel)}}_{A^{-}}$ is number of fixed anions in the box with the gel \ie acetic groups in the polymer gel.
-Solving this equation with respect to $N^{{(gel)}}_{A^{-}}$ gives us the distribution of the ions between two boxes.
-
-%probably not needed
-\begin{eqnarray}
-    %N_{Cl^{-}}^{(gel)} = \frac{\frac{N^{{(gel)}}_{A^{-}} V_{salt}^{2}}{2} + N_{pairs} V_{gel}^{2} - \frac{V_{salt} \sqrt{N^{{(gel)}}_{A^{-}}^{2} V_{salt}^{2} + 4 N^{{(gel)}}_{A^{-}} N_{pairs} V_{gel}^{2} + 4 N_{pairs}^{2} V_{gel}^{2}}}{2}}{V_{gel}^{2} - V_{salt}^{2}}
-    \\
-    N_{Na^{+}}^{(gel)} = N^{{(gel)}}_{A^{-}} + N_{Cl^{-}}^{(gel)}
-    \\
-    N_{Cl^{-}}^{(salt)} = N_{Na^{+}}^{(gel)} = N_{pairs} - N_{Cl^{-}}^{(gel)}
-\end{eqnarray}
-
 \end{document}

### 2022-07-07 esi.tex
esi.tex

@@
+\documentclass[journal=mamobx, layout=twocolumns,manuscript=article]{achemso}
+
+\makeatletter
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
+
+\title{Supporting information to the article\\ ``Water desalination using polyelectrolyte hydrogel. Gibbs ensemble modeling''}
+
+\author{Mikhail Laktionov}
+
+\affiliation[cuni]{Department of Physical and Macromolecular Chemistry, Faculty of Science,
+Charles University in Prague, Czech Republic}
+
+\alsoaffiliation[itmo]{St. Petersburg National Research University of Information Technologies,
+Mechanics and Optics, St. Petersburg, Russia.}
+
+\author{Lucie Nová}
+\author{Oleg V. Rud}
+
+\affiliation{Department of Physical and Macromolecular Chemistry, Faculty of Science,
+Charles University in Prague, Czech Republic}
+
+\alsoaffiliation[imc]{Institute of Macromolecular Compounds of Russian Academy of Sciences,
+Saint-Petersburg, Russia}
+
+\email{oleg.rud@natur.cuni.cz}
+
+\abbreviations{MC, MD, RO, FO}
+
+\keywords{polyelectrolye hydrogel, simulation, desalination}
+
+%% Because html converters don't know tabularnewline
+\providecommand{\tabularnewline}{\\}
+
+\input{definitions.tex}
+\makeatother
+
 \newpage
-\section*{Supplementary Information}
-\subsection{Sampling routine}
-Data gained from Molecular Dynamics (MD) and Markov Chain Monte Carlo processes (MD) are highly autocorrelated, thus we can not imply statistic developed for uncorrelated data.
-We have written a small in-house python package to calculate the expected value, the margin of error and effective sample size of correlated data.
 
-The goal of the routine is to estimate mean and margins of error for an observable e.g.
-pressure, number of particles, end-to-end distance of a chain for a given confidence level or effective sample size.
+\begin{document}
 
-We also provided the way to limit sampling procedure with some timeout value. Our routine based on [] %[https://www.physik.uni-leipzig.de/~janke/Paper/nic10_423_2002.pdf]
-
-There are multiple sampling routines developed for autocorrelated data, i.e. binning analysis, ... %some notes what others do
-
-Expected value of the observable $X$ estimated as the mere mean of the sample $\overline{X}$, the same way one would do for uncorrelated data, whilst to estimate margins of error and \emph{effective} sample size $N_{eff}$ we used the next formulae.
-First of all we have to correct sample size to account that data is correlated:
-\begin{eqnarray}
-    N_{eff} = \frac{N}{2\tau}
-    \\
-    \tau  = \frac{1}{2} + \sum_{k=1}^{N} \text{acf} (k) (1-\frac{k}{N})
-\end{eqnarray}
-where $\tau$ is integrated autocorrelation time, $N$ size of autocorrelated data, $\text{acf} (k)$ is autocorrelation function on lag.
-
-Note that ideally integral of  $\text{acf} (k)$ monotonically approaches some finite value, but due to unavoidable errors in number representation in computer and numeric integration methods it does not hold.
-For that reason instead of $\text{acf} (k)$ integral we use the maximum of its cumulative sum.
-
-Margins of error (MOE) for a given confidence level $\gamma$ and effective sample size $N_{eff}$ is calculated using the next equation:
-\begin{eqnarray}
-    \text{MOE}(\gamma) = \frac{S_{N}}{\sqrt{N_{eff}}} t_{((1+\gamma)/2, N_{eff}-1)}
-\end{eqnarray}
-where $t_{(\alpha, \nu)}$ is percentile function (inverse cumulative distribution function) of Student’s distribution with $\nu$ degrees of freedom for $\alpha$ percentile,
-$S_N$ is standard deviation of the sample.
-
-The true mean of the observable $\mu_X$ lies inside the confidence interval with the confidence level $\gamma$.
-\begin{equation}
-    \Pr(\overline{X} - MOE(\gamma) \leq \mu_X \leq \overline{X} + MOE(\gamma)) = \gamma
-\end{equation}
-
-In our study we set $\gamma = 0.95$
-
-\subsubsection{Routine implementation details}
-%Probably we don't need this section
-
-The arguments of our sampling routine are a function to calculate next sample and one of the next arguments: margins of error, effective sample size and timeout.
-
-An observable is sampled in a loop till one of required targets is met (timeout, the margins of error or sample size). 
-In the each following iteration of the loop, mean value and the margins of error are calculated with ever increasing precision and sample size.
-
-The loop follows the next steps:
-\begin{itemize}
-    \item Sample new data to double the sample size
-    \item Recalculate $\tau$, $N_{eff}$, MOE
-    \item If MOE is less, or $N_{eff}$ is bigger than desired, or run time exceed timeout exit loop
-\end{itemize}
-
-The routine returns mean of the sample, margins of error that defines confidence interval where true mean of distribution lies and \emph{effective} sample size that accounts that data is autocorrelated.
-
-The routine is also described in Figure \ref{fig: sampling_diagram}
-
-\begin{figure*}[t]
-\includegraphics[width = 0.9\textwidth]{figures/sample_to_target_scheme.png}
-\caption{Sampling routine diagram}
-\label{fig: sampling_diagram}
-\end{figure*}
-
-\subsection{Monte Carlo process}
-\subsubsection{Open system}
-Free energy in grand-cannonical ensemble
+\subsection{Ion exchange Monte Carlo sampling}
+\paragraph{Open system.}
+Consider the free energy in the grand-canonical ensemble for single particle type, \ie the Landau potential:
 \begin{equation}
@@
 \end{equation}
-where $S$ is the entropy. Boltzman formula
+where $E$ is internal energy, $T$~--- temperature, $S$~--- entropy, $N$ is the number of particles.
+The entropy $S$ is given by the Boltzmann formula~\cite{Nagle2004}:
 \begin{equation}
@@
 \end{equation}
-\subsubsection{Closed system}
+In our case we insert ions only as electroneutral pairs, $\na$ and $\cl$, so the corresponding formula for the free energy change turns to 
+\begin{equation}
+\Delta\Omega=\kT\ln\left(V^{2\xi}\frac{\Nna!}{\left(\Nna+\xi\right)!}\frac{\Ncl!}{\left(\Ncl+\xi\right)!}\right)+
+\xi\left(\muna+\mucl\right)+\Delta E
+\label{eq: DeltaG RE one}
+\end{equation}
+
+In order to simulate an ensemble which exchanges particles with the bath (bulk reservoir) we need to perform the following Monte Carlo procedure \cite{Frenlkel2002_book}
+\begin{enumerate}
+	\item we propose the new configuration of the system by insertion (or deletion) of an ion pair so that the total number of pairs changes from $N$ to $N+\xi$, $\xi=\pm1$
+	\item we accept the new configuration if $\mathcal{R}^{\xi}<e^{\Delta\Omega/\kT}$, where $\mathcal{R}$ is uniformly distributed random number in range between $0$ and $1$.
+	\item continue untill the desired number of accepted moves is reached
+\end{enumerate}
+
+\paragraph{Closed system.}
 In closed system ion pairs are exchanged between two finite volume boxes.
-
 \begin{equation}
@@
 \end{equation}
-
-Suppose an ion pair has been moved from box to another, then the change in entropy can be expressed as
-\begin{eqnarray}
-    \Delta S = 2 \log \left(\frac{V^{I}}{V^{II}} \right) ^ {\gamma}  \left(\frac{(N_{Na^{+}}^{I}+\mathcal{H}(\gamma))(N_{Cl^{-}}^{I}+\mathcal{H}(\gamma))}{(N_{Na^{+}}^{II}+\mathcal{H}(-\gamma))(N_{Cl^{-}}^{II}+\mathcal{H}(-\gamma))}\right)^{-\gamma}
-\end{eqnarray}
-where $\gamma$ defines the direction of the trial move, so that $\gamma_{I \rightarrow II} = -1$ when an ion pair moved from box I to box II and  $\gamma_{II \rightarrow I} = 1$ otherwise, $\mathcal{H}$ is the Heaviside step function.
-
-The probability that the move will be accepted is calculated from the free energy change as
+Suppose an ion pair has been moved from one box to another, then the change in entropy can be expressed as
 \begin{equation}
-    \mathcal{P} = \exp(-\beta (\Delta E_{pot} - k_B T \Delta S))
+    \Delta S = 2 k_B \ln \left(\frac{V^{I}}{V^{II}} \right) ^ {\xi}  \left(\frac{(N_{Na^{+}}^{I}+\theta(\xi))(N_{Cl^{-}}^{I}+\theta(\xi))}{(N_{Na^{+}}^{II}+\theta(-\xi))(N_{Cl^{-}}^{II}+\theta(-\xi))}\right)^{-\xi}
 \end{equation}
-
-Thus, moving an ion pair from box I to box II change the entropy
+where $\xi$ again defines the direction of the trial move, so that $\xi_{I \rightarrow II} = -1$ when an ion pair moved from box I to box II and  $\xi_{II \rightarrow I} = 1$ otherwise, $\theta(\xi)$ is the Heaviside step function.
+The corresponding total free energy change in both systems is the following 
 \begin{equation}
-    \Delta S_{I \rightarrow II} = 2 \log \left(\frac{V^{II}}{V^{I}} \right)  \frac{N_{Na^{+}}^{I} N_{Cl^{-}}^{I}}{(N_{Na^{+}}^{II}+1)(N_{Cl^{-}}^{II}+1)}
+\Delta\Omega = \Delta E^{I}+\Delta E^{II}+T\Delta S
 \end{equation}
-
-The probability of this move ${I \rightarrow II}$ to be accepted
-
-\begin{equation}
-    \mathcal{P}_{I \rightarrow II} = \exp\left(-\beta (\Delta E_{pot} - 2 k_B T \log \left(\frac{V^{II}}{V^{I}} \right)  \frac{N_{Na^{+}}^{I} N_{Cl^{-}}^{I}}{(N_{Na^{+}}^{II}+1)(N_{Cl^{-}}^{II}+1)})\right)
-\end{equation}
-
-\begin{itemize}
-\item perform a move of a random ion pair 
-    \begin{equation}
-    \left(\na +\cl\right)^{I} \leftrightarrows\left(\na +\cl\right)^{II}
-\end{equation}
-
-\item accept if 
-    \begin{equation}
-    \mathrm{rand}(0,1] < \left(\frac{V^{II}}{V^{I}}\right)^{\xi}\prod_{i=Na,\ Cl}\frac{N^I_i!}{(N^I_i+\xi)!}\frac{N^{II}_i!}{(N^{II}_i+\xi)!}\exp(-\beta\Delta E_{pot})
-\end{equation}
-\end{itemize}
+The Monte Carlo sampling procedure is the following
+\begin{enumerate}
+	\item propose the new configuration of the system by moving the ion pair from one volume to another 
+	\item accept the new configuration if $\mathcal{R}^{\xi}<e^{\Delta\Omega/\kT}$
+	\item continue untill the desired number of accepted moves is reached
+\end{enumerate}
 
 \subsection{Donnan equilibrium in finite volume reservoirs}
+\todo{mb we remove this section}
 Before we can explore any system properties and collect data the system has to be equilibrated.
@@
 
-%probably not needed
+\begin{equation}
+N_{Cl^{-}}^{(gel)} = \frac{\frac{\NA \Vout^{2}}{2} + N_{pairs} \Vgel^{2} - \frac{\Vout \sqrt{N^{{(gel)}}_{A^{-}}^{2} \Vout^{2} + 4 N^{{(gel)}}_{A^{-}} N_{pairs} \Vgel^{2} + 4 N_{pairs}^{2} \Vgel^{2}}}{2}}{\Vgel^{2} - \Vout^{2}}
+\end{equation}
+
+\todoi{
+This paragraph moved from overleaf
+
+Compression of the gel in infinite reservoir does not  change its salinity, on the contrary, upon compression of the gel in closed reservoir salinity of separated liquid is decreasing (supernatant salinity), using the Donnan law formulated for finite reservoir salinity can be expressed as
+\begin{equation*}
+    c_s^\prime = \frac{\sqrt{4\alpha^{2} c_{p}^{2} \left(1-\gamma\right)^{2} + \alpha c_{p} c_{s} \gamma^{2} + c_{s}^{2} \gamma^{2}}-\frac{\alpha c_{p} \left(1-\gamma\right)}{2} - c_{s} \left(1-\gamma\right)}{\gamma^{2} - \left(1-\gamma\right)^{2}}
+\end{equation*}
+where $\gamma = V_{gel}/V_0$ is relative to initial volume compression.
+}
 \begin{eqnarray}
@@
 \end{eqnarray}
+\subsection{Sampling routine}
+Data gained from Molecular Dynamics (MD) and Monte Carlo processes (MC) are highly autocorrelated, thus we can not imply statistic developed for uncorrelated data. 
+We have written a small in-house python package realizing the routine estimating mean and error for the observables provided by simulation, \ie pressure, number of particles, end-to-end distance of a chain for a given confidence level or effective sample size.
+Within this routine we provided the way to limit sampling procedure with some timeout value, in a way similar to described in \href{https://www.physik.uni-leipzig.de/~janke/Paper/nic10_423_2002.pdf}{Janke2002}
+
+The expected value of the observable $X$ is estimated as a simple sample mean of $\overline{X}$, just like for uncorrelated data.
+While estimating the errors and \emph{effective} sample size $N_{\text{eff}}$, the following formulas were used.
+\begin{equation}
+    N_{eff} = \frac{N}{2\tau}
+\end{equation}    
+\begin{equation}
+    \tau  = \frac{1}{2} + \sum_{k=1}^{N} \text{acf} (k) (1-\frac{k}{N})
+\end{equation}
+where $\tau$ is integrated autocorrelation time, $N$ size of autocorrelated data, $\text{acf} (k)$ is autocorrelation function on lag.
+
+Note that ideally integral of  $\text{acf} (k)$ monotonically approaches some finite value, but due to unavoidable errors in number representation in computer and numeric integration methods it does not hold.
+For that reason instead of $\text{acf} (k)$ integral we use the maximum of its cumulative sum.
+
+Margins of error (MOE) for a given confidence level $\gamma$ and effective sample size $N_{eff}$ is calculated using the following equation:
+\begin{eqnarray}
+    \text{MOE}(\gamma) = \frac{S_{N}}{\sqrt{N_{\text{eff}}}} t_{((1+\gamma)/2, N_{\text{eff}}-1)}
+\end{eqnarray}
+where $t_{(\alpha, \nu)}$ is percentile function (inverse cumulative distribution function) of Student’s distribution with $\nu$ degrees of freedom for $\alpha$ percentile,
+$S_N$ is standard deviation of the sample.
+The true mean of the observable $\mu_X$ lies inside the confidence interval with the confidence level $\gamma$.
+\begin{equation}
+    \Pr(\overline{X} - MOE(\gamma) \leq \mu_X \leq \overline{X} + MOE(\gamma)) = \gamma
+\end{equation}
+In our study we set $\gamma = 0.95$
+
+\paragraph{Routine implementation details.}
+%Probably we don't need this section
+
+The sampling routine takes the function calculating an observable $X$ as an argument. 
+In addition, it takes as a parameter one of the following values: the desired margins of error, target effective sample size or timeout.
+An observable is sampled in a loop till one of required targets is met (timeout, the margins of error or sample size). 
+In the each following iteration of the loop, mean value and the margins of error are calculated with ever increasing precision and sample size.
+
+The loop follows the next steps:
+\begin{itemize}
+    \item Sample new data to double the sample size
+    \item Recalculate $\tau$, $N_{eff}$, and MOE
+    \item Exit the loop if either MOE is less than the desired, 
+    			or $N_{eff}$ is bigger than the desired, 
+    			or run time exceed timeout.
+\end{itemize}
+Finally, it returns mean of the sample, margins of error that defines confidence interval where true mean of distribution lies and \emph{effective} sample size. 
+The routine is also described schematically in Figure \ref{fig: sampling_diagram}
+
+\begin{figure*}[t]
+\includegraphics[width = 0.9\textwidth]{figures/sample_to_target_scheme.png}
+\caption{Sampling routine diagram}
+\label{fig: sampling_diagram}
+\end{figure*}
+\bibliographystyle{plain}
+\bibliography{lit/gibbs.bib}
+\end{document}

### 2022-07-07 gibbs.tex
esi open system
edited table

@@
 \documentclass[journal=mamobx, layout=twocolumns,manuscript=article]{achemso}
-
-\usepackage[utf8]{inputenc}
-\usepackage{geometry}
-\geometry{verbose}
-\usepackage{xcolor}
-\usepackage{verbatim}
-\usepackage{multirow}
-\usepackage{amsmath}
-\usepackage{amsthm}
-\usepackage{graphicx}
-\usepackage[unicode=true,pdfusetitle,
- bookmarks=false,
- breaklinks=true,pdfborder={0 0 0},pdfborderstyle={},backref=false,colorlinks=true]
- {hyperref}
-\usepackage[textsize=small]{todonotes}
 
@@
 \hline 
-\multirow{2}{*}{{\small{}$91.47$}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{{\small{}$57.08\pm0.122\enskip\longrightarrow$}} & \multirow{2}{*}{{\small{}2.74}} & \multirow{2}{*}{{\small{}$95.4\pm1.86$}} &  & \multirow{2}{*}{}\tabularnewline
+\multirow{2}{*}{{\small{}$91.47$}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{{\small{}$57.08\pm0.122\enskip\longrightarrow$}} & \multirow{2}{*}{{\small{}2.74}} & \multirow{2}{*}{{\small{}$95.4\pm1.9$}} &  & \multirow{2}{*}{}\tabularnewline
  &  & \multicolumn{2}{r|}{{\small{}$71.75\pm0.024$}} &  &  & \multirow{8}{*}{{\small{}\hspace{-1em}}\textcolor{teal}{\small{}$\left.\begin{array}{l}
@@
 \end{array}\right\rbrace $$\rotatebox{90}{\hspace{-5em}{\color{teal}\ensuremath{\begin{array}{cc}
-W^{\mathrm{sim}}= & 202.8\pm3.23\\
+W^{\mathrm{sim}}= & 202.8\pm3.2\\
 W^{id}= & 52.9\\
@@
 \cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
-\multicolumn{2}{l|}{{\small{}$89.41\pm0.229\enskip\longrightarrow$}} & \multirow{2}{*}{{\small{}56.90}} & \multirow{2}{*}{} & \multirow{2}{*}{{\small{}2.72}} & \multirow{2}{*}{{\small{}$109.1\pm1.72$}} &  & \multirow{2}{*}{}\tabularnewline
+\multicolumn{2}{l|}{{\small{}$89.41\pm0.23\enskip\longrightarrow$}} & \multirow{2}{*}{{\small{}56.90}} & \multirow{2}{*}{} & \multirow{2}{*}{{\small{}2.72}} & \multirow{2}{*}{{\small{}$109.1\pm1.7$}} &  & \multirow{2}{*}{}\tabularnewline
 \multicolumn{2}{r|}{{\small{}$73.63\pm0.03$}} &  &  &  &  &  & \tabularnewline
 \cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
-\multirow{2}{*}{\textcolor{teal}{\small{}63.93}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{teal}{\small{}$37.28\pm0.083\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{teal}{\small{}3.26}} & \multirow{2}{*}{\textcolor{teal}{\small{}$100.9\pm1.69$}} &  & \tabularnewline
- &  & \multicolumn{2}{r|}{\textcolor{teal}{\small{}$50.58\pm0.013$}} &  &  &  & \multirow{8}{*}{{\small{}\hspace{-1em}}\textcolor{olive}{\small{}$\left.\begin{array}{l}
+\multirow{2}{*}{\textcolor{teal}{\small{}63.93}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{teal}{\small{}$37.28\pm0.08\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{teal}{\small{}3.26}} & \multirow{2}{*}{\textcolor{teal}{\small{}$100.9\pm1.7$}} &  & \tabularnewline
+ &  & \multicolumn{2}{r|}{\textcolor{teal}{\small{}$50.579\pm0.013$}} &  &  &  & \multirow{8}{*}{{\small{}\hspace{-1em}}\textcolor{olive}{\small{}$\left.\begin{array}{l}
 \\
@@
 \end{array}\right\rbrace $$\rotatebox{90}{\hspace{-5em}\ensuremath{\begin{array}{cc}
-W^{\mathrm{sim}}= & 207.3\pm2.19\\
+W^{\mathrm{sim}}= & 207.3\pm2.2\\
 W^{id}= & 38.2\\
@@
 \cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
-\multicolumn{2}{l|}{\textcolor{teal}{\small{}$62.05\pm0.15\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{teal}{\small{}37.17}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{teal}{\small{}3.18}} & \multirow{2}{*}{\textcolor{teal}{\small{}$107.4\pm1.37$}} &  & \tabularnewline
-\multicolumn{2}{r|}{\textcolor{teal}{\small{}$48.21\pm0.016$}} &  &  &  &  &  & \tabularnewline
+\multicolumn{2}{l|}{\textcolor{teal}{\small{}$62.05\pm0.15\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{teal}{\small{}37.17}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{teal}{\small{}3.18}} & \multirow{2}{*}{\textcolor{teal}{\small{}$107.4\pm1.4$}} &  & \tabularnewline
+\multicolumn{2}{r|}{\textcolor{teal}{\small{}$48.21\pm0.02$}} &  &  &  &  &  & \tabularnewline
 \cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
-\multirow{2}{*}{\textcolor{olive}{\small{}44.91}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{olive}{\small{}$23.75\pm0.057\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{olive}{\small{}3.82}} & \multirow{2}{*}{\textcolor{olive}{\small{}$106.7\pm1.51$}} &  & \tabularnewline
- &  & \multicolumn{2}{r|}{\textcolor{olive}{\small{}$35.91\pm0.010$}} &  &  & \multirow{8}{*}{{\small{}\hspace{-1em}}\textcolor{red}{\small{}$\left.\begin{array}{l}
+\multirow{2}{*}{\textcolor{olive}{\small{}44.91}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{olive}{\small{}$23.75\pm0.06\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{olive}{\small{}3.82}} & \multirow{2}{*}{\textcolor{olive}{\small{}$106.7\pm1.5$}} &  & \tabularnewline
+ &  & \multicolumn{2}{r|}{\textcolor{olive}{\small{}$35.911\pm0.010$}} &  &  & \multirow{8}{*}{{\small{}\hspace{-1em}}\textcolor{red}{\small{}$\left.\begin{array}{l}
 \\
@@
 \end{array}\right\rbrace \rotatebox{90}{\hspace{-5em}\ensuremath{\begin{array}{cc}
-W^{\mathrm{sim}}= & 222.3\pm2.43\\
+W^{\mathrm{sim}}= & 222.3\pm2.5\\
 W^{\mathrm{id}}= & 43.8\ {\color{red}{\scriptstyle (41.0)}}\\
@@
 \cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
-\multicolumn{2}{l|}{\textcolor{olive}{\small{}$43.46\pm0.12\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{olive}{\small{}24.27}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{olive}{\small{}3.91}} & \multirow{2}{*}{\textcolor{olive}{\small{}$106.4\pm1.13$}} &  & \tabularnewline
-\multicolumn{2}{r|}{\textcolor{olive}{\small{}$30.80\pm0.008$}} &  &  &  &  &  & \tabularnewline
+\multicolumn{2}{l|}{\textcolor{olive}{\small{}$43.46\pm0.12\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{olive}{\small{}24.27}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{olive}{\small{}3.91}} & \multirow{2}{*}{\textcolor{olive}{\small{}$106.4\pm1.1$}} &  & \tabularnewline
+\multicolumn{2}{r|}{\textcolor{olive}{\small{}$30.795\pm0.008$}} &  &  &  &  &  & \tabularnewline
 \cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
-\multirow{2}{*}{\textcolor{red}{\small{}31.93}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{red}{\small{}$14.66\pm0.037\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{red}{\small{}4.20}} & \multirow{2}{*}{\textcolor{red}{\small{}$107.9\pm1.42$}} &  & \tabularnewline
- &  & \multicolumn{2}{r|}{\textcolor{red}{\small{}$25.30\pm0.006$}} &  &  &  & \multirow{8}{*}{{\small{}\hspace{-1em}}\textcolor{orange}{\small{}$\left.\begin{array}{l}
+\multirow{2}{*}{\textcolor{red}{\small{}31.93}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{red}{\small{}$14.66\pm0.04\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{red}{\small{}4.20}} & \multirow{2}{*}{\textcolor{red}{\small{}$107.9\pm1.4$}} &  & \tabularnewline
+ &  & \multicolumn{2}{r|}{\textcolor{red}{\small{}$25.297\pm0.006$}} &  &  &  & \multirow{8}{*}{{\small{}\hspace{-1em}}\textcolor{orange}{\small{}$\left.\begin{array}{l}
 \\
@@
 \end{array}\right\rbrace \rotatebox{90}{\hspace{-5em}\ensuremath{\begin{array}{cc}
-W^{\mathrm{sim}}= & 218.7\pm2.19\\
+W^{\mathrm{sim}}= & 218.7\pm2.2\\
 W^{id}= & 66.6\ {\scriptstyle (22.0)}\\
@@
 \cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
-\multicolumn{2}{l|}{\textcolor{red}{\small{}$30.03\pm0.084\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{red}{\small{}14.55}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{red}{\small{}$\begin{array}{c}
+\multicolumn{2}{l|}{\textcolor{red}{\small{}$30.03\pm0.08\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{red}{\small{}14.55}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{red}{\small{}$\begin{array}{c}
 4.17\\
@@
 \end{array}$}} & \multirow{2}{*}{\textcolor{red}{\small{}$\begin{array}{c}
-115.6\pm0.92\\
+115.6\pm0.9\\
 {\scriptstyle (57.3)}
@@
 \multicolumn{2}{r|}{\textcolor{red}{\small{}$\begin{array}{c}
-18.59\pm0.004\,\\
+18.585\pm0.004\,\\
 {\scriptstyle (22.32)}
@@
 \cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
-\multirow{2}{*}{\textcolor{orange}{\small{}22.30}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{orange}{\small{}$8.84\pm0.026\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{orange}{\small{}$\begin{array}{c}
+\multirow{2}{*}{\textcolor{orange}{\small{}22.30}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{orange}{\small{}$8.84\pm0.03\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{orange}{\small{}$\begin{array}{c}
 4.75\\
@@
 \end{array}$}} & \multirow{2}{*}{\textcolor{orange}{\small{}$\begin{array}{c}
-108.1\pm1.26\\
+108.1\pm1.3\\
 {\scriptstyle (68.3)}
@@
  &  & \multicolumn{2}{r|}{\textcolor{orange}{\small{}$\begin{array}{c}
-\text{17.95}\pm\text{0.004}\\
+\text{17.945}\pm\text{0.004}\\
 {\scriptstyle (14.56)}
@@
 \end{array}\right\rbrace \rotatebox{90}{\hspace{-5em}\ensuremath{\begin{array}{cc}
-W^{\mathrm{sim}}= & 227.5\pm2.23\\
+W^{\mathrm{sim}}= & 227.5\pm2.3\\
 W^{id}= & 69.7\\
@@
 \cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
-\multicolumn{2}{l|}{\textcolor{orange}{\small{}$20.74\pm0.064\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{orange}{\small{}8.83}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{orange}{\small{}$4.71$}} & \multirow{2}{*}{\textcolor{orange}{\small{}$110.8\pm0.77$}} &  & \tabularnewline
-\multicolumn{2}{r|}{\textcolor{orange}{\small{}$11.08\pm0.002$}} &  &  &  &  &  & \tabularnewline
+\multicolumn{2}{l|}{\textcolor{orange}{\small{}$20.74\pm0.06\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{orange}{\small{}8.83}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{orange}{\small{}$4.71$}} & \multirow{2}{*}{\textcolor{orange}{\small{}$110.8\pm0.8$}} &  & \tabularnewline
+\multicolumn{2}{r|}{\textcolor{orange}{\small{}$11.082\pm0.002$}} &  &  &  &  &  & \tabularnewline
 \cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
-\multirow{2}{*}{\textcolor{magenta}{\small{}10.90}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{magenta}{\small{}$3.00\pm0.01\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{magenta}{\small{}6.08}} & \multirow{2}{*}{\textcolor{magenta}{\small{}$106.9\pm1.05$}} &  & \tabularnewline
- &  & \multicolumn{2}{r|}{\textcolor{magenta}{\small{}9.01$\pm$0.002}} &  &  &  & \tabularnewline
+\multirow{2}{*}{\textcolor{magenta}{\small{}10.90}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{magenta}{\small{}$3.00\pm0.01\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{magenta}{\small{}6.08}} & \multirow{2}{*}{\textcolor{magenta}{\small{}$106.9\pm1.1$}} &  & \tabularnewline
+ &  & \multicolumn{2}{r|}{\textcolor{magenta}{\small{}9.011$\pm$0.002}} &  &  &  & \tabularnewline
 \cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
-\multicolumn{2}{l|}{\textcolor{magenta}{\small{}$9.83\pm0.046\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{magenta}{\small{}3.12}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{magenta}{\small{}5.78}} & \multirow{2}{*}{\textcolor{magenta}{\small{}$119.4\pm0.97$}} &  & \tabularnewline
-\multicolumn{2}{r|}{\textcolor{magenta}{\small{}$3.86\pm0.001$}} &  &  &  &  &  & \tabularnewline
+\multicolumn{2}{l|}{\textcolor{magenta}{\small{}$9.83\pm0.05\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{magenta}{\small{}3.12}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{magenta}{\small{}5.78}} & \multirow{2}{*}{\textcolor{magenta}{\small{}$119.4\pm1.0$}} &  & \tabularnewline
+\multicolumn{2}{r|}{\textcolor{magenta}{\small{}$3.862\pm0.001$}} &  &  &  &  &  & \tabularnewline
 \end{tabular*}
@@
 \caption{The estimates of the efficiency of the desalination process. All the units are calculated per one mol of gel segments. Values in brackets
-are the estimates corresponding to crossection of 'red' and 'orange' lines on the plots of figures \ref{fig: PV and CV} and \ref{fig: NV and CN}
-}
+are the estimates corresponding to crossection of 'red' and 'orange' lines on the plots of Figures \ref{fig: PV and CV} and \ref{fig: NV and CN}
+\label{tab: table}}
 \end{table}

### 2022-07-07 esi.tex
nex expression for c_s^prime

@@
 
-\begin{equation}
-N_{Cl^{-}}^{(gel)} = \frac{\frac{\NA \Vout^{2}}{2} + N_{pairs} \Vgel^{2} - \frac{\Vout \sqrt{N^{{(gel)}}_{A^{-}}^{2} \Vout^{2} + 4 N^{{(gel)}}_{A^{-}} N_{pairs} \Vgel^{2} + 4 N_{pairs}^{2} \Vgel^{2}}}{2}}{\Vgel^{2} - \Vout^{2}}
-\end{equation}
+%\begin{equation}
+%N_{Cl^{-}}^{(gel)} = \frac{\frac{\NA \Vout^{2}}{2} + N_{pairs} \Vgel^{2} - \frac{\Vout \sqrt{N^{{(gel)}}_{A^{-}}^{2} \Vout^{2} + 4 N^{{(gel)}}_{A^{-}} N_{pairs} \Vgel^{2} + 4 N_{pairs}^{2} \Vgel^{2}}}{2}}{\Vgel^{2} - \Vout^{2}}
+%\end{equation}
 
@@
 \begin{equation*}
-    c_s^\prime = \frac{\sqrt{4\alpha^{2} c_{p}^{2} \left(1-\gamma\right)^{2} + \alpha c_{p} c_{s} \gamma^{2} + c_{s}^{2} \gamma^{2}}-\frac{\alpha c_{p} \left(1-\gamma\right)}{2} - c_{s} \left(1-\gamma\right)}{\gamma^{2} - \left(1-\gamma\right)^{2}}
+    %c_s^\prime = \frac{\sqrt{4\alpha^{2} c_{p}^{2} \left(1-\gamma\right)^{2} + \alpha c_{p} c_{s} \gamma^{2} + c_{s}^{2} \gamma^{2}}-\frac{\alpha c_{p} \left(1-\gamma\right)}{2} - c_{s} \left(1-\gamma\right)}{\gamma^{2} - \left(1-\gamma\right)^{2}}
+
+    c_s^\prime =\frac{- V c_{s} \left(V - V_{gel}\right) - \frac{\alpha \left(V - V_{gel}\right)}{2} + \sqrt{V^{2} V_{gel}^{2} c_{s}^{2} + V V_{gel}^{2} \alpha c_{s} + \frac{\alpha^{2} \left(V - V_{gel}\right)^{2}}{4}}}{V_{gel}^{2} - \left(V - V_{gel}\right)^{2}}
+
 \end{equation*}

### 2022-07-07 sympy_donnan.py
symbolic calculation for donnan

@@ -1,5 +1,5 @@
 # %%
-from sympy import Symbol, Eq, solve
+from sympy import Symbol, Eq, solve, sqrt, latex
 # KNOWN
 N_pairs = Symbol("N_pairs", positive=True)  # number of all particles
 # v= Symbol("v", positive = True) #relative volume of the gel
@@ -17,16 +17,36 @@ mass_law
 # %%
 Anions_gel = solve(mass_law, x)[0]
 Anions_gel
+
 # %%
 print(Anions_gel)
 #%%
-c_s_0 = Symbol("c_s0", positive=True)  # init salt conc
-V_gel_0 = Symbol("V_gel0", positive=True)  # init salt conc
-v = Symbol("v", positive=True)  # compression
-c_gel_0 = Symbol("c_gel0", positive=True)
-c_gel = Symbol("c_salt", positive=True)
-c_s_reservoir = Symbol("c_salt^reservoir", positive=True)
-
+c_s_0 = Symbol("c_s", positive=True)  # init salt conc
+V_gel_0 = Symbol("V", positive=True)  # init salt conc
+c_p =  Symbol("c_p", positive=True) # gel init molar volume
+alpha =  Symbol("alpha", positive=True) # gel ionization degree
+gamma =  Symbol("gamma", positive=True) # gel compression
+Anions_gel_inf = sqrt(A_fixed**2 + 4*c_s_0**2*V_gel_0**2)/2 - A_fixed/2
+Anions_gel_inf
 #%%
 Anions_gel.subs(N_pairs, c_s_0*V_gel_0)
+# %%
+(Anions_gel**2).simplify()
+# %%
+Anion_salt = N_pairs-Anions_gel
+Anion_salt.simplify()
+# %%
+c_s=Anion_salt.subs(N_pairs, c_s_0*V_gel_0).subs(A_fixed, alpha*c_p*V_gel_0)/V_salt
+c_s = c_s.simplify()
+# %%
+c_s_on_gamma = c_s.subs(V_gel, gamma*V_gel_0).subs(V_salt,(1-gamma)*V_gel_0).simplify()
+
+# %%
+c_s_on_gamma.subs(gamma,0)
+# %%
+print(latex(c_s_on_gamma))
+# %%
+c_s = c_s.subs(V_salt, V_gel_0 - V_gel).subs(c_p, 1/V_gel_0).simplify()
+# %%
+print(latex(c_s))
 # %%

### 2022-07-08 esi.tex
Edited donnan section in esi

--- 2022-07-07 esi.tex
@@
 \subsection{Donnan equilibrium in finite volume reservoirs}
-\todo{mb we remove this section}
 Before we can explore any system properties and collect data the system has to be equilibrated.
-To achieve this we perform equilibration routine consist of sequence of Molecular Dynamics and Monte Carlo steps.
-%Here we describe our technique
+To achieve this we perform equilibration routine which consist of sequence of Molecular Dynamics and Monte Carlo steps.
 The result of equilibration is stationary of any observable such as pressure, end-to-end distance for polymer chains and ion distribution between reservoirs. 
-
 The success and the cost in terms of computational time for the equilibration process heavily depend on initial guess. 
@@
 \begin{equation}
-    \frac{\left(N_{pairs} - N_{Cl^{-}}^{(gel)}\right)^2}{V_{salt}^2} = \frac{N_{Cl^{-}}^{gel} (N^{{(gel)}}_{A^{-}} + N_{Cl^{-}}^{(gel)})}{V_{gel}^2}
+    \frac{\Ncl\out\Nna\out}{\Vout^2} = \frac{\Ncl\gel\Nna\gel}{\Vgel^2}
 \end{equation}
-where $N^{{(gel)}}_{A^{-}}$ is number of fixed anions in the box with the gel \ie acetic groups in the polymer gel.
-Solving this equation with respect to $N^{{(gel)}}_{A^{-}}$ gives us the distribution of the ions between two boxes.
+or
+\begin{equation}
+    \frac{\left(\Ncl\tot - \Ncl\gel\right)^2}{\Vout^2} = \frac{\Ncl\gel (\NA + \Ncl\gel)}{\Vgel^2}
+\end{equation}
+where $\NA$ is number of fixed anions in the box with the gel \ie acetic groups in the polymer gel.
+Solving this equation with respect to $\Ncl\gel$ gives us the distribution of the ions between two boxes.
+\begin{equation}
+\frac{- N - \frac{1}{2}\NA \gamma^{2} + \gamma \NA \sqrt{\left(\frac{N}{\NA}\right)^{2} + \frac{N}{\NA} +  \left(\frac{\gamma}{2}\right)^{2}}}{\gamma^{2} - 1 }
+\end{equation}
+where $\gamma = \Vout/\Vgel$ is a relative to initial volume compression.
 
-\begin{equation}
-N_{Cl^{-}}^{(gel)} = \frac{\frac{\NA \Vout^{2}}{2} + N_{pairs} \Vgel^{2} - \frac{\Vout \sqrt{N^{{(gel)}}_{A^{-}}^{2} \Vout^{2} + 4 N^{{(gel)}}_{A^{-}} N_{pairs} \Vgel^{2} + 4 N_{pairs}^{2} \Vgel^{2}}}{2}}{\Vgel^{2} - \Vout^{2}}
-\end{equation}
-
-\todoi{
-This paragraph moved from overleaf
-
-Compression of the gel in infinite reservoir does not  change its salinity, on the contrary, upon compression of the gel in closed reservoir salinity of separated liquid is decreasing (supernatant salinity), using the Donnan law formulated for finite reservoir salinity can be expressed as
-\begin{equation*}
-    c_s^\prime = \frac{\sqrt{4\alpha^{2} c_{p}^{2} \left(1-\gamma\right)^{2} + \alpha c_{p} c_{s} \gamma^{2} + c_{s}^{2} \gamma^{2}}-\frac{\alpha c_{p} \left(1-\gamma\right)}{2} - c_{s} \left(1-\gamma\right)}{\gamma^{2} - \left(1-\gamma\right)^{2}}
-\end{equation*}
-where $\gamma = V_{gel}/V_0$ is relative to initial volume compression.
-}
-\begin{eqnarray}
-    %N_{Cl^{-}}^{(gel)} = \frac{\frac{N^{{(gel)}}_{A^{-}} V_{salt}^{2}}{2} + N_{pairs} V_{gel}^{2} - \frac{V_{salt} \sqrt{N^{{(gel)}}_{A^{-}}^{2} V_{salt}^{2} + 4 N^{{(gel)}}_{A^{-}} N_{pairs} V_{gel}^{2} + 4 N_{pairs}^{2} V_{gel}^{2}}}{2}}{V_{gel}^{2} - V_{salt}^{2}}
-    \\
-    N_{Na^{+}}^{(gel)} = N^{{(gel)}}_{A^{-}} + N_{Cl^{-}}^{(gel)}
-    \\
-    N_{Cl^{-}}^{(salt)} = N_{Na^{+}}^{(gel)} = N_{pairs} - N_{Cl^{-}}^{(gel)}
-\end{eqnarray}
 \subsection{Sampling routine}

### 2022-07-08 gibbs.tex
Edited donnan section in esi

@@
 \end{equation*}
-where $\ccl\gel$ and $\cna\gel$ are the internal concentration of monovalent anions and cations, $\cs$ is the salinity of external solution $\Vgel$ is the gel molar volume (inverse density of gel segments) and $\alpha$ is ionization degree.
+where $\ccl\gel$ and $\cna\gel$ are the internal concentration of monovalent anions and cations, $\cs$ is the salinity of external solution,  $\Vgel$ is the gel molar volume (inverse density of gel segments) and $\alpha$ is ionization degree (in the case of our study $\alpha=1$).
 The $\pm$ sign in the formula accounts for the change between the cases of gel made of polyanion or polycation.
@@
 The gel partial pressure, $\Pgel$, is the pressure that needs to be applied to the gel via a solvent permeable filter to compress the gel to a specific molar volume, $\Vgel$. 
-By gel molar volume $\Vgel$ we assume the volume of the gel calculated per on mole of gel monomer units.
+By gel molar volume $\Vgel$ we assume the volume of the gel calculated per on mol of gel monomer units.
 
@@
 \begin{tabular*}{1\textwidth}{@{\extracolsep{\fill}}ll|lc|c|l|ll}
-\multicolumn{1}{l|}{$c_{s}^{0}$, mM} & $c_{s}^{5}$, mM & \multicolumn{1}{l|}{$n_{\cl}^{0}$, mM} & $n_{\cl}^{5}$, mM & $\Delta v$, l & $|W$\textbar , J/L & \multicolumn{2}{c}{$W^{id}$, J/L}\tabularnewline
+\multicolumn{1}{l|}{$c_{s}^{0}$, mM} & $c_{s}^{5}$, mM & \multicolumn{1}{l|}{$n_{\cl}^{0}$, mM} & $n_{\cl}^{5}$, mM & $\Delta \Vgel$, l & $|W$\textbar , J/l & \multicolumn{2}{c}{$W^{id}$, J/l}\tabularnewline
 \hline 

### 2022-07-19 ETI/cover_letter.tex
TOC figure

\documentclass[12pt]{dinbrief}

%\usepackage{english}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{color}

\usepackage[unicode=true, pdfusetitle, bookmarks=true, bookmarksnumbered=false, bookmarksopen=false, breaklinks=false, pdfborder={0 0 0}, pdfborderstyle={}, backref=false, colorlinks=true] {hyperref}

%\usepackage[pdfborder={0 0 0}]{hyperref}

\date{\today}

\place{Prague}

\nowindowtics
\nowindowrules

\newcommand{\theeditor}{Professor Ravi Naidu}

\newcommand{\thejournal}{\textit{Environmental Technology \& Innovation}}
\newcommand{\cl}{\mathrm{Cl^-}}
\newcommand{\na}{\mathrm{Na^+}}

\newcommand{\ie}{\textit{i.~e.} } 
\enabledraftstandard

\begin{document}

\begin{letter}{
Dr. Oleg Rud\\
Department of Physical and Macromolecular Chemistry\\
Faculty of Science, Charles University\\
Hlavova 8, 128 43 Prague, Czech Republic\\
E-mail: oleg.rud@natur.cuni.cz\\
}
\vspace*{-1.5cm}

\opening{Dear \theeditor,}

Herewith we would like to submit our manuscript: \textit{Water desalination using polyelectrolyte hydrogel. Gibbs ensemble modeling}
authored by
Mikhail Laktionov, Lucie Nová and Oleg V. Rud,
 to be considered for publication in \thejournal. 
In the submitted manuscript we modeled hydrogel in Gibbs ensemble, \ie in equilibrium with a small amount of aqueous solution, and demonstrated that the compression of the gel in such an ensemble slightly decreases the salinity of the outside solution. 
We employed this phenomenon and modeled the process of water desalination as a cascade of hydrogel swellings and compressions changing the outside salinity from $\sim 0.1$ to 0.01 mol/l.

We believe that our work brings new insights into the complex problem of seawater desalination
that fits within the scope of \thejournal, and that it will be of interest to its broad readership.

\vspace{5ex}

Yours sincerely,\\
on behalf of all co-authors,

\hspace{80ex}\ O.V. Rud\\

%The advantage of the proposed desalination procedure over the forward osmosis is that the gel acts both as a draw solute and as a separation membrane. 
%That helps to avoid various blocking phenomena (characteristic of membrane processes), which required a regular chemical and mechanical cleaning.
%Moreover, the relatively low pressures needed for hydrogel compression allow to  maintain the hydrogel mechanical properties and integrity for its reuse in a serial cycle.

\end{letter}
\end{document}

### 2022-07-19 gibbs.tex
TOC figure

@@
 
-\affiliation{Department of Physical and Macromolecular Chemistry, Faculty of Science,
-Charles University in Prague, Czech Republic}
-
+\affiliation{Department of Physical and Macromolecular Chemistry, Faculty of Science, Charles University in Prague, Czech Republic}
 \alsoaffiliation[imc]{Institute of Macromolecular Compounds of Russian Academy of Sciences,
@@
 \begin{figure*}[t]
-\centering \includegraphics[width=0.7\textwidth]{figures/simgibbs}\caption{Diamond-like network in the simulation box. Color code represents
+\centering \includegraphics[width=0.7\textwidth]{{figures/simgibbs}.pdf}\caption{Diamond-like network in the simulation box. Color code represents
 the individual ion types (red: $\na$, blue: $\cl$, yellow: $\ca$)
@@
 \subfloat[Open system \label{fig: open}]
-{\includegraphics[width=0.5\textwidth]{figures/gc}}
+{\includegraphics[width=0.5\textwidth]{figures/gc.pdf}}
 \subfloat[Closed system \label{fig: closed}]
-{\includegraphics[width=0.5\textwidth]{figures/gibbs}}
+{\includegraphics[width=0.5\textwidth]{figures/gibbs.pdf}}
 \caption{Diamond-like network in the simulation box. Color code represents
@@
 \subfloat[The gel partial pressure vs gel molar volume \label{fig: PV}]
-{\includegraphics[width=0.48\textwidth]{figures/fig_PV_pub}}
+{\includegraphics[width=0.48\textwidth]{figures/fig_PV_pub.pdf}}
 \hspace{0.02\textwidth}
 \subfloat[Supernate salinity vs gel molar volume\label{fig: CV}]
-{\includegraphics[width=0.48\textwidth]{figures/fig_CV_pub}}
+{\includegraphics[width=0.48\textwidth]{figures/fig_CV_pub.pdf}}
 \caption{
@@
 \subfloat[Pressure vs gel molar volume \label{fig: NV}]
-{\includegraphics[width=0.49\textwidth]{figures/fig_NV_pub}}
+{\includegraphics[width=0.49\textwidth]{figures/fig_NV_pub.pdf}}
 \subfloat[Salinity vs gel molar volume\label{fig: CN}]
-{\includegraphics[width=0.495\textwidth]{figures/fig_NVbox_mu_pub}}
+{\includegraphics[width=0.495\textwidth]{figures/fig_NVbox_mu_pub.pdf}}
 \caption{The compression of the gel in \emph{open system} (solid lines) and in \emph{closed system} (dotted lines). 
@@
 \section{Conclusions}
-We have modeled the compression of the gel in thermodynamic equilibrium with the reservoir of limited amount of water.
-We have shown that in case of gel made of strong polyelectrolyte, the compression always lead to decrease of the surrounding salinity.
-We have modeled the process of water desalination combining two processes: 
-(1) the swelling of the gel in \emph{open} system, exchanging ions with big reservoir at constant salinity. 
-(2) the compression of the gel in \emph{closed} system, when the gel affect the salinity in surrounding solution.
-We estimated the energy needed to produce one liter of water and have show that the method 
-%at least theoretically 
-may compete with the modern technologies used in modern industry.
+We have modeled the compression of the gel in thermodynamic equilibrium with the reservoir of the limited amount of water.
+We have shown that in the case of gel made of strong polyelectrolyte, the compression always decreases the surrounding salinity.
+We have modeled the process of water desalination by combining two processes: 
+(1) the swelling of the gel in \emph{open} system, exchanging ions with a big reservoir at constant salinity. 
+(2) the compression of the gel in \emph{closed} system, when the gel affects the salinity in the surrounding solution.
+We estimated the energy needed to produce one liter of water and have shown that the method may compete with the modern technologies used in modern industry.
 
@@
 
-This research was supported by the Czech Science Foundation (grant
-19-17847Y) (OR, LN, AK), Government of Russian Federation, grant number
-14.W03.31.0022. AK thanks the Grant Agency of Charles University for
-support (project 318120). Computational resources were supplied by
-the project ``e-Infrastruktura CZ'' (e-INFRA LM2018140) provided
-within the program Projects of Large Research, Development and Innovations
-Infrastructures.
+This research was supported by the Czech Science Foundation (grant 19-17847Y)
+Government of Russian Federation, grant number 14.W03.31.0022. 
+Computational resources were supplied by the project ``e-Infrastruktura CZ'' (e-INFRA LM2018140) provided within the program Projects of Large Research, Development and Innovations Infrastructures.
 

### 2022-08-12 Creta_ecis2022/presentation/beamer.tex
presentation ecis

\documentclass[10pt]{beamer}

\newcommand{\cl}{\mathrm{Cl^-}}
\newcommand{\br}{\mathrm{Br^-}}
\newcommand{\na}{\mathrm{Na^+}}
\newcommand{\h}{\mathrm{H^+}}
\newcommand{\ka}{\mathrm{K^+}}
\newcommand{\oh}{\mathrm{OH^-}}
\newcommand{\ca}{\mathrm{Ca^{2+}}}
\newcommand{\mg}{\mathrm{Mg^{2+}}}
\newcommand{\so}{\mathrm{SO_4^{2-}}}
\newcommand{\cs}{c_{\mathrm{s}}}
\newcommand{\gel}{^{gel}}
\newcommand{\Vgel}{V\gel}
\newcommand{\NA}{N_{\mathrm{A^-}}}
\newcommand{\pK}{\mathrm{p}K}
\newcommand{\pH}{\mathrm{pH}}
\newcommand{\cp}{c_\mathrm{p}}
\newcommand{\kT}{kT}
\usepackage{subfig}
\usetheme[progressbar=frametitle]{metropolis}
\usepackage{appendixnumberbeamer}

\usepackage{booktabs}
\usepackage[scale=2]{ccicons}

\usepackage{pgfplots}
\usepgfplotslibrary{dateplot}

\usepackage{xspace}
\newcommand{\themename}{\textbf{\textsc{metropolis}}\xspace}

\title{Modeling of weak polyelectrolyte hydrogels under compression. }
\subtitle{Implications for water desalination.}
% \date{\today}
\author{Oleg V. Rud}
\institute{Department of Physical and Macromolecular Chemistry, Faculty of Science, Charles University in Prague, Hlavova 8, Praha 2 128 00, Czech Republic
\\
\\
Institute of Macromolecular Compounds of Russian Academy of Sciences, 199004, Bolshoy pr. 31, Saint-Petersburg, Russia
}

% \titlegraphic{\hfill\includegraphics[height=1.5cm]{figures/cuni_logo.png}}

\begin{document}

\maketitle

%\begin{frame}{Table of contents}
%  \setbeamertemplate{section in toc}[sections numbered]
%  \tableofcontents%[hideallsubsections]
%\end{frame}

\section[Intro]{Introduction}

\begin{frame}[fragile]{Introduction}

	\begin{columns}[T,onlytextwidth]% COLUMNS
		\column{0.5\textwidth}
			\begin{figure}[t]
				{\includegraphics[width=\columnwidth]{{figures/gibbs_ca}.pdf}}
			\end{figure}

		\column{0.5\textwidth}
	\begin{itemize}
		\item Desalination
		\item Hydrogels for desalination 
		\item Forward osmosis
		\item Various stimuli: thermo-, pH-, electric-, magnetic-, light-indused gel collapse
		\item Manfred Wilhelm and Yu Chi experiment
	\end{itemize}

	\end{columns}% COLUMNS
	{\scriptsize 
	Fengler, C., Arens, L., Horn, H., Wilhelm, M. (2020). {\bf Desalination of Seawater Using Cationic Poly(acrylamide) Hydrogels and Mechanical Forces for Separation.} Macromolecular Materials and Engineering\\
	Yu, C., Wang, Y., Lang, X., Fan, S. (2016). {\bf A Method for Seawater Desalination via Squeezing Ionic Hydrogels.} Environmental Science and Technology}
\end{frame}

\begin{frame}[fragile]{Donnan prediction}
  \begin{columns}[T,onlytextwidth]% COLUMNS
    \column{0.35\textwidth}
\begin{figure}
\includegraphics[height=4.5cm]{figures/gel_donnan.png}
\caption{The compression of hydrogel  affects the ionic composition of supernatant}
\end{figure}

  \column{0.55\textwidth}

\begin{itemize}
\item Donnan equilibrium
$c_s^2 = c^{in}_{Na}\cdot c^{in}_{Cl}$
\item Electroneutrality
$\alpha N$ of self charges\\
$\alpha N$ of neutralizing counterions\\
$c^{in}_{Cl}$ of free ion pairs
\item
By compression to the dry state 
one can exclude brine of concentration
\begin{equation*}
N_{excl}/V=\begin{cases}
c_s^{in}<c_s,\\
\\
c_s^{in}+\alpha N/V_{gel}>c_s,
\end{cases}
\end{equation*}
\end{itemize}

  \end{columns}% COLUMNS

\end{frame}

\section{The model of a polyelectrolyte gel.}
\subsection{Langevin dynamics.}
\begin{frame}{Langevin dynamics. }
	\begin{columns}[T,onlytextwidth]% COLUMNS
		\column{0.4\textwidth}
			\begin{figure}
				\includegraphics[height=4.5cm]{figures/snapshot_cut.png}
				\caption{The snapshot of the hydrogel model for Langevin dynamics}
			\end{figure}   
		\column{0.01\textwidth}
		\column{0.6\textwidth}

		\begin{itemize}
			\item 
				Diamond network of point particles
			\item
				Lennard--Jones interaction
		\end{itemize}
		\begin{equation*}
			V_{LJ}(r) = 
			\begin{cases}
				4\varepsilon\left(\left(\frac{\sigma}{r-r_c}\right)^{12}-\left(\frac{\sigma}{r-r_c}\right)^{6}\right) & ,\ r<r_{c}\\
				0 & ,\ r>r_{c}
			\end{cases}
		\end{equation*}
		\begin{itemize}
			\item FENE potential
			\begin{equation*}
				V_{FENE}(r)=-\frac{1}{2}\Theta\Delta r_{max}^{2}\ln\left[1-\left(\frac{r-r_{0}}{\Delta r_{max}}\right)^{2}\right]
			\end{equation*}
			\item
				Electrostatic interaction
				\begin{equation*}
					V_{EL}=l_{B}k_{B}T\cdot\frac{q_{1}q_{2}}{r}
				\end{equation*}

		\end{itemize}

	\end{columns} % COLUMNS
\end{frame}

\subsection{Grand-reaction ensemble.}

{
\usebackgroundtemplate{\includegraphics[width=\paperwidth]{figures/grand_reaction_model.png}}
\begin{frame}{Grand-reaction ensemble.}
\begin{columns}[T,onlytextwidth]% COLUMNS
\column{0.3\textwidth}
\vspace{4.5cm}
Ionization equilibrium in \textbf{reaction} ensemble
\begin{equation*}
	\boxed{
		\mathrm{pA^- + H_3O^+ \leftrightarrows pAH}
	}
\end{equation*}

\column{0.4\textwidth}
Constant salinity 
\begin{equation*}
\boxed{c_s = c_\mathrm{Cl}^- = c_\mathrm{Na}^+}
\end{equation*}
The simulation box freely 
exchanges ions with reservoir as in \textbf{grand cannonical} ensemble
\end{columns} % COLUMNS
\vspace{0.5cm}
{\scriptsize Landsgesell, J., Hebbeker, P., Rud, O., Lunkad, R., Košovan, P., \\ Holm, C. (2020). 
{\bf Grand-Reaction Method for Simulations of Ionization \\
Equilibria Coupled to Ion Partitioning. }
Macromolecules, 53(8), 3007–3020. }
\end{frame}
}

{
\begin{frame}{Grand-reaction ensemble.}
	\textbf{Grand canonical ensemble}\\ 
	\vspace{1cm}
	The free energy of the grand-canonical ensemble for single particle type
	\begin{equation*}
		\boxed{
		\Omega=E-TS+\mu N\label{eq:Omega-GC}}
	\end{equation*}
	The entropy $S$ expands via Boltzmann formula
	\begin{columns}[T,onlytextwidth]% COLUMNS
		\column{0.5\textwidth}
			\begin{equation*}
				S=k_{B}\ln\frac{V^{N}}{N!}\label{eq:entropy}
			\end{equation*}
		\column{0.5\textwidth}
			\begin{equation*}
				\Omega=E-k_BT\ln\frac{V^N}{N!}+\mu N \label{eq: Omega_GC}
			\end{equation*}
	\end{columns} % COLUMNS
	The change of free energy associated with a sngle particle exchange is 
	\begin{equation*}
		\boxed{
		\Delta\Omega=k_BT\ln\left(V^{\xi}\frac{N!}{\left(N+\xi\right)!}\right)+\xi\mu+\Delta E\label{eq: DeltaG GC}}
	\end{equation*}
	{\tt accept if $\mathcal{R}^{\xi}<e^{\Delta\Omega/k_BT}$}
\end{frame}
}

{

\begin{frame}{Grand-reaction ensemble.}

	\begin{columns}[T,onlytextwidth]% COLUMNS
		\column{0.5\textwidth}
			\begin{figure}
				\includegraphics[height=4.cm]{figures/standard_states.pdf}
			\end{figure} 
		\column{0.5\textwidth}	
			\textbf{Reaction ensemble}\\ 
			\vspace{1cm}
			The reaction of an acidic unit 
			\begin{equation*}
				\mathrm{HA}\stackrel{K}{\leftrightarrows}\mathrm{A^-}+\mathrm{H^+}\label{eq: acid reaction}
			\end{equation*}
			\begin{equation*}
				\Omega=E-TS+\sum_i\left(\mu_i-\mu^\ominus_i\right) N_i\label{eq:Omega-RE}
			\end{equation*}
	\end{columns} % COLUMNS
	\vspace{1cm}
	Then the change of system free energy during a single reaction step
	\begin{equation*}
		\Delta\Omega=k_BT\ln\left(\prod_i V^{\nu_i\xi}\frac{N_i!}{\left(N_i+\nu_i\xi\right)!}\right)+
		\xi\left(\sum_i\nu_i\mu_i-\sum_i\nu_i\mu_i^\ominus\right)+\Delta E
		\label{eq: DeltaG RE one}
	\end{equation*}
	{\tt accept if $\mathcal{R}^{\xi}<e^{\Delta\Omega/k_BT}$}
\end{frame}
}

\begin{frame}{Grand-reaction ensemble.}
\begin{columns}[T,onlytextwidth]% COLUMNS
\column{0.7\textwidth}
\begin{equation*}\boxed{
\Delta\Omega=k_BT\ln\left(K^\xi\prod_i V^{\nu_i\xi}\frac{N_i!}{\left(N_i+\nu_i\xi\right)!}\right)+\Delta E}
\end{equation*}
\column{0.3\textwidth}
\begin{equation*}\boxed{
K = e^{-\sum_i\nu_i \mu_i^\ominus }} 
\end{equation*}
\end{columns} % COLUMNS

\vspace{0.6cm}
\begin{columns}[T,onlytextwidth]% COLUMNS
\column{0.5\textwidth}
	\begin{equation*}
		\mathrm{HA}\stackrel{K}{\leftrightarrows}\mathrm{A^-}+\mathrm{H^+} 
	\end{equation*}
	\begin{equation*}
		K= \mu_\h^\ominus+\mu_\mathrm{A^-}^\ominus - \mu_\mathrm{HA}^\ominus
	\end{equation*}
	\vspace{0.2cm}
\begin{equation*}
\emptyset \leftrightarrows  \na  +\cl
\end{equation*}
\begin{equation*}
K= \mu_\na+\mu_\cl
\end{equation*}
\vspace{0.2cm}
\begin{equation*}
\emptyset \leftrightarrows \ca + 2\cl
\end{equation*}
\begin{equation*}
K= 2\mu_\ca+\mu_\cl
\end{equation*}
\column{0.5\textwidth}
			\begin{figure}
				\includegraphics[height=4.cm]{figures/standard_states.pdf}
			\end{figure} 
\end{columns} % COLUMNS

\end{frame}

\begin{frame}{Grand-reaction ensemble.}

	\begin{columns}[T,onlytextwidth]% COLUMNS
		\column{0.5\textwidth}
			\begin{figure}
				\includegraphics[height=4.cm]{figures/standard_states.pdf}
			\end{figure} 
		\column{0.5\textwidth}	
			\textbf{Moderate pH conditions}\\ 
			\vspace{1cm}
			The reaction of an acidic unit 
			\begin{equation*}
				\mathrm{HA}\stackrel{K}{\leftrightarrows}\mathrm{A^-}+\mathrm{H^+}\label{eq: acid reaction}
			\end{equation*}
	Is happening only simultaneously with one of these two
	\begin{eqnarray*}
		\h&\leftrightarrows&\na \label{eq:hna} \\
		2\h&\leftrightarrows&\ca \label{eq:hca}
	\end{eqnarray*}

	\end{columns} % COLUMNS
\begin{eqnarray*}
\mathrm{HA}\stackrel{K'}{\leftrightarrows}\mathrm{A}^{-}+\na, &K' = K \exp(\mu_\h-\mu_\na) \\
2\mathrm{HA}\stackrel{K''}{\leftrightarrows}2\mathrm{A}^{-}+\ca, &K'' = K \exp(2\mu_\h-\mu_\ca)
\end{eqnarray*}
\end{frame}

\begin{frame}{Simulation protocol.}
\begin{enumerate}
\item {\tt Choose randomly: LMD, RE, or EX.}	\vspace{0.5cm}
\item {\tt Simulate the chosen, collecting 50 samples of: }
	\vspace{0.3cm}
	\begin{columns}[T,onlytextwidth]% COLUMNS
		\column{0.3\textwidth}
			\fbox{\parbox{\textwidth}{LMD: pressure, $P$, and $\{R_e\}$}}
		\column{0.3\textwidth}
	       		\fbox{\parbox{\textwidth}{RE: number of ionized segments, $\NA$}}
      		\column{0.3\textwidth}
        		\fbox{\parbox{\textwidth}{EX: number of salt ions, $N_\na$ and $N_\cl$}}
	\end{columns} % COLUMNS
	\vspace{0.5cm}
    {\tt Check the autocorrelation of each samples array.\\
    Pearson coefficient must be < 0.2. }
	\vspace{0.5cm}
\item {\tt Repeat collecting at least 200 averages from each process}.
\end{enumerate}
\end{frame}

\section{Results}

\begin{frame}{Monovalent salt. Compression.}
	\begin{figure}[t]
		\subfloat[low salinity, $c_s = 0.007$ mol/l]
			{\includegraphics[width=0.5\columnwidth]{{figures/gel_pressure_log_density_cs0.006_N_Samples200}.pdf}}
			{\includegraphics[width=0.5\columnwidth]{{figures/gel_alpha_log_density_cs0.006_N_Samples200}.pdf}}
		\subfloat[high salinity, $c_s = 0.209$ mol/l]
			{\includegraphics[width=0.5\columnwidth]{{figures/gel_pressure_log_density_cs0.15_N_Samples200}.pdf}}
			{\includegraphics[width=0.5\columnwidth]{{figures/gel_alpha_log_density_cs0.15_N_Samples200}.pdf}}
	\end{figure}
\end{frame}

\begin{frame}{Monovalent salt. ``No electrostatics'' vs ``Mean field theory''.}
	\begin{equation*}
		\frac{\alpha}{1-\alpha}10^{\pK-\pH} =\sqrt{1+\left(\frac{\alpha\cp}{2\cs}\right)^{2}} - \frac{\alpha\cp}{2\cs}
	\end{equation*}
	Together with electroneutrality condition it translates to
	\begin{equation*}
		-\frac{{{\alpha}^{3}}{\cp}}{{\cs}}+
		{\alpha}^{2}\left(\frac{{\cp}}{{\cs}}+\Theta-\frac{1}{\Theta}\right)+
		\frac{2 \alpha}{\Theta}-\frac{1}{\Theta}=0
	\end{equation*}
	where $\Theta = 10^{\pK-\pH}$.
	\begin{figure}
		\subfloat[low salinity, $c_s = 0.007$ mol/l]
			{\includegraphics[width=0.47\columnwidth]{{figures/gel_alpha_log_density_lB0.0_cs0.006_N_Samples200}.pdf}}
\subfloat[high salinity, $c_s = 0.209$ mol/l]
			{\includegraphics[width=0.47\columnwidth]{{figures/gel_alpha_log_density_lB0.0_cs0.15_N_Samples200}.pdf}}
	\end{figure}
\end{frame}

\begin{frame}{Monovalent salt. Desalination effect.}

	\begin{figure}[t]
		{\includegraphics[width=0.5\columnwidth]{{figures/gibbs3}.pdf}}
		\caption{
			Schematic illustration of the hydrogel being compressed isotropically by pressure $\Delta P$ 
			from the initial volume at free swelling equilibrium, $V_0$ to a volume $\Vgel$. 
			Simultaneously, the gel exchanges small ions with a reservoir solution of salinity $\cs$.}
	\end{figure}
\end{frame}

\begin{frame}{Monovalent salt. Desalination effect.}
	\begin{figure}[t]
		\subfloat[low salinity, $c_s = 0.007$ mol/l]
			{\includegraphics[width=0.5\columnwidth]{{figures/gel_Na_log_density_cs0.006_N_Samples200}.pdf}}
			{\includegraphics[width=0.5\columnwidth]{{figures/gel_Cl_log_density_cs0.15_N_Samples200}.pdf}}
		\subfloat[high salinity, $c_s = 0.209$ mol/l]
			{\includegraphics[width=0.5\columnwidth]{{figures/gel_Na_log_density_cs0.15_N_Samples200}.pdf}}
			{\includegraphics[width=0.5\columnwidth]{{figures/gel_Cl_log_density_cs0.15_N_Samples200}.pdf}}
	\end{figure}
\end{frame}

\begin{frame}{Divalent salt. }
	\begin{columns}[T,onlytextwidth]% COLUMNS
		\column{0.55\textwidth}
			\begin{figure}
				\includegraphics[width=1\columnwidth]{figures/vmdscene.png}
			\end{figure} 		
		\column{0.4\textwidth}
			{\Large Seawater model: }
			\begin{eqnarray*}
				c_\cl&=&0.54\text{ mol/l} \\
				&&\text{of negative ions} 
				%c_\so&=&0.028 \text{ mol/l of negative divalent ions} 
			\end{eqnarray*}
			\begin{eqnarray*}
				c_\na&=&0.47\text{ mol/l} \\
				&&\text{of positive ions} 
			\end{eqnarray*}

			\begin{eqnarray*}
				c_\ca&=&0.063\text{ mol/l} \\
				&&\text{of positive divalent ions}  \\
			\end{eqnarray*}

	\end{columns}
	\begin{columns}[T,onlytextwidth]% COLUMNS
		\column{0.5\textwidth}
			\begin{eqnarray*}
				c_{\na}&\simeq0.87\cdot c_{\cl} \\
				c_{\ca}&\simeq0.117\cdot c_{\cl} \\
				%c_{\so}&\simeq&c_{\cl}\cdot0.0282/0.55=0.051c_{\cl} 
			\end{eqnarray*}
		\column{0.5\textwidth}
			\begin{eqnarray*}
				\mu_{\na}&=&\mu_{\cl} - 0.139\kT\\
				\mu_{\ca}&=&\mu_{\cl} - 2.03\kT\\
			\end{eqnarray*}	
	\end{columns}		
\end{frame}
\begin{frame}{Divalent salt. Compression.}

	\begin{figure}[t]
		\subfloat[low salinity, $c_s = 0.007$ mol/l]
			{\includegraphics[width=0.5\columnwidth]{{figures/gel_pressure_log_density_pCa3.16_cs0.006_N_Samples200}.pdf}}
			{\includegraphics[width=0.5\columnwidth]{{figures/gel_alpha_log_density_pCa3.16_cs0.006_N_Samples200}.pdf}}			
		\subfloat[high salinity, $c_s = 0.209$ mol/l]
			{\includegraphics[width=0.5\columnwidth]{{figures/gel_pressure_log_density_pCa1.77_cs0.15_N_Samples200}.pdf}}
			{\includegraphics[width=0.5\columnwidth]{{figures/gel_alpha_log_density_pCa1.77_cs0.15_N_Samples200}.pdf}}
	\end{figure}
\end{frame}

\begin{frame}{Divalent salt. Desalination or ion exchange.}
Low salinity $c_\cl = 0.007$
	\begin{figure}
	\subfloat{\includegraphics[width=0.5\columnwidth]{{figures/gel_Cl_log_density_pCa3.16_cs0.006_N_Samples200}.pdf}}
	\subfloat{\includegraphics[width=0.5\columnwidth]{{figures/gel_Na_log_density_pCa3.16_cs0.006_N_Samples200}.pdf}}
	\vspace{0.3cm}
	\\
	\subfloat{\includegraphics[width=0.5\columnwidth]{{figures/gel_Ca_log_density_pCa3.16_cs0.006_N_Samples200}.pdf}}
	\end{figure}

\end{frame}

\begin{frame}{Divalent salt. Desalination or ion exchange.}
High salinity $c_\cl = 0.263$
	\begin{figure}
	\subfloat{\includegraphics[width=0.5\columnwidth]{{figures/gel_Cl_log_density_pCa1.77_cs0.15_N_Samples200}.pdf}}
	\subfloat{\includegraphics[width=0.5\columnwidth]{{figures/gel_Na_log_density_pCa1.77_cs0.15_N_Samples200}.pdf}}
	\vspace{0.3cm}	
	\\
	\subfloat{\includegraphics[width=0.5\columnwidth]{{figures/gel_Ca_log_density_pCa1.77_cs0.15_N_Samples200}.pdf}}
	\end{figure}

\end{frame}

\section{Conclusion}

\begin{frame}{Summary}
\begin{enumerate}
\item monovalent ions
	\begin{enumerate}
		\item ionization of the hydrogel is suppressed as compared to predictions for monomeric acid, due 
			\begin{itemize}
				\item to the Donnan partitioning of H + ions; 
				\item to the electrostatic repulsion between charges of the gel.
			\end{itemize}
		\item the decrease of ionisation degree is much less significant than previously estimated using mean-feld models.
		\item decreasing the ionization of the gel upon compression may completely reverse the desalination effect forcing the gel to  release counterions upon compression instead of absorbing them.
	\end{enumerate}
\item with divalent ions
	\begin{enumerate}
		\item the electrostatics is almost completelly screened
		\item alpha does not change versus compression
		\item The compression of gel in presence of divalent ions works as ion exchanger of Ca ion by Na
	\end{enumerate}
\end{enumerate}
\end{frame}

{\setbeamercolor{palette primary}{fg=black, bg=yellow}
\begin{frame}[standout]
  Questions?
\end{frame}
}

\appendix

\begin{frame}{Monovalent salt. ``No electrostatics'' vs ``Mean field theory''.}
	\begin{figure}[t]
		\subfloat[low salinity, $c_s = 0.007$ mol/l]
			{\includegraphics[width=0.5\columnwidth]{{figures/gel_pressure_log_density_lB0.0_cs0.006_N_Samples200}.pdf}}
			{\includegraphics[width=0.5\columnwidth]{{figures/gel_alpha_log_density_lB0.0_cs0.006_N_Samples200}.pdf}}
		\subfloat[high salinity, $c_s = 0.209$ mol/l]
			{\includegraphics[width=0.5\columnwidth]{{figures/gel_pressure_log_density_lB0.0_cs0.15_N_Samples200}.pdf}}
			{\includegraphics[width=0.5\columnwidth]{{figures/gel_alpha_log_density_lB0.0_cs0.15_N_Samples200}.pdf}}
	\end{figure}
\end{frame}
\end{document}
\begin{frame}[fragile]{Typography}
      \begin{verbatim}The theme provides sensible defaults to
\emph{emphasize} text, \alert{accent} parts
or show \textbf{bold} results.\end{verbatim}

  \begin{center}becomes\end{center}

  The theme provides sensible defaults to \emph{emphasize} text,
  \alert{accent} parts or show \textbf{bold} results.
\end{frame}

\begin{frame}{Font feature test}
  \begin{itemize}
    \item Regular
    \item \textit{Italic}
    \item \textsc{SmallCaps}
    \item \textbf{Bold}
    \item \textbf{\textit{Bold Italic}}
    \item \textbf{\textsc{Bold SmallCaps}}
    \item \texttt{Monospace}
    \item \texttt{\textit{Monospace Italic}}
    \item \texttt{\textbf{Monospace Bold}}
    \item \texttt{\textbf{\textit{Monospace Bold Italic}}}
  \end{itemize}
\end{frame}

\begin{frame}{Lists}
  \begin{columns}[T,onlytextwidth]% COLUMNS
    \column{0.33\textwidth}
      Items
      \begin{itemize}
        \item Milk \item Eggs \item Potatos
      \end{itemize}

    \column{0.33\textwidth}
      Enumerations
      \begin{enumerate}
        \item First, \item Second and \item Last.
      \end{enumerate}

    \column{0.33\textwidth}
      Descriptions
      \begin{description}
        \item[PowerPoint] Meeh. \item[Beamer] Yeeeha.
      \end{description}
  \end{columns}
\end{frame}
\begin{frame}{Animation}
  \begin{itemize}[<+- | alert@+>]
    \item \alert<4>{This is\only<4>{ really} important}
    \item Now this
    \item And now this
  \end{itemize}
\end{frame}
\begin{frame}{Figures}
  \begin{figure}
    \newcounter{density}
    \setcounter{density}{20}
    \begin{tikzpicture}
      \def\couleur{alerted text.fg}
      \path[coordinate] (0,0)  coordinate(A)
                  ++( 90:5cm) coordinate(B)
                  ++(0:5cm) coordinate(C)
                  ++(-90:5cm) coordinate(D);
      \draw[fill=\couleur!\thedensity] (A) -- (B) -- (C) --(D) -- cycle;
      \foreach \x in {1,...,40}{%
          \pgfmathsetcounter{density}{\thedensity+20}
          \setcounter{density}{\thedensity}
          \path[coordinate] coordinate(X) at (A){};
          \path[coordinate] (A) -- (B) coordinate[pos=.10](A)
                              -- (C) coordinate[pos=.10](B)
                              -- (D) coordinate[pos=.10](C)
                              -- (X) coordinate[pos=.10](D);
          \draw[fill=\couleur!\thedensity] (A)--(B)--(C)-- (D) -- cycle;
      }
    \end{tikzpicture}
    \caption{Rotated square from
    \href{http://www.texample.net/tikz/examples/rotated-polygons/}{texample.net}.}
  \end{figure}
\end{frame}
\begin{frame}{Tables}
  \begin{table}
    \caption{Largest cities in the world (source: Wikipedia)}
    \begin{tabular}{lr}
      \toprule
      City & Population\\
      \midrule
      Mexico City & 20,116,842\\
      Shanghai & 19,210,000\\
      Peking & 15,796,450\\
      Istanbul & 14,160,467\\
      \bottomrule
    \end{tabular}
  \end{table}
\end{frame}
\begin{frame}{Blocks}
  Three different block environments are pre-defined and may be styled with an
  optional background color.

  \begin{columns}[T,onlytextwidth]% COLUMNS
    \column{0.5\textwidth}
      \begin{block}{Default}
        Block content.
      \end{block}

      \begin{alertblock}{Alert}
        Block content.
      \end{alertblock}

      \begin{exampleblock}{Example}
        Block content.
      \end{exampleblock}

    \column{0.5\textwidth}

      \metroset{block=fill}

      \begin{block}{Default}
        Block content.
      \end{block}

      \begin{alertblock}{Alert}
        Block content.
      \end{alertblock}

      \begin{exampleblock}{Example}
        Block content.
      \end{exampleblock}

  \end{columns}% COLUMNS
\end{frame}
\begin{frame}{Math}
  \begin{equation*}
    e = \lim_{n\to \infty} \left(1 + \frac{1}{n}\right)^n
  \end{equation*}
\end{frame}
\begin{frame}{Line plots}
  \begin{figure}
    \begin{tikzpicture}
      \begin{axis}[
        mlineplot,
        width=0.9\textwidth,
        height=6cm,
      ]

        \addplot {sin(deg(x))};
        \addplot+[samples=100] {sin(deg(2*x))};

      \end{axis}
    \end{tikzpicture}
  \end{figure}
\end{frame}
\begin{frame}{Bar charts}
  \begin{figure}
    \begin{tikzpicture}
      \begin{axis}[
        mbarplot,
        xlabel={Foo},
        ylabel={Bar},
        width=0.9\textwidth,
        height=6cm,
      ]

      \addplot plot coordinates {(1, 20) (2, 25) (3, 22.4) (4, 12.4)};
      \addplot plot coordinates {(1, 18) (2, 24) (3, 23.5) (4, 13.2)};
      \addplot plot coordinates {(1, 10) (2, 19) (3, 25) (4, 15.2)};

      \legend{lorem, ipsum, dolor}

      \end{axis}
    \end{tikzpicture}
  \end{figure}
\end{frame}
\begin{frame}{Quotes}
  \begin{quote}
    Veni, Vidi, Vici
  \end{quote}
\end{frame}

{%
\setbeamertemplate{frame footer}{My custom footer}
\begin{frame}[fragile]{Frame footer}
    \themename defines a custom beamer template to add a text to the footer. It can be set via
    \begin{verbatim}\setbeamertemplate{frame footer}{My custom footer}\end{verbatim}
\end{frame}
}

\begin{frame}{References}
  Some references to showcase [allowframebreaks] \cite{knuth92,ConcreteMath,Simpson,Er01,greenwade93}
\end{frame}

\section{Conclusion}

\begin{frame}{Summary}

  Get the source of this theme and the demo presentation from

  \begin{center}\url{github.com/matze/mtheme}\end{center}

  The theme \emph{itself} is licensed under a
  \href{http://creativecommons.org/licenses/by-sa/4.0/}{Creative Commons
  Attribution-ShareAlike 4.0 International License}.

  \begin{center}\ccbysa\end{center}

\end{frame}

{\setbeamercolor{palette primary}{fg=black, bg=yellow}
\begin{frame}[standout]
  Questions?
\end{frame}
}

\appendix

\begin{frame}[fragile]{Backup slides}
  Sometimes, it is useful to add slides at the end of your presentation to
  refer to during audience questions.

  The best way to do this is to include the \verb|appendixnumberbeamer|
  package in your preamble and call \verb|\appendix| before your backup slides.

  \themename will automatically turn off slide numbering and progress bars for
  slides in the appendix.
\end{frame}

\begin{frame}[allowframebreaks]{References}

  \bibliography{hydrogel}
  \bibliographystyle{abbrv}

\end{frame}

### 2022-08-12 Creta_ecis2022/presentation/join.sh

@@ -1,0 +1,1 @@
+pdftk slide0.pdf slide1.pdf slide2.pdf slide3.pdf slide4.pdf slide5.pdf slide5_1.pdf slide6.pdf slide7.pdf slide8.pdf slide9.pdf slide10.pdf slide11.pdf slide12.pdf slide13.pdf slide14.pdf  cat output  all.pdf

### 2022-08-26 MDPI/response_letter.tex
respnonse letter

\documentclass[12pt]{dinbrief}
%\usepackage{english}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{color}
\usepackage[textsize=small]{todonotes}

\usepackage[unicode=true, pdfusetitle, bookmarks=true, bookmarksnumbered=false, bookmarksopen=false, breaklinks=false, pdfborder={0 0 0}, pdfborderstyle={}, backref=false, colorlinks=true] {hyperref}

%\usepackage[pdfborder={0 0 0}]{hyperref}

\date{\today}

\place{Prague}

\nowindowtics
\nowindowrules

\newcommand{\theeditor}{Dr. David Díaz-Díaz}

\newcommand{\thejournal}{\textit{Gels }}
\newcommand{\cl}{\mathrm{Cl^-}}
\newcommand{\na}{\mathrm{Na^+}}

%\newcommand{\ie}{\textit{i.~e.} } 
\enabledraftstandard
\newcommand{\ie}{\textit{i.~e.} }
\newcommand{\cref}{c^{\ominus}}
%\newcommand{\cs}{c_{s}}
\newcommand{\kT}{k_\mathrm{B}T}
\newcommand{\kB}{k_\mathrm{B}}
\newcommand{\lb}{l_\mathrm{B}}
%\newcommand{\NA}{N_{\mathrm{A^-}}}
\newcommand{\NA}{N_{\mathrm{A}}}
\newcommand{\muna}{\mu_\mathrm{Na^+}}

\newcommand{\mucl}{\mu_\mathrm{Cl^-}}
\newcommand{\muca}{\mu_\mathrm{Ca^{2+}}}
\newcommand{\muh}{\mu_\mathrm{H^+}}
\newcommand{\mua}{\mu_\mathrm{A^-}}
\newcommand{\muha}{\mu_\mathrm{HA}}
\newcommand{\muoh}{\mu_\mathrm{OH}}

\newcommand{\cna}{c_\mathrm{Na^+}}
\newcommand{\ccl}{c_\mathrm{Cl^-}}
\newcommand{\cca}{c_\mathrm{Ca^{2+}}}
\newcommand{\ch}{c_\mathrm{H^+}}
\newcommand{\cp}{c_\mathrm{p}}
\newcommand{\nna}{n_\mathrm{Na^+}}
\newcommand{\ncl}{n_\mathrm{Cl^-}}
\newcommand{\Nna}{N_\mathrm{Na^+}}
\newcommand{\Ncl}{N_\mathrm{Cl^-}}

\newcommand{\ncleq}{\widetilde{N}_\mathrm{Cl^-}}
\newcommand{\nca}{N_\mathrm{Ca^{2+}}}

\newcommand{\superin}{^\mathrm{in}}
\newcommand{\subin}{_\mathrm{in}}
\newcommand{\subi}{_\mathrm{i}}

\newcommand{\gel}{^\mathrm{gel}}
\newcommand{\tot}{^\mathrm{tot}}
\newcommand{\out}{^{\mathrm{out}}}
\newcommand{\coh}{c_\mathrm{OH}}
\newcommand{\bulk}{^{\mathrm{b}}}
\renewcommand{\H}{\mathrm{H^+}}
\newcommand{\A}{\mathrm{A^-}}
\newcommand{\AH}{\mathrm{AH}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
%% A simple dot to overcome graphicx limitations
\newcommand{\lyxdot}{.}
\newcommand{\todoi}[1]{\todo[inline]{#1}}
\newcommand{\br}{\mathrm{Br^-}}
\newcommand{\h}{\mathrm{H^+}}
\newcommand{\ka}{\mathrm{K^+}}
\newcommand{\oh}{\mathrm{OH^-}}
\newcommand{\ca}{\mathrm{Ca^{2+}}}
\newcommand{\mg}{\mathrm{Mg^{2+}}}
\newcommand{\so}{\mathrm{SO_4^{2-}}}

\newcommand{\EI}{E_{\mathrm{I}}}
\newcommand{\EII}{E_{\mathrm{II}}}
\newcommand{\SI}{S_{\mathrm{I}}}
\newcommand{\SII}{S_{\mathrm{II}}}
\newcommand{\NI}{N_{\mathrm{I}}}
\newcommand{\NII}{N_{\mathrm{II}}}
\newcommand{\VI}{V_{\mathrm{I}}}
\newcommand{\VII}{V_{\mathrm{II}}}
\newcommand{\FI}{F_{\mathrm{I}}}
\newcommand{\FII}{F_{\mathrm{II}}}
\newcommand{\nnaI}{N^{\na}_{\mathrm{I}}}
\newcommand{\nclI}{N^{\cl}_{\mathrm{I}}}
\newcommand{\nnaII}{N^{\na}_{\mathrm{II}}}
\newcommand{\nclII}{N^{\cl}_{\mathrm{II}}}

\newcommand{\Ka}{K_{\mathrm{A}}}
\newcommand{\pKa}{\mathrm{p}\Ka}
\newcommand{\pK}{\mathrm{p}K}
\newcommand{\pH}{\mathrm{pH}}
\newcommand{\mol}{\mathrm{mol}}
\newcommand{\molperl}{\mathrm{mol/l}}
\newcommand{\kg}{\mathrm{kg}}
\newcommand{\res}{^{\mathrm{res}}}
\newcommand{\pHres}{\pH\res}
\newcommand{\pHgel}{\pH\gel}
\newcommand{\cs}{c_{\mathrm{s}}}
\newcommand{\csres}{\cs\res}
\newcommand{\Vgel}{V_\mathrm{gel}}
\newcommand{\Ngel}{N_\mathrm{gel}}
\newcommand{\Pgel}{\Pi}
\newcommand{\Pres}{P_\mathrm{res}}
\newcommand{\Pout}{P_\mathrm{out}}
\newcommand{\Vout}{V_\mathrm{out}}
\newcommand{\Vbox}{V_0}
\newcommand{\PE}{polyelectrolyte{}}

\begin{document}

\begin{letter}{
Dr. Oleg Rud\\
Department of Physical and Macromolecular Chemistry\\
Faculty of Science, Charles University\\
Hlavova 8, 128 43 Prague, Czech Republic\\
E-mail: oleg.rud@natur.cuni.cz\\
}
\vspace*{-1.5cm}

\opening{Dear \theeditor,}

In response to your e-mail from 23d August 2022, we hereby submit the revised
version, of our manuscript, entitled "Water desalination using polyelectrolyte hydrogel. Gibbs ensemble modeling''.

We carefully considered all reviewer comments and introduced changes in the manuscript in order to address them.
Below, we provide a point-by-point response to all reviewer comments, including a brief description of the modifications introduced in response to these comments.
Additionally, we provide a pdf version of the manuscript with the relevant changes highlighted in colour.

Main changes in the manuscript include:
\begin{itemize}
    \item 
    \item 
    \item 
    \item 
\end{itemize}

We believe that, after considering the modifications in response to reviewer comments, you will find our manuscript suitable for publication in Desalination.

On behalf of all authors,
with best regards\\
\\
Oleg V. Rud\\

%\closing{ \ 
%}

\end{letter}

% modify the page to use the space more efficiently
\addtolength{\textwidth}{1.5cm}
\addtolength{\textheight}{2.0cm}

\textbf{Reviewer 1}
\textit{}

\begin{enumerate}
\item \textit{The main findings of your results should be highlighted in abstract}

\item \textit{Please do not separate introduction in three sections combine with problem and technology you used and challenges and your solutions.}

\item \textit{In page 4 heading 2. (How to start with and ??)}.\\
Corrected.

\item \textit{All formula and models should be supported with reference for instant equation 3.}
Added todonote

\item \textit{In page 6, please remove the footer, it is not a book to describe issues below}.\\
Corrected. Now this sentence is appears in text (in brackets).

\item \textit{How do you think control factors in open system such as pressure and temperature}

\end{enumerate}

\textbf{Reviewer 2}
\textit{This manuscript is about creating a new model the thermodynamic equilibrium between coexisting phases of the gel and supernate aqueous solution.}
\begin{enumerate}

\item \textit{Abstract needs to re-write as and please follow the IMRAD instruction.}
\item \textit{There is introduction in the abstract, however, it needs to write more about the aim of this work, method, result and conclusion.}
\item \textit{Avoid to use word 'we' in the abstract as well as manuscript.}
\item \textit{line 247 in what table?}
\item \textit{Where is the method of this work?}
\item \textit{It is suggested that to carefully improve this manuscript as well as the writing and grammatical error.}
\item \textit{Please explain more detail about the process, how the process run and how the data could be explained and become more interesting for reader.}

\end{enumerate}

\textbf{Reviewer 2}

\textit{}
\begin{enumerate}
\item \textit{The full stop in the title should be revised.}
\item \textit{The abstract needs to be revised and be more attractive. The research gap, novelty and main findings should be concisely mentioned in the abstract.}
\item \textit{In this current shape, the manuscript looks like a report. The authors have to revise the flow of the context to attract the readers.}
\item \textit{The manuscript must be improved by checking once again in English and technical writing. }

\item \textit{The whole manuscript must be supported by enough recent references. Revise the whole context.}
\item \textit{The beginning of the introduction part must be revised to be more attractive.}
\item \textit{The authors can follow the following references to generally highlight the global contamination and environmental pollution problems at the beginning of the introduction part  \href{https://doi.org/10.1016/j.jwpe.2022.102847}{https://doi.org/10.1016/j.jwpe.2022.102847} ; \href{https://doi.org/10.1016/j.ceramint.2022.05.151}{https://doi.org/10.1016/j.ceramint.2022.05.151} ; 
\href{https://doi.org/10.3390/catal12050500}{https://doi.org/10.3390/catal12050500} ; 
\href{https://doi.org/10.1007/s11356-022-21160-7}{https://doi.org/10.1007/s11356-022-21160-7} ; 
\href{https://doi.org/10.3390/ma15134547}{https://doi.org/10.3390/ma15134547}. 
Then, highlight the water desalination technologies and Gibbs ensemble (\href{https://doi.org/10.3390/nano10020293}{https://doi.org/10.3390/nano10020293}).}
\item \textit{Authors should indicate a clear gap in knowledge which this study seeks to bridge, and potentially contribute to knowledge. }

\item \textit{L 125-126, meaningless sentence. Revise the whole context.}
\item \textit{All sections/subsections titles must be revised to be expressive.}
\item \textit{Statistical physics considerations including setup and calculations should be added.}
\item \textit{The authors should identify the limitations of this study and the recommended future studies in the conclusion part.
}
\end{enumerate}

%~ \bibliographystyle{unsrt}
%~ \bibliography{desalination}
\bibliographystyle{unsrt}
\bibliography{lit/gibbs}
\end{document}

### 2022-08-26 MDPI/MDPI_template/template.tex
respnonse letter

%  LaTeX support: latex@mdpi.com 
%  For support, please attach all files needed for compiling as well as the log file, and specify your operating system, LaTeX version, and LaTeX editor.

%=================================================================
\documentclass[journal,article,submit,pdftex,moreauthors]{Definitions/mdpi} 
% For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal and change "submit" to "accept". The document class line would be, e.g., \documentclass[preprints,article,accept,moreauthors,pdftex]{mdpi}. This is especially recommended for submission to arXiv, where line numbers should be removed before posting. For preprints.org, the editorial staff will make this change immediately prior to posting.

%--------------------
% Class Options:
%--------------------
%----------
% journal
%----------
% Choose between the following MDPI journals:
% acoustics, actuators, addictions, admsci, adolescents, aerospace, agriculture, agriengineering, agronomy, ai, algorithms, allergies, alloys, analytica, animals, antibiotics, antibodies, antioxidants, applbiosci, appliedchem, appliedmath, applmech, applmicrobiol, applnano, applsci, aquacj, architecture, arts, asc, asi, astronomy, atmosphere, atoms, audiolres, automation, axioms, bacteria, batteries, bdcc, behavsci, beverages, biochem, bioengineering, biologics, biology, biomass, biomechanics, biomed, biomedicines, biomedinformatics, biomimetics, biomolecules, biophysica, biosensors, biotech, birds, bloods, blsf, brainsci, breath, buildings, businesses, cancers, carbon, cardiogenetics, catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, chemproc, children, chips, cimb, civileng, cleantechnol, climate, clinpract, clockssleep, cmd, coasts, coatings, colloids, colorants, commodities, compounds, computation, computers, condensedmatter, conservation, constrmater, cosmetics, covid, crops, cryptography, crystals, csmf, ctn, curroncol, currophthalmol, cyber, dairy, data, dentistry, dermato, dermatopathology, designs, diabetology, diagnostics, dietetics, digital, disabilities, diseases, diversity, dna, drones, dynamics, earth, ebj, ecologies, econometrics, economies, education, ejihpe, electricity, electrochem, electronicmat, electronics, encyclopedia, endocrines, energies, eng, engproc, ent, entomology, entropy, environments, environsciproc, epidemiologia, epigenomes, est, fermentation, fibers, fintech, fire, fishes, fluids, foods, forecasting, forensicsci, forests, foundations, fractalfract, fuels, futureinternet, futureparasites, futurepharmacol, futurephys, futuretransp, galaxies, games, gases, gastroent, gastrointestdisord, gels, genealogy, genes, geographies, geohazards, geomatics, geosciences, geotechnics, geriatrics, hazardousmatters, healthcare, hearts, hemato, heritage, highthroughput, histories, horticulturae, humanities, humans, hydrobiology, hydrogen, hydrology, hygiene, idr, ijerph, ijfs, ijgi, ijms, ijns, ijtm, ijtpp, immuno, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jal, jcdd, jcm, jcp, jcs, jdb, jeta, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmp, jmse, jne, jnt, jof, joitmc, jor, journalmedia, jox, jpm, jrfm, jsan, jtaer, jzbg, kidney, kidneydial, knowledge, land, languages, laws, life, liquids, literature, livers, logics, logistics, lubricants, lymphatics, machines, macromol, magnetism, magnetochemistry, make, marinedrugs, materials, materproc, mathematics, mca, measurements, medicina, medicines, medsci, membranes, merits, metabolites, metals, meteorology, methane, metrology, micro, microarrays, microbiolres, micromachines, microorganisms, microplastics, minerals, mining, modelling, molbank, molecules, mps, msf, mti, muscles, nanoenergyadv, nanomanufacturing, nanomaterials, ncrna, network, neuroglia, neurolint, neurosci, nitrogen, notspecified, nri, nursrep, nutraceuticals, nutrients, obesities, oceans, ohbm, onco, oncopathology, optics, oral, organics, organoids, osteology, oxygen, parasites, parasitologia, particles, pathogens, pathophysiology, pediatrrep, pharmaceuticals, pharmaceutics, pharmacoepidemiology, pharmacy, philosophies, photochem, photonics, phycology, physchem, physics, physiologia, plants, plasma, pollutants, polymers, polysaccharides, poultry, powders, preprints, proceedings, processes, prosthesis, proteomes, psf, psych, psychiatryint, psychoactives, publications, quantumrep, quaternary, qubs, radiation, reactions, recycling, regeneration, religions, remotesensing, reports, reprodmed, resources, rheumato, risks, robotics, ruminants, safety, sci, scipharm, seeds, sensors, separations, sexes, signals, sinusitis, skins, smartcities, sna, societies, socsci, software, soilsystems, solar, solids, sports, standards, stats, stresses, surfaces, surgeries, suschem, sustainability, symmetry, synbio, systems, taxonomy, technologies, telecom, test, textiles, thalassrep, thermo, tomography, tourismhosp, toxics, toxins, transplantology, transportation, traumacare, traumas, tropicalmed, universe, urbansci, uro, vaccines, vehicles, venereology, vetsci, vibration, viruses, vision, waste, water, wem, wevj, wind, women, world, youth, zoonoticdis

%---------
% article
%---------
% The default type of manuscript is "article", but can be replaced by: 
% abstract, addendum, article, book, bookreview, briefreport, casereport, comment, commentary, communication, conferenceproceedings, correction, conferencereport, entry, expressionofconcern, extendedabstract, datadescriptor, editorial, essay, erratum, hypothesis, interestingimage, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, studyprotocol, systematicreview, supfile, technicalnote, viewpoint, guidelines, registeredreport, tutorial
% supfile = supplementary materials

%----------
% submit
%----------
% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted. This will only make changes to the frontpage (e.g., the logo of the journal will get visible), the headings, and the copyright information. Also, line numbering will be removed. Journal info and pagination for accepted papers will also be assigned by the Editorial Office.

%------------------
% moreauthors
%------------------
% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.

%---------
% pdftex
%---------
% The option pdftex is for use with pdfLaTeX. If eps figures are used, remove the option pdftex and use LaTeX and dvi2pdf.

%=================================================================
% MDPI internal commands
\firstpage{1} 
\makeatletter 
\setcounter{page}{\@firstpage} 
\makeatother
\pubvolume{1}
\issuenum{1}
\articlenumber{0}
\pubyear{2022}
\copyrightyear{2022}
%\externaleditor{Academic Editor: Firstname Lastname}
\datereceived{} 
%\daterevised{} % Only for the journal Acoustics
\dateaccepted{} 
\datepublished{} 
%\datecorrected{} % Corrected papers include a "Corrected: XXX" date in the original paper.
%\dateretracted{} % Corrected papers include a "Retracted: XXX" date in the original paper.
\hreflink{https://doi.org/} % If needed use \linebreak
%\doinum{}
%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
%\pdfoutput=1

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, soul, multirow, microtype, tikz, totcount, changepage, attrib, upgreek, cleveref, amsthm, hyphenat, natbib, hyperref, footmisc, url, geometry, newfloat, caption

%=================================================================
%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).

%=================================================================
% Full title of the paper (Capitalized)
\Title{Title}

% MDPI internal command: Title for citation in the left column
\TitleCitation{Title}

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0000-0000-000X} % Add \orcidA{} behind the author's name
%\newcommand{\orcidauthorB}{0000-0000-0000-000X} % Add \orcidB{} behind the author's name

% Authors, for the paper (add full first names)
\Author{Firstname Lastname $^{1,\dagger,\ddagger}$\orcidA{}, Firstname Lastname $^{2,\ddagger}$ and Firstname Lastname $^{2,}$*}

%\longauthorlist{yes}

% MDPI internal command: Authors, for metadata in PDF
\AuthorNames{Firstname Lastname, Firstname Lastname and Firstname Lastname}

% MDPI internal command: Authors, for citation in the left column
\AuthorCitation{Lastname, F.; Lastname, F.; Lastname, F.}
% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Affiliation 1; e-mail@e-mail.com\\
$^{2}$ \quad Affiliation 2; e-mail@e-mail.com}

% Contact information of the corresponding author
\corres{Correspondence: e-mail@e-mail.com; Tel.: (optional; include country code; if there are multiple corresponding authors, add author initials) +xx-xxxx-xxx-xxxx (F.L.)}

% Current address and/or shared authorship
\firstnote{Current address: Affiliation 3.} 
\secondnote{These authors contributed equally to this work.}
% The commands \thirdnote{} till \eighthnote{} are available for further notes

%\simplesumm{} % Simple summary

%\conference{} % An extended version of a conference paper

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{A single paragraph of about 200 words maximum. For research articles, abstracts should give a pertinent overview of the work. We strongly encourage authors to use the following style of structured abstracts, but without headings: (1) Background: place the question addressed in a broad context and highlight the purpose of the study; (2) Methods: describe briefly the main methods or treatments applied; (3) Results: summarize the article's main findings; (4) Conclusions: indicate the main conclusions or interpretations. The abstract should be an objective representation of the article, it must not contain results which are not presented and substantiated in the main text and should not exaggerate the main conclusions.}

% Keywords
\keyword{keyword 1; keyword 2; keyword 3 (List three to ten pertinent keywords specific to the article; yet reasonably common within the subject discipline.)}

% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
%\PACS{J0101}
%\MSC{}
%\JEL{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Diversity
%\LSID{\url{http://}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Applied Sciences
%\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work. This section is not mandatory.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Data
%\dataset{DOI number or link to the deposited data set if the data set is published separately. If the data set shall be published as a supplement to this paper, this field will be filled by the journal editors. In this case, please submit the data set as a supplement.}
%\datasetlicense{License under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Toxins
%\keycontribution{The breakthroughs or highlights of the manuscript. Authors can write one or two sentences to describe the most important part of the paper.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Encyclopedia
%\encyclopediadef{For entry manuscripts only: please provide a brief overview of the entry title instead of an abstract.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Advances in Respiratory Medicine
%\addhighlights{yes}
%\renewcommand{\addhighlights}{%
%	\begin{itemize}[labelsep=2.5mm]
%		\item This is an obligatory section in ``Advances in Respiratory Medicine'', whose goal is to increase the discoverability and readability of the article via search engines and other scholars.
%		\item Highlights consist of a short collection of (3–6) bullet points that capture the gap in knowledge the manuscript is addressing, as well as breakthroughs and other important points.
%		\item The Highlights section may also be used to showcase a new method used during the study (if any).
%	\end{itemize}
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\setcounter{section}{-1} %% Remove this when starting to work on the template.
\section{How to Use this Template}

The template details the sections that can be used in a manuscript. Note that the order and names of article sections may differ from the requirements of the journal (e.g., the positioning of the Materials and Methods section). Please check the instructions on the authors' page of the journal to verify the correct order and names. For any questions, please contact the editorial office of the journal or support@mdpi.com. For LaTeX-related questions please contact latex@mdpi.com.%\endnote{This is an endnote.} % To use endnotes, please un-comment \printendnotes below (before References). Only journal Laws uses \footnote.

% The order of the section titles is: Introduction, Materials and Methods, Results, Discussion, Conclusions for these journals: aerospace,algorithms,antibodies,antioxidants,atmosphere,axioms,biomedicines,carbon,crystals,designs,diagnostics,environments,fermentation,fluids,forests,fractalfract,informatics,information,inventions,jfmk,jrfm,lubricants,neonatalscreening,neuroglia,particles,pharmaceutics,polymers,processes,technologies,viruses,vision

\section{Introduction}

The introduction should briefly place the study in a broad context and highlight why it is important. It should define the purpose of the work and its significance. The current state of the research field should be reviewed carefully and key publications cited. Please highlight controversial and diverging hypotheses when necessary. Finally, briefly mention the main aim of the work and highlight the principal conclusions. As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research. Citing a journal paper \cite{ref-journal}. Now citing a book reference \cite{ref-book1,ref-book2} or other reference types \cite{ref-unpublish,ref-communication,ref-proceeding}. Please use the command \citep{ref-thesis,ref-url} for the following MDPI journals, which use author--date citation: Administrative Sciences, Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, Journal of Intelligence, Journalism and Media, JRFM, Languages, Laws, Religions, Risks, Social Sciences, Literature.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Materials and Methods}

Materials and Methods should be described with sufficient details to allow others to replicate and build on published results. Please note that publication of your manuscript implicates that you must make all materials, data, computer code, and protocols associated with the publication available to readers. Please disclose at the submission stage any restrictions on the availability of materials or information. New methods and protocols should be described in detail while well-established methods can be briefly described and appropriately cited.

Research manuscripts reporting large datasets that are deposited in a publicly avail-able database should specify where the data have been deposited and provide the relevant accession numbers. If the accession numbers have not yet been obtained at the time of submission, please state that they will be provided during review. They must be provided prior to publication.

Interventionary studies involving animals or humans, and other studies require ethical approval must list the authority that provided approval and the corresponding ethical approval code.
\begin{quote}
This is an example of a quote.
\end{quote}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}

This section may be divided by subheadings. It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
\subsection{Subsection}
\subsubsection{Subsubsection}

Bulleted lists look like this:
\begin{itemize}
\item	First bullet;
\item	Second bullet;
\item	Third bullet.
\end{itemize}

Numbered lists can be added as follows:
\begin{enumerate}
\item	First item; 
\item	Second item;
\item	Third item.
\end{enumerate}

The text continues here.

\subsection{Figures, Tables and Schemes}

All figures and tables should be cited in the main text as Figure~\ref{fig1}, Table~\ref{tab1}, Table~\ref{tab2}, etc.

\begin{figure}[H]
\includegraphics[width=10.5 cm]{Definitions/logo-mdpi}
\caption{This is a figure. Schemes follow the same formatting. If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel. (\textbf{b}) Description of what is contained in the second panel. Figures should be placed in the main text near to the first time they are cited. A caption on a single line should be centered.\label{fig1}}
\end{figure}   
\unskip

\begin{table}[H] 
\caption{This is a table caption. Tables should be placed in the main text near to the first time they are~cited.\label{tab1}}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\begin{tabularx}{\textwidth}{CCC}
\toprule
\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
\midrule
Entry 1		& Data			& Data\\
Entry 2		& Data			& Data\\
\bottomrule
\end{tabularx}
\end{table}
\unskip

\begin{table}[H]
\caption{This is a wide table.\label{tab2}}
	\begin{adjustwidth}{-\extralength}{0cm}
		\newcolumntype{C}{>{\centering\arraybackslash}X}
		\begin{tabularx}{\fulllength}{CCCC}
			\toprule
			\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}     & \textbf{Title 4}\\
			\midrule
			Entry 1		& Data			& Data			& Data\\
			Entry 2		& Data			& Data			& Data \textsuperscript{1}\\
			\bottomrule
		\end{tabularx}
	\end{adjustwidth}
	\noindent{\footnotesize{\textsuperscript{1} This is a table footnote.}}
\end{table}

%\begin{listing}[H]
%\caption{Title of the listing}
%\rule{\columnwidth}{1pt}
%\raggedright Text of the listing. In font size footnotesize, small, or normalsize. Preferred format: left aligned and single spaced. Preferred border format: top border line and bottom border line.
%\rule{\columnwidth}{1pt}
%\end{listing}

Text.

Text.

\subsection{Formatting of Mathematical Components}

This is the example 1 of equation:
\begin{linenomath}
\begin{equation}
a = 1,
\end{equation}
\end{linenomath}
the text following an equation need not be a new paragraph. Please punctuate equations as regular text.
%% If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments). This ensures correct linenumbering. The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph.

This is the example 2 of equation:
\begin{adjustwidth}{-\extralength}{0cm}
\begin{equation}
a = b + c + d + e + f + g + h + i + j + k + l + m + n + o + p + q + r + s + t + u + v + w + x + y + z
\end{equation}
\end{adjustwidth}

% Example of a page in landscape format (with table and table footnote).
%\startlandscape
%\begin{table}[H] %% Table in wide page
%\caption{This is a very wide table.\label{tab3}}
%	\begin{tabularx}{\textwidth}{CCCC}
%		\toprule
%		\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}	& \textbf{Title 4}\\
%		\midrule
%		Entry 1		& Data			& Data			& This cell has some longer content that runs over two lines.\\
%		Entry 2		& Data			& Data			& Data\textsuperscript{1}\\
%		\bottomrule
%	\end{tabularx}
%	\begin{adjustwidth}{+\extralength}{0cm}
%		\noindent\footnotesize{\textsuperscript{1} This is a table footnote.}
%	\end{adjustwidth}
%\end{table}
%\finishlandscape

% Example of a figure that spans the whole page width. The same concept works for tables, too.
\begin{figure}[H]
\begin{adjustwidth}{-\extralength}{0cm}
\centering
\includegraphics[width=13.5cm]{Definitions/logo-mdpi}
\end{adjustwidth}
\caption{This is a wide figure.\label{fig2}}
\end{figure}

Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows:
%% Example of a theorem:
\begin{Theorem}
Example text of a theorem.
\end{Theorem}

The text continues here. Proofs must be formatted as follows:

%% Example of a proof:
\begin{proof}[Proof of Theorem 1]
Text of the proof. Note that the phrase ``of Theorem 1'' is optional if it is clear which theorem is being referred to.
\end{proof}
The text continues here.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}

Authors should discuss the results and how they can be interpreted from the perspective of previous studies and of the working hypotheses. The findings and their implications should be discussed in the broadest context possible. Future research directions may also be highlighted.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}

This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Patents}

This section is not mandatory, but may be added if there are patents resulting from the work reported in this manuscript.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{6pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
%\supplementary{The following supporting information can be downloaded at:  \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title.}

% Only for the journal Methods and Protocols:
% If you wish to submit a video article, please do so with any other supplementary material.
% \supplementary{The following supporting information can be downloaded at: \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title. A supporting video article is available at doi: link.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{For research articles with several authors, a short paragraph specifying their individual contributions must be provided. The following statements should be used ``Conceptualization, X.X. and Y.Y.; methodology, X.X.; software, X.X.; validation, X.X., Y.Y. and Z.Z.; formal analysis, X.X.; investigation, X.X.; resources, X.X.; data curation, X.X.; writing---original draft preparation, X.X.; writing---review and editing, X.X.; visualization, X.X.; supervision, X.X.; project administration, X.X.; funding acquisition, Y.Y. All authors have read and agreed to the published version of the manuscript.'', please turn to the  \href{http://img.mdpi.org/data/contributor-role-instruction.pdf}{CRediT taxonomy} for the term explanation. Authorship must be limited to those who have contributed substantially to the work~reported.}

\funding{Please add: ``This research received no external funding'' or ``This research was funded by NAME OF FUNDER grant number XXX.'' and  and ``The APC was funded by XXX''. Check carefully that the details given are accurate and use the standard spelling of funding agency names at \url{https://search.crossref.org/funding}, any errors may affect your future funding.}

\institutionalreview{In this section, you should add the Institutional Review Board Statement and approval number, if relevant to your study. You might choose to exclude this statement if the study did not require ethical approval. Please note that the Editorial Office might ask you for further information. Please add “The study was conducted in accordance with the Declaration of Helsinki, and approved by the Institutional Review Board (or Ethics Committee) of NAME OF INSTITUTE (protocol code XXX and date of approval).” for studies involving humans. OR “The animal study protocol was approved by the Institutional Review Board (or Ethics Committee) of NAME OF INSTITUTE (protocol code XXX and date of approval).” for studies involving animals. OR “Ethical review and approval were waived for this study due to REASON (please provide a detailed justification).” OR “Not applicable” for studies not involving humans or animals.}

\informedconsent{Any research article describing a study involving humans should contain this statement. Please add ``Informed consent was obtained from all subjects involved in the study.'' OR ``Patient consent was waived due to REASON (please provide a detailed justification).'' OR ``Not applicable'' for studies not involving humans. You might also choose to exclude this statement if the study did not involve humans.

Written informed consent for publication must be obtained from participating patients who can be identified (including by the patients themselves). Please state ``Written informed consent has been obtained from the patient(s) to publish this paper'' if applicable.}

\dataavailability{In this section, please provide details regarding where data supporting reported results can be found, including links to publicly archived datasets analyzed or generated during the study. Please refer to suggested Data Availability Statements in section ``MDPI Research Data Policies'' at \url{https://www.mdpi.com/ethics}. If the study did not report any data, you might add ``Not applicable'' here.}

\acknowledgments{In this section you can acknowledge any support given which is not covered by the author contribution or funding sections. This may include administrative and technical support, or donations in kind (e.g., materials used for experiments).}

\conflictsofinterest{Declare conflicts of interest or state ``The authors declare no conflict of interest.'' Authors must identify and declare any personal circumstances or interest that may be perceived as inappropriately influencing the representation or interpretation of reported research results. Any role of the funders in the design of the study; in the collection, analyses or interpretation of data; in the writing of the manuscript; or in the decision to publish the results must be declared in this section. If there is no role, please state ``The funders had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript; or in the decision to publish the~results''.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional
\sampleavailability{Samples of the compounds ... are available from the authors.}

%% Only for journal Encyclopedia
%\entrylink{The Link to this entry published on the encyclopedia platform.}

\abbreviations{Abbreviations}{
The following abbreviations are used in this manuscript:\\

\noindent 
\begin{tabular}{@{}ll}
MDPI & Multidisciplinary Digital Publishing Institute\\
DOAJ & Directory of open access journals\\
TLA & Three letter acronym\\
LD & Linear dichroism
\end{tabular}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional
\appendixtitles{no} % Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
\appendixstart
\appendix
\section[\appendixname~\thesection]{}
\subsection[\appendixname~\thesubsection]{}
The appendix is an optional section that can contain details and data supplemental to the main text---for example, explanations of experimental details that would disrupt the flow of the main text but nonetheless remain crucial to understanding and reproducing the research shown; figures of replicates for experiments of which representative data are shown in the main text can be added here if brief, or as Supplementary Data. Mathematical proofs of results not central to the paper can be added as an appendix.

\begin{table}[H] 
\caption{This is a table caption.\label{tab5}}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\begin{tabularx}{\textwidth}{CCC}
\toprule
\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
\midrule
Entry 1		& Data			& Data\\
Entry 2		& Data			& Data\\
\bottomrule
\end{tabularx}
\end{table}

\section[\appendixname~\thesection]{}
All appendix sections must be cited in the main text. In the appendices, Figures, Tables, etc. should be labeled, starting with ``A''---e.g., Figure A1, Figure A2, etc.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{adjustwidth}{-\extralength}{0cm}
%\printendnotes[custom] % Un-comment to print a list of endnotes

\reftitle{References}

% Please provide either the correct journal abbreviation (e.g. according to the “List of Title Word Abbreviations” http://www.issn.org/services/online-services/access-to-the-ltwa/) or the full name of the journal.
% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.

%=====================================
% References, variant A: external bibliography
%=====================================
%\bibliography{your_external_BibTeX_file}

%=====================================
% References, variant B: internal bibliography
%=====================================
\begin{thebibliography}{999}
% Reference 1
\bibitem[Author1(year)]{ref-journal}
Author~1, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142--149.
% Reference 2
\bibitem[Author2(year)]{ref-book1}
Author~2, L. The title of the cited contribution. In {\em The Book Title}; Editor 1, F., Editor 2, A., Eds.; Publishing House: City, Country, 2007; pp. 32--58.
% Reference 3
\bibitem[Author3(year)]{ref-book2}
Author 1, A.; Author 2, B. \textit{Book Title}, 3rd ed.; Publisher: Publisher Location, Country, 2008; pp. 154--196.
% Reference 4
\bibitem[Author4(year)]{ref-unpublish}
Author 1, A.B.; Author 2, C. Title of Unpublished Work. \textit{Abbreviated Journal Name} year, \textit{phrase indicating stage of publication (submitted; accepted; in press)}.
% Reference 5
\bibitem[Author5(year)]{ref-communication}
Author 1, A.B. (University, City, State, Country); Author 2, C. (Institute, City, State, Country). Personal communication, 2012.
% Reference 6
\bibitem[Author6(year)]{ref-proceeding}
Author 1, A.B.; Author 2, C.D.; Author 3, E.F. Title of presentation. In Proceedings of the Name of the Conference, Location of Conference, Country, Date of Conference (Day Month Year); Abstract Number (optional), Pagination (optional).
% Reference 7
\bibitem[Author7(year)]{ref-thesis}
Author 1, A.B. Title of Thesis. Level of Thesis, Degree-Granting University, Location of University, Date of Completion.
% Reference 8
\bibitem[Author8(year)]{ref-url}
Title of Site. Available online: URL (accessed on Day Month Year).
\end{thebibliography}

% If authors have biography, please use the format below
%\section*{Short Biography of Authors}
%\bio
%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author1.pdf}}}
%{\textbf{Firstname Lastname} Biography of first author}
%
%\bio
%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author2.jpg}}}
%{\textbf{Firstname Lastname} Biography of second author}

% For the MDPI journals use author-date citation, please follow the formatting guidelines on http://www.mdpi.com/authors/references
% To cite two works by the same author: \citeauthor{ref-journal-1a} (\citeyear{ref-journal-1a}, \citeyear{ref-journal-1b}). This produces: Whittaker (1967, 1975)
% To cite two works by the same author with specific pages: \citeauthor{ref-journal-3a} (\citeyear{ref-journal-3a}, p. 328; \citeyear{ref-journal-3b}, p.475). This produces: Wong (1999, p. 328; 2000, p. 475)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% for journal Sci
%\reviewreports{\\
%Reviewer 1 comments and authors’ response\\
%Reviewer 2 comments and authors’ response\\
%Reviewer 3 comments and authors’ response
%}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{adjustwidth}
\end{document}

### 2022-08-26 MDPI/cover_letter.tex
respnonse letter

--- 2022-07-19 ETI/cover_letter.tex
@@
 \usepackage{color}
+\usepackage[textsize=small]{todonotes}
 
@@
 
-\newcommand{\theeditor}{Professor Ravi Naidu}
+\newcommand{\theeditor}{Dr. David Díaz-Díaz}
 
-\newcommand{\thejournal}{\textit{Environmental Technology \& Innovation}}
+\newcommand{\thejournal}{\textit{Gels }}
 \newcommand{\cl}{\mathrm{Cl^-}}
@@
 
-Herewith we would like to submit our manuscript: \textit{Water desalination using polyelectrolyte hydrogel. Gibbs ensemble modeling}
+Herewith we would like to submit our manuscript: ``\textit{Water desalination using polyelectrolyte hydrogel. Gibbs ensemble modeling}''
 authored by
@@
 
-We believe that our work brings new insights into the complex problem of seawater desalination
-that fits within the scope of \thejournal, and that it will be of interest to its broad readership.
+Our study develops a general understanding of the physics of polyelectrolyte hydrogels.
+It also brings new insights into their application to seawater desalination.
+Thus, we believe that the study fits within the scope of \thejournal and that it will be of interest to its broad readership.
 
 \vspace{5ex}
+
+We confirm that neither the manuscript nor any parts of its content are currently under consideration or published in another journal.
+
+All authors have approved the manuscript and agree with its submission to (journal name).
 

### 2022-08-26 gibbs.tex
respnonse letter

@@
 %\documentclass{achemso}
-\documentclass[journal=mamobx, layout=twocolumns,manuscript=article]{achemso}
+\documentclass[layout=twocolumns,manuscript=article]{achemso}
 
@@
 \affiliation{Department of Physical and Macromolecular Chemistry, Faculty of Science, Charles University in Prague, Czech Republic}
-\alsoaffiliation[imc]{Institute of Macromolecular Compounds of Russian Academy of Sciences,
-Saint-Petersburg, Russia}
+\alsoaffiliation[imc]{Institute of Macromolecular Compounds of Russian Academy of Sciences, Saint-Petersburg, Russia}
 
@@
 \begin{abstract}
-Recently polyelectrolyte hydrogels have been proposed as draw agents for reverse osmosis desalination techniques. 
-Indeed, polyelectrolyte hydrogels have the ability to absorb a big amount of water across forward osmosis membrane as a result of their swelling pressure. 
+Recently polyelectrolyte hydrogels have been proposed as draw agents for the forward osmosis desalination techniques. 
+Indeed, polyelectrolyte hydrogels have the ability to absorb a big amount of water across an osmosis membrane as a result of their swelling pressure. 
 On the other hand, the insoluble cross-linked network of the gel enables dewatering under the influence of a stimulus (thermal and/or mechanical).

### 2022-08-26 gibbs_mdpi.tex
respnonse letter

--- 2022-08-26 gibbs.tex
@@
-%% LyX 2.3.4.2 created this file.  For more info, see http://www.lyx.org/.
-%% Do not edit unless you really know what you are doing.
-%\documentclass{achemso}
-\documentclass[layout=twocolumns,manuscript=article]{achemso}
+%  LaTeX support: latex@mdpi.com 
+%  For support, please attach all files needed for compiling as well as the log file, and specify your operating system, LaTeX version, and LaTeX editor.
 
+%=================================================================
+\documentclass[journal,article,submit,pdftex,moreauthors]{Definitions/mdpi} 
+\usepackage{subfig}
+\usepackage[textsize=small]{todonotes}
+\newcommand{\ie}{\textit{i.~e.} }
+\newcommand{\cref}{c^{\ominus}}
+%\newcommand{\cs}{c_{s}}
+\newcommand{\kT}{k_\mathrm{B}T}
+\newcommand{\kB}{k_\mathrm{B}}
+\newcommand{\lb}{l_\mathrm{B}}
+%\newcommand{\NA}{N_{\mathrm{A^-}}}
+\newcommand{\NA}{N_{\mathrm{A}}}
+\newcommand{\muna}{\mu_\mathrm{Na^+}}
+
+\newcommand{\mucl}{\mu_\mathrm{Cl^-}}
+\newcommand{\muca}{\mu_\mathrm{Ca^{2+}}}
+\newcommand{\muh}{\mu_\mathrm{H^+}}
+\newcommand{\mua}{\mu_\mathrm{A^-}}
+\newcommand{\muha}{\mu_\mathrm{HA}}
+\newcommand{\muoh}{\mu_\mathrm{OH}}
+
+\newcommand{\cna}{c_\mathrm{Na^+}}
+\newcommand{\ccl}{c_\mathrm{Cl^-}}
+\newcommand{\cca}{c_\mathrm{Ca^{2+}}}
+\newcommand{\ch}{c_\mathrm{H^+}}
+\newcommand{\cp}{c_\mathrm{p}}
+\newcommand{\nna}{n_\mathrm{Na^+}}
+\newcommand{\ncl}{n_\mathrm{Cl^-}}
+\newcommand{\Nna}{N_\mathrm{Na^+}}
+\newcommand{\Ncl}{N_\mathrm{Cl^-}}
+
+\newcommand{\ncleq}{\widetilde{N}_\mathrm{Cl^-}}
+\newcommand{\nca}{N_\mathrm{Ca^{2+}}}
+
+\newcommand{\superin}{^\mathrm{in}}
+\newcommand{\subin}{_\mathrm{in}}
+\newcommand{\subi}{_\mathrm{i}}
+
+\newcommand{\gel}{^\mathrm{gel}}
+\newcommand{\tot}{^\mathrm{tot}}
+\newcommand{\out}{^{\mathrm{out}}}
+\newcommand{\coh}{c_\mathrm{OH}}
+\newcommand{\bulk}{^{\mathrm{b}}}
+\renewcommand{\H}{\mathrm{H^+}}
+\newcommand{\A}{\mathrm{A^-}}
+\newcommand{\AH}{\mathrm{AH}}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
+%% A simple dot to overcome graphicx limitations
+
+\newcommand{\cl}{\mathrm{Cl^-}}
+\newcommand{\br}{\mathrm{Br^-}}
+\newcommand{\na}{\mathrm{Na^+}}
+\newcommand{\h}{\mathrm{H^+}}
+\newcommand{\ka}{\mathrm{K^+}}
+\newcommand{\oh}{\mathrm{OH^-}}
+\newcommand{\ca}{\mathrm{Ca^{2+}}}
+\newcommand{\mg}{\mathrm{Mg^{2+}}}
+
+\newcommand{\Ka}{K_{\mathrm{A}}}
+\newcommand{\pKa}{\mathrm{p}\Ka}
+\newcommand{\pK}{\mathrm{p}K}
+\newcommand{\pH}{\mathrm{pH}}
+\newcommand{\mol}{\mathrm{mol}}
+\newcommand{\molperl}{\mathrm{mol/l}}
+\newcommand{\kg}{\mathrm{kg}}
+\newcommand{\res}{^{\mathrm{res}}}
+\newcommand{\pHres}{\pH\res}
+\newcommand{\pHgel}{\pH\gel}
+\newcommand{\cs}{c_{\mathrm{s}}}
+%\newcommand{\cs}{c_{\mathrm{salt}}}
+\newcommand{\csres}{\cs\res}
+%\newcommand{\Vgel}{V\gel}
+\newcommand{\Vgel}{V_\mathrm{gel}}
+%\newcommand{\Vgel}{V}
+\newcommand{\Ngel}{N_\mathrm{gel}}
+%\newcommand{\Vgeleq}{\widetilde{V}_\mathrm{gel}}}
+%\newcommand{\Pgel}{P_\mathrm{gel}}
+\newcommand{\Pgel}{\Pi}
+\newcommand{\Pres}{P_\mathrm{res}}
+\newcommand{\Pout}{P_\mathrm{out}}
+\newcommand{\Vout}{V_\mathrm{out}}
+%\newcommand{\Vbox}{V_\mathrm{box}}
+\newcommand{\Vbox}{V_0}
+\newcommand{\PE}{polyelectrolyte{}}
+
+\newcommand{\reffig}[1]{Figure~\ref{#1}}
+\newcommand{\refeq}[1]{Equation~\ref{#1}{}}
+\newcommand{\etal}{\textit{et al.}{}}
+
+% For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal and change "submit" to "accept".
+The document class line would be, e.g., \documentclass[preprints,article,accept,moreauthors,pdftex]{mdpi}.
+This is especially recommended for submission to arXiv, where line numbers should be removed before posting.
+For preprints.org, the editorial staff will make this change immediately prior to posting.
+
+%--------------------
+% Class Options:
+%--------------------
+%----------
+% journal
+%----------
+% Choose between the following MDPI journals:
+% acoustics, actuators, addictions, admsci, adolescents, aerospace, agriculture, agriengineering, agronomy, ai, algorithms, allergies, alloys, analytica, animals, antibiotics, antibodies, antioxidants, applbiosci, appliedchem, appliedmath, applmech, applmicrobiol, applnano, applsci, aquacj, architecture, arts, asc, asi, astronomy, atmosphere, atoms, audiolres, automation, axioms, bacteria, batteries, bdcc, behavsci, beverages, biochem, bioengineering, biologics, biology, biomass, biomechanics, biomed, biomedicines, biomedinformatics, biomimetics, biomolecules, biophysica, biosensors, biotech, birds, bloods, blsf, brainsci, breath, buildings, businesses, cancers, carbon, cardiogenetics, catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, chemproc, children, chips, cimb, civileng, cleantechnol, climate, clinpract, clockssleep, cmd, coasts, coatings, colloids, colorants, commodities, compounds, computation, computers, condensedmatter, conservation, constrmater, cosmetics, covid, crops, cryptography, crystals, csmf, ctn, curroncol, currophthalmol, cyber, dairy, data, dentistry, dermato, dermatopathology, designs, diabetology, diagnostics, dietetics, digital, disabilities, diseases, diversity, dna, drones, dynamics, earth, ebj, ecologies, econometrics, economies, education, ejihpe, electricity, electrochem, electronicmat, electronics, encyclopedia, endocrines, energies, eng, engproc, ent, entomology, entropy, environments, environsciproc, epidemiologia, epigenomes, est, fermentation, fibers, fintech, fire, fishes, fluids, foods, forecasting, forensicsci, forests, foundations, fractalfract, fuels, futureinternet, futureparasites, futurepharmacol, futurephys, futuretransp, galaxies, games, gases, gastroent, gastrointestdisord, gels, genealogy, genes, geographies, geohazards, geomatics, geosciences, geotechnics, geriatrics, hazardousmatters, healthcare, hearts, hemato, heritage, highthroughput, histories, horticulturae, humanities, humans, hydrobiology, hydrogen, hydrology, hygiene, idr, ijerph, ijfs, ijgi, ijms, ijns, ijtm, ijtpp, immuno, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jal, jcdd, jcm, jcp, jcs, jdb, jeta, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmp, jmse, jne, jnt, jof, joitmc, jor, journalmedia, jox, jpm, jrfm, jsan, jtaer, jzbg, kidney, kidneydial, knowledge, land, languages, laws, life, liquids, literature, livers, logics, logistics, lubricants, lymphatics, machines, macromol, magnetism, magnetochemistry, make, marinedrugs, materials, materproc, mathematics, mca, measurements, medicina, medicines, medsci, membranes, merits, metabolites, metals, meteorology, methane, metrology, micro, microarrays, microbiolres, micromachines, microorganisms, microplastics, minerals, mining, modelling, molbank, molecules, mps, msf, mti, muscles, nanoenergyadv, nanomanufacturing, nanomaterials, ncrna, network, neuroglia, neurolint, neurosci, nitrogen, notspecified, nri, nursrep, nutraceuticals, nutrients, obesities, oceans, ohbm, onco, oncopathology, optics, oral, organics, organoids, osteology, oxygen, parasites, parasitologia, particles, pathogens, pathophysiology, pediatrrep, pharmaceuticals, pharmaceutics, pharmacoepidemiology, pharmacy, philosophies, photochem, photonics, phycology, physchem, physics, physiologia, plants, plasma, pollutants, polymers, polysaccharides, poultry, powders, preprints, proceedings, processes, prosthesis, proteomes, psf, psych, psychiatryint, psychoactives, publications, quantumrep, quaternary, qubs, radiation, reactions, recycling, regeneration, religions, remotesensing, reports, reprodmed, resources, rheumato, risks, robotics, ruminants, safety, sci, scipharm, seeds, sensors, separations, sexes, signals, sinusitis, skins, smartcities, sna, societies, socsci, software, soilsystems, solar, solids, sports, standards, stats, stresses, surfaces, surgeries, suschem, sustainability, symmetry, synbio, systems, taxonomy, technologies, telecom, test, textiles, thalassrep, thermo, tomography, tourismhosp, toxics, toxins, transplantology, transportation, traumacare, traumas, tropicalmed, universe, urbansci, uro, vaccines, vehicles, venereology, vetsci, vibration, viruses, vision, waste, water, wem, wevj, wind, women, world, youth, zoonoticdis
+
+%---------
+% article
+%---------
+% The default type of manuscript is "article", but can be replaced by: 
+% abstract, addendum, article, book, bookreview, briefreport, casereport, comment, commentary, communication, conferenceproceedings, correction, conferencereport, entry, expressionofconcern, extendedabstract, datadescriptor, editorial, essay, erratum, hypothesis, interestingimage, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, studyprotocol, systematicreview, supfile, technicalnote, viewpoint, guidelines, registeredreport, tutorial
+% supfile = supplementary materials
+
+%----------
+% submit
+%----------
+% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted.
+This will only make changes to the frontpage (e.g., the logo of the journal will get visible), the headings, and the copyright information.
+Also, line numbering will be removed.
+Journal info and pagination for accepted papers will also be assigned by the Editorial Office.
+
+%------------------
+% moreauthors
+%------------------
+% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.
+
+%---------
+% pdftex
+%---------
+% The option pdftex is for use with pdfLaTeX. If eps figures are used, remove the option pdftex and use LaTeX and dvi2pdf.
+
+%=================================================================
+% MDPI internal commands
+\firstpage{1} 
 \makeatletter 
+\setcounter{page}{\@firstpage} 
+\makeatother
+\pubvolume{1}
+\issuenum{1}
+\articlenumber{0}
+\pubyear{2022}
+\copyrightyear{2022}
+%\externaleditor{Academic Editor: Firstname Lastname}
+\datereceived{} 
+%\daterevised{} % Only for the journal Acoustics
+\dateaccepted{} 
+\datepublished{} 
+%\datecorrected{} % Corrected papers include a "Corrected: XXX" date in the original paper.
+%\dateretracted{} % Corrected papers include a "Retracted: XXX" date in the original paper.
+\hreflink{https://doi.org/} % If needed use \linebreak
+%\doinum{}
+%------------------------------------------------------------------
+% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
+%\pdfoutput=1
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
+%=================================================================
+% Add packages and commands here.
+The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, soul, multirow, microtype, tikz, totcount, changepage, attrib, upgreek, cleveref, amsthm, hyphenat, natbib, hyperref, footmisc, url, geometry, newfloat, caption
 
-\title{Water desalination using polyelectrolyte hydrogel. Gibbs ensemble modeling}
+%=================================================================
+%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
+%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).
 
-\author{Mikhail Laktionov}
+%=================================================================
+% Full title of the paper (Capitalized)
+\Title{Water desalination using polyelectrolyte hydrogel. Gibbs ensemble modeling}
 
-\affiliation[cuni]{Department of Physical and Macromolecular Chemistry, Faculty of Science,
-Charles University in Prague, Czech Republic}
+% MDPI internal command: Title for citation in the left column
+\TitleCitation{Title}
 
-\alsoaffiliation[itmo]{St. Petersburg National Research University of Information Technologies,
-Mechanics and Optics, St. Petersburg, Russia.}
+% Author Orchid ID: enter ID or remove command
+\newcommand{\orcidauthorA}{0000-0003-3412-7707} % Add \orcidA{} behind the author's name
+\newcommand{\orcidauthorB}{0000-0003-3616-3285} % Add \orcidB{} behind the author's name
+\newcommand{\orcidauthorC}{0000-0002-8501-0464} % Add \orcidB{} behind the author's name
 
-\author{Lucie Nová}
-\author{Oleg V. Rud}
+% Authors, for the paper (add full first names)
+\Author{Mikhail Laktionov $^{1, 2}$\orcidA{}, Lucie Nová $^{1}$\orcidB{} and Oleg V. Rud $^{1, 3}$*\orcidC{}}
 
-\affiliation{Department of Physical and Macromolecular Chemistry, Faculty of Science, Charles University in Prague, Czech Republic}
-\alsoaffiliation[imc]{Institute of Macromolecular Compounds of Russian Academy of Sciences, Saint-Petersburg, Russia}
+%\longauthorlist{yes}
 
-\email{oleg.rud@natur.cuni.cz}
+% MDPI internal command: Authors, for metadata in PDF
+\AuthorNames{Mikhail Laktionov, Lucie Nová and Oleg V. Rud}
 
-\abbreviations{MC, MD, RO, FO}
+% MDPI internal command: Authors, for citation in the left column
+\AuthorCitation{Lastname, F.; Lastname, F.; Lastname, F.}
+% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.
 
-\keywords{polyelectrolye hydrogel, simulation, desalination}
+% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
+\address{%
+$^{1}$ \quad Department of Physical and Macromolecular Chemistry, Faculty of Science, Charles University in Prague, Czech Republic; e-mail@e-mail.com\\
+$^{2}$ \quad St. Petersburg National Research University of Information Technologies, Mechanics and Optics, St. Petersburg, Russia; e-mail@e-mail.com\\
+$^{3}$ \quad Institute of Macromolecular Compounds of Russian Academy of Sciences, Saint-Petersburg, Russia; e-mail@e-mail.com}
 
-%% Because html converters don't know tabularnewline
-\providecommand{\tabularnewline}{\\}
+% Contact information of the corresponding author
+\corres{Correspondence: oleg.rud@natur.cuni.cz; }
 
-\input{definitions.tex}
-\makeatother
+% Current address and/or shared authorship
+%\firstnote{Current address: Affiliation 3.} 
+%\secondnote{These authors contributed equally to this work.}
+% The commands \thirdnote{} till \eighthnote{} are available for further notes
 
-\begin{document}
-\begin{abstract}
-Recently polyelectrolyte hydrogels have been proposed as draw agents for the forward osmosis desalination techniques. 
+%\simplesumm{} % Simple summary
+
+%\conference{} % An extended version of a conference paper
+
+% Abstract (Do not insert blank lines, i.e. \\) 
+\abstract{Recently polyelectrolyte hydrogels have been proposed as draw agents for the forward osmosis desalination techniques. 
 Indeed, polyelectrolyte hydrogels have the ability to absorb a big amount of water across an osmosis membrane as a result of their swelling pressure. 
@@
 Finally, we performed a set of simulations modeling the process of continuous decrease of solution salinity up to freshwater concentrations.
+}
 
-\end{abstract}
+% Keywords
+\keyword{polyelectrolye hydrogel; simulation; desalination}
+
+% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
+%\PACS{J0101}
+%\MSC{}
+%\JEL{}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Only for the journal Diversity
+%\LSID{\url{http://}}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Only for the journal Applied Sciences
+%\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work. This section is not mandatory.}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Only for the journal Data
+%\dataset{DOI number or link to the deposited data set if the data set is published separately.
+If the data set shall be published as a supplement to this paper, this field will be filled by the journal editors.
+In this case, please submit the data set as a supplement.}
+%\datasetlicense{License under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Only for the journal Toxins
+%\keycontribution{The breakthroughs or highlights of the manuscript. Authors can write one or two sentences to describe the most important part of the paper.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Only for the journal Encyclopedia
+%\encyclopediadef{For entry manuscripts only: please provide a brief overview of the entry title instead of an abstract.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Only for the journal Advances in Respiratory Medicine
+%\addhighlights{yes}
+%\renewcommand{\addhighlights}{%
+%	\begin{itemize}[labelsep=2.5mm]
+%		\item This is an obligatory section in ``Advances in Respiratory Medicine'', whose goal is to increase the discoverability and readability of the article via search engines and other scholars.
+%		\item Highlights consist of a short collection of (3–6) bullet points that capture the gap in knowledge the manuscript is addressing, as well as breakthroughs and other important points.
+%		\item The Highlights section may also be used to showcase a new method used during the study (if any).
+%	\end{itemize}
+%}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{document}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\setcounter{section}{-1} %% Remove this when starting to work on the template.
 
 \section{Introduction\label{sec: intro}}
-
-\paragraph{Water desalination technologies.}
-
+\subsection{Water desalination technologies}
 Two basic approaches for separating water from salt are present in modern desalination technology \cite{Miller2003,Curto2021}.
@@
 
-\paragraph{Hydrogels for desalination.}
+\subsection{Hydrogels for desalination}
 Hydrogels are three-dimensional networks of polymer chains that are crosslinked by either physical or chemical bonds. 
@@
 
-\paragraph{Physics behind the desalination process.}
+\subsection{Physics behind the desalination process}
 %The maximum entropy principle requires the density of charges to be more-less the same throughout the system medium. 
@@
 is defined by Donnan law \cite{Rud2018}
-\begin{equation*}
+\begin{equation}
 \frac{\ccl\gel}{\cs}=\frac{\cs}{\cna\gel}=\sqrt{1+\left(\frac{\alpha}{2\cs\Vgel}\right)^{2}}\pm\frac{\alpha}{2\cs\Vgel}
-\end{equation*}
+\end{equation}
 where $\ccl\gel$ and $\cna\gel$ are the internal concentration of monovalent anions and cations, $\cs$ is the salinity of external solution,  $\Vgel$ is the gel molar volume (inverse density of gel segments) and $\alpha$ is ionization degree (in the case of our study $\alpha=1$).
@@
 
-\begin{figure*}[t]
-\centering \includegraphics[width=0.7\textwidth]{{figures/simgibbs}.pdf}\caption{Diamond-like network in the simulation box. Color code represents
+\begin{figure*}[h]
+\centering 
+\includegraphics[width=0.7\textwidth]{{figures/simgibbs}.pdf}\caption{Diamond-like network in the simulation box. Color code represents
 the individual ion types (red: $\na$, blue: $\cl$, yellow: $\ca$)
@@
 
-\begin{figure*}[t]
-\centering 
-\subfloat[Open system \label{fig: open}]
-{\includegraphics[width=0.5\textwidth]{figures/gc.pdf}}
-\subfloat[Closed system \label{fig: closed}]
-{\includegraphics[width=0.5\textwidth]{figures/gibbs.pdf}}
-\caption{Diamond-like network in the simulation box. Color code represents
-the individual ion types (red: $\na$, blue: $\cl$, yellow: $\ca$)
-and the hydrogel (gray: neutral segment ($\AH$), cyan: charged segment
-($\A$)). \label{fig:open and closed}.}
-\end{figure*}
 We simulate the compression of the gel in two ensembles.
@@
 \item The first is so called \emph{open system}, when the simulation box with gel freely exchanges ions with a big amount of aqueous solution of certain constant salinity, $\cs$. 
-\item And in \emph{closed system}, when the gel is in equilibrium with a finite volume of aqueous solution.
+\item The second is \emph{closed system}, when the gel is in equilibrium with a finite volume of aqueous solution.
 \end{enumerate}
@@
 
-\paragraph{Open system.}
+\begin{figure*}[h]
+\centering 
+\subfloat[Open system \label{fig: open}]
+{\includegraphics[width=0.5\textwidth]{figures/gc.pdf}}
+\subfloat[Closed system \label{fig: closed}]
+{\includegraphics[width=0.5\textwidth]{figures/gibbs.pdf}}
+\caption{Diamond-like network in the simulation box. Color code represents
+the individual ion types (red: $\na$, blue: $\cl$, yellow: $\ca$)
+and the hydrogel (gray: neutral segment ($\AH$), cyan: charged segment
+($\A$)). \label{fig:open and closed}.}
+\end{figure*}
+\subsection{Open system}
 We simulate the open system using the grand reaction method \cite{Landsgesel2020a,Rud2020}.
@@
 The insertion (and deletion) of ion pairs is considered as a reaction of creation (or annihilation) of an ion pair 
-\[
+\begin{equation}
 \varnothing\stackrel{K}{\leftrightarrows}\na+\cl
-\]
+\end{equation}
 with a reaction constant defined by the chemical potential of ions,
@@
 
-\paragraph{Closed system.}
+\subsection{Closed system}
 The similar scheme we use to simulate the gel in closed system. 
@@
 
-\paragraph{Algorithm.}
+\subsection{Algorithm}
 The thermodynamic equilibrium between the two volumes implies the exchange of ion pairs between them, which is done by means of MC procedure in a way similar to described in \cite{Panagiotopoulos1988b}.
@@
 
-\paragraph{Compression in open system.}
-\begin{figure*}[t]
+\subsection{Compression in open system}
+\begin{figure*}[h]
+\begin{adjustwidth}{-\extralength}{0cm}
 \subfloat[The gel partial pressure vs gel molar volume \label{fig: PV}]
-{\includegraphics[width=0.48\textwidth]{figures/fig_PV_pub.pdf}}
+{\includegraphics[width=0.65\textwidth]{figures/fig_PV_pub.pdf}}
 \hspace{0.02\textwidth}
 \subfloat[Supernate salinity vs gel molar volume\label{fig: CV}]
-{\includegraphics[width=0.48\textwidth]{figures/fig_CV_pub.pdf}}
+{\includegraphics[width=0.65\textwidth]{figures/fig_CV_pub.pdf}}
 \caption{
@@
 Each solid curve corresponds to different salinity of the reservoir $\cs$ (see legend). Shadowed area limit the states with applied pressure below zero and above 5 bar.\label{fig: PV and CV}}
+\end{adjustwidth}
 \end{figure*}
@@
 It is caused by the decrease of ions osmotic pressure and by a screening of electrostatic interactions \cite{Zhulina2000, Landsgesel2020a}.
-\footnote{The salinity dependence of the size of \emph{weak} polyelectrolyte gel is in general non-monotonic. We discuss this case in \cite{Rud2018}.}
+(The salinity dependence of the size of \emph{weak} polyelectrolyte gel is in general non-monotonic. We discuss this case in \cite{Rud2018}.)
 
-\begin{figure*}[t]
+\begin{figure*}[h]
+\begin{adjustwidth}{-\extralength}{0cm}
 \subfloat[Pressure vs gel molar volume \label{fig: NV}]
-{\includegraphics[width=0.49\textwidth]{figures/fig_NV_pub.pdf}}
+{\includegraphics[width=0.65\textwidth]{figures/fig_NV_pub.pdf}}
+\hspace{0.02\textwidth}
 \subfloat[Salinity vs gel molar volume\label{fig: CN}]
-{\includegraphics[width=0.495\textwidth]{figures/fig_NVbox_mu_pub.pdf}}
+{\includegraphics[width=0.65\textwidth]{figures/fig_NVbox_mu_pub.pdf}}
 \caption{The compression of the gel in \emph{open system} (solid lines) and in \emph{closed system} (dotted lines). 
@@
 \label{fig: NV and CN}}
-
+\end{adjustwidth}
 %\todoi{Replace y-axis labels by $\ncl$}
@@
 
-\paragraph{Compression in closed system.}
+\subsection{Compression in closed system}
 %Each set of simulations in \emph{open system} defines the free swelling equilibrium states of the gel for each salinity, \ie the state where the gel partial pressure equals zero. 
@@
 
-\paragraph{Desalination scheme.}
+\subsection{Desalination scheme}
 As we have seen, the compression of the gel in a closed system affects the salinity, whereas the compression in an open system affects the amount of ions in a volume where the gel is compressed in. 
@@
 
-\paragraph{The efficiency of desalination.}
+\subsection{The efficiency of desalination}
 The theoretical minimum specific energy for seawater desalination (
@@
 \end{equation}
+\todo{the equation must be supported by referrence}
 Here, in the table, we present the absolute values of the work, whereas one should keep in mind that the compression implies the work is done by external force and the swelling implies that the work is done by gel.
@@
 \begin{table}
-\begin{tabular*}{1\textwidth}{@{\extracolsep{\fill}}ll|lc|c|l|ll}
+\caption{The estimates of the efficiency of the desalination process. All the units are calculated per one mol of gel segments. Values in brackets
+are the estimates corresponding to crossection of 'red' and 'orange' lines on the plots of Figures \ref{fig: PV and CV} and \ref{fig: NV and CN}
+\label{tab: table}}
+\begin{adjustwidth}{-0.0\extralength}{0cm}
+		\newcolumntype{C}{>{\centering\arraybackslash}X}
+\begin{tabularx}{1\textwidth}{@{\extracolsep{\fill}}ll|lc|c|l|ll}
 \multicolumn{1}{l|}{$c_{s}^{0}$, mM} & $c_{s}^{5}$, mM & \multicolumn{1}{l|}{$n_{\cl}^{0}$, mM} & $n_{\cl}^{5}$, mM & $\Delta \Vgel$, l & $|W$\textbar , J/l & \multicolumn{2}{c}{$W^{id}$, J/l}\tabularnewline
@@
 \multicolumn{2}{r|}{\textcolor{magenta}{\small{}$3.862\pm0.001$}} &  &  &  &  &  & \tabularnewline
-\end{tabular*}
-
-\caption{The estimates of the efficiency of the desalination process. All the units are calculated per one mol of gel segments. Values in brackets
-are the estimates corresponding to crossection of 'red' and 'orange' lines on the plots of Figures \ref{fig: PV and CV} and \ref{fig: NV and CN}
-\label{tab: table}}
+\end{tabularx}
+\end{adjustwidth}
 \end{table}
@@
 
-\section*{Acknowledgments}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\vspace{6pt}
 
-This research was supported by the Czech Science Foundation (grant 19-17847Y)
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% optional
+%\supplementary{The following supporting information can be downloaded at:  \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title.}
+
+% Only for the journal Methods and Protocols:
+% If you wish to submit a video article, please do so with any other supplementary material.
+% \supplementary{The following supporting information can be downloaded at: \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title.
+A supporting video article is available at doi: link.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\authorcontributions{Conceptualization, O.R.
+; methodology, M.L.; software, M.L.; validation, M.L., L.N.
+and O.R.; formal analysis, L.N.; data curation, M.L.; writing---original draft preparation, O.R.; writing---review and editing, L.N.
+%All authors have read and agreed to the published version of the manuscript.', please turn to the  \href{http://img.mdpi.org/data/contributor-role-instruction.pdf}{CRediT taxonomy} for the term explanation.
+Authorship must be limited to those who have contributed substantially to the work~reported.
+}
+
+\funding{``This research was funded by Czech Science Foundation grant number 19-17847Y'' and Government of Russian Federation  grant number 14.W03.31.0022. }
+
+\acknowledgments{This research was supported by the Czech Science Foundation (grant 19-17847Y)
 Government of Russian Federation, grant number 14.W03.31.0022. 
-Computational resources were supplied by the project ``e-Infrastruktura CZ'' (e-INFRA LM2018140) provided within the program Projects of Large Research, Development and Innovations Infrastructures.
+}
 
+\conflictsofinterest{The authors declare no conflict of interest.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{adjustwidth}{-\extralength}{0cm}
+%\printendnotes[custom] % Un-comment to print a list of endnotes
+
+\reftitle{References}
+
+% Please provide either the correct journal abbreviation (e.g.
+according to the “List of Title Word Abbreviations” http://www.issn.org/services/online-services/access-to-the-ltwa/) or the full name of the journal.
+% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.
+
+%=====================================
+% References, variant A: external bibliography
+%=====================================
+%\bibliography{your_external_BibTeX_file}
 \bibliography{lit/gibbs}
 
-\newpage
-%\listoftodos
+% If authors have biography, please use the format below
+%\section*{Short Biography of Authors}
+%\bio
+%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author1.pdf}}}
+%{\textbf{Firstname Lastname} Biography of first author}
+%
+%\bio
+%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author2.jpg}}}
+%{\textbf{Firstname Lastname} Biography of second author}
 
+% For the MDPI journals use author-date citation, please follow the formatting guidelines on http://www.mdpi.com/authors/references
+% To cite two works by the same author: \citeauthor{ref-journal-1a} (\citeyear{ref-journal-1a}, \citeyear{ref-journal-1b}). This produces: Whittaker (1967, 1975)
+% To cite two works by the same author with specific pages: \citeauthor{ref-journal-3a} (\citeyear{ref-journal-3a}, p.
+328; \citeyear{ref-journal-3b}, p.475).
+This produces: Wong (1999, p.
+328; 2000, p.
+475)
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% for journal Sci
+%\reviewreports{\\
+%Reviewer 1 comments and authors’ response\\
+%Reviewer 2 comments and authors’ response\\
+%Reviewer 3 comments and authors’ response
+%}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\end{adjustwidth}
 \end{document}

### 2022-08-26 gibbs_mdpi_submission1.tex
respnonse letter

--- 2022-08-26 gibbs_mdpi.tex
@@
 \usepackage{subfig}
-\usepackage[textsize=small]{todonotes}
 \newcommand{\ie}{\textit{i.~e.} }
@@
 \section{Introduction\label{sec: intro}}
-\subsection{Water desalination technologies}
+\subsection{Water desalination technologies.}
 Two basic approaches for separating water from salt are present in modern desalination technology \cite{Miller2003,Curto2021}.
@@
 
-\subsection{Hydrogels for desalination}
+\subsection{Hydrogels for desalination.}
 Hydrogels are three-dimensional networks of polymer chains that are crosslinked by either physical or chemical bonds. 
@@
 
-\subsection{Physics behind the desalination process}
+\subsection{Physics behind the desalination process.}
 %The maximum entropy principle requires the density of charges to be more-less the same throughout the system medium. 
@@
 is defined by Donnan law \cite{Rud2018}
-\begin{equation}
+\begin{equation*}
 \frac{\ccl\gel}{\cs}=\frac{\cs}{\cna\gel}=\sqrt{1+\left(\frac{\alpha}{2\cs\Vgel}\right)^{2}}\pm\frac{\alpha}{2\cs\Vgel}
-\end{equation}
+\end{equation*}
 where $\ccl\gel$ and $\cna\gel$ are the internal concentration of monovalent anions and cations, $\cs$ is the salinity of external solution,  $\Vgel$ is the gel molar volume (inverse density of gel segments) and $\alpha$ is ionization degree (in the case of our study $\alpha=1$).
@@
 \end{figure*}
-\subsection{Open system}
+\subsection{Open system.}
 We simulate the open system using the grand reaction method \cite{Landsgesel2020a,Rud2020}.
@@
 The insertion (and deletion) of ion pairs is considered as a reaction of creation (or annihilation) of an ion pair 
-\begin{equation}
+\[
 \varnothing\stackrel{K}{\leftrightarrows}\na+\cl
-\end{equation}
+\]
 with a reaction constant defined by the chemical potential of ions,
@@
 
-\subsection{Closed system}
+\subsection{Closed system.}
 The similar scheme we use to simulate the gel in closed system. 
@@
 
-\subsection{Algorithm}
+\subsection{Algorithm.}
 The thermodynamic equilibrium between the two volumes implies the exchange of ion pairs between them, which is done by means of MC procedure in a way similar to described in \cite{Panagiotopoulos1988b}.
@@
 
-\subsection{Compression in open system}
+\subsection{Compression in open system.}
 \begin{figure*}[h]
@@
 It is caused by the decrease of ions osmotic pressure and by a screening of electrostatic interactions \cite{Zhulina2000, Landsgesel2020a}.
-(The salinity dependence of the size of \emph{weak} polyelectrolyte gel is in general non-monotonic. We discuss this case in \cite{Rud2018}.)
+\footnote{The salinity dependence of the size of \emph{weak} polyelectrolyte gel is in general non-monotonic. We discuss this case in \cite{Rud2018}.}
 
@@
 
-\subsection{Compression in closed system}
+\subsection{Compression in closed system.}
 %Each set of simulations in \emph{open system} defines the free swelling equilibrium states of the gel for each salinity, \ie the state where the gel partial pressure equals zero. 
@@
 
-\subsection{Desalination scheme}
+\subsection{Desalination scheme.}
 As we have seen, the compression of the gel in a closed system affects the salinity, whereas the compression in an open system affects the amount of ions in a volume where the gel is compressed in. 
@@
 
-\subsection{The efficiency of desalination}
+\subsection{The efficiency of desalination.}
 The theoretical minimum specific energy for seawater desalination (
@@
 \end{equation}
-\todo{the equation must be supported by referrence}
 Here, in the table, we present the absolute values of the work, whereas one should keep in mind that the compression implies the work is done by external force and the swelling implies that the work is done by gel.

### 2022-08-26 figures/gc.py

@@ -1,4 +1,3 @@
-
 import pandas as pd    
 import scipy
 from veusz_embed import *
@@ -23,7 +22,6 @@ def function(v, a, gamma, b):
 
 gibbs_raw['delta_P_bar_mean'] = gibbs_raw.delta_P_Pa_mean * 1e-5
 gibbs_raw['delta_P_bar_err'] = gibbs_raw.delta_P_Pa_err * 1e-5
-
 
 gibbs_df = pd.DataFrame()
 for (idx, group), color in zip(gibbs_raw.groupby(by = 'n_pairs'), color_cycle):
@@ -96,6 +94,10 @@ for (index, row), color in zip(gibbs_df.iterrows(), color_cycle):
     Ccl0 = Ccl_closed[0][idx0] 
     Ccl5 = Ccl_closed[0][idx5]
     Ccl10 = Ccl_closed[0][idx10]
+
+    Ccl0_err  = Ccl_closed[1][idx0] 
+    Ccl5_err  = Ccl_closed[1][idx5]
+    Ccl10_err = Ccl_closed[1][idx10]
     
     Ncl0 = Ncl_closed[0]
     Ncl5 = Ncl_closed[idx5]
@@ -128,8 +130,11 @@ for (index, row), color in zip(gibbs_df.iterrows(), color_cycle):
     xy.markerSize.val = '4pt'
     xy.MarkerFill.color.val = color
     #####
-    pp = P[0]
-    vv = V
+    pp = np.array(P[0])
+    pp_err = np.array(P[1])
+    pp_ceil = np.array(P[0]+0.5*P[1])
+    pp_floor = np.array(P[0]-0.5*P[1])
+    vv = np.array(V)
     cc = Ccl_closed[0]
     pp = np.delete(pp,np.argwhere(P[0]<0))
     pp = np.delete(pp,np.argwhere(P[0]>5))
@@ -138,6 +143,13 @@ for (index, row), color in zip(gibbs_df.iterrows(), color_cycle):
     cc = np.delete(cc,np.argwhere(P[0]<0))
     cc = np.delete(cc,np.argwhere(P[0]>5))
 
+    pp_err = np.delete(pp_err, np.argwhere(P[0]<0))
+    pp_ceil = np.delete(pp_ceil,np.argwhere(P[0]<0))
[…]

### 2022-08-26 sympy_donnan.py

@@ -1,5 +1,19 @@
 # %%
 from sympy import Symbol, Eq, solve, sqrt, latex
+
+
+
+x     = Symbol("x", positive=True)  # number of all particles
+gamma = Symbol("gamma", positive=True)  # number of all particles
+N     = Symbol("N", positive=True)  # number of all particles
+NA    = Symbol("NA", positive=True)  # number of all particles
+NA    = Symbol("NA", positive=True)  # number of all particles
+
+
+eq = x**2*(gamma**2-1)+x*(2*N-gamma**2*NA) - N**2
+solve(eq, x)
+
+
 # KNOWN
 N_pairs = Symbol("N_pairs", positive=True)  # number of all particles
 # v= Symbol("v", positive = True) #relative volume of the gel

### 2022-08-26 zip.sh
cleanup

@@ -1,33 +1,0 @@
-#!/bin/bash
-
-#rm -r zip/figs || mkdir -p zip/figures
-
-# chek that esi is up to date
-#latexmk -pdf scf-gel
-#latexmk -pdf esi
-
-name="gibbs"
-
-main_file=$name".tex"
-files="definitions.tex gibbs.pdf gibbs.bbl esi.pdf esi.tex"
-figs=`grep 'includegraphics' $main_file | grep -v "grep"| grep -v '%.include' |sed 's/^.*\\includegraphics.*{fig/fig/' |  grep eps | sed 's/\.eps.*$/\.eps/' | sed 's/\}//g'`
-figs="$figs `grep 'includegraphics' $main_file          | grep -v '%.include' |sed 's/^.*\\includegraphics.*{fig/fig/' |  grep png | sed 's/\.png.*$/\.png/' | sed 's/\}//g'`"
-figs="$figs `grep 'includegraphics' $main_file          | grep -v '%.include' |sed 's/^.*\\includegraphics.*{fig/fig/' |  grep pdf | sed 's/\.pdf.*$/\.pdf/' | sed 's/\}//g'`"
-#echo "figs: $figs";
-
-for f in $figs; do echo $f; done
-
-zip $name.zip $main_file $files $figs
-
-echo "Test whether it works"
-mkdir -p try
-rm -r try/* 
-echo "wd: `pwd`"
-cd try
-echo "wd: `pwd`"
-cp ../$name.zip ./
-unzip $name.zip
-echo "wd: `pwd`"
-latexmk -pdf $name && evince $name".pdf"
-
-

### 2022-08-26 zip.sh
zip.sh

@@ -1,0 +1,33 @@
+#!/bin/bash
+
+#rm -r zip/figs || mkdir -p zip/figures
+
+# chek that esi is up to date
+#latexmk -pdf scf-gel
+#latexmk -pdf esi
+
+name="gibbs"
+
+main_file=$name".tex"
+files="definitions.tex gibbs.pdf gibbs.bbl esi.pdf esi.tex"
+figs=`grep 'includegraphics' $main_file | grep -v "grep"| grep -v '%.include' |sed 's/^.*\\includegraphics.*{fig/fig/' |  grep eps | sed 's/\.eps.*$/\.eps/' | sed 's/\}//g'`
+figs="$figs `grep 'includegraphics' $main_file          | grep -v '%.include' |sed 's/^.*\\includegraphics.*{fig/fig/' |  grep png | sed 's/\.png.*$/\.png/' | sed 's/\}//g'`"
+figs="$figs `grep 'includegraphics' $main_file          | grep -v '%.include' |sed 's/^.*\\includegraphics.*{fig/fig/' |  grep pdf | sed 's/\.pdf.*$/\.pdf/' | sed 's/\}//g'`"
+#echo "figs: $figs";
+
+for f in $figs; do echo $f; done
+
+zip $name.zip $main_file $files $figs
+
+echo "Test whether it works"
+mkdir -p try
+rm -r try/* 
+echo "wd: `pwd`"
+cd try
+echo "wd: `pwd`"
+cp ../$name.zip ./
+unzip $name.zip
+echo "wd: `pwd`"
+latexmk -pdf $name && evince $name".pdf"
+
+

### 2022-09-01 MDPI/response_letter.tex
Update MDPI/response_letter.tex
Update MDPI/response_letter.tex, gibbs.tex

@@
 \item \textit{Where is the method of this work?}
+We did not want to bother the readers too much with technical aspects of the smulations. 
+The method idea is outlined in the paragraph "Physics behind the desalination process" and in the section "Theory behind the simulation". Some more technical issues are in ESI.
 \item \textit{It is suggested that to carefully improve this manuscript as well as the writing and grammatical error.}
@@
 
-\textbf{Reviewer 2}
+\textbf{Reviewer 3}
 
@@
 \item \textit{The full stop in the title should be revised.}
+Noted. Revised.
 \item \textit{The abstract needs to be revised and be more attractive. The research gap, novelty and main findings should be concisely mentioned in the abstract.}
@@
 }
+We identified the study limitations and considered the implications and future perspectives of the study. We added the respective paragraphs.
 \end{enumerate}

### 2022-09-01 Creta_ecis2022/presentation/beamer.tex
presentation for ecis

@@
 
-\title{Modeling of weak polyelectrolyte hydrogels under compression. }
-\subtitle{Implications for water desalination.}
+\title{Water desalination using polyelectrolyte hydrogel.  }
+\subtitle{Gibbs ensemble modelling.}
 % \date{\today}
@@
 \section[Intro]{Introduction}
+\begin{frame}[fragile]{Introduction. Desalination.}
+\begin{enumerate}
+\item Distillation
+\item Reverse osmosis
+\item Forward osmosis
+\end{enumerate}
+\end{frame}
+\begin{frame}[fragile]{Introduction. Forward osmsis.}
 
-\begin{frame}[fragile]{Introduction}
+\begin{enumerate}
+	\item Hydrogels for desalination
+	\item Forward osmosis
+	\item Various stimuli: thermo-, pH-, electric-, magnetic-, light-indused gel shrinkage
+\end{enumerate}
+\begin{figure}[t]
+	{\includegraphics[width=\columnwidth]{{figures/FO}.png}}
+\end{figure}
+\end{frame}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}[fragile]{Introduction. Manfred Wilhelm experiment}
 	\begin{columns}[T,onlytextwidth]% COLUMNS
-		\column{0.5\textwidth}
+		\column{0.4\textwidth}
 			\begin{figure}[t]
-				{\includegraphics[width=\columnwidth]{{figures/gibbs_ca}.pdf}}
+				{\includegraphics[width=0.9\columnwidth]{{figures/exp}.png}}
 			\end{figure}
 
-		\column{0.5\textwidth}
-	\begin{itemize}
-		\item Desalination
-		\item Hydrogels for desalination 
-		\item Forward osmosis
-		\item Various stimuli: thermo-, pH-, electric-, magnetic-, light-indused gel collapse
-		\item Manfred Wilhelm and Yu Chi experiment
-	\end{itemize}
+		\column{0.6\textwidth}
+			\begin{figure}[t]
+				{\includegraphics[width=0.9\columnwidth]{{figures/scheme}.png}}
+			\end{figure}
+	\end{columns}% COLUMNS
 
-	\end{columns}% COLUMNS
-	{\scriptsize 
-	Fengler, C., Arens, L., Horn, H., Wilhelm, M.
+	{\scriptsize Fengler, C., Arens, L., Horn, H., Wilhelm, M.
 (2020).
@@
 \end{frame}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\begin{frame}[fragile]{Donnan prediction}
+\section[Model]{Model of the gel}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}[fragile]{Model of the gel}
   \begin{columns}[T,onlytextwidth]% COLUMNS
@@
 \includegraphics[height=4.5cm]{figures/gel_donnan.png}
-\caption{The compression of hydrogel  affects the ionic composition of supernatant}
 \end{figure}
@@
 \begin{itemize}
-\item Donnan equilibrium
-$c_s^2 = c^{in}_{Na}\cdot c^{in}_{Cl}$
-\item Electroneutrality
-$\alpha N$ of self charges\\
-$\alpha N$ of neutralizing counterions\\
-$c^{in}_{Cl}$ of free ion pairs
-\item
-By compression to the dry state 
-one can exclude brine of concentration
-\begin{equation*}
-N_{excl}/V=\begin{cases}
-c_s^{in}<c_s,\\
-\\
-c_s^{in}+\alpha N/V_{gel}>c_s,
-\end{cases}
-\end{equation*}
+\item The gel is a particle of mAcro size 
+\item In aqueous solution
+\item Infinite network of polymer chains
+\item Each bead is charged
 \end{itemize}
@@
   \end{columns}% COLUMNS
+\begin{itemize}
+\item The gel itself is a membrane
+\item Donnan equilibrium
+$c_s^2 = c^{in}_{Na}\cdot c^{in}_{Cl}$
+\item The compression of hydrogel  affects the ionic composition of supernatant
+\end{itemize}
 
 \end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}[fragile]{Model of the gel. Two ensembles.}
+
+	\begin{columns}[T,onlytextwidth]% COLUMNS
+		\column{0.5\textwidth}
+			\begin{figure}[t]
+				{\includegraphics[width=0.9\columnwidth]{{figures/gc}.pdf}}
+			\end{figure}
+			\centering Open system \\(grand-cannonical ensemble)
+		\column{0.5\textwidth}
+			\begin{figure}[t]
+				{\includegraphics[width=0.9\columnwidth]{{figures/gibbs}.pdf}}
+			\end{figure}
+			\centering Closed system \\(Gibbs ensemble)
+	\end{columns}% COLUMNS
+
+\end{frame}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2022-09-02 gibbs.tex
Update MDPI/response_letter.tex, gibbs.tex

@@
 
-\title{Water desalination using polyelectrolyte hydrogel. Gibbs ensemble modeling}
+\title{Water desalination using polyelectrolyte hydrogel: Gibbs ensemble modeling}
 
@@
 
-We model the gel as a network of 16 linear polymer chains, each by 30 monomer units. 
-The chains are connected to a diamond-like polymer network throught 8 crosslinking units, and put into a simulation box with periodic boundaries (see \reffig{fig:diamond}). 
-Each unit of the network carries a negative electric charge, which is equal to the charge of electron. 
-Except the particles of the network, the monovalent co- and counter-ions ions, $\cl$ and $\na$, are present in simulation box. 
-The total electric charge of all the particles in the box is zero, therefore the amount of $\na$ ions is bigger than that of $\cl$ by the number of hydrogel units, $\Ngel=16\cdot30 + 8=488$.
+Our model of the gel is a network of 16 linear polymer chains, each consisting of 30 monomer units. 
+These polymer chains are connected to a diamond-like network by 8 crosslinking units.
+This means, there are together $\Ngel=16\cdot30 + 8=488$ gel monomers in the simulation box (see \reffig{fig:diamond}).
+Each monomer unit of the network carries a negative elementary electric charge, thus simulating fully ionized polyacidic gel.
+Except the particles in the network, the monovalent co- and counter-ions ions, $\cl$ and $\na$, are present in simulation box. 
+The total electric charge of all the particles in the box is zero, therefore the amount of $\na$ ions is bigger than that of $\cl$ by the number of hydrogel units.
+The entire simulation box setup employs periodic boundaries.
 
@@
 \end{figure*}
+
 We simulate the compression of the gel in two ensembles.
@@
 
+\subsection{Study limitations}
+TODO
+
+\subsection{Implications and future perspectives}
+TODO
+
 \section*{Acknowledgments}

### 2022-09-02 gibbs.tex
Update gibbs.tex

@@
 
-We simulate the compression of the gel in two ensembles.
+\subsection{Gibbs ensemble}
+\todoi{We have the "Gibbs ensemble" in the title, and this term is not used in the manuscript at all.}
+TODO concise description of Gibbs ensemble
+
+The simulation of the gel compression is performed in two ensembles:
 \begin{enumerate}
-\item The first is so called \emph{open system}, when the simulation box with gel freely exchanges ions with a big amount of aqueous solution of certain constant salinity, $\cs$. 
-\item And in \emph{closed system}, when the gel is in equilibrium with a finite volume of aqueous solution.
+\item \emph{open system}, when the simulation box with gel exchanges ions with an infinite reservoir containing aqueous solution of constant salinity, $\cs$. 
+\item emph{closed system}, when the simulation box with the gel exchanges ions with a finite volume of aqueous solution.
 \end{enumerate}
-The compression of the gel in the \emph{open} system does not affect the surrounding salinity, thus the density of ions outside the gel remains constant $\cs =$ $\cna=$ $\ccl=$ $\text{Const}$ (\reffig{fig: open}).
-On the contrary, what remains constant in the \emph{closed} system, is the total number of $\na$ and $\cl$ ions, that are contained in the gel and in the external volume, \ie in the volume $\Vbox$ (\reffig{fig: closed}).
+The compression of the gel in the \emph{open system} does not affect the salinity in the reservoir, thus the density of ions outside the gel remains constant $\cs =$ $\cna=$ $\ccl=$ $\text{Const}$ (\reffig{fig: open}).
+On the contrary, the compression of the gel in the \emph{closed system} changes the salinity in the reservoir, but the total number of $\na$ and $\cl$ ions in the gel and in the reservoir, \ie in the volume $\Vbox$ (\reffig{fig: closed}), remains constant.
 

### 2022-09-02 gibbs.tex
Update gibbs.tex

@@
 
-\paragraph{Water desalination technologies.}
+\paragraph{Water desalination technologies}
 
@@
 
-\paragraph{Hydrogels for desalination.}
+\paragraph{Hydrogels for desalination}
 Hydrogels are three-dimensional networks of polymer chains that are crosslinked by either physical or chemical bonds. 
@@
 
-\paragraph{Physics behind the desalination process.}
+\paragraph{Physics behind the desalination process}
 %The maximum entropy principle requires the density of charges to be more-less the same throughout the system medium. 
@@
 
-%Let $\nna$ and $\ncl$ be the density of the corresponding ion in the compression volume, $\Vbox$ averaged over this volume
+The amount of the individual ion types in gel, $N_i$, is given by
 \begin{equation}
@@
 \end{equation}
-where $i \in \{\na, \cl\}$,  $N_i$ is the amount of the corresponding ions in gel, $\Vgel$~--- volume of the gel, $\Vbox$~--- the volume in which the gel is compressed. 
-As $\Vbox$ we choose the volume of the gel in the free swelling equilibrium state.
+where $i \in \{\na, \cl\}$, $\Vgel$~--- volume of the gel, $\Vbox$~--- the volume in which the gel is compressed. 
+Vbox$ is the gel volume in the free swelling equilibrium state.
 
-%Then in closed system $\nna$ and $\ncl$ remain constant, whereas the salinity of supernate, $\cs$, may change with the change of the gel volume.
-
-\paragraph{Open system.}
+\paragraph{Open system}
 We simulate the open system using the grand reaction method \cite{Landsgesel2020a,Rud2020}.
-This method is a hybrid of molecular dynamics (MD) and Monte Carlo (MC). 
-The whole simulation represents a chain of subsimulations of MD and MC followed one by each other. 
-For MD simulation we used a standard Langevin dynamics \cite{Grest1986} which models the mechanical movement of all the system particles. 
-Whereas MC simulates the thermodynamic equilibrium with reservoir, which exchanges ions with the simulation box. 
+This method is a hybrid of Molecular dynamics (MD) and Monte Carlo (MC). 
+The whole simulation consists of MD and MC subsimulations, followed one by each other. 
+The MD simulation is a standard Langevin dynamics \cite{Grest1986}, which models the mechanical motion of all particles in the system. 
+MC simulates the thermodynamic equilibrium with reservoir and handles the ion exchange with the simulation box. 
 The insertion (and deletion) of ion pairs is considered as a reaction of creation (or annihilation) of an ion pair 
@@
 
-\paragraph{Closed system.}
-The similar scheme we use to simulate the gel in closed system. 
+\paragraph{Closed system}
+Analogical scheme simulates the gel in the closed system. 
 The procedure represents a chain of subsequent MD and MC simulation, but now the molecular dynamics is running in two simulation boxes simultaneously.
@@
 
-\paragraph{Algorithm.}
+\paragraph{Algorithm}
 The thermodynamic equilibrium between the two volumes implies the exchange of ion pairs between them, which is done by means of MC procedure in a way similar to described in \cite{Panagiotopoulos1988b}.
@@
 
-\paragraph{Compression in open system.}
+\paragraph{Compression in open system}
 \begin{figure*}[t]
@@
 
-\paragraph{Compression in closed system.}
+\paragraph{Compression in closed system}
 %Each set of simulations in \emph{open system} defines the free swelling equilibrium states of the gel for each salinity, \ie the state where the gel partial pressure equals zero. 
@@
 
-\paragraph{Desalination scheme.}
+\paragraph{Desalination scheme}
 As we have seen, the compression of the gel in a closed system affects the salinity, whereas the compression in an open system affects the amount of ions in a volume where the gel is compressed in. 

### 2022-09-02 gibbs.tex
Update gibbs.tex

@@
 the individual ion types (red: $\na$, blue: $\cl$, yellow: $\ca$)
-and the hydrogel (gray: neutral segment ($\AH$), cyan: charged segment
+and the hydrogel (grey: neutral segment ($\AH$), cyan: charged segment
 ($\A$)). \label{fig:open and closed}.}
@@
 \paragraph{Open system}
-We simulate the open system using the grand reaction method \cite{Landsgesel2020a,Rud2020}.
+We use the grand reaction method \cite{Landsgesel2020a,Rud2020} to simulate the open system.
 This method is a hybrid of Molecular dynamics (MD) and Monte Carlo (MC). 
-The whole simulation consists of MD and MC subsimulations, followed one by each other. 
+The whole simulation consists of MD and MC subsimulations, consecutively followed one by each other. 
 The MD simulation is a standard Langevin dynamics \cite{Grest1986}, which models the mechanical motion of all particles in the system. 
@@
 $K=\exp\left(\muna+\mucl\right).$
+The simulation setup is sketched in \reffig{fig:open}.
 
 \paragraph{Closed system}
-Analogical scheme simulates the gel in the closed system. 
-The procedure represents a chain of subsequent MD and MC simulation, but now the molecular dynamics is running in two simulation boxes simultaneously.
-The first box of the volume $\Vgel$ contains the gel with ions, and the second box, $\Vout$--- contains only ions. 
-The total volume of both boxes is kept constant, $\Vbox=V_{\mathrm{gel}}+V_{\mathrm{out}}$, so the compression of the gel implies the decreasing $\Vgel$ and increasing $\Vout$.
-These two boxes are represented in \reffig{fig:diamond}.
+Analogical scheme is used for the simulation of the gel in the closed system. 
+The procedure  again consists of subsequent MD and MC subsimulation, but now the MD is running in two simulation boxes simultaneously.
+The first box of the volume $\Vgel$ contains the gel with ions and the second box of the volume $\Vout$ contains only ions. 
+The total volume of both boxes is constant, $\Vbox=V_{\mathrm{gel}}+V_{\mathrm{out}}$, so the gel compression implies the decrease of $\Vgel$ and increase of $\Vout$.
+The simulation setup is sketched in \reffig{fig:closed}.
 

### 2022-09-02 gibbs.tex
Update gibbs.tex

@@
 \paragraph{Algorithm}
-The thermodynamic equilibrium between the two volumes implies the exchange of ion pairs between them, which is done by means of MC procedure in a way similar to described in \cite{Panagiotopoulos1988b}.
-The simulation algorithm is following:
+The thermodynamic equilibrium between the two subvolumes implies the exchange of ion pairs between them.
+This is performed by means of MC procedure in a way similar to described in \cite{Panagiotopoulos1988b}.
+
+As mentioned above, the simulation consists of MD and MC subsimulations. The algorithm is following:
 \begin{enumerate}
-\item Simulate molecular dynamics in both boxes; collect the observables, for example, values of pressure $P$, to an array; 
-\item Perform Monte-Carlo procedure simulating ion pair exchange; collect the arrays of observables samples: number of ions in both boxes, 
+\item Simulate MD in both boxes and collect the observables (pressure, $P$)
+\item Perform MC procedure simulating ion exchange and collect the observables (number of ions in both boxes, 
 %$\nna\gel$,
@@
 %$\nna\out$ 
-and $\Ncl\out$ ; 
+and $\Ncl\out$ )
 \item Repeat the procedure until the desired length of sample arrays is reached.

### 2022-09-02 MDPI/response_letter.tex
Update MDPI/response_letter.tex, gibbs.tex
Update MDPI/response_letter.tex

@@
 \item \textit{Avoid to use word 'we' in the abstract as well as manuscript.}
+Corrected.
 \item \textit{line 247 in what table?}
@@
 We did not want to bother the readers too much with technical aspects of the smulations. 
-The method idea is outlined in the paragraph "Physics behind the desalination process" and in the section "Theory behind the simulation". Some more technical issues are in ESI.
+The method idea is outlined in the paragraph "Physics behind the desalination process" and described in the section "Theory behind the simulation". Some more technical issues are in ESI.
 \item \textit{It is suggested that to carefully improve this manuscript as well as the writing and grammatical error.}
+We improved the writing style of the manuscript and corrected the grammatical errors.
 \item \textit{Please explain more detail about the process, how the process run and how the data could be explained and become more interesting for reader.}
@@
 \item \textit{In this current shape, the manuscript looks like a report. The authors have to revise the flow of the context to attract the readers.}
+We have revised and changed the manuscript to be more attractive for the readers. 
 \item \textit{The manuscript must be improved by checking once again in English and technical writing. }
+We improved the writing style of the manuscript and corrected the grammatical errors.
 
@@
 \item \textit{L 125-126, meaningless sentence. Revise the whole context.}
+Corrected.
 \item \textit{All sections/subsections titles must be revised to be expressive.}

### 2022-09-02 gibbs.tex
Update gibbs.tex, MDPI/response_letter.tex

@@
 \todoi{We have the "Gibbs ensemble" in the title, and this term is not used in the manuscript at all.}
-TODO concise description of Gibbs ensemble
+TODO concise description of Gibbs ensemble, solving the task to Reviewer 2, Q5 and Q7
 
@@
 
+\subsection{Simulations}
+TODO put here the parts from "Results and Discussion", which are actually neither Results nor Discussion
+\paragraph{Compression in the \emph{open system}}
+\paragraph{Compression in the \emph{closed system}}
+
 \section{Results and discussion }
@@
 \caption{
-The compression of the gel in open system (solid lines) and in closed system (dotted lines). 
-Each solid curve corresponds to different salinity of the reservoir $\cs$ (see legend). Shadowed area limit the states with applied pressure below zero and above 5 bar.\label{fig: PV and CV}}
+The compression of the gel in the \emph{open system} (solid lines) and in the \emph{closed system} (dotted lines). 
+Each solid curve corresponds to different salinity of the reservoir $\cs$ (see legend).
+The shadowed areas limit the states with applied pressure below zero and above 5 bar.\label{fig: PV and CV}}
 \end{figure*}
@@
 {\includegraphics[width=0.495\textwidth]{figures/fig_NVbox_mu_pub.pdf}}
-\caption{The compression of the gel in \emph{open system} (solid lines) and in \emph{closed system} (dotted lines). 
-Shadowed area limit the states with applied pressure below zero and above 5 bar.
+\caption{The compression of the gel in the \emph{open system} (solid lines) and in the \emph{closed system} (dotted lines). 
+The shadowed areas limit the states with applied pressure below zero and above 5 bar.
 The values $N_\cl$ are the virtual numbers of present $\cl$ ions in \emph{closed system} simulation boxes.

### 2022-09-03 Creta_ecis2022/presentation/beamer.tex
beamer

@@
 \newcommand{\cp}{c_\mathrm{p}}
+\newcommand{\muna}{\mu_\mathrm{Na^+}}
+\newcommand{\mucl}{\mu_\mathrm{Cl^-}}
+\newcommand{\muca}{\mu_\mathrm{Ca^{2+}}}
+\newcommand{\muh}{\mu_\mathrm{H^+}}
+\newcommand{\mua}{\mu_\mathrm{A^-}}
+\newcommand{\muha}{\mu_\mathrm{HA}}
+\newcommand{\muoh}{\mu_\mathrm{OH}}
+\newcommand{\cna}{c_\mathrm{Na^+}}
+\newcommand{\ccl}{c_\mathrm{Cl^-}}
+\newcommand{\cca}{c_\mathrm{Ca^{2+}}}
+\newcommand{\ch}{c_\mathrm{H^+}}
+
+\newcommand{\nna}{N_\mathrm{Na^+}}
+\newcommand{\ncl}{N_\mathrm{Cl^-}}
+\newcommand{\nca}{N_\mathrm{Ca^{2+}}}
+
 \newcommand{\kT}{kT}
@@
 
-\section[Model]{Model of the gel}
+\section{The model of a polyelectrolyte gel.}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\section{The model of a polyelectrolyte gel.}
+\subsection{Grand-cannonical ensemble.}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{frame}{Grand-cannonical ensemble.}
+	\begin{columns}[T,onlytextwidth]% COLUMNS
+	\column{0.5\textwidth}
+	\column{0.5\textwidth}
+	The free energy of the grand-canonical ensemble exchanging ion pair with the bath
+	\begin{equation*}
+		\boxed{
+		\Omega=E-TS+\mu N}
+	\end{equation*}
+	The entropy $S$ expands via Boltzmann formula
+		\begin{equation*}
+			S=k_{B}\ln\frac{V^{N}}{N!}\label{eq:entropy}
+		\end{equation*}
+	\end{columns}% COLUMNS		
+	The change of free energy associated with a single particle exchange is 
+	\begin{equation*}
+		\boxed{
+		\Delta\Omega=k_BT\xi\ln V \left(N+\theta(\xi)\right)+\xi\mu+\Delta E\label{eq: DeltaG GC}}
+	\end{equation*}
+	{\tt accept if $\mathcal{R}^{\xi}<e^{\Delta\Omega/k_BT}$}
+\end{frame}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Gibbs ensemble.}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{Gibbs ensemble.}
+	\begin{columns}[T,onlytextwidth]% COLUMNS
+		\column{0.5\textwidth}
+		\begin{figure}[t]
+			{\includegraphics[width=0.9\columnwidth]{{figures/simgibbs}.pdf}}
+		\end{figure}
+		\column{0.5\textwidth}
+			The free energy of the grand-canonical ensemble for single particle type
+	\begin{equation*}
+		\boxed{
+		\Omega=E_1+E_2-TS}
+	\end{equation*}
+
+	\begin{equation}
+		S=k_B \ln \frac{V_1^{N_1}}{N_1!}\frac{V_2^{N_2}}{N_2!}
+	\end{equation}
+	\end{columns}% COLUMNS		
+	The change of free energy associated with a single particle exchange is 
+	\begin{equation*}
+		\boxed{
+		\Delta\Omega=k_BT\xi \ln\left(\frac{V_1}{V_2}\frac{N_2+\theta(-\xi)}{N_1+\theta(\xi)}\right)+\Delta E_1 +\Delta E_2\label{eq: DeltaG GC}}
+	\end{equation*}
+	{\tt accept if $\mathcal{R}^{\xi}<e^{\Delta\Omega/k_BT}$}
+
+\end{frame}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection{Langevin dynamics.}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{frame}{Langevin dynamics. }
@@
 {
-\begin{frame}{Grand-reaction ensemble.}
-	\textbf{Grand canonical ensemble}\\ 
-	\vspace{1cm}
-	The free energy of the grand-canonical ensemble for single particle type
-	\begin{equation*}
-		\boxed{
-		\Omega=E-TS+\mu N\label{eq:Omega-GC}}
-	\end{equation*}
-	The entropy $S$ expands via Boltzmann formula
-	\begin{columns}[T,onlytextwidth]% COLUMNS
-		\column{0.5\textwidth}
-			\begin{equation*}
-				S=k_{B}\ln\frac{V^{N}}{N!}\label{eq:entropy}
-			\end{equation*}
-		\column{0.5\textwidth}
-			\begin{equation*}
-				\Omega=E-k_BT\ln\frac{V^N}{N!}+\mu N \label{eq: Omega_GC}
-			\end{equation*}
-	\end{columns} % COLUMNS
-	The change of free energy associated with a sngle particle exchange is 
-	\begin{equation*}
-		\boxed{
-		\Delta\Omega=k_BT\ln\left(V^{\xi}\frac{N!}{\left(N+\xi\right)!}\right)+\xi\mu+\Delta E\label{eq: DeltaG GC}}
-	\end{equation*}
-	{\tt accept if $\mathcal{R}^{\xi}<e^{\Delta\Omega/k_BT}$}
-\end{frame}
+
 }
@@
 
-\end{frame}
-
-\begin{frame}{Grand-reaction ensemble.}
-
-	\begin{columns}[T,onlytextwidth]% COLUMNS
-		\column{0.5\textwidth}
-			\begin{figure}
-				\includegraphics[height=4.cm]{figures/standard_states.pdf}
-			\end{figure} 
-		\column{0.5\textwidth}	
-			\textbf{Moderate pH conditions}\\ 
-			\vspace{1cm}
-			The reaction of an acidic unit 
-			\begin{equation*}
-				\mathrm{HA}\stackrel{K}{\leftrightarrows}\mathrm{A^-}+\mathrm{H^+}\label{eq: acid reaction}
-			\end{equation*}
-	Is happening only simultaneously with one of these two
-	\begin{eqnarray*}
-		\h&\leftrightarrows&\na \label{eq:hna} \\
-		2\h&\leftrightarrows&\ca \label{eq:hca}
-	\end{eqnarray*}
-
-	\end{columns} % COLUMNS
-\begin{eqnarray*}
-\mathrm{HA}\stackrel{K'}{\leftrightarrows}\mathrm{A}^{-}+\na, &K' = K \exp(\mu_\h-\mu_\na) \\
-2\mathrm{HA}\stackrel{K''}{\leftrightarrows}2\mathrm{A}^{-}+\ca, &K'' = K \exp(2\mu_\h-\mu_\ca)
-\end{eqnarray*}
 \end{frame}

### 2022-09-03 Creta_ecis2022/presentation/beamer.tex
presentation finalized (almost)

@@
 \begin{frame}[fragile]{Introduction. Desalination.}
+
 			\begin{enumerate}
@@
 			\end{enumerate}
+
+		\begin{figure}[t]
+			{\includegraphics[width=0.6\columnwidth]{{figures/RO}.pdf}}
+		\end{figure}
 \end{frame}
@@
 	\begin{columns}[T,onlytextwidth]% COLUMNS
-		\column{0.4\textwidth}
+		\column{0.5\textwidth}
 			\begin{figure}[t]
-				{\includegraphics[width=0.9\columnwidth]{{figures/exp}.png}}
+				{\includegraphics[width=\columnwidth]{{figures/experiment}.pdf}}
 			\end{figure}
 
-		\column{0.6\textwidth}
+		\column{0.5\textwidth}
 			\begin{figure}[t]
@@
 	\end{columns}% COLUMNS
+
+	\vspace{1cm}
 
@@
 			\centering Closed system \\(Gibbs ensemble)
+	\end{columns}% COLUMNS
+
+\end{frame}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}[fragile]{Carnot cycle for desalination}
+
+	\begin{columns}[T,onlytextwidth]% COLUMNS
+		\column{0.3	\textwidth}
+			\begin{figure}[t]
+				{\includegraphics[width=0.9\columnwidth]{{figures/carnot}.pdf}}
+			\end{figure}
+
+		\column{0.7\textwidth}
+		\begin{enumerate}
+			\item A fully reversible desalination cycle 
+			\item Analogy with Carnot cycle
+		\end{enumerate}
+		{\centering
+			\begin{figure}[t]
+				{\includegraphics[width=0.6\columnwidth]{{figures/cycles}.pdf}}
+			\end{figure}
+		}
+		\begin{flushright}
+		 Rud, et al. (2018). 
+		 \end{flushright}
 	\end{columns}% COLUMNS
@@
 
-\subsection{Grand-reaction ensemble.}
-
-{
-\usebackgroundtemplate{\includegraphics[width=\paperwidth]{figures/grand_reaction_model.png}}
-\begin{frame}{Grand-reaction ensemble.}
-\begin{columns}[T,onlytextwidth]% COLUMNS
-\column{0.3\textwidth}
-\vspace{4.5cm}
-Ionization equilibrium in \textbf{reaction} ensemble
-\begin{equation*}
-	\boxed{
-		\mathrm{pA^- + H_3O^+ \leftrightarrows pAH}
-	}
-\end{equation*}
-
-\column{0.4\textwidth}
-Constant salinity 
-\begin{equation*}
-\boxed{c_s = c_\mathrm{Cl}^- = c_\mathrm{Na}^+}
-\end{equation*}
-The simulation box freely 
-exchanges ions with reservoir as in \textbf{grand cannonical} ensemble
-\end{columns} % COLUMNS
-\vspace{0.5cm}
-{\scriptsize Landsgesell, J., Hebbeker, P., Rud, O., Lunkad, R., Košovan, P., \\ Holm, C. (2020). 
-{\bf Grand-Reaction Method for Simulations of Ionization \\
-Equilibria Coupled to Ion Partitioning. }
-Macromolecules, 53(8), 3007–3020. }
-\end{frame}
-}
-
-{
-
-}
-
-{
-
-\begin{frame}{Grand-reaction ensemble.}
-
-	\begin{columns}[T,onlytextwidth]% COLUMNS
-		\column{0.5\textwidth}
-			\begin{figure}
-				\includegraphics[height=4.cm]{figures/standard_states.pdf}
-			\end{figure} 
-		\column{0.5\textwidth}	
-			\textbf{Reaction ensemble}\\ 
-			\vspace{1cm}
-			The reaction of an acidic unit 
-			\begin{equation*}
-				\mathrm{HA}\stackrel{K}{\leftrightarrows}\mathrm{A^-}+\mathrm{H^+}\label{eq: acid reaction}
-			\end{equation*}
-			\begin{equation*}
-				\Omega=E-TS+\sum_i\left(\mu_i-\mu^\ominus_i\right) N_i\label{eq:Omega-RE}
-			\end{equation*}
-	\end{columns} % COLUMNS
-	\vspace{1cm}
-	Then the change of system free energy during a single reaction step
-	\begin{equation*}
-		\Delta\Omega=k_BT\ln\left(\prod_i V^{\nu_i\xi}\frac{N_i!}{\left(N_i+\nu_i\xi\right)!}\right)+
-		\xi\left(\sum_i\nu_i\mu_i-\sum_i\nu_i\mu_i^\ominus\right)+\Delta E
-		\label{eq: DeltaG RE one}
-	\end{equation*}
-	{\tt accept if $\mathcal{R}^{\xi}<e^{\Delta\Omega/k_BT}$}
-\end{frame}
-}
-
-\begin{frame}{Grand-reaction ensemble.}
-\begin{columns}[T,onlytextwidth]% COLUMNS
-\column{0.7\textwidth}
-\begin{equation*}\boxed{
-\Delta\Omega=k_BT\ln\left(K^\xi\prod_i V^{\nu_i\xi}\frac{N_i!}{\left(N_i+\nu_i\xi\right)!}\right)+\Delta E}
-\end{equation*}
-\column{0.3\textwidth}
-\begin{equation*}\boxed{
-K = e^{-\sum_i\nu_i \mu_i^\ominus }} 
-\end{equation*}
-\end{columns} % COLUMNS
-
-\vspace{0.6cm}
-\begin{columns}[T,onlytextwidth]% COLUMNS
-\column{0.5\textwidth}
-	\begin{equation*}
-		\mathrm{HA}\stackrel{K}{\leftrightarrows}\mathrm{A^-}+\mathrm{H^+} 
-	\end{equation*}
-	\begin{equation*}
-		K= \mu_\h^\ominus+\mu_\mathrm{A^-}^\ominus - \mu_\mathrm{HA}^\ominus
-	\end{equation*}
-	\vspace{0.2cm}
-\begin{equation*}
-\emptyset \leftrightarrows  \na  +\cl
-\end{equation*}
-\begin{equation*}
-K= \mu_\na+\mu_\cl
-\end{equation*}
-\vspace{0.2cm}
-\begin{equation*}
-\emptyset \leftrightarrows \ca + 2\cl
-\end{equation*}
-\begin{equation*}
-K= 2\mu_\ca+\mu_\cl
-\end{equation*}
-\column{0.5\textwidth}
-			\begin{figure}
-				\includegraphics[height=4.cm]{figures/standard_states.pdf}
-			\end{figure} 
-\end{columns} % COLUMNS
-
-\end{frame}
-
 \begin{frame}{Simulation protocol.}
 \begin{enumerate}
-\item {\tt Choose randomly: LMD, RE, or EX.}	\vspace{0.5cm}
+\item {\tt Choose randomly: LMD, or EX.}	\vspace{0.5cm}
 \item {\tt Simulate the chosen, collecting 50 samples of: }
@@
 	\begin{columns}[T,onlytextwidth]% COLUMNS
+		\column{0.1\textwidth}
 		\column{0.3\textwidth}
@@
    		\column{0.3\textwidth}
-	       		\fbox{\parbox{\textwidth}{RE: number of ionized segments, $\NA$}}
-      		\column{0.3\textwidth}
       		\fbox{\parbox{\textwidth}{EX: number of salt ions, $N_\na$ and $N_\cl$}}
+		\column{0.1\textwidth}
 	\end{columns} % COLUMNS
@@
 
-\begin{frame}{Monovalent salt. Compression.}
+\begin{frame}{Desalination in \{$P$, $V$\} coordinates.}
 	\begin{figure}[t]
-		\subfloat[low salinity, $c_s = 0.007$ mol/l]
-			{\includegraphics[width=0.5\columnwidth]{{figures/gel_pressure_log_density_cs0.006_N_Samples200}.pdf}}
-			{\includegraphics[width=0.5\columnwidth]{{figures/gel_alpha_log_density_cs0.006_N_Samples200}.pdf}}
-		\subfloat[high salinity, $c_s = 0.209$ mol/l]
-			{\includegraphics[width=0.5\columnwidth]{{figures/gel_pressure_log_density_cs0.15_N_Samples200}.pdf}}
-			{\includegraphics[width=0.5\columnwidth]{{figures/gel_alpha_log_density_cs0.15_N_Samples200}.pdf}}
+		{\includegraphics[width=\columnwidth]{{figures/results_1}.pdf}}
 	\end{figure}
@@
 
-\begin{frame}{Monovalent salt. ``No electrostatics'' vs ``Mean field theory''.}
-	\begin{equation*}
-		\frac{\alpha}{1-\alpha}10^{\pK-\pH} =\sqrt{1+\left(\frac{\alpha\cp}{2\cs}\right)^{2}} - \frac{\alpha\cp}{2\cs}
-	\end{equation*}
-	Together with electroneutrality condition it translates to
-	\begin{equation*}
-		-\frac{{{\alpha}^{3}}{\cp}}{{\cs}}+
-		{\alpha}^{2}\left(\frac{{\cp}}{{\cs}}+\Theta-\frac{1}{\Theta}\right)+
-		\frac{2 \alpha}{\Theta}-\frac{1}{\Theta}=0
-	\end{equation*}
-	where $\Theta = 10^{\pK-\pH}$.
-	\begin{figure}
-		\subfloat[low salinity, $c_s = 0.007$ mol/l]
-			{\includegraphics[width=0.47\columnwidth]{{figures/gel_alpha_log_density_lB0.0_cs0.006_N_Samples200}.pdf}}
-\subfloat[high salinity, $c_s = 0.209$ mol/l]
-			{\includegraphics[width=0.47\columnwidth]{{figures/gel_alpha_log_density_lB0.0_cs0.15_N_Samples200}.pdf}}
+\begin{frame}{Desalination in \{$\cs$, $V$\} coordinates.}
+	\begin{figure}[t]
+		{\includegraphics[width=\columnwidth]{{figures/results_3}.pdf}}
 	\end{figure}
@@
 
-\begin{frame}{Monovalent salt. Desalination effect.}
-
+\begin{frame}{Desalination in \{$N$, $V$\} coordinates.}
 	\begin{figure}[t]
-		{\includegraphics[width=0.5\columnwidth]{{figures/gibbs3}.pdf}}
-		\caption{
-			Schematic illustration of the hydrogel being compressed isotropically by pressure $\Delta P$ 
-			from the initial volume at free swelling equilibrium, $V_0$ to a volume $\Vgel$. 
-			Simultaneously, the gel exchanges small ions with a reservoir solution of salinity $\cs$.}
+		{\includegraphics[width=\columnwidth]{{figures/results_4}.pdf}}
 	\end{figure}
@@
 
-\begin{frame}{Monovalent salt. Desalination effect.}
+\begin{frame}{Desalination in \{$\cs$, $N$\} coordinates.}
 	\begin{figure}[t]
-		\subfloat[low salinity, $c_s = 0.007$ mol/l]
-			{\includegraphics[width=0.5\columnwidth]{{figures/gel_Na_log_density_cs0.006_N_Samples200}.pdf}}
-			{\includegraphics[width=0.5\columnwidth]{{figures/gel_Cl_log_density_cs0.15_N_Samples200}.pdf}}
-		\subfloat[high salinity, $c_s = 0.209$ mol/l]
-			{\includegraphics[width=0.5\columnwidth]{{figures/gel_Na_log_density_cs0.15_N_Samples200}.pdf}}
-			{\includegraphics[width=0.5\columnwidth]{{figures/gel_Cl_log_density_cs0.15_N_Samples200}.pdf}}
+		{\includegraphics[width=\columnwidth]{{figures/results_2}.pdf}}
 	\end{figure}
-\end{frame}
-
-\begin{frame}{Divalent salt. }
-	\begin{columns}[T,onlytextwidth]% COLUMNS
-		\column{0.55\textwidth}
-			\begin{figure}
-				\includegraphics[width=1\columnwidth]{figures/vmdscene.png}
-			\end{figure} 		
-		\column{0.4\textwidth}
-			{\Large Seawater model: }
-			\begin{eqnarray*}
-				c_\cl&=&0.54\text{ mol/l} \\
-				&&\text{of negative ions} 
-				%c_\so&=&0.028 \text{ mol/l of negative divalent ions} 
-			\end{eqnarray*}
-			\begin{eqnarray*}
-				c_\na&=&0.47\text{ mol/l} \\
-				&&\text{of positive ions} 
-			\end{eqnarray*}
-
-			\begin{eqnarray*}
-				c_\ca&=&0.063\text{ mol/l} \\
-				&&\text{of positive divalent ions}  \\
-			\end{eqnarray*}
-
-	\end{columns}
-	\begin{columns}[T,onlytextwidth]% COLUMNS
-		\column{0.5\textwidth}
-			\begin{eqnarray*}
-				c_{\na}&\simeq0.87\cdot c_{\cl} \\
-				c_{\ca}&\simeq0.117\cdot c_{\cl} \\
-				%c_{\so}&\simeq&c_{\cl}\cdot0.0282/0.55=0.051c_{\cl} 
-			\end{eqnarray*}
-		\column{0.5\textwidth}
-			\begin{eqnarray*}
-				\mu_{\na}&=&\mu_{\cl} - 0.139\kT\\
-				\mu_{\ca}&=&\mu_{\cl} - 2.03\kT\\
-			\end{eqnarray*}	
-	\end{columns}		
-\end{frame}
-\begin{frame}{Divalent salt. Compression.}
-
-	\begin{figure}[t]
-		\subfloat[low salinity, $c_s = 0.007$ mol/l]
-			{\includegraphics[width=0.5\columnwidth]{{figures/gel_pressure_log_density_pCa3.16_cs0.006_N_Samples200}.pdf}}
-			{\includegraphics[width=0.5\columnwidth]{{figures/gel_alpha_log_density_pCa3.16_cs0.006_N_Samples200}.pdf}}			
-		\subfloat[high salinity, $c_s = 0.209$ mol/l]
-			{\includegraphics[width=0.5\columnwidth]{{figures/gel_pressure_log_density_pCa1.77_cs0.15_N_Samples200}.pdf}}
-			{\includegraphics[width=0.5\columnwidth]{{figures/gel_alpha_log_density_pCa1.77_cs0.15_N_Samples200}.pdf}}
-	\end{figure}
-\end{frame}
-
-\begin{frame}{Divalent salt. Desalination or ion exchange.}
-Low salinity $c_\cl = 0.007$
-	\begin{figure}
-	\subfloat{\includegraphics[width=0.5\columnwidth]{{figures/gel_Cl_log_density_pCa3.16_cs0.006_N_Samples200}.pdf}}
-	\subfloat{\includegraphics[width=0.5\columnwidth]{{figures/gel_Na_log_density_pCa3.16_cs0.006_N_Samples200}.pdf}}
-	\vspace{0.3cm}
-	\\
-	\subfloat{\includegraphics[width=0.5\columnwidth]{{figures/gel_Ca_log_density_pCa3.16_cs0.006_N_Samples200}.pdf}}
-	\end{figure}
-
-\end{frame}
-
-\begin{frame}{Divalent salt. Desalination or ion exchange.}
-High salinity $c_\cl = 0.263$
-	\begin{figure}
-	\subfloat{\includegraphics[width=0.5\columnwidth]{{figures/gel_Cl_log_density_pCa1.77_cs0.15_N_Samples200}.pdf}}
-	\subfloat{\includegraphics[width=0.5\columnwidth]{{figures/gel_Na_log_density_pCa1.77_cs0.15_N_Samples200}.pdf}}
-	\vspace{0.3cm}	
-	\\
-	\subfloat{\includegraphics[width=0.5\columnwidth]{{figures/gel_Ca_log_density_pCa1.77_cs0.15_N_Samples200}.pdf}}
-	\end{figure}
-
 \end{frame}
@@
 \begin{frame}[standout]
-  Questions?
+  Questions are welcome.
+
+  \vspace{2cm}
+{\small Many thanks to }
+	\begin{columns}[T,onlytextwidth]% COLUMNS
+		\column{0.33\textwidth}
+			\begin{figure}[t]
+				{\includegraphics[width=\columnwidth]{{figures/gacr}.pdf}}\\
+				\vspace{2mm}
+				{\includegraphics[width=\columnwidth]{{figures/megagrant}.pdf}}\\
+				\vspace{2mm}
+				{\includegraphics[width=\columnwidth]{{figures/metacentrum}.png}}
+			\end{figure}
+			\column{0.66\textwidth}
+			\centering
+			\vspace{5mm}
+			{\small
+			\begin{itemize}
+			\item Czech Science Foundation (grant 19-17847Y)			\vspace{3mm}
+			\item Russian Federation, grant number 14.W03.31.0022   \vspace{3mm}
+			\item “e-Infrastruktura CZ” (e-INFRA LM2018140)
+			\end{itemize}}
+	\end{columns}
 \end{frame}
@@
 
-\begin{frame}{Monovalent salt. ``No electrostatics'' vs ``Mean field theory''.}
-	\begin{figure}[t]
-		\subfloat[low salinity, $c_s = 0.007$ mol/l]
-			{\includegraphics[width=0.5\columnwidth]{{figures/gel_pressure_log_density_lB0.0_cs0.006_N_Samples200}.pdf}}
-			{\includegraphics[width=0.5\columnwidth]{{figures/gel_alpha_log_density_lB0.0_cs0.006_N_Samples200}.pdf}}
-		\subfloat[high salinity, $c_s = 0.209$ mol/l]
-			{\includegraphics[width=0.5\columnwidth]{{figures/gel_pressure_log_density_lB0.0_cs0.15_N_Samples200}.pdf}}
-			{\includegraphics[width=0.5\columnwidth]{{figures/gel_alpha_log_density_lB0.0_cs0.15_N_Samples200}.pdf}}
-	\end{figure}
-\end{frame}
 \end{document}

### 2022-09-05 gibbs.tex
Update gibbs.tex

@@
 
-\subsection{Simulations}
-TODO put here the parts from "Results and Discussion", which are actually neither Results nor Discussion
-\paragraph{Compression in the \emph{open system}}
-\paragraph{Compression in the \emph{closed system}}
-
-\section{Results and discussion }
+\section{Results and discussion}
 
@@
 It is caused by the decrease of ions osmotic pressure and by a screening of electrostatic interactions \cite{Zhulina2000, Landsgesel2020a}.
-\footnote{The salinity dependence of the size of \emph{weak} polyelectrolyte gel is in general non-monotonic. We discuss this case in \cite{Rud2018}.}
+(The salinity dependence of the size of \emph{weak} polyelectrolyte gel is in general non-monotonic. We discuss this case in \cite{Rud2018}.)
 

### 2022-09-05 gibbs.tex
Update gibbs.tex

@@
 \end{figure*}
-First, we run a set of simulations modeling the gel compression in \emph{open system}, \ie in equilibrium with a big bath of certain salinity, $\cs$. 
-The simulations are run for a set of different simulation box volumes. 
-Each simulation returns the averaged pressure, $P$, and the number of $\cl$ ions, which are present in the simulation box, $\ncl$.
+First, we ran a set of simulations modeling the gel compression in \emph{open system}, \ie in equilibrium with a big bath of certain salinity, $\cs$. 
+The simulations were run for a set of different simulation box volumes. 
+Each simulation provided pressure, $P$, and the number of $\cl$ ions, which are present in the simulation box, $\ncl$.
 
-In order to get the partial pressure of the gel, we substitute from $P$ the osmotic pressure of ions in the reservoir: $\Pgel=P - \Pout$.
-$\Pout$, in turn, we calculate by running a separate simulation of a reservoir, containing ionic gas in equilibrium with the bath of the same salinity $\cs$. 
+In order to get the partial pressure of the gel, we subtracted from $P$ the osmotic pressure of ions in the reservoir: $\Pgel=P - \Pout$.
+$\Pout$, in turn, we obtained from a separate simulation of a reservoir, containing ionic gas in equilibrium with the bath of the same salinity $\cs$. 
 The gel partial pressure, $\Pgel$, is the pressure that needs to be applied to the gel via a solvent permeable filter to compress the gel to a specific molar volume, $\Vgel$.
-By gel molar volume $\Vgel$ we assume the volume of the gel calculated per on mol of gel monomer units.
+$\Vgel$ is the gel volume per one mole of gel monomer units.
 
-The dependencies of $\Pgel$ on $\Vgel$ are present in Figure \ref{fig: PV} for a set of different salinities. 
-These dependencies (the case of \emph{open system}) are represented by solid lines. 
+These dependencies of $\Pgel$ on $\Vgel$ for \emph{open system} for a set of various salinities are presented
+in Figure \ref{fig: PV} by solid lines. 
 For example, the blue solid line illustrates the compression (or swelling) of the gel in equilibrium with a reservoir of salinity, $\cs=0.063$ mol/l. 

### 2022-09-05 gibbs.tex
Update gibbs.tex

@@
 The points where the pressure equals zero, $\Pgel=0$, (indicated by filled circles) are the gel \emph{free swelling equilibrium} states.
-These states shift towards smaller volumes with increase of salinity. 
-In general, the increase of salinity shift all the $\Pgel(V)$ curves towards smaller volumes.
+These states are characterized by the corresponding molar volume of the gel, $\Vgel^0$ and the amount of ions in gel \{$\Nna^0$, $\Ncl^0$\} 
+(Index ``0'' stands for zero bar applied pressure).
+The \emph{free swelling equilibrium} states' positions shift towards smaller volumes with increase of salinity. 
+In general, the increase of salinity shifts all the $\Pgel(V)$ curves towards smaller volumes.
 This effect is well known and is typical for all branched \emph{strong} polyelectrolytes. 
@@
 \paragraph{Compression in closed system}
-%Each set of simulations in \emph{open system} defines the free swelling equilibrium states of the gel for each salinity, \ie the state where the gel partial pressure equals zero. 
-The free swelling equilibrium states are characterized by the corresponding molar volume of the gel, $\Vgel^0$ and the amount of ions in gel \{$\Nna^0$, $\Ncl^0$\} 
-(Index ``0'' stands for zero bar applied pressure).
-We use these states as the starting ones for the gel compression in \emph{closed system}. 
-Thus, we simulate the compression of the gel in a closed volume, $\Vbox$, which is equal to $\Vgel^0$, and contains $\Ncl^0$ of $\cl$ ions and the $\na$ ions in the amount neutralizing the system, $\Nna^0 = $$\Ncl^0 + \Ngel$.
+The simulations in \emph{closed systems} start from the corresponding $\Vgel^0$ and \{$\Nna^0$, $\Ncl^0$\} values
+obtained from the \emph{open system} simulations.
+The simulation of gel compression in a closed volume, $\Vbox$, starts at the point $\Vbox = \Vgel^0$,
+and ion content $\Ncl^0$ for $\cl$ ions. The $\na$ ions amount is neutralize the system, $\Nna^0 = $$\Ncl^0 + \Ngel$.
 

### 2022-09-05 gibbs.tex
Update gibbs.tex

@@
 \paragraph{Compression in closed system}
-The simulations in \emph{closed systems} start from the corresponding $\Vgel^0$ and \{$\Nna^0$, $\Ncl^0$\} values
-obtained from the \emph{open system} simulations.
+The simulations in \emph{closed systems} start from the $\Vgel^0$ and \{$\Nna^0$, $\Ncl^0$\} values
+obtained from the corresponding \emph{open system} simulations.
 The simulation of gel compression in a closed volume, $\Vbox$, starts at the point $\Vbox = \Vgel^0$,
@@
 
-We prepare two systems, one~--- simulating the gel of the volume $\Vgel$, and another~--- simulating the supernatant solution of the volume $\Vout = \Vbox - \Vgel$.
-Also, the ions of the amount $\Ncl^0$ and $\Nna^0$ are shared between the two volumes.
+We prepare two systems: one for simulation of the gel at the volume $\Vgel$,
+and the other one for simulation of the supernatant solution at the volume $\Vout = \Vbox - \Vgel$.
+Note that the ions of the amount $\Ncl^0$ and $\Nna^0$ are shared by the two volumes.
 
-The processes of the gel compression in \emph{closed} system are depicted in Figure~\ref{fig: PV} as dotted lines.
-In this plot, the blue dotted line, for example, illustrates the compression of the gel equilibrated with the solution of salinity $\cs=0.063$ mol/l, in a volume which gel has at zero pressure. 
-Since, in this case, the volumes of the gel $\Vgel$ and of the supernate $\Vout$ are comparable, the compression of the gel decreases the salinity of supernate, $\cs$. 
-%The supernate salinity now decreases with compression.
-This dependence is illustrated \reffig{fig: CV}, where the same swelling/compression processes are displayed in different coordinates: \ie salinity of supernate versus the gel molar volume, $\cs(\Vgel)$.
+The processes of the gel compression in \emph{closed system} are depicted in Figure~\ref{fig: PV} as dotted lines.
+In this plot, for example, the blue dotted line illustrates the compression of the gel equilibrated with the solution of salinity $\cs=0.063$ mol/l at volume, at which the gel has at zero pressure. 
+The volume values $\Vgel$ and $\Vout$ are comparable in the \emph{closed system} case.
+Therefore, the gel compression causes decrease of the salinity in the supernate, $\cs$. 
+This dependence is illustrated in \reffig{fig: CV}, where the same swelling/compression processes are displayed in different coordinates: \ie salinity of supernate versus the gel molar volume, $\cs(\Vgel)$.
 In these coordinates, all the open system compressions show up as horizontal lines, which reflects the constant salinity, whereas the compressions in closed system demonstrate the change of $\cs$ from $\cs^{0}=0.063$ at zero pressure $\Pgel$ to $\cs^{5}=0.045$ mol/l at $P\gel=5$ bar (index ``5'' stands for 5 bar).

### 2022-09-05 gibbs.tex
Update gibbs.tex

@@
 
-Although the salinity during compression in \emph{open} system remains constant, the number of ions in a compression volume, \ie in the volume where the gel is compressed (or swells), changes.
-%As the compression volume $\Vbox$ we chose the volume of the free swelling equilibrium state of the gel, $\Vbox = \Vgel^0$.
-In the Figure \ref{fig: NV} we depicted the number of $\cl$ ions in the volume $\Vbox$, calculated per unit volume, $\ncl =$ $\Ncl/\Vbox$, as a function of the gel molar volume. 
-The depicted value can be considered as the density of $\cl$ ions averaged out over the compression volume $\Vbox$.
+Although the salinity during compression in \emph{open system} remains constant, the amount of ions in the compressed subsystem (\ie in the volume where the gel is compressed (or swells)), changes.
+Here, the compression volume $\Vbox$ is the volume of the \emph{free swelling equilibrium} state of the gel, $\Vbox = \Vgel^0$.
+Figure \ref{fig: NV} shows number of $\cl$ ions in the volume $\Vbox$ per unit volume, $\ncl =$ $\Ncl/\Vbox$, as a function of the gel molar volume. 
+The depicted values can be considered as the average density of $\cl$ ions in the compression volume $\Vbox$.
 
-As expected in the case of closed system compression these dependencies look like horizontal lines, whereas in an open system, the amount of ions in compression volume increases with compression. 
-This implies, that the compression of the gel in the open system pulls out the ions from the bath to the compression volume, $\Vbox$. 
+The $\ncl$-$\Vgel$ dependencies look like horizontal lines in the case of \emph{closed system} compression,
+whereas $\ncl$ increases with $\Vgel$ during the compression in the \emph{open system} case. 
+This implies, that the compression of the gel in the \emph{open system} pulls out the ions from the bath to the compression volume, $\Vbox$. 
 And vice versa, the swelling of the gel pushes ions out to the bath.
 
-Finally, in Figure \ref{fig: CN} the same processes are depicted in coordinates $\ncl$ --- $\cs$. 
-In these coordinates, both ways of the compression, in \emph{open} and in \emph{closed} system, appear as straight vertical and horizontal lines correspondingly.
+Finally, the same processes are depicted in Figure \ref{fig: CN} in coordinates $\ncl$ --- $\cs$. 
+In these coordinates, both ways of the compression, in \emph{open} and in \emph{closed} systems, appear as straight vertical and horizontal lines correspondingly.
 
 In our study, we modeled the compression of the gel in equilibrium with reservoirs of 40 different salinities, ranging from 0.001 to 0.5 mol/l. 
-Every open system compression resulted in a defined free swelling equilibrium state, which we used as the initial ones for the compression in closed systems. 
+The \emph{open system} compressions resulted in a defined free swelling equilibrium states,
+which we used as the initial conditions for the respective compressions in \emph{closed systems}. 
 All the corresponding dependencies are depicted in Figures~\ref{fig: PV and CV} and \ref{fig: NV and CN} as thin grey dashed lines (some of them are highlighted and colored).
 The states corresponding to $P^{gel}=0$, 5 and 10 bar pressure are marked by open circles, squares, and crosses respectively. 
-The non-shadowed areas in the Figures highlight the states in which the gel partial pressure ranges between 0 and 5 bar.
+The non-shadowed areas in the Figures highlight the states in which the gel partial pressure ranges between the experimentally relevant values, 0 and 5 bar.
 

### 2022-09-05 gibbs.tex
Update gibbs.tex

@@
 \paragraph{Desalination scheme}
-As we have seen, the compression of the gel in a closed system affects the salinity, whereas the compression in an open system affects the amount of ions in a volume where the gel is compressed in. 
+It follows that the compression of the gel in the \emph{closed system} affects the salinity, whereas the compression in the \emph{open system} affects the amount of ions in the gel subsystem. 
 Here we show how to employ these phenomena for water desalination. 
-The highlighted colored lines on plots of Figures \ref{fig: PV and CV} and \ref{fig: NV and CN} form a sequence of the following one by each other swellings and compressions of the hydrogel, correspondingly in \emph{open} and \emph{closed} systems.
+The highlighted colored lines on plots of Figures \ref{fig: PV and CV} and \ref{fig: NV and CN} form a sequence gel swellings and compressions, following one by one, correspondingly in \emph{open} and \emph{closed} systems.
 This sequence forms the water desalination process.
-Starting from swelling the gel in the \emph{open} system at high salinity ($\cs=0.091$ mol/l, solid black line), the gel gets compressed in \emph{closed} system until the pressure reaches 5 bar (dashed black line).
-Then the same gel swells in a reservoir of a bit lower salinity (\ie $\cs=0.064$ mol/l, light blue line). 
-After swelling, the gel is compressed again by the pressure of 5 bar in \emph{closed} system (dashed light blue line).  
-Then the gel is put swelling in a reservoir of even smaller salinity ($\cs=0.045$ mol/l, solid yellow line). 
-And so on. 
-The chain of alternating swelling and compression steps ends up when salinity gets equal to $\cs=4\cdot10^{-3}$ mol/l after compression in closed system (dashed magenta line).
+Starting from swelling the gel in the \emph{open system} at high salinity ($\cs=0.091$ mol/l, solid black line), the gel is compressed in the \emph{closed system} until the pressure reaches 5 bar (dashed black line).
+Then the same gel swells in a reservoir of a bit lower salinity in the \emph{open system} (\ie $\cs=0.064$ mol/l, light blue line). 
+After the swelling, the gel is compressed again with the pressure 5 bar in \emph{closed system} (dashed light blue line).  
+Then the gel swells in a reservoir of even smaller salinity ($\cs=0.045$ mol/l, solid yellow line), and so on. 
+This chain of alternating swellings and compressions ends up when salinity is equal to $\cs=4\cdot10^{-3}$ mol/l after the compression in the \emph{closed system} (dashed magenta line).
 
-The plots of Figures \ref{fig: PV and CV} and \ref{fig: NV and CN} depict the whole process in all the possible coordinates
-In all the plots the whole process looks like a staircase, especially in the Figure~\ref{fig: CN}, where open system processes are horizontal lines and closed system are vertical ones, a 'staircase' has rectangular steps
+The plots in Figures \ref{fig: PV and CV} and \ref{fig: NV and CN} depict the whole process in all possible coordinate representations.
+In all plots, the lines corresponding to sequential swellings and compressions during the whole desalination process resemble a 'pathway'.
+In particular, the desalination process depicted in Figure~\ref{fig: CN} resembles a staircase,
+where the \emph{open system} processes are horizontal lines and the \emph{closed system} processes are vertical lines.
 

### 2022-09-05 gibbs.tex
Update gibbs.tex

@@
 \end{equation}
-where $R$ is a universal gas constant, $c_{f}$ is the salinity of feed water, $c_p$~--- of product water and $c_b$~--- the salinity of the brine, which necessarily appears in any desalination process.
+where $R$ is a universal gas constant, $c_{f}$ is the salinity of feed water, $c_p$ is the salinity of product water and $c_b$ is the salinity of the brine, which necessarily appears in any desalination process.
 $R_{w}$ is a recovery ratio, \ie the ratio between volume of produced water and the volume of the feed water. 
@@
 The third column shows the change of the gel volume in corresponding process, $\Delta v$. 
-The fourth column contain the work needed for the compression in the corresponding process, calculated per volume of extracted solution. 
+The fourth column contains the work needed for the compression in the corresponding process per volume of extracted solution. 
 This value is an integral of corresponding $\Pgel(\Vgel)$ dependence
@@
 \end{equation}
-Here, in the table, we present the absolute values of the work, whereas one should keep in mind that the compression implies the work is done by external force and the swelling implies that the work is done by gel.
+Table 1 presents the absolute values of the work. Note that the compression implies the work done by external force, but the swelling implies the work done by the gel.
 
@@
 
-To give a clue of comparison with ideal desalination process efficiency, in the fifth column we provided the values of specific energy consumption, $W^\text{id}$, which are calculated by means of \refeq{eq:SEC} as follows.
-We consider, for example, the solution of concentration $\cs^f=44.91$ mmol/l as a feed solution, and the solutions of $\cs^p=31.93$ mmol/l and $\cs^b = 63.93$ mmol/l 
-correspondingly as produced product and brine solutions.
+To give a clue of comparison with ideal desalination process efficiency, the fifth column provides the values of specific energy consumption, $W^\text{id}$, which are calculated by means of \refeq{eq:SEC}, using the following procedure:
+Let§s assume the concentration of the feed solution to be $\cs^f=44.91$ mmol/l and the concentrations of product and brine solutions to be $\cs^p=31.93$ mmol/l and $\cs^b = 63.93$ mmol/l, respectively.
 \begin{enumerate}
-    \item first, the gel, equilibrated with feed solution, is getting compressed in a closed system.
-    The volume of the gel changes by $\Delta v^p = 3.69$ l  and the salinity of supernate decreases from $\cs^f$ to $\cs^p$.
-    The volume of product solution equals $\Delta v^p$
-    \item Then the squeezed gel is put back into the feed solution and is getting equilibrated there under pressure, so it does not swell. 
-    \item After equilibration the gel is let to swell in a closed system such that the salinity of the external solution increases reaching the value of $\cs^b$.
-    \item Finally, the gel is taken out and squeezed by 5 bar in an open system in equilibrium with the bath of the brine. 
-    The change of the gel volume in this process is $\Delta v^b = 3.26$ l/mol, which equals the volume of the produced brine. 
+    \item The gel, equilibrated with the feed solution, is compressed in the \emph{closed system}.
+    The gel volume decreases by $\Delta v^p = 3.69$ liters and the salinity of supernate decreases from $\cs^f$ to $\cs^p$.
+    The volume of the product solution is $\Delta v^p$
+    \item The squeezed gel is put back into the feed solution and is quilibrated there under pressure, so it does not swell. 
+    \item After the equilibration, the gel swells in the \emph{closed system} and the salinity of the external solution increases to the value $\cs^b$.
+    \item Finally, the gel is taken out and compressed by 5 bar in the \emph{open system} in equilibrium with the brine bath. 
+    The change of the gel volume in this process is $\Delta v^b = 3.26$ l/mol, which equals to the volume of the produced brine. 
 \end{enumerate}
-Thus the recovery ratio $R_w = \Delta v^p / (\Delta v^p + \Delta v^b) \simeq $ 0.53 and the theoretical minimum specific energy of desalination with corresponding $\cs^f$, $\cs^p$ and $\cs^b$ is $W^{id} =$ 38.2 J/l (\refeq{eq:SEC}).
+Thus the recovery ratio $R_w = \Delta v^p / (\Delta v^p + \Delta v^b) \simeq $ 0.53 and the theoretical minimum specific energy of the desalination process with corresponding $\cs^f$, $\cs^p$ and $\cs^b$ is $W^{id} =$ 38.2 J/l (\refeq{eq:SEC}).
 
-Such estimations are provided in the fifth column of the table, for five triplets of values $\cs^f$, $\cs^p$, and $\cs^b$.
-$W_{\mathrm{sim}}$ is the energy calculated by integration of $\Pgel(\Vgel)$ dependencies~--- sum of corresponding comressions in closed and open systems, $W_{\mathrm{id}}$~--- the estimate based on the equation \refeq{eq:SEC} and $R_w$~--- is the corresponding recovery ratio.
-Note that calculating the $W_{\mathrm{sim}}$ we accounted for only the work done on the gel during compression, whereas the work done by the gel itself during swelling was not taken into account.
+The estimated $W^{id}$ values are provided in the fifth column of the table, for five triplets of $\cs^f$, $\cs^p$,$\cs^b$ values .
+$W_{\mathrm{sim}}$ is the energy calculated by integration of $\Pgel(\Vgel)$ dependencies as the sum of corresponding compressions in \emph{closed} and \emph{open} systems, $W_{\mathrm{id}}$ is the estimation based on the equation \refeq{eq:SEC} and $R_w$ is the corresponding recovery ratio.
+Note that calculating the $W_{\mathrm{sim}}$ we accounted for only the work done on the gel during the compression, whereas the work done by the gel itself during swelling was not taken into account.
 The ratio between $W_{\mathrm{sim}}$ and $W_{\mathrm{id}}$ ranges from 3.26 to 5.43, which is comparable to that of RO.

### 2022-09-06 gibbs.tex
clean app, changed style to mdpi

@@
-%% LyX 2.3.4.2 created this file.  For more info, see http://www.lyx.org/.
-%% Do not edit unless you really know what you are doing.
-%\documentclass{achemso}
-\documentclass[layout=twocolumns,manuscript=article]{achemso}
+%  LaTeX support: latex@mdpi.com 
+%  For support, please attach all files needed for compiling as well as the log file, and specify your operating system, LaTeX version, and LaTeX editor.
 
-\makeatletter
+%=================================================================
+\documentclass[journal,article,submit,pdftex,moreauthors]{Definitions/mdpi} 
+\usepackage{subfig}
+\usepackage[textsize=small]{todonotes}
+\newcommand{\ie}{\textit{i.~e.} }
+\newcommand{\cref}{c^{\ominus}}
+%\newcommand{\cs}{c_{s}}
+\newcommand{\kT}{k_\mathrm{B}T}
+\newcommand{\kB}{k_\mathrm{B}}
+\newcommand{\lb}{l_\mathrm{B}}
+%\newcommand{\NA}{N_{\mathrm{A^-}}}
+\newcommand{\NA}{N_{\mathrm{A}}}
+\newcommand{\muna}{\mu_\mathrm{Na^+}}
 
+\newcommand{\mucl}{\mu_\mathrm{Cl^-}}
+\newcommand{\muca}{\mu_\mathrm{Ca^{2+}}}
+\newcommand{\muh}{\mu_\mathrm{H^+}}
+\newcommand{\mua}{\mu_\mathrm{A^-}}
+\newcommand{\muha}{\mu_\mathrm{HA}}
+\newcommand{\muoh}{\mu_\mathrm{OH}}
+
+\newcommand{\cna}{c_\mathrm{Na^+}}
+\newcommand{\ccl}{c_\mathrm{Cl^-}}
+\newcommand{\cca}{c_\mathrm{Ca^{2+}}}
+\newcommand{\ch}{c_\mathrm{H^+}}
+\newcommand{\cp}{c_\mathrm{p}}
+\newcommand{\nna}{n_\mathrm{Na^+}}
+\newcommand{\ncl}{n_\mathrm{Cl^-}}
+\newcommand{\Nna}{N_\mathrm{Na^+}}
+\newcommand{\Ncl}{N_\mathrm{Cl^-}}
+
+\newcommand{\ncleq}{\widetilde{N}_\mathrm{Cl^-}}
+\newcommand{\nca}{N_\mathrm{Ca^{2+}}}
+
+\newcommand{\superin}{^\mathrm{in}}
+\newcommand{\subin}{_\mathrm{in}}
+\newcommand{\subi}{_\mathrm{i}}
+
+\newcommand{\gel}{^\mathrm{gel}}
+\newcommand{\tot}{^\mathrm{tot}}
+\newcommand{\out}{^{\mathrm{out}}}
+\newcommand{\coh}{c_\mathrm{OH}}
+\newcommand{\bulk}{^{\mathrm{b}}}
+\renewcommand{\H}{\mathrm{H^+}}
+\newcommand{\A}{\mathrm{A^-}}
+\newcommand{\AH}{\mathrm{AH}}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
 
-\title{Water desalination using polyelectrolyte hydrogel: Gibbs ensemble modeling}
+\newcommand{\cl}{\mathrm{Cl^-}}
+\newcommand{\br}{\mathrm{Br^-}}
+\newcommand{\na}{\mathrm{Na^+}}
+\newcommand{\h}{\mathrm{H^+}}
+\newcommand{\ka}{\mathrm{K^+}}
+\newcommand{\oh}{\mathrm{OH^-}}
+\newcommand{\ca}{\mathrm{Ca^{2+}}}
+\newcommand{\mg}{\mathrm{Mg^{2+}}}
 
-\author{Mikhail Laktionov}
+\newcommand{\Ka}{K_{\mathrm{A}}}
+\newcommand{\pKa}{\mathrm{p}\Ka}
+\newcommand{\pK}{\mathrm{p}K}
+\newcommand{\pH}{\mathrm{pH}}
+\newcommand{\mol}{\mathrm{mol}}
+\newcommand{\molperl}{\mathrm{mol/l}}
+\newcommand{\kg}{\mathrm{kg}}
+\newcommand{\res}{^{\mathrm{res}}}
+\newcommand{\pHres}{\pH\res}
+\newcommand{\pHgel}{\pH\gel}
+\newcommand{\cs}{c_{\mathrm{s}}}
+%\newcommand{\cs}{c_{\mathrm{salt}}}
+\newcommand{\csres}{\cs\res}
+%\newcommand{\Vgel}{V\gel}
+\newcommand{\Vgel}{V_\mathrm{gel}}
+%\newcommand{\Vgel}{V}
+\newcommand{\Ngel}{N_\mathrm{gel}}
+%\newcommand{\Vgeleq}{\widetilde{V}_\mathrm{gel}}}
+%\newcommand{\Pgel}{P_\mathrm{gel}}
+\newcommand{\Pgel}{\Pi}
+\newcommand{\Pres}{P_\mathrm{res}}
+\newcommand{\Pout}{P_\mathrm{out}}
+\newcommand{\Vout}{V_\mathrm{out}}
+%\newcommand{\Vbox}{V_\mathrm{box}}
+\newcommand{\Vbox}{V_0}
+\newcommand{\PE}{polyelectrolyte{}}
 
-\affiliation[cuni]{Department of Physical and Macromolecular Chemistry, Faculty of Science,
-Charles University in Prague, Czech Republic}
+\newcommand{\reffig}[1]{Figure~\ref{#1}}
+\newcommand{\refeq}[1]{Equation~\ref{#1}{}}
+\newcommand{\etal}{\textit{et al.}{}}
 
-\alsoaffiliation[itmo]{St. Petersburg National Research University of Information Technologies,
-Mechanics and Optics, St. Petersburg, Russia.}
+% For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal and change "submit" to "accept".
+The document class line would be, e.g., \documentclass[preprints,article,accept,moreauthors,pdftex]{mdpi}.
+This is especially recommended for submission to arXiv, where line numbers should be removed before posting.
+For preprints.org, the editorial staff will make this change immediately prior to posting.
 
-\author{Lucie Nová}
-\author{Oleg V. Rud}
+%--------------------
+% Class Options:
+%--------------------
+%----------
+% journal
+%----------
+% Choose between the following MDPI journals:
+% acoustics, actuators, addictions, admsci, adolescents, aerospace, agriculture, agriengineering, agronomy, ai, algorithms, allergies, alloys, analytica, animals, antibiotics, antibodies, antioxidants, applbiosci, appliedchem, appliedmath, applmech, applmicrobiol, applnano, applsci, aquacj, architecture, arts, asc, asi, astronomy, atmosphere, atoms, audiolres, automation, axioms, bacteria, batteries, bdcc, behavsci, beverages, biochem, bioengineering, biologics, biology, biomass, biomechanics, biomed, biomedicines, biomedinformatics, biomimetics, biomolecules, biophysica, biosensors, biotech, birds, bloods, blsf, brainsci, breath, buildings, businesses, cancers, carbon, cardiogenetics, catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, chemproc, children, chips, cimb, civileng, cleantechnol, climate, clinpract, clockssleep, cmd, coasts, coatings, colloids, colorants, commodities, compounds, computation, computers, condensedmatter, conservation, constrmater, cosmetics, covid, crops, cryptography, crystals, csmf, ctn, curroncol, currophthalmol, cyber, dairy, data, dentistry, dermato, dermatopathology, designs, diabetology, diagnostics, dietetics, digital, disabilities, diseases, diversity, dna, drones, dynamics, earth, ebj, ecologies, econometrics, economies, education, ejihpe, electricity, electrochem, electronicmat, electronics, encyclopedia, endocrines, energies, eng, engproc, ent, entomology, entropy, environments, environsciproc, epidemiologia, epigenomes, est, fermentation, fibers, fintech, fire, fishes, fluids, foods, forecasting, forensicsci, forests, foundations, fractalfract, fuels, futureinternet, futureparasites, futurepharmacol, futurephys, futuretransp, galaxies, games, gases, gastroent, gastrointestdisord, gels, genealogy, genes, geographies, geohazards, geomatics, geosciences, geotechnics, geriatrics, hazardousmatters, healthcare, hearts, hemato, heritage, highthroughput, histories, horticulturae, humanities, humans, hydrobiology, hydrogen, hydrology, hygiene, idr, ijerph, ijfs, ijgi, ijms, ijns, ijtm, ijtpp, immuno, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jal, jcdd, jcm, jcp, jcs, jdb, jeta, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmp, jmse, jne, jnt, jof, joitmc, jor, journalmedia, jox, jpm, jrfm, jsan, jtaer, jzbg, kidney, kidneydial, knowledge, land, languages, laws, life, liquids, literature, livers, logics, logistics, lubricants, lymphatics, machines, macromol, magnetism, magnetochemistry, make, marinedrugs, materials, materproc, mathematics, mca, measurements, medicina, medicines, medsci, membranes, merits, metabolites, metals, meteorology, methane, metrology, micro, microarrays, microbiolres, micromachines, microorganisms, microplastics, minerals, mining, modelling, molbank, molecules, mps, msf, mti, muscles, nanoenergyadv, nanomanufacturing, nanomaterials, ncrna, network, neuroglia, neurolint, neurosci, nitrogen, notspecified, nri, nursrep, nutraceuticals, nutrients, obesities, oceans, ohbm, onco, oncopathology, optics, oral, organics, organoids, osteology, oxygen, parasites, parasitologia, particles, pathogens, pathophysiology, pediatrrep, pharmaceuticals, pharmaceutics, pharmacoepidemiology, pharmacy, philosophies, photochem, photonics, phycology, physchem, physics, physiologia, plants, plasma, pollutants, polymers, polysaccharides, poultry, powders, preprints, proceedings, processes, prosthesis, proteomes, psf, psych, psychiatryint, psychoactives, publications, quantumrep, quaternary, qubs, radiation, reactions, recycling, regeneration, religions, remotesensing, reports, reprodmed, resources, rheumato, risks, robotics, ruminants, safety, sci, scipharm, seeds, sensors, separations, sexes, signals, sinusitis, skins, smartcities, sna, societies, socsci, software, soilsystems, solar, solids, sports, standards, stats, stresses, surfaces, surgeries, suschem, sustainability, symmetry, synbio, systems, taxonomy, technologies, telecom, test, textiles, thalassrep, thermo, tomography, tourismhosp, toxics, toxins, transplantology, transportation, traumacare, traumas, tropicalmed, universe, urbansci, uro, vaccines, vehicles, venereology, vetsci, vibration, viruses, vision, waste, water, wem, wevj, wind, women, world, youth, zoonoticdis
 
-\affiliation{Department of Physical and Macromolecular Chemistry, Faculty of Science, Charles University in Prague, Czech Republic}
-\alsoaffiliation[imc]{Institute of Macromolecular Compounds of Russian Academy of Sciences, Saint-Petersburg, Russia}
+%---------
+% article
+%---------
+% The default type of manuscript is "article", but can be replaced by: 
+% abstract, addendum, article, book, bookreview, briefreport, casereport, comment, commentary, communication, conferenceproceedings, correction, conferencereport, entry, expressionofconcern, extendedabstract, datadescriptor, editorial, essay, erratum, hypothesis, interestingimage, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, studyprotocol, systematicreview, supfile, technicalnote, viewpoint, guidelines, registeredreport, tutorial
+% supfile = supplementary materials
 
-\email{oleg.rud@natur.cuni.cz}
+%----------
+% submit
+%----------
+% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted.
+This will only make changes to the frontpage (e.g., the logo of the journal will get visible), the headings, and the copyright information.
+Also, line numbering will be removed.
+Journal info and pagination for accepted papers will also be assigned by the Editorial Office.
 
-\abbreviations{MC, MD, RO, FO}
+%------------------
+% moreauthors
+%------------------
+% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.
 
-\keywords{polyelectrolye hydrogel, simulation, desalination}
+%---------
+% pdftex
+%---------
+% The option pdftex is for use with pdfLaTeX. If eps figures are used, remove the option pdftex and use LaTeX and dvi2pdf.
 
-%% Because html converters don't know tabularnewline
-\providecommand{\tabularnewline}{\\}
+%=================================================================
+% MDPI internal commands
+\firstpage{1} 
+\makeatletter 
+\setcounter{page}{\@firstpage} 
+\makeatother
+\pubvolume{1}
+\issuenum{1}
+\articlenumber{0}
+\pubyear{2022}
+\copyrightyear{2022}
+%\externaleditor{Academic Editor: Firstname Lastname}
+\datereceived{} 
+%\daterevised{} % Only for the journal Acoustics
+\dateaccepted{} 
+\datepublished{} 
+%\datecorrected{} % Corrected papers include a "Corrected: XXX" date in the original paper.
+%\dateretracted{} % Corrected papers include a "Retracted: XXX" date in the original paper.
+\hreflink{https://doi.org/} % If needed use \linebreak
+%\doinum{}
+%------------------------------------------------------------------
+% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
+%\pdfoutput=1
 
-\input{definitions.tex}
-\makeatother
+%=================================================================
+% Add packages and commands here.
+The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, soul, multirow, microtype, tikz, totcount, changepage, attrib, upgreek, cleveref, amsthm, hyphenat, natbib, hyperref, footmisc, url, geometry, newfloat, caption
 
-\begin{document}
-\begin{abstract}
-Recently polyelectrolyte hydrogels have been proposed as draw agents for the forward osmosis desalination techniques. 
+%=================================================================
+%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
+%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).
+
+%=================================================================
+% Full title of the paper (Capitalized)
+%\Title{Water desalination using polyelectrolyte hydrogel. Gibbs ensemble modeling}
+\Title{Water desalination using polyelectrolyte hydrogel: Gibbs ensemble modeling}
+
+% MDPI internal command: Title for citation in the left column
+\TitleCitation{Title}
+
+% Author Orchid ID: enter ID or remove command
+\newcommand{\orcidauthorA}{0000-0003-3412-7707} % Add \orcidA{} behind the author's name
+\newcommand{\orcidauthorB}{0000-0003-3616-3285} % Add \orcidB{} behind the author's name
+\newcommand{\orcidauthorC}{0000-0002-8501-0464} % Add \orcidB{} behind the author's name
+
+% Authors, for the paper (add full first names)
+\Author{Mikhail Laktionov $^{1, 2}$\orcidA{}, Lucie Nová $^{1}$\orcidB{} and Oleg V. Rud $^{1, 3}$*\orcidC{}}
+
+\keyword{polyelectrolye hydrogel; simulation; desalination} 
+%\longauthorlist{yes}
+
+% MDPI internal command: Authors, for metadata in PDF
+\AuthorNames{Mikhail Laktionov, Lucie Nová and Oleg V. Rud}
+
+% MDPI internal command: Authors, for citation in the left column
+\AuthorCitation{Lastname, F.; Lastname, F.; Lastname, F.}
+% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.
+
+% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
+\address{%
+$^{1}$ \quad Department of Physical and Macromolecular Chemistry, Faculty of Science, Charles University in Prague, Czech Republic; e-mail@e-mail.com\\
+$^{2}$ \quad St. Petersburg National Research University of Information Technologies, Mechanics and Optics, St. Petersburg, Russia; e-mail@e-mail.com\\
+$^{3}$ \quad Institute of Macromolecular Compounds of Russian Academy of Sciences, Saint-Petersburg, Russia; e-mail@e-mail.com}
+
+% Contact information of the corresponding author
+\corres{Correspondence: oleg.rud@natur.cuni.cz; }
+
+% Current address and/or shared authorship
+%\firstnote{Current address: Affiliation 3.} 
+%\secondnote{These authors contributed equally to this work.}
+% The commands \thirdnote{} till \eighthnote{} are available for further notes
+
+%\simplesumm{} % Simple summary
+
+%\conference{} % An extended version of a conference paper
+
+% Abstract (Do not insert blank lines, i.e. \\) 
+\abstract{Recently polyelectrolyte hydrogels have been proposed as draw agents for the forward osmosis desalination techniques. 
 Indeed, polyelectrolyte hydrogels have the ability to absorb a big amount of water across an osmosis membrane as a result of their swelling pressure. 
@@
 Finally, we performed a set of simulations modeling the process of continuous decrease of solution salinity up to freshwater concentrations.
+}
 
-\end{abstract}
+% Keywords
+
+% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
+%\PACS{J0101}
+%\MSC{}
+%\JEL{}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Only for the journal Diversity
+%\LSID{\url{http://}}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Only for the journal Applied Sciences
+%\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work. This section is not mandatory.}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Only for the journal Data
+%\dataset{DOI number or link to the deposited data set if the data set is published separately.
+If the data set shall be published as a supplement to this paper, this field will be filled by the journal editors.
+In this case, please submit the data set as a supplement.}
+%\datasetlicense{License under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Only for the journal Toxins
+%\keycontribution{The breakthroughs or highlights of the manuscript. Authors can write one or two sentences to describe the most important part of the paper.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Only for the journal Encyclopedia
+%\encyclopediadef{For entry manuscripts only: please provide a brief overview of the entry title instead of an abstract.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Only for the journal Advances in Respiratory Medicine
+%\addhighlights{yes}
+%\renewcommand{\addhighlights}{%
+%	\begin{itemize}[labelsep=2.5mm]
+%		\item This is an obligatory section in ``Advances in Respiratory Medicine'', whose goal is to increase the discoverability and readability of the article via search engines and other scholars.
+%		\item Highlights consist of a short collection of (3–6) bullet points that capture the gap in knowledge the manuscript is addressing, as well as breakthroughs and other important points.
+%		\item The Highlights section may also be used to showcase a new method used during the study (if any).
+%	\end{itemize}
+%}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{document}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\setcounter{section}{-1} %% Remove this when starting to work on the template.
 
 \section{Introduction\label{sec: intro}}
-
-\paragraph{Water desalination technologies}
-
+\subsection{Water desalination technologies}
 Two basic approaches for separating water from salt are present in modern desalination technology \cite{Miller2003,Curto2021}.
@@
 
-\paragraph{Hydrogels for desalination}
+\subsection{Hydrogels for desalination}
 Hydrogels are three-dimensional networks of polymer chains that are crosslinked by either physical or chemical bonds. 
@@
 
-\paragraph{Physics behind the desalination process}
+\subsection{Physics behind the desalination process}
 %The maximum entropy principle requires the density of charges to be more-less the same throughout the system medium. 
@@
 
-Our model of the gel is a network of 16 linear polymer chains, each consisting of 30 monomer units. 
+Our model of the gel is a network of 16 linear polymer chains, each consisting of 30 monomer 
+units. 
 These polymer chains are connected to a diamond-like network by 8 crosslinking units.
-This means, there are together $\Ngel=16\cdot30 + 8=488$ gel monomers in the simulation box (see \reffig{fig:diamond}).
-Each monomer unit of the network carries a negative elementary electric charge, thus simulating fully ionized polyacidic gel.
-Except the particles in the network, the monovalent co- and counter-ions ions, $\cl$ and $\na$, are present in simulation box. 
-The total electric charge of all the particles in the box is zero, therefore the amount of $\na$ ions is bigger than that of $\cl$ by the number of hydrogel units.
+This means, there are $\Ngel=16\cdot30 + 8=488$ gel monomers in the simulation box 
+(see \reffig{fig:diamond}).
+Each monomer unit of the network carries a negative elementary electric charge, thus 
+simulating fully ionized polyacidic gel.
+Except the particles in the network, the monovalent co- and counter-ions ions, 
+$\cl$ and $\na$, are present in simulation box. 
+The total electric charge of all the particles in the box is zero, therefore the amount 
+of $\na$ ions is bigger than that of $\cl$ by the number of hydrogel units.
 The entire simulation box setup employs periodic boundaries.
 
-\begin{figure*}[t]
+\begin{figure*}[h]
 \centering 
@@
 \subsection{Gibbs ensemble}
-\todoi{We have the "Gibbs ensemble" in the title, and this term is not used in the manuscript at all.}
+\todo{We have the "Gibbs ensemble" in the title, and this term is not used in the manuscript at all.}
 TODO concise description of Gibbs ensemble, solving the task to Reviewer 2, Q5 and Q7
@@
 \begin{enumerate}
-\item \emph{open system}, when the simulation box with gel exchanges ions with an infinite reservoir containing aqueous solution of constant salinity, $\cs$. 
+\item \emph{open system}, when the simulation box with gel exchanges ions with an infinite 
+reservoir containing aqueous solution of constant salinity, $\cs$. 
 \item emph{closed system}, when the simulation box with the gel exchanges ions with a finite volume of aqueous solution.
 \end{enumerate}
-The compression of the gel in the \emph{open system} does not affect the salinity in the reservoir, thus the density of ions outside the gel remains constant $\cs =$ $\cna=$ $\ccl=$ $\text{Const}$ (\reffig{fig: open}).
+The compression of the gel in the \emph{open system} does not affect the salinity in the 
+reservoir, thus the density of ions outside the gel remains constant 
+$\cs =$ $\cna=$ $\ccl=$ $\text{Const}$ (\reffig{fig: open}). 
 On the contrary, the compression of the gel in the \emph{closed system} changes the salinity in the reservoir, but the total number of $\na$ and $\cl$ ions in the gel and in the reservoir, \ie in the volume $\Vbox$ (\reffig{fig: closed}), remains constant.
@@
 where $i \in \{\na, \cl\}$, $\Vgel$~--- volume of the gel, $\Vbox$~--- the volume in which the gel is compressed. 
-Vbox$ is the gel volume in the free swelling equilibrium state.
+$\Vbox$ is the gel volume in the free swelling equilibrium state.
 
-\paragraph{Open system}
+\subsection{Open system}
 We use the grand reaction method \cite{Landsgesel2020a,Rud2020} to simulate the open system.
+\todo{beter to say "method described in REF", to avoid the word 'grand reaction'}
 This method is a hybrid of Molecular dynamics (MD) and Monte Carlo (MC). 
@@
 The insertion (and deletion) of ion pairs is considered as a reaction of creation (or annihilation) of an ion pair 
-\[
+\begin{equation}
 \varnothing\stackrel{K}{\leftrightarrows}\na+\cl
-\]
+\end{equation}
 with a reaction constant defined by the chemical potential of ions,
 $K=\exp\left(\muna+\mucl\right).$
-The simulation setup is sketched in \reffig{fig:open}.
+The simulation setup is sketched in \reffig{fig:open}\todo{it is not a 'simulation' setup}.
 
-\paragraph{Closed system}
+\subsection{Closed system}
 Analogical scheme is used for the simulation of the gel in the closed system. 
@@
 
-\paragraph{Algorithm}
-The thermodynamic equilibrium between the two subvolumes implies the exchange of ion pairs between them.
+\subsection{Algorithm}
+The thermodynamic equilibrium between the two subvolumes implies the exchange of ion pairs 
+between them.
 This is performed by means of MC procedure in a way similar to described in \cite{Panagiotopoulos1988b}.
@@
 
-\paragraph{Compression in open system}
-\begin{figure*}[t]
+\subsection{Compression in open system}
+\begin{figure*}[h]
+	\begin{adjustwidth}{-\extralength}{0cm}
 	\subfloat[The gel partial pressure vs gel molar volume \label{fig: PV}]
-{\includegraphics[width=0.48\textwidth]{figures/fig_PV_pub.pdf}}
+		{\includegraphics[width=0.65\textwidth]{figures/fig_PV_pub.pdf}}
 	\hspace{0.02\textwidth}
 	\subfloat[Supernate salinity vs gel molar volume\label{fig: CV}]
-{\includegraphics[width=0.48\textwidth]{figures/fig_CV_pub.pdf}}
+		{\includegraphics[width=0.65\textwidth]{figures/fig_CV_pub.pdf}}
 	\caption{
@@
 	The shadowed areas limit the states with applied pressure below zero and above 5 bar.\label{fig: PV and CV}}
+	\end{adjustwidth}
 \end{figure*}
-First, we ran a set of simulations modeling the gel compression in \emph{open system}, \ie in equilibrium with a big bath of certain salinity, $\cs$. 
+First, we run a set of simulations modeling the gel compression in \emph{open system}, \ie in equilibrium with a big bath of certain salinity, $\cs$. 
 The simulations were run for a set of different simulation box volumes. 
-Each simulation provided pressure, $P$, and the number of $\cl$ ions, which are present in the simulation box, $\ncl$.
+Each simulation returned the averaged values of pressure, $P$, and the number of $\cl$ ions, present in the simulation box, $\ncl$.
 
@@
 
-\begin{figure*}[t]
+\begin{figure*}[h]
+\begin{adjustwidth}{-\extralength}{0cm}
 \subfloat[Pressure vs gel molar volume \label{fig: NV}]
-{\includegraphics[width=0.49\textwidth]{figures/fig_NV_pub.pdf}}
+{\includegraphics[width=0.65\textwidth]{figures/fig_NV_pub.pdf}}
+\hspace{0.02\textwidth}
 \subfloat[Salinity vs gel molar volume\label{fig: CN}]
-{\includegraphics[width=0.495\textwidth]{figures/fig_NVbox_mu_pub.pdf}}
-\caption{The compression of the gel in the \emph{open system} (solid lines) and in the \emph{closed system} (dotted lines). 
-The shadowed areas limit the states with applied pressure below zero and above 5 bar.
+{\includegraphics[width=0.65\textwidth]{figures/fig_NVbox_mu_pub.pdf}}
+\caption{The compression of the gel in \emph{open system} (solid lines) and in \emph{closed system} (dotted lines). 
+Shadowed area limit the states with applied pressure below zero and above 5 bar.
 The values $N_\cl$ are the virtual numbers of present $\cl$ ions in \emph{closed system} simulation boxes.
 \label{fig: NV and CN}}
-
+\end{adjustwidth}
 %\todoi{Replace y-axis labels by $\ncl$}
@@
 
-\paragraph{Compression in closed system}
+\subsection{Compression in closed system}
 The simulations in \emph{closed systems} start from the $\Vgel^0$ and \{$\Nna^0$, $\Ncl^0$\} values
@@
 
-\paragraph{Desalination scheme}
+\subsection{Desalination scheme}
 It follows that the compression of the gel in the \emph{closed system} affects the salinity, whereas the compression in the \emph{open system} affects the amount of ions in the gel subsystem. 
@@
 The third column shows the change of the gel volume in corresponding process, $\Delta v$. 
-The fourth column contains the work needed for the compression in the corresponding process per volume of extracted solution. 
-This value is an integral of corresponding $\Pgel(\Vgel)$ dependence
+The fourth column contains the work needed for the compression in the corresponding process 
+per volume of extracted solution. 
+This value is an integral of corresponding $\Pgel(\Vgel)$ dependence \citep{Atkins} 
 \begin{equation}
@@
 \end{equation}
-Table 1 presents the absolute values of the work. Note that the compression implies the work done by external force, but the swelling implies the work done by the gel.
+\todo{the equation must be supported by referrence}
+Here, in the table, we present the absolute values of the work, 
+whereas one should keep in mind that the compression implies the work 
+is done by external force and the swelling implies that the work is done by gel.
 
 \begin{table}
-\begin{tabular*}{1\textwidth}{@{\extracolsep{\fill}}ll|lc|c|l|ll}
+\caption{The estimates of the efficiency of the desalination process. All the units are calculated per one mol of gel segments. Values in brackets
+are the estimates corresponding to crossection of 'red' and 'orange' lines on the plots of Figures \ref{fig: PV and CV} and \ref{fig: NV and CN}
+\label{tab: table}}
+\begin{adjustwidth}{-0.0\extralength}{0cm}
+		\newcolumntype{C}{>{\centering\arraybackslash}X}
+\begin{tabularx}{1\textwidth}{@{\extracolsep{\fill}}ll|lc|c|l|ll}
 \multicolumn{1}{l|}{$c_{s}^{0}$, mM} & $c_{s}^{5}$, mM & \multicolumn{1}{l|}{$n_{\cl}^{0}$, mM} & $n_{\cl}^{5}$, mM & $\Delta \Vgel$, l & $|W$\textbar , J/l & \multicolumn{2}{c}{$W^{id}$, J/l}\tabularnewline
@@
 $W_{\mathrm{sim}}$ is the energy calculated by integration of $\Pgel(\Vgel)$ dependencies as the sum of corresponding compressions in \emph{closed} and \emph{open} systems, $W_{\mathrm{id}}$ is the estimation based on the equation \refeq{eq:SEC} and $R_w$ is the corresponding recovery ratio.
+\todo{how the integration was performed}
 Note that calculating the $W_{\mathrm{sim}}$ we accounted for only the work done on the gel during the compression, whereas the work done by the gel itself during swelling was not taken into account.
@@
 \section{Conclusions}
-We have modeled the compression of the gel in thermodynamic equilibrium with the reservoir of the limited amount of water.
-We have shown that in the case of gel made of strong polyelectrolyte, the compression always decreases the surrounding salinity.
-We have modeled the process of water desalination by combining two processes: 
-(1) the swelling of the gel in \emph{open} system, exchanging ions with a big reservoir at constant salinity. 
-(2) the compression of the gel in \emph{closed} system, when the gel affects the salinity in the surrounding solution.
-We estimated the energy needed to produce one liter of water and have shown that the method may compete with the modern technologies used in modern industry.
+We have modeled the compression of the gel in thermodynamic equilibrium with the reservoir of the limited water amount.
+We have shown that the compression always decreases the surrounding salinity in the case of strong polyelectrolyte gel.
+We have modeled the process of water desalination by sequential combinations of two processes: 
+(1) swelling of the gel in \emph{open system}, exchanging ions with a big reservoir at constant salinity
+(2) compression of the gel in \emph{closed system}, when the gel affects the salinity in the surrounding solution
+We estimated the energy consumtion of this process for production of one liter potable water from brine as $W^{id} =$ 38.2 J/l.
+We have shown that this method may compete with the modern technologies used in modern industry. \todo{energy costs of other desalination methods???}
 

### 2022-09-06 scripts/data/.unison.sh

@@ -1,0 +1,13 @@
+#!/bin/bash
+# set paths / dirs
+_path="$HOME/gibbs/scripts/data/"
+ 
+# binary file name
+_unison=/usr/bin/unison-2.48-gtk
+ 
+# server names 
+# sync server1.cyberciti.com with rest of the server in cluster
+_rserver="owain.natur.cuni.cz"
+ 
+${_unison} -batch "${p}"  "ssh://${_rserver}/${_path}"
+

### 2022-09-06 MDPI/response_letter.tex
Update MDPI/response_letter.tex

@@
 \item \textit{Where is the method of this work?} 
-We did not want to bother the readers too much with technical aspects of the smulations. 
-The method idea is outlined in the paragraph "Physics behind the desalination process" and described in the section "Theory behind the simulation". Some more technical issues are in ESI.
+The method idea is outlined in the paragraph "Physics behind the desalination process" and described in the section "Theory behind the simulation".
+We did not want to bother the readers too much with technical aspects of the smulations, so technical details are in ESI.
 \item \textit{It is suggested that to carefully improve this manuscript as well as the writing and grammatical error.}
@@
 \item \textit{Statistical physics considerations including setup and calculations should be added.}
+We added the paragraph about Gibbs ensemble.
 \item \textit{The authors should identify the limitations of this study and the recommended future studies in the conclusion part.

### 2022-09-06 gibbs_achemso.tex

--- 2022-09-05 gibbs.tex
@@
 $W_{\mathrm{sim}}$ is the energy calculated by integration of $\Pgel(\Vgel)$ dependencies as the sum of corresponding compressions in \emph{closed} and \emph{open} systems, $W_{\mathrm{id}}$ is the estimation based on the equation \refeq{eq:SEC} and $R_w$ is the corresponding recovery ratio.
+\todoi{how the integration was performed}
 Note that calculating the $W_{\mathrm{sim}}$ we accounted for only the work done on the gel during the compression, whereas the work done by the gel itself during swelling was not taken into account.
@@
 \section{Conclusions}
-We have modeled the compression of the gel in thermodynamic equilibrium with the reservoir of the limited amount of water.
-We have shown that in the case of gel made of strong polyelectrolyte, the compression always decreases the surrounding salinity.
-We have modeled the process of water desalination by combining two processes: 
-(1) the swelling of the gel in \emph{open} system, exchanging ions with a big reservoir at constant salinity. 
-(2) the compression of the gel in \emph{closed} system, when the gel affects the salinity in the surrounding solution.
-We estimated the energy needed to produce one liter of water and have shown that the method may compete with the modern technologies used in modern industry.
+We have modeled the compression of the gel in thermodynamic equilibrium with the reservoir of the limited water amount.
+We have shown that the compression always decreases the surrounding salinity in the case of strong polyelectrolyte gel.
+We have modeled the process of water desalination by sequential combinations of two processes: 
+(1) swelling of the gel in \emph{open system}, exchanging ions with a big reservoir at constant salinity
+(2) compression of the gel in \emph{closed system}, when the gel affects the salinity in the surrounding solution
+We estimated the energy consumtion of this process for production of one liter potable water from brine as $W^{id} =$ 38.2 J/l.
+We have shown that this method may compete with the modern technologies used in modern industry. \todoi{energy costs of other desalination methods???}
 

### 2022-09-06 gibbs_mdpi.tex

@@
 The third column shows the change of the gel volume in corresponding process, $\Delta v$. 
-The fourth column contain the work needed for the compression in the corresponding process, calculated per volume of extracted solution. 
-This value is an integral of corresponding $\Pgel(\Vgel)$ dependence
+The fourth column contain the work needed for the gel compression in the corresponding process.
+This value is an integral of corresponding $\Pgel(\Vgel)$ dependence \citep{Atkins} 
 \begin{equation}

### 2022-09-06 gibbs.tex
Alternative titles added
Update gibbs.tex

--- 2022-09-05 gibbs.tex
@@
 
-\section{Conclusions}
-We have modeled the compression of the gel in thermodynamic equilibrium with the reservoir of the limited amount of water.
-We have shown that in the case of gel made of strong polyelectrolyte, the compression always decreases the surrounding salinity.
-We have modeled the process of water desalination by combining two processes: 
-(1) the swelling of the gel in \emph{open} system, exchanging ions with a big reservoir at constant salinity. 
-(2) the compression of the gel in \emph{closed} system, when the gel affects the salinity in the surrounding solution.
-We estimated the energy needed to produce one liter of water and have shown that the method may compete with the modern technologies used in modern industry.
-
 \subsection{Study limitations}
-TODO
+Like other simulation based studies, our research has a limited validity,
+primarily resulting from the simplifications applied in the used model.
+For example, our coarse-grained model cannot differentiate polystyrene sulphonate gel from other strong polyacidic gels.
+However, these limitations are also the advantage of our model because the results of our study
+can be applied to similar systems, including polybasic gels with all the charges reversed.
 
 \subsection{Implications and future perspectives}
-TODO
+We are aware that the concept introduced in this simulation study need to be experimentally verified.
+Therefore, in the future, we want to focus on experimental aspects of desalination based on polyacidic gel compression.
+
+\section{Conclusions}
+We have modeled the compression of the gel in thermodynamic equilibrium with the reservoir of the limited water amount.
+We have shown that the compression always decreases the surrounding salinity in the case of strong polyelectrolyte gel.
+We have modeled the process of water desalination by sequential combinations of two processes: 
+(1) swelling of the gel in \emph{open system}, exchanging ions with a big reservoir at constant salinity
+(2) compression of the gel in \emph{closed system}, when the gel affects the salinity in the surrounding solution
+We estimated the energy consumtion of this process for production of one liter potable water from brine as $W^{id} =$ 38.2 J/l.
+We have shown that this method may compete with the modern technologies used in modern industry. \todoi{energy costs of other desalination methods???}
 

### 2022-09-06 gibbs.tex

--- 2022-09-06 gibbs.tex
@@
 \Title{Water desalination using polyelectrolyte hydrogel: Gibbs ensemble modeling}
+
+% Alternative titles
+%\Title{What the Gibbs ensemble modeling says about water desalination using polyelectrolyte hydrogel}
+%\Title{Water desalination using polyelectrolyte hydrogel from the Gibbs ensemble modeling point of view}
 
@@
 
+\subsection{Study limitations}
+Like other simulation based studies, our research has a limited validity,
+primarily resulting from the simplifications applied in the used model.
+For example, our coarse-grained model cannot differentiate polystyrene sulphonate gel from other strong polyacidic gels.
+However, these limitations are also the advantage of our model because the results of our study
+can be applied to similar systems, including polybasic gels with all the charges reversed.
+
+\subsection{Implications and future perspectives}
+We are aware that the concept introduced in this simulation study need to be experimentally verified.
+Therefore, in the future, we want to focus on experimental aspects of desalination based on polyacidic gel compression.
+
 \section{Conclusions}
@@
 We have shown that this method may compete with the modern technologies used in modern industry. \todo{energy costs of other desalination methods???}
-
-\subsection{Study limitations}
-TODO
-
-\subsection{Implications and future perspectives}
-TODO
 

### 2022-09-06 gibbs.tex
Update gibbs.tex

@@
 We are aware that the concept introduced in this simulation study need to be experimentally verified.
-Therefore, in the future, we want to focus on experimental aspects of desalination based on polyacidic gel compression.
 
@@
 (2) compression of the gel in \emph{closed system}, when the gel affects the salinity in the surrounding solution
-We estimated the energy consumtion of this process for production of one liter potable water from brine as $W^{id} =$ 38.2 J/l.
-We have shown that this method may compete with the modern technologies used in modern industry. \todo{energy costs of other desalination methods???}
+We estimated the energy consumtion of the whole process for production of one liter potable water from brine as $W^{id} =$ 38.2 J/l.
+Let us compare this value with the energy cost of RO, which is around 20000 J/l.
+We have shown that the propsed gel compression method can compete with modern technologies used in modern industry.
 

### 2022-09-06 gibbs.tex
added references proposed by third reviewer

--- 2022-09-06 gibbs.tex
@@
 \subsection{Water desalination technologies}
+
+\todo[inline]{
+The authors can follow the following references to generally highlight the global contamination and environmental pollution problems at the beginning of the introduction part
+https://doi.org/10.1016/j.jwpe.2022.102847 \cite{baaloudj2022_1}\\
+https://doi.org/10.1016/j.ceramint.2022.05.151 \cite{shahzad2022}\\
+https://doi.org/10.3390/catal12050500 \cite{baaloudj2022}\\
+https://doi.org/10.1007/s11356-022-21160-7 \cite{guesmi2022}\\
+https://doi.org/10.3390/ma15134547 \cite{kane2022}\\. 
+Then, highlight the water desalination technologies and Gibbs ensemble (https://doi.org/10.3390/nano10020293 \cite{erdos2020}).
+}
+
 Two basic approaches for separating water from salt are present in modern desalination technology \cite{Miller2003,Curto2021}.
@@
 
-\subsection{Study limitations}
-Like other simulation based studies, our research has a limited validity,
-primarily resulting from the simplifications applied in the used model.
-For example, our coarse-grained model cannot differentiate polystyrene sulphonate gel from other strong polyacidic gels.
-However, these limitations are also the advantage of our model because the results of our study
-can be applied to similar systems, including polybasic gels with all the charges reversed.
-
-\subsection{Implications and future perspectives}
-We are aware that the concept introduced in this simulation study need to be experimentally verified.
-Therefore, in the future, we want to focus on experimental aspects of desalination based on polyacidic gel compression.
-
 \section{Conclusions}
@@
 We have shown that this method may compete with the modern technologies used in modern industry. \todo{energy costs of other desalination methods???}
+
+\subsection{Study limitations}
+TODO
+
+\subsection{Implications and future perspectives}
+TODO
 

### 2022-09-06 gibbs.tex
Apply 1 suggestion(s) to 1 file(s)

--- 2022-09-06 gibbs.tex
@@
 (2) compression of the gel in \emph{closed system}, when the gel affects the salinity in the surrounding solution
-We estimated the energy consumtion of the whole process for production of one liter potable water from brine as $W^{id} =$ 38.2 J/l.
+We estimated the energy consumption of the whole process for producing a liter of potable water from brine as $W^{id} =$ 38.2 J/l.
 Let us compare this value with the energy cost of RO, which is around 20000 J/l.

### 2022-09-07 gibbs.tex
more about the model

@@
 
-Our model of the gel is a network of 16 linear polymer chains, each consisting of 30 monomer 
+We propose a cascade desalination process to lower supernatant salinity, it is worth to note that we are not limited with this process only.
+For this process the gel must be commpressed/decompressed in an \emph{open} and \emph{closed} system.
+
+By the \emph{open system} we mean that the gel is equlibrated with an \textbf{infinite} reservoir outside, such that there are the same ions chemical potential, the same temperature and desired pressure difference between the gel and the reservoir.
+Number of  $\na$ and $\cl$ ions and gel volume $\Vgel$ are allowed to change.
+
+By the \emph{closed system} we mean that the gel is equlibrated with a \textbf{finite} reservoir, in this case after equilibration the gel and the reservoir again have the same ions chemical potential, the same temperature and desired pressure difference between the gel and the reservoir.
+Although, the number of ions and volume of gel and reservoir may vary, the total number of ions and the total volume are constant.
+
+The compression of the gel in the \emph{open system} does not affect the salinity in the 
+reservoir, thus the density of ions and their chemical potential outside the gel remains constant 
+$\cs =$ $\cna=$ $\ccl=$ $\text{Const}$ (\reffig{fig: open}). 
+On the contrary, the compression of the gel in the \emph{closed system} changes the salinity in the reservoir, but the total number of $\na$ and $\cl$ ions in the gel and in the reservoir, \ie in the volume $\Vbox$ (\reffig{fig: closed}), remains constant.
+
+In the both cases there is two coexisting systems with constant $\mu P T$ allowed to exchange particles and change volume, which is represented as Gibbs ensemble.
+
+Unfortunately, there is no universal computationally effective technique to sample pressure difference, volume, and number of particles at the same.
+To equilibrate and sample pressure difference and volume we use molecular dynamics (MD) simulation, while equlibration and sampling of ions distribution between the gel and a reservoir is done via Monte-Carlo (MC) simulation.
+In this sence employed techniques is called MCMD.
+
+To simulate processes in \emph{open system} and  \emph{closed system} two complementary models MC and MD were implemented.
+
+\subsubsection*{Molecular Dynamics}
+
+Our MD model of the gel is a network of 16 linear polymer chains, each consisting of 30 monomer 
 units. 
@@
 The entire simulation box setup employs periodic boundaries. 
+This model is used in MD part of \emph{open system} and \emph{closed system} simulation.
+
+For the MD part of emph{closed system} simulation analougous simulation box is created without any polymer monomers.
 
@@
 \end{figure*}
+
+\subsection{}
 

### 2022-09-07 gibbs.tex
minor

@@
 
-\subsubsection*{Molecular Dynamics}
+\subsubsection*{Molecular Dynamics model}
 
@@
 The entire simulation box setup employs periodic boundaries.
+Coloumb interaction computed by P3M method.
 This model is used in MD part of \emph{open system} and \emph{closed system} simulation.
 
-For the MD part of emph{closed system} simulation analougous simulation box is created without any polymer monomers.
+For the MD part of \emph{closed system} simulation analougous simulation box is created without any polymer monomers to model the finite reservoir. 
+The amount of $\na$ ions is equal to $\cl$.
+
+By integration Langevin motion equation by Verlet algorithm for each particles we sample 
+total energy of the system and pressure. 
+Kinetic energy, bonded, non-bonded and Coloumb interaction contribute to the total energy of a system.
+Pressure in the system calculated as in ref [Essmann et al., 1995, doi:10.1063/1.470117]
+\todo{I do not know if it is needed, ML}
+
+When computing MD the gel and reservoir box are essentially NVT-ensembles.
+
+\subsubsection*{Monte Carlo model}
+
+In the \emph{open system} system box with the gel and the monovalent co- and counter-ions ions, 
+$\cl$ and $\na$ is allowed to exchange particles with infinite reservoir with constant chemical potential.
+
+\dots
+
+In the \emph{closed system} system two boxes one with the gel and the other with ions pairs only iare allowed to exchange particles.
 

### 2022-09-07 gibbs.tex
conclusions rewritten

--- 2022-09-06 gibbs.tex
@@
 \section{Conclusions}
-We have modeled the compression of the gel in thermodynamic equilibrium with the reservoir of the limited water amount.
-We have shown that the compression always decreases the surrounding salinity in the case of strong polyelectrolyte gel.
-We have modeled the process of water desalination by sequential combinations of two processes: 
-(1) swelling of the gel in \emph{open system}, exchanging ions with a big reservoir at constant salinity
-(2) compression of the gel in \emph{closed system}, when the gel affects the salinity in the surrounding solution
-We estimated the energy consumption of the whole process for producing a liter of potable water from brine as $W^{id} =$ 38.2 J/l.
-Let us compare this value with the energy cost of RO, which is around 20000 J/l.
-We have shown that the propsed gel compression method can compete with modern technologies used in modern industry.
+We have modeled the compression of the polyelectrolyte gel in thermodynamic equilibrium with the supernatant aqueous solution of a limited amount.
+We have shown that the compression of the gel decreases the supernatant salinity.
+We employed this phenomenon for modeling the process of water desalination.
+The desalination was done as a sequential combination of two processes:
+(1) swelling of the gel in \emph{open system}, exchanging ions with a big reservoir at constant salinity;
+(2) compression of the gel in \emph{closed system}, when the gel exchanges ions with a small reservoir affecting its salinity.
+We estimated the energy consumption needed for producing one liter of potable water from brine and have shown that the proposed gel compression method may compete with modern desalination technologies.
 

### 2022-09-08 gibbs.tex
Apply 1 suggestion(s) to 1 file(s)

--- 2022-09-07 gibbs.tex
@@
 
-By the \emph{closed system} we mean that the gel is equlibrated with a \textbf{finite} reservoir, in this case after equilibration the gel and the reservoir again have the same ions chemical potential, the same temperature and desired pressure difference between the gel and the reservoir.
+By the \emph{closed system} we mean that the gel is equilibrated with a \textbf{finite} reservoir of an aqueous solution, in this case after equilibration the gel and the reservoir again have the same ions chemical potential, the same temperature, and desired pressure difference between the gel and the reservoir.
 Although, the number of ions and volume of gel and reservoir may vary, the total number of ions and the total volume are constant.

### 2022-09-08 gibbs.tex
Apply 1 suggestion(s) to 1 file(s)

@@
 
-By the \emph{open system} we mean that the gel is equlibrated with an \textbf{infinite} reservoir outside, such that there are the same ions chemical potential, the same temperature and desired pressure difference between the gel and the reservoir.
-Number of  $\na$ and $\cl$ ions and gel volume $\Vgel$ are allowed to change.
+By the \emph{open system} we mean that the gel is in thermodynamic equilibrium with an \textbf{infinite} reservoir of an aqueous solution.
+%, such that there are the same ion's chemical potential, the same temperature, and desired pressure difference between the gel and the reservoir.
+The number of  $\na$ and $\cl$ ions and gel volume $\Vgel$ are allowed to change.
 

### 2022-09-08 gibbs.tex
minor
intrmediate changes in model section

@@
 
-We propose a cascade desalination process to lower supernatant salinity, it is worth to note that we are not limited with this process only.
+We propose a cascade desalination process to lower supernatant salinity.
+%it is worth to note that we are not limited with this process only.
 For this process the gel must be commpressed/decompressed in an \emph{open} and \emph{closed} system.
-
-By the \emph{open system} we mean that the gel is in thermodynamic equilibrium with an \textbf{infinite} reservoir of an aqueous solution.
+By the \emph{open system} we mean that the gel is in thermodynamic equilibrium with huge, effectively \textbf{infinite}, reservoir of an aqueous solution. 
+The gel freely exchanges ions with the reservoir, while their concentration in reservoir (and chemical potential) remains constant.
 %, such that there are the same ion's chemical potential, the same temperature, and desired pressure difference between the gel and the reservoir.
 The number of  $\na$ and $\cl$ ions and gel volume $\Vgel$ are allowed to change.
+By the \emph{closed system} we mean that the gel is in equilibrium with a \textbf{finite} reservoir of an aqueous solution. 
+In this case the exchange of ions between the gel and the reservoir may affect their concentration in reservoir, whereas the  
+%again have the same ions chemical potential, the same temperature, and desired pressure difference between the gel and the reservoir. 
+%Although, the number of ions and volume of gel and reservoir may vary, 
+the total number of ions (in gel and in reservoir) is constant.
 
-By the \emph{closed system} we mean that the gel is equilibrated with a \textbf{finite} reservoir of an aqueous solution, in this case after equilibration the gel and the reservoir again have the same ions chemical potential, the same temperature, and desired pressure difference between the gel and the reservoir.
-Although, the number of ions and volume of gel and reservoir may vary, the total number of ions and the total volume are constant.
-
-The compression of the gel in the \emph{open system} does not affect the salinity in the 
-reservoir, thus the density of ions and their chemical potential outside the gel remains constant 
-$\cs =$ $\cna=$ $\ccl=$ $\text{Const}$ (\reffig{fig: open}). 
+Due to huge size of the reservoir, the compression of the gel in the \emph{open system} does not affect the reservoir salinity, $\cs =$ $\cna=$ $\ccl=$ $\text{Const}$ (\reffig{fig: open}), whereas the number of ions entrapped in the volume $\Vbox$ changes.
 On the contrary, the compression of the gel in the \emph{closed system} changes the salinity in the reservoir, but the total number of $\na$ and $\cl$ ions in the gel and in the reservoir, \ie in the volume $\Vbox$ (\reffig{fig: closed}), remains constant.
 
-In the both cases there is two coexisting systems with constant $\mu P T$ allowed to exchange particles and change volume, which is represented as Gibbs ensemble.
+%In both cases there are two coexisting systems with constant $\mu P T$ allowed to exchange particles and change volume, which is represented as Gibbs ensemble.
 

### 2022-09-08 gibbs.tex
MD

@@
 
-\section{Theory behind the simulation\label{sec: theory}}
+\section{Model and methods\label{sec: theory}}
 
@@
 
-\subsection{Model}
+\subsection{Open and closed sytems}
 
@@
 %it is worth to note that we are not limited with this process only.
-For this process the gel must be commpressed/decompressed in an \emph{open} and \emph{closed} system.
+For this process the gel must be compressed/decompressed in an \emph{open} and \emph{closed} system.
 By the \emph{open system} we mean that the gel is in thermodynamic equilibrium with huge, effectively \textbf{infinite}, reservoir of an aqueous solution. 
-The gel freely exchanges ions with the reservoir, while their concentration in reservoir (and chemical potential) remains constant.
+%The gel freely exchanges ions with the reservoir, while their concentration in reservoir (and chemical potential) remains constant.
 %, such that there are the same ion's chemical potential, the same temperature, and desired pressure difference between the gel and the reservoir.
@@
 By the \emph{closed system} we mean that the gel is in equilibrium with a \textbf{finite} reservoir of an aqueous solution. 
-In this case the exchange of ions between the gel and the reservoir may affect their concentration in reservoir, whereas the  
+In this case the exchange of ions between the gel and the reservoir may affect their concentration in reservoir.%, whereas the  
 %again have the same ions chemical potential, the same temperature, and desired pressure difference between the gel and the reservoir. 
 %Although, the number of ions and volume of gel and reservoir may vary, 
-the total number of ions (in gel and in reservoir) is constant.
+%total number of $\na$ and $\cl$ ions in the gel and in the reservoir, \ie in the volume $\Vbox$ remains constant.
 
-Due to huge size of the reservoir, the compression of the gel in the \emph{open system} does not affect the reservoir salinity, $\cs =$ $\cna=$ $\ccl=$ $\text{Const}$ (\reffig{fig: open}), whereas the number of ions entrapped in the volume $\Vbox$ changes.
+Due to huge size of the reservoir, the compression of the gel in the \emph{open system} does not affect the reservoir salinity, $\cs =$ $\cna=$ $\ccl=$ $\text{Const}$ (\reffig{fig: open}), whereas the number of ions entrapped in the volume $\Vbox$ changes (\reffig{fig: closed}).
 On the contrary, the compression of the gel in the \emph{closed system} changes the salinity in the reservoir, but the total number of $\na$ and $\cl$ ions in the gel and in the reservoir, \ie in the volume $\Vbox$ (\reffig{fig: closed}), remains constant.
@@
 
-Unfortunately, there is no universal computationally effective technique to sample pressure difference, volume, and number of particles at the same.
-To equilibrate and sample pressure difference and volume we use molecular dynamics (MD) simulation, while equlibration and sampling of ions distribution between the gel and a reservoir is done via Monte-Carlo (MC) simulation.
-In this sence employed techniques is called MCMD.
+%Unfortunately, there is no universal computationally effective technique to sample pressure difference, volume, and number of particles at the same. 
+The mechanical movement and the exchange of ions occur simulataneously in real systems, however, we simulate them alternating each other in stop-run mode in a random order. 
+To sample mechanical properties of the gel and reservoir we use MD simulation, whereas to sample the ions distribution between the gel and a reservoir we use MC simulation.
+The details of this hybryd computational technique can be found in our previous studies of polyelectrolytes in open system \cite{Rud2020, Rud2022, Landsgesel2020a}.
 
-To simulate processes in \emph{open system} and  \emph{closed system} two complementary models MC and MD were implemented.
+%In this sense employed techniques is called MCMD.
 
-\subsubsection*{Molecular Dynamics model}
+%To simulate processes in \emph{open system} and  \emph{closed system} two complementary models MC and MD were implemented.
 
-Our MD model of the gel is a network of 16 linear polymer chains, each consisting of 30 monomer 
-units. 
+\subsection{Langevin Dynamics}
+
+We model the gel as a network of 16 linear polymer chains, each consisting of 30 monomer units. 
 These polymer chains are connected to a diamond-like network by 8 crosslinking units.
@@
 The total electric charge of all the particles in the box is zero, therefore the amount 
-of $\na$ ions is bigger than that of $\cl$ by the number of hydrogel units.
-The entire simulation box setup employs periodic boundaries.
-Coloumb interaction computed by P3M method.
-This model is used in MD part of \emph{open system} and \emph{closed system} simulation.
+of $\na$ ions is bigger than that of $\cl$ by the number of hydrogel units, $\Ngel$.
+The solvent assumed to be water, which is modeled implicitly via setting up dielectric permittivity $\epsilon=80$.
 
-For the MD part of \emph{closed system} simulation analougous simulation box is created without any polymer monomers to model the finite reservoir. 
-The amount of $\na$ ions is equal to $\cl$.
+We use three types of interactions, \ie bonded interactions, short-range non-bonded interactions and electrostatic interactions.
 
-By integration Langevin motion equation by Verlet algorithm for each particles we sample 
-total energy of the system and pressure. 
-Kinetic energy, bonded, non-bonded and Coloumb interaction contribute to the total energy of a system.
-Pressure in the system calculated as in ref [Essmann et al., 1995, doi:10.1063/1.470117]
-\todo{I do not know if it is needed, ML}
+We use Finite extension nonlinear elastic (FENE) potential~\refeq{eq:fene} to account for the bonding interactions.
+\begin{equation}\label{eq:fene}
+    V_\mathrm{FENE}(r) = -\frac{1}{2} K \Delta r_\mathrm{max}^2\ln \left[ 1 - \left(\frac{r-r_0}{\Delta r_\mathrm{max}} \right)^2 \right ],
+\end{equation}
+where $K$ is the magnitude of symmetric interaction between two segments,
+$\Delta r_{\mathrm{max}}$ is the maximal stretching length of the bond and $r_0$ is the equilibrium bond length.
+In our simulations we set $K = 10 \kT/\sigma^{2}$, $\Delta r_{\mathrm{max}} = 2 \sigma$ and $r_0 = 1.0\sigma$~\cite{Jin2007}.
 
-When computing MD the gel and reservoir box are essentially NVT-ensembles.
+The non-bonded interactions are modelled by the truncated Lennard-Jones interaction potential.
+This potential imposes strong repulsion between all particles at short distances:
+\begin{equation}
+    \begin{split}\label{eq:LJ}
+        V_\mathrm{LJ}(r) =
+        \begin{cases}
+            4 \varepsilon \left( \left(\cfrac{\sigma}{r}\right)^{12}
+            - \left(\cfrac{\sigma}{r}\right)^6\right)
+            & \mathrm{if~} r < r_\mathrm{cut}\\
+            0
+            & \mathrm{elsewhere}
+        \end{cases},
+    \end{split}
+\end{equation}
+where $r$ is the interparticle distance,
+$\sigma = 0.35 \mathrm{nm}$ is a chosen characteristic size of the particles,
+$\varepsilon$ is the depth of the potential well in $\kT$ units and $r_\mathrm{cut}$ is the cut-off distance beyond which the potential is set zero.
 
-\subsubsection*{Monte Carlo model}
+We model the long range electrostatic interactions by the Coulomb potential:
+\begin{equation}
+    V_{\mathrm{EL}}=\lb\kT \cfrac{q_{1}q_{2}}{r},
+\end{equation}
+where $\lb$ is Bjerrum length; $\lb = 2\sigma = 0.7 \mathrm{nm}$ which corresponds to water the Bjerrum length in water at $T=300 \mathrm{K}$.
 
-In the \emph{open system} system box with the gel and the monovalent co- and counter-ions ions, 
+We use Langevin thermostat, \ie we add two additional terms to force in equation of motion
+\begin{equation}
+f_i =  -\gamma v_i(t)+\sqrt{2\gamma \kT }\eta_i(t),
+\end{equation}
+where the first term correspond to constant friction with $\gamma$ being a friction coefficient, and the second one corresponds to random thermal force with $\eta_i$ being a normally distributed random number (see for details \cite{Grest1986}).
+
+Integrating the Langevin motion equation for all the particles we sample total energy of the system and pressure \cite{essmann1995}.
+
+\subsubsection{Monte Carlo sampling}
+
+General scheme of the Monte Carlo in the \emph{open system} system box with the gel and the monovalent co- and counter-ions ions, 
 $\cl$ and $\na$ is allowed to exchange particles with infinite reservoir with constant chemical potential.

### 2022-09-08 gibbs.tex
started MC sampling in open system.

@@
 
-\subsubsection{Monte Carlo sampling}
-
-General scheme of the Monte Carlo in the \emph{open system} system box with the gel and the monovalent co- and counter-ions ions, 
+\subsubsection{Monte Carlo sampling in open system}
+
+Monte Carlo scheme for sampling the exchange of ions in \emph{open system} is based on the formula for free energy of grand canonical ensemble.
+
+\begin{equation}
+    \Omega=E-TS+\sum_i\mu_i N_i\label{eq:Omega-GC}
+\end{equation}
+where $E$ is internal energy, $T$~--- temperature, $S$~--- entropy, $N_i$ is the number of ions of type $i\in\{\na,\ \cl\}$.
+
+%Our model system represents a finite volume $V$ which exchanges particles with the bath of infinite volume.
+%The infinity of the volume means, that the particle exchange between the system and the bath does not influence on the chemical potentials in the bath.
+%Such ensemble is called grand canonical ensemble; the free energy in this ensemble, the Landau potential, is
+The entropy $S$ is given by the Boltzmann formula~\cite{Nagle2004}:
+\begin{equation}
+    S=\kB\sum_i\ln\frac{V^{N_i}}{N_i!}\label{eq:entropy}
+\end{equation}
+%\todo{for partiles without interactions}
+It accounts for two contributions:
+\begin{enumerate}
+    \item the combinatorial entropy $S_{c}=-\sum_i\kB\ln N_i!$ which reflects the freedom of choice among $N$ particles
+    \item the mixing entropy $S_{m}=\kB \sum_i N_i\ln V$ which reflects the freedom to place the chosen particle randomly within the simulation box. 
+\end{enumerate}
+$V$ is the unitless volume, \ie the volume measured in units of $\sigma^3$. 
+Thus \refeq{eq:Omega-GC} turns to 
+%\todo{this is not reason, moreover A.10 is already wrong as for units}
+\begin{equation}
+    \Omega=E-\kT\ln\prod_i\frac{V^N_i}{N_i!}+\sum_i\mu_i N_i
+\label{eq: Omega_GC}
+\end{equation}
+The change of free energy associated with an exchange of ion pair is
+\begin{equation}
+    \Delta\Omega=\kT\ln\prod_i\left(V^{\xi}\frac{N_i!}{\left(N_i+\xi\right)!}\right)+\xi\mu_i+\Delta E
+\label{eq: DeltaG GC}
+\end{equation}
+where $\xi=+1$ stands for insertion of an ion pair and $\xi=-1$ for deletion.
+In general $\xi$ can be any number, but in case when  $\xi = \pm 1$ the previous equation gets simplified 
+\begin{equation}
+    \Delta\Omega=\kT\ln V^{2\xi} \prod_i \left(N_i+\theta(\xi)\right)^{-\xi}+\xi\mu_i+\Delta E
+\label{eq: DeltaG GC_simpl}
+\end{equation}
+where $\theta$ is the Heaviside function, $\theta(\xi) = 1, \mathtt{if}\  \xi>0$ , $\theta(\xi) = 0, \mathtt{if}\  \xi<0$
+
+The procedure of the Monte Carlo Sampling is the following \cite{Frenlkel2002_book}
+\begin{enumerate}
+	\item we propose the new configuration of the system by insertion (or deletion) of an ion pair, $\xi=\pm1$
+	\item we accept the new configuration if
+	\begin{equation}
+        \mathcal{R}^{\xi}<e^{\Delta\Omega/\kT}=V^{2\xi} \prod_i \left(N_i+\theta(\xi)\right)^{-\xi}e^{\left(\Delta E+\xi\mu\right)/\kT}\label{eq: GC acceptance}
+	\end{equation}
+\end{enumerate}
+where $\mathcal{R}$ is uniformly distributed random number in range between $0$ and $1$.
+
+\subsection{Monte Carlo sampling in closed system}
+In the same way we derive the acceptance criterion for sampling the closed system (Gibbs ensemble)
+
+The free energy of the Gibbs ensemble is a sum of free energies of the gel and the external volume.
+
+\begin{equation}
+    \Omega=E\gel-TS\gel + E\out-TS\out \label{eq:Omega-GC}
+\end{equation}
+
+The entropy $S$ is given by the Boltzmann formula~\cite{Nagle2004}:
+\begin{equation}
+    S=\kB\sum_i\ln\frac{V\gel^{N\gel_i}}{N_i!}\label{eq:entropy}
+\end{equation}
+%\todo{for partiles without interactions}
+It accounts for two contributions:
+\begin{enumerate}
+    \item the combinatorial entropy $S_{c}=-\sum_i\kB\ln N_i!$ which reflects the freedom of choice among $N$ particles
+    \item the mixing entropy $S_{m}=\kB \sum_i N_i\ln V$ which reflects the freedom to place the chosen particle randomly within the simulation box. 
+\end{enumerate}
+$V$ is the unitless volume, \ie the volume measured in units of $\sigma^3$. 
+Thus \refeq{eq:Omega-GC} turns to 
+%\todo{this is not reason, moreover A.10 is already wrong as for units}
+\begin{equation}
+    \Omega=E-\kT\ln\prod_i\frac{V^N_i}{N_i!}+\sum_i\mu_i N_i
+\label{eq: Omega_GC}
+\end{equation}
+The change of free energy associated with an exchange of ion pair is
+\begin{equation}
+    \Delta\Omega=\kT\ln\prod_i\left(V^{\xi}\frac{N_i!}{\left(N_i+\xi\right)!}\right)+\xi\mu_i+\Delta E
+\label{eq: DeltaG GC}
+\end{equation}
+where $\xi=+1$ stands for insertion of an ion pair and $\xi=-1$ for deletion.
+In general $\xi$ can be any number, but in case when  $\xi = \pm 1$ the previous equation gets simplified 
+\begin{equation}
+    \Delta\Omega=\kT\ln V^{2\xi} \prod_i \left(N_i+\theta(\xi)\right)^{-\xi}+\xi\mu_i+\Delta E
+\label{eq: DeltaG GC_simpl}
+\end{equation}
+where $\theta$ is the Heaviside function, $\theta(\xi) = 1, \mathtt{if}\  \xi>0$ , $\theta(\xi) = 0, \mathtt{if}\  \xi<0$
+
+The procedure of the Monte Carlo Sampling is the following \cite{Frenlkel2002_book}
+\begin{enumerate}
+	\item we propose the new configuration of the system by insertion (or deletion) of an ion pair, $\xi=\pm1$
+	\item we accept the new configuration if
+	\begin{equation}
+        \mathcal{R}^{\xi}<e^{\Delta\Omega/\kT}=V^{2\xi} \prod_i \left(N_i+\theta(\xi)\right)^{-\xi}e^{\left(\Delta E+\xi\mu\right)/\kT}\label{eq: GC acceptance}
+	\end{equation}
+\end{enumerate}
+where $\mathcal{R}$ is uniformly distributed random number in range between $0$ and $1$.
+
+We model the ionization equilibrium by means of sampling the reaction ensemble~\cite{Smith1994, Turner2008a}.
+In the reaction ensemble we perform chemical reactions as simultaneous insertion, deletion or identity change of particles according to the reaction equation.
+For example we assume the ionization of an acidic unit which proceeds according to the reaction equation
+\begin{equation}
+    \mathrm{AH}\stackrel{K}{\leftrightarrows}\A+\h\label{eq: acid reaction}
+\end{equation}
+We perform the forward direction of this reaction
+by inserting a $\h$ particle and replacing $\AH$ by $\A$.
+We perform the reverse direction of this reaction
+by deleting a $\h$ particle and replacing $\A$ by $\AH$.
+
+In order to account for the particles creation and deletion
+we need to introduce standard states for individual reacting species.
+The creation of a particle then means that the particle is removed from the standard state
+and inserted into the studied system, and vice versa for deletion.
+Each species in its standard state has the \emph{standard} chemical potential, $\mu^\ominus_i$.
+The choice of standard state for each component is arbitrary
+and we usually define it as pure component at standard pressure $10^5$ Pa
+and concentration $1 \molperl$~\cite{IUPAC}.
+
+Thus we rewrite the formula for free energy \refeq{eq:Omega-GC}
+accounting for particles creation and deletion as
+\begin{equation}
+    \Omega=E-TS+\sum_i\left(\mu_i-\mu^\ominus_i\right) N_i\label{eq:Omega-RE}
+\end{equation}
+where the last term in \refeq{eq:Omega-RE} stands for the exchange of particles between the studied system and the standard states.
+
+Let's have the reaction extent $\xi = (N_i - N_{i,0})/\nu_i$
+where $N_i$, resp. $N_{i,0}$ is the actual, resp. initial number of the $i$-th particle species,
+$\nu_i$ is its stoichiometric coefficient.
+and $i$ runs over individual species involved
+in the chemical reaction \refeq{eq: acid reaction} $i \in (\h,\ \A,\ \AH)$. 
+The stoichiometric coefficients are positive for reaction products
+and negative for reactants: $\nu_\h=1$, $\nu_\A=1$, $\nu_\AH=-1$.
+Therefore we take $\xi = +1$ for the forward reaction direction
+and $\xi = -1$ for the reverse reaction direction.
+Then we can write the change of the free energy of the studied system during one reaction step as
+\begin{equation}
+\Delta\Omega_{\mathrm{re}}=\kT\ln\left(\prod_i V^{\nu_i\xi}\frac{N_i!}{\left(N_i+\nu_i\xi\right)!}\right)+
+\xi\left(\sum_i\nu_i\mu_i-\sum_i\nu_i\mu_i^\ominus\right)+\Delta E
+\label{eq: DeltaG RE one}
+\end{equation}
+%\begin{multline}
+%    \Delta\Omega_{\mathrm{re}}=\kT\ln\left(\prod_i V^{\nu_i\xi}\frac{N_i!}{\left(N_i+\nu_i\xi\right)!}\right)+\\
+%    \xi\left(\sum_i\nu_i\mu_i-\sum_i\nu_i\mu_i^\ominus\right)+\Delta E
+%\label{eq: DeltaG RE one}
+%\end{multline}
+
+We write $\sum_i\nu_i \mu_i = 0$
+for the chemical reaction in equilibrium.
+
+The term $\sum_i\nu_i\mu_i^\ominus$ is the standard Gibbs free energy change
+of the reaction \refeq{eq: acid reaction}.
+which defines the equilibrium reaction constant \cite{Atkins} as
+\begin{equation}
+    K = e^{-\sum_i\nu_i \mu_i^\ominus / \kT}
+\end{equation}
+
+Finally, the \refeq{eq: DeltaG RE one} translates to
+\begin{equation}
+    \Delta\Omega_{\mathrm{re}}=\kT\ln\left(K^\xi\prod_i V^{\nu_i\xi}\frac{N_i!}{\left(N_i+\nu_i\xi\right)!}\right)+\Delta E
+\label{eq: DeltaG RE two}
+\end{equation}
+
+\subsection{Ion pairs insertions\label{sec: ion insertions}}
+We treat the exchange of mobile ions with the reservoir as simultaneous insertion or deletion
+of ion pairs or sets in the simulation box.
+We insert/delete either $\na$ and $\cl$ ion pair or the two $\cl$ ions together with one $\ca$ ion.
+Thus we model the insertion as:
+\begin{eqnarray}
+    \na +  \cl &\leftrightarrows& \emptyset\label{eq:nacl} \\
+    \ca + 2\cl &\leftrightarrows& \emptyset \label{eq:cacl}
+\end{eqnarray}
+with the corresponding equilibrium reaction constants, reflecting the free energy change during the insertion
+\begin{eqnarray*}
+    K_\mathrm{NaCl}     = \exp\left(\left(\mu_\na+ \mu_\cl \right) /\kT\right), \\
+    K_{\mathrm{CaCl}_2} = \exp\left(\left(\mu_\ca+2\mu_\cl \right /\kT\right))
+\end{eqnarray*}
+%$K_\mathrm{NaCl}= \exp\left(\mu_\na+\mu_\cl \right)$, $K_{\mathrm{CaCl}_2} = \exp\left(\mu_\ca+2\mu_\cl \right)$
+
+the Monte Carlo in the \emph{open system} box with the gel and the monovalent co- and counter-ions ions, 
 $\cl$ and $\na$ is allowed to exchange particles with infinite reservoir with constant chemical potential.

### 2022-09-14 gibbs.tex
Update gibbs.tex

--- 2022-09-08 gibbs.tex
@@
 These three properties of the gels make it possible to use them for desalination and at the same time avoid the use of expensive membranes.
-In this article, we present our recent theoretical study of the use of polyelectrolyte hydrogel for water desalination. 
-We modeled the thermodynamic equilibrium between coexisting phases of the gel and supernate aqueous salt solution.
-We have shown that the salinity of the supernate phase decreases during compression of the gel due to the release of absorbed in gel solution of lower salinity. 
-Finally, we performed a set of simulations modeling the process of continuous decrease of solution salinity up to freshwater concentrations.
+
+In this article, we present our recent theoretical study of the usage of polyelectrolyte hydrogel for water desalination. 
+Using coarse-grained model and the Gibbs ensemble, we modeled the thermodynamic equilibrium between coexisting phases of the gel and corresponding supernate aqueous 
+salt solution.
+
+We performed a sequence of step-by-step hydrogel compressions in \emph{open} and \emph{closed} systems.
+The compression in \emph{open system} causes the decrease of salt ions inside the hydrogel,
+while the compression in \emph{clesed system} causes the decrease of the supernatant solution.
+We modeled this stepwise process of continuous decrease of seawater salinity up to freshwater concentrations.
+We estimated the energy costs of the entire process as 38.2 J per production of 1 liter of potable water, which is comparable with reverse osmosis.
 }
@@
 
-We propose a cascade desalination process to lower supernatant salinity.
-%it is worth to note that we are not limited with this process only.
-For this process the gel must be commpressed/decompressed in an \emph{open} and \emph{closed} system.
-By the \emph{open system} we mean that the gel is in thermodynamic equilibrium with huge, effectively \textbf{infinite}, reservoir of an aqueous solution. 
-The gel freely exchanges ions with the reservoir, while their concentration in reservoir (and chemical potential) remains constant.
-%, such that there are the same ion's chemical potential, the same temperature, and desired pressure difference between the gel and the reservoir.
-The number of  $\na$ and $\cl$ ions and gel volume $\Vgel$ are allowed to change.
-By the \emph{closed system} we mean that the gel is in equilibrium with a \textbf{finite} reservoir of an aqueous solution. 
-In this case the exchange of ions between the gel and the reservoir may affect their concentration in reservoir, whereas the  
-%again have the same ions chemical potential, the same temperature, and desired pressure difference between the gel and the reservoir. 
-%Although, the number of ions and volume of gel and reservoir may vary, 
-the total number of ions (in gel and in reservoir) is constant.
-
-Due to huge size of the reservoir, the compression of the gel in the \emph{open system} does not affect the reservoir salinity, $\cs =$ $\cna=$ $\ccl=$ $\text{Const}$ (\reffig{fig: open}), whereas the number of ions entrapped in the volume $\Vbox$ changes.
-On the contrary, the compression of the gel in the \emph{closed system} changes the salinity in the reservoir, but the total number of $\na$ and $\cl$ ions in the gel and in the reservoir, \ie in the volume $\Vbox$ (\reffig{fig: closed}), remains constant.
-
-%In both cases there are two coexisting systems with constant $\mu P T$ allowed to exchange particles and change volume, which is represented as Gibbs ensemble.
-
-Unfortunately, there is no universal computationally effective technique to sample pressure difference, volume, and number of particles at the same.
-To equilibrate and sample pressure difference and volume we use molecular dynamics (MD) simulation, while equlibration and sampling of ions distribution between the gel and a reservoir is done via Monte-Carlo (MC) simulation.
-In this sence employed techniques is called MCMD.
-
-To simulate processes in \emph{open system} and  \emph{closed system} two complementary models MC and MD were implemented.
-
-\subsubsection*{Molecular Dynamics model}
-
-Our MD model of the gel is a network of 16 linear polymer chains, each consisting of 30 monomer 
+Our model of the gel is a network of 16 linear polymer chains, each consisting of 30 monomer 
 units. 
@@
 The entire simulation box setup employs periodic boundaries.
-Coloumb interaction computed by P3M method.
-This model is used in MD part of \emph{open system} and \emph{closed system} simulation.
-
-For the MD part of \emph{closed system} simulation analougous simulation box is created without any polymer monomers to model the finite reservoir. 
-The amount of $\na$ ions is equal to $\cl$.
-
-By integration Langevin motion equation by Verlet algorithm for each particles we sample 
-total energy of the system and pressure. 
-Kinetic energy, bonded, non-bonded and Coloumb interaction contribute to the total energy of a system.
-Pressure in the system calculated as in ref [Essmann et al., 1995, doi:10.1063/1.470117]
-\todo{I do not know if it is needed, ML}
-
-When computing MD the gel and reservoir box are essentially NVT-ensembles.
-
-\subsubsection*{Monte Carlo model}
-
-In the \emph{open system} system box with the gel and the monovalent co- and counter-ions ions, 
-$\cl$ and $\na$ is allowed to exchange particles with infinite reservoir with constant chemical potential.
-
-\dots
-
-In the \emph{closed system} system two boxes one with the gel and the other with ions pairs only iare allowed to exchange particles.
 
@@
 \end{figure*}
-
-\subsection{}
 

### 2022-09-14 gibbs.tex
Update gibbs.tex

@@
 % Abstract (Do not insert blank lines, i.e. \\) 
-\abstract{Recently polyelectrolyte hydrogels have been proposed as draw agents for the forward osmosis desalination techniques. 
+\abstract{Recently, polyelectrolyte hydrogels have been proposed as draw agents for the forward osmosis desalination techniques. 
 Indeed, polyelectrolyte hydrogels have the ability to absorb a big amount of water across an osmosis membrane as a result of their swelling pressure. 
-On the other hand, the insoluble cross-linked network of the gel enables dewatering under the influence of a stimulus (thermal and/or mechanical).
-Moreover, from a thermodynamic perspective, the polyelectrolyte hydrogel is already an osmotic membrane rejecting ions between external and internal solutions.
-These three properties of the gels make it possible to use them for desalination and at the same time avoid the use of expensive membranes.
-
-In this article, we present our recent theoretical study of the usage of polyelectrolyte hydrogel for water desalination. 
-Using coarse-grained model and the Gibbs ensemble, we modeled the thermodynamic equilibrium between coexisting phases of the gel and corresponding supernate aqueous 
-salt solution.
-
+On the other hand, the insoluble cross-linked hydrogel network enables dewatering under the influence of external (thermal and/or mechanical) stimulus.
+Moreover, from a thermodynamic perspective, the polyelectrolyte hydrogel is already an osmotic membrane.
+These above mentioned hydrogel properties designates them as excellent candidates for desalination, and, at the same time, avoid the use of expensive membranes.
+In this article, we present our recent theoretical study of polyelectrolyte hydrogel usage for water desalination. 
+Employing coarse-grained model and the Gibbs ensemble, we modeled the thermodynamic equilibrium between coexisting gel phase and supernate aqueous salt solution phase.
 We performed a sequence of step-by-step hydrogel compressions in \emph{open} and \emph{closed} systems.
 The compression in \emph{open system} causes the decrease of salt ions inside the hydrogel,
-while the compression in \emph{clesed system} causes the decrease of the supernatant solution.
-We modeled this stepwise process of continuous decrease of seawater salinity up to freshwater concentrations.
+while the compression in \emph{clesed system} causes the decrease of the salt concentration in the supernatant solution.
+We modeled this stepwise process of continuous decrease of water salinity from seawater up to freshwater concentrations.
 We estimated the energy costs of the entire process as 38.2 J per production of 1 liter of potable water, which is comparable with reverse osmosis.

### 2022-09-14 MDPI/response_letter.tex
Update MDPI/response_letter.tex

@@
 \item \textit{The main findings of your results should be highlighted in abstract} 
+We have rewritten the abstract. The abstract now contains main findings of our paper.
 
@@
 \item \textit{Abstract needs to re-write as and please follow the IMRAD instruction.}
+We have rewritten the abstract. We believe that the abstract is much more attractive now.
 \item \textit{There is introduction in the abstract, however, it needs to write more about the aim of this work, method, result and conclusion.}
+We have rewritten the abstract according to your advice.
 \item \textit{Avoid to use word 'we' in the abstract as well as manuscript.}
@@
 \item \textit{line 247 in what table?}
+We meant Table 1. Corrected.
 \item \textit{Where is the method of this work?} 
@@
 \item \textit{The abstract needs to be revised and be more attractive. The research gap, novelty and main findings should be concisely mentioned in the abstract.}
+We have rewritten the abstract. We believe that the abstract is much more attractive now.
 \item \textit{In this current shape, the manuscript looks like a report. The authors have to revise the flow of the context to attract the readers.}

### 2022-09-14 gibbs.tex

@@
 The compression in \emph{open system} causes the decrease of salt ions inside the hydrogel,
-while the compression in \emph{clesed system} causes the decrease of the salt concentration in the supernatant solution.
+while the compression in \emph{closed system} causes the decrease of the salt concentration in the supernatant solution.
 We modeled this stepwise process of continuous decrease of water salinity from seawater up to freshwater concentrations.

### 2022-09-15 gibbs.tex

@@
 
-\subsection{Model}
+\subsection{Open and closed sytems}
 
-Our model of the gel is a network of 16 linear polymer chains, each consisting of 30 monomer 
-units. 
+We propose a cascade desalination process to lower supernatant salinity.
+%it is worth to note that we are not limited with this process only.
+For this process the gel must be compressed/decompressed in an \emph{open} and \emph{closed} system.
+By the \emph{open system} we mean that the gel is in thermodynamic equilibrium with huge, effectively \textbf{infinite}, reservoir of an aqueous solution. 
+%The gel freely exchanges ions with the reservoir, while their concentration in reservoir (and chemical potential) remains constant.
+%, such that there are the same ion's chemical potential, the same temperature, and desired pressure difference between the gel and the reservoir.
+The number of  $\na$ and $\cl$ ions and gel volume $\Vgel$ are allowed to change.
+By the \emph{closed system} we mean that the gel is in equilibrium with a \textbf{finite} reservoir of an aqueous solution. 
+In this case the exchange of ions between the gel and the reservoir may affect their concentration in reservoir.%, whereas the  
+%again have the same ions chemical potential, the same temperature, and desired pressure difference between the gel and the reservoir. 
+%Although, the number of ions and volume of gel and reservoir may vary, 
+%total number of $\na$ and $\cl$ ions in the gel and in the reservoir, \ie in the volume $\Vbox$ remains constant.
+
+Due to huge size of the reservoir, the compression of the gel in the \emph{open system} does not affect the reservoir salinity, $\cs =$ $\cna=$ $\ccl=$ $\text{Const}$ (\reffig{fig: open}), whereas the number of ions entrapped in the volume $\Vbox$ changes (\reffig{fig: closed}).
+On the contrary, the compression of the gel in the \emph{closed system} changes the salinity in the reservoir, but the total number of $\na$ and $\cl$ ions in the gel and in the reservoir, \ie in the volume $\Vbox$ (\reffig{fig: closed}), remains constant.
+
+%In both cases there are two coexisting systems with constant $\mu P T$ allowed to exchange particles and change volume, which is represented as Gibbs ensemble.
+
+%Unfortunately, there is no universal computationally effective technique to sample pressure difference, volume, and number of particles at the same. 
+The mechanical movement and the exchange of ions occur simulataneously in real systems, however, we simulate them alternating each other in stop-run mode in a random order. 
+To sample mechanical properties of the gel and reservoir we use MD simulation, whereas to sample the ions distribution between the gel and a reservoir we use MC simulation.
+The details of this hybryd computational technique can be found in our previous studies of polyelectrolytes in open system \cite{Rud2020, Rud2022, Landsgesel2020a}.
+
+%In this sense employed techniques is called MCMD.
+
+%To simulate processes in \emph{open system} and  \emph{closed system} two complementary models MC and MD were implemented.
+
+\subsection{Langevin Dynamics}
+
+We model the gel as a network of 16 linear polymer chains, each consisting of 30 monomer units. 
 These polymer chains are connected to a diamond-like network by 8 crosslinking units.
@@
 The total electric charge of all the particles in the box is zero, therefore the amount 
-of $\na$ ions is bigger than that of $\cl$ by the number of hydrogel units.
-The entire simulation box setup employs periodic boundaries.
+of $\na$ ions is bigger than that of $\cl$ by the number of hydrogel units, $\Ngel$.
+The solvent assumed to be water, which is modeled implicitly via setting up dielectric permittivity $\epsilon=80$.
+
+We use three types of interactions, \ie bonded interactions, short-range non-bonded interactions and electrostatic interactions.
+
+We use Finite extension nonlinear elastic (FENE) potential~\refeq{eq:fene} to account for the bonding interactions.
+\begin{equation}\label{eq:fene}
+    V_\mathrm{FENE}(r) = -\frac{1}{2} K \Delta r_\mathrm{max}^2\ln \left[ 1 - \left(\frac{r-r_0}{\Delta r_\mathrm{max}} \right)^2 \right ],
+\end{equation}
+where $K$ is the magnitude of symmetric interaction between two segments,
+$\Delta r_{\mathrm{max}}$ is the maximal stretching length of the bond and $r_0$ is the equilibrium bond length.
+In our simulations we set $K = 10 \kT/\sigma^{2}$, $\Delta r_{\mathrm{max}} = 2 \sigma$ and $r_0 = 1.0\sigma$~\cite{Jin2007}.
+
+The non-bonded interactions are modelled by the truncated Lennard-Jones interaction potential.
+This potential imposes strong repulsion between all particles at short distances:
+\begin{equation}
+    \begin{split}\label{eq:LJ}
+        V_\mathrm{LJ}(r) =
+        \begin{cases}
+            4 \varepsilon \left( \left(\cfrac{\sigma}{r}\right)^{12}
+            - \left(\cfrac{\sigma}{r}\right)^6\right)
+            & \mathrm{if~} r < r_\mathrm{cut}\\
+            0
+            & \mathrm{elsewhere}
+        \end{cases},
+    \end{split}
+\end{equation}
+where $r$ is the interparticle distance,
+$\sigma = 0.35 \mathrm{nm}$ is a chosen characteristic size of the particles,
+$\varepsilon$ is the depth of the potential well in $\kT$ units and $r_\mathrm{cut}$ is the cut-off distance beyond which the potential is set zero.
+
+We model the long range electrostatic interactions by the Coulomb potential:
+\begin{equation}
+    V_{\mathrm{EL}}=\lb\kT \cfrac{q_{1}q_{2}}{r},
+\end{equation}
+where $\lb$ is Bjerrum length; $\lb = 2\sigma = 0.7 \mathrm{nm}$ which corresponds to water the Bjerrum length in water at $T=300 \mathrm{K}$.
+
+We use Langevin thermostat, \ie we add two additional terms to force in equation of motion
+\begin{equation}
+f_i =  -\gamma v_i(t)+\sqrt{2\gamma \kT }\eta_i(t),
+\end{equation}
+where the first term correspond to constant friction with $\gamma$ being a friction coefficient, and the second one corresponds to random thermal force with $\eta_i$ being a normally distributed random number (see for details \cite{Grest1986}).
+
+Integrating the Langevin motion equation for all the particles we sample total energy of the system and pressure \cite{essmann1995}.
+
+\subsubsection{Monte Carlo sampling in open system}
+
+Monte Carlo scheme for sampling the exchange of ions in \emph{open system} is based on the formula for free energy of grand canonical ensemble.
+
+\begin{equation}
+    \Omega=E-TS+\sum_i\mu_i N_i\label{eq:Omega-GC}
+\end{equation}
+where $E$ is internal energy, $T$~--- temperature, $S$~--- entropy, $N_i$ is the number of ions of type $i\in\{\na,\ \cl\}$.
+
+%Our model system represents a finite volume $V$ which exchanges particles with the bath of infinite volume.
+%The infinity of the volume means, that the particle exchange between the system and the bath does not influence on the chemical potentials in the bath.
+%Such ensemble is called grand canonical ensemble; the free energy in this ensemble, the Landau potential, is
+The entropy $S$ is given by the Boltzmann formula~\cite{Nagle2004}:
+\begin{equation}
+    S=\kB\sum_i\ln\frac{V^{N_i}}{N_i!}\label{eq:entropy}
+\end{equation}
+%\todo{for partiles without interactions}
+It accounts for two contributions:
+\begin{enumerate}
+    \item the combinatorial entropy $S_{c}=-\sum_i\kB\ln N_i!$ which reflects the freedom of choice among $N$ particles
+    \item the mixing entropy $S_{m}=\kB \sum_i N_i\ln V$ which reflects the freedom to place the chosen particle randomly within the simulation box. 
+\end{enumerate}
+$V$ is the unitless volume, \ie the volume measured in units of $\sigma^3$. 
+Thus \refeq{eq:Omega-GC} turns to 
+%\todo{this is not reason, moreover A.10 is already wrong as for units}
+\begin{equation}
+    \Omega=E-\kT\ln\prod_i\frac{V^N_i}{N_i!}+\sum_i\mu_i N_i
+\label{eq: Omega_GC}
+\end{equation}
+The change of free energy associated with an exchange of ion pair is
+\begin{equation}
+    \Delta\Omega=\kT\ln\prod_i\left(V^{\xi}\frac{N_i!}{\left(N_i+\xi\right)!}\right)+\xi\mu_i+\Delta E
+\label{eq: DeltaG GC}
+\end{equation}
+where $\xi=+1$ stands for insertion of an ion pair and $\xi=-1$ for deletion.
+In general $\xi$ can be any number, but in case when  $\xi = \pm 1$ the previous equation gets simplified 
+\begin{equation}
+    \Delta\Omega=\kT\ln V^{2\xi} \prod_i \left(N_i+\theta(\xi)\right)^{-\xi}+\xi\mu_i+\Delta E
+\label{eq: DeltaG GC_simpl}
+\end{equation}
+where $\theta$ is the Heaviside function, $\theta(\xi) = 1, \mathtt{if}\  \xi>0$ , $\theta(\xi) = 0, \mathtt{if}\  \xi<0$
+
+The procedure of the Monte Carlo Sampling is the following \cite{Frenlkel2002_book}
+\begin{enumerate}
+	\item we propose the new configuration of the system by insertion (or deletion) of an ion pair, $\xi=\pm1$
+	\item we accept the new configuration if
+	\begin{equation}
+        \mathcal{R}^{\xi}<e^{\Delta\Omega/\kT}=V^{2\xi} \prod_i \left(N_i+\theta(\xi)\right)^{-\xi}e^{\left(\Delta E+\xi\mu\right)/\kT}\label{eq: GC acceptance}
+	\end{equation}
+\end{enumerate}
+where $\mathcal{R}$ is uniformly distributed random number in range between $0$ and $1$.
+
+\subsection{Monte Carlo sampling in closed system}
+In the same way we derive the acceptance criterion for sampling the closed system (Gibbs ensemble)
+
+The free energy of the Gibbs ensemble is a sum of free energies of the gel and the external volume.
+
+\begin{equation}
+    \Omega=E\gel-TS\gel + E\out-TS\out \label{eq:Omega-GC}
+\end{equation}
+
+The entropy $S$ is given by the Boltzmann formula~\cite{Nagle2004}:
+\begin{equation}
+    S=\kB\sum_i\ln\frac{V\gel^{N\gel_i}}{N_i!}\label{eq:entropy}
+\end{equation}
+%\todo{for partiles without interactions}
+It accounts for two contributions:
+\begin{enumerate}
+    \item the combinatorial entropy $S_{c}=-\sum_i\kB\ln N_i!$ which reflects the freedom of choice among $N$ particles
+    \item the mixing entropy $S_{m}=\kB \sum_i N_i\ln V$ which reflects the freedom to place the chosen particle randomly within the simulation box. 
+\end{enumerate}
+$V$ is the unitless volume, \ie the volume measured in units of $\sigma^3$. 
+Thus \refeq{eq:Omega-GC} turns to 
+%\todo{this is not reason, moreover A.10 is already wrong as for units}
+\begin{equation}
+    \Omega=E-\kT\ln\prod_i\frac{V^N_i}{N_i!}+\sum_i\mu_i N_i
+\label{eq: Omega_GC}
+\end{equation}
+The change of free energy associated with an exchange of ion pair is
+\begin{equation}
+    \Delta\Omega=\kT\ln\prod_i\left(V^{\xi}\frac{N_i!}{\left(N_i+\xi\right)!}\right)+\xi\mu_i+\Delta E
+\label{eq: DeltaG GC}
+\end{equation}
+where $\xi=+1$ stands for insertion of an ion pair and $\xi=-1$ for deletion.
+In general $\xi$ can be any number, but in case when  $\xi = \pm 1$ the previous equation gets simplified 
+\begin{equation}
+    \Delta\Omega=\kT\ln V^{2\xi} \prod_i \left(N_i+\theta(\xi)\right)^{-\xi}+\xi\mu_i+\Delta E
+\label{eq: DeltaG GC_simpl}
+\end{equation}
+where $\theta$ is the Heaviside function, $\theta(\xi) = 1, \mathtt{if}\  \xi>0$ , $\theta(\xi) = 0, \mathtt{if}\  \xi<0$
+
+The procedure of the Monte Carlo Sampling is the following \cite{Frenlkel2002_book}
+\begin{enumerate}
+	\item we propose the new configuration of the system by insertion (or deletion) of an ion pair, $\xi=\pm1$
+	\item we accept the new configuration if
+	\begin{equation}
+        \mathcal{R}^{\xi}<e^{\Delta\Omega/\kT}=V^{2\xi} \prod_i \left(N_i+\theta(\xi)\right)^{-\xi}e^{\left(\Delta E+\xi\mu\right)/\kT}\label{eq: GC acceptance}
+	\end{equation}
+\end{enumerate}
+where $\mathcal{R}$ is uniformly distributed random number in range between $0$ and $1$.
+
+We model the ionization equilibrium by means of sampling the reaction ensemble~\cite{Smith1994, Turner2008a}.
+In the reaction ensemble we perform chemical reactions as simultaneous insertion, deletion or identity change of particles according to the reaction equation.
+For example we assume the ionization of an acidic unit which proceeds according to the reaction equation
+\begin{equation}
+    \mathrm{AH}\stackrel{K}{\leftrightarrows}\A+\h\label{eq: acid reaction}
+\end{equation}
+We perform the forward direction of this reaction
+by inserting a $\h$ particle and replacing $\AH$ by $\A$.
+We perform the reverse direction of this reaction
+by deleting a $\h$ particle and replacing $\A$ by $\AH$.
+
+In order to account for the particles creation and deletion
+we need to introduce standard states for individual reacting species.
+The creation of a particle then means that the particle is removed from the standard state
+and inserted into the studied system, and vice versa for deletion.
+Each species in its standard state has the \emph{standard} chemical potential, $\mu^\ominus_i$.
+The choice of standard state for each component is arbitrary
+and we usually define it as pure component at standard pressure $10^5$ Pa
+and concentration $1 \molperl$~\cite{IUPAC}.
+
+Thus we rewrite the formula for free energy \refeq{eq:Omega-GC}
+accounting for particles creation and deletion as
+\begin{equation}
+    \Omega=E-TS+\sum_i\left(\mu_i-\mu^\ominus_i\right) N_i\label{eq:Omega-RE}
+\end{equation}
+where the last term in \refeq{eq:Omega-RE} stands for the exchange of particles between the studied system and the standard states.
+
+Let's have the reaction extent $\xi = (N_i - N_{i,0})/\nu_i$
+where $N_i$, resp. $N_{i,0}$ is the actual, resp. initial number of the $i$-th particle species,
+$\nu_i$ is its stoichiometric coefficient.
+and $i$ runs over individual species involved
+in the chemical reaction \refeq{eq: acid reaction} $i \in (\h,\ \A,\ \AH)$. 
+The stoichiometric coefficients are positive for reaction products
+and negative for reactants: $\nu_\h=1$, $\nu_\A=1$, $\nu_\AH=-1$.
+Therefore we take $\xi = +1$ for the forward reaction direction
+and $\xi = -1$ for the reverse reaction direction.
+Then we can write the change of the free energy of the studied system during one reaction step as
+\begin{equation}
+\Delta\Omega_{\mathrm{re}}=\kT\ln\left(\prod_i V^{\nu_i\xi}\frac{N_i!}{\left(N_i+\nu_i\xi\right)!}\right)+
+\xi\left(\sum_i\nu_i\mu_i-\sum_i\nu_i\mu_i^\ominus\right)+\Delta E
+\label{eq: DeltaG RE one}
+\end{equation}
+%\begin{multline}
+%    \Delta\Omega_{\mathrm{re}}=\kT\ln\left(\prod_i V^{\nu_i\xi}\frac{N_i!}{\left(N_i+\nu_i\xi\right)!}\right)+\\
+%    \xi\left(\sum_i\nu_i\mu_i-\sum_i\nu_i\mu_i^\ominus\right)+\Delta E
+%\label{eq: DeltaG RE one}
+%\end{multline}
+
+We write $\sum_i\nu_i \mu_i = 0$
+for the chemical reaction in equilibrium.
+
+The term $\sum_i\nu_i\mu_i^\ominus$ is the standard Gibbs free energy change
+of the reaction \refeq{eq: acid reaction}.
+which defines the equilibrium reaction constant \cite{Atkins} as
+\begin{equation}
+    K = e^{-\sum_i\nu_i \mu_i^\ominus / \kT}
+\end{equation}
+
+Finally, the \refeq{eq: DeltaG RE one} translates to
+\begin{equation}
+    \Delta\Omega_{\mathrm{re}}=\kT\ln\left(K^\xi\prod_i V^{\nu_i\xi}\frac{N_i!}{\left(N_i+\nu_i\xi\right)!}\right)+\Delta E
+\label{eq: DeltaG RE two}
+\end{equation}
+
+\subsection{Ion pairs insertions\label{sec: ion insertions}}
+We treat the exchange of mobile ions with the reservoir as simultaneous insertion or deletion
+of ion pairs or sets in the simulation box.
+We insert/delete either $\na$ and $\cl$ ion pair or the two $\cl$ ions together with one $\ca$ ion.
+Thus we model the insertion as:
+\begin{eqnarray}
+    \na +  \cl &\leftrightarrows& \emptyset\label{eq:nacl} \\
+    \ca + 2\cl &\leftrightarrows& \emptyset \label{eq:cacl}
+\end{eqnarray}
+with the corresponding equilibrium reaction constants, reflecting the free energy change during the insertion
+\begin{eqnarray*}
+    K_\mathrm{NaCl}     = \exp\left(\left(\mu_\na+ \mu_\cl \right) /\kT\right), \\
+    K_{\mathrm{CaCl}_2} = \exp\left(\left(\mu_\ca+2\mu_\cl \right /\kT\right))
+\end{eqnarray*}
+%$K_\mathrm{NaCl}= \exp\left(\mu_\na+\mu_\cl \right)$, $K_{\mathrm{CaCl}_2} = \exp\left(\mu_\ca+2\mu_\cl \right)$
+
+the Monte Carlo in the \emph{open system} box with the gel and the monovalent co- and counter-ions ions, 
+$\cl$ and $\na$ is allowed to exchange particles with infinite reservoir with constant chemical potential.
+
+\dots
+
+In the \emph{closed system} system two boxes one with the gel and the other with ions pairs only iare allowed to exchange particles.
 

### 2022-09-15 MDPI/response_letter.tex
Update MDPI/response_letter.tex

@@
 \item \textit{Please do not separate introduction in three sections combine with problem and technology you used and challenges and your solutions.}
+Corrected. We have rewritten and improved the Introduction.
 
@@
 \item \textit{The whole manuscript must be supported by enough recent references. Revise the whole context.}
+We added more recent references.
 \item \textit{The beginning of the introduction part must be revised to be more attractive.}
+Corrected. We haǘe rewritten and improved the Introduction section.
 \item \textit{The authors can follow the following references to generally highlight the global contamination and environmental pollution problems at the beginning of the introduction part  \href{https://doi.org/10.1016/j.jwpe.2022.102847}{https://doi.org/10.1016/j.jwpe.2022.102847} ; \href{https://doi.org/10.1016/j.ceramint.2022.05.151}{https://doi.org/10.1016/j.ceramint.2022.05.151} ;
@@
 Then, highlight the water desalination technologies and Gibbs ensemble (\href{https://doi.org/10.3390/nano10020293}{https://doi.org/10.3390/nano10020293}).}
+Corrected. We added the citations, which are relevant to the studied problems, in their appropriate places.
 \item \textit{Authors should indicate a clear gap in knowledge which this study seeks to bridge, and potentially contribute to knowledge. }
-
+The purpose of our paper is to show that desalination using polyelectrolyte hydrogels is a cheap and therefore competitive alternative to reverse osmosis.
+We highlighted this idea in the Introduction and Conclusion sections.
 \item \textit{L 125-126, meaningless sentence. Revise the whole context.}
@@
 \item \textit{All sections/subsections titles must be revised to be expressive.}
+Corrected. We have rewritten and improved not only the Introduction, but the sections Model and Methods, Results, Conclusions as well.
 \item \textit{Statistical physics considerations including setup and calculations should be added.}

### 2022-09-15 gibbs.tex
Update gibbs.tex

@@
 \section{Introduction\label{sec: intro}}
+
+Waste water treatment and technology is one of the greatest concerns of modern sustainable society. 
+The water has to be disposed of both biological \cite{guesmi2022} and chemical \cite{baaloudj2022_1,shahzad2022} pollutants.
+Most imporatntly, water treatment technologies have to be prepared for the still increasing need for production of potable water from the brine, \ie for desalination.
+
 \subsection{Water desalination technologies}
-
-\todo[inline]{
-The authors can follow the following references to generally highlight the global contamination and environmental pollution problems at the beginning of the introduction part
-https://doi.org/10.1016/j.jwpe.2022.102847 \cite{baaloudj2022_1}\\
-https://doi.org/10.1016/j.ceramint.2022.05.151 \cite{shahzad2022}\\
-https://doi.org/10.3390/catal12050500 \cite{baaloudj2022}\\
-https://doi.org/10.1007/s11356-022-21160-7 \cite{guesmi2022}\\
-https://doi.org/10.3390/ma15134547 \cite{kane2022}\\. 
-Then, highlight the water desalination technologies and Gibbs ensemble (https://doi.org/10.3390/nano10020293 \cite{erdos2020}).
-}
-
 Two basic approaches for separating water from salt are present in modern desalination technology \cite{Miller2003,Curto2021}.
@@
 %The target of our study is to model the thermodynamic equilibrium between the two boxes and to show how the compression of the gel affects the ion density in the outside solution.
+
+TODO Then, highlight the water desalination technologies and Gibbs ensemble (https://doi.org/10.3390/nano10020293 \cite{erdos2020}).
 

### 2022-09-15 gibbs.tex
Update gibbs.tex

@@
 
-Waste water treatment and technology is one of the greatest concerns of modern sustainable society. 
-The water has to be disposed of both biological \cite{guesmi2022} and chemical \cite{baaloudj2022_1,shahzad2022} pollutants.
-Most imporatntly, water treatment technologies have to be prepared for the still increasing need for production of potable water from the brine, \ie for desalination.
+Waste water treatment and technology is one of the greatest concerns of modern society. 
+The waste water has to be disposed of both biological \cite{guesmi2022} and chemical \cite{baaloudj2022_1,shahzad2022} pollutants.
+Most imporatntly, water treatment technologies are needed for the still increasing demand on production of potable water from the brine, \ie for desalination.
 
@@
 The first approach is distillation, which uses heat to cause a phase change of the water to vapor. The vapor phase is separated from the brine and condenses to liquid fresh water. 
-The released condensation energy is directed back to heating the feed solution.
+The released condensation energy is directed back to heat the feed solution..
 Distillation processes were the first desalination techniques conducted on a large commercial scale and still account for a large portion of the modern world’s desalination capacity.
 
-The second approach is to physically separate the brine components using an osmotic membrane transparent only for water molecules, which move in response to a water chemical potential difference.
-In the context of our study, we will mention the reverse osmosis process (RO)~--- the major process of all the modern desalination industry, and the newly emerging membrane
-technology~--- forward osmosis (FO) \cite{Akther2015}. 
+The second approach is to physically separate the brine components using an osmotic membrane transparent only for water molecules, which move in response to the difference in water chemical potential.
+In the context of our study, we will mention the reverse osmosis process (RO) as the major process of all the modern desalination industry, and the newly emerging membrane technology~--- forward osmosis (FO) \cite{Akther2015}.
 In RO, the difference in water chemical potential originates from a difference in pressures applied to the feed and to product solutions. 
@@
 Distillation is easy and cheap technology but it is characterized by relatively high energy costs due to the dissipation of thermal energy. 
-On the contrary, RO uses expensive osmotic membranes, which need to be replaced regularly because of scaling and fouling. 
+In turn, RO uses expensive osmotic membranes, which need to be replaced regularly because of scaling and fouling. 
 Moreover, RO requires very high operating pressures, ranging from 20 to 200 bar, to let the water pass through the membrane. 
-But in terms of energy losses, it works close to the thermodynamic limit.
+But, in terms of energy losses, it works close to the thermodynamic limit.
 Thus, theoretically, per one ion pair transferred from freshwater to salty water, it consumes only the energy equal to the difference between the chemical potentials of the transfered ions.

### 2022-09-15 gibbs.tex
Update gibbs.tex

@@
 When a dehydrated or deswollen hydrogel uptakes water, its polymer chains extend, creating a swelling pressure. 
-For example, as reported in \cite{Wack_2009} weakly crosslinked poly(acrylic acid) (PAA) copolymers with polymer volume fractions between 0.03 and 0.30 exhibit a swelling pressure ranging from 0.20--4.23 MPa.
+For example, as reported in \cite{Wack_2009}, weakly crosslinked poly(acrylic acid) (PAA) copolymers with polymer volume fractions between 0.03 and 0.30 exhibit a swelling pressure ranging from 0.20--4.23 MPa.
 Polyelectrolyte hydrogels, which are carrying ionic groups on the comonomer units (like PAA), are able to reject salt ions from the solution, they absorb a solution of lower salinity than that they are equilibrated with.
 
-An important, advantageous aspect of polymer hydrogels is that they can undergo reversible volume change, \ie solution --- gel phase transitions in response to environmental stimuli. 
-This aspect causes hydrogels to be labeled as ‘smart’ hydrogels. 
+An important, advantageous aspect of polymer hydrogels is that they can undergo reversible volume change, \ie solution --- gel phase transitions in response to external stimuli. 
+This aspect causes hydrogels to be labeled as ‘smart’ materials. 
 Many physical and chemical stimuli have been applied to induce various responses of such smart hydrogels, in particular, to change them from hydrophilic to hydrophobic, thereby releasing water. 
@@
 
-The smart properties of hydrogels were utilized for desalination in a recent study by Li \etal \cite{Li2011}, where hydrogels have been considered as draw agents for FO. 
-In this study authors have shown, that hydrogels, 
-are able to absorb water across the FO membrane due to their swelling and osmotic pressure and
+Recently, Li \etal \cite{Li2011} took advantage of the smart hydrogel properties for desalination purposes. In this work, the authors used hydrogels as draw agents for FO. 
+They have demonstrated that the hydrogels are able to absorb water across the FO membrane due to their swelling and osmotic pressure and
 allow dewatering under the influence of stimuli (thermal and/or mechanical), due to their insoluble cross-linked polymer network.
-For instance, Li \etal proposed the use of hydrogel made of thermoresponsive polyelectrolyte~--- copolymer of poly-N-isopropyl acrylamide (p-NIPAAm) and polyacrylic acid (p-AA).
-Depending on the temperature the network of the gel appears to be either hydrophilic or hydrophobic. 
-In the hydrophilic state, the gel is used as a draw solute accumulating water inside, then in the hydrophobic state, the water releases out.
-
-Moreover, from a thermodynamics perspective, the polyelectrolyte hydrogel itself is an osmotic membrane generating Donnan potential, which rejects ions between outer and inner solutions \cite{Wang_2014}.
+They have proposed the use of hydrogel based on thermoresponsive polyelectrolyte~--- copolymer of poly-N-isopropyl acrylamide (p-NIPAAm) and polyacrylic acid (p-AA).
+This gel network is either hydrophilic or hydrophobic, depending on the temperature.
+Such gel accumulates water inside the network in its hydrophilic state, but it releases the water out in its hydrophobic state.
+
+From a thermodynamics perspective, the polyelectrolyte hydrogel itself is an osmotic membrane generating Donnan potential, which rejects ions between outer and inner solutions \cite{Wang_2014}. 
 Such a view on hydrogels was employed in a series of works by the group of prof. Wilhelm (see for example \cite{Arens_2017,Fengler_2020}). 
 The authors of these works proposed to get rid of the osmotic membrane and simply use only micro filtration to compress the hydrogel squeezing out the accumulated inside the gel solution. 
-In their method first, the deswollen hydrogel was equilibrated with saline water feed. 
-During equilibration, the gel was swelling absorbing water. 
+In their method, the deswollen hydrogel was first equilibrated with saline water feed. 
+During the equilibration, the gel was swelling, absorbing the water. 
 Then it was taken out from the feed solution and mechanically squeezed by means of a microfiltration membrane. 
-The squeezed out brine was obtained to have lower salinity than the feed water.
-
-A similar approach was used by Ali \etal \cite{Ali2015}. 
-In their study the thermosensitive gel was used (based on copolymers p-NIPAAm and p-AA), so instead of physical compression, the dewatering was done by an external heating stimulus (sunlight). 
-At night the gel was equilibrating with feed water and at daytime, under sunlight, the gel was shrinking and releasing the collected inside solution.
+They have found that the brine, which was squeezed out, had lower salinity than the feed water.
+
+Similar approach was used by Ali \etal \cite{Ali2015}. 
+Here the authors used the thermosensitive gel (based on copolymers p-NIPAAm and p-AA), and instead of physical compression, the dewatering was done by an external heating stimulus (sunlight). 
+The gel was equilibrated with feed water during the night, and, at daytime, under sunlight, the gel was shrinking and releasing the solution.
 

### 2022-09-15 gibbs.tex
Update gibbs.tex

@@
 \subsection{Physics behind the desalination process}
-%The maximum entropy principle requires the density of charges to be more-less the same throughout the system medium. 
-Since the polyelectrolyte gel has its own charges and its own neutralizing counterions, the density of mobile ions (which are able to freely enter and leave the gel) in gel appears to be smaller than their density outside the gel.
-Therefore the internal solution of the gel has a lower density of mobile ions than that in the solution outside. 
+Since the polyelectrolyte gel has its own charges and its own neutralizing counterions, the density of mobile ions (which are able to freely enter and leave the gel) inside the gel network appears to be smaller than their density outside the gel.
+Therefore the internal solution in the gel has lower density of mobile ions than the solution outside. 
 In that sense, the gel acts as an osmotic membrane separating solutions \cite{Rud2020}. 
-The driving force of the separation is the Donnan potential originated from the charges of the hydrogel network. 
-The density of mobile ions difference between ions concentrations in the internal and external solutions
+The driving force of the separation is the Donnan potential, which originates from the charges in the hydrogel network. 
+The difference between the densities (concentrations) of the mobile ions in the internal and external solutions
 is defined by Donnan law \cite{Rud2018}
@@
 \end{equation}
-where $\ccl\gel$ and $\cna\gel$ are the internal concentration of monovalent anions and cations, $\cs$ is the salinity of external solution,  $\Vgel$ is the gel molar volume (inverse density of gel segments) and $\alpha$ is ionization degree (in the case of our study $\alpha=1$).
-The $\pm$ sign in the formula accounts for the change between the cases of gel made of polyanion or polycation.
+where $\ccl\gel$ and $\cna\gel$ are the concentrations of monovalent anions and cations in the internal solution,
+$\cs$ is the salinity of external solution,  $\Vgel$ is the gel molar volume (inverse density of gel segments)
+and $\alpha$ is ionization degree (in the case of our study $\alpha=1$). 
+The $\pm$ sign in the formula accounts for the sign change for the cases of polyanion or polycation gels.
 

### 2022-09-15 gibbs.tex
Update gibbs.tex

@@
 
-Recently, Li \etal \cite{Li2011} took advantage of the smart hydrogel properties for desalination purposes. In this work, the authors used hydrogels as draw agents for FO. 
+Li \etal \cite{Li2011} took advantage of the smart hydrogel properties for desalination purposes. In this work, the authors used hydrogels as draw agents for FO. 
 They have demonstrated that the hydrogels are able to absorb water across the FO membrane due to their swelling and osmotic pressure and
@@
 
-The lower salinity solution can be extracted from the gel by means of compression and/or other stimulus providing that the charge of the gel remains constant.
-In the case of gel made of weak (pH-sensitive) polyelectrolyte, the compression discharges the gel, therefore the neutralizing counterions leave out the gel diminishing the desalination effect \cite{Rud2018}.
-%Nevertheless, in\cite{Rud2018} we discussed how the release of counterions may be employed for desalination as well.
+As shown in \cite{Li_2011,Ali_2015,Arens_2017,Fengler_2020}, the solution of lower salinity can be extracted from the gel by means of compression and/or other stimulus, provided that the charge in the gel remains constant.
+In the case of weak polyelectrolyte (pH-sensitive) gel, the compression discharges the gel and therefore the neutralizing counterions leave out the gel, diminishing the desalination effect \cite{Rud2018}.
 
@@
 Indeed, the use of high hydraulic pressure diminishes all the advantages of this method over RO, and the reversibility of hydrogel swelling after strong compression remains questionable. 
-Nevertheless, in the current study, we model the compression of the gel limiting ourselves to low compression rates, less than 5 bar, and studied how the compression of the gel affects the surrounding salinity.
-We modelled also the desalination process, as a cascade of following one by each other gel swellings and compressions driving the salinity of supernate down to drinkable water. 
-%In the current study we would like to concentrate on the use of gel made of strong polyelectrolyte for water desalination. 
-%Namely, to investigate how the compression of the gel affects the salinity of the surrounding the gel solution and to propose the way of water desalination employing the hydrogel swelling/deswelling set of processes.
-
-%The target of our study is to model the thermodynamic equilibrium between the two boxes and to show how the compression of the gel affects the ion density in the outside solution.
-
-TODO Then, highlight the water desalination technologies and Gibbs ensemble (https://doi.org/10.3390/nano10020293 \cite{erdos2020}).
+Nevertheless, in this study, we model the compression of the gel limiting ourselves to low compression rates, less than 5 bar, and studied how the compression of the gel affects the surrounding salinity.
+We modelled the desalination process, as a cascade of step-by-step gel swellings and compressions, driving the salinity of the supernate down to potable water.
+
+% water desalination technologies and Gibbs ensemble (https://doi.org/10.3390/nano10020293 \cite{erdos2020}).
 

### 2022-09-15 gibbs.tex
methods section is done (almost)

--- 2022-09-15 gibbs.tex
@@
 \newcommand{\Vgel}{V_\mathrm{gel}}
+\newcommand{\vgel}{v_\mathrm{gel}}
+\newcommand{\Egel}{E_\mathrm{gel}}
+\newcommand{\Sgel}{S_\mathrm{gel}}
 %\newcommand{\Vgel}{V}
@@
 \newcommand{\Vout}{V_\mathrm{out}}
+\newcommand{\Eout}{E_\mathrm{out}}
+\newcommand{\Sout}{S_\mathrm{out}}
 %\newcommand{\Vbox}{V_\mathrm{box}}
@@
 % Abstract (Do not insert blank lines, i.e. \\) 
-\abstract{Recently, polyelectrolyte hydrogels have been proposed as draw agents for the forward osmosis desalination techniques. 
-Indeed, polyelectrolyte hydrogels have the ability to absorb a big amount of water across an osmosis membrane as a result of their swelling pressure. 
-On the other hand, the insoluble cross-linked hydrogel network enables dewatering under the influence of external (thermal and/or mechanical) stimulus.
+\abstract{
+Recently, polyelectrolyte hydrogels have been proposed as draw agents for forward osmosis (FO) desalination techniques. 
+Indeed, polyelectrolyte hydrogels can absorb a big amount of water across an osmosis membrane as a result of their swelling pressure. 
+On the other hand, the insoluble cross-linked hydrogel network enables dewatering under the influence of external (thermal and/or mechanical) stimuli.
 Moreover, from a thermodynamic perspective, the polyelectrolyte hydrogel is already an osmotic membrane.
-These above mentioned hydrogel properties designates them as excellent candidates for desalination, and, at the same time, avoid the use of expensive membranes.
+These above-mentioned hydrogel properties designate them as excellent candidates for desalination, and, at the same time, avoid the use of expensive membranes.
 In this article, we present our recent theoretical study of polyelectrolyte hydrogel usage for water desalination. 
-Employing coarse-grained model and the Gibbs ensemble, we modeled the thermodynamic equilibrium between coexisting gel phase and supernate aqueous salt solution phase.
+Employing a coarse-grained model and the Gibbs ensemble, we modeled the thermodynamic equilibrium between coexisting gel phase and the supernate aqueous salt solution phase.
 We performed a sequence of step-by-step hydrogel compressions in \emph{open} and \emph{closed} systems.
@@
 We modeled this stepwise process of continuous decrease of water salinity from seawater up to freshwater concentrations.
-We estimated the energy costs of the entire process as 38.2 J per production of 1 liter of potable water, which is comparable with reverse osmosis.
+We estimated the energy costs of the process to be comparable with reverse osmosis.
+%as 38.2 J per production of 1 liter of potable water, which is comparable with reverse osmosis.
 }
@@
 \section{Introduction\label{sec: intro}}
-
-Waste water treatment and technology is one of the greatest concerns of modern society. 
-The waste water has to be disposed of both biological \cite{guesmi2022} and chemical \cite{baaloudj2022_1,shahzad2022} pollutants.
-Most imporatntly, water treatment technologies are needed for the still increasing demand on production of potable water from the brine, \ie for desalination.
-
 \subsection{Water desalination technologies}
+
+\todo[inline]{
+The authors can follow the following references to generally highlight the global contamination and environmental pollution problems at the beginning of the introduction part
+https://doi.org/10.1016/j.jwpe.2022.102847 \cite{baaloudj2022_1}\\
+https://doi.org/10.1016/j.ceramint.2022.05.151 \cite{shahzad2022}\\
+https://doi.org/10.3390/catal12050500 \cite{baaloudj2022}\\
+https://doi.org/10.1007/s11356-022-21160-7 \cite{guesmi2022}\\
+https://doi.org/10.3390/ma15134547 \cite{kane2022}\\. 
+Then, highlight the water desalination technologies and Gibbs ensemble (https://doi.org/10.3390/nano10020293 \cite{erdos2020}).
+}
+
 Two basic approaches for separating water from salt are present in modern desalination technology \cite{Miller2003,Curto2021}.
@@
 The first approach is distillation, which uses heat to cause a phase change of the water to vapor. The vapor phase is separated from the brine and condenses to liquid fresh water.
-The released condensation energy is directed back to heat the feed solution..
+The released condensation energy is directed back to heating the feed solution.
 Distillation processes were the first desalination techniques conducted on a large commercial scale and still account for a large portion of the modern world’s desalination capacity.
 
-The second approach is to physically separate the brine components using an osmotic membrane transparent only for water molecules, which move in response to the difference in water chemical potential.
-In the context of our study, we will mention the reverse osmosis process (RO) as the major process of all the modern desalination industry, and the newly emerging membrane technology~--- forward osmosis (FO) \cite{Akther2015}.
+The second approach is to physically separate the brine components using an osmotic membrane transparent only for water molecules, which move in response to a water chemical potential difference.
+In the context of our study, we will mention the reverse osmosis process (RO)~--- the major process of all the modern desalination industry, and the newly emerging membrane
+technology~--- forward osmosis (FO) \cite{Akther2015}.
 In RO, the difference in water chemical potential originates from a difference in pressures applied to the feed and to product solutions.
@@
 Distillation is easy and cheap technology but it is characterized by relatively high energy costs due to the dissipation of thermal energy.
-In turn, RO uses expensive osmotic membranes, which need to be replaced regularly because of scaling and fouling. 
+On the contrary, RO uses expensive osmotic membranes, which need to be replaced regularly because of scaling and fouling.
 Moreover, RO requires very high operating pressures, ranging from 20 to 200 bar, to let the water pass through the membrane.
-But, in terms of energy losses, it works close to the thermodynamic limit.
+But in terms of energy losses, it works close to the thermodynamic limit.
 Thus, theoretically, per one ion pair transferred from freshwater to salty water, it consumes only the energy equal to the difference between the chemical potentials of the transfered ions.
@@
 When a dehydrated or deswollen hydrogel uptakes water, its polymer chains extend, creating a swelling pressure.
-For example, as reported in \cite{Wack_2009}, weakly crosslinked poly(acrylic acid) (PAA) copolymers with polymer volume fractions between 0.03 and 0.30 exhibit a swelling pressure ranging from 0.20--4.23 MPa.
+For example, as reported in \cite{Wack_2009} weakly crosslinked poly(acrylic acid) (PAA) copolymers with polymer volume fractions between 0.03 and 0.30 exhibit a swelling pressure ranging from 0.20--4.23 MPa.
 Polyelectrolyte hydrogels, which are carrying ionic groups on the comonomer units (like PAA), are able to reject salt ions from the solution, they absorb a solution of lower salinity than that they are equilibrated with.
 
-An important, advantageous aspect of polymer hydrogels is that they can undergo reversible volume change, \ie solution --- gel phase transitions in response to external stimuli. 
-This aspect causes hydrogels to be labeled as ‘smart’ materials. 
+An important, advantageous aspect of polymer hydrogels is that they can undergo reversible volume change, \ie solution --- gel phase transitions in response to environmental stimuli.
+This aspect causes hydrogels to be labeled as ‘smart’ hydrogels.
 Many physical and chemical stimuli have been applied to induce various responses of such smart hydrogels, in particular, to change them from hydrophilic to hydrophobic, thereby releasing water.
@@
 
-Recently, Li \etal \cite{Li2011} took advantage of the smart hydrogel properties for desalination purposes. In this work, the authors used hydrogels as draw agents for FO. 
-They have demonstrated that the hydrogels are able to absorb water across the FO membrane due to their swelling and osmotic pressure and
+The smart properties of hydrogels were utilized for desalination in a recent study by Li \etal \cite{Li2011}, where hydrogels have been considered as draw agents for FO.
+In this study authors have shown, that hydrogels,
+are able to absorb water across the FO membrane due to their swelling and osmotic pressure and
 allow dewatering under the influence of stimuli (thermal and/or mechanical), due to their insoluble cross-linked polymer network.
-They have proposed the use of hydrogel based on thermoresponsive polyelectrolyte~--- copolymer of poly-N-isopropyl acrylamide (p-NIPAAm) and polyacrylic acid (p-AA).
-This gel network is either hydrophilic or hydrophobic, depending on the temperature.
-Such gel accumulates water inside the network in its hydrophilic state, but it releases the water out in its hydrophobic state.
-
-From a thermodynamics perspective, the polyelectrolyte hydrogel itself is an osmotic membrane generating Donnan potential, which rejects ions between outer and inner solutions \cite{Wang_2014}. 
+For instance, Li \etal proposed the use of hydrogel made of thermoresponsive polyelectrolyte~--- copolymer of poly-N-isopropyl acrylamide (p-NIPAAm) and polyacrylic acid (p-AA).
+Depending on the temperature the network of the gel appears to be either hydrophilic or hydrophobic.
+In the hydrophilic state, the gel is used as a draw solute accumulating water inside, then in the hydrophobic state, the water releases out.
+
+Moreover, from a thermodynamics perspective, the polyelectrolyte hydrogel itself is an osmotic membrane generating Donnan potential, which rejects ions between outer and inner solutions \cite{Wang_2014}.
 Such a view on hydrogels was employed in a series of works by the group of prof. Wilhelm (see for example \cite{Arens_2017,Fengler_2020}).
 The authors of these works proposed to get rid of the osmotic membrane and simply use only micro filtration to compress the hydrogel squeezing out the accumulated inside the gel solution.
-In their method, the deswollen hydrogel was first equilibrated with saline water feed. 
-During the equilibration, the gel was swelling, absorbing the water. 
+In their method first, the deswollen hydrogel was equilibrated with saline water feed.
+During equilibration, the gel was swelling absorbing water.
 Then it was taken out from the feed solution and mechanically squeezed by means of a microfiltration membrane.
-They have found that the brine, which was squeezed out, had lower salinity than the feed water.
-
-Similar approach was used by Ali \etal \cite{Ali2015}. 
-Here the authors used the thermosensitive gel (based on copolymers p-NIPAAm and p-AA), and instead of physical compression, the dewatering was done by an external heating stimulus (sunlight). 
-The gel was equilibrated with feed water during the night, and, at daytime, under sunlight, the gel was shrinking and releasing the solution.
+The squeezed out brine was obtained to have lower salinity than the feed water.
+
+A similar approach was used by Ali \etal \cite{Ali2015}.
+In their study the thermosensitive gel was used (based on copolymers p-NIPAAm and p-AA), so instead of physical compression, the dewatering was done by an external heating stimulus (sunlight).
+At night the gel was equilibrating with feed water and at daytime, under sunlight, the gel was shrinking and releasing the collected inside solution.
 
@@
 
-TODO Then, highlight the water desalination technologies and Gibbs ensemble (https://doi.org/10.3390/nano10020293 \cite{erdos2020}).
-
 \section{Model and methods\label{sec: theory}}
 
-\begin{figure*}[h]
-\centering 
-\includegraphics[width=0.7\textwidth]{{figures/simgibbs}.pdf}\caption{Diamond-like network in the simulation box. Color code represents
-the individual ion types (red: $\na$, blue: $\cl$, yellow: $\ca$)
-and the hydrogel (gray: neutral segment ($\AH$), cyan: charged segment
-($\A$)). \label{fig:diamond}.}
-\end{figure*}
-
 \subsection{Open and closed sytems}
-
-We propose a cascade desalination process to lower supernatant salinity.
-%it is worth to note that we are not limited with this process only.
-For this process the gel must be compressed/decompressed in an \emph{open} and \emph{closed} system.
-By the \emph{open system} we mean that the gel is in thermodynamic equilibrium with huge, effectively \textbf{infinite}, reservoir of an aqueous solution. 
-%The gel freely exchanges ions with the reservoir, while their concentration in reservoir (and chemical potential) remains constant.
-%, such that there are the same ion's chemical potential, the same temperature, and desired pressure difference between the gel and the reservoir.
-The number of  $\na$ and $\cl$ ions and gel volume $\Vgel$ are allowed to change.
-By the \emph{closed system} we mean that the gel is in equilibrium with a \textbf{finite} reservoir of an aqueous solution. 
-In this case the exchange of ions between the gel and the reservoir may affect their concentration in reservoir.%, whereas the  
-%again have the same ions chemical potential, the same temperature, and desired pressure difference between the gel and the reservoir. 
-%Although, the number of ions and volume of gel and reservoir may vary, 
-%total number of $\na$ and $\cl$ ions in the gel and in the reservoir, \ie in the volume $\Vbox$ remains constant.
-
-Due to huge size of the reservoir, the compression of the gel in the \emph{open system} does not affect the reservoir salinity, $\cs =$ $\cna=$ $\ccl=$ $\text{Const}$ (\reffig{fig: open}), whereas the number of ions entrapped in the volume $\Vbox$ changes (\reffig{fig: closed}).
-On the contrary, the compression of the gel in the \emph{closed system} changes the salinity in the reservoir, but the total number of $\na$ and $\cl$ ions in the gel and in the reservoir, \ie in the volume $\Vbox$ (\reffig{fig: closed}), remains constant.
-
-%In both cases there are two coexisting systems with constant $\mu P T$ allowed to exchange particles and change volume, which is represented as Gibbs ensemble.
-
-%Unfortunately, there is no universal computationally effective technique to sample pressure difference, volume, and number of particles at the same. 
-The mechanical movement and the exchange of ions occur simulataneously in real systems, however, we simulate them alternating each other in stop-run mode in a random order. 
-To sample mechanical properties of the gel and reservoir we use MD simulation, whereas to sample the ions distribution between the gel and a reservoir we use MC simulation.
-The details of this hybryd computational technique can be found in our previous studies of polyelectrolytes in open system \cite{Rud2020, Rud2022, Landsgesel2020a}.
-
-%In this sense employed techniques is called MCMD.
-
-%To simulate processes in \emph{open system} and  \emph{closed system} two complementary models MC and MD were implemented.
-
-\subsection{Langevin Dynamics}
-
-We model the gel as a network of 16 linear polymer chains, each consisting of 30 monomer units. 
-These polymer chains are connected to a diamond-like network by 8 crosslinking units.
-This means, there are $\Ngel=16\cdot30 + 8=488$ gel monomers in the simulation box 
-(see \reffig{fig:diamond}).
-Each monomer unit of the network carries a negative elementary electric charge, thus 
-simulating fully ionized polyacidic gel.
-Except the particles in the network, the monovalent co- and counter-ions ions, 
-$\cl$ and $\na$, are present in simulation box. 
-The total electric charge of all the particles in the box is zero, therefore the amount 
-of $\na$ ions is bigger than that of $\cl$ by the number of hydrogel units, $\Ngel$.
-The solvent assumed to be water, which is modeled implicitly via setting up dielectric permittivity $\epsilon=80$.
-
-We use three types of interactions, \ie bonded interactions, short-range non-bonded interactions and electrostatic interactions.
-
-We use Finite extension nonlinear elastic (FENE) potential~\refeq{eq:fene} to account for the bonding interactions.
-\begin{equation}\label{eq:fene}
-    V_\mathrm{FENE}(r) = -\frac{1}{2} K \Delta r_\mathrm{max}^2\ln \left[ 1 - \left(\frac{r-r_0}{\Delta r_\mathrm{max}} \right)^2 \right ],
-\end{equation}
-where $K$ is the magnitude of symmetric interaction between two segments,
-$\Delta r_{\mathrm{max}}$ is the maximal stretching length of the bond and $r_0$ is the equilibrium bond length.
-In our simulations we set $K = 10 \kT/\sigma^{2}$, $\Delta r_{\mathrm{max}} = 2 \sigma$ and $r_0 = 1.0\sigma$~\cite{Jin2007}.
-
-The non-bonded interactions are modelled by the truncated Lennard-Jones interaction potential.
-This potential imposes strong repulsion between all particles at short distances:
-\begin{equation}
-    \begin{split}\label{eq:LJ}
-        V_\mathrm{LJ}(r) =
-        \begin{cases}
-            4 \varepsilon \left( \left(\cfrac{\sigma}{r}\right)^{12}
-            - \left(\cfrac{\sigma}{r}\right)^6\right)
-            & \mathrm{if~} r < r_\mathrm{cut}\\
-            0
-            & \mathrm{elsewhere}
-        \end{cases},
-    \end{split}
-\end{equation}
-where $r$ is the interparticle distance,
-$\sigma = 0.35 \mathrm{nm}$ is a chosen characteristic size of the particles,
-$\varepsilon$ is the depth of the potential well in $\kT$ units and $r_\mathrm{cut}$ is the cut-off distance beyond which the potential is set zero.
-
-We model the long range electrostatic interactions by the Coulomb potential:
-\begin{equation}
-    V_{\mathrm{EL}}=\lb\kT \cfrac{q_{1}q_{2}}{r},
-\end{equation}
-where $\lb$ is Bjerrum length; $\lb = 2\sigma = 0.7 \mathrm{nm}$ which corresponds to water the Bjerrum length in water at $T=300 \mathrm{K}$.
-
-We use Langevin thermostat, \ie we add two additional terms to force in equation of motion
-\begin{equation}
-f_i =  -\gamma v_i(t)+\sqrt{2\gamma \kT }\eta_i(t),
-\end{equation}
-where the first term correspond to constant friction with $\gamma$ being a friction coefficient, and the second one corresponds to random thermal force with $\eta_i$ being a normally distributed random number (see for details \cite{Grest1986}).
-
-Integrating the Langevin motion equation for all the particles we sample total energy of the system and pressure \cite{essmann1995}.
-
-\subsubsection{Monte Carlo sampling in open system}
-
-Monte Carlo scheme for sampling the exchange of ions in \emph{open system} is based on the formula for free energy of grand canonical ensemble.
-
-\begin{equation}
-    \Omega=E-TS+\sum_i\mu_i N_i\label{eq:Omega-GC}
-\end{equation}
-where $E$ is internal energy, $T$~--- temperature, $S$~--- entropy, $N_i$ is the number of ions of type $i\in\{\na,\ \cl\}$.
-
-%Our model system represents a finite volume $V$ which exchanges particles with the bath of infinite volume.
-%The infinity of the volume means, that the particle exchange between the system and the bath does not influence on the chemical potentials in the bath.
-%Such ensemble is called grand canonical ensemble; the free energy in this ensemble, the Landau potential, is
-The entropy $S$ is given by the Boltzmann formula~\cite{Nagle2004}:
-\begin{equation}
-    S=\kB\sum_i\ln\frac{V^{N_i}}{N_i!}\label{eq:entropy}
-\end{equation}
-%\todo{for partiles without interactions}
-It accounts for two contributions:
-\begin{enumerate}
-    \item the combinatorial entropy $S_{c}=-\sum_i\kB\ln N_i!$ which reflects the freedom of choice among $N$ particles
-    \item the mixing entropy $S_{m}=\kB \sum_i N_i\ln V$ which reflects the freedom to place the chosen particle randomly within the simulation box. 
-\end{enumerate}
-$V$ is the unitless volume, \ie the volume measured in units of $\sigma^3$. 
-Thus \refeq{eq:Omega-GC} turns to 
-%\todo{this is not reason, moreover A.10 is already wrong as for units}
-\begin{equation}
-    \Omega=E-\kT\ln\prod_i\frac{V^N_i}{N_i!}+\sum_i\mu_i N_i
-\label{eq: Omega_GC}
-\end{equation}
-The change of free energy associated with an exchange of ion pair is
-\begin{equation}
-    \Delta\Omega=\kT\ln\prod_i\left(V^{\xi}\frac{N_i!}{\left(N_i+\xi\right)!}\right)+\xi\mu_i+\Delta E
-\label{eq: DeltaG GC}
-\end{equation}
-where $\xi=+1$ stands for insertion of an ion pair and $\xi=-1$ for deletion.
-In general $\xi$ can be any number, but in case when  $\xi = \pm 1$ the previous equation gets simplified 
-\begin{equation}
-    \Delta\Omega=\kT\ln V^{2\xi} \prod_i \left(N_i+\theta(\xi)\right)^{-\xi}+\xi\mu_i+\Delta E
-\label{eq: DeltaG GC_simpl}
-\end{equation}
-where $\theta$ is the Heaviside function, $\theta(\xi) = 1, \mathtt{if}\  \xi>0$ , $\theta(\xi) = 0, \mathtt{if}\  \xi<0$
-
-The procedure of the Monte Carlo Sampling is the following \cite{Frenlkel2002_book}
-\begin{enumerate}
-	\item we propose the new configuration of the system by insertion (or deletion) of an ion pair, $\xi=\pm1$
-	\item we accept the new configuration if
-	\begin{equation}
-        \mathcal{R}^{\xi}<e^{\Delta\Omega/\kT}=V^{2\xi} \prod_i \left(N_i+\theta(\xi)\right)^{-\xi}e^{\left(\Delta E+\xi\mu\right)/\kT}\label{eq: GC acceptance}
-	\end{equation}
-\end{enumerate}
-where $\mathcal{R}$ is uniformly distributed random number in range between $0$ and $1$.
-
-\subsection{Monte Carlo sampling in closed system}
-In the same way we derive the acceptance criterion for sampling the closed system (Gibbs ensemble)
-
-The free energy of the Gibbs ensemble is a sum of free energies of the gel and the external volume.
-
-\begin{equation}
-    \Omega=E\gel-TS\gel + E\out-TS\out \label{eq:Omega-GC}
-\end{equation}
-
-The entropy $S$ is given by the Boltzmann formula~\cite{Nagle2004}:
-\begin{equation}
-    S=\kB\sum_i\ln\frac{V\gel^{N\gel_i}}{N_i!}\label{eq:entropy}
-\end{equation}
-%\todo{for partiles without interactions}
-It accounts for two contributions:
-\begin{enumerate}
-    \item the combinatorial entropy $S_{c}=-\sum_i\kB\ln N_i!$ which reflects the freedom of choice among $N$ particles
-    \item the mixing entropy $S_{m}=\kB \sum_i N_i\ln V$ which reflects the freedom to place the chosen particle randomly within the simulation box. 
-\end{enumerate}
-$V$ is the unitless volume, \ie the volume measured in units of $\sigma^3$. 
-Thus \refeq{eq:Omega-GC} turns to 
-%\todo{this is not reason, moreover A.10 is already wrong as for units}
-\begin{equation}
-    \Omega=E-\kT\ln\prod_i\frac{V^N_i}{N_i!}+\sum_i\mu_i N_i
-\label{eq: Omega_GC}
-\end{equation}
-The change of free energy associated with an exchange of ion pair is
-\begin{equation}
-    \Delta\Omega=\kT\ln\prod_i\left(V^{\xi}\frac{N_i!}{\left(N_i+\xi\right)!}\right)+\xi\mu_i+\Delta E
-\label{eq: DeltaG GC}
-\end{equation}
-where $\xi=+1$ stands for insertion of an ion pair and $\xi=-1$ for deletion.
-In general $\xi$ can be any number, but in case when  $\xi = \pm 1$ the previous equation gets simplified 
-\begin{equation}
-    \Delta\Omega=\kT\ln V^{2\xi} \prod_i \left(N_i+\theta(\xi)\right)^{-\xi}+\xi\mu_i+\Delta E
-\label{eq: DeltaG GC_simpl}
-\end{equation}
-where $\theta$ is the Heaviside function, $\theta(\xi) = 1, \mathtt{if}\  \xi>0$ , $\theta(\xi) = 0, \mathtt{if}\  \xi<0$
-
-The procedure of the Monte Carlo Sampling is the following \cite{Frenlkel2002_book}
-\begin{enumerate}
-	\item we propose the new configuration of the system by insertion (or deletion) of an ion pair, $\xi=\pm1$
-	\item we accept the new configuration if
-	\begin{equation}
-        \mathcal{R}^{\xi}<e^{\Delta\Omega/\kT}=V^{2\xi} \prod_i \left(N_i+\theta(\xi)\right)^{-\xi}e^{\left(\Delta E+\xi\mu\right)/\kT}\label{eq: GC acceptance}
-	\end{equation}
-\end{enumerate}
-where $\mathcal{R}$ is uniformly distributed random number in range between $0$ and $1$.
-
-We model the ionization equilibrium by means of sampling the reaction ensemble~\cite{Smith1994, Turner2008a}.
-In the reaction ensemble we perform chemical reactions as simultaneous insertion, deletion or identity change of particles according to the reaction equation.
-For example we assume the ionization of an acidic unit which proceeds according to the reaction equation
-\begin{equation}
-    \mathrm{AH}\stackrel{K}{\leftrightarrows}\A+\h\label{eq: acid reaction}
-\end{equation}
-We perform the forward direction of this reaction
-by inserting a $\h$ particle and replacing $\AH$ by $\A$.
-We perform the reverse direction of this reaction
-by deleting a $\h$ particle and replacing $\A$ by $\AH$.
-
-In order to account for the particles creation and deletion
-we need to introduce standard states for individual reacting species.
-The creation of a particle then means that the particle is removed from the standard state
-and inserted into the studied system, and vice versa for deletion.
-Each species in its standard state has the \emph{standard} chemical potential, $\mu^\ominus_i$.
-The choice of standard state for each component is arbitrary
-and we usually define it as pure component at standard pressure $10^5$ Pa
-and concentration $1 \molperl$~\cite{IUPAC}.
-
-Thus we rewrite the formula for free energy \refeq{eq:Omega-GC}
-accounting for particles creation and deletion as
-\begin{equation}
-    \Omega=E-TS+\sum_i\left(\mu_i-\mu^\ominus_i\right) N_i\label{eq:Omega-RE}
-\end{equation}
-where the last term in \refeq{eq:Omega-RE} stands for the exchange of particles between the studied system and the standard states.
-
-Let's have the reaction extent $\xi = (N_i - N_{i,0})/\nu_i$
-where $N_i$, resp. $N_{i,0}$ is the actual, resp. initial number of the $i$-th particle species,
-$\nu_i$ is its stoichiometric coefficient.
-and $i$ runs over individual species involved
-in the chemical reaction \refeq{eq: acid reaction} $i \in (\h,\ \A,\ \AH)$. 
-The stoichiometric coefficients are positive for reaction products
-and negative for reactants: $\nu_\h=1$, $\nu_\A=1$, $\nu_\AH=-1$.
-Therefore we take $\xi = +1$ for the forward reaction direction
-and $\xi = -1$ for the reverse reaction direction.
-Then we can write the change of the free energy of the studied system during one reaction step as
-\begin{equation}
-\Delta\Omega_{\mathrm{re}}=\kT\ln\left(\prod_i V^{\nu_i\xi}\frac{N_i!}{\left(N_i+\nu_i\xi\right)!}\right)+
-\xi\left(\sum_i\nu_i\mu_i-\sum_i\nu_i\mu_i^\ominus\right)+\Delta E
-\label{eq: DeltaG RE one}
-\end{equation}
-%\begin{multline}
-%    \Delta\Omega_{\mathrm{re}}=\kT\ln\left(\prod_i V^{\nu_i\xi}\frac{N_i!}{\left(N_i+\nu_i\xi\right)!}\right)+\\
-%    \xi\left(\sum_i\nu_i\mu_i-\sum_i\nu_i\mu_i^\ominus\right)+\Delta E
-%\label{eq: DeltaG RE one}
-%\end{multline}
-
-We write $\sum_i\nu_i \mu_i = 0$
-for the chemical reaction in equilibrium.
-
-The term $\sum_i\nu_i\mu_i^\ominus$ is the standard Gibbs free energy change
-of the reaction \refeq{eq: acid reaction}.
-which defines the equilibrium reaction constant \cite{Atkins} as
-\begin{equation}
-    K = e^{-\sum_i\nu_i \mu_i^\ominus / \kT}
-\end{equation}
-
-Finally, the \refeq{eq: DeltaG RE one} translates to
-\begin{equation}
-    \Delta\Omega_{\mathrm{re}}=\kT\ln\left(K^\xi\prod_i V^{\nu_i\xi}\frac{N_i!}{\left(N_i+\nu_i\xi\right)!}\right)+\Delta E
-\label{eq: DeltaG RE two}
-\end{equation}
-
-\subsection{Ion pairs insertions\label{sec: ion insertions}}
-We treat the exchange of mobile ions with the reservoir as simultaneous insertion or deletion
-of ion pairs or sets in the simulation box.
-We insert/delete either $\na$ and $\cl$ ion pair or the two $\cl$ ions together with one $\ca$ ion.
-Thus we model the insertion as:
-\begin{eqnarray}
-    \na +  \cl &\leftrightarrows& \emptyset\label{eq:nacl} \\
-    \ca + 2\cl &\leftrightarrows& \emptyset \label{eq:cacl}
-\end{eqnarray}
-with the corresponding equilibrium reaction constants, reflecting the free energy change during the insertion
-\begin{eqnarray*}
-    K_\mathrm{NaCl}     = \exp\left(\left(\mu_\na+ \mu_\cl \right) /\kT\right), \\
-    K_{\mathrm{CaCl}_2} = \exp\left(\left(\mu_\ca+2\mu_\cl \right /\kT\right))
-\end{eqnarray*}
-%$K_\mathrm{NaCl}= \exp\left(\mu_\na+\mu_\cl \right)$, $K_{\mathrm{CaCl}_2} = \exp\left(\mu_\ca+2\mu_\cl \right)$
-
-the Monte Carlo in the \emph{open system} box with the gel and the monovalent co- and counter-ions ions, 
-$\cl$ and $\na$ is allowed to exchange particles with infinite reservoir with constant chemical potential.
-
-\dots
-
-In the \emph{closed system} system two boxes one with the gel and the other with ions pairs only iare allowed to exchange particles.
-
 \begin{figure*}[h]
@@
 
-\subsection{}
-
-\subsection{Gibbs ensemble}
-\todo{We have the "Gibbs ensemble" in the title, and this term is not used in the manuscript at all.}
-TODO concise description of Gibbs ensemble, solving the task to Reviewer 2, Q5 and Q7
-
-The simulation of the gel compression is performed in two ensembles:
+We propose the desalination process as a cascade of gel compressions and decompressions lowering the  supernatant salinity.
+%it is worth to note that we are not limited with this process only.
+In this process, the gel is supposed to be compressed/decompressed in an \emph{open system} and in a \emph{closed system}.
+The compression in \emph{open system} assumes that the gel is in thermodynamic equilibrium with a huge (effectively \textbf{infinite}) reservoir of an aqueous solution, whereas 
+the \emph{closed system} implies that the gel is in equilibrium with a \textbf{finite} reservoir of an aqueous solution.
+
+Due to huge size of the reservoir, the compression of the gel in \emph{open system} does not affect the reservoir salinity, $\cs =$ $\cna=$ $\ccl=$ $\text{Const}$, whereas the number of ions entrapped in the volume $\Vbox$ changes (\reffig{fig: open}).
+On the contrary, the compression of the gel in the \emph{closed system} changes the salinity in the reservoir, but the total number of $\na$ and $\cl$ ions in the gel and in the reservoir, \ie in the volume $\Vbox$ (\reffig{fig: closed}), remains constant.
+
+%In the case of \emph{open system} the gel is the grand canonical ensemle, as $\mu, V, T = \mbox{Const}$, while the case of \emph{closed system} the gel and the explicit reservoir are a variation of Gibbs ensemble \cite{Panagiotopoulos1988b} performed with constant volume for the both boxes, equal chemical potentials of ion species at constant temperature.
+
+%Unfortunately, there is no universal computationally effective technique to sample pressure difference, volume, and number of particles at the same. 
+The mechanical movement and the exchange of ions occur simulataneously in reality, however, we simulate them alternating each other in stop-run mode. 
+To sample mechanical properties of the gel and reservoir we use MD simulation, whereas to sample the ions distribution between the gel and a reservoir we use MC simulation.
+The details of this hybryd MCMD computational technique can be found in our previous studies of polyelectrolytes in open system \cite{Rud2020, Rud2022, Landsgesel2020a}.
+
+\subsection{Langevin Dynamics}
+\begin{figure*}[h]
+\centering 
+\includegraphics[width=0.7\textwidth]{{figures/simgibbs}.pdf}\caption{Diamond-like network in the simulation box. Color code represents
+the individual ion types (red: $\na$, blue: $\cl$, yellow: $\ca$)
+and the hydrogel (gray: neutral segment ($\AH$), cyan: charged segment
+($\A$)). \label{fig:diamond}.}
+\end{figure*}
+We model the gel as a network of 16 linear polymer chains, each consisting of 30 monomer units.
+These polymer chains are connected to a diamond-like network by 8 crosslinking units.
+This means, there are $\Ngel=16\cdot30 + 8=488$ gel monomers in the simulation box (see \reffig{fig:diamond}).
+The network is put in simulation cubic box of the volume $\Vgel$ with periodic boundary conditions, which virtually emulaates an infinite polymer network.
+
+Each monomer unit of the network carries a negative elementary electric charge.
+Except for the gel monomers, the monovalent co- and counter-ions ions, $\cl$ and $\na$, are present in the simulation box.
+The total electric charge of all the particles in the box is zero, therefore the amount of $\na$ ions exceeds the amount of $\cl$ by $\Ngel$.
+
+Each pair of the particles interact via the truncated Lennard-Jones interaction potential, which imposes strong repulsion between all particles at short distances:
+\begin{equation}
+    \begin{split}\label{eq:LJ}
+        V_\mathrm{LJ}(r) =
+        \begin{cases}
+            4 \varepsilon \left( \left(\cfrac{\sigma}{r}\right)^{12}
+            - \left(\cfrac{\sigma}{r}\right)^6\right)
+            & \mathrm{if~} r < r_\mathrm{cut}\\
+            0
+            & \mathrm{elsewhere}
+        \end{cases},
+    \end{split}
+\end{equation}
+where 
+$r$ is the interparticle distance, 
+$\sigma = 0.35 \mathrm{nm}$ is a chosen characteristic size of the particles, 
+$\varepsilon = \kT$ is the depth of the potential and 
+$r_\mathrm{cut}$ is the cut-off distance beyond which the potential is set zero.
+
+The bonds connecting the gel to a network are modeled using finite extension nonlinear elastic potential (FENE)
+\begin{equation}\label{eq:fene}
+V_\mathrm{FENE}(r) = -\frac{1}{2} K \Delta r_\mathrm{max}^2\ln \left[ 1 - \left(\frac{r-r_0}{\Delta r_\mathrm{max}} \right)^2 \right ],
+\end{equation}
+where
+$r$ is the distance between the bonded segments,
+$K$ is the magnitude of their interaction,
+$\Delta r_{\mathrm{max}}$ is the maximal stretching length of the bond and
+$r_0$ is the equilibrium bond length.
+For our simulations we chose $K = 10 \kT/\sigma^{2}$, $\Delta r_{\mathrm{max}} = 2 \sigma$ and $r_0 = 1.0\sigma$~\cite{Jin2007}.
+
+All the charged paticles interact via Coulomb electrostatic potential:
+\begin{equation}
+    V_{\mathrm{EL}}=\lb\kT \cfrac{q_{1}q_{2}}{r},
+\end{equation}
+where $\lb$ is Bjerrum length; $\lb = 2\sigma = 0.7 \mathrm{nm}$ which corresponds to the  Bjerrum length in water at temperature $T=300 \mathrm{K}$, $\kB$ --- Botlzman constant.
+In that sense, the solvent (water) accounted for in the model implicitly via setting up dielectric permittivity $\epsilon=80$.
+
+We used Langevin thermostat, \ie the two additional terms to force in equation of motion were added
+\begin{equation}
+\mathbf{f}_i =  -\gamma \mathbf{v}_i(t)+\sqrt{2\gamma \kT }\boldsymbol{\eta}_i(t),
+\end{equation}
+where the first term correspond to constant friction with $\gamma$ being a friction coefficient,
+ and the second one corresponds to random thermal force with $\boldsymbol{\eta}_i$ being a normally distributed random vector; $\mathbf{v}_i$~--- velocity of $i$-th particle (see for details \cite{Grest1986}).
+
+\subsubsection{Monte Carlo sampling in \emph{open system}}
+Monte Carlo scheme for sampling the exchange of ions in \emph{open system} is based on the formula for free energy of grand canonical ensemble.
+\begin{equation}
+    \Omega_{\mathrm{open}}=E-TS+\sum_i\mu_i N_i\label{eq:Omega-GC}
+\end{equation}
+where $E$ is internal energy, $T$~--- temperature, $S$~--- entropy, $N_i$ is the number of ions of type $i\in\{\na,\ \cl\}$, $\mu_i$~--- corresponding chemical potential.
+
+%Our model system represents a finite volume $V$ which exchanges particles with the bath of infinite volume.
+%The infinity of the volume means, that the particle exchange between the system and the bath does not influence on the chemical potentials in the bath.
+%Such ensemble is called grand canonical ensemble; the free energy in this ensemble, the Landau potential, is
+The entropy $S$ is given by the Boltzmann formula~\cite{Nagle2004}
+\begin{equation}
+    S=\kB\sum_i\ln\frac{\Vgel^{N_i}}{N_i!}\label{eq:entropy}
+\end{equation}
+%\todo{for partiles without interactions}
+which accounts for two contributions:
 \begin{enumerate}
-\item \emph{open system}, when the simulation box with gel exchanges ions with an infinite 
-reservoir containing aqueous solution of constant salinity, $\cs$. 
-\item emph{closed system}, when the simulation box with the gel exchanges ions with a finite volume of aqueous solution.
+    \item the combinatorial entropy $S_{c}=-\kB\sum_i\ln N_i!$ which reflects the freedom of choice among the particles
+    \item the mixing entropy $S_{m}=\kB \sum_i N_i\ln \Vgel$ which reflects the freedom to place the chosen particle randomly within the simulation box. 
 \end{enumerate}
-The compression of the gel in the \emph{open system} does not affect the salinity in the 
-reservoir, thus the density of ions outside the gel remains constant 
-$\cs =$ $\cna=$ $\ccl=$ $\text{Const}$ (\reffig{fig: open}). 
-On the contrary, the compression of the gel in the \emph{closed system} changes the salinity in the reservoir, but the total number of $\na$ and $\cl$ ions in the gel and in the reservoir, \ie in the volume $\Vbox$ (\reffig{fig: closed}), remains constant.
-
-The amount of the individual ion types in gel, $N_i$, is given by
-\begin{equation}
-N_i = N_i\gel + \cs\cdot(\Vbox - \Vgel)
-\end{equation}
-where $i \in \{\na, \cl\}$, $\Vgel$~--- volume of the gel, $\Vbox$~--- the volume in which the gel is compressed. 
-$\Vbox$ is the gel volume in the free swelling equilibrium state.
-
-\subsection{Open system}
-We use the grand reaction method \cite{Landsgesel2020a,Rud2020} to simulate the open system.
-\todo{beter to say "method described in REF", to avoid the word 'grand reaction'}
-This method is a hybrid of Molecular dynamics (MD) and Monte Carlo (MC). 
-The whole simulation consists of MD and MC subsimulations, consecutively followed one by each other. 
-The MD simulation is a standard Langevin dynamics \cite{Grest1986}, which models the mechanical motion of all particles in the system. 
-MC simulates the thermodynamic equilibrium with reservoir and handles the ion exchange with the simulation box. 
-The insertion (and deletion) of ion pairs is considered as a reaction of creation (or annihilation) of an ion pair 
-\begin{equation}
-\varnothing\stackrel{K}{\leftrightarrows}\na+\cl
-\end{equation}
-with a reaction constant defined by the chemical potential of ions,
-$K=\exp\left(\muna+\mucl\right).$
-The simulation setup is sketched in \reffig{fig:open}\todo{it is not a 'simulation' setup}.
-
-\subsection{Closed system}
-Analogical scheme is used for the simulation of the gel in the closed system. 
-The procedure  again consists of subsequent MD and MC subsimulation, but now the MD is running in two simulation boxes simultaneously.
-The first box of the volume $\Vgel$ contains the gel with ions and the second box of the volume $\Vout$ contains only ions. 
-The total volume of both boxes is constant, $\Vbox=V_{\mathrm{gel}}+V_{\mathrm{out}}$, so the gel compression implies the decrease of $\Vgel$ and increase of $\Vout$.
-The simulation setup is sketched in \reffig{fig:closed}.
+$\Vgel$ is the unitless volume, \ie the volume measured in units of $\sigma^3$. 
+Thus the change of free energy associated with an exchange of ion pairs is
+\begin{equation}
+\Delta\Omega_\mathrm{open}=\kT\ln\prod_i\left(\Vgel^{\xi}\frac{N_i!}{\left(N_i+\xi\right)!}\right)+\xi\sum_i\mu_i+\Delta E
+\label{eq: DeltaG GC}
+\end{equation}
+where $\xi$ is an algebraic number of inserted (or removed) ion pairs; in general $\xi$ can be any number, but in the case when $\xi = \pm 1$, which corresponds to addition or removal of only one ion pair, the \refeq{eq: DeltaG GC} gets simplified
+\begin{equation}
+    \Delta\Omega_\mathrm{open}=\kT\ln \Vgel^{2\xi} \prod_i \left(N_i+\theta(\xi)\right)^{-\xi}+\xi\sum_i\mu_i+\Delta E
+\label{eq: DeltaG GC_simpl}
+\end{equation}
+where $\theta$ is the Heaviside function, $\theta(\xi) = 1$, if $\xi=+1$, $\theta(\xi) = 0$, if $\xi=-1$.
+
+The procedure of the Monte Carlo Sampling is the following \cite{Frenlkel2002_book}
+\begin{enumerate}
+	\item propose the new configuration of the system by insertion (or deletion) of an ion pair, $\xi=\pm1$
+	\item accept the new configuration if
+	\begin{equation}
+        \mathcal{R}^{\xi}<e^{\Delta\Omega_\mathrm{open}/\kT}=\Vgel^{2\xi} \prod_i \left(N_i+\theta(\xi)\right)^{-\xi}e^{\left(\Delta E+\xi\mu\right)/\kT}\label{eq: GC acceptance}
+	\end{equation}
+	where $\mathcal{R}$ is uniformly distributed random number in range between $0$ and $1$.
+	\item then collect the number of ions, $\Nna$ and $\Ncl$ to the samples array.
+\end{enumerate}
+
+\subsection{Monte Carlo sampling in closed system}
+
+In the \emph{closed system} a the gel exchanges particles with explicit finite reservoir box. 
+The total number of ion species in both boxes is fixed, whereas the density of ions in extrernal reservoir is defined by thermodynamic equilibrium between the two subvolumes (see \reffig{fig: closed}.
+The Monte Carlo sampling of the distribution of ions between the subvolumes performed in a way similar to described in \cite{Panagiotopoulos1988b}.
+\todo{add here that citation about Gibbs ensemble}
+
+The free energy of the Gibbs ensemble is a sum of the gel's free energy and that of the external volume.
+\begin{equation}
+    \Omega_{\mathrm{closed}}=\Egel-T\Sgel + \Eout-T\Sout \label{eq:Omega-GC}
+\end{equation}
+using similar reasoning as for \emph{open system} one can derive the change of free energy associated with ion pair exchange 
+\begin{equation}
+\Delta \Omega_{\mathrm{closed}} =2 k_B T \ln \left(\frac{\Vgel}{\Vout} \right) ^ {\xi}\prod_i \left(\frac{N_{i}\gel+\theta(\xi)}{N_{i}\out+\theta(-\xi)}\right)^{-\xi} + \Delta \Egel + \Delta \Eout
+\end{equation}
+where $\xi$ defines the direction of the trial move, so that $\xi = -1$ when an ion pair moved from gel to outside volume and  $\xi = +1$ otherwise, $\Delta \Egel$ and $\Delta \Eout$ are corresponding changes of the potential energy of the gel and the outside volumes.
+
+Then the procedure of sampling is the same as that for \emph{open sysytem}: (1) propose the move of an ion pair, (2) accept a new state if $\mathcal{R}^{\xi}<\exp({\Delta\Omega_\mathrm{closed}/\kT}$), (3) repeat the procedure until the desired number of samples is reached.
 
 \subsection{Algorithm}
-The thermodynamic equilibrium between the two subvolumes implies the exchange of ion pairs 
-between them.
-This is performed by means of MC procedure in a way similar to described in \cite{Panagiotopoulos1988b}.
-
-As mentioned above, the simulation consists of MD and MC subsimulations. The algorithm is following:
+
+As mentioned above, the whole simulation run consists of MD and MC subsimulations of mechanical movement of the particles and ion exchange. The algorithm is following:
 \begin{enumerate}
-\item Simulate MD in both boxes and collect the observables (pressure, $P$)
-\item Perform MC procedure simulating ion exchange and collect the observables (number of ions in both boxes, 
-%$\nna\gel$,
-$\Ncl\gel$ 
-%$\nna\out$ 
-and $\Ncl\out$ )
-\item Repeat the procedure until the desired length of sample arrays is reached.
+\item Initiate the systems to simulate: the gel of the volume $\Vgel$ and the external solution of the volume $\Vout$;
+\item Equilibrate the system running interspersing the MD and MC stages
+\item Run the MD subsimulation and collect the observables: pressure in both volumes, $P_\mathrm{gel}$, $P_\mathrm{out}$, and distancies between the nodes of the gel network.
+The last one needed to estimate the autocorrelation of MD simulation;
+\item Run MC procedure simulating ion exchange and collect the number of ions in both boxes, 
+$\Ncl\gel$ and $\Ncl\out$; 
+\item Repeat the MD and MC subsimulations until the desired length of sample arrays is reached.
 \end{enumerate}
+
+Using the data obtained from simulations we calculate  
+$\vgel$ --- molar volume of the gel, \ie the volume of the gel per one mol of gel segments, $\vgel = \Vgel / \Ngel$;
+$\Pgel$ --- partial pressure of the gel, \ie the pressure that needs to be applied to the gel via a solvent permeable filter to compress the gel to a specific molar volume;
+$\cs$ --- the density of ions in  the outside volume;
+and $\ncl$ --- the total amount of the ions in both volumes divided by the total volume of both boxes, $\ncl = \Ncl/\Vbox$
+
+$\Vbox$ was chosen to be close to the gel free swelling equilibrium, that to the the state when $\Pgel = 0$. 
+In order to obtain the value $\Vbox$ we perform the set of open system simulations for various $\Vgel$. That value of $\Vgel$, at which $\Pgel$ is closest to zero we choose as $\Vbox$.
+Then as soon as $\Vbox$ is defined we perform the compression of the gel in closed system decreasing the $\Vgel$ starting from $\Vbox$ and correspondingly increasing the outer volume $\Vout$.
+
+\todo{We have the "Gibbs ensemble" in the title, and this term is not used in the manuscript at all.
+TODO concise description of Gibbs ensemble, solving the task to Reviewer 2, Q5 and Q7}
 
@@
 \end{figure*}
-First, we run a set of simulations modeling the gel compression in \emph{open system}, \ie in equilibrium with a big bath of certain salinity, $\cs$. 
-The simulations were run for a set of different simulation box volumes. 
-Each simulation returned the averaged values of pressure, $P$, and the number of $\cl$ ions, present in the simulation box, $\ncl$.
-
-In order to get the partial pressure of the gel, we subtracted from $P$ the osmotic pressure of ions in the reservoir: $\Pgel=P - \Pout$.
+So, at the beginning, we run a set of simulations modeling the gel compression in \emph{open system}, \ie in equilibrium with a big bath of certain salinity, $\cs$. 
+The simulations were run for a set of different gel volumes, $\Vgel$. 
+Each simulation returned the averaged values of pressures, $P_\mathrm{gel}$, and the number of $\cl$ ions, present in the simulation box, $\Ncl\gel$.
+
+In order to get the \emph{partial pressure} of the gel, we subtracted from $P_\mathrm{gel}$ the osmotic pressure of ions in the reservoir: $\Pgel=P_\mathrm{gel} - \Pout$.
 $\Pout$, in turn, we obtained from a separate simulation of a reservoir, containing ionic gas in equilibrium with the bath of the same salinity $\cs$.
-The gel partial pressure, $\Pgel$, is the pressure that needs to be applied to the gel via a solvent permeable filter to compress the gel to a specific molar volume, $\Vgel$.
-$\Vgel$ is the gel volume per one mole of gel monomer units.
-
-These dependencies of $\Pgel$ on $\Vgel$ for \emph{open system} for a set of various salinities are presented
+
+The dependencies of $\Pgel$ on $\Vgel$ for \emph{open system} for a set of various salinities are presented
 in Figure \ref{fig: PV} by solid lines. 

### 2022-09-15 gibbs.tex
merged by meld the changes in intro from Lucie

@@
 }
+Waste water treatment and technology is one of the greatest concerns of modern society. 
+The waste water has to be disposed of both biological \cite{guesmi2022} and chemical \cite{baaloudj2022_1,shahzad2022} pollutants.
+Most imporatntly, water treatment technologies are needed for the still increasing demand on production of potable water from the brine, \ie for desalination.
 
+\subsection{Water desalination technologies}
 Two basic approaches for separating water from salt are present in modern desalination technology \cite{Miller2003,Curto2021}.
@@
 The first approach is distillation, which uses heat to cause a phase change of the water to vapor. The vapor phase is separated from the brine and condenses to liquid fresh water. 
-The released condensation energy is directed back to heating the feed solution.
+The released condensation energy is directed back to heat the feed solution.
 Distillation processes were the first desalination techniques conducted on a large commercial scale and still account for a large portion of the modern world’s desalination capacity.
 
-The second approach is to physically separate the brine components using an osmotic membrane transparent only for water molecules, which move in response to a water chemical potential difference.
-In the context of our study, we will mention the reverse osmosis process (RO)~--- the major process of all the modern desalination industry, and the newly emerging membrane
-technology~--- forward osmosis (FO) \cite{Akther2015}.
+The second approach is to physically separate the brine components using an osmotic membrane transparent only for water molecules, which move in response to the difference in water chemical potential.
+In the context of our study, we will mention the reverse osmosis process (RO) as the major process of all the modern desalination industry, and the newly emerging membrane technology~--- forward osmosis (FO) \cite{Akther2015}.
 In RO, the difference in water chemical potential originates from a difference in pressures applied to the feed and to product solutions. 
@@
 Distillation is easy and cheap technology but it is characterized by relatively high energy costs due to the dissipation of thermal energy. 
-On the contrary, RO uses expensive osmotic membranes, which need to be replaced regularly because of scaling and fouling.
+In turn, RO uses expensive osmotic membranes, which need to be replaced regularly because of scaling and fouling. 
 Moreover, RO requires very high operating pressures, ranging from 20 to 200 bar, to let the water pass through the membrane. 
-But in terms of energy losses, it works close to the thermodynamic limit.
+But, in terms of energy losses, it works close to the thermodynamic limit.
 Thus, theoretically, per one ion pair transferred from freshwater to salty water, it consumes only the energy equal to the difference between the chemical potentials of the transfered ions.
@@
 When a dehydrated or deswollen hydrogel uptakes water, its polymer chains extend, creating a swelling pressure. 
-For example, as reported in \cite{Wack_2009} weakly crosslinked poly(acrylic acid) (PAA) copolymers with polymer volume fractions between 0.03 and 0.30 exhibit a swelling pressure ranging from 0.20--4.23 MPa.
+For example, as reported in \cite{Wack_2009}, weakly crosslinked poly(acrylic acid) (PAA) copolymers with polymer volume fractions between 0.03 and 0.30 exhibit a swelling pressure ranging from 0.20--4.23 MPa.
 Polyelectrolyte hydrogels, which are carrying ionic groups on the comonomer units (like PAA), are able to reject salt ions from the solution, they absorb a solution of lower salinity than that they are equilibrated with.
 
-An important, advantageous aspect of polymer hydrogels is that they can undergo reversible volume change, \ie solution --- gel phase transitions in response to environmental stimuli.
-This aspect causes hydrogels to be labeled as ‘smart’ hydrogels.
+An important, advantageous aspect of polymer hydrogels is that they can undergo reversible volume change, \ie solution --- gel phase transitions in response to external stimuli. 
+This aspect causes hydrogels to be labeled as ‘smart’ materials. 
 Many physical and chemical stimuli have been applied to induce various responses of such smart hydrogels, in particular, to change them from hydrophilic to hydrophobic, thereby releasing water. 
@@
 
-The smart properties of hydrogels were utilized for desalination in a recent study by Li \etal \cite{Li2011}, where hydrogels have been considered as draw agents for FO.
-In this study authors have shown, that hydrogels,
-are able to absorb water across the FO membrane due to their swelling and osmotic pressure and
+Li \etal \cite{Li2011} took advantage of the smart hydrogel properties for desalination purposes. In this work, the authors used hydrogels as draw agents for FO. 
+They have demonstrated that the hydrogels are able to absorb water across the FO membrane due to their swelling and osmotic pressure and
 allow dewatering under the influence of stimuli (thermal and/or mechanical), due to their insoluble cross-linked polymer network.
-For instance, Li \etal proposed the use of hydrogel made of thermoresponsive polyelectrolyte~--- copolymer of poly-N-isopropyl acrylamide (p-NIPAAm) and polyacrylic acid (p-AA).
-Depending on the temperature the network of the gel appears to be either hydrophilic or hydrophobic.
-In the hydrophilic state, the gel is used as a draw solute accumulating water inside, then in the hydrophobic state, the water releases out.
+They have proposed the use of hydrogel based on thermoresponsive polyelectrolyte~--- copolymer of poly-N-isopropyl acrylamide (p-NIPAAm) and polyacrylic acid (p-AA).
+This gel network is either hydrophilic or hydrophobic, depending on the temperature.
+Such gel accumulates water inside the network in its hydrophilic state, but it releases the water out in its hydrophobic state.
 
-Moreover, from a thermodynamics perspective, the polyelectrolyte hydrogel itself is an osmotic membrane generating Donnan potential, which rejects ions between outer and inner solutions \cite{Wang_2014}.
+From a thermodynamics perspective, the polyelectrolyte hydrogel itself is an osmotic membrane generating Donnan potential, which rejects ions between outer and inner solutions \cite{Wang_2014}. 
 Such a view on hydrogels was employed in a series of works by the group of prof. Wilhelm (see for example \cite{Arens_2017,Fengler_2020}). 
 The authors of these works proposed to get rid of the osmotic membrane and simply use only micro filtration to compress the hydrogel squeezing out the accumulated inside the gel solution. 
-In their method first, the deswollen hydrogel was equilibrated with saline water feed.
-During equilibration, the gel was swelling absorbing water.
+In their method, the deswollen hydrogel was first equilibrated with saline water feed. 
+During the equilibration, the gel was swelling, absorbing the water. 
 Then it was taken out from the feed solution and mechanically squeezed by means of a microfiltration membrane. 
-The squeezed out brine was obtained to have lower salinity than the feed water.
+They have found that the brine, which was squeezed out, had lower salinity than the feed water.
 
-A similar approach was used by Ali \etal \cite{Ali2015}.
-In their study the thermosensitive gel was used (based on copolymers p-NIPAAm and p-AA), so instead of physical compression, the dewatering was done by an external heating stimulus (sunlight).
-At night the gel was equilibrating with feed water and at daytime, under sunlight, the gel was shrinking and releasing the collected inside solution.
+Similar approach was used by Ali \etal \cite{Ali2015}. 
+Here the authors used the thermosensitive gel (based on copolymers p-NIPAAm and p-AA), and instead of physical compression, the dewatering was done by an external heating stimulus (sunlight). 
+The gel was equilibrated with feed water during the night, and, at daytime, under sunlight, the gel was shrinking and releasing the solution.
 
 \subsection{Physics behind the desalination process}
-%The maximum entropy principle requires the density of charges to be more-less the same throughout the system medium. 
-Since the polyelectrolyte gel has its own charges and its own neutralizing counterions, the density of mobile ions (which are able to freely enter and leave the gel) in gel appears to be smaller than their density outside the gel.
-Therefore the internal solution of the gel has a lower density of mobile ions than that in the solution outside.
+Since the polyelectrolyte gel has its own charges and its own neutralizing counterions, the density of mobile ions (which are able to freely enter and leave the gel) inside the gel network appears to be smaller than their density outside the gel.
+Therefore the internal solution in the gel has lower density of mobile ions than the solution outside. 
 In that sense, the gel acts as an osmotic membrane separating solutions \cite{Rud2020}. 
-The driving force of the separation is the Donnan potential originated from the charges of the hydrogel network.
-The density of mobile ions difference between ions concentrations in the internal and external solutions
+The driving force of the separation is the Donnan potential, which originates from the charges in the hydrogel network. 
+The difference between the densities (concentrations) of the mobile ions in the internal and external solutions
 is defined by Donnan law \cite{Rud2018}
@@
 \end{equation}
-where $\ccl\gel$ and $\cna\gel$ are the internal concentration of monovalent anions and cations, $\cs$ is the salinity of external solution,  $\Vgel$ is the gel molar volume (inverse density of gel segments) and $\alpha$ is ionization degree (in the case of our study $\alpha=1$).
-The $\pm$ sign in the formula accounts for the change between the cases of gel made of polyanion or polycation.
+where $\ccl\gel$ and $\cna\gel$ are the concentrations of monovalent anions and cations in the internal solution,
+$\cs$ is the salinity of external solution,  $\Vgel$ is the gel molar volume (inverse density of gel segments)
+and $\alpha$ is ionization degree (in the case of our study $\alpha=1$). 
+The $\pm$ sign in the formula accounts for the sign change for the cases of polyanion or polycation gels.
 
-The lower salinity solution can be extracted from the gel by means of compression and/or other stimulus providing that the charge of the gel remains constant.
-In the case of gel made of weak (pH-sensitive) polyelectrolyte, the compression discharges the gel, therefore the neutralizing counterions leave out the gel diminishing the desalination effect \cite{Rud2018}.
-%Nevertheless, in\cite{Rud2018} we discussed how the release of counterions may be employed for desalination as well.
+As shown in \cite{Li_2011,Ali_2015,Arens_2017,Fengler_2020}, the solution of lower salinity can be extracted from the gel by means of compression and/or other stimulus, provided that the charge in the gel remains constant.
+In the case of weak polyelectrolyte (pH-sensitive) gel, the compression discharges the gel and therefore the neutralizing counterions leave out the gel, diminishing the desalination effect \cite{Rud2018}.
 
@@
 Indeed, the use of high hydraulic pressure diminishes all the advantages of this method over RO, and the reversibility of hydrogel swelling after strong compression remains questionable. 
-Nevertheless, in the current study, we model the compression of the gel limiting ourselves to low compression rates, less than 5 bar, and studied how the compression of the gel affects the surrounding salinity.
-We modelled also the desalination process, as a cascade of following one by each other gel swellings and compressions driving the salinity of supernate down to drinkable water. 
-%In the current study we would like to concentrate on the use of gel made of strong polyelectrolyte for water desalination. 
-%Namely, to investigate how the compression of the gel affects the salinity of the surrounding the gel solution and to propose the way of water desalination employing the hydrogel swelling/deswelling set of processes.
+Nevertheless, in this study, we model the compression of the gel limiting ourselves to low compression rates, less than 5 bar, and studied how the compression of the gel affects the surrounding salinity.
+We modelled the desalination process, as a cascade of step-by-step gel swellings and compressions, driving the salinity of the supernate down to potable water.
 
-%The target of our study is to model the thermodynamic equilibrium between the two boxes and to show how the compression of the gel affects the ion density in the outside solution.
+% water desalination technologies and Gibbs ensemble (https://doi.org/10.3390/nano10020293 \cite{erdos2020}).
 

### 2022-09-15 MDPI/response_letter.tex

@@
 \item \textit{Please do not separate introduction in three sections combine with problem and technology you used and challenges and your solutions.}
-Corrected. We have rewritten and improved the Introduction.
+We have rewritten and improved the Introduction. 
+Actually, we would like to keep the separation of the Introduction section in the respective subsections, because the Introduction is relativelly long and we beelive that dividing it in subsections facilitates its readability.
 

### 2022-09-16 gibbs.tex
changed abstract, intro , figures and model (a littel)

@@
 \abstract{
-Recently, polyelectrolyte hydrogels have been proposed as draw agents for forward osmosis (FO) desalination techniques. 
-Indeed, polyelectrolyte hydrogels can absorb a big amount of water across an osmosis membrane as a result of their swelling pressure. 
+Polyelectrolyte hydrogels can absorb a big amount of water across an osmotic membrane as a result of their swelling pressure.
 On the other hand, the insoluble cross-linked hydrogel network enables dewatering under the influence of external (thermal and/or mechanical) stimuli.
 Moreover, from a thermodynamic perspective, the polyelectrolyte hydrogel is already an osmotic membrane.
-These above-mentioned hydrogel properties designate them as excellent candidates for desalination, and, at the same time, avoid the use of expensive membranes.
+These above-mentioned properties designate hydrogels as excellent candidates for use in desalination, allowing, at the same time, to avoid the use of expensive membranes.
 In this article, we present our recent theoretical study of polyelectrolyte hydrogel usage for water desalination.
 Employing a coarse-grained model and the Gibbs ensemble, we modeled the thermodynamic equilibrium between coexisting gel phase and the supernate aqueous salt solution phase.
-We performed a sequence of step-by-step hydrogel compressions in \emph{open} and \emph{closed} systems.
-The compression in \emph{open system} causes the decrease of salt ions inside the hydrogel,
-while the compression in \emph{closed system} causes the decrease of the salt concentration in the supernatant solution.
-We modeled this stepwise process of continuous decrease of water salinity from seawater up to freshwater concentrations.
-We estimated the energy costs of the process to be comparable with reverse osmosis.
-%as 38.2 J per production of 1 liter of potable water, which is comparable with reverse osmosis.
+We performed a sequence of step-by-step hydrogel swellings and compressions in \emph{open} and \emph{closed} systems, \ie in equilibrium with a big and with a comparably small reservoir of aqueous solutions.
+The swelling in \emph{open system} causes the removal of ions from the big reservoir, whereas the compression in \emph{closed system} causes the decrease of the salt concentration in the small reservoir.
+We modeled this stepwise process of continuous decrease of water salinity from seawater up to freshwater concentrations and estimated the energy costs of the process to be comparable with reverse osmosis.%as 38.2 J per production of 1 liter of potable water, which is comparable with reverse osmosis.
 }
@@
 \section{Introduction\label{sec: intro}}
-\subsection{Water desalination technologies}
-
-\todo[inline]{
-The authors can follow the following references to generally highlight the global contamination and environmental pollution problems at the beginning of the introduction part
-https://doi.org/10.1016/j.jwpe.2022.102847 \cite{baaloudj2022_1}\\
-https://doi.org/10.1016/j.ceramint.2022.05.151 \cite{shahzad2022}\\
-https://doi.org/10.3390/catal12050500 \cite{baaloudj2022}\\
-https://doi.org/10.1007/s11356-022-21160-7 \cite{guesmi2022}\\
-https://doi.org/10.3390/ma15134547 \cite{kane2022}\\. 
-Then, highlight the water desalination technologies and Gibbs ensemble (https://doi.org/10.3390/nano10020293 \cite{erdos2020}).
-}
-Waste water treatment and technology is one of the greatest concerns of modern society. 
+Wastewater treatment and technology are one of the greatest concerns of modern society.
 The waste water has to be disposed of both biological \cite{guesmi2022} and chemical \cite{baaloudj2022_1,shahzad2022} pollutants.
-Most imporatntly, water treatment technologies are needed for the still increasing demand on production of potable water from the brine, \ie for desalination.
+Most importantly, water treatment technologies are needed for the still increasing demand on the production of potable water from the brine, \ie for desalination.
 
@@
 
-The first approach is distillation, which uses heat to cause a phase change of the water to vapor. The vapor phase is separated from the brine and condenses to liquid fresh water. 
+The first approach is distillation, which uses heat to cause a phase change of the water to vapor. 
+The vapor phase is separated from the brine and condenses to liquid fresh water. 
 The released condensation energy is directed back to heat the feed solution.
@@
 Hydrogels are three-dimensional networks of polymer chains that are crosslinked by either physical or chemical bonds.
-They are able to entrap large volumes of water attracted by the high concentration of hydrophilic groups. 
-When a dehydrated or deswollen hydrogel uptakes water, its polymer chains extend, creating a swelling pressure. 
+They can entrap large volumes of water attracted by the high concentration of hydrophilic groups.
+When a dehydrated or deswollen hydrogel uptakes water, its polymer chains extend, creating swelling pressure.
 For example, as reported in \cite{Wack_2009}, weakly crosslinked poly(acrylic acid) (PAA) copolymers with polymer volume fractions between 0.03 and 0.30 exhibit a swelling pressure ranging from 0.20--4.23 MPa.
-Polyelectrolyte hydrogels, which are carrying ionic groups on the comonomer units (like PAA), are able to reject salt ions from the solution, they absorb a solution of lower salinity than that they are equilibrated with.
+\emph{Polyelectrolyte} hydrogels, which are carrying ionic groups on the comonomer units (like PAA), can reject salt ions from the solution, \ie they absorb a solution of lower salinity than that they are equilibrated with.
 
-An important, advantageous aspect of polymer hydrogels is that they can undergo reversible volume change, \ie solution --- gel phase transitions in response to external stimuli. 
+An important advantageous aspect of polymer hydrogels is that they can undergo reversible volume change, \ie gel --- solution volume phase transitions in response to external stimuli.
 This aspect causes hydrogels to be labeled as ‘smart’ materials.
@@
 
-Li \etal \cite{Li2011} took advantage of the smart hydrogel properties for desalination purposes. In this work, the authors used hydrogels as draw agents for FO. 
+Li \etal \cite{Li2011} took advantage of the use of smart hydrogels for desalination purposes as draw agents for FO.
 They have demonstrated that the hydrogels are able to absorb water across the FO membrane due to their swelling and osmotic pressure and
 allow dewatering under the influence of stimuli (thermal and/or mechanical), due to their insoluble cross-linked polymer network.
-They have proposed the use of hydrogel based on thermoresponsive polyelectrolyte~--- copolymer of poly-N-isopropyl acrylamide (p-NIPAAm) and polyacrylic acid (p-AA).
-This gel network is either hydrophilic or hydrophobic, depending on the temperature.
-Such gel accumulates water inside the network in its hydrophilic state, but it releases the water out in its hydrophobic state.
+Li \etal have proposed the use of hydrogel based on thermoresponsive polyelectrolyte~--- copolymer of poly-N-isopropyl acrylamide (p-NIPAAm) and polyacrylic acid (p-AA).
+Depending on the temperature this gel network is either hydrophilic or hydrophobic, so it accumulates water inside the network in its hydrophilic state, but it releases the water out in its hydrophobic state.
 
@@
 Such a view on hydrogels was employed in a series of works by the group of prof. Wilhelm (see for example \cite{Arens_2017,Fengler_2020}).
-The authors of these works proposed to get rid of the osmotic membrane and simply use only micro filtration to compress the hydrogel squeezing out the accumulated inside the gel solution. 
+The authors of these works proposed to get rid of the osmotic membrane and simply use only microfiltration to compress the hydrogel squeezing out the accumulated inside the gel solution.
 In their method, the deswollen hydrogel was first equilibrated with saline water feed.
@@
 Then it was taken out from the feed solution and mechanically squeezed by means of a microfiltration membrane.
-They have found that the brine, which was squeezed out, had lower salinity than the feed water.
+The squeezed-out brine was found, to have lower salinity than the feed water.
 
-Similar approach was used by Ali \etal \cite{Ali2015}. 
+A similar approach was used by Ali \etal \cite{Ali2015}.
 Here the authors used the thermosensitive gel (based on copolymers p-NIPAAm and p-AA), and instead of physical compression, the dewatering was done by an external heating stimulus (sunlight).
-The gel was equilibrated with feed water during the night, and, at daytime, under sunlight, the gel was shrinking and releasing the solution.
+The gel was equilibrated with feed water during the night, and, in the daytime, under sunlight, the gel was shrinking releasing the solution.
 
 \subsection{Physics behind the desalination process}
-Since the polyelectrolyte gel has its own charges and its own neutralizing counterions, the density of mobile ions (which are able to freely enter and leave the gel) inside the gel network appears to be smaller than their density outside the gel.
-Therefore the internal solution in the gel has lower density of mobile ions than the solution outside. 
+Since the polyelectrolyte gel has its charges and its neutralizing counterions, the density of mobile ions (which can freely enter and leave the gel) inside the gel network appears to be smaller than their density outside the gel.
+Therefore the internal solution in the gel has a lower density of mobile ions than the solution outside.
 In that sense, the gel acts as an osmotic membrane separating solutions \cite{Rud2020}.
@@
 \begin{equation}
-\frac{\ccl\gel}{\cs}=\frac{\cs}{\cna\gel}=\sqrt{1+\left(\frac{\alpha}{2\cs\Vgel}\right)^{2}}\pm\frac{\alpha}{2\cs\Vgel}
+\frac{\ccl\gel}{\cs}=\frac{\cs}{\cna\gel}=\sqrt{1+\left(\frac{\alpha}{2\cs\vgel}\right)^{2}}\pm\frac{\alpha}{2\cs\vgel}
 \end{equation}
 where $\ccl\gel$ and $\cna\gel$ are the concentrations of monovalent anions and cations in the internal solution,
-$\cs$ is the salinity of external solution,  $\Vgel$ is the gel molar volume (inverse density of gel segments)
-and $\alpha$ is ionization degree (in the case of our study $\alpha=1$). 
-The $\pm$ sign in the formula accounts for the sign change for the cases of polyanion or polycation gels.
+$\cs$ is the salinity of the external solution, $\vgel$ is the gel molar volume (inverse density of gel segments)
+and $\alpha$ is the ionization degree (in the case of our study $\alpha=1$).
+The ``$\pm$'' sign in the formula accounts for the sign change for the cases of polyanion or polycation gels.
 
-As shown in \cite{Li_2011,Ali_2015,Arens_2017,Fengler_2020}, the solution of lower salinity can be extracted from the gel by means of compression and/or other stimulus, provided that the charge in the gel remains constant.
+As shown in \cite{Li2011, Ali2015, Arens_2017, Fengler_2020}, the solution of lower salinity can be extracted from the gel by means of compression and/or other stimuli, provided that the charge in the gel remains constant.
 In the case of weak polyelectrolyte (pH-sensitive) gel, the compression discharges the gel and therefore the neutralizing counterions leave out the gel, diminishing the desalination effect \cite{Rud2018}.
@@
 Nevertheless, in this study, we model the compression of the gel limiting ourselves to low compression rates, less than 5 bar, and studied how the compression of the gel affects the surrounding salinity.
-We modelled the desalination process, as a cascade of step-by-step gel swellings and compressions, driving the salinity of the supernate down to potable water.
+We modeled the desalination process, as a cascade of step-by-step gel swellings and compressions, driving the salinity of the supernate down to potable water.
+
+\section{Model and methods\label{sec: theory}}
 
 % water desalination technologies and Gibbs ensemble (https://doi.org/10.3390/nano10020293 \cite{erdos2020}).
-
-\section{Model and methods\label{sec: theory}}
 
@@
 the \emph{closed system} implies that the gel is in equilibrium with a \textbf{finite} reservoir of an aqueous solution.
+
+By thermodynamic equilibrium, we assume that the gel freely exchanges ions with the reservoir.
+Thus, the \emph{open system} implies the grand canonical ensemble of mobile ions, in which the change of free energy due to ion exchange is accounted for by their chemical potential.
+The \emph{closed system} is the Gibbs ensemble of ions moving between two volumes of the gel phase and the supernatant.
 
@@
 
-In the \emph{closed system} a the gel exchanges particles with explicit finite reservoir box. 
+In the \emph{closed system} the gel exchanges particles with explicit finite reservoir box. 
 The total number of ion species in both boxes is fixed, whereas the density of ions in extrernal reservoir is defined by thermodynamic equilibrium between the two subvolumes (see \reffig{fig: closed}.
-The Monte Carlo sampling of the distribution of ions between the subvolumes performed in a way similar to described in \cite{Panagiotopoulos1988b}.
-\todo{add here that citation about Gibbs ensemble}
+The Monte Carlo sampling of the distribution of ions between the subvolumes performed in a way similar to described in \cite{Panagiotopoulos1988b, Erdos2020}.
 
@@
 Using the data obtained from simulations we calculate  
-$\vgel$ --- molar volume of the gel, \ie the volume of the gel per one mol of gel segments, $\vgel = \Vgel / \Ngel$;
-$\Pgel$ --- partial pressure of the gel, \ie the pressure that needs to be applied to the gel via a solvent permeable filter to compress the gel to a specific molar volume;
 $\cs$ --- the density of ions in  the outside volume;
-and $\ncl$ --- the total amount of the ions in both volumes divided by the total volume of both boxes, $\ncl = \Ncl/\Vbox$
+$\vgel$ --- molar volume of the gel, \ie the volume of the gel per one mol of gel segments, $\vgel = \Vgel / \Ngel$,
+$\ncl$ --- the total amount of the ions in both volumes divided by the total volume of both boxes, $\ncl = \Ncl/\Vbox$ and
+$\Pgel$ --- partial pressure of the gel, \ie the pressure that needs to be applied to the gel via a solvent permeable filter to compress the gel to a specific molar volume; This pressure is 
+We obtain the \emph{partial pressure} as a difference between the presure in gel and in the outer volume $\Pgel=P_\mathrm{gel} - \Pout$.
+%$\Pout$, in turn, we obtained from a separate simulation of a reservoir, containing ionic gas in equilibrium with the bath of the same salinity $\cs$.
 
-$\Vbox$ was chosen to be close to the gel free swelling equilibrium, that to the the state when $\Pgel = 0$. 
-In order to obtain the value $\Vbox$ we perform the set of open system simulations for various $\Vgel$. That value of $\Vgel$, at which $\Pgel$ is closest to zero we choose as $\Vbox$.
-Then as soon as $\Vbox$ is defined we perform the compression of the gel in closed system decreasing the $\Vgel$ starting from $\Vbox$ and correspondingly increasing the outer volume $\Vout$.
-
-\todo{We have the "Gibbs ensemble" in the title, and this term is not used in the manuscript at all.
-TODO concise description of Gibbs ensemble, solving the task to Reviewer 2, Q5 and Q7}
+The volume $\Vbox$ was chosen to be close to the gel free swelling equilibrium, that is to the state where $\Pgel = 0$.
+In order to obtain the value $\Vbox$ we perform the set of open system simulations for various $\Vgel$.
+That value of $\Vgel$, at which $\Pgel$ is closest to zero we choose as $\Vbox$.
+Then, as soon as $\Vbox$ is defined, we perform the compression of the gel in \emph{closed system} varying values of $\Vgel<\Vbox$ and $\Vout= \Vbox - \Vgel$.
 
@@
 Each simulation returned the averaged values of pressures, $P_\mathrm{gel}$, and the number of $\cl$ ions, present in the simulation box, $\Ncl\gel$.
-
-In order to get the \emph{partial pressure} of the gel, we subtracted from $P_\mathrm{gel}$ the osmotic pressure of ions in the reservoir: $\Pgel=P_\mathrm{gel} - \Pout$.
-$\Pout$, in turn, we obtained from a separate simulation of a reservoir, containing ionic gas in equilibrium with the bath of the same salinity $\cs$.
 
@@
 \end{equation}
-\todo{the equation must be supported by referrence}
 Here, in the table, we present the absolute values of the work, 
@@
 We are aware that the concept introduced in this simulation study need to be experimentally verified.
+Therefore, in the future, we want to focus on experimental aspects of desalination based on polyacidic gel compression.
 

### 2022-09-16 gibbs.tex
hybrid

@@
 To sample mechanical properties of the gel and reservoir we use MD simulation, whereas to sample the ions distribution between the gel and a reservoir we use MC simulation.
-The details of this hybryd MCMD computational technique can be found in our previous studies of polyelectrolytes in open system \cite{Rud2020, Rud2022, Landsgesel2020a}.
+The details of this hybrid MCMD computational technique can be found in our previous studies of polyelectrolytes in open system \cite{Rud2020, Rud2022, Landsgesel2020a}.
 

### 2022-09-16 MDPI/response_letter.tex
finished the revision

--- 2022-09-14 MDPI/response_letter.tex
@@
 \begin{itemize}
-    \item 
-    \item 
-    \item 
-    \item 
+    \item Minor changes in title of the article.
+    \item The rewritten abstract and introduction.
+    \item Added the detailed explanation of model and methods used in the study.
+    \item Minor changes in Figures.
+
 \end{itemize}
 
-We believe that, after considering the modifications in response to reviewer comments, you will find our manuscript suitable for publication in Desalination.
+We also attache the pdf file reflecting the difference between the current version of the manuscript and the submitted one.
+
+We believe that, after considering the modifications in response to reviewer comments, you will find our manuscript suitable for publication in Gels.
 
@@
 \item \textit{The main findings of your results should be highlighted in abstract}
-We have rewritten the abstract. The abstract now contains main findings of our paper.
+
+We have rewritten the abstract.
 
 \item \textit{Please do not separate introduction in three sections combine with problem and technology you used and challenges and your solutions.}
+
+We have rewritten the Introduction section.
+We wanted to keep the separation of the Introduction section into the respective subsections because the Introduction is relatively lengthy, so we believe that dividing it into subsections reduces its readability.
 
@@
 \item \textit{All formula and models should be supported with reference for instant equation 3.}
-Added todonote
+Corrected
 
 \item \textit{In page 6, please remove the footer, it is not a book to describe issues below}.\\
-Corrected. Now this sentence is appears in text (in brackets).
+Corrected. Now this sentence appears in text (in brackets).
 
 \item \textit{How do you think control factors in open system such as pressure and temperature}
+
+In our simulation, we control the volume of the simulation box and measure the pressure using the virial theorem.
+The pressure value which is depicted in the Figures assumed to be a partial pressure of the gel, which is calculated as the difference between the pressure in the gel and the pressure calculated in a separate simulation box containing only ions (with no gel).
+Temperature assumed to be constant and equal to 300 K, which is guaranteed by applying a Langevin thermostat.
 
@@
 \item \textit{Abstract needs to re-write as and please follow the IMRAD instruction.}
+
 We have rewritten the abstract. We believe that the abstract is much more attractive now.
 \item \textit{There is introduction in the abstract, however, it needs to write more about the aim of this work, method, result and conclusion.}
-We have rewritten the abstract according to your advice.
+
+Corrected
 \item \textit{Avoid to use word 'we' in the abstract as well as manuscript.}
+
 Corrected.
 \item \textit{line 247 in what table?}
-We meant Table 1. Corrected.
+
+We meant Table 1. Corrected in text.
 \item \textit{Where is the method of this work?}
-The method idea is outlined in the paragraph "Physics behind the desalination process" and described in the section "Theory behind the simulation".
-We did not want to bother the readers too much with technical aspects of the smulations, so technical details are in ESI.
+
+The method idea is outlined in the paragraph "Physics behind the desalination process" and described in the section "Model and methods". 
+%We did not want to bother the readers too much with technical aspects of the smulations, so technical details are in ESI.
 \item \textit{It is suggested that to carefully improve this manuscript as well as the writing and grammatical error.}
+
 We improved the writing style of the manuscript and corrected the grammatical errors.
+
 \item \textit{Please explain more detail about the process, how the process run and how the data could be explained and become more interesting for reader.}
+
+Added corresponding paragraph in ``Model and methods `` section
 
@@
 \item \textit{The full stop in the title should be revised.}
+
 Noted. Revised.
 \item \textit{The abstract needs to be revised and be more attractive. The research gap, novelty and main findings should be concisely mentioned in the abstract.}
+
 We have rewritten the abstract. We believe that the abstract is much more attractive now.
 \item \textit{In this current shape, the manuscript looks like a report. The authors have to revise the flow of the context to attract the readers.}
+
 We have revised and changed the manuscript to be more attractive for the readers. 
 \item \textit{The manuscript must be improved by checking once again in English and technical writing. }
+
 We improved the writing style of the manuscript and corrected the grammatical errors.
@@
 \item \textit{The whole manuscript must be supported by enough recent references. Revise the whole context.}
+
+We added more recent references.
 \item \textit{The beginning of the introduction part must be revised to be more attractive.}
-\item \textit{The authors can follow the following references to generally highlight the global contamination and environmental pollution problems at the beginning of the introduction part  \href{https://doi.org/10.1016/j.jwpe.2022.102847}{https://doi.org/10.1016/j.jwpe.2022.102847} ; \href{https://doi.org/10.1016/j.ceramint.2022.05.151}{https://doi.org/10.1016/j.ceramint.2022.05.151} ;
-\href{https://doi.org/10.3390/catal12050500}{https://doi.org/10.3390/catal12050500} ; 
-\href{https://doi.org/10.1007/s11356-022-21160-7}{https://doi.org/10.1007/s11356-022-21160-7} ; 
-\href{https://doi.org/10.3390/ma15134547}{https://doi.org/10.3390/ma15134547}. 
-Then, highlight the water desalination technologies and Gibbs ensemble (\href{https://doi.org/10.3390/nano10020293}{https://doi.org/10.3390/nano10020293}).}
+
+Corrected. We have rewritten the Introduction section.
+\item \textit{The authors can follow the following references to generally highlight the global contamination and environmental pollution problems at the beginning of the introduction part \\ \href{https://doi.org/10.1016/j.jwpe.2022.102847}{https://doi.org/10.1016/j.jwpe.2022.102847} ;\\
+\href{https://doi.org/10.1016/j.ceramint.2022.05.151}{https://doi.org/10.1016/j.ceramint.2022.05.151} ;\\
+\href{https://doi.org/10.3390/catal12050500}{https://doi.org/10.3390/catal12050500} ; \\
+\href{https://doi.org/10.1007/s11356-022-21160-7}{https://doi.org/10.1007/s11356-022-21160-7} ;\\
+\href{https://doi.org/10.3390/ma15134547}{https://doi.org/10.3390/ma15134547}. \\
+Then, highlight the water desalination technologies and Gibbs ensemble\\
+(\href{https://doi.org/10.3390/nano10020293}{https://doi.org/10.3390/nano10020293}).}
+
+Corrected. We added the citations, which are relevant to the studied problems, in their appropriate places.
 \item \textit{Authors should indicate a clear gap in knowledge which this study seeks to bridge, and potentially contribute to knowledge. }
 
+The purpose of our paper is to show that desalination using polyelectrolyte hydrogels is a cheap and therefore competitive alternative to reverse osmosis.
+We highlighted this idea in the Introduction and Conclusion sections.
 \item \textit{L 125-126, meaningless sentence. Revise the whole context.}
+
 Corrected.
 \item \textit{All sections/subsections titles must be revised to be expressive.}
+
+Corrected. We have rewritten and improved not only the Introduction, but the sections Model and Methods, Results, Conclusions as well.
 \item \textit{Statistical physics considerations including setup and calculations should be added.}
-We added the paragraph about Gibbs ensemble.
-\item \textit{The authors should identify the limitations of this study and the recommended future studies in the conclusion part.
-}
+
+We rewritten the section ``Model and methods'' and added there a detailed explanation of our methodology.
+\item \textit{The authors should identify the limitations of this study and the recommended future studies in the conclusion part.}
+
 We identified the study limitations and considered the implications and future perspectives of the study. We added the respective paragraphs.

### 2022-09-16 gibbs.tex
finished the revision

@@
 
-\subsection{Langevin Dynamics}
+\subsection{Molecular Dynamics}
 \begin{figure*}[h]
@@
 
-\subsubsection{Monte Carlo sampling in \emph{open system}}
-Monte Carlo scheme for sampling the exchange of ions in \emph{open system} is based on the formula for free energy of grand canonical ensemble.
+\subsection{Monte Carlo sampling in open system}
+Monte Carlo scheme for sampling the exchange of ions in \emph{open system} is based on the formula for free energy of grand canonical ensemble, $\Omega$
 \begin{equation}
@@
 $\ncl$ --- the total amount of the ions in both volumes divided by the total volume of both boxes, $\ncl = \Ncl/\Vbox$ and
-$\Pgel$ --- partial pressure of the gel, \ie the pressure that needs to be applied to the gel via a solvent permeable filter to compress the gel to a specific molar volume; This pressure is 
-We obtain the \emph{partial pressure} as a difference between the presure in gel and in the outer volume $\Pgel=P_\mathrm{gel} - \Pout$.
+$\Pgel$ --- \emph{partial pressure} of the gel, \ie the pressure that needs to be applied to the gel via a solvent permeable filter to compress the gel to a specific molar volume.
+We obtain the gel partial pressure as a difference between the presure in gel and in the outer volume $\Pgel=P_\mathrm{gel} - \Pout$.
 %$\Pout$, in turn, we obtained from a separate simulation of a reservoir, containing ionic gas in equilibrium with the bath of the same salinity $\cs$.
@@
 \subsection{The efficiency of desalination}
-The theoretical minimum specific energy for seawater desalination (
-%$\cs=35$ g/l, 
-$\cs\simeq0.6$ mol/l as for pure NaCl) is $\sim3.9$ kJ/l (1.1 kWh/m$^3$) for 50\% recovery \cite{Wang_2020}.
+The theoretical minimum specific energy for seawater desalination ($\cs\simeq0.6$ mol/l as for pure NaCl) is $\sim3.9$ kJ/l (1.1 kWh/m$^3$) for 50\% recovery \cite{Wang_2020}.
 This value is calculated as follows
 \begin{equation}
-W=2RT\left(\frac{c_{f}}{R_{w}}\ln\frac{c_{b}}{c_{f}}-c_{p}\ln\frac{c_{b}}{c_{p}}\right)
+W_{\mathrm{id}}=2RT\left(\frac{c_{f}}{R_{w}}\ln\frac{c_{b}}{c_{f}}-c_{p}\ln\frac{c_{b}}{c_{p}}\right)
 \label{eq:SEC}
@@
 where $R$ is a universal gas constant, $c_{f}$ is the salinity of feed water, $c_p$ is the salinity of product water and $c_b$ is the salinity of the brine, which necessarily appears in any desalination process.
-$R_{w}$ is a recovery ratio, \ie the ratio between volume of produced water and the volume of the feed water. 
+$R_{w}$ is a recovery ratio, \ie the ratio between the volume of produced water and the volume of the feed water.
 50\% recovery ratio means that one part of feed water divides into two equal volume solutions of the product water and of the brine.
 Of course, a significant amount of additional energy is required to operate the system\cite{Kim_2019}.
-It has been reported that the specific energy consumption (SEC) of reverse osmosis (RO) process is 2.5~-- 4.0 kWh/m3 (9~-- 14.4 kJ/l), which is significantly higher than its minimum specific energy.
-The SEC of a real-scale RO plant is even higher, approximately 3.5~-- 4.5 kWh/$m^{3}$ (12.6 - 16.2 kJ/L), including pre-treatment and post-treatment processes \cite{Kim_2018}. 
+It has been reported that the specific energy consumption (SEC) of the reverse osmosis (RO) process is 2.5~-- 4.0 kWh/m3 (9.0~-- 14.4 kJ/l), which is significantly higher than its minimum specific energy.
+The SEC of a real-scale RO plant is even higher, approximately 3.5~-- 4.5 kWh/$m^{3}$ (12.6 - 16.2 kJ/l), including pre-treatment and post-treatment processes \cite{Kim_2018}.
 %Because of the inherent high energy requirement for RO desalination, seawater is not commonly utilized over traditional surface water.
 
-In order to compare the efficiency of the process presented in \ref{fig: PV and CV} and \ref{fig: NV and CN} with provided values, we collect the corresponding data to the Table~\ref{tab: table}.
-The presented desalination process is a cascade of six swellings in open system, at six different (constant) salinities $\cs$, each followed by six compressions in closed system, at six different (constant) $\ncl$.
+To compare the efficiency of the desalination process presented in \reffig{fig: PV and CV} and \reffig{fig: NV and CN} with provided values, we collect the corresponding data to Table~\ref{tab: table}.
+The presented desalination process is a cascade of six swellings in an open system, at six different (constant) salinities $\cs$, each followed by six compressions in a closed system, at six different (constant) $\ncl$.
 Each swelling and compression process is presented as a row of Table~\ref{tab: table}, which is colored by matching the lines in the Figures.
-The first column of the table contains values $\cs^0$ and $\cs^5$, which stand for the supernate salinity at 0 and 5 bar compression; in open system, supernate salinity does not change, so $\cs^0$ and $\cs^5$ are presented by a single number.
+The first column of the table contains values $\cs^0$ and $\cs^5$, which stand for the supernate salinity at 0 and 5 bar compression; in an open system, supernate salinity does not change, so $\cs^0$ and $\cs^5$ are presented by a single number.
 The second column contains values of $n^0$ and $n^5$, which stand for the number of $\cl$ ions in compression volume $\Vbox$, at 0 and 5 bar pressure (divided by $\Vbox$).
-The number of ion does not change in closed system compression, thus $n^0$ and $n^5$ are the same in the corresponding rows.
-The third column shows the change of the gel volume in corresponding process, $\Delta v$. 
-The fourth column contains the work needed for the compression in the corresponding process 
-per volume of extracted solution. 
-This value is an integral of corresponding $\Pgel(\Vgel)$ dependence \citep{Atkins} 
+The number of ions does not change in closed system compression, thus $n^0$ and $n^5$ are the same in the corresponding rows.
+The third column shows the change of the gel volume in the corresponding process, $\Delta v$.
+The fourth column contains the work needed for the compression in the corresponding process per volume of extracted solution.
+This value is obtained as numerical integration of corresponding $\Pgel(\Vgel)$ dependence \citep{Atkins}
 \begin{equation}
@@
 \end{equation}
-Here, in the table, we present the absolute values of the work, 
-whereas one should keep in mind that the compression implies the work 
-is done by external force and the swelling implies that the work is done by gel.
+In this column, we presented the absolute values of the work,
+whereas one should keep in mind that compression implies, that the work is done by external force and swelling implies, that the work is done by gel.
 
@@
 \end{array}\right\rbrace $$\rotatebox{90}{\hspace{-5em}{\color{teal}\ensuremath{\begin{array}{cc}
+W^{id}= & 52.9\\
 W^{\mathrm{sim}}= & 202.8\pm3.2\\
-W^{id}= & 52.9\\
 R_{w}= & 0.54
@@
 \end{array}\right\rbrace $$\rotatebox{90}{\hspace{-5em}\ensuremath{\begin{array}{cc}
+W^{id}= & 38.2\\
 W^{\mathrm{sim}}= & 207.3\pm2.2\\
-W^{id}= & 38.2\\
 R_{w}= & 0.53
@@
 \end{array}\right\rbrace \rotatebox{90}{\hspace{-5em}\ensuremath{\begin{array}{cc}
+W^{\mathrm{id}}= & 43.8\ {\color{red}{\scriptstyle (41.0)}}\\
 W^{\mathrm{sim}}= & 222.3\pm2.5\\
-W^{\mathrm{id}}= & 43.8\ {\color{red}{\scriptstyle (41.0)}}\\
 R_{w}= & 0.52\ {\scriptstyle (0.46)}
@@
 \end{array}\right\rbrace \rotatebox{90}{\hspace{-5em}\ensuremath{\begin{array}{cc}
+W^{id}= & 66.6\ {\scriptstyle (22.0)}\\
 W^{\mathrm{sim}}= & 218.7\pm2.2\\
-W^{id}= & 66.6\ {\scriptstyle (22.0)}\\
 R_{w}= & 0.53\ {\scriptstyle (0.49)}
@@
 \end{array}\right\rbrace \rotatebox{90}{\hspace{-5em}\ensuremath{\begin{array}{cc}
+W^{id}= & 69.7\\
 W^{\mathrm{sim}}= & 227.5\pm2.3\\
-W^{id}= & 69.7\\
 R_{w}= & 0.55
@@
 
-To give a clue of comparison with ideal desalination process efficiency, the fifth column provides the values of specific energy consumption, $W^\text{id}$, which are calculated by means of \refeq{eq:SEC}, using the following procedure:
-Let§s assume the concentration of the feed solution to be $\cs^f=44.91$ mmol/l and the concentrations of product and brine solutions to be $\cs^p=31.93$ mmol/l and $\cs^b = 63.93$ mmol/l, respectively.
+To give a clue of comparison with ideal desalination process efficiency, the fifth column provides the values of ideal specific energy consumption, $W^\text{id}$, which are calculated employing \refeq{eq:SEC}, for concentrations of feed, product and brine solutions, $\cs^f$,  $\cs^p$, $\cs^b$, as indicated by curly brackets.
+For example, having $\cs^f=44.91$, $\cs^p=31.93$ and $\cs^b = 63.93$ mmol/l, (5th, 7th and 3rd rows of the table) one can imagine the following desalination process
 \begin{enumerate}
-    \item The gel, equilibrated with the feed solution, is compressed in the \emph{closed system}.
+\item First, the gel equilibrated with the feed solution, is compressed in the \emph{closed system}.
 The gel volume decreases by $\Delta v^p = 3.69$ liters and the salinity of supernate decreases from $\cs^f$ to $\cs^p$.
 The volume of the product solution is $\Delta v^p$
-    \item The squeezed gel is put back into the feed solution and is quilibrated there under pressure, so it does not swell. 
-    \item After the equilibration, the gel swells in the \emph{closed system} and the salinity of the external solution increases to the value $\cs^b$.
-    \item Finally, the gel is taken out and compressed by 5 bar in the \emph{open system} in equilibrium with the brine bath. 
-    The change of the gel volume in this process is $\Delta v^b = 3.26$ l/mol, which equals to the volume of the produced brine. 
+\item The squeezed gel is put back into the feed solution and is equilibrated there under pressure, so it does not swell.
+\item After the equilibration, the gel swells in the \emph{closed system}, so the salinity of the external solution increases to the value $\cs^b$.
+\item Finally, the gel is taken out and compressed by pressure 5bar in the \emph{open system} in equilibrium with the brine bath.
+The change of the gel volume in this process is $\Delta v^b = 3.26$ l/mol, which equals the volume of the produced brine.
 \end{enumerate}
@@
 
-The estimated $W^{id}$ values are provided in the fifth column of the table, for five triplets of $\cs^f$, $\cs^p$,$\cs^b$ values .
-$W_{\mathrm{sim}}$ is the energy calculated by integration of $\Pgel(\Vgel)$ dependencies as the sum of corresponding compressions in \emph{closed} and \emph{open} systems, $W_{\mathrm{id}}$ is the estimation based on the equation \refeq{eq:SEC} and $R_w$ is the corresponding recovery ratio.
-\todo{how the integration was performed}
-Note that calculating the $W_{\mathrm{sim}}$ we accounted for only the work done on the gel during the compression, whereas the work done by the gel itself during swelling was not taken into account.
+The estimated $W^{id}$ values are provided in the fifth column of the table, for five triplets of $\cs^f$, $\cs^p$,$\cs^b$ values.
+In the same column we provide $W_{\mathrm{sim}}$ --- the specific energy consumptions calculated by a numerical integration of $\Pgel(\Vgel)$ dependencies. 
+The provided values  $W_{\mathrm{sim}}$ are the sum of energies needed for corresponding compression processes, \ie in \emph{closed} and \emph{open} systems.
+The values $R_w$, which are also provided in 5th colum are the corresponding recovery ratios.
+
 The ratio between $W_{\mathrm{sim}}$ and $W_{\mathrm{id}}$ ranges from 3.26 to 5.43, which is comparable to that of RO.
+Note, that calculating the $W_{\mathrm{sim}}$ we accounted for only the work done on the gel during the compression, whereas the work done by the gel itself during swelling was not taken into account.
+The process, which accounts for the energy recovery was described in our previous studies \cite{Prokacheva2021, Rud2018}
 
 \subsection{Study limitations}
-Like other simulation based studies, our research has a limited validity,
-primarily resulting from the simplifications applied in the used model.
+Like other simulation based studies, our research has a limited validity, primarily resulting from the simplifications applied in the used model.
 For example, our coarse-grained model cannot differentiate polystyrene sulphonate gel from other strong polyacidic gels.

### 2022-09-16 diff.sh

@@ -1,3 +1,3 @@
-latexdiff gibbs_old.tex gibbs.tex  > diff.tex
+latexdiff gibbs_mdpi_submission1.tex gibbs.tex  > diff.tex
 latexmk -pdf -f diff.tex
 evince diff.pdf

### 2022-10-14 MDPI/proof/manuscript.v5/gels-1883243-english_edit.tex
proofreading

%  LaTeX support: latex@mdpi.com 
%  For support, please attach all files needed for compiling as well as the log file, and specify your operating system, LaTeX version, and LaTeX editor.

%=================================================================
\documentclass[gels,article,accept,pdftex,moreauthors]{Definitions/mdpi} 
\usepackage[labelformat=simple]{subfig}
\renewcommand\thesubfigure{\normalfont(\textbf{\alph{subfigure}})}

\usepackage[textsize=small]{todonotes}
\newcommand{\ie}{{i.e.,} }
\newcommand{\cref}{c^{\ominus}}
%\newcommand{\cs}{c_{s}}
\newcommand{\kT}{k_\mathrm{B}T}
\newcommand{\kB}{k_\mathrm{B}}
\newcommand{\lb}{l_\mathrm{B}}
%\newcommand{\NA}{N_{\mathrm{A^-}}}
\newcommand{\NA}{N_{\mathrm{A}}}
\newcommand{\muna}{\mu_\mathrm{Na^+}}

\newcommand{\mucl}{\mu_\mathrm{Cl^-}}
\newcommand{\muca}{\mu_\mathrm{Ca^{2+}}}
\newcommand{\muh}{\mu_\mathrm{H^+}}
\newcommand{\mua}{\mu_\mathrm{A^-}}
\newcommand{\muha}{\mu_\mathrm{HA}}
\newcommand{\muoh}{\mu_\mathrm{OH}}

\newcommand{\cna}{c_\mathrm{Na^+}}
\newcommand{\ccl}{c_\mathrm{Cl^-}}
\newcommand{\cca}{c_\mathrm{Ca^{2+}}}
\newcommand{\ch}{c_\mathrm{H^+}}
\newcommand{\cp}{c_\mathrm{p}}
\newcommand{\nna}{n_\mathrm{Na^+}}
\newcommand{\ncl}{n_\mathrm{Cl^-}}
\newcommand{\Nna}{N_\mathrm{Na^+}}
\newcommand{\Ncl}{N_\mathrm{Cl^-}}

\newcommand{\ncleq}{\widetilde{N}_\mathrm{Cl^-}}
\newcommand{\nca}{N_\mathrm{Ca^{2+}}}

\newcommand{\superin}{^\mathrm{in}}
\newcommand{\subin}{_\mathrm{in}}
\newcommand{\subi}{_\mathrm{i}}

\newcommand{\gel}{^\mathrm{gel}}
\newcommand{\tot}{^\mathrm{tot}}
\newcommand{\out}{^{\mathrm{out}}}
\newcommand{\coh}{c_\mathrm{OH}}
\newcommand{\bulk}{^{\mathrm{b}}}
\renewcommand{\H}{\mathrm{H^+}}
\newcommand{\A}{\mathrm{A^-}}
\newcommand{\AH}{\mathrm{AH}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.

\newcommand{\cl}{\mathrm{Cl^-}}
\newcommand{\br}{\mathrm{Br^-}}
\newcommand{\na}{\mathrm{Na^+}}
\newcommand{\h}{\mathrm{H^+}}
\newcommand{\ka}{\mathrm{K^+}}
\newcommand{\oh}{\mathrm{OH^-}}
\newcommand{\ca}{\mathrm{Ca^{2+}}}
\newcommand{\mg}{\mathrm{Mg^{2+}}}

\newcommand{\Ka}{K_{\mathrm{A}}}
\newcommand{\pKa}{\mathrm{p}\Ka}
\newcommand{\pK}{\mathrm{p}K}
\newcommand{\pH}{\mathrm{pH}}
\newcommand{\mol}{\mathrm{mol}}
\newcommand{\molperl}{\mathrm{mol/L}}
\newcommand{\kg}{\mathrm{kg}}
\newcommand{\res}{^{\mathrm{res}}}
\newcommand{\pHres}{\pH\res}
\newcommand{\pHgel}{\pH\gel}
\newcommand{\cs}{c_{\mathrm{s}}}
%\newcommand{\cs}{c_{\mathrm{salt}}}
\newcommand{\csres}{\cs\res}
%\newcommand{\Vgel}{V\gel}
\newcommand{\Vgel}{V_\mathrm{gel}}
\newcommand{\vgel}{v_\mathrm{gel}}
\newcommand{\Egel}{E_\mathrm{gel}}
\newcommand{\Sgel}{S_\mathrm{gel}}
%\newcommand{\Vgel}{V}
\newcommand{\Ngel}{N_\mathrm{gel}}
%\newcommand{\Vgeleq}{\widetilde{V}_\mathrm{gel}}}
%\newcommand{\Pgel}{P_\mathrm{gel}}
\newcommand{\Pgel}{\Pi}
\newcommand{\Pres}{P_\mathrm{res}}
\newcommand{\Pout}{P_\mathrm{out}}
\newcommand{\Vout}{V_\mathrm{out}}
\newcommand{\Eout}{E_\mathrm{out}}
\newcommand{\Sout}{S_\mathrm{out}}
%\newcommand{\Vbox}{V_\mathrm{box}}
\newcommand{\Vbox}{V_0}
\newcommand{\PE}{polyelectrolyte{}}

\newcommand{\reffig}[1]{Figure~\ref{#1}}
\newcommand{\refeq}[1]{Equation~(\ref{#1}){}}
\newcommand{\etal}{{et al.}{}}

% For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal and change "submit" to "accept". The document class line would be, e.g., \documentclass[preprints,article,accept,moreauthors,pdftex]{mdpi}. This is especially recommended for submission to arXiv, where line numbers should be removed before posting. For preprints.org, the editorial staff will make this change immediately prior to posting.

%--------------------
% Class Options:
%--------------------
%----------
% journal
%----------
% Choose between the following MDPI journals:
% acoustics, actuators, addictions, admsci, adolescents, aerospace, agriculture, agriengineering, agronomy, ai, algorithms, allergies, alloys, analytica, animals, antibiotics, antibodies, antioxidants, applbiosci, appliedchem, appliedmath, applmech, applmicrobiol, applnano, applsci, aquacj, architecture, arts, asc, asi, astronomy, atmosphere, atoms, audiolres, automation, axioms, bacteria, batteries, bdcc, behavsci, beverages, biochem, bioengineering, biologics, biology, biomass, biomechanics, biomed, biomedicines, biomedinformatics, biomimetics, biomolecules, biophysica, biosensors, biotech, birds, bloods, blsf, brainsci, breath, buildings, businesses, cancers, carbon, cardiogenetics, catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, chemproc, children, chips, cimb, civileng, cleantechnol, climate, clinpract, clockssleep, cmd, coasts, coatings, colloids, colorants, commodities, compounds, computation, computers, condensedmatter, conservation, constrmater, cosmetics, covid, crops, cryptography, crystals, csmf, ctn, curroncol, currophthalmol, cyber, dairy, data, dentistry, dermato, dermatopathology, designs, diabetology, diagnostics, dietetics, digital, disabilities, diseases, diversity, dna, drones, dynamics, earth, ebj, ecologies, econometrics, economies, education, ejihpe, electricity, electrochem, electronicmat, electronics, encyclopedia, endocrines, energies, eng, engproc, ent, entomology, entropy, environments, environsciproc, epidemiologia, epigenomes, est, fermentation, fibers, fintech, fire, fishes, fluids, foods, forecasting, forensicsci, forests, foundations, fractalfract, fuels, futureinternet, futureparasites, futurepharmacol, futurephys, futuretransp, galaxies, games, gases, gastroent, gastrointestdisord, gels, genealogy, genes, geographies, geohazards, geomatics, geosciences, geotechnics, geriatrics, hazardousmatters, healthcare, hearts, hemato, heritage, highthroughput, histories, horticulturae, humanities, humans, hydrobiology, hydrogen, hydrology, hygiene, idr, ijerph, ijfs, ijgi, ijms, ijns, ijtm, ijtpp, immuno, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jal, jcdd, jcm, jcp, jcs, jdb, jeta, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmp, jmse, jne, jnt, jof, joitmc, jor, journalmedia, jox, jpm, jrfm, jsan, jtaer, jzbg, kidney, kidneydial, knowledge, land, languages, laws, life, liquids, literature, livers, logics, logistics, lubricants, lymphatics, machines, macromol, magnetism, magnetochemistry, make, marinedrugs, materials, materproc, mathematics, mca, measurements, medicina, medicines, medsci, membranes, merits, metabolites, metals, meteorology, methane, metrology, micro, microarrays, microbiolres, micromachines, microorganisms, microplastics, minerals, mining, modelling, molbank, molecules, mps, msf, mti, muscles, nanoenergyadv, nanomanufacturing, nanomaterials, ncrna, network, neuroglia, neurolint, neurosci, nitrogen, notspecified, nri, nursrep, nutraceuticals, nutrients, obesities, oceans, ohbm, onco, oncopathology, optics, oral, organics, organoids, osteology, oxygen, parasites, parasitologia, particles, pathogens, pathophysiology, pediatrrep, pharmaceuticals, pharmaceutics, pharmacoepidemiology, pharmacy, philosophies, photochem, photonics, phycology, physchem, physics, physiologia, plants, plasma, pollutants, polymers, polysaccharides, poultry, powders, preprints, proceedings, processes, prosthesis, proteomes, psf, psych, psychiatryint, psychoactives, publications, quantumrep, quaternary, qubs, radiation, reactions, recycling, regeneration, religions, remotesensing, reports, reprodmed, resources, rheumato, risks, robotics, ruminants, safety, sci, scipharm, seeds, sensors, separations, sexes, signals, sinusitis, skins, smartcities, sna, societies, socsci, software, soilsystems, solar, solids, sports, standards, stats, stresses, surfaces, surgeries, suschem, sustainability, symmetry, synbio, systems, taxonomy, technologies, telecom, test, textiles, thalassrep, thermo, tomography, tourismhosp, toxics, toxins, transplantology, transportation, traumacare, traumas, tropicalmed, universe, urbansci, uro, vaccines, vehicles, venereology, vetsci, vibration, viruses, vision, waste, water, wem, wevj, wind, women, world, youth, zoonoticdis

%---------
% article
%---------
% The default type of manuscript is "article", but can be replaced by: 
% abstract, addendum, article, book, bookreview, briefreport, casereport, comment, commentary, communication, conferenceproceedings, correction, conferencereport, entry, expressionofconcern, extendedabstract, datadescriptor, editorial, essay, erratum, hypothesis, interestingimage, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, studyprotocol, systematicreview, supfile, technicalnote, viewpoint, guidelines, registeredreport, tutorial
% supfile = supplementary materials

%----------
% submit
%----------
% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted. This will only make changes to the frontpage (e.g., the logo of the journal will get visible), the headings, and the copyright information. Also, line numbering will be removed. Journal info and pagination for accepted papers will also be assigned by the Editorial Office.

%------------------
% moreauthors
%------------------
% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.

%---------
% pdftex
%---------
% The option pdftex is for use with pdfLaTeX. If eps figures are used, remove the option pdftex and use LaTeX and dvi2pdf.

%=================================================================
% MDPI internal commands
\firstpage{1} 
\makeatletter 
\setcounter{page}{\@firstpage} 
\makeatother
\pubvolume{1}
\issuenum{1}
\articlenumber{0}
\pubyear{2022}
\copyrightyear{2022}
\externaleditor{Academic Editor: \hl{Firstname Lastname}} %MDPI: please add the Academic Editor
\datereceived{9 August 2022} 
%\daterevised{} % Only for the journal Acoustics
\dateaccepted{10 October 2022} 
\datepublished{} 
%\datecorrected{} % Corrected papers include a "Corrected: XXX" date in the original paper.
%\dateretracted{} % Corrected papers include a "Retracted: XXX" date in the original paper.
\hreflink{https://doi.org/} % If needed use \linebreak
%\doinum{}
%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
%\pdfoutput=1

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, soul, multirow, microtype, tikz, totcount, changepage, attrib, upgreek, cleveref, amsthm, hyphenat, natbib, hyperref, footmisc, url, geometry, newfloat, caption

%=================================================================
%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).

%=================================================================
% Full title of the paper (Capitalized)
%\Title{Water desalination using polyelectrolyte hydrogel. Gibbs ensemble modeling}
\Title{Water Desalination Using Polyelectrolyte Hydrogel: Gibbs~Ensemble Modeling}

% Alternative titles
%\Title{What the Gibbs ensemble modeling says about water desalination using polyelectrolyte hydrogel}
%\Title{Water desalination using polyelectrolyte hydrogel from the Gibbs ensemble modeling point of view}

% MDPI internal command: Title for citation in the left column
\TitleCitation{Water Desalination Using Polyelectrolyte Hydrogel: Gibbs Ensemble Modeling}

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0003-3412-7707} % Add \orcidA{} behind the author's name
\newcommand{\orcidauthorB}{0000-0003-3616-3285} % Add \orcidB{} behind the author's name
\newcommand{\orcidauthorC}{0000-0002-8501-0464} % Add \orcidB{} behind the author's name

% Authors, for the paper (add full first names)
\Author{Mikhail Laktionov %MDPI: Please carefully check the accuracy of names and affiliations. 
%MDPI: The name of this author is different from the submitting system. Please confirm which one is correct.
 $^{1, 2}$\orcidA{}, Lucie Nová $^{1}$\orcidB{} and Oleg V. Rud $^{1, 3}$*\orcidC{}}

\keyword{polyelectrolye hydrogel; simulation; desalination} 
%\longauthorlist{yes}

% MDPI internal command: Authors, for metadata in PDF
\AuthorNames{Mikhail Laktionov, Lucie Nová and Oleg V. Rud}

% MDPI internal command: Authors, for citation in the left column
\AuthorCitation{Laktionov, M.; Nová, L.; Rud, O.V.}
% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Department of Physical and Macromolecular Chemistry, Faculty of Science, Charles University in Prague, Prague 12800, Czech Republic
; miklakt@gmail.com (M.L.); lucie.nova@natur.cuni.cz (L.N.)\\
$^{2}$ \quad Saint-Petersburg National Research University of Information Technologies, Mechanics and Optics, Saint-Petersburg 197101, Russia\\
$^{3}$ \quad Institute of Macromolecular Compounds of Russian Academy of Sciences, Saint-Petersburg 199004, Russia}

% Contact information of the corresponding author
\corres{Correspondence: oleg.rud@natur.cuni.cz}

% Current address and/or shared authorship
%\firstnote{Current address: Affiliation 3.} 
%\secondnote{These authors contributed equally to this work.}
% The commands \thirdnote{} till \eighthnote{} are available for further notes

%\simplesumm{} % Simple summary

%\conference{} % An extended version of a conference paper

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{
Polyelectrolyte hydrogels can absorb a large amount of water across an osmotic membrane as a result of their swelling pressure.
On the other hand, the insoluble cross-linked hydrogel network enables dewatering under the influence of external (thermal and/or mechanical) stimuli.
Moreover, from a thermodynamic perspective, a polyelectrolyte hydrogel is already an osmotic membrane.
These properties designate hydrogels as excellent candidates for use in desalination, at the same time avoiding the use of expensive membranes.
In this article, we present our recent theoretical study of polyelectrolyte hydrogel usage for water desalination.
Employing a coarse-grained model and the Gibbs ensemble, we modeled the thermodynamic equilibrium between the coexisting gel phase and the supernate aqueous salt solution phase.
We performed a sequence of step-by-step hydrogel swellings and compressions in \emph{open} and \emph{closed} systems, \ie in equilibrium with a large and with a comparably small reservoir of aqueous solution.
The swelling in an \emph{open system} removes ions from the large reservoir, whereas the compression in a \emph{closed system} decreases the salt concentration in the small reservoir.
We modeled this stepwise process of continuous decrease of water salinity from seawater up to freshwater concentrations and estimated the energy cost of the process to be comparable to that of reverse osmosis.%as 38.2 J per production of 1 L of potable water, which is comparable with reverse osmosis.
}

% Keywords
%AE keywords are missing

% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
%\PACS{J0101}
%\MSC{}
%\JEL{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Diversity
%\LSID{\url{http://}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Applied Sciences
%\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work. This section is not mandatory.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Data
%\dataset{DOI number or link to the deposited data set if the data set is published separately. If the data set shall be published as a supplement to this paper, this field will be filled by the journal editors. In this case, please submit the data set as a supplement.}
%\datasetlicense{License under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Toxins
%\keycontribution{The breakthroughs or highlights of the manuscript. Authors can write one or two sentences to describe the most important part of the paper.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Encyclopedia
%\encyclopediadef{For entry manuscripts only: please provide a brief overview of the entry title instead of an abstract.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Advances in Respiratory Medicine
%\addhighlights{yes}
%\renewcommand{\addhighlights}{%
%	\begin{itemize}[labelsep=2.5mm]
%		\item This is an obligatory section in ``Advances in Respiratory Medicine'', whose goal is to increase the discoverability and readability of the article via search engines and other scholars.
%		\item Highlights consist of a short collection of (3–6) bullet points that capture the gap in knowledge the manuscript is addressing, as well as breakthroughs and other important points.
%		\item The Highlights section may also be used to showcase a new method used during the study (if any).
%	\end{itemize}
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\setcounter{section}{-1} %% Remove this when starting to work on the template.

\section{Introduction\label{sec: intro}}
Wastewater treatment and technology are one of the greatest concerns of modern society and must dispose of both biological \cite{guesmi2022} and chemical \cite{baaloudj2022_1,shahzad2022} pollutants.
Most importantly, water treatment technologies are needed for the ever-increasing demand for the production of potable water from brine, \ie for desalination.

\subsection{Water Desalination Technologies}
Two basic approaches for separating water from salt are present in modern desalination technology \cite{Miller2003,Curto2021}.

The first approach is distillation, which uses heat to cause a phase change of the water to vapor. 
The vapor phase is separated from the brine and condenses to liquid fresh water. 
The released condensation energy is directed back to heat the feed solution.
Distillation was the first desalination technique conducted on a large commercial scale and still accounts for a large portion of the modern world’s desalination capacity.

The second approach is to physically separate the brine components using an osmotic membrane through which only water molecules can pass; the water molecules move in response to the difference in water chemical potential.
In the context of our study, we mention reverse osmosis (RO) as the major process of all modern desalination industries, and the newly emerging membrane technology is described as forward osmosis (FO) \cite{Akther2015}. 
In RO, the difference in water chemical potential originates from a difference in pressures applied to the feed and product solutions. 
In FO, the chemical potential difference is due to an addition to the solution from one side of the membrane (draw solution)---the so-called draw solutes, which lower the water chemical potential in the draw solution.

Distillation is easy and cheap technology, but it is characterized by relatively high energy costs due to the dissipation of thermal energy. 
In turn, RO uses expensive osmotic membranes that need to be replaced regularly because of scaling and fouling. 
Moreover, RO requires very high operating pressures, ranging from 20 to 200 bar, to let the water pass through the membrane. 
However, in terms of energy losses, it works close to the thermodynamic limit.
Thus, theoretically, for each ion pair transferred from freshwater to saltwater, RO consumes only the energy equal to the difference between the chemical potentials of the transferred ions.

The absence of large hydraulic pressure in FO (unlike in RO) reduces the energy consumption in pumping and decreases membrane scaling and fouling, therefore significantly increasing the lifetime of the membranes. 
In FO, the draw solutes (agents) are dispersed and/or dissolved in water to form homogeneous draw solutions. 
The correct choice of draw agents is of paramount importance. 
As an osmotically driven process, the draw solute is expected to significantly reduce the water chemical potential and consequently generate high osmotic pressure. 
On the other hand, the draw solute is expected to be easily separated from water \cite{Cai2016}.

\subsection{Hydrogels for Desalination}
Hydrogels are three-dimensional networks of polymer chains that are crosslinked by either physical or chemical bonds.
They can entrap large volumes of water that are attracted by the high concentration of hydrophilic groups.
When a dehydrated or deswollen hydrogel uptakes water, its polymer chains extend, creating swelling pressure.
For example, as reported in \cite{Wack_2009}, weakly crosslinked poly(acrylic acid) (PAA) copolymers with polymer volume fractions between 0.03 and 0.30 exhibit swelling pressure ranging from \mbox{0.20--4.23~MPa}.
\emph{Polyelectrolyte} hydrogels, which carry ionic groups on the comonomer units (similar to PAA),  %Please ensure meaning has been retained.
can reject salt ions from the solution, \ie they absorb a solution of lower salinity than that of the solution with which they are equilibrated. %Please ensure meaning has been retained.

An important advantageous aspect of polymer hydrogels is that they can undergo reversible volume change, \ie gel--solution volume phase transitions in response to external stimuli.
This aspect causes hydrogels to be labeled as ‘smart’ materials.
Many physical and chemical stimuli have been applied to induce various responses in such smart hydrogels, in particular, to change them from hydrophilic to hydrophobic, thereby releasing water.
The physical stimuli include: temperature, solvent composition, light, mechanical pressure, sound, and electric and/or magnetic fields, whilst the chemical (or biochemical) stimuli include pH, ionic strength, and specific molecular recognition \cite{Tanaka_1982,Serizawa_2001,Lietor_Santos_2009,Qiu_2001}.

Li \etal~\cite{Li2011} took advantage of the use of smart hydrogels for desalination purposes as draw agents for FO.
They demonstrated that hydrogels are able to absorb water across the FO membrane due to their swelling and osmotic pressure and
allow dewatering under the influence of stimuli (thermal and/or mechanical) due to their insoluble cross-linked polymer network.
Li \etal~proposed the use of hydrogels based on a thermoresponsive polyelectrolyte---a copolymer of poly-N-isopropyl acrylamide (p-NIPAAm) and polyacrylic acid (p-AA). Depending on the temperature, this gel network is either hydrophilic or hydrophobic, so it accumulates water inside the network in its hydrophilic state, but it releases water in its hydrophobic state.

From a thermodynamics perspective, the polyelectrolyte hydrogel itself is an osmotic membrane that generates a Donnan potential, which rejects ions between outer and inner solutions \cite{Wang_2014}.
Such a view of hydrogels was employed in a series of works by the group of Prof. Wilhelm (see, for example, \cite{Arens_2017,Fengler_2020}).
The authors of these works proposed to get rid of the osmotic membrane and simply use only microfiltration to compress the hydrogel, squeezing out the accumulated water  %Please ensure meaning has been retained.
inside the gel solution.
In their method, the deswollen hydrogel was first equilibrated with a saline water feed.
During equilibration, the gel swelled, absorbing water.
Then, the gel was taken out of the feed solution and mechanically squeezed by means of a microfiltration membrane.
The squeezed-out brine was found to have lower salinity than the feedwater.

A similar approach was used by Ali \etal~\cite{Ali2015}.
Here, the authors used a thermosensitive gel (based on copolymers p-NIPAAm and p-AA), and instead of physical compression, dewatering was done by external heating (sunlight).
The gel was equilibrated with feedwater during the night, and in the daytime under sunlight, the gel shrank, releasing the solution.

\subsection{Physics behind the Desalination Process}
Since polyelectrolyte gels have charges and neutralizing counterions, the density of mobile ions (which can freely enter and leave the gel) inside the gel network appears to be lower than their density outside the gel.
Therefore, the internal solution in the gel has a lower density of mobile ions than the solution outside.
In that sense, the gel acts as an osmotic membrane, separating solutions \cite{Rud2020}.
The driving force of the separation is the Donnan potential, which originates from the charges in the hydrogel network.
The difference between the densities (concentrations) of the mobile ions in the internal and external solutions
is defined by Donnan's law \cite{Rud2018}
\begin{equation}
\frac{\ccl\gel}{\cs}=\frac{\cs}{\cna\gel}=\sqrt{1+\left(\frac{\alpha}{2\cs\vgel}\right)^{2}}\pm\frac{\alpha}{2\cs\vgel}
\end{equation}
where $\ccl\gel$ and $\cna\gel$ are the concentrations of monovalent anions and cations, respectively, %Please ensure meaning has been retained.
 in the internal solution,
$\cs$ is the salinity of the external solution, $\vgel$ is the gel molar volume (inverse density of gel segments),
and $\alpha$ is the ionization degree (for our study, $\alpha=1$).
The ``$\pm$'' sign in the formula accounts for the sign change in polyanion vs. polycation gels.

As shown in \cite{Li2011, Ali2015, Arens_2017, Fengler_2020}, a solution of lower salinity can be extracted from the gel by means of compression and/or other stimuli provided that the charge in the gel remains constant.
In the case of weak polyelectrolyte (pH-sensitive) gels, compression discharges the gel, and therefore, the neutralizing counterions leave the gel, diminishing the desalination effect \cite{Rud2018}.

One can argue that the Donnan effect alone is insufficient to achieve high salt rejection~\cite{Cai2016}, and the salinity of the water squeezed from hydrogels under very high hydraulic pressure (up to 100 bar \cite{Fengler_2020}) turns out to be not much different from the initial salinity.
Indeed, the use of high hydraulic pressure diminishes all the advantages of this method over RO, and the reversibility of hydrogel swelling after strong compression remains questionable.
Nevertheless, in this study, we limit ourselves to low compression rates, less than 5 bar, when modeling the compression of the gel, and we study how compression of the gel affects the surrounding salinity.
We model the desalination process as a cascade of step-by-step gel swellings and compressions, driving the salinity of the supernate down to potable water.

\section{\highlighting{Model and Methods} %MDPI: to AE: please note that the section title in Gels Template: 1. Introduction; 2. Results and Discussion; 3. Conclusions; 4. Materials and Methods
\label{sec: theory}}

% water desalination technologies and Gibbs ensemble (https://doi.org/10.3390/nano10020293 \cite{erdos2020}).

\subsection{Open and Closed Systems}

We propose the desalination process as a cascade of gel compressions and decompressions, lowering the  supernatant salinity.
%it is worth to note that we are not limited with this process only.
In this process, the gel is supposed to be compressed/decompressed in an \emph{open system %MDPI: Please confirm if the italics should be retained.
%Oleg Rud: Confirm, let it retain
} and in a \emph{closed system}.
The compression in the \emph{open system} assumes that the gel is in thermodynamic equilibrium with a huge (effectively \textbf{infinite}) reservoir of aqueous solution \reffig{fig: open}, whereas 
the \emph{closed system} implies that the gel is in equilibrium with a \textbf{finite %MDPI: Please confirm if the bold should be retained.
%Oleg Rud: Confirm, let it retain
} reservoir of an aqueous solution \reffig{fig: closed}.

By thermodynamic equilibrium, we assume that the gel freely exchanges ions with the reservoir.
Thus, the \emph{open system} implies a grand canonical ensemble of mobile ions in which the change of free energy due to ion exchange is accounted for by their chemical potential.
The \emph{closed system} is the Gibbs ensemble of ions moving between two volumes of the gel phase and the supernatant.

Due to the huge size of the reservoir, compression of the gel in the \emph{open system} does not affect reservoir salinity, $\cs =$ $\cna=$ $\ccl=$ $\text{Const}$, whereas the number of ions entrapped in the volume $\Vbox$ changes (\reffig{fig:open and closed}a).
On the contrary, compression of the gel in the \emph{closed system} changes the salinity in the reservoir, but the total number of $\na$ and $\cl$ ions in the gel and in the reservoir, \ie in the volume $\Vbox$ (\reffig{fig:open and closed}b), remains~constant.
\begin{figure}[H]
	{\captionsetup{position=bottom,justification=centering}
	\subfloat[Open system \label{fig: open}]
	{\includegraphics[width=0.5\textwidth]{figures/gc.pdf}}
	\subfloat[Closed system \label{fig: closed}]
	{\includegraphics[width=0.5\textwidth]{figures/gibbs.pdf}}}

	\caption{The hydrogel compressed in \emph{open} and in \emph{closed} system.
		Red and blue circles represent $\na$ and$\cl$ ions. $V_0$ is the volume which gel has in free swelling equilibrium state.\label{fig:open and closed}}
\end{figure}
%In the case of \emph{open system} the gel is the grand canonical ensemle, as $\mu, V, T = \mbox{Const}$, while the case of \emph{closed system} the gel and the explicit reservoir are a variation of Gibbs ensemble \cite{Panagiotopoulos1988b} performed with constant volume for the both boxes, equal chemical potentials of ion species at constant temperature.

%Unfortunately, there is no universal computationally effective technique to sample pressure difference, volume, and number of particles at the same. 
Mechanical movement and the exchange of ions occur simultaneously in reality; however, we simulate them as alternating in a stop--run mode. 
To sample mechanical properties of the gel and reservoir, we use MD simulation, whereas to sample the ion distribution between the gel and a reservoir, we use MC simulation.
The details of this hybrid MCMD computational technique can be found in our previous studies of polyelectrolytes in open systems \cite{Rud2020, Rud2022, Landsgesel2020a}.

\subsection{Molecular Dynamics}

We model the gel as a network of 16 linear polymer chains, each consisting of 30~monomer units.
These polymer chains are connected to a diamond-like network by eight~crosslinking units.
This means there are $\Ngel=16\cdot30 + 8=488$ gel monomers in the simulation box (see \reffig{fig:diamond}).
The network is put in a simulated cubic box with volume $\Vgel$ with periodic boundary conditions, which virtually emulates an infinite polymer~network.
\begin{figure}[H]

\includegraphics[width=0.7\textwidth]{{figures/simgibbs}.pdf}\caption{Diamond-like network in the simulation box. Color code represents
the individual ion types (red: $\na$, blue: $\cl$)
and the hydrogel (gray: neutral segment ($\AH$), cyan: charged segment
($\A$)). \label{fig:diamond}}
\end{figure}
Each monomer unit of the network carries a negative elementary electric charge.
Except for the gel monomers, the monovalent co- and counter-ions, $\cl$ and $\na$, are present in the simulation box.
The total electric charge of all the particles in the box is zero; therefore the number of $\na$ ions exceeds the number of $\cl$ ions by $\Ngel$.

Each pair of particles interact via the truncated Lennard--Jones interaction potential, which imposes strong repulsion between all particles at short distances:
\begin{equation}
    \begin{split}\label{eq:LJ}
        V_\mathrm{LJ}(r) =
        \begin{cases}
            4 \varepsilon \left( \left(\cfrac{\sigma}{r}\right)^{12}
            - \left(\cfrac{\sigma}{r}\right)^6\right)
            & \mathrm{if~} r < r_\mathrm{cut}\\
            0
            & \mathrm{elsewhere}
        \end{cases},
    \end{split}
\end{equation}
where 
$r$ is the interparticle distance, 
$\sigma = 0.35~\mathrm{nm}$ is a chosen characteristic size of the particles, 
$\varepsilon = \kT$ is the depth of the potential, and 
$r_\mathrm{cut}$ is the cut-off distance beyond which the potential is set zero.

The bonds connecting the gel to a network are modeled using finite extension nonlinear elastic potential (FENE)
\begin{equation}\label{eq:fene}
V_\mathrm{FENE}(r) = -\frac{1}{2} K \Delta r_\mathrm{max}^2\ln \left[ 1 - \left(\frac{r-r_0}{\Delta r_\mathrm{max}} \right)^2 \right ],
\end{equation}
where
$r$ is the distance between the bonded segments,
$K$ is the magnitude of their interaction,
$\Delta r_{\mathrm{max}}$ is the maximal stretching length of the bond, and
$r_0$ is the equilibrium bond length.
For our simulations, we chose $K = 10 \kT/\sigma^{2}$, $\Delta r_{\mathrm{max}} = 2 \sigma$, and $r_0 = 1.0\sigma$~\cite{Jin2007}.

All the charged particles interact via Coulomb electrostatic potential:
\begin{equation}
    V_{\mathrm{EL}}=\lb\kT \cfrac{q_{1}q_{2}}{r},
\end{equation}
where $\lb$ is Bjerrum length---$\lb = 2\sigma = 0.7~\mathrm{nm}$, which corresponds to the  Bjerrum length in water at temperature $T=300~\mathrm{K}$---and $\kB$ is the Botlzman constant.
In that sense, the solvent (water) is accounted for in the model implicitly via setting up dielectric permittivity $\epsilon=80$.

We used the Langevin thermostat, \ie two additional terms for force in the equation of motion were added
\begin{equation}
\mathbf{f}_i =  -\gamma \mathbf{v}_i(t)+\sqrt{2\gamma \kT }\boldsymbol{\eta}_i(t),
\end{equation}
where the first term corresponds to constant friction, with $\gamma$ being a friction coefficient,
 and the second term corresponds to random thermal force, with $\boldsymbol{\eta}_i$ being a normally distributed random vector; $\mathbf{v}_i$ is the velocity of the $i$-th particle (for details see \cite{Grest1986}).

\subsection{Monte Carlo Sampling in an Open System}
The Monte Carlo scheme for sampling the exchange of ions in an \emph{open system} is based on the formula for free energy of grand canonical ensemble $\Omega$
\begin{equation}
    \Omega_{\mathrm{open}}=E-TS+\sum_i\mu_i N_i\label{eq:Omega-GC}
\end{equation}
where $E$ is internal energy, $T$ is temperature, $S$ is entropy, $N_i$ is the number of ions of type $i\in\{\na,\ \cl\}$, and $\mu_i$ is the corresponding chemical potential.

%Our model system represents a finite volume $V$ which exchanges particles with the bath of infinite volume.
%The infinity of the volume means, that the particle exchange between the system and the bath does not influence on the chemical potentials in the bath.
%Such ensemble is called grand canonical ensemble; the free energy in this ensemble, the Landau potential, is
The entropy $S$ is given by the Boltzmann formula~\cite{Nagle2004}
\begin{equation}
    S=\kB\sum_i\ln\frac{\Vgel^{N_i}}{N_i!}\label{eq:entropy}
\end{equation}
%\todo{for partiles without interactions}
which accounts for two contributions:
\begin{enumerate}
    \item The combinatorial entropy $S_{c}=-\kB\sum_i\ln N_i!$, which reflects the freedom of choice among the particles;
    \item The mixing entropy $S_{m}=\kB \sum_i N_i\ln \Vgel$, which reflects the freedom to place the chosen particle randomly within the simulation box. 
\end{enumerate}

$\Vgel$ is the unitless volume, \ie the volume measured in units of $\sigma^3$. 
Thus, the change of free energy associated with an exchange of ion pairs is
\begin{equation}
\Delta\Omega_\mathrm{open}=\kT\ln\prod_i\left(\Vgel^{\xi}\frac{N_i!}{\left(N_i+\xi\right)!}\right)+\xi\sum_i\mu_i+\Delta E
\label{eq: DeltaG GC}
\end{equation}
where $\xi$ is an algebraic number of inserted (or removed) ion pairs; in general, $\xi$ can be any number, but when $\xi = \pm 1$, which corresponds to addition or removal of only one ion pair,  \refeq{eq: DeltaG GC} gets simplified
\begin{equation}
    \Delta\Omega_\mathrm{open}=\kT\ln \Vgel^{2\xi} \prod_i \left(N_i+\theta(\xi)\right)^{-\xi}+\xi\sum_i\mu_i+\Delta E
\label{eq: DeltaG GC_simpl}
\end{equation}
where $\theta$ is the Heaviside function; $\theta(\xi) = 1$ if $\xi=+1$; $\theta(\xi) = 0$ if $\xi=-1$.

The procedure for Monte Carlo sampling is as follows: \cite{Frenlkel2002_book}
\begin{enumerate}
	\item Propose the new configuration of the system by insertion (or deletion) of an ion pair, $\xi=\pm1$;
	\item Accept the new configuration if
	\begin{equation}
        \mathcal{R}^{\xi}<e^{\Delta\Omega_\mathrm{open}/\kT}=\Vgel^{2\xi} \prod_i \left(N_i+\theta(\xi)\right)^{-\xi}e^{\left(\Delta E+\xi\mu\right)/\kT}\label{eq: GC acceptance}
	\end{equation}
	where $\mathcal{R}$ is a uniformly distributed random number in the range between $0$ and $1$;
	\item Then, collect the number of ions, $\Nna$ and $\Ncl$, to the samples array.
\end{enumerate}

\subsection{Monte Carlo Sampling in Closed System}

In the \emph{closed system}, the gel exchanges particles with the explicit finite reservoir box. 
The total number of ion species in both boxes is fixed, whereas the density of ions in the external reservoir is defined by thermodynamic equilibrium between the two subvolumes (see \reffig{fig:open and closed}b. Monte Carlo sampling of the distribution of ions between the subvolumes is performed in a way similar to that described in \cite{Panagiotopoulos1988b, Erdos2020}.

The free energy of the Gibbs ensemble is a sum of the gel's free energy and that of the external volume.
\begin{equation}
    \Omega_{\mathrm{closed}}=\Egel-T\Sgel + \Eout-T\Sout \label{eq:Omega-GC}
\end{equation}
Using reasoning similar to that of the \emph{open system}, one can derive the change of free energy associated with ion-pair exchange 
\begin{equation}
\Delta \Omega_{\mathrm{closed}} =2 k_B T \ln \left(\frac{\Vgel}{\Vout} \right) ^ {\xi}\prod_i \left(\frac{N_{i}\gel+\theta(\xi)}{N_{i}\out+\theta(-\xi)}\right)^{-\xi} + \Delta \Egel + \Delta \Eout
\end{equation}
where $\xi$ defines the direction of the trial move, so that $\xi = -1$ when an ion pair moves from the gel to the outside volume, and  $\xi = +1$ otherwise; $\Delta \Egel$ and $\Delta \Eout$ are corresponding changes of the potential energy of the gel and the outside volumes, respectively.

Then, the procedure for sampling is the same as that of the \emph{open system}: (1) propose the move of an ion pair; (2) accept a new state if $\mathcal{R}^{\xi}<\exp({\Delta\Omega_\mathrm{closed}/\kT}$); and (3) repeat the procedure until the desired number of samples is reached.

\subsection{Algorithm}
As mentioned above, the whole simulation run consists of MD and MC subsimulations of mechanical movement of the particles and ion exchange. The algorithm follows:
\begin{enumerate}
\item Initiate the systems to simulate: the gel of volume $\Vgel$ and the external solution of volume $\Vout$;
\item Equilibrate the system, interspersing the MD and MC stages;
\item Run the MD subsimulation and collect the observables: pressure in both volumes, $P_\mathrm{gel}$, $P_\mathrm{out}$, and distances between the nodes of the gel network. The latter is needed to estimate the autocorrelation of the MD simulation;
\item Run the MC procedure, simulating ion exchange, and collect the number of ions in both boxes, 
$\Ncl\gel$ and $\Ncl\out$; 
\item Repeat the MD and MC subsimulations until the desired length of sample arrays is reached.
\end{enumerate}

Using the data obtained from simulations, we calculate  
$\cs$, the density of ions in  the outside volume;
$\vgel$, molar volume of the gel, \ie the volume of the gel per one mol of gel segments, $\vgel = \Vgel / \Ngel$;
$\ncl$, the total number of ions in both volumes divided by the total volume of both boxes, $\ncl = \Ncl/\Vbox$; and
$\Pgel$, \emph{partial pressure} of the gel, \ie the pressure that needs to be applied to the gel via a solvent-permeable filter to compress the gel to a specific molar volume.
We obtain the gel partial pressure as the difference between the pressure in the gel and the pressure in the outer volume, $\Pgel=P_\mathrm{gel} - \Pout$.
%$\Pout$, in turn, we obtained from a separate simulation of a reservoir, containing ionic gas in equilibrium with the bath of the same salinity $\cs$.

The volume $\Vbox$ was chosen to be close to the gel free-swelling equilibrium, that is, to the state where $\Pgel = 0$.
In order to obtain the value $\Vbox$, we perform a set of open system simulations for various $\Vgel$ values.
The value of $\Vgel$ at which $\Pgel$ is closest to zero is chosen as $\Vbox$.
Then, as soon as $\Vbox$ is defined, we compress the gel in the \emph{closed system} with varying values of $\Vgel<\Vbox$ and $\Vout= \Vbox - \Vgel$.

\section{Results and Discussion}

\subsection{Compression in Open System}

Initially, we run a set of simulations modeling the gel compression in an \emph{open system}, \ie in equilibrium with a big bath of certain salinity, $\cs$. 
The simulations are run for a set of different gel volumes, $\Vgel$. 
Each simulation returns the averaged values of pressures, $P_\mathrm{gel}$, and the number of $\cl$ ions present in the simulation box, $\Ncl\gel$.

The dependencies of $\Pgel$ on $\Vgel$ for the \emph{open system} for a set of various salinities are presented
in Figure \ref{fig: PV and CV}a as solid lines. 
For example, the blue solid line illustrates the compression (or swelling) of the gel in equilibrium with a reservoir of salinity $\cs=0.063$ mol/L. 
The points where the pressure equals zero, $\Pgel=0$, (indicated by filled circles) are the gel \emph{free-swelling equilibrium} states.
These states are characterized by the corresponding molar volume of the gel, $\Vgel^0$, and the amount of ions in gel \{$\Nna^0$, $\Ncl^0$\} 
(Index ``0'' stands for zero bar applied pressure).
The \emph{free-swelling equilibrium} state positions shift towards smaller volumes with increased salinity. 
In general, increased salinity shifts all the $\Pgel(V)$ curves towards smaller volumes.
This effect is well known and is typical for all branched \emph{strong} polyelectrolytes. 
It is caused by the decrease of ion osmotic pressure and by the screening of electrostatic interactions \cite{Zhulina2000, Landsgesel2020a}.
(The salinity dependence on the size of a \emph{weak} polyelectrolyte gel is in general non-monotonic. We discuss this in \cite{Rud2018}.)
\begin{figure}[H]
	\begin{adjustwidth}{-\extralength}{0cm}
	\centering
	{\captionsetup{position=bottom,justification=centering}
	\subfloat[Gel partial pressure vs. gel molar volume \label{fig: PV}]
		{\includegraphics[width=0.65\textwidth]{figures/fig_PV_pub.pdf}}
	\hspace{0.02\textwidth}
	\subfloat[Supernate salinity vs. gel molar volume\label{fig: CV}]
		{\includegraphics[width=0.65\textwidth]{figures/fig_CV_pub.pdf}}	}\end{adjustwidth}
	\caption{
	Compression of the gel in the \emph{open system} (solid lines) and in the \emph{closed system} (dotted lines). 
	Each solid curve corresponds to different salinity of the reservoir $\cs$ (see legend).
	The shaded areas limit the states with applied pressure below zero and above 5 bar.\label{fig: PV and CV}}

\end{figure}

\subsection{Compression in Closed System}
The simulations in the \emph{closed systems} start from the $\Vgel^0$ and \{$\Nna^0$, $\Ncl^0$\} values
obtained from the corresponding \emph{open system} simulations.
The simulation of gel compression in a closed volume, $\Vbox$, starts at the point $\Vbox = \Vgel^0$
and ion content $\Ncl^0$ for $\cl$ ions. The number of $\na$ ions neutralizes the system, $\Nna^0 = $$\Ncl^0 + \Ngel$.

We prepare two systems: one for simulation of the gel at the volume $\Vgel$
and the other for simulation of the supernatant solution at the volume $\Vout = \Vbox - \Vgel$.
Note that the number of $\Ncl^0$ and $\Nna^0$ ions  %Please ensure meaning has been retained.
are shared by the two volumes.

The processes of gel compression in the \emph{closed system} is depicted in Figure~\ref{fig: PV and CV}a as dotted lines.
In this plot, for example, the blue dotted line illustrates the compression of the gel equilibrated with solution with salinity $\cs=0.063$ mol/L at the volume at which the gel has zero pressure. 
The volume values $\Vgel$ and $\Vout$ are comparable in the \emph{closed system} case.
Therefore, gel compression decreases the salinity in the supernate, $\cs$. 
This dependence is illustrated in \reffig{fig: PV and CV}b, where the same swelling/compression processes are displayed in different coordinates: \ie salinity of the supernate versus the gel molar volume, $\cs(\Vgel)$.
In these coordinates, all the open-system compressions show up as horizontal lines, which reflects the constant salinity, whereas the compressions in the closed system demonstrate the change of $\cs$ from $\cs^{0}=0.063$ at the zero-pressure $\Pgel$ to $\cs^{5}=0.045$~mol/L at $P\gel=5$ bar (index ``5'' stands for 5 bar).

Although the salinity during compression in the \emph{open system} remains constant, the number of ions in the compressed subsystem (\ie in the volume where the gel is compressed (or swells)) changes.
Here, the compression volume $\Vbox$ is the volume of the \emph{free-swelling equilibrium} state of the gel, $\Vbox = \Vgel^0$.
Figure \ref{fig: NV and CN}a shows number of $\cl$ ions in the volume $\Vbox$ per unit volume, $\ncl =$ $\Ncl/\Vbox$, as a function of the gel molar volume. 
The depicted values can be considered as the average density of $\cl$ ions in the compression volume $\Vbox$.

The $\ncl$-$\Vgel$ dependencies look like horizontal lines in the case of \emph{closed system} compression,
whereas $\ncl$ increases with $\Vgel$ during the compression in the \emph{open system} case. 
This implies, that the compression of the gel in the \emph{open system} pulls out the ions from the bath to the compression volume, $\Vbox$. 
And vice versa, the swelling of the gel pushes ions out to the bath.
\begin{figure}[H]
\begin{adjustwidth}{-\extralength}{0cm}
{\captionsetup{position=bottom,justification=centering}
\subfloat[Pressure vs. gel molar volume \label{fig: NV}]
{\includegraphics[width=0.65\textwidth]{figures/fig_NV_pub.pdf}}
\hspace{0.02\textwidth}
\subfloat[Salinity vs. gel molar volume\label{fig: CN}]
{\includegraphics[width=0.65\textwidth]{figures/fig_NVbox_mu_pub.pdf}}}\end{adjustwidth}
\caption{The compression of the gel in \emph{open system} (solid lines) and in \emph{closed system} (dotted lines). 
Shadowed area limit the states with applied pressure below zero and above 5 bar.
The values $N_\cl$ are the virtual numbers of present $\cl$ ions in \emph{closed system} simulation boxes.
\label{fig: NV and CN}}

%\todoi{Replace y-axis labels by $\ncl$}
\end{figure}
Finally, the same processes are depicted in Figure \ref{fig: NV and CN}b in coordinates $\ncl$---$\cs$. 
In these coordinates, both ways of the compression, in \emph{open} and in \emph{closed} systems, appear as straight vertical and horizontal lines correspondingly.

In our study, we modeled the compression of the gel in equilibrium with reservoirs of 40 different salinities, ranging from 0.001 to 0.5 mol/L. 
The \emph{open system} compressions resulted in defined free-swelling equilibrium states,
which we used as the initial conditions for the respective compressions in the \emph{closed system}. 
All the corresponding dependencies are depicted in Figures~\ref{fig: PV and CV} and \ref{fig: NV and CN} as thin grey dashed lines (some of them are highlighted and colored).
The states corresponding to $P^{gel}=0$, 5, and 10 bar pressures are marked by open circles, squares, and crosses, respectively. 
The non-shaded areas in the figures highlight the states in which the gel partial pressure ranges between the experimentally relevant values of 0 and 5 bar.

\subsection{Desalination Scheme}
It follows that compression of the gel in the \emph{closed system} affects the salinity, whereas compression in the \emph{open system} affects the number of ions in the gel subsystem. 
Here, we show how to employ these phenomena for water desalination. 
The highlighted colored lines on the plots in Figures \ref{fig: PV and CV} and \ref{fig: NV and CN} form a sequence of gel swellings and compressions, following one another and corresponding to  \emph{open} and \emph{closed} systems. 
This sequence forms the water desalination process.
Starting from swelling the gel in the \emph{open system} at high salinity ($\cs=0.091$ mol/L, solid black line), the gel is compressed in the \emph{closed system} until the pressure reaches 5 bar (dashed black line). 
Then, the same gel swells in a reservoir with slightly lower salinity in the \emph{open system} (\ie $\cs=0.064$ mol/L, light blue line). 
After swelling, the gel is compressed again with 5 bar pressure in the \emph{closed system} (dashed light blue line).  
Then, the gel swells in a reservoir of even smaller salinity ($\cs=0.045$ mol/L, solid yellow line), and so on. 
This chain of alternating swellings and compressions ends up when salinity is equal to $\cs=4\times10^{-3}$ mol/L after compression in the \emph{closed system} (dashed magenta line).

The plots in Figures \ref{fig: PV and CV} and \ref{fig: NV and CN} depict the whole process in all possible coordinate representations.
In all plots, the lines corresponding to sequential swellings and compressions during the whole desalination process resemble a 'pathway'.
In particular, the desalination process depicted in Figure~\ref{fig: NV and CN}b resembles a staircase,
where the \emph{open system} processes are horizontal lines and the \emph{closed system} processes are vertical lines.

%\begin{enumerate}
%    \item as gel partial pressure versus gel molar volume, $\Pgel(\Vgel)$ (\ref{fig: PV}), 
%    \item as supernatant salinity versus gel molar volume, $\cs(\Vgel)$ (\ref{fig: CV}),
%    \item the amount of $\cl$ ions in a compression volume versus gel volume, $\ncl(\Vgel)$ (\ref{fig: NV}), 
%    \item $\ncl$ as function of supernatant salinity.
%\end{enumerate}

%Then we repeat the simulation of hydrogel swelling in open system but setting as a salinity of the reservoir the new, obtained from the previous process, value $\cs=$ 0.045 mol/L. 
%Again, as soon as we obtain the free swelling equilibrium state (at new salinity), with corresponding new values of $V\gel$ and $\ncl$, we start simulating the compression in closed system. Now the salinity changes again, decreasing from 0.045 to 0.031 mol/L (at 5 bar). 
%These two processes are depicted by solid and dotted yellow lines in Figure~\ref{fig:fig_PV}.
%The Figure shows also the repetition of this procedure three more times until the salinity reaches the value $\cs=0.01$ mol/L. 
%The last dashed magenta line shows the compression in closed system which ends up with $\cs=4\cdot10^{-4}$ mol/L. 
%Schematically this process is depicted in the inset to the plot.

%The same process is depicted on Figure~\ref{fig:fig_CV} but in different coordinates: salinity versus volume. 
%In this coordinates the swelling in open system appear to be horizontal line, since the salinity in this process is constant. 
%Again we start from swelling in open system untill the gel reaches its free swelling equilibrium (solid blue line).
%Then the gel is compressed in closed system (dashed blue line), ending up in a state with applied to the gel pressure 5 bar. 
%In this process the surrounding solution salinitiy changes from 0.064 to 0.045 mol/L.
%Then the gel again swells in open system, but at new salinity.

\subsection{The Efficiency of Desalination}
The theoretical minimum specific energy for seawater desalination ($\cs\simeq0.6$ mol/L for pure NaCl) is $\sim$$3.9$ kJ/L (1.1 kWh/m$^3$) for 50\% recovery \cite{Wang_2020}.
This value is calculated as~follows
\begin{equation}
W_{\mathrm{id}}=2RT\left(\frac{c_{f}}{R_{w}}\ln\frac{c_{b}}{c_{f}}-c_{p}\ln\frac{c_{b}}{c_{p}}\right)
\label{eq:SEC}
\end{equation}
where $R$ is the universal gas constant, $c_{f}$ is the salinity of the feedwater, $c_p$ is the salinity of the product water, $c_b$ is the salinity of the brine, which necessarily appears in any desalination process, and
$R_{w}$ is the recovery ratio, \ie the ratio of the volume of water produced and the feedwater volume. A 50\% recovery ratio means that one part feedwater divides into two equal volume solutions of product water and brine.
Of course, a significant amount of additional energy is required to operate the system \cite{Kim_2019}.
It has been reported that the specific energy consumption (SEC) of reverse osmosis (RO) is 2.5--4.0 kWh/m3 (9.0--14.4 kJ/L), which is significantly higher than its minimum specific energy.
The SEC of a real-scale RO plant is even higher, approximately 3.5--4.5~kWh/m$^{3}$ (12.6--16.2~kJ/L), including pre-treatment and post-treatment processes~\cite{Kim_2018}.
%Because of the inherent high energy requirement for RO desalination, seawater is not commonly utilized over traditional surface water.

To compare the efficiency of the desalination process presented in Figures \ref{fig: PV and CV} and \ref{fig: NV and CN} with provided values, we collect the corresponding data in Table~\ref{tab: table}.
The presented desalination process is a cascade of six swellings in an open system at six different (constant) salinities $\cs$, each followed by six compressions in a closed system at six different (constant) $\ncl$.
Each swelling and compression process is presented as a row in Table~\ref{tab: table}, which is colored by matching the lines in the figures.
The first column of the table contains values for $\cs^0$ and $\cs^5$, which stand for the supernate salinity at 0 and 5 bar compression, respectively; in an open system, supernate salinity does not change, so $\cs^0$ and $\cs^5$ are represented by a single number.
The second column contains values of $n^0$ and $n^5$, which stand for the number of $\cl$ ions in compression volume $\Vbox$ at 0 and 5 bar pressure, respectively, (divided by $\Vbox$).
The number of ions does not change in closed system compression; thus, $n^0$ and $n^5$ are the same in the corresponding rows.
The third column shows the change of the gel volume in the corresponding process, $\Delta v$.
The fourth column contains the work needed for compression in the corresponding process per volume of extracted solution.
This value is obtained as the numerical integration of corresponding $\Pgel(\Vgel)$ dependence \citep{Atkins}
\begin{equation}
W = \frac{\int_{v^0}^{v^5} \Pgel d\Vgel}{\Delta v}
\end{equation}

In this column, we present the absolute values of the work,
whereas one should keep in mind that compression implies that the work is done by external force, and swelling implies that the work is done by the gel.

For comparison with ideal desalination process efficiency, the fifth column provides values for ideal specific energy consumption, $W^\text{id}$, which are calculated employing \refeq{eq:SEC}, for the concentrations of feed, product, and brine solutions, $\cs^f$,  $\cs^p$, $\cs^b$, respectively, as indicated by curly brackets.
For example, with $\cs^f=44.91$, $\cs^p=31.93$, and $\cs^b = 63.93$~mmol/L, (fifth, seventh, and third rows of the table), one can imagine the following desalination~process
\begin{enumerate}
\item First, the gel equilibrates with the feed solution and is compressed in the \emph{closed system}.
The gel volume decreases by $\Delta v^p = 3.69$ liters, and the salinity of the supernate decreases from $\cs^f$ to $\cs^p$.
The volume of the product solution is $\Delta v^p$.
\item The squeezed gel is put back into the feed solution and is equilibrated there under pressure, so it does not swell.
\item After equilibration, the gel swells in the \emph{closed system}, so the salinity of the external solution increases to the value $\cs^b$.
\item Finally, the gel is taken out and compressed at 5 bar pressure in the \emph{open system} in equilibrium with the brine bath.
The change of the gel volume in this process is $\Delta v^b = 3.26$ L/mol, which equals the volume of the produced brine.
\end{enumerate}

\begin{table}[H]
\caption{Estimates of  %MDPI: Please confirm if the format of the table should be retained, e.g., the color of the font, the text direction, vertical line
% Oleg Rud: Confirm the colors and the directions of the table must retain
desalination efficiency. All units are calculated per one mol of gel segments. Values in brackets correspond to crossection of `red' and `orange' lines on the plots in Figures \ref{fig: PV and CV} and \ref{fig: NV and CN}.
\label{tab: table}}

\begin{adjustwidth}{-\extralength}{0cm}

		\newcolumntype{C}{>{\centering\arraybackslash}X}
\begin{tabularx}{1\fulllength}{@{\extracolsep{\fill}}ll|lc|c|l|ll}
\noalign{\hrule height 1pt}
\multicolumn{1}{l|}{\textbf{\boldmath{$c_{s}^{0}$}, mM}} & \textbf{\boldmath{$c_{s}^{5}$}, mM} & \multicolumn{1}{l|}{\textbf{\boldmath{$n_{\cl}^{0}$}, mM}} & \textbf{\boldmath{$n_{\cl}^{5}$}, mM} & \textbf{\boldmath{$\Delta \Vgel$}, L} & \textbf{\boldmath{$|W$}\textbar , J/L} & \multicolumn{2}{c}{\textbf{\boldmath{$W^{id}$}, J/L}}\tabularnewline

\noalign{\hrule height 0.5pt} 
\multirow{2}{*}{{\small{}$91.47$}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{{\small{}$57.08\pm0.122\enskip\longrightarrow$}} & \multirow{2}{*}{{\small{}2.74}} & \multirow{2}{*}{{\small{}$95.4\pm1.9$}} &  & \multirow{2}{*}{}\tabularnewline
 &  & \multicolumn{2}{r|}{{\small{}$71.75\pm0.024$}} &  &  & \multirow{8}{*}{{\small{}\hspace{-1em}}\textcolor{teal}{\small{}$\left.\begin{array}{l}
\\
\\
\\
\\
\\
\\
\\
\\
\end{array}\right\rbrace $$\rotatebox{90}{\hspace{-5em}{\color{teal}\ensuremath{\begin{array}{cc}
W^{id}= & 52.9\\
W^{\mathrm{sim}}= & 202.8\pm3.2\\
R_{w}= & 0.54
\end{array}}}}$}} & \tabularnewline
\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
\multicolumn{2}{l|}{{\small{}$89.41\pm0.23\enskip\longrightarrow$}} & \multirow{2}{*}{{\small{}56.90}} & \multirow{2}{*}{} & \multirow{2}{*}{{\small{}2.72}} & \multirow{2}{*}{{\small{}$109.1\pm1.7$}} &  & \multirow{2}{*}{}\tabularnewline
\multicolumn{2}{r|}{{\small{}$73.63\pm0.03$}} &  &  &  &  &  & \tabularnewline
\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
\multirow{2}{*}{\textcolor{teal}{\small{}63.93}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{teal}{\small{}$37.28\pm0.08\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{teal}{\small{}3.26}} & \multirow{2}{*}{\textcolor{teal}{\small{}$100.9\pm1.7$}} &  & \tabularnewline
 &  & \multicolumn{2}{r|}{\textcolor{teal}{\small{}$50.579\pm0.013$}} &  &  &  & \multirow{8}{*}{{\small{}\hspace{-1em}}\textcolor{olive}{\small{}$\left.\begin{array}{l}
\\
\\
\\
\\
\\
\\
\\
\\
\end{array}\right\rbrace $$\rotatebox{90}{\hspace{-5em}\ensuremath{\begin{array}{cc}
W^{id}= & 38.2\\
W^{\mathrm{sim}}= & 207.3\pm2.2\\
R_{w}= & 0.53
\end{array}}}$}}\tabularnewline
\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
\multicolumn{2}{l|}{\textcolor{teal}{\small{}$62.05\pm0.15\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{teal}{\small{}37.17}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{teal}{\small{}3.18}} & \multirow{2}{*}{\textcolor{teal}{\small{}$107.4\pm1.4$}} &  & \tabularnewline
\multicolumn{2}{r|}{\textcolor{teal}{\small{}$48.21\pm0.02$}} &  &  &  &  &  & \tabularnewline
\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
\multirow{2}{*}{\textcolor{olive}{\small{}44.91}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{olive}{\small{}$23.75\pm0.06\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{olive}{\small{}3.82}} & \multirow{2}{*}{\textcolor{olive}{\small{}$106.7\pm1.5$}} &  & \tabularnewline
 &  & \multicolumn{2}{r|}{\textcolor{olive}{\small{}$35.911\pm0.010$}} &  &  & \multirow{8}{*}{{\small{}\hspace{-1em}}\textcolor{red}{\small{}$\left.\begin{array}{l}
\\
\\
\\
\\
\\
\\
\\
\\
\\
\end{array}\right\rbrace \rotatebox{90}{\hspace{-5em}\ensuremath{\begin{array}{cc}
W^{\mathrm{id}}= & 43.8\ {\color{red}{\scriptstyle (41.0)}}\\
W^{\mathrm{sim}}= & 222.3\pm2.5\\
R_{w}= & 0.52\ {\scriptstyle (0.46)}
\end{array}}}$}} & \tabularnewline
\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
\multicolumn{2}{l|}{\textcolor{olive}{\small{}$43.46\pm0.12\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{olive}{\small{}24.27}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{olive}{\small{}3.91}} & \multirow{2}{*}{\textcolor{olive}{\small{}$106.4\pm1.1$}} &  & \tabularnewline
\multicolumn{2}{r|}{\textcolor{olive}{\small{}$30.795\pm0.008$}} &  &  &  &  &  & \tabularnewline
\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
\multirow{2}{*}{\textcolor{red}{\small{}31.93}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{red}{\small{}$14.66\pm0.04\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{red}{\small{}4.20}} & \multirow{2}{*}{\textcolor{red}{\small{}$107.9\pm1.4$}} &  & \tabularnewline
 &  & \multicolumn{2}{r|}{\textcolor{red}{\small{}$25.297\pm0.006$}} &  &  &  & \multirow{8}{*}{{\small{}\hspace{-1em}}\textcolor{orange}{\small{}$\left.\begin{array}{l}
\\
\\
\\
\\
\\
\\
\\
\\
\\
\end{array}\right\rbrace \rotatebox{90}{\hspace{-5em}\ensuremath{\begin{array}{cc}
W^{id}= & 66.6\ {\scriptstyle (22.0)}\\
W^{\mathrm{sim}}= & 218.7\pm2.2\\
R_{w}= & 0.53\ {\scriptstyle (0.49)}
\end{array}}}$}}\tabularnewline
\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
\multicolumn{2}{l|}{\textcolor{red}{\small{}$30.03\pm0.08\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{red}{\small{}14.55}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{red}{\small{}$\begin{array}{c}
4.17\\
{\scriptstyle (3.22)}
\end{array}$}} & \multirow{2}{*}{\textcolor{red}{\small{}$\begin{array}{c}
115.6\pm0.9\\
{\scriptstyle (57.3)}
\end{array}$}} &  & \tabularnewline
\multicolumn{2}{r|}{\textcolor{red}{\small{}$\begin{array}{c}
18.585\pm0.004\,\\
{\scriptstyle (22.32)}
\end{array}$}} &  &  &  &  &  & \tabularnewline
\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
\multirow{2}{*}{\textcolor{orange}{\small{}22.30}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{orange}{\small{}$8.84\pm0.03\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{orange}{\small{}$\begin{array}{c}
4.75\\
{\scriptstyle (3.76)}
\end{array}$}} & \multirow{2}{*}{\textcolor{orange}{\small{}$\begin{array}{c}
108.1\pm1.3\\
{\scriptstyle (68.3)}
\end{array}$}} &  & \tabularnewline
 &  & \multicolumn{2}{r|}{\textcolor{orange}{\small{}$\begin{array}{c}
\text{17.945}\pm\text{0.004}\\
{\scriptstyle (14.56)}
\end{array}$}} &  &  & \multirow{7}{*}{{\small{}\hspace{-1em}}\textcolor{magenta}{\small{}$\left.\begin{array}{l}
\\
\\
\\
\\
\\
\\
\\
\end{array}\right\rbrace \rotatebox{90}{\hspace{-5em}\ensuremath{\begin{array}{cc}
W^{id}= & 69.7\\
W^{\mathrm{sim}}= & 227.5\pm2.3\\
R_{w}= & 0.55
\end{array}}}$}} & \\[1ex]
\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
\multicolumn{2}{l|}{\textcolor{orange}{\small{}$20.74\pm0.06\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{orange}{\small{}8.83}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{orange}{\small{}$4.71$}} & \multirow{2}{*}{\textcolor{orange}{\small{}$110.8\pm0.8$}} &  & \tabularnewline
\multicolumn{2}{r|}{\textcolor{orange}{\small{}$11.082\pm0.002$}} &  &  &  &  &  & \tabularnewline
\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
\multirow{2}{*}{\textcolor{magenta}{\small{}10.90}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{magenta}{\small{}$3.00\pm0.01\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{magenta}{\small{}6.08}} & \multirow{2}{*}{\textcolor{magenta}{\small{}$106.9\pm1.1$}} &  & \tabularnewline
 &  & \multicolumn{2}{r|}{\textcolor{magenta}{\small{}9.011$\pm$0.002}} &  &  &  & \tabularnewline
\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
\multicolumn{2}{l|}{\textcolor{magenta}{\small{}$9.83\pm0.05\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{magenta}{\small{}3.12}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{magenta}{\small{}5.78}} & \multirow{2}{*}{\textcolor{magenta}{\small{}$119.4\pm1.0$}} &  & \tabularnewline
\multicolumn{2}{r|}{\textcolor{magenta}{\small{}$3.862\pm0.001$}} &  &  &  &  &  & \\[2ex]
\noalign{\hrule height 1pt}
\end{tabularx}
\end{adjustwidth}
\end{table}

Thus, the recovery ratio $R_w = \Delta v^p / (\Delta v^p + \Delta v^b) \simeq $ 0.53 and the theoretical minimum specific energy of the desalination process with corresponding $\cs^f$, $\cs^p,$ and $\cs^b$ is $W^{id} =$ 38.2~J/L (\refeq{eq:SEC}).

The estimated $W^{id}$ values are provided in the fifth column of the table for five triplets of $\cs^f$, $\cs^p$,$\cs^b$ values.
In the same column, we provide $W_{\mathrm{sim}}$---the specific energy consumption calculated by a numerical integration of $\Pgel(\Vgel)$ dependencies. 
The provided values  $W_{\mathrm{sim}}$ are the sum of energies needed for corresponding compression processes, \ie in the \emph{closed} and \emph{open} systems.
The values $R_w$, which are also provided in fifth column, are the corresponding recovery ratios.

The ratio between $W_{\mathrm{sim}}$ and $W_{\mathrm{id}}$ ranges from 3.26 to 5.43, which is comparable to that of RO.
Note that when calculating $W_{\mathrm{sim}}$, we accounted for only the work done on the gel during compression, whereas the work done by the gel itself during swelling was not taken into account. 
The process that accounts for energy recovery was described in our previous studies \cite{Prokacheva2021, Rud2018}

\subsection{Study Limitations}
Like other simulation-based studies, our research has limited validity, primarily resulting from the simplifications applied in the used model.
For example, our coarse-grained model cannot differentiate polystyrene sulphonate gel from other strong polyacidic gels.
However, these limitations are also the advantage of our model, because the results of our study
can be applied to similar systems, including polybasic gels with all the charges~reversed.

\subsection{Implications and Future Perspectives}
We are aware that the concept introduced in this simulation study needs to be experimentally verified.
Therefore, in the future, we want to focus on experimental aspects of desalination based on polyacidic gel compression.

\section{Conclusions}
\textls[-5]{We have modeled compression of a polyelectrolyte gel in thermodynamic equilibrium with a supernatant aqueous solution of limited amount.
We have shown that compression of the gel decreases the supernatant salinity.
We employed this phenomenon to model water desalination.
The desalination was done as a sequential combination of two processes:
(1) swelling of the gel in an \emph{open system}, exchanging ions with a large reservoir at constant salinity;
(2) compression of the gel in a \emph{closed system}, during which the gel exchanges ions with a small reservoir, affecting its salinity.
We estimated the energy consumption needed for producing one liter of potable water from brine and have shown that the proposed gel compression method may compete with modern desalination~technologies. %MDPI: we noticed that the supplementary file has been uploaded in submitting system. please confirm if there is a supplementary, if so, please cite it in main text and add section of supplementary materils “\supplementary{The following are available at \linksupplementary{s1}, Figure S1: title, Table S1: title, Video S1: title.} ”. Please note that the reference in supplementary should be also included in mian text.
% Oleg Rud: There is no need of supplementary materials anymore, since we added the method description into the main text.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{6pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
%\supplementary{The following supporting information can be downloaded at:  \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title.}

% Only for the journal Methods and Protocols:
% If you wish to submit a video article, please do so with any other supplementary material.
% \supplementary{The following supporting information can be downloaded at: \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title. A supporting video article is available at doi: link.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{Conceptualization, O.V.R.; methodology, M.L.; software, M.L.; validation, M.L., L.N., and O.V.R.; formal analysis, L.N.; data curation, M.L.; writing---original draft preparation, O.V.R.; writing---review and editing, L.N. All authors have read and agreed to the published version of the manuscript.
%All authors have read and agreed to the published version of the manuscript.', please turn to the  \href{http://img.mdpi.org/data/contributor-role-instruction.pdf}{CRediT taxonomy} for the term explanation. Authorship must be limited to those who have contributed substantially to the work~reported.
}

\funding{``This research was funded by Czech Science Foundation grant number 19-17847Y'' and government of the Russian Federation grant number 14.W03.31.0022. }

%\institutionalreview{\hl{~}}%MDPI: In this section, please add the Institutional Review Board Statement and approval number for studies involving humans or animals. Please note that the Editorial Office might ask you for further information. Please add ``The study was conducted according to the guidelines of the Declaration of Helsinki, and approved by the Institutional Review Board (or Ethics Committee) of NAME OF INSTITUTE (protocol code XXX and date of approval).'' OR ``Ethical review and approval were waived for this study, due to REASON (please provide a detailed justification).'' OR ``Not applicable'' for studies not involving humans or animals. You might also choose to exclude this statement if the study did not involve humans or animals.

%\informedconsent{\hl{~}}%MDPI: Any research article describing a study involving humans should contain this statement. Please add ``Informed consent was obtained from all subjects involved in the study.'' OR ``Patient consent was waived due to REASON (please provide a detailed justification).'' OR ``Not applicable'' for studies not involving humans. You might also choose to exclude this statement if the study did not involve humans. Written informed consent for publication must be obtained from participating patients who can be identified (including by the patients themselves). Please state ``Written informed consent has been obtained from the patient(s) to publish this paper'' if applicable.

%\dataavailability{\hl{~}} %MDPI: In this section, please provide details regarding where data supporting reported results can be found, including links to publicly archived datasets analyzed or generated during the study. Please refer to suggested Data Availability Statements in section ``MDPI Research Data Policies'' at \url{https://www.mdpi.com/ethics}. You might choose to exclude this statement if the study did not report any data.

%\acknowledgments{\hl{This research was supported by the Czech Science Foundation (grant 19-17847Y) and the 
%government of the Russian Federation (grant number 14.W03.31.0022).} %MDPI: The contents in acknowledgments are the same as those in funding. please confirm if it can be deleted in acknowledgments
 % Confirm it can be deleted in acknowledjements
%}

\conflictsofinterest{The authors declare no conflict of interest.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{adjustwidth}{-\extralength}{0cm}
%\printendnotes[custom] % Un-comment to print a list of endnotes

\reftitle{References}

% Please provide either the correct journal abbreviation (e.g. according to the “List of Title Word Abbreviations” http://www.issn.org/services/online-services/access-to-the-ltwa/) or the full name of the journal.
% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.

%=====================================
% References, variant A: external bibliography
%=====================================
%\bibliography{your_external_BibTeX_file}
\begin{thebibliography}{999}

\bibitem[Guesmi \em{et~al.}(2022)Guesmi, Cherif, Baaloudj, Kenfoud, Badawi,
  Elfalleh, Hamadi, Khezami, and Assadi]{guesmi2022}
Guesmi, A.; Cherif, M.M.; Baaloudj, O.; Kenfoud, H.; Badawi, A.K.; Elfalleh,
  W.; Hamadi, N.B.; Khezami, L.; Assadi, A.A.
\newblock Disinfection of corona and myriad viruses in water by non-thermal
  plasma: A review.
\newblock {\em Environ. Sci. Pollut. Res.} {\bf 2022}, {\em 29},~55321--55335.
\newblock
  https://doi.org/10.1007/s11356-022-21160-7.%}{\detokenize{10.1007/s11356-022-21160-7}}}.

\bibitem[Baaloudj \em{et~al.}(2022)Baaloudj, Badawi, Kenfoud, Benrighi, Hassan,
  Nasrallah, and Assadi]{baaloudj2022_1}
Baaloudj, O.; Badawi, A.K.; Kenfoud, H.; Benrighi, Y.; Hassan, R.; Nasrallah,
  N.; Assadi, A.A.
\newblock Techno-economic studies for a pilot-scale Bi12TiO20 based
  photocatalytic system for pharmaceutical wastewater treatment: From
  laboratory studies to commercial-scale applications.
\newblock {\em J. Water Process. Eng.} {\bf 2022}, {\em
  48},~102847.
\newblock
  https://doi.org/10.1016/j.jwpe.2022.102847.%}{\detokenize{10.1016/j.jwpe.2022.102847}}}.

\bibitem[Shahzad \em{et~al.}(2022)Shahzad, Badawi, Rehan, Khan, Khan, Shah,
  Ali, and Ismail]{shahzad2022}
Shahzad, W.; Badawi, A.K.; Rehan, Z.A.; Khan, A.M.; Khan, R.A.; Shah, F.; Ali,
  S.; Ismail, B.
\newblock Enhanced visible light photocatalytic performance of
  Sr0.3(Ba,Mn)0.7ZrO3 perovskites anchored on graphene oxide.
\newblock {\em Ceram. Int.} {\bf 2022}, {\em 48},~24979--24988.
\newblock
  https://doi.org/10.1016/j.ceramint.2022.05.151.%}{\detokenize{10.1016/j.ceramint.2022.05.151}}}.

\bibitem[Miller(2003)]{Miller2003}
Miller, J.
\newblock \emph{Review of Water Resources and Desalination Technologies}; 
Sandia National Laboratories (SNL): Albuquerque, NM, USA, 2003;
\newblock Technical Report; 
\newblock https://doi.org/10.2172/809106; 
%MDPI: Please add the name of the publisher and the location of it.
.

\newblock {\em {Physical Chemistry}}, 9th ed.; Oxford University Press:
  New York, NY, USA, 2010.
\newblock
  https://doi.org/10.2172/809106.%}{\detokenize{10.2172/809106}}}.

\bibitem[Curto \em{et~al.}(2021)Curto, Franzitta, and Guercio]{Curto2021}
Curto, D.; Franzitta, V.; Guercio, A.
\newblock A Review of the Water Desalination Technologies.
\newblock {\em Appl. Sci.} {\bf 2021}, {\em 11},~670.
\newblock
  https://doi.org/10.3390/app11020670.%}{\detokenize{10.3390/app11020670}}}.

\bibitem[Akther \em{et~al.}(2015)Akther, Sodiq, Giwa, Daer, Arafat, and
  Hasan]{Akther2015}
Akther, N.; Sodiq, A.; Giwa, A.; Daer, S.; Arafat, H.A.; Hasan, S.W.
\newblock Recent advancements in forward osmosis desalination: A~review.
\newblock {\em Chem. Eng. J.} {\bf 2015}, {\em 281},~502--522.
\newblock
  https://doi.org/10.1016/j.cej.2015.05.080.%}{\detokenize{10.1016/j.cej.2015.05.080}}}.

\bibitem[Cai and Hu(2016)]{Cai2016}
Cai, Y.; Hu, X.M.
\newblock A critical review on draw solutes development for forward osmosis.
\newblock {\em Desalination} {\bf 2016}, {\em 391},~16--29.
\newblock
  https://doi.org/10.1016/j.desal.2016.03.021.%}{\detokenize{10.1016/j.desal.2016.03.021}}}.

\bibitem[Wack and Ulbricht(2009)]{Wack_2009}
Wack, H.; Ulbricht, M.
\newblock Effect of synthesis composition on the swelling pressure of polymeric
  hydrogels.
\newblock {\em Polymer} {\bf 2009}, {\em 50},~2075--2080.
\newblock
  https://doi.org/10.1016/j.polymer.2009.02.041.%}{\detokenize{10.1016/j.polymer.2009.02.041}}}.

\bibitem[Tanaka \em{et~al.}(1982)Tanaka, Nishio, Sun, and
  Ueno-Nishio]{Tanaka_1982}
Tanaka, T.; Nishio, I.; Sun, S.T.; Ueno-Nishio, S.
\newblock Collapse of Gels in an Electric Field.
\newblock {\em Science} {\bf 1982}, {\em 218},~467--469.
\newblock
  https://doi.org/10.1126/science.218.4571.467.%}{\detokenize{10.1126/science.218.4571.467}}}.

\bibitem[Serizawa \em{et~al.}(2001)Serizawa, Wakita, and Akashi]{Serizawa_2001}
Serizawa, T.; Wakita, K.; Akashi, M.
\newblock Rapid Deswelling of Porous Poly(N-isopropylacrylamide) Hydrogels
  Prepared by Incorporation of Silica Particles.
\newblock {\em Macromolecules} {\bf 2001}, {\em 35},~10--12.
\newblock
  https://doi.org/10.1021/ma011362+.%}{\detokenize{10.1021/ma011362+}}}.

\bibitem[Lietor-Santos \em{et~al.}(2009)Lietor-Santos, Sierra-Martin, Vavrin,
  Hu, Gasser, and Fernandez-Nieves]{Lietor_Santos_2009}
Lietor-Santos, J.J.; Sierra-Martin, B.; Vavrin, R.; Hu, Z.; Gasser, U.;
  Fernandez-Nieves, A.
\newblock Deswelling Microgel Particles Using Hydrostatic Pressure.
\newblock {\em Macromolecules} {\bf 2009}, {\em 42},~6225--6230.
\newblock
  https://doi.org/10.1021/ma9010654.%}{\detokenize{10.1021/ma9010654}}}.

\bibitem[Qiu and Park(2001)]{Qiu_2001}
Qiu, Y.; Park, K.
\newblock Environment-sensitive hydrogels for drug delivery.
\newblock {\em Adv. Drug Deliv. Rev.} {\bf 2001}, {\em 53},~321--339.
\newblock
  https://doi.org/10.1016/s0169-409x(01)00203-4.%}{\detokenize{10.1016/s0169-409x(01)00203-4}}}.

\bibitem[Li \em{et~al.}(2011)Li, Zhang, Yao, Simon, and Wang]{Li2011}
Li, D.; Zhang, X.; Yao, J.; Simon, G.P.; Wang, H.
\newblock Stimuli-responsive polymer hydrogels as a new class of draw agent for
  forward osmosis desalination.
\newblock {\em Chem. Commun.} {\bf 2011}, {\em 47},~1710.
\newblock
  https://doi.org/10.1039/c0cc04701e.%}{\detokenize{10.1039/c0cc04701e}}}.

\bibitem[Wang \em{et~al.}(2014)Wang, Wei, and Simon]{Wang_2014}
Wang, H.; Wei, J.; Simon, G.P.
\newblock Response to Osmotic Pressure versus Swelling Pressure: Comment on
  {\textquotedblleft}Bifunctional Polymer Hydrogel Layers As Forward Osmosis
  Draw Agents for Continuous Production of Fresh Water Using Solar
  Energy{\textquotedblright}.
\newblock {\em Environ. Sci. Technol.} {\bf 2014}, {\em
  48},~4214--4215.
\newblock
  https://doi.org/10.1021/es5011016.%}{\detokenize{10.1021/es5011016}}}.

\bibitem[Arens \em{et~al.}(2017)Arens, Albrecht, Höpfner, Schlag, Habicht,
  Seiffert, and Wilhelm]{Arens_2017}
Arens, L.; Albrecht, J.B.; Höpfner, J.; Schlag, K.; Habicht, A.; Seiffert, S.;
  Wilhelm, M.
\newblock Energy Consumption for the Desalination of Salt Water Using
  Polyelectrolyte Hydrogels as the Separation Agent.
\newblock {\em Macromol. Chem. Phys.} {\bf 2017}, {\em 218},~1700237.
\newblock
  https://doi.org/10.1002/macp.201700237.%}{\detokenize{10.1002/macp.201700237}}}.

\bibitem[Fengler \em{et~al.}(2020)Fengler, Arens, Horn, and
  Wilhelm]{Fengler_2020}
Fengler, C.; Arens, L.; Horn, H.; Wilhelm, M.
\newblock Desalination of Seawater Using Cationic Poly(acrylamide) Hydrogels
  and Mechanical Forces for Separation.
\newblock {\em Macromol. Mater. Eng.} {\bf 2020}, {\em 305},~2000383.
\newblock
  https://doi.org/10.1002/mame.202000383.%}{\detokenize{10.1002/mame.202000383}}}.

\bibitem[Ali \em{et~al.}(2015)Ali, Gebert, Hennecke, Graf, Ulbricht, and
  Gutmann]{Ali2015}
Ali, W.; Gebert, B.; Hennecke, T.; Graf, K.; Ulbricht, M.; Gutmann, J.S.
\newblock Design of Thermally Responsive Polymeric Hydrogels for Brackish Water
  Desalination: Effect of Architecture on Swelling, Deswelling, and Salt
  Rejection.
\newblock {\em ACS Appl. Mater. Interfaces}
  {\bf 2015}, {\em 7},~15696--15706.
\newblock
  https://doi.org/10.1021/acsami.5b03878.%}{\detokenize{10.1021/acsami.5b03878}}}.

\bibitem[Rud \em{et~al.}(2021)Rud, Landsgesell, Holm, and Ko{\v
  s}ovan]{Rud2020}
Rud, O.V.; Landsgesell, J.; Holm, C.; Ko{\v s}ovan, P.
\newblock {Modeling of weak polyelectrolyte hydrogels under compression --
  Implications for water desalination}.
\newblock {\em Desalination} {\bf 2021}, {\em 506},~114995.
\newblock
  https://doi.org/10.1016/j.desal.2021.114995.%}{\detokenize{10.1016/j.desal.2021.114995}}}.

\bibitem[Rud \em{et~al.}(2018)Rud, Borisov, and Ko{\v s}ovan]{Rud2018}
Rud, O.; Borisov, O.; Ko{\v s}ovan, P.
\newblock {Thermodynamic model for a reversible desalination cycle using weak
  polyelectrolyte hydrogels}.
\newblock {\em Desalination} {\bf 2018}, {\em 442},~32--43.
\newblock
  https://doi.org/10.1016/j.desal.2018.05.002.%}{\detokenize{10.1016/j.desal.2018.05.002}}}.

\bibitem[Rud \em{et~al.}(2022)Rud, Kazakov, Nova, and Uhlik]{Rud2022}
Rud, O.V.; Kazakov, A.D.; Nova, L.; Uhlik, F.
\newblock Polyelectrolyte Hydrogels as Draw Agents for Desalination of
  Solutions with Multivalent Ions.
\newblock {\em Macromolecules} {\bf 2022}, {\em 55}, 1763--1770.
\newblock
  https://doi.org/10.1021/acs.macromol.1c02266.%}{\detokenize{10.1021/acs.macromol.1c02266}}}.

\bibitem[Landsgesell \em{et~al.}(2020)Landsgesell, Hebbeker, Rud, Lunkad, Ko{\v
  s}ovan, and Holm]{Landsgesel2020a}
Landsgesell, J.; Hebbeker, P.; Rud, O.; Lunkad, R.; Ko{\v s}ovan, P.; Holm, C.
\newblock {Grand-Reaction Method for Simulations of Ionization Equilibria
  Coupled to Ion Partitioning}.
\newblock {\em Macromolecules} {\bf 2020}, {\em 53},~3007--3020.
\newblock
  https://doi.org/10.1021/acs.macromol.0c00260.%}{\detokenize{10.1021/acs.macromol.0c00260}}}.

\bibitem[Jin and Collins(2007)]{Jin2007}
Jin, S.; Collins, L.R.
\newblock {Dynamics of dissolved polymer chains in isotropic turbulence}.
\newblock {\em New J. Phys.} {\bf 2007}, {\em 9},~360.
\newblock
  https://doi.org/10.1088/1367-2630/9/10/360.%}{\detokenize{10.1088/1367-2630/9/10/360}}}.

\bibitem[Grest and Kremer(1986)]{Grest1986}
Grest, G.S.; Kremer, K.
\newblock Molecular dynamics simulation for polymers in the presence of a heat
  bath.
\newblock {\em Phys. Rev. A} {\bf 1986}, {\em 33},~3628--3631.
\newblock
  https://doi.org/10.1103/PhysRevA.33.3628.%}{\detokenize{10.1103/PhysRevA.33.3628}}}.

\bibitem[Nagle(2004)]{Nagle2004}
Nagle, J.F.
\newblock {Regarding the Entropy of Distinguishable Particles}.
\newblock {\em J. Stat. Phys.} {\bf 2004}, {\em
  117},~1047--1062.
\newblock
  https://doi.org/10.1007/s10955-004-5715-5.%}{\detokenize{10.1007/s10955-004-5715-5}}}.

\bibitem[Frenkel and Smit(2002)]{Frenlkel2002_book}
Frenkel, D.; Smit, B.
\newblock {\em {Understanding Molecular Simulation}}; Academic Press:  San  Diego, CA, USA,  2002.

\bibitem[Panagiotopoulos \em{et~al.}(1988)Panagiotopoulos, Quirke, Stapleton,
  and Tildesley]{Panagiotopoulos1988b}
Panagiotopoulos, A.; Quirke, N.; Stapleton, M.; Tildesley, D.
\newblock {Phase equilibria by simulation in the Gibbs ensemble}.
\newblock {\em Mol. Phys.} {\bf 1988}, {\em 63},~527--545.
\newblock
  https://doi.org/10.1080/00268978800100361.%}{\detokenize{10.1080/00268978800100361}}}.

\bibitem[Erdos \em{et~al.}(2020)Erdos, Galteland, Bedeaux, Kjelstrup, Moultos,
  and Vlugt]{Erdos2020}
Erdos, M.; Galteland, O.; Bedeaux, D.; Kjelstrup, S.; Moultos, O.A.; Vlugt,
  T.J.H.
\newblock Gibbs Ensemble Monte Carlo Simulation of Fluids in Confinement:
  Relation between the Differential and Integral Pressures.
\newblock {\em Nanomaterials} {\bf 2020}, {\em 10},~293.
\newblock
  https://doi.org/10.3390/nano10020293.%}{\detokenize{10.3390/nano10020293}}}.

\bibitem[Zhulina \em{et~al.}(2000)Zhulina, {Klein Wolterink}, and
  Borisov]{Zhulina2000}
Zhulina, E.; {Klein Wolterink}, J.; Borisov, O.
\newblock {Screening Effects in a Polyelectrolyte Brush: Self-Consistent-Field
  Theory}.
\newblock {\em Macromolecules} {\bf 2000}, {\em
  33}, 4945--4953.
\newblock
  https://doi.org/10.1021/ma990187i.%}{\detokenize{10.1021/ma990187i}}}.

\bibitem[Wang \em{et~al.}(2020)Wang, Violet, DuChanois, and
  Elimelech]{Wang_2020}
Wang, L.; Violet, C.; DuChanois, R.M.; Elimelech, M.
\newblock Derivation of the Theoretical Minimum Energy of Separation of
  Desalination Processes.
\newblock {\em J. Chem. Educ.} {\bf 2020}, {\em 97},~4361--4369.
\newblock
  https://doi.org/10.1021/acs.jchemed.0c01194.%}{\detokenize{10.1021/acs.jchemed.0c01194}}}.

\bibitem[Kim \em{et~al.}(2019)Kim, Park, Yang, and Hong]{Kim_2019}
Kim, J.; Park, K.; Yang, D.R.; Hong, S.
\newblock A comprehensive review of energy consumption of seawater reverse
  osmosis desalination plants.
\newblock {\em Appl. Energy} {\bf 2019}, {\em 254},~113652.
\newblock
  https://doi.org/10.1016/j.apenergy.2019.113652.%}{\detokenize{10.1016/j.apenergy.2019.113652}}}.

\bibitem[Kim and Hong(2018)]{Kim_2018}
Kim, J.; Hong, S.
\newblock A novel single-pass reverse osmosis configuration for high-purity
  water production and low energy consumption in seawater desalination.
\newblock {\em Desalination} {\bf 2018}, {\em 429},~142--154.
\newblock
  https://doi.org/10.1016/j.desal.2017.12.026.%}{\detokenize{10.1016/j.desal.2017.12.026}}}.

\bibitem[Atkins and de~Paula(2010)]{Atkins}
Atkins, P.; de~Paula, J.
\newblock {\em {Physical Chemistry}}, 9th ed.; Oxford University Press:
  New York, NY, USA, 2010.

\bibitem[Prokacheva \em{et~al.}(2021)Prokacheva, Rud, Uhl\'{\i}k, and
  Borisov]{Prokacheva2021}
Prokacheva, V.M.; Rud, O.V.; Uhl\'{\i}k, F.; Borisov, O.V.
\newblock {Phase transition in hydrophobic weak polyelectrolyte gel utilized
  for water desalination}.
\newblock {\em Desalination} {\bf 2021}, {\em 511},~115092.
\newblock
  https://doi.org/10.1016/j.desal.2021.115092.%}{\detokenize{10.1016/j.desal.2021.115092}}}.

\end{thebibliography}

% If authors have biography, please use the format below
%\section*{Short Biography of Authors}
%\bio
%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author1.pdf}}}
%{\textbf{Firstname Lastname} Biography of first author}
%
%\bio
%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author2.jpg}}}
%{\textbf{Firstname Lastname} Biography of second author}

% For the MDPI journals use author-date citation, please follow the formatting guidelines on http://www.mdpi.com/authors/references
% To cite two works by the same author: \citeauthor{ref-journal-1a} (\citeyear{ref-journal-1a}, \citeyear{ref-journal-1b}). This produces: Whittaker (1967, 1975)
% To cite two works by the same author with specific pages: \citeauthor{ref-journal-3a} (\citeyear{ref-journal-3a}, p. 328; \citeyear{ref-journal-3b}, p.475). This produces: Wong (1999, p. 328; 2000, p. 475)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% for journal Sci
%\reviewreports{\\
%Reviewer 1 comments and authors’ response\\
%Reviewer 2 comments and authors’ response\\
%Reviewer 3 comments and authors’ response
%}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{adjustwidth}
\end{document}

### 2022-10-14 MDPI/proof/manuscript.v5/orig.tex
proofreading

--- 2022-10-14 MDPI/proof/manuscript.v5/gels-1883243-english_edit.tex
@@
 \copyrightyear{2022}
-\externaleditor{Academic Editor: \hl{Firstname Lastname}} %MDPI: please add the Academic Editor
+\externaleditor{Academic Editor: \hl{Firstname Lastname} %MDPI: please add the Academic Editor
+}
 \datereceived{9 August 2022} 
@@
 % Authors, for the paper (add full first names)
-\Author{Mikhail Laktionov %MDPI: Please carefully check the accuracy of names and affiliations. 
+\Author{\hl{Mikhail Laktionov} %MDPI: Please carefully check the accuracy of names and affiliations. 
 %MDPI: The name of this author is different from the submitting system. Please confirm which one is correct.
@@
 % MDPI internal command: Authors, for citation in the left column
-\AuthorCitation{Laktionov, M.; Nová, L.; Rud, O.V.}
+\AuthorCitation{\hl{Laktionov, M.;} %MDPI: Please check all author names carefully.
+ Nová, L.; Rud, O.V.}
 % If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.
@@
 \address{%
-$^{1}$ \quad Department of Physical and Macromolecular Chemistry, Faculty of Science, Charles University in Prague, Prague 12800, Czech Republic
+$^{1}$ \quad Department of Physical and Macromolecular Chemistry, Faculty of Science, Charles University in Prague, \hl{Czech Republic}%MDPI: please add the city and post code
 ; miklakt@gmail.com (M.L.); lucie.nova@natur.cuni.cz (L.N.)\\
-$^{2}$ \quad Saint-Petersburg National Research University of Information Technologies, Mechanics and Optics, Saint-Petersburg 197101, Russia\\
-$^{3}$ \quad Institute of Macromolecular Compounds of Russian Academy of Sciences, Saint-Petersburg 199004, Russia}
+$^{2}$ \quad St. Petersburg National Research University of Information Technologies, Mechanics and Optics, \hl{St.~Petersburg}%MDPI: please add the post code
+, Russia\\
+$^{3}$ \quad Institute of Macromolecular Compounds of Russian Academy of Sciences, \hl{Saint-Petersburg}, Russia}
 
@@
 %it is worth to note that we are not limited with this process only.
-In this process, the gel is supposed to be compressed/decompressed in an \emph{open system %MDPI: Please confirm if the italics should be retained.
-%Oleg Rud: Confirm, let it retain
+In this process, the gel is supposed to be compressed/decompressed in an \emph{\hl{open system} %MDPI: Please confirm if the italics should be retained.
 } and in a \emph{closed system}.
-The compression in the \emph{open system} assumes that the gel is in thermodynamic equilibrium with a huge (effectively \textbf{infinite}) reservoir of aqueous solution \reffig{fig: open}, whereas 
-the \emph{closed system} implies that the gel is in equilibrium with a \textbf{finite %MDPI: Please confirm if the bold should be retained.
-%Oleg Rud: Confirm, let it retain
-} reservoir of an aqueous solution \reffig{fig: closed}.
+The compression in the \emph{\hl{open system}} assumes that the gel is in thermodynamic equilibrium with a huge (effectively \textbf{\hl{infinite}}) reservoir of aqueous solution, whereas 
+the \emph{\hl{closed system}} implies that the gel is in equilibrium with a \textbf{\hl{finite} %MDPI: Please confirm if the bold should be retained.
+} reservoir of an aqueous solution.
 
@@
 
-	\caption{The hydrogel compressed in \emph{open} and in \emph{closed} system.
-		Red and blue circles represent $\na$ and$\cl$ ions. $V_0$ is the volume which gel has in free swelling equilibrium state.\label{fig:open and closed}}
+	\caption{\hl{Diamond-like network} %MDPI: Please cite the figure in the text and ensure the first citation of each figure appears in numerical order.
+ in the simulation box. Color code represents
+		the individual ion types (red: $\na$, blue: $\cl$, yellow: $\ca$)
+		and the hydrogel (grey: neutral segment ($\AH$), cyan: charged segment
+		($\A$)). \label{fig:open and closed}}
 \end{figure}
@@
 \includegraphics[width=0.7\textwidth]{{figures/simgibbs}.pdf}\caption{Diamond-like network in the simulation box. Color code represents
-the individual ion types (red: $\na$, blue: $\cl$)
+the individual ion types (red: $\na$, blue: $\cl$, yellow: $\ca$)
 and the hydrogel (gray: neutral segment ($\AH$), cyan: charged segment
@@
 
-\begin{table}[H]
-\caption{Estimates of  %MDPI: Please confirm if the format of the table should be retained, e.g., the color of the font, the text direction, vertical line
-% Oleg Rud: Confirm the colors and the directions of the table must retain
-desalination efficiency.
-All units are calculated per one mol of gel segments.
-Values in brackets correspond to crossection of `red' and `orange' lines on the plots in Figures \ref{fig: PV and CV} and \ref{fig: NV and CN}.
-\label{tab: table}}
-
-\begin{adjustwidth}{-\extralength}{0cm}
-
-		\newcolumntype{C}{>{\centering\arraybackslash}X}
-\begin{tabularx}{1\fulllength}{@{\extracolsep{\fill}}ll|lc|c|l|ll}
-\noalign{\hrule height 1pt}
-\multicolumn{1}{l|}{\textbf{\boldmath{$c_{s}^{0}$}, mM}} & \textbf{\boldmath{$c_{s}^{5}$}, mM} & \multicolumn{1}{l|}{\textbf{\boldmath{$n_{\cl}^{0}$}, mM}} & \textbf{\boldmath{$n_{\cl}^{5}$}, mM} & \textbf{\boldmath{$\Delta \Vgel$}, L} & \textbf{\boldmath{$|W$}\textbar , J/L} & \multicolumn{2}{c}{\textbf{\boldmath{$W^{id}$}, J/L}}\tabularnewline
-
-\noalign{\hrule height 0.5pt} 
-\multirow{2}{*}{{\small{}$91.47$}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{{\small{}$57.08\pm0.122\enskip\longrightarrow$}} & \multirow{2}{*}{{\small{}2.74}} & \multirow{2}{*}{{\small{}$95.4\pm1.9$}} &  & \multirow{2}{*}{}\tabularnewline
- &  & \multicolumn{2}{r|}{{\small{}$71.75\pm0.024$}} &  &  & \multirow{8}{*}{{\small{}\hspace{-1em}}\textcolor{teal}{\small{}$\left.\begin{array}{l}
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\end{array}\right\rbrace $$\rotatebox{90}{\hspace{-5em}{\color{teal}\ensuremath{\begin{array}{cc}
-W^{id}= & 52.9\\
-W^{\mathrm{sim}}= & 202.8\pm3.2\\
-R_{w}= & 0.54
-\end{array}}}}$}} & \tabularnewline
-\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
-\multicolumn{2}{l|}{{\small{}$89.41\pm0.23\enskip\longrightarrow$}} & \multirow{2}{*}{{\small{}56.90}} & \multirow{2}{*}{} & \multirow{2}{*}{{\small{}2.72}} & \multirow{2}{*}{{\small{}$109.1\pm1.7$}} &  & \multirow{2}{*}{}\tabularnewline
-\multicolumn{2}{r|}{{\small{}$73.63\pm0.03$}} &  &  &  &  &  & \tabularnewline
-\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
-\multirow{2}{*}{\textcolor{teal}{\small{}63.93}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{teal}{\small{}$37.28\pm0.08\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{teal}{\small{}3.26}} & \multirow{2}{*}{\textcolor{teal}{\small{}$100.9\pm1.7$}} &  & \tabularnewline
- &  & \multicolumn{2}{r|}{\textcolor{teal}{\small{}$50.579\pm0.013$}} &  &  &  & \multirow{8}{*}{{\small{}\hspace{-1em}}\textcolor{olive}{\small{}$\left.\begin{array}{l}
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\end{array}\right\rbrace $$\rotatebox{90}{\hspace{-5em}\ensuremath{\begin{array}{cc}
-W^{id}= & 38.2\\
-W^{\mathrm{sim}}= & 207.3\pm2.2\\
-R_{w}= & 0.53
-\end{array}}}$}}\tabularnewline
-\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
-\multicolumn{2}{l|}{\textcolor{teal}{\small{}$62.05\pm0.15\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{teal}{\small{}37.17}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{teal}{\small{}3.18}} & \multirow{2}{*}{\textcolor{teal}{\small{}$107.4\pm1.4$}} &  & \tabularnewline
-\multicolumn{2}{r|}{\textcolor{teal}{\small{}$48.21\pm0.02$}} &  &  &  &  &  & \tabularnewline
-\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
-\multirow{2}{*}{\textcolor{olive}{\small{}44.91}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{olive}{\small{}$23.75\pm0.06\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{olive}{\small{}3.82}} & \multirow{2}{*}{\textcolor{olive}{\small{}$106.7\pm1.5$}} &  & \tabularnewline
- &  & \multicolumn{2}{r|}{\textcolor{olive}{\small{}$35.911\pm0.010$}} &  &  & \multirow{8}{*}{{\small{}\hspace{-1em}}\textcolor{red}{\small{}$\left.\begin{array}{l}
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\end{array}\right\rbrace \rotatebox{90}{\hspace{-5em}\ensuremath{\begin{array}{cc}
-W^{\mathrm{id}}= & 43.8\ {\color{red}{\scriptstyle (41.0)}}\\
-W^{\mathrm{sim}}= & 222.3\pm2.5\\
-R_{w}= & 0.52\ {\scriptstyle (0.46)}
-\end{array}}}$}} & \tabularnewline
-\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
-\multicolumn{2}{l|}{\textcolor{olive}{\small{}$43.46\pm0.12\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{olive}{\small{}24.27}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{olive}{\small{}3.91}} & \multirow{2}{*}{\textcolor{olive}{\small{}$106.4\pm1.1$}} &  & \tabularnewline
-\multicolumn{2}{r|}{\textcolor{olive}{\small{}$30.795\pm0.008$}} &  &  &  &  &  & \tabularnewline
-\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
-\multirow{2}{*}{\textcolor{red}{\small{}31.93}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{red}{\small{}$14.66\pm0.04\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{red}{\small{}4.20}} & \multirow{2}{*}{\textcolor{red}{\small{}$107.9\pm1.4$}} &  & \tabularnewline
- &  & \multicolumn{2}{r|}{\textcolor{red}{\small{}$25.297\pm0.006$}} &  &  &  & \multirow{8}{*}{{\small{}\hspace{-1em}}\textcolor{orange}{\small{}$\left.\begin{array}{l}
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\end{array}\right\rbrace \rotatebox{90}{\hspace{-5em}\ensuremath{\begin{array}{cc}
-W^{id}= & 66.6\ {\scriptstyle (22.0)}\\
-W^{\mathrm{sim}}= & 218.7\pm2.2\\
-R_{w}= & 0.53\ {\scriptstyle (0.49)}
-\end{array}}}$}}\tabularnewline
-\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
-\multicolumn{2}{l|}{\textcolor{red}{\small{}$30.03\pm0.08\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{red}{\small{}14.55}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{red}{\small{}$\begin{array}{c}
-4.17\\
-{\scriptstyle (3.22)}
-\end{array}$}} & \multirow{2}{*}{\textcolor{red}{\small{}$\begin{array}{c}
-115.6\pm0.9\\
-{\scriptstyle (57.3)}
-\end{array}$}} &  & \tabularnewline
-\multicolumn{2}{r|}{\textcolor{red}{\small{}$\begin{array}{c}
-18.585\pm0.004\,\\
-{\scriptstyle (22.32)}
-\end{array}$}} &  &  &  &  &  & \tabularnewline
-\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
-\multirow{2}{*}{\textcolor{orange}{\small{}22.30}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{orange}{\small{}$8.84\pm0.03\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{orange}{\small{}$\begin{array}{c}
-4.75\\
-{\scriptstyle (3.76)}
-\end{array}$}} & \multirow{2}{*}{\textcolor{orange}{\small{}$\begin{array}{c}
-108.1\pm1.3\\
-{\scriptstyle (68.3)}
-\end{array}$}} &  & \tabularnewline
- &  & \multicolumn{2}{r|}{\textcolor{orange}{\small{}$\begin{array}{c}
-\text{17.945}\pm\text{0.004}\\
-{\scriptstyle (14.56)}
-\end{array}$}} &  &  & \multirow{7}{*}{{\small{}\hspace{-1em}}\textcolor{magenta}{\small{}$\left.\begin{array}{l}
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\end{array}\right\rbrace \rotatebox{90}{\hspace{-5em}\ensuremath{\begin{array}{cc}
-W^{id}= & 69.7\\
-W^{\mathrm{sim}}= & 227.5\pm2.3\\
-R_{w}= & 0.55
-\end{array}}}$}} & \\[1ex]
-\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
-\multicolumn{2}{l|}{\textcolor{orange}{\small{}$20.74\pm0.06\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{orange}{\small{}8.83}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{orange}{\small{}$4.71$}} & \multirow{2}{*}{\textcolor{orange}{\small{}$110.8\pm0.8$}} &  & \tabularnewline
-\multicolumn{2}{r|}{\textcolor{orange}{\small{}$11.082\pm0.002$}} &  &  &  &  &  & \tabularnewline
-\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
-\multirow{2}{*}{\textcolor{magenta}{\small{}10.90}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{magenta}{\small{}$3.00\pm0.01\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{magenta}{\small{}6.08}} & \multirow{2}{*}{\textcolor{magenta}{\small{}$106.9\pm1.1$}} &  & \tabularnewline
- &  & \multicolumn{2}{r|}{\textcolor{magenta}{\small{}9.011$\pm$0.002}} &  &  &  & \tabularnewline
-\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
-\multicolumn{2}{l|}{\textcolor{magenta}{\small{}$9.83\pm0.05\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{magenta}{\small{}3.12}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{magenta}{\small{}5.78}} & \multirow{2}{*}{\textcolor{magenta}{\small{}$119.4\pm1.0$}} &  & \tabularnewline
-\multicolumn{2}{r|}{\textcolor{magenta}{\small{}$3.862\pm0.001$}} &  &  &  &  &  & \\[2ex]
-\noalign{\hrule height 1pt}
-\end{tabularx}
-\end{adjustwidth}
-\end{table}
-
 Thus, the recovery ratio $R_w = \Delta v^p / (\Delta v^p + \Delta v^b) \simeq $ 0.53 and the theoretical minimum specific energy of the desalination process with corresponding $\cs^f$, $\cs^p,$ and $\cs^b$ is $W^{id} =$ 38.2~J/L (\refeq{eq:SEC}).
@@
 (2) compression of the gel in a \emph{closed system}, during which the gel exchanges ions with a small reservoir, affecting its salinity.
-We estimated the energy consumption needed for producing one liter of potable water from brine and have shown that the proposed gel compression method may compete with modern desalination~technologies.
-%MDPI: we noticed that the supplementary file has been uploaded in submitting system.
+We estimated the energy consumption needed for producing one liter of potable water from brine and have shown that the proposed gel compression method may compete with modern \hl{desalination~technologies.} %MDPI: we noticed that the supplementary file has been uploaded in submitting system.
 please confirm if there is a supplementary, if so, please cite it in main text and add section of supplementary materils “\supplementary{The following are available at \linksupplementary{s1}, Figure S1: title, Table S1: title, Video S1: title.} ”.
 Please note that the reference in supplementary should be also included in mian text.
-% Oleg Rud: There is no need of supplementary materials anymore, since we added the method description into the main text.
+
 }
@@
 
-%\institutionalreview{\hl{~}}%MDPI: In this section, please add the Institutional Review Board Statement and approval number for studies involving humans or animals.
+\institutionalreview{\hl{~}}%MDPI: In this section, please add the Institutional Review Board Statement and approval number for studies involving humans or animals.
 Please note that the Editorial Office might ask you for further information.
@@
 
-%\informedconsent{\hl{~}}%MDPI: Any research article describing a study involving humans should contain this statement.
+\informedconsent{\hl{~}}%MDPI: Any research article describing a study involving humans should contain this statement.
 Please add ``Informed consent was obtained from all subjects involved in the study.'' OR ``Patient consent was waived due to REASON (please provide a detailed justification).'' OR ``Not applicable'' for studies not involving humans.
@@
 
-%\dataavailability{\hl{~}} %MDPI: In this section, please provide details regarding where data supporting reported results can be found, including links to publicly archived datasets analyzed or generated during the study.
+\dataavailability{\hl{~}} %MDPI: In this section, please provide details regarding where data supporting reported results can be found, including links to publicly archived datasets analyzed or generated during the study.
 Please refer to suggested Data Availability Statements in section ``MDPI Research Data Policies'' at \url{https://www.mdpi.com/ethics}.
@@
 
-%\acknowledgments{\hl{This research was supported by the Czech Science Foundation (grant 19-17847Y) and the 
-%government of the Russian Federation (grant number 14.W03.31.0022).} %MDPI: The contents in acknowledgments are the same as those in funding. please confirm if it can be deleted in acknowledgments
- % Confirm it can be deleted in acknowledjements
-%}
+\acknowledgments{\hl{This research was supported by the Czech Science Foundation (grant 19-17847Y) and the 
+government of the Russian Federation (grant number 14.W03.31.0022).} %MDPI: The contents in acknowledgments are the same as those in funding. please confirm if it can be deleted in acknowledgments
+
+}
 
@@
 \newblock \emph{Review of Water Resources and Desalination Technologies};
-Sandia National Laboratories (SNL): Albuquerque, NM, USA, 2003;
-\newblock Technical Report; 
-\newblock https://doi.org/10.2172/809106; 
-%MDPI: Please add the name of the publisher and the location of it.
+\newblock Technical Report;  \hl{2003}%MDPI: Please add the name of the publisher and the location of it.
 .
-
-\newblock {\em {Physical Chemistry}}, 9th ed.; Oxford University Press:
-  New York, NY, USA, 2010.
 \newblock

### 2022-10-14 MDPI/proof/manuscript.v5/temp.tex
proofreading

--- 2022-10-14 MDPI/proof/manuscript.v5/gels-1883243-english_edit.tex
@@
 \begin{table}[H]
-\caption{Estimates of  %MDPI: Please confirm if the format of the table should be retained, e.g., the color of the font, the text direction, vertical line
-% Oleg Rud: Confirm the colors and the directions of the table must retain
+\caption{\hl{Estimates of } %MDPI: Please confirm if the format of the table should be retained, e.g., the color of the font, the text direction, vertical line
 desalination efficiency.

### 2022-10-14 MDPI/reviewer1.tex
proofreading

--- 2022-08-26 gibbs.tex
@@
-%% LyX 2.3.4.2 created this file.  For more info, see http://www.lyx.org/.
-%% Do not edit unless you really know what you are doing.
-%\documentclass{achemso}
-\documentclass[layout=twocolumns,manuscript=article]{achemso}
+\documentclass[12pt]{dinbrief}
+%\usepackage{english}
+\usepackage[english]{babel}
+\usepackage[utf8]{inputenc}
+\usepackage{color}
+\usepackage[textsize=small]{todonotes}
 
-\makeatletter
+\usepackage[unicode=true, pdfusetitle, bookmarks=true, bookmarksnumbered=false, bookmarksopen=false, breaklinks=false, pdfborder={0 0 0}, pdfborderstyle={}, backref=false, colorlinks=true] {hyperref}
 
+%\usepackage[pdfborder={0 0 0}]{hyperref}
+
+\date{\today}
+
+\place{Prague}
+
+\nowindowtics
+\nowindowrules
+
+\newcommand{\theeditor}{Dr. David Díaz-Díaz}
+
+\newcommand{\thejournal}{\textit{Gels }}
+\newcommand{\cl}{\mathrm{Cl^-}}
+\newcommand{\na}{\mathrm{Na^+}}
+
+%\newcommand{\ie}{\textit{i.~e.} } 
+\enabledraftstandard
+\newcommand{\ie}{\textit{i.~e.} }
+\newcommand{\cref}{c^{\ominus}}
+%\newcommand{\cs}{c_{s}}
+\newcommand{\kT}{k_\mathrm{B}T}
+\newcommand{\kB}{k_\mathrm{B}}
+\newcommand{\lb}{l_\mathrm{B}}
+%\newcommand{\NA}{N_{\mathrm{A^-}}}
+\newcommand{\NA}{N_{\mathrm{A}}}
+\newcommand{\muna}{\mu_\mathrm{Na^+}}
+
+\newcommand{\mucl}{\mu_\mathrm{Cl^-}}
+\newcommand{\muca}{\mu_\mathrm{Ca^{2+}}}
+\newcommand{\muh}{\mu_\mathrm{H^+}}
+\newcommand{\mua}{\mu_\mathrm{A^-}}
+\newcommand{\muha}{\mu_\mathrm{HA}}
+\newcommand{\muoh}{\mu_\mathrm{OH}}
+
+\newcommand{\cna}{c_\mathrm{Na^+}}
+\newcommand{\ccl}{c_\mathrm{Cl^-}}
+\newcommand{\cca}{c_\mathrm{Ca^{2+}}}
+\newcommand{\ch}{c_\mathrm{H^+}}
+\newcommand{\cp}{c_\mathrm{p}}
+\newcommand{\nna}{n_\mathrm{Na^+}}
+\newcommand{\ncl}{n_\mathrm{Cl^-}}
+\newcommand{\Nna}{N_\mathrm{Na^+}}
+\newcommand{\Ncl}{N_\mathrm{Cl^-}}
+
+\newcommand{\ncleq}{\widetilde{N}_\mathrm{Cl^-}}
+\newcommand{\nca}{N_\mathrm{Ca^{2+}}}
+
+\newcommand{\superin}{^\mathrm{in}}
+\newcommand{\subin}{_\mathrm{in}}
+\newcommand{\subi}{_\mathrm{i}}
+
+\newcommand{\gel}{^\mathrm{gel}}
+\newcommand{\tot}{^\mathrm{tot}}
+\newcommand{\out}{^{\mathrm{out}}}
+\newcommand{\coh}{c_\mathrm{OH}}
+\newcommand{\bulk}{^{\mathrm{b}}}
+\renewcommand{\H}{\mathrm{H^+}}
+\newcommand{\A}{\mathrm{A^-}}
+\newcommand{\AH}{\mathrm{AH}}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
+%% A simple dot to overcome graphicx limitations
+\newcommand{\lyxdot}{.}
+\newcommand{\todoi}[1]{\todo[inline]{#1}}
+\newcommand{\br}{\mathrm{Br^-}}
+\newcommand{\h}{\mathrm{H^+}}
+\newcommand{\ka}{\mathrm{K^+}}
+\newcommand{\oh}{\mathrm{OH^-}}
+\newcommand{\ca}{\mathrm{Ca^{2+}}}
+\newcommand{\mg}{\mathrm{Mg^{2+}}}
+\newcommand{\so}{\mathrm{SO_4^{2-}}}
 
-\title{Water desalination using polyelectrolyte hydrogel. Gibbs ensemble modeling}
+\newcommand{\EI}{E_{\mathrm{I}}}
+\newcommand{\EII}{E_{\mathrm{II}}}
+\newcommand{\SI}{S_{\mathrm{I}}}
+\newcommand{\SII}{S_{\mathrm{II}}}
+\newcommand{\NI}{N_{\mathrm{I}}}
+\newcommand{\NII}{N_{\mathrm{II}}}
+\newcommand{\VI}{V_{\mathrm{I}}}
+\newcommand{\VII}{V_{\mathrm{II}}}
+\newcommand{\FI}{F_{\mathrm{I}}}
+\newcommand{\FII}{F_{\mathrm{II}}}
+\newcommand{\nnaI}{N^{\na}_{\mathrm{I}}}
+\newcommand{\nclI}{N^{\cl}_{\mathrm{I}}}
+\newcommand{\nnaII}{N^{\na}_{\mathrm{II}}}
+\newcommand{\nclII}{N^{\cl}_{\mathrm{II}}}
 
-\author{Mikhail Laktionov}
-
-\affiliation[cuni]{Department of Physical and Macromolecular Chemistry, Faculty of Science,
-Charles University in Prague, Czech Republic}
-
-\alsoaffiliation[itmo]{St. Petersburg National Research University of Information Technologies,
-Mechanics and Optics, St. Petersburg, Russia.}
-
-\author{Lucie Nová}
-\author{Oleg V. Rud}
-
-\affiliation{Department of Physical and Macromolecular Chemistry, Faculty of Science, Charles University in Prague, Czech Republic}
-\alsoaffiliation[imc]{Institute of Macromolecular Compounds of Russian Academy of Sciences, Saint-Petersburg, Russia}
-
-\email{oleg.rud@natur.cuni.cz}
-
-\abbreviations{MC, MD, RO, FO}
-
-\keywords{polyelectrolye hydrogel, simulation, desalination}
-
-%% Because html converters don't know tabularnewline
-\providecommand{\tabularnewline}{\\}
-
-\input{definitions.tex}
-\makeatother
+\newcommand{\Ka}{K_{\mathrm{A}}}
+\newcommand{\pKa}{\mathrm{p}\Ka}
+\newcommand{\pK}{\mathrm{p}K}
+\newcommand{\pH}{\mathrm{pH}}
+\newcommand{\mol}{\mathrm{mol}}
+\newcommand{\molperl}{\mathrm{mol/l}}
+\newcommand{\kg}{\mathrm{kg}}
+\newcommand{\res}{^{\mathrm{res}}}
+\newcommand{\pHres}{\pH\res}
+\newcommand{\pHgel}{\pH\gel}
+\newcommand{\cs}{c_{\mathrm{s}}}
+\newcommand{\csres}{\cs\res}
+\newcommand{\Vgel}{V_\mathrm{gel}}
+\newcommand{\Ngel}{N_\mathrm{gel}}
+\newcommand{\Pgel}{\Pi}
+\newcommand{\Pres}{P_\mathrm{res}}
+\newcommand{\Pout}{P_\mathrm{out}}
+\newcommand{\Vout}{V_\mathrm{out}}
+\newcommand{\Vbox}{V_0}
+\newcommand{\PE}{polyelectrolyte{}}
 
 \begin{document}
-\begin{abstract}
-Recently polyelectrolyte hydrogels have been proposed as draw agents for the forward osmosis desalination techniques. 
-Indeed, polyelectrolyte hydrogels have the ability to absorb a big amount of water across an osmosis membrane as a result of their swelling pressure. 
-On the other hand, the insoluble cross-linked network of the gel enables dewatering under the influence of a stimulus (thermal and/or mechanical).
-Moreover, from a thermodynamic perspective, the polyelectrolyte hydrogel is already an osmotic membrane rejecting ions between external and internal solutions.
-These three properties of the gels make it possible to use them for desalination and at the same time avoid the use of expensive membranes.
-In this article, we present our recent theoretical study of the use of polyelectrolyte hydrogel for water desalination. 
-We modeled the thermodynamic equilibrium between coexisting phases of the gel and supernate aqueous salt solution.
-We have shown that the salinity of the supernate phase decreases during compression of the gel due to the release of absorbed in gel solution of lower salinity. 
-Finally, we performed a set of simulations modeling the process of continuous decrease of solution salinity up to freshwater concentrations.
 
-\end{abstract}
+\textbf{Reviewer 1}
+\textit{}
 
-\section{Introduction\label{sec: intro}}
+\begin{enumerate}
+\item \textit{The main findings of your results should be highlighted in abstract}
 
-\paragraph{Water desalination technologies.}
+We have rewritten the abstract.
 
-Two basic approaches for separating water from salt are present in modern desalination technology \cite{Miller2003,Curto2021}.
+\item \textit{Please do not separate introduction in three sections combine with problem and technology you used and challenges and your solutions.}
 
-The first approach is distillation, which uses heat to cause a phase change of the water to vapor. The vapor phase is separated from the brine and condenses to liquid fresh water. 
-The released condensation energy is directed back to heating the feed solution.
-Distillation processes were the first desalination techniques conducted on a large commercial scale and still account for a large portion of the modern world’s desalination capacity.
+We have rewritten the Introduction section.
+We wanted to keep the separation of the Introduction section into the respective subsections because the Introduction is relatively lengthy, so we believe that dividing it into subsections reduces its readability.
 
-The second approach is to physically separate the brine components using an osmotic membrane transparent only for water molecules, which move in response to a water chemical potential difference.
-In the context of our study, we will mention the reverse osmosis process (RO)~--- the major process of all the modern desalination industry, and the newly emerging membrane
-technology~--- forward osmosis (FO) \cite{Akther2015}. 
-In RO, the difference in water chemical potential originates from a difference in pressures applied to the feed and to product solutions. 
-In FO, the chemical potential difference is due to an addition to solution from one side of the membrane (draw solution) the so-called draw solutes, which are lowering the water chemical potential in draw solution.
+\item \textit{In page 4 heading 2. (How to start with and ??)}.\\
+Corrected.
 
-Distillation is easy and cheap technology but it is characterized by relatively high energy costs due to the dissipation of thermal energy. 
-On the contrary, RO uses expensive osmotic membranes, which need to be replaced regularly because of scaling and fouling. 
-Moreover, RO requires very high operating pressures, ranging from 20 to 200 bar, to let the water pass through the membrane. 
-But in terms of energy losses, it works close to the thermodynamic limit.
-Thus, theoretically, per one ion pair transferred from freshwater to salty water, it consumes only the energy equal to the difference between the chemical potentials of the transfered ions.
+\item \textit{All formula and models should be supported with reference for instant equation 3.}
+Corrected
 
-The absence of large hydraulic pressure in FO process (unlike in RO) allows to reduce the energy consumption in pumping, reduce membrane scaling and fouling, and therefore significantly increase the lifetime of the membranes.
-In FO, the draw solutes (agents) are dispersed and/or dissolved in water form homogeneous draw solutions. 
-The correct choice of the draw agents is a task of paramount importance. 
-As an osmotically driven process, the draw solute is expected to significantly reduce the water chemical potential, and consequently generate a high osmotic pressure. 
-On the other hand, the draw solute is expected to be easily separated from water \cite{Cai2016}.
+\item \textit{In page 6, please remove the footer, it is not a book to describe issues below}.\\
+Corrected. Now this sentence appears in text (in brackets).
 
-\paragraph{Hydrogels for desalination.}
-Hydrogels are three-dimensional networks of polymer chains that are crosslinked by either physical or chemical bonds. 
-They are able to entrap large volumes of water attracted by the high concentration of hydrophilic groups. 
-When a dehydrated or deswollen hydrogel uptakes water, its polymer chains extend, creating a swelling pressure. 
-For example, as reported in \cite{Wack_2009} weakly crosslinked poly(acrylic acid) (PAA) copolymers with polymer volume fractions between 0.03 and 0.30 exhibit a swelling pressure ranging from 0.20--4.23 MPa.
-Polyelectrolyte hydrogels, which are carrying ionic groups on the comonomer units (like PAA), are able to reject salt ions from the solution, they absorb a solution of lower salinity than that they are equilibrated with.
+\item \textit{How do you think control factors in open system such as pressure and temperature}
 
-An important, advantageous aspect of polymer hydrogels is that they can undergo reversible volume change, \ie solution --- gel phase transitions in response to environmental stimuli. 
-This aspect causes hydrogels to be labeled as ‘smart’ hydrogels. 
-Many physical and chemical stimuli have been applied to induce various responses of such smart hydrogels, in particular, to change them from hydrophilic to hydrophobic, thereby releasing water. 
-The physical stimuli include: temperature, solvent composition, light, mechanical pressure, sound, electric and/or magnetic field, whilst the chemical (or biochemical) stimuli include pH, ionic strength, and specific molecular recognition \cite{Tanaka_1982,Serizawa_2001,Lietor_Santos_2009,Qiu_2001}.
+In our simulation, we control the volume of the simulation box and measure the pressure using the virial theorem.
+The pressure value which is depicted in the Figures assumed to be a partial pressure of the gel, which is calculated as the difference between the pressure in the gel and the pressure calculated in a separate simulation box containing only ions (with no gel).
+Temperature assumed to be constant and equal to 300 K, which is guaranteed by applying a Langevin thermostat.
 
-The smart properties of hydrogels were utilized for desalination in a recent study by Li \etal \cite{Li2011}, where hydrogels have been considered as draw agents for FO. 
-In this study authors have shown, that hydrogels, 
-are able to absorb water across the FO membrane due to their swelling and osmotic pressure and
-allow dewatering under the influence of stimuli (thermal and/or mechanical), due to their insoluble cross-linked polymer network.
-For instance, Li \etal proposed the use of hydrogel made of thermoresponsive polyelectrolyte~--- copolymer of poly-N-isopropyl acrylamide (p-NIPAAm) and polyacrylic acid (p-AA).
-Depending on the temperature the network of the gel appears to be either hydrophilic or hydrophobic. 
-In the hydrophilic state, the gel is used as a draw solute accumulating water inside, then in the hydrophobic state, the water releases out.
-
-Moreover, from a thermodynamics perspective, the polyelectrolyte hydrogel itself is an osmotic membrane generating Donnan potential, which rejects ions between outer and inner solutions \cite{Wang_2014}.
-Such a view on hydrogels was employed in a series of works by the group of prof. Wilhelm (see for example \cite{Arens_2017,Fengler_2020}). 
-The authors of these works proposed to get rid of the osmotic membrane and simply use only micro filtration to compress the hydrogel squeezing out the accumulated inside the gel solution. 
-In their method first, the deswollen hydrogel was equilibrated with saline water feed. 
-During equilibration, the gel was swelling absorbing water. 
-Then it was taken out from the feed solution and mechanically squeezed by means of a microfiltration membrane. 
-The squeezed out brine was obtained to have lower salinity than the feed water.
-
-A similar approach was used by Ali \etal \cite{Ali2015}. 
-In their study the thermosensitive gel was used (based on copolymers p-NIPAAm and p-AA), so instead of physical compression, the dewatering was done by an external heating stimulus (sunlight). 
-At night the gel was equilibrating with feed water and at daytime, under sunlight, the gel was shrinking and releasing the collected inside solution.
-
-\paragraph{Physics behind the desalination process.}
-%The maximum entropy principle requires the density of charges to be more-less the same throughout the system medium. 
-Since the polyelectrolyte gel has its own charges and its own neutralizing counterions, the density of mobile ions (which are able to freely enter and leave the gel) in gel appears to be smaller than their density outside the gel.
-Therefore the internal solution of the gel has a lower density of mobile ions than that in the solution outside. 
-In that sense, the gel acts as an osmotic membrane separating solutions \cite{Rud2020}. 
-The driving force of the separation is the Donnan potential originated from the charges of the hydrogel network. 
-The density of mobile ions difference between ions concentrations in the internal and external solutions
-is defined by Donnan law \cite{Rud2018}
-\begin{equation*}
-\frac{\ccl\gel}{\cs}=\frac{\cs}{\cna\gel}=\sqrt{1+\left(\frac{\alpha}{2\cs\Vgel}\right)^{2}}\pm\frac{\alpha}{2\cs\Vgel}
-\end{equation*}
-where $\ccl\gel$ and $\cna\gel$ are the internal concentration of monovalent anions and cations, $\cs$ is the salinity of external solution,  $\Vgel$ is the gel molar volume (inverse density of gel segments) and $\alpha$ is ionization degree (in the case of our study $\alpha=1$).
-The $\pm$ sign in the formula accounts for the change between the cases of gel made of polyanion or polycation.
-
-The lower salinity solution can be extracted from the gel by means of compression and/or other stimulus providing that the charge of the gel remains constant.
-In the case of gel made of weak (pH-sensitive) polyelectrolyte, the compression discharges the gel, therefore the neutralizing counterions leave out the gel diminishing the desalination effect \cite{Rud2018}.
-%Nevertheless, in\cite{Rud2018} we discussed how the release of counterions may be employed for desalination as well.
-
-One can argue that the sole Donnan effect is insufficient to achieve a high salt rejection \cite{Cai2016} and the salinity of the water squeezed from hydrogel under a very high hydraulic pressure (up to 100 bar \cite{Fengler_2020}) turns out to be not much different from the initial.
-Indeed, the use of high hydraulic pressure diminishes all the advantages of this method over RO, and the reversibility of hydrogel swelling after strong compression remains questionable. 
-Nevertheless, in the current study, we model the compression of the gel limiting ourselves to low compression rates, less than 5 bar, and studied how the compression of the gel affects the surrounding salinity.
-We modelled also the desalination process, as a cascade of following one by each other gel swellings and compressions driving the salinity of supernate down to drinkable water. 
-%In the current study we would like to concentrate on the use of gel made of strong polyelectrolyte for water desalination. 
-%Namely, to investigate how the compression of the gel affects the salinity of the surrounding the gel solution and to propose the way of water desalination employing the hydrogel swelling/deswelling set of processes.
-
-%The target of our study is to model the thermodynamic equilibrium between the two boxes and to show how the compression of the gel affects the ion density in the outside solution.
-
-\section{Theory behind the simulation\label{sec: theory}}
-
-\begin{figure*}[t]
-\centering \includegraphics[width=0.7\textwidth]{{figures/simgibbs}.pdf}\caption{Diamond-like network in the simulation box. Color code represents
-the individual ion types (red: $\na$, blue: $\cl$, yellow: $\ca$)
-and the hydrogel (gray: neutral segment ($\AH$), cyan: charged segment
-($\A$)). \label{fig:diamond}.}
-\end{figure*}
-
-\subsection{Model}
-
-We model the gel as a network of 16 linear polymer chains, each by 30 monomer units. 
-The chains are connected to a diamond-like polymer network throught 8 crosslinking units, and put into a simulation box with periodic boundaries (see \reffig{fig:diamond}). 
-Each unit of the network carries a negative electric charge, which is equal to the charge of electron. 
-Except the particles of the network, the monovalent co- and counter-ions ions, $\cl$ and $\na$, are present in simulation box. 
-The total electric charge of all the particles in the box is zero, therefore the amount of $\na$ ions is bigger than that of $\cl$ by the number of hydrogel units, $\Ngel=16\cdot30 + 8=488$.
-
-\begin{figure*}[t]
-\centering 
-\subfloat[Open system \label{fig: open}]
-{\includegraphics[width=0.5\textwidth]{figures/gc.pdf}}
-\subfloat[Closed system \label{fig: closed}]
-{\includegraphics[width=0.5\textwidth]{figures/gibbs.pdf}}
-\caption{Diamond-like network in the simulation box. Color code represents
-the individual ion types (red: $\na$, blue: $\cl$, yellow: $\ca$)
-and the hydrogel (gray: neutral segment ($\AH$), cyan: charged segment
-($\A$)). \label{fig:open and closed}.}
-\end{figure*}
-We simulate the compression of the gel in two ensembles.
-\begin{enumerate}
-\item The first is so called \emph{open system}, when the simulation box with gel freely exchanges ions with a big amount of aqueous solution of certain constant salinity, $\cs$. 
-\item And in \emph{closed system}, when the gel is in equilibrium with a finite volume of aqueous solution.
-\end{enumerate}
-The compression of the gel in the \emph{open} system does not affect the surrounding salinity, thus the density of ions outside the gel remains constant $\cs =$ $\cna=$ $\ccl=$ $\text{Const}$ (\reffig{fig: open}).
-On the contrary, what remains constant in the \emph{closed} system, is the total number of $\na$ and $\cl$ ions, that are contained in the gel and in the external volume, \ie in the volume $\Vbox$ (\reffig{fig: closed}).
-
-%Let $\nna$ and $\ncl$ be the density of the corresponding ion in the compression volume, $\Vbox$ averaged over this volume
-\begin{equation}
-N_i = N_i\gel + \cs\cdot(\Vbox - \Vgel)
-\end{equation}
-where $i \in \{\na, \cl\}$,  $N_i$ is the amount of the corresponding ions in gel, $\Vgel$~--- volume of the gel, $\Vbox$~--- the volume in which the gel is compressed. 
-As $\Vbox$ we choose the volume of the gel in the free swelling equilibrium state.
-
-%Then in closed system $\nna$ and $\ncl$ remain constant, whereas the salinity of supernate, $\cs$, may change with the change of the gel volume.
-
-\paragraph{Open system.}
-We simulate the open system using the grand reaction method \cite{Landsgesel2020a,Rud2020}.
-This method is a hybrid of molecular dynamics (MD) and Monte Carlo (MC). 
-The whole simulation represents a chain of subsimulations of MD and MC followed one by each other. 
-For MD simulation we used a standard Langevin dynamics \cite{Grest1986} which models the mechanical movement of all the system particles. 
-Whereas MC simulates the thermodynamic equilibrium with reservoir, which exchanges ions with the simulation box. 
-The insertion (and deletion) of ion pairs is considered as a reaction of creation (or annihilation) of an ion pair 
-\[
-\varnothing\stackrel{K}{\leftrightarrows}\na+\cl
-\]
-with a reaction constant defined by the chemical potential of ions,
-$K=\exp\left(\muna+\mucl\right).$
-
-\paragraph{Closed system.}
-The similar scheme we use to simulate the gel in closed system. 
-The procedure represents a chain of subsequent MD and MC simulation, but now the molecular dynamics is running in two simulation boxes simultaneously.
-The first box of the volume $\Vgel$ contains the gel with ions, and the second box, $\Vout$--- contains only ions. 
-The total volume of both boxes is kept constant, $\Vbox=V_{\mathrm{gel}}+V_{\mathrm{out}}$, so the compression of the gel implies the decreasing $\Vgel$ and increasing $\Vout$.
-These two boxes are represented in \reffig{fig:diamond}.
-
-\paragraph{Algorithm.}
-The thermodynamic equilibrium between the two volumes implies the exchange of ion pairs between them, which is done by means of MC procedure in a way similar to described in \cite{Panagiotopoulos1988b}.
-The simulation algorithm is following:
-\begin{enumerate}
-\item Simulate molecular dynamics in both boxes; collect the observables, for example, values of pressure $P$, to an array; 
-\item Perform Monte-Carlo procedure simulating ion pair exchange; collect the arrays of observables samples: number of ions in both boxes, 
-%$\nna\gel$,
-$\Ncl\gel$ 
-%$\nna\out$ 
-and $\Ncl\out$ ; 
-\item Repeat the procedure until the desired length of sample arrays is reached.
 \end{enumerate}
 
-\section{Results and discussion }
-
-\paragraph{Compression in open system.}
-\begin{figure*}[t]
-\subfloat[The gel partial pressure vs gel molar volume \label{fig: PV}]
-{\includegraphics[width=0.48\textwidth]{figures/fig_PV_pub.pdf}}
-\hspace{0.02\textwidth}
-\subfloat[Supernate salinity vs gel molar volume\label{fig: CV}]
-{\includegraphics[width=0.48\textwidth]{figures/fig_CV_pub.pdf}}
-\caption{
-The compression of the gel in open system (solid lines) and in closed system (dotted lines). 
-Each solid curve corresponds to different salinity of the reservoir $\cs$ (see legend). Shadowed area limit the states with applied pressure below zero and above 5 bar.\label{fig: PV and CV}}
-\end{figure*}
-First, we run a set of simulations modeling the gel compression in \emph{open system}, \ie in equilibrium with a big bath of certain salinity, $\cs$. 
-The simulations are run for a set of different simulation box volumes. 
-Each simulation returns the averaged pressure, $P$, and the number of $\cl$ ions, which are present in the simulation box, $\ncl$.
-
-In order to get the partial pressure of the gel, we substitute from $P$ the osmotic pressure of ions in the reservoir: $\Pgel=P - \Pout$.
-$\Pout$, in turn, we calculate by running a separate simulation of a reservoir, containing ionic gas in equilibrium with the bath of the same salinity $\cs$. 
-The gel partial pressure, $\Pgel$, is the pressure that needs to be applied to the gel via a solvent permeable filter to compress the gel to a specific molar volume, $\Vgel$. 
-By gel molar volume $\Vgel$ we assume the volume of the gel calculated per on mol of gel monomer units.
-
-The dependencies of $\Pgel$ on $\Vgel$ are present in Figure \ref{fig: PV} for a set of different salinities. 
-These dependencies (the case of \emph{open system}) are represented by solid lines. 
-For example, the blue solid line illustrates the compression (or swelling) of the gel in equilibrium with a reservoir of salinity, $\cs=0.063$ mol/l. 
-The points where the pressure equals zero, $\Pgel=0$, (indicated by filled circles) are the gel \emph{free swelling equilibrium} states. 
-These states shift towards smaller volumes with increase of salinity. 
-In general, the increase of salinity shift all the $\Pgel(V)$ curves towards smaller volumes.
-This effect is well known and is typical for all branched \emph{strong} polyelectrolytes. 
-It is caused by the decrease of ions osmotic pressure and by a screening of electrostatic interactions \cite{Zhulina2000, Landsgesel2020a}.
-\footnote{The salinity dependence of the size of \emph{weak} polyelectrolyte gel is in general non-monotonic. We discuss this case in \cite{Rud2018}.}
-
-\begin{figure*}[t]
-\subfloat[Pressure vs gel molar volume \label{fig: NV}]
-{\includegraphics[width=0.49\textwidth]{figures/fig_NV_pub.pdf}}
-\subfloat[Salinity vs gel molar volume\label{fig: CN}]
-{\includegraphics[width=0.495\textwidth]{figures/fig_NVbox_mu_pub.pdf}}
-\caption{The compression of the gel in \emph{open system} (solid lines) and in \emph{closed system} (dotted lines). 
-Shadowed area limit the states with applied pressure below zero and above 5 bar.
-The values $N_\cl$ are the virtual numbers of present $\cl$ ions in \emph{closed system} simulation boxes.
-\label{fig: NV and CN}}
-
-%\todoi{Replace y-axis labels by $\ncl$}
-\end{figure*}
-
-\paragraph{Compression in closed system.}
-%Each set of simulations in \emph{open system} defines the free swelling equilibrium states of the gel for each salinity, \ie the state where the gel partial pressure equals zero. 
-The free swelling equilibrium states are characterized by the corresponding molar volume of the gel, $\Vgel^0$ and the amount of ions in gel \{$\Nna^0$, $\Ncl^0$\} 
-(Index ``0'' stands for zero bar applied pressure).
-We use these states as the starting ones for the gel compression in \emph{closed system}. 
-Thus, we simulate the compression of the gel in a closed volume, $\Vbox$, which is equal to $\Vgel^0$, and contains $\Ncl^0$ of $\cl$ ions and the $\na$ ions in the amount neutralizing the system, $\Nna^0 = $$\Ncl^0 + \Ngel$.
-
-We prepare two systems, one~--- simulating the gel of the volume $\Vgel$, and another~--- simulating the supernatant solution of the volume $\Vout = \Vbox - \Vgel$.
-Also, the ions of the amount $\Ncl^0$ and $\Nna^0$ are shared between the two volumes.
-
-The processes of the gel compression in \emph{closed} system are depicted in Figure~\ref{fig: PV} as dotted lines.
-In this plot, the blue dotted line, for example, illustrates the compression of the gel equilibrated with the solution of salinity $\cs=0.063$ mol/l, in a volume which gel has at zero pressure. 
-Since, in this case, the volumes of the gel $\Vgel$ and of the supernate $\Vout$ are comparable, the compression of the gel decreases the salinity of supernate, $\cs$. 
-%The supernate salinity now decreases with compression.
-This dependence is illustrated \reffig{fig: CV}, where the same swelling/compression processes are displayed in different coordinates: \ie salinity of supernate versus the gel molar volume, $\cs(\Vgel)$.
-In these coordinates, all the open system compressions show up as horizontal lines, which reflects the constant salinity, whereas the compressions in closed system demonstrate the change of $\cs$ from $\cs^{0}=0.063$ at zero pressure $\Pgel$ to $\cs^{5}=0.045$ mol/l at $P\gel=5$ bar (index ``5'' stands for 5 bar).
-
-Although the salinity during compression in \emph{open} system remains constant, the number of ions in a compression volume, \ie in the volume where the gel is compressed (or swells), changes.
-%As the compression volume $\Vbox$ we chose the volume of the free swelling equilibrium state of the gel, $\Vbox = \Vgel^0$.
-In the Figure \ref{fig: NV} we depicted the number of $\cl$ ions in the volume $\Vbox$, calculated per unit volume, $\ncl =$ $\Ncl/\Vbox$, as a function of the gel molar volume. 
-The depicted value can be considered as the density of $\cl$ ions averaged out over the compression volume $\Vbox$.
-
-As expected in the case of closed system compression these dependencies look like horizontal lines, whereas in an open system, the amount of ions in compression volume increases with compression. 
-This implies, that the compression of the gel in the open system pulls out the ions from the bath to the compression volume, $\Vbox$. 
-And vice versa, the swelling of the gel pushes ions out to the bath.
-
-Finally, in Figure \ref{fig: CN} the same processes are depicted in coordinates $\ncl$ --- $\cs$. 
-In these coordinates, both ways of the compression, in \emph{open} and in \emph{closed} system, appear as straight vertical and horizontal lines correspondingly.
-
-In our study, we modeled the compression of the gel in equilibrium with reservoirs of 40 different salinities, ranging from 0.001 to 0.5 mol/l. 
-Every open system compression resulted in a defined free swelling equilibrium state, which we used as the initial ones for the compression in closed systems. 
-All the corresponding dependencies are depicted in Figures~\ref{fig: PV and CV} and \ref{fig: NV and CN} as thin grey dashed lines (some of them are highlighted and colored).
-The states corresponding to $P^{gel}=0$, 5 and 10 bar pressure are marked by open circles, squares, and crosses respectively. 
-The non-shadowed areas in the Figures highlight the states in which the gel partial pressure ranges between 0 and 5 bar.
-
-\paragraph{Desalination scheme.}
-As we have seen, the compression of the gel in a closed system affects the salinity, whereas the compression in an open system affects the amount of ions in a volume where the gel is compressed in. 
-Here we show how to employ these phenomena for water desalination. 
-The highlighted colored lines on plots of Figures \ref{fig: PV and CV} and \ref{fig: NV and CN} form a sequence of the following one by each other swellings and compressions of the hydrogel, correspondingly in \emph{open} and \emph{closed} systems.
-This sequence forms the water desalination process.
-Starting from swelling the gel in the \emph{open} system at high salinity ($\cs=0.091$ mol/l, solid black line), the gel gets compressed in \emph{closed} system until the pressure reaches 5 bar (dashed black line).
-Then the same gel swells in a reservoir of a bit lower salinity (\ie $\cs=0.064$ mol/l, light blue line). 
-After swelling, the gel is compressed again by the pressure of 5 bar in \emph{closed} system (dashed light blue line).  
-Then the gel is put swelling in a reservoir of even smaller salinity ($\cs=0.045$ mol/l, solid yellow line). 
-And so on. 
-The chain of alternating swelling and compression steps ends up when salinity gets equal to $\cs=4\cdot10^{-3}$ mol/l after compression in closed system (dashed magenta line).
-
-The plots of Figures \ref{fig: PV and CV} and \ref{fig: NV and CN} depict the whole process in all the possible coordinates
-In all the plots the whole process looks like a staircase, especially in the Figure~\ref{fig: CN}, where open system processes are horizontal lines and closed system are vertical ones, a 'staircase' has rectangular steps
-
-%\begin{enumerate}
-%    \item as gel partial pressure versus gel molar volume, $\Pgel(\Vgel)$ (\ref{fig: PV}), 
-%    \item as supernatant salinity versus gel molar volume, $\cs(\Vgel)$ (\ref{fig: CV}),
-%    \item the amount of $\cl$ ions in a compression volume versus gel volume, $\ncl(\Vgel)$ (\ref{fig: NV}), 
-%    \item $\ncl$ as function of supernatant salinity.
-%\end{enumerate}
-
-%Then we repeat the simulation of hydrogel swelling in open system but setting as a salinity of the reservoir the new, obtained from the previous process, value $\cs=$ 0.045 mol/l. 
-%Again, as soon as we obtain the free swelling equilibrium state (at new salinity), with corresponding new values of $V\gel$ and $\ncl$, we start simulating the compression in closed system.
-Now the salinity changes again, decreasing from 0.045 to 0.031 mol/l (at 5 bar).
-%These two processes are depicted by solid and dotted yellow lines in Figure~\ref{fig:fig_PV}.
-%The Figure shows also the repetition of this procedure three more times until the salinity reaches the value $\cs=0.01$ mol/l. 
-%The last dashed magenta line shows the compression in closed system which ends up with $\cs=4\cdot10^{-4}$ mol/l. 
-%Schematically this process is depicted in the inset to the plot.
-
-%The same process is depicted on Figure~\ref{fig:fig_CV} but in different coordinates: salinity versus volume. 
-%In this coordinates the swelling in open system appear to be horizontal line, since the salinity in this process is constant. 
-%Again we start from swelling in open system untill the gel reaches its free swelling equilibrium (solid blue line).
-%Then the gel is compressed in closed system (dashed blue line), ending up in a state with applied to the gel pressure 5 bar. 
-%In this process the surrounding solution salinitiy changes from 0.064 to 0.045 mol/l.
-%Then the gel again swells in open system, but at new salinity.
-
-\paragraph{The efficiency of desalination.}
-The theoretical minimum specific energy for seawater desalination (
-%$\cs=35$ g/l, 
-$\cs\simeq0.6$ mol/l as for pure NaCl) is $\sim3.9$ kJ/l (1.1 kWh/m$^3$) for 50\% recovery \cite{Wang_2020}.
-This value is calculated as follows 
-\begin{equation}
-W=2RT\left(\frac{c_{f}}{R_{w}}\ln\frac{c_{b}}{c_{f}}-c_{p}\ln\frac{c_{b}}{c_{p}}\right)
-\label{eq:SEC}
-\end{equation}
-where $R$ is a universal gas constant, $c_{f}$ is the salinity of feed water, $c_p$~--- of product water and $c_b$~--- the salinity of the brine, which necessarily appears in any desalination process.
-$R_{w}$ is a recovery ratio, \ie the ratio between volume of produced water and the volume of the feed water. 
-50\% recovery ratio means that one part of feed water divides into two equal volume solutions of the product water and of the brine.
-Of course, a significant amount of additional energy is required to operate the system\cite{Kim_2019}. 
-It has been reported that the specific energy consumption (SEC) of reverse osmosis (RO) process is 2.5~-- 4.0 kWh/m3 (9~-- 14.4 kJ/l), which is significantly higher than its minimum specific energy.
-The SEC of a real-scale RO plant is even higher, approximately 3.5~-- 4.5 kWh/$m^{3}$ (12.6 - 16.2 kJ/L), including pre-treatment and post-treatment processes \cite{Kim_2018}. 
-%Because of the inherent high energy requirement for RO desalination, seawater is not commonly utilized over traditional surface water.
-
-In order to compare the efficiency of the process presented in \ref{fig: PV and CV} and \ref{fig: NV and CN} with provided values, we collect the corresponding data to the Table~\ref{tab: table}.
-The presented desalination process is a cascade of six swellings in open system, at six different (constant) salinities $\cs$, each followed by six compressions in closed system, at six different (constant) $\ncl$.
-Each swelling and compression process is presented as a row of Table~\ref{tab: table}, which is colored by matching the lines in the Figures.
-The first column of the table contains values $\cs^0$ and $\cs^5$, which stand for the supernate salinity at 0 and 5 bar compression; in open system, supernate salinity does not change, so $\cs^0$ and $\cs^5$ are presented by a single number.
-The second column contains values of $n^0$ and $n^5$, which stand for the number of $\cl$ ions in compression volume $\Vbox$, at 0 and 5 bar pressure (divided by $\Vbox$). 
-The number of ion does not change in closed system compression, thus $n^0$ and $n^5$ are the same in the corresponding rows.
-The third column shows the change of the gel volume in corresponding process, $\Delta v$. 
-The fourth column contain the work needed for the compression in the corresponding process, calculated per volume of extracted solution. 
-This value is an integral of corresponding $\Pgel(\Vgel)$ dependence
-\begin{equation}
-    W = \frac{\int_{v^0}^{v^5} \Pgel d\Vgel}{\Delta v}
-\end{equation}
-Here, in the table, we present the absolute values of the work, whereas one should keep in mind that the compression implies the work is done by external force and the swelling implies that the work is done by gel.
-
-\begin{table}
-\begin{tabular*}{1\textwidth}{@{\extracolsep{\fill}}ll|lc|c|l|ll}
-\multicolumn{1}{l|}{$c_{s}^{0}$, mM} & $c_{s}^{5}$, mM & \multicolumn{1}{l|}{$n_{\cl}^{0}$, mM} & $n_{\cl}^{5}$, mM & $\Delta \Vgel$, l & $|W$\textbar , J/l & \multicolumn{2}{c}{$W^{id}$, J/l}\tabularnewline
-\hline 
-\hline 
-\multirow{2}{*}{{\small{}$91.47$}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{{\small{}$57.08\pm0.122\enskip\longrightarrow$}} & \multirow{2}{*}{{\small{}2.74}} & \multirow{2}{*}{{\small{}$95.4\pm1.9$}} &  & \multirow{2}{*}{}\tabularnewline
- &  & \multicolumn{2}{r|}{{\small{}$71.75\pm0.024$}} &  &  & \multirow{8}{*}{{\small{}\hspace{-1em}}\textcolor{teal}{\small{}$\left.\begin{array}{l}
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\end{array}\right\rbrace $$\rotatebox{90}{\hspace{-5em}{\color{teal}\ensuremath{\begin{array}{cc}
-W^{\mathrm{sim}}= & 202.8\pm3.2\\
-W^{id}= & 52.9\\
-R_{w}= & 0.54
-\end{array}}}}$}} & \tabularnewline
-\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
-\multicolumn{2}{l|}{{\small{}$89.41\pm0.23\enskip\longrightarrow$}} & \multirow{2}{*}{{\small{}56.90}} & \multirow{2}{*}{} & \multirow{2}{*}{{\small{}2.72}} & \multirow{2}{*}{{\small{}$109.1\pm1.7$}} &  & \multirow{2}{*}{}\tabularnewline
-\multicolumn{2}{r|}{{\small{}$73.63\pm0.03$}} &  &  &  &  &  & \tabularnewline
-\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
-\multirow{2}{*}{\textcolor{teal}{\small{}63.93}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{teal}{\small{}$37.28\pm0.08\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{teal}{\small{}3.26}} & \multirow{2}{*}{\textcolor{teal}{\small{}$100.9\pm1.7$}} &  & \tabularnewline
- &  & \multicolumn{2}{r|}{\textcolor{teal}{\small{}$50.579\pm0.013$}} &  &  &  & \multirow{8}{*}{{\small{}\hspace{-1em}}\textcolor{olive}{\small{}$\left.\begin{array}{l}
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\end{array}\right\rbrace $$\rotatebox{90}{\hspace{-5em}\ensuremath{\begin{array}{cc}
-W^{\mathrm{sim}}= & 207.3\pm2.2\\
-W^{id}= & 38.2\\
-R_{w}= & 0.53
-\end{array}}}$}}\tabularnewline
-\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
-\multicolumn{2}{l|}{\textcolor{teal}{\small{}$62.05\pm0.15\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{teal}{\small{}37.17}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{teal}{\small{}3.18}} & \multirow{2}{*}{\textcolor{teal}{\small{}$107.4\pm1.4$}} &  & \tabularnewline
-\multicolumn{2}{r|}{\textcolor{teal}{\small{}$48.21\pm0.02$}} &  &  &  &  &  & \tabularnewline
-\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
-\multirow{2}{*}{\textcolor{olive}{\small{}44.91}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{olive}{\small{}$23.75\pm0.06\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{olive}{\small{}3.82}} & \multirow{2}{*}{\textcolor{olive}{\small{}$106.7\pm1.5$}} &  & \tabularnewline
- &  & \multicolumn{2}{r|}{\textcolor{olive}{\small{}$35.911\pm0.010$}} &  &  & \multirow{8}{*}{{\small{}\hspace{-1em}}\textcolor{red}{\small{}$\left.\begin{array}{l}
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\end{array}\right\rbrace \rotatebox{90}{\hspace{-5em}\ensuremath{\begin{array}{cc}
-W^{\mathrm{sim}}= & 222.3\pm2.5\\
-W^{\mathrm{id}}= & 43.8\ {\color{red}{\scriptstyle (41.0)}}\\
-R_{w}= & 0.52\ {\scriptstyle (0.46)}
-\end{array}}}$}} & \tabularnewline
-\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
-\multicolumn{2}{l|}{\textcolor{olive}{\small{}$43.46\pm0.12\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{olive}{\small{}24.27}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{olive}{\small{}3.91}} & \multirow{2}{*}{\textcolor{olive}{\small{}$106.4\pm1.1$}} &  & \tabularnewline
-\multicolumn{2}{r|}{\textcolor{olive}{\small{}$30.795\pm0.008$}} &  &  &  &  &  & \tabularnewline
-\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
-\multirow{2}{*}{\textcolor{red}{\small{}31.93}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{red}{\small{}$14.66\pm0.04\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{red}{\small{}4.20}} & \multirow{2}{*}{\textcolor{red}{\small{}$107.9\pm1.4$}} &  & \tabularnewline
- &  & \multicolumn{2}{r|}{\textcolor{red}{\small{}$25.297\pm0.006$}} &  &  &  & \multirow{8}{*}{{\small{}\hspace{-1em}}\textcolor{orange}{\small{}$\left.\begin{array}{l}
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\end{array}\right\rbrace \rotatebox{90}{\hspace{-5em}\ensuremath{\begin{array}{cc}
-W^{\mathrm{sim}}= & 218.7\pm2.2\\
-W^{id}= & 66.6\ {\scriptstyle (22.0)}\\
-R_{w}= & 0.53\ {\scriptstyle (0.49)}
-\end{array}}}$}}\tabularnewline
-\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
-\multicolumn{2}{l|}{\textcolor{red}{\small{}$30.03\pm0.08\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{red}{\small{}14.55}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{red}{\small{}$\begin{array}{c}
-4.17\\
-{\scriptstyle (3.22)}
-\end{array}$}} & \multirow{2}{*}{\textcolor{red}{\small{}$\begin{array}{c}
-115.6\pm0.9\\
-{\scriptstyle (57.3)}
-\end{array}$}} &  & \tabularnewline
-\multicolumn{2}{r|}{\textcolor{red}{\small{}$\begin{array}{c}
-18.585\pm0.004\,\\
-{\scriptstyle (22.32)}
-\end{array}$}} &  &  &  &  &  & \tabularnewline
-\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
-\multirow{2}{*}{\textcolor{orange}{\small{}22.30}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{orange}{\small{}$8.84\pm0.03\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{orange}{\small{}$\begin{array}{c}
-4.75\\
-{\scriptstyle (3.76)}
-\end{array}$}} & \multirow{2}{*}{\textcolor{orange}{\small{}$\begin{array}{c}
-108.1\pm1.3\\
-{\scriptstyle (68.3)}
-\end{array}$}} &  & \tabularnewline
- &  & \multicolumn{2}{r|}{\textcolor{orange}{\small{}$\begin{array}{c}
-\text{17.945}\pm\text{0.004}\\
-{\scriptstyle (14.56)}
-\end{array}$}} &  &  & \multirow{7}{*}{{\small{}\hspace{-1em}}\textcolor{magenta}{\small{}$\left.\begin{array}{l}
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\end{array}\right\rbrace \rotatebox{90}{\hspace{-5em}\ensuremath{\begin{array}{cc}
-W^{\mathrm{sim}}= & 227.5\pm2.3\\
-W^{id}= & 69.7\\
-R_{w}= & 0.55
-\end{array}}}$}} & \tabularnewline
-\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
-\multicolumn{2}{l|}{\textcolor{orange}{\small{}$20.74\pm0.06\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{orange}{\small{}8.83}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{orange}{\small{}$4.71$}} & \multirow{2}{*}{\textcolor{orange}{\small{}$110.8\pm0.8$}} &  & \tabularnewline
-\multicolumn{2}{r|}{\textcolor{orange}{\small{}$11.082\pm0.002$}} &  &  &  &  &  & \tabularnewline
-\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
-\multirow{2}{*}{\textcolor{magenta}{\small{}10.90}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{magenta}{\small{}$3.00\pm0.01\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{magenta}{\small{}6.08}} & \multirow{2}{*}{\textcolor{magenta}{\small{}$106.9\pm1.1$}} &  & \tabularnewline
- &  & \multicolumn{2}{r|}{\textcolor{magenta}{\small{}9.011$\pm$0.002}} &  &  &  & \tabularnewline
-\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
-\multicolumn{2}{l|}{\textcolor{magenta}{\small{}$9.83\pm0.05\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{magenta}{\small{}3.12}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{magenta}{\small{}5.78}} & \multirow{2}{*}{\textcolor{magenta}{\small{}$119.4\pm1.0$}} &  & \tabularnewline
-\multicolumn{2}{r|}{\textcolor{magenta}{\small{}$3.862\pm0.001$}} &  &  &  &  &  & \tabularnewline
-\end{tabular*}
-
-\caption{The estimates of the efficiency of the desalination process. All the units are calculated per one mol of gel segments. Values in brackets
-are the estimates corresponding to crossection of 'red' and 'orange' lines on the plots of Figures \ref{fig: PV and CV} and \ref{fig: NV and CN}
-\label{tab: table}}
-\end{table}
-
-To give a clue of comparison with ideal desalination process efficiency, in the fifth column we provided the values of specific energy consumption, $W^\text{id}$, which are calculated by means of \refeq{eq:SEC} as follows.
-We consider, for example, the solution of concentration $\cs^f=44.91$ mmol/l as a feed solution, and the solutions of $\cs^p=31.93$ mmol/l and $\cs^b = 63.93$ mmol/l 
-correspondingly as produced product and brine solutions.
-\begin{enumerate}
-    \item first, the gel, equilibrated with feed solution, is getting compressed in a closed system.
-    The volume of the gel changes by $\Delta v^p = 3.69$ l  and the salinity of supernate decreases from $\cs^f$ to $\cs^p$.
-    The volume of product solution equals $\Delta v^p$
-    \item Then the squeezed gel is put back into the feed solution and is getting equilibrated there under pressure, so it does not swell. 
-    \item After equilibration the gel is let to swell in a closed system such that the salinity of the external solution increases reaching the value of $\cs^b$.
-    \item Finally, the gel is taken out and squeezed by 5 bar in an open system in equilibrium with the bath of the brine. 
-    The change of the gel volume in this process is $\Delta v^b = 3.26$ l/mol, which equals the volume of the produced brine. 
-\end{enumerate}
-Thus the recovery ratio $R_w = \Delta v^p / (\Delta v^p + \Delta v^b) \simeq $ 0.53 and the theoretical minimum specific energy of desalination with corresponding $\cs^f$, $\cs^p$ and $\cs^b$ is $W^{id} =$ 38.2 J/l (\refeq{eq:SEC}).
-
-Such estimations are provided in the fifth column of the table, for five triplets of values $\cs^f$, $\cs^p$, and $\cs^b$.
-$W_{\mathrm{sim}}$ is the energy calculated by integration of $\Pgel(\Vgel)$ dependencies~--- sum of corresponding comressions in closed and open systems, $W_{\mathrm{id}}$~--- the estimate based on the equation \refeq{eq:SEC} and $R_w$~--- is the corresponding recovery ratio.
-Note that calculating the $W_{\mathrm{sim}}$ we accounted for only the work done on the gel during compression, whereas the work done by the gel itself during swelling was not taken into account.
-The ratio between $W_{\mathrm{sim}}$ and $W_{\mathrm{id}}$ ranges from 3.26 to 5.43, which is comparable to that of RO.
-
-\section{Conclusions}
-We have modeled the compression of the gel in thermodynamic equilibrium with the reservoir of the limited amount of water.
-We have shown that in the case of gel made of strong polyelectrolyte, the compression always decreases the surrounding salinity.
-We have modeled the process of water desalination by combining two processes: 
-(1) the swelling of the gel in \emph{open} system, exchanging ions with a big reservoir at constant salinity. 
-(2) the compression of the gel in \emph{closed} system, when the gel affects the salinity in the surrounding solution.
-We estimated the energy needed to produce one liter of water and have shown that the method may compete with the modern technologies used in modern industry.
-
-\section*{Acknowledgments}
-
-This research was supported by the Czech Science Foundation (grant 19-17847Y)
-Government of Russian Federation, grant number 14.W03.31.0022. 
-Computational resources were supplied by the project ``e-Infrastruktura CZ'' (e-INFRA LM2018140) provided within the program Projects of Large Research, Development and Innovations Infrastructures.
-
+\bibliographystyle{unsrt}
 \bibliography{lit/gibbs}
-
-\newpage
-%\listoftodos
-
 \end{document}

### 2022-10-14 MDPI/reviewer2.tex
proofreading

--- 2022-10-14 MDPI/reviewer1.tex
@@
 
-\textbf{Reviewer 1}
-\textit{}
+\textbf{Reviewer 2}
+\textit{This manuscript is about creating a new model the thermodynamic equilibrium between coexisting phases of the gel and supernate aqueous solution.}
+\begin{enumerate}
 
-\begin{enumerate}
-\item \textit{The main findings of your results should be highlighted in abstract}
+\item \textit{Abstract needs to re-write as and please follow the IMRAD instruction.}
 
-We have rewritten the abstract.
+We have rewritten the abstract. We believe that the abstract is much more attractive now.
+\item \textit{There is introduction in the abstract, however, it needs to write more about the aim of this work, method, result and conclusion.}
 
-\item \textit{Please do not separate introduction in three sections combine with problem and technology you used and challenges and your solutions.}
+Corrected
+\item \textit{Avoid to use word 'we' in the abstract as well as manuscript.}
 
-We have rewritten the Introduction section.
-We wanted to keep the separation of the Introduction section into the respective subsections because the Introduction is relatively lengthy, so we believe that dividing it into subsections reduces its readability.
+Corrected.
+\item \textit{line 247 in what table?}
 
-\item \textit{In page 4 heading 2. (How to start with and ??)}.\\
-Corrected.
+We meant Table 1. Corrected in text.
+\item \textit{Where is the method of this work?}
 
-\item \textit{All formula and models should be supported with reference for instant equation 3.}
-Corrected
+The method idea is outlined in the paragraph "Physics behind the desalination process" and described in the section "Model and methods". 
+%We did not want to bother the readers too much with technical aspects of the smulations, so technical details are in ESI.
+\item \textit{It is suggested that to carefully improve this manuscript as well as the writing and grammatical error.}
 
-\item \textit{In page 6, please remove the footer, it is not a book to describe issues below}.\\
-Corrected. Now this sentence appears in text (in brackets).
+We improved the writing style of the manuscript and corrected the grammatical errors.
 
-\item \textit{How do you think control factors in open system such as pressure and temperature}
+\item \textit{Please explain more detail about the process, how the process run and how the data could be explained and become more interesting for reader.}
 
-In our simulation, we control the volume of the simulation box and measure the pressure using the virial theorem.
-The pressure value which is depicted in the Figures assumed to be a partial pressure of the gel, which is calculated as the difference between the pressure in the gel and the pressure calculated in a separate simulation box containing only ions (with no gel).
-Temperature assumed to be constant and equal to 300 K, which is guaranteed by applying a Langevin thermostat.
+Added corresponding paragraph in ``Model and methods `` section
 
@@
 
+%~ \bibliographystyle{unsrt}
+%~ \bibliography{desalination}
 \bibliographystyle{unsrt}

### 2022-10-14 MDPI/reviewer3.tex
proofreading

--- 2022-10-14 MDPI/reviewer2.tex
@@
 
-\textbf{Reviewer 2}
-\textit{This manuscript is about creating a new model the thermodynamic equilibrium between coexisting phases of the gel and supernate aqueous solution.}
+\textbf{Reviewer 3}
+
+\textit{}
 \begin{enumerate}
+\item \textit{The full stop in the title should be revised.}
 
-\item \textit{Abstract needs to re-write as and please follow the IMRAD instruction.}
+Noted. Revised.
+\item \textit{The abstract needs to be revised and be more attractive. The research gap, novelty and main findings should be concisely mentioned in the abstract.}
 
 We have rewritten the abstract. We believe that the abstract is much more attractive now.
-\item \textit{There is introduction in the abstract, however, it needs to write more about the aim of this work, method, result and conclusion.}
+\item \textit{In this current shape, the manuscript looks like a report. The authors have to revise the flow of the context to attract the readers.}
 
-Corrected
-\item \textit{Avoid to use word 'we' in the abstract as well as manuscript.}
-
-Corrected.
-\item \textit{line 247 in what table?}
-
-We meant Table 1. Corrected in text.
-\item \textit{Where is the method of this work?}
-
-The method idea is outlined in the paragraph "Physics behind the desalination process" and described in the section "Model and methods". 
-%We did not want to bother the readers too much with technical aspects of the smulations, so technical details are in ESI.
-\item \textit{It is suggested that to carefully improve this manuscript as well as the writing and grammatical error.}
+We have revised and changed the manuscript to be more attractive for the readers. 
+\item \textit{The manuscript must be improved by checking once again in English and technical writing. }
 
@@
 
-\item \textit{Please explain more detail about the process, how the process run and how the data could be explained and become more interesting for reader.}
+\item \textit{The whole manuscript must be supported by enough recent references. Revise the whole context.}
 
-Added corresponding paragraph in ``Model and methods `` section
+We added more recent references.
+\item \textit{The beginning of the introduction part must be revised to be more attractive.}
 
+Corrected. We have rewritten the Introduction section.
+\item \textit{The authors can follow the following references to generally highlight the global contamination and environmental pollution problems at the beginning of the introduction part \\ \href{https://doi.org/10.1016/j.jwpe.2022.102847}{https://doi.org/10.1016/j.jwpe.2022.102847} ;\\
+\href{https://doi.org/10.1016/j.ceramint.2022.05.151}{https://doi.org/10.1016/j.ceramint.2022.05.151} ;\\
+\href{https://doi.org/10.3390/catal12050500}{https://doi.org/10.3390/catal12050500} ; \\
+\href{https://doi.org/10.1007/s11356-022-21160-7}{https://doi.org/10.1007/s11356-022-21160-7} ;\\
+\href{https://doi.org/10.3390/ma15134547}{https://doi.org/10.3390/ma15134547}. \\
+Then, highlight the water desalination technologies and Gibbs ensemble\\
+(\href{https://doi.org/10.3390/nano10020293}{https://doi.org/10.3390/nano10020293}).}
+
+Corrected. We added the citations, which are relevant to the studied problems, in their appropriate places.
+\item \textit{Authors should indicate a clear gap in knowledge which this study seeks to bridge, and potentially contribute to knowledge. }
+
+The purpose of our paper is to show that desalination using polyelectrolyte hydrogels is a cheap and therefore competitive alternative to reverse osmosis.
+We highlighted this idea in the Introduction and Conclusion sections.
+\item \textit{L 125-126, meaningless sentence. Revise the whole context.}
+
+Corrected.
+\item \textit{All sections/subsections titles must be revised to be expressive.}
+
+Corrected. We have rewritten and improved not only the Introduction, but the sections Model and Methods, Results, Conclusions as well.
+\item \textit{Statistical physics considerations including setup and calculations should be added.}
+
+We rewritten the section ``Model and methods'' and added there a detailed explanation of our methodology.
+\item \textit{The authors should identify the limitations of this study and the recommended future studies in the conclusion part.}
+
+We identified the study limitations and considered the implications and future perspectives of the study. We added the respective paragraphs.
 \end{enumerate}

### 2022-10-14 MDPI/proof/manuscript.v5/diff.sh

@@ -1,0 +1,3 @@
+latexdiff orig.tex edit.tex  > diff.tex
+latexmk -pdf -f diff.tex
+evince diff.pdf

### 2024-07-15 MDPI/proof/manuscript.v5/edit.tex
Cleaned up files. Article moved to MDPI directory

--- 2022-10-14 MDPI/proof/manuscript.v5/gels-1883243-english_edit.tex
@@
 \copyrightyear{2022}
-\externaleditor{Academic Editor: \hl{Firstname Lastname}} %MDPI: please add the Academic Editor
+%\externaleditor{Academic Editor: \hl{Firstname Lastname}} %MDPI: please add the Academic Editor
 \datereceived{9 August 2022} 
@@
 
-\section{\highlighting{Model and Methods} %MDPI: to AE: please note that the section title in Gels Template: 1. Introduction; 2. Results and Discussion; 3. Conclusions; 4. Materials and Methods
-\label{sec: theory}}
-
+%\section{\highlighting{Model and Methods} %MDPI: to AE: please note that the section title in Gels Template: 1. Introduction; 2. Results and Discussion; 3. Conclusions; 4. Materials and Methods
+%\label{sec: theory}}
+\section{Results and Discussion\label{sec: RD}}
 % water desalination technologies and Gibbs ensemble (https://doi.org/10.3390/nano10020293 \cite{erdos2020}).
@@
 	\caption{The hydrogel compressed in \emph{open} and in \emph{closed} system.
-		Red and blue circles represent $\na$ and$\cl$ ions. $V_0$ is the volume which gel has in free swelling equilibrium state.\label{fig:open and closed}}
+		Red and blue circles represent $\na$ and $\cl$ ions. $V_0$ is the volume which gel has in free swelling equilibrium state.\label{fig:open and closed}}
 \end{figure}
@@
 Mechanical movement and the exchange of ions occur simultaneously in reality; however, we simulate them as alternating in a stop--run mode. 
-To sample mechanical properties of the gel and reservoir, we use MD simulation, whereas to sample the ion distribution between the gel and a reservoir, we use MC simulation.
-The details of this hybrid MCMD computational technique can be found in our previous studies of polyelectrolytes in open systems \cite{Rud2020, Rud2022, Landsgesel2020a}.
-
-\subsection{Molecular Dynamics}
-
-We model the gel as a network of 16 linear polymer chains, each consisting of 30~monomer units.
-These polymer chains are connected to a diamond-like network by eight~crosslinking units.
-This means there are $\Ngel=16\cdot30 + 8=488$ gel monomers in the simulation box (see \reffig{fig:diamond}).
-The network is put in a simulated cubic box with volume $\Vgel$ with periodic boundary conditions, which virtually emulates an infinite polymer~network.
-\begin{figure}[H]
-
-\includegraphics[width=0.7\textwidth]{{figures/simgibbs}.pdf}\caption{Diamond-like network in the simulation box. Color code represents
-the individual ion types (red: $\na$, blue: $\cl$)
-and the hydrogel (gray: neutral segment ($\AH$), cyan: charged segment
-($\A$)). \label{fig:diamond}}
-\end{figure}
-Each monomer unit of the network carries a negative elementary electric charge.
-Except for the gel monomers, the monovalent co- and counter-ions, $\cl$ and $\na$, are present in the simulation box.
-The total electric charge of all the particles in the box is zero; therefore the number of $\na$ ions exceeds the number of $\cl$ ions by $\Ngel$.
-
-Each pair of particles interact via the truncated Lennard--Jones interaction potential, which imposes strong repulsion between all particles at short distances:
-\begin{equation}
-    \begin{split}\label{eq:LJ}
-        V_\mathrm{LJ}(r) =
-        \begin{cases}
-            4 \varepsilon \left( \left(\cfrac{\sigma}{r}\right)^{12}
-            - \left(\cfrac{\sigma}{r}\right)^6\right)
-            & \mathrm{if~} r < r_\mathrm{cut}\\
-            0
-            & \mathrm{elsewhere}
-        \end{cases},
-    \end{split}
-\end{equation}
-where 
-$r$ is the interparticle distance, 
-$\sigma = 0.35~\mathrm{nm}$ is a chosen characteristic size of the particles, 
-$\varepsilon = \kT$ is the depth of the potential, and 
-$r_\mathrm{cut}$ is the cut-off distance beyond which the potential is set zero.
-
-The bonds connecting the gel to a network are modeled using finite extension nonlinear elastic potential (FENE)
-\begin{equation}\label{eq:fene}
-V_\mathrm{FENE}(r) = -\frac{1}{2} K \Delta r_\mathrm{max}^2\ln \left[ 1 - \left(\frac{r-r_0}{\Delta r_\mathrm{max}} \right)^2 \right ],
-\end{equation}
-where
-$r$ is the distance between the bonded segments,
-$K$ is the magnitude of their interaction,
-$\Delta r_{\mathrm{max}}$ is the maximal stretching length of the bond, and
-$r_0$ is the equilibrium bond length.
-For our simulations, we chose $K = 10 \kT/\sigma^{2}$, $\Delta r_{\mathrm{max}} = 2 \sigma$, and $r_0 = 1.0\sigma$~\cite{Jin2007}.
-
-All the charged particles interact via Coulomb electrostatic potential:
-\begin{equation}
-    V_{\mathrm{EL}}=\lb\kT \cfrac{q_{1}q_{2}}{r},
-\end{equation}
-where $\lb$ is Bjerrum length---$\lb = 2\sigma = 0.7~\mathrm{nm}$, which corresponds to the  Bjerrum length in water at temperature $T=300~\mathrm{K}$---and $\kB$ is the Botlzman constant.
-In that sense, the solvent (water) is accounted for in the model implicitly via setting up dielectric permittivity $\epsilon=80$.
-
-We used the Langevin thermostat, \ie two additional terms for force in the equation of motion were added
-\begin{equation}
-\mathbf{f}_i =  -\gamma \mathbf{v}_i(t)+\sqrt{2\gamma \kT }\boldsymbol{\eta}_i(t),
-\end{equation}
-where the first term corresponds to constant friction, with $\gamma$ being a friction coefficient,
- and the second term corresponds to random thermal force, with $\boldsymbol{\eta}_i$ being a normally distributed random vector; $\mathbf{v}_i$ is the velocity of the $i$-th particle (for details see \cite{Grest1986}).
-
-\subsection{Monte Carlo Sampling in an Open System}
-The Monte Carlo scheme for sampling the exchange of ions in an \emph{open system} is based on the formula for free energy of grand canonical ensemble $\Omega$
-\begin{equation}
-    \Omega_{\mathrm{open}}=E-TS+\sum_i\mu_i N_i\label{eq:Omega-GC}
-\end{equation}
-where $E$ is internal energy, $T$ is temperature, $S$ is entropy, $N_i$ is the number of ions of type $i\in\{\na,\ \cl\}$, and $\mu_i$ is the corresponding chemical potential.
-
-%Our model system represents a finite volume $V$ which exchanges particles with the bath of infinite volume.
-%The infinity of the volume means, that the particle exchange between the system and the bath does not influence on the chemical potentials in the bath.
-%Such ensemble is called grand canonical ensemble; the free energy in this ensemble, the Landau potential, is
-The entropy $S$ is given by the Boltzmann formula~\cite{Nagle2004}
-\begin{equation}
-    S=\kB\sum_i\ln\frac{\Vgel^{N_i}}{N_i!}\label{eq:entropy}
-\end{equation}
-%\todo{for partiles without interactions}
-which accounts for two contributions:
-\begin{enumerate}
-    \item The combinatorial entropy $S_{c}=-\kB\sum_i\ln N_i!$, which reflects the freedom of choice among the particles;
-    \item The mixing entropy $S_{m}=\kB \sum_i N_i\ln \Vgel$, which reflects the freedom to place the chosen particle randomly within the simulation box. 
-\end{enumerate}
-
-$\Vgel$ is the unitless volume, \ie the volume measured in units of $\sigma^3$. 
-Thus, the change of free energy associated with an exchange of ion pairs is
-\begin{equation}
-\Delta\Omega_\mathrm{open}=\kT\ln\prod_i\left(\Vgel^{\xi}\frac{N_i!}{\left(N_i+\xi\right)!}\right)+\xi\sum_i\mu_i+\Delta E
-\label{eq: DeltaG GC}
-\end{equation}
-where $\xi$ is an algebraic number of inserted (or removed) ion pairs; in general, $\xi$ can be any number, but when $\xi = \pm 1$, which corresponds to addition or removal of only one ion pair,  \refeq{eq: DeltaG GC} gets simplified
-\begin{equation}
-    \Delta\Omega_\mathrm{open}=\kT\ln \Vgel^{2\xi} \prod_i \left(N_i+\theta(\xi)\right)^{-\xi}+\xi\sum_i\mu_i+\Delta E
-\label{eq: DeltaG GC_simpl}
-\end{equation}
-where $\theta$ is the Heaviside function; $\theta(\xi) = 1$ if $\xi=+1$; $\theta(\xi) = 0$ if $\xi=-1$.
-
-The procedure for Monte Carlo sampling is as follows: \cite{Frenlkel2002_book}
-\begin{enumerate}
-	\item Propose the new configuration of the system by insertion (or deletion) of an ion pair, $\xi=\pm1$;
-	\item Accept the new configuration if
-	\begin{equation}
-        \mathcal{R}^{\xi}<e^{\Delta\Omega_\mathrm{open}/\kT}=\Vgel^{2\xi} \prod_i \left(N_i+\theta(\xi)\right)^{-\xi}e^{\left(\Delta E+\xi\mu\right)/\kT}\label{eq: GC acceptance}
-	\end{equation}
-	where $\mathcal{R}$ is a uniformly distributed random number in the range between $0$ and $1$;
-	\item Then, collect the number of ions, $\Nna$ and $\Ncl$, to the samples array.
-\end{enumerate}
-
-\subsection{Monte Carlo Sampling in Closed System}
-
-In the \emph{closed system}, the gel exchanges particles with the explicit finite reservoir box. 
-The total number of ion species in both boxes is fixed, whereas the density of ions in the external reservoir is defined by thermodynamic equilibrium between the two subvolumes (see \reffig{fig:open and closed}b.
-Monte Carlo sampling of the distribution of ions between the subvolumes is performed in a way similar to that described in \cite{Panagiotopoulos1988b, Erdos2020}.
-
-The free energy of the Gibbs ensemble is a sum of the gel's free energy and that of the external volume.
-\begin{equation}
-    \Omega_{\mathrm{closed}}=\Egel-T\Sgel + \Eout-T\Sout \label{eq:Omega-GC}
-\end{equation}
-Using reasoning similar to that of the \emph{open system}, one can derive the change of free energy associated with ion-pair exchange 
-\begin{equation}
-\Delta \Omega_{\mathrm{closed}} =2 k_B T \ln \left(\frac{\Vgel}{\Vout} \right) ^ {\xi}\prod_i \left(\frac{N_{i}\gel+\theta(\xi)}{N_{i}\out+\theta(-\xi)}\right)^{-\xi} + \Delta \Egel + \Delta \Eout
-\end{equation}
-where $\xi$ defines the direction of the trial move, so that $\xi = -1$ when an ion pair moves from the gel to the outside volume, and  $\xi = +1$ otherwise; $\Delta \Egel$ and $\Delta \Eout$ are corresponding changes of the potential energy of the gel and the outside volumes, respectively.
-
-Then, the procedure for sampling is the same as that of the \emph{open system}: (1) propose the move of an ion pair; (2) accept a new state if $\mathcal{R}^{\xi}<\exp({\Delta\Omega_\mathrm{closed}/\kT}$); and (3) repeat the procedure until the desired number of samples is reached.
-
-\subsection{Algorithm}
-As mentioned above, the whole simulation run consists of MD and MC subsimulations of mechanical movement of the particles and ion exchange. The algorithm follows:
-\begin{enumerate}
-\item Initiate the systems to simulate: the gel of volume $\Vgel$ and the external solution of volume $\Vout$;
-\item Equilibrate the system, interspersing the MD and MC stages;
-\item Run the MD subsimulation and collect the observables: pressure in both volumes, $P_\mathrm{gel}$, $P_\mathrm{out}$, and distances between the nodes of the gel network.
-The latter is needed to estimate the autocorrelation of the MD simulation;
-\item Run the MC procedure, simulating ion exchange, and collect the number of ions in both boxes, 
-$\Ncl\gel$ and $\Ncl\out$; 
-\item Repeat the MD and MC subsimulations until the desired length of sample arrays is reached.
-\end{enumerate}
+To sample mechanical properties of the gel and reservoir, we use Molecular Dynamics (MD) simulation, whereas to sample the ion distribution between the gel and a reservoir, we use Monte Carlo (MC) simulation.
+The details of this hybrid MCMD computational technique can be found in our previous studies of polyelectrolytes in open systems \cite{Rud2020, Rud2022, Landsgesel2020a} and in Section~\ref{sec: MM}.
 
@@
 Then, as soon as $\Vbox$ is defined, we compress the gel in the \emph{closed system} with varying values of $\Vgel<\Vbox$ and $\Vout= \Vbox - \Vgel$.
-
-\section{Results and Discussion}
 
@@
 \end{table}
-
 Thus, the recovery ratio $R_w = \Delta v^p / (\Delta v^p + \Delta v^b) \simeq $ 0.53 and the theoretical minimum specific energy of the desalination process with corresponding $\cs^f$, $\cs^p,$ and $\cs^b$ is $W^{id} =$ 38.2~J/L (\refeq{eq:SEC}).
@@
 }
+\section{Materials and Methods\label{sec: MM}}
+
+\subsection{Molecular Dynamics}
+
+We model the gel as a network of 16 linear polymer chains, each consisting of 30~monomer units.
+These polymer chains are connected to a diamond-like network by eight~crosslinking units.
+This means there are $\Ngel=16\cdot30 + 8=488$ gel monomers in the simulation box (see \reffig{fig:diamond}).
+The network is put in a simulated cubic box with volume $\Vgel$ with periodic boundary conditions, which virtually emulates an infinite polymer~network.
+\begin{figure}[H]
+
+\includegraphics[width=0.7\textwidth]{{figures/simgibbs}.pdf}
+\caption{
+Diamond-like network in the simulation box. 
+Red and blue particles are the ions $\na$ and $\cl$. \label{fig:diamond}}
+\end{figure}
+Each monomer unit of the network carries a negative elementary electric charge.
+Except for the gel monomers, the monovalent co- and counter-ions, $\cl$ and $\na$, are present in the simulation box.
+The total electric charge of all the particles in the box is zero; therefore the number of $\na$ ions exceeds the number of $\cl$ ions by $\Ngel$.
+
+Each pair of particles interact via the truncated Lennard--Jones interaction potential, which imposes strong repulsion between all particles at short distances:
+\begin{equation}
+    \begin{split}\label{eq:LJ}
+        V_\mathrm{LJ}(r) =
+        \begin{cases}
+            4 \varepsilon \left( \left(\cfrac{\sigma}{r}\right)^{12}
+            - \left(\cfrac{\sigma}{r}\right)^6\right)
+            & \mathrm{if~} r < r_\mathrm{cut}\\
+            0
+            & \mathrm{elsewhere}
+        \end{cases},
+    \end{split}
+\end{equation}
+where 
+$r$ is the interparticle distance, 
+$\sigma = 0.35~\mathrm{nm}$ is a chosen characteristic size of the particles, 
+$\varepsilon = \kT$ is the depth of the potential, and 
+$r_\mathrm{cut}$ is the cut-off distance beyond which the potential is set zero.
+
+The bonds connecting the gel to a network are modeled using finite extension nonlinear elastic potential (FENE)
+\begin{equation}\label{eq:fene}
+V_\mathrm{FENE}(r) = -\frac{1}{2} K \Delta r_\mathrm{max}^2\ln \left[ 1 - \left(\frac{r-r_0}{\Delta r_\mathrm{max}} \right)^2 \right ],
+\end{equation}
+where
+$r$ is the distance between the bonded segments,
+$K$ is the magnitude of their interaction,
+$\Delta r_{\mathrm{max}}$ is the maximal stretching length of the bond, and
+$r_0$ is the equilibrium bond length.
+For our simulations, we chose $K = 10 \kT/\sigma^{2}$, $\Delta r_{\mathrm{max}} = 2 \sigma$, and $r_0 = 1.0\sigma$~\cite{Jin2007}.
+
+All the charged particles interact via Coulomb electrostatic potential:
+\begin{equation}
+    V_{\mathrm{EL}}=\lb\kT \cfrac{q_{1}q_{2}}{r},
+\end{equation}
+where $\lb$ is Bjerrum length---$\lb = 2\sigma = 0.7~\mathrm{nm}$, which corresponds to the  Bjerrum length in water at temperature $T=300~\mathrm{K}$---and $\kB$ is the Botlzman constant.
+In that sense, the solvent (water) is accounted for in the model implicitly via setting up dielectric permittivity $\epsilon=80$.
+
+We used the Langevin thermostat, \ie two additional terms for force in the equation of motion were added
+\begin{equation}
+\mathbf{f}_i =  -\gamma \mathbf{v}_i(t)+\sqrt{2\gamma \kT }\boldsymbol{\eta}_i(t),
+\end{equation}
+where the first term corresponds to constant friction, with $\gamma$ being a friction coefficient,
+ and the second term corresponds to random thermal force, with $\boldsymbol{\eta}_i$ being a normally distributed random vector; $\mathbf{v}_i$ is the velocity of the $i$-th particle (for details see \cite{Grest1986}).
+
+\subsection{Monte Carlo Sampling in an Open System}
+The Monte Carlo scheme for sampling the exchange of ions in an \emph{open system} is based on the formula for free energy of grand canonical ensemble $\Omega$
+\begin{equation}
+    \Omega_{\mathrm{open}}=E-TS+\sum_i\mu_i N_i\label{eq:Omega-GC}
+\end{equation}
+where $E$ is internal energy, $T$ is temperature, $S$ is entropy, $N_i$ is the number of ions of type $i\in\{\na,\ \cl\}$, and $\mu_i$ is the corresponding chemical potential.
+
+%Our model system represents a finite volume $V$ which exchanges particles with the bath of infinite volume.
+%The infinity of the volume means, that the particle exchange between the system and the bath does not influence on the chemical potentials in the bath.
+%Such ensemble is called grand canonical ensemble; the free energy in this ensemble, the Landau potential, is
+The entropy $S$ is given by the Boltzmann formula~\cite{Nagle2004}
+\begin{equation}
+    S=\kB\sum_i\ln\frac{\Vgel^{N_i}}{N_i!}\label{eq:entropy}
+\end{equation}
+%\todo{for partiles without interactions}
+which accounts for two contributions:
+\begin{enumerate}
+    \item The combinatorial entropy $S_{c}=-\kB\sum_i\ln N_i!$, which reflects the freedom of choice among the particles;
+    \item The mixing entropy $S_{m}=\kB \sum_i N_i\ln \Vgel$, which reflects the freedom to place the chosen particle randomly within the simulation box. 
+\end{enumerate}
+
+$\Vgel$ is the unitless volume, \ie the volume measured in units of $\sigma^3$. 
+Thus, the change of free energy associated with an exchange of ion pairs is
+\begin{equation}
+\Delta\Omega_\mathrm{open}=\kT\ln\prod_i\left(\Vgel^{\xi}\frac{N_i!}{\left(N_i+\xi\right)!}\right)+\xi\sum_i\mu_i+\Delta E
+\label{eq: DeltaG GC}
+\end{equation}
+where $\xi$ is an algebraic number of inserted (or removed) ion pairs; in general, $\xi$ can be any number, but when $\xi = \pm 1$, which corresponds to addition or removal of only one ion pair,  \refeq{eq: DeltaG GC} gets simplified
+\begin{equation}
+    \Delta\Omega_\mathrm{open}=\kT\ln \Vgel^{2\xi} \prod_i \left(N_i+\theta(\xi)\right)^{-\xi}+\xi\sum_i\mu_i+\Delta E
+\label{eq: DeltaG GC_simpl}
+\end{equation}
+where $\theta$ is the Heaviside function; $\theta(\xi) = 1$ if $\xi=+1$; $\theta(\xi) = 0$ if $\xi=-1$.
+
+The procedure for Monte Carlo sampling is as follows: \cite{Frenlkel2002_book}
+\begin{enumerate}
+	\item Propose the new configuration of the system by insertion (or deletion) of an ion pair, $\xi=\pm1$;
+	\item Accept the new configuration if
+	\begin{equation}
+        \mathcal{R}^{\xi}<e^{\Delta\Omega_\mathrm{open}/\kT}=\Vgel^{2\xi} \prod_i \left(N_i+\theta(\xi)\right)^{-\xi}e^{\left(\Delta E+\xi\mu\right)/\kT}\label{eq: GC acceptance}
+	\end{equation}
+	where $\mathcal{R}$ is a uniformly distributed random number in the range between $0$ and $1$;
+	\item Then, collect the number of ions, $\Nna$ and $\Ncl$, to the samples array.
+\end{enumerate}
+
+\subsection{Monte Carlo Sampling in Closed System}
+
+In the \emph{closed system}, the gel exchanges particles with the explicit finite reservoir box. 
+The total number of ion species in both boxes is fixed, whereas the density of ions in the external reservoir is defined by thermodynamic equilibrium between the two subvolumes (see \reffig{fig:open and closed}b.
+Monte Carlo sampling of the distribution of ions between the subvolumes is performed in a way similar to that described in \cite{Panagiotopoulos1988b, Erdos2020}.
+
+The free energy of the Gibbs ensemble is a sum of the gel's free energy and that of the external volume.
+\begin{equation}
+    \Omega_{\mathrm{closed}}=\Egel-T\Sgel + \Eout-T\Sout \label{eq:Omega-GC}
+\end{equation}
+Using reasoning similar to that of the \emph{open system}, one can derive the change of free energy associated with ion-pair exchange 
+\begin{equation}
+\Delta \Omega_{\mathrm{closed}} =2 k_B T \ln \left(\frac{\Vgel}{\Vout} \right) ^ {\xi}\prod_i \left(\frac{N_{i}\gel+\theta(\xi)}{N_{i}\out+\theta(-\xi)}\right)^{-\xi} + \Delta \Egel + \Delta \Eout
+\end{equation}
+where $\xi$ defines the direction of the trial move, so that $\xi = -1$ when an ion pair moves from the gel to the outside volume, and  $\xi = +1$ otherwise; $\Delta \Egel$ and $\Delta \Eout$ are corresponding changes of the potential energy of the gel and the outside volumes, respectively.
+
+Then, the procedure for sampling is the same as that of the \emph{open system}: (1) propose the move of an ion pair; (2) accept a new state if $\mathcal{R}^{\xi}<\exp({\Delta\Omega_\mathrm{closed}/\kT}$); and (3) repeat the procedure until the desired number of samples is reached.
+
+\subsection{Algorithm}
+As mentioned above, the whole simulation run consists of MD and MC sub-simulations of the mechanical movement of the particles and ion exchange. The algorithm is the following:
+\begin{enumerate}
+\item Initiate the systems to simulate: the gel of volume $\Vgel$ and the external solution of volume $\Vout$;
+\item Equilibrate the system, interspersing the MD and MC stages;
+\item Run the MD subsimulation and collect the observables: pressure in both volumes, $P_\mathrm{gel}$, $P_\mathrm{out}$, and distances between the nodes of the gel network.
+The latter is needed to estimate the autocorrelation of the MD simulation;
+\item Run the MC procedure, simulating ion exchange, and collect the number of ions in both boxes, 
+$\Ncl\gel$ and $\Ncl\out$; 
+\item Repeat the MD and MC subsimulations until the desired length of sample arrays is reached.
+\end{enumerate}
 

### 2024-07-15 MDPI/proof/manuscript.v5/orig.tex
Cleaned up files. Article moved to MDPI directory

@@
 
+\begin{table}[H]
+\caption{Estimates of  %MDPI: Please confirm if the format of the table should be retained, e.g., the color of the font, the text direction, vertical line
+% Oleg Rud: Confirm the colors and the directions of the table must retain
+desalination efficiency.
+All units are calculated per one mol of gel segments.
+Values in brackets correspond to crossection of `red' and `orange' lines on the plots in Figures \ref{fig: PV and CV} and \ref{fig: NV and CN}.
+\label{tab: table}}
+
+\begin{adjustwidth}{-\extralength}{0cm}
+
+		\newcolumntype{C}{>{\centering\arraybackslash}X}
+\begin{tabularx}{1\fulllength}{@{\extracolsep{\fill}}ll|lc|c|l|ll}
+\noalign{\hrule height 1pt}
+\multicolumn{1}{l|}{\textbf{\boldmath{$c_{s}^{0}$}, mM}} & \textbf{\boldmath{$c_{s}^{5}$}, mM} & \multicolumn{1}{l|}{\textbf{\boldmath{$n_{\cl}^{0}$}, mM}} & \textbf{\boldmath{$n_{\cl}^{5}$}, mM} & \textbf{\boldmath{$\Delta \Vgel$}, L} & \textbf{\boldmath{$|W$}\textbar , J/L} & \multicolumn{2}{c}{\textbf{\boldmath{$W^{id}$}, J/L}}\tabularnewline
+
+\noalign{\hrule height 0.5pt} 
+\multirow{2}{*}{{\small{}$91.47$}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{{\small{}$57.08\pm0.122\enskip\longrightarrow$}} & \multirow{2}{*}{{\small{}2.74}} & \multirow{2}{*}{{\small{}$95.4\pm1.9$}} &  & \multirow{2}{*}{}\tabularnewline
+ &  & \multicolumn{2}{r|}{{\small{}$71.75\pm0.024$}} &  &  & \multirow{8}{*}{{\small{}\hspace{-1em}}\textcolor{teal}{\small{}$\left.\begin{array}{l}
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\end{array}\right\rbrace $$\rotatebox{90}{\hspace{-5em}{\color{teal}\ensuremath{\begin{array}{cc}
+W^{id}= & 52.9\\
+W^{\mathrm{sim}}= & 202.8\pm3.2\\
+R_{w}= & 0.54
+\end{array}}}}$}} & \tabularnewline
+\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
+\multicolumn{2}{l|}{{\small{}$89.41\pm0.23\enskip\longrightarrow$}} & \multirow{2}{*}{{\small{}56.90}} & \multirow{2}{*}{} & \multirow{2}{*}{{\small{}2.72}} & \multirow{2}{*}{{\small{}$109.1\pm1.7$}} &  & \multirow{2}{*}{}\tabularnewline
+\multicolumn{2}{r|}{{\small{}$73.63\pm0.03$}} &  &  &  &  &  & \tabularnewline
+\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
+\multirow{2}{*}{\textcolor{teal}{\small{}63.93}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{teal}{\small{}$37.28\pm0.08\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{teal}{\small{}3.26}} & \multirow{2}{*}{\textcolor{teal}{\small{}$100.9\pm1.7$}} &  & \tabularnewline
+ &  & \multicolumn{2}{r|}{\textcolor{teal}{\small{}$50.579\pm0.013$}} &  &  &  & \multirow{8}{*}{{\small{}\hspace{-1em}}\textcolor{olive}{\small{}$\left.\begin{array}{l}
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\end{array}\right\rbrace $$\rotatebox{90}{\hspace{-5em}\ensuremath{\begin{array}{cc}
+W^{id}= & 38.2\\
+W^{\mathrm{sim}}= & 207.3\pm2.2\\
+R_{w}= & 0.53
+\end{array}}}$}}\tabularnewline
+\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
+\multicolumn{2}{l|}{\textcolor{teal}{\small{}$62.05\pm0.15\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{teal}{\small{}37.17}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{teal}{\small{}3.18}} & \multirow{2}{*}{\textcolor{teal}{\small{}$107.4\pm1.4$}} &  & \tabularnewline
+\multicolumn{2}{r|}{\textcolor{teal}{\small{}$48.21\pm0.02$}} &  &  &  &  &  & \tabularnewline
+\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
+\multirow{2}{*}{\textcolor{olive}{\small{}44.91}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{olive}{\small{}$23.75\pm0.06\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{olive}{\small{}3.82}} & \multirow{2}{*}{\textcolor{olive}{\small{}$106.7\pm1.5$}} &  & \tabularnewline
+ &  & \multicolumn{2}{r|}{\textcolor{olive}{\small{}$35.911\pm0.010$}} &  &  & \multirow{8}{*}{{\small{}\hspace{-1em}}\textcolor{red}{\small{}$\left.\begin{array}{l}
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\end{array}\right\rbrace \rotatebox{90}{\hspace{-5em}\ensuremath{\begin{array}{cc}
+W^{\mathrm{id}}= & 43.8\ {\color{red}{\scriptstyle (41.0)}}\\
+W^{\mathrm{sim}}= & 222.3\pm2.5\\
+R_{w}= & 0.52\ {\scriptstyle (0.46)}
+\end{array}}}$}} & \tabularnewline
+\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
+\multicolumn{2}{l|}{\textcolor{olive}{\small{}$43.46\pm0.12\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{olive}{\small{}24.27}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{olive}{\small{}3.91}} & \multirow{2}{*}{\textcolor{olive}{\small{}$106.4\pm1.1$}} &  & \tabularnewline
+\multicolumn{2}{r|}{\textcolor{olive}{\small{}$30.795\pm0.008$}} &  &  &  &  &  & \tabularnewline
+\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
+\multirow{2}{*}{\textcolor{red}{\small{}31.93}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{red}{\small{}$14.66\pm0.04\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{red}{\small{}4.20}} & \multirow{2}{*}{\textcolor{red}{\small{}$107.9\pm1.4$}} &  & \tabularnewline
+ &  & \multicolumn{2}{r|}{\textcolor{red}{\small{}$25.297\pm0.006$}} &  &  &  & \multirow{8}{*}{{\small{}\hspace{-1em}}\textcolor{orange}{\small{}$\left.\begin{array}{l}
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\end{array}\right\rbrace \rotatebox{90}{\hspace{-5em}\ensuremath{\begin{array}{cc}
+W^{id}= & 66.6\ {\scriptstyle (22.0)}\\
+W^{\mathrm{sim}}= & 218.7\pm2.2\\
+R_{w}= & 0.53\ {\scriptstyle (0.49)}
+\end{array}}}$}}\tabularnewline
+\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
+\multicolumn{2}{l|}{\textcolor{red}{\small{}$30.03\pm0.08\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{red}{\small{}14.55}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{red}{\small{}$\begin{array}{c}
+4.17\\
+{\scriptstyle (3.22)}
+\end{array}$}} & \multirow{2}{*}{\textcolor{red}{\small{}$\begin{array}{c}
+115.6\pm0.9\\
+{\scriptstyle (57.3)}
+\end{array}$}} &  & \tabularnewline
+\multicolumn{2}{r|}{\textcolor{red}{\small{}$\begin{array}{c}
+18.585\pm0.004\,\\
+{\scriptstyle (22.32)}
+\end{array}$}} &  &  &  &  &  & \tabularnewline
+\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
+\multirow{2}{*}{\textcolor{orange}{\small{}22.30}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{orange}{\small{}$8.84\pm0.03\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{orange}{\small{}$\begin{array}{c}
+4.75\\
+{\scriptstyle (3.76)}
+\end{array}$}} & \multirow{2}{*}{\textcolor{orange}{\small{}$\begin{array}{c}
+108.1\pm1.3\\
+{\scriptstyle (68.3)}
+\end{array}$}} &  & \tabularnewline
+ &  & \multicolumn{2}{r|}{\textcolor{orange}{\small{}$\begin{array}{c}
+\text{17.945}\pm\text{0.004}\\
+{\scriptstyle (14.56)}
+\end{array}$}} &  &  & \multirow{7}{*}{{\small{}\hspace{-1em}}\textcolor{magenta}{\small{}$\left.\begin{array}{l}
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\end{array}\right\rbrace \rotatebox{90}{\hspace{-5em}\ensuremath{\begin{array}{cc}
+W^{id}= & 69.7\\
+W^{\mathrm{sim}}= & 227.5\pm2.3\\
+R_{w}= & 0.55
+\end{array}}}$}} & \\[1ex]
+\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
+\multicolumn{2}{l|}{\textcolor{orange}{\small{}$20.74\pm0.06\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{orange}{\small{}8.83}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{orange}{\small{}$4.71$}} & \multirow{2}{*}{\textcolor{orange}{\small{}$110.8\pm0.8$}} &  & \tabularnewline
+\multicolumn{2}{r|}{\textcolor{orange}{\small{}$11.082\pm0.002$}} &  &  &  &  &  & \tabularnewline
+\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
+\multirow{2}{*}{\textcolor{magenta}{\small{}10.90}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{magenta}{\small{}$3.00\pm0.01\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{magenta}{\small{}6.08}} & \multirow{2}{*}{\textcolor{magenta}{\small{}$106.9\pm1.1$}} &  & \tabularnewline
+ &  & \multicolumn{2}{r|}{\textcolor{magenta}{\small{}9.011$\pm$0.002}} &  &  &  & \tabularnewline
+\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
+\multicolumn{2}{l|}{\textcolor{magenta}{\small{}$9.83\pm0.05\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{magenta}{\small{}3.12}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{magenta}{\small{}5.78}} & \multirow{2}{*}{\textcolor{magenta}{\small{}$119.4\pm1.0$}} &  & \tabularnewline
+\multicolumn{2}{r|}{\textcolor{magenta}{\small{}$3.862\pm0.001$}} &  &  &  &  &  & \\[2ex]
+\noalign{\hrule height 1pt}
+\end{tabularx}
+\end{adjustwidth}
+\end{table}
+
 Thus, the recovery ratio $R_w = \Delta v^p / (\Delta v^p + \Delta v^b) \simeq $ 0.53 and the theoretical minimum specific energy of the desalination process with corresponding $\cs^f$, $\cs^p,$ and $\cs^b$ is $W^{id} =$ 38.2~J/L (\refeq{eq:SEC}).

### 2024-07-15 MDPI/proof/manuscript.v6/Definitions/journalnames.tex
Cleaned up files. Article moved to MDPI directory

%%Updated on 28 December 2021
%,% Website Name,%,%,% Website Name,%%,% Full Name,%%,% Short Name,%%,% DOI abbr,%%,% ISSN,% \continuouspages
%\DeclareOption{}{\gdef\@journal{}\gdef\@journalfull{}\gdef\@journalshort{}\gdef\@doiabbr{}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{acoustics}{\gdef\@journal{acoustics}\gdef\@journalfull{Acoustics}\gdef\@journalshort{Acoustics}\gdef\@doiabbr{acoustics}\gdef\@ISSN{2624-599X}\gdef\@continuouspages{yes}}
\DeclareOption{actuators}{\gdef\@journal{actuators}\gdef\@journalfull{Actuators}\gdef\@journalshort{Actuators}\gdef\@doiabbr{act}\gdef\@ISSN{2076-0825}}
\DeclareOption{addictions}{\gdef\@journal{addictions}\gdef\@journalfull{Addictions}\gdef\@journalshort{Addictions}\gdef\@doiabbr{}\gdef\@ISSN{0006-0006}}
\DeclareOption{admsci}{\gdef\@journal{admsci}\gdef\@journalfull{Administrative Sciences}\gdef\@journalshort{Adm. Sci.}\gdef\@doiabbr{admsci}\gdef\@ISSN{2076-3387}}
\DeclareOption{adolescents}{\gdef\@journal{adolescents}\gdef\@journalfull{Adolescents}\gdef\@journalshort{Adolescents}\gdef\@doiabbr{adolescents}\gdef\@ISSN{2673-7051}\gdef\@continuouspages{yes}}
\DeclareOption{aerospace}{\gdef\@journal{aerospace}\gdef\@journalfull{Aerospace}\gdef\@journalshort{Aerospace}\gdef\@doiabbr{aerospace}\gdef\@ISSN{2226-4310}}
\DeclareOption{agriculture}{\gdef\@journal{agriculture}\gdef\@journalfull{Agriculture}\gdef\@journalshort{Agriculture}\gdef\@doiabbr{agriculture}\gdef\@ISSN{2077-0472}}
\DeclareOption{agriengineering}{\gdef\@journal{agriengineering}\gdef\@journalfull{AgriEngineering}\gdef\@journalshort{AgriEngineering}\gdef\@doiabbr{agriengineering}\gdef\@ISSN{2624-7402}\gdef\@continuouspages{yes}}
\DeclareOption{agronomy}{\gdef\@journal{agronomy}\gdef\@journalfull{Agronomy}\gdef\@journalshort{Agronomy}\gdef\@doiabbr{agronomy}\gdef\@ISSN{2073-4395}}
\DeclareOption{ai}{\gdef\@journal{ai}\gdef\@journalfull{AI}\gdef\@journalshort{AI}\gdef\@doiabbr{ai}\gdef\@ISSN{2673-2688}\gdef\@continuouspages{yes}}
\DeclareOption{algorithms}{\gdef\@journal{algorithms}\gdef\@journalfull{Algorithms}\gdef\@journalshort{Algorithms}\gdef\@doiabbr{a}\gdef\@ISSN{1999-4893}}
\DeclareOption{allergies}{\gdef\@journal{allergies}\gdef\@journalfull{Allergies}\gdef\@journalshort{Allergies}\gdef\@doiabbr{allergies}\gdef\@ISSN{2313-5786}}
\DeclareOption{alloys}{\gdef\@journal{alloys}\gdef\@journalfull{Alloys}\gdef\@journalshort{Alloys}\gdef\@doiabbr{alloys}\gdef\@ISSN{2674-063X}\gdef\@continuouspages{yes}}
\DeclareOption{analytica}{\gdef\@journal{analytica}\gdef\@journalfull{Analytica}\gdef\@journalshort{Analytica}\gdef\@doiabbr{analytica}\gdef\@ISSN{2673-4532}\gdef\@continuouspages{yes}}
\DeclareOption{anatomia}{\gdef\@journal{anatomia}\gdef\@journalfull{Anatomia}\gdef\@journalshort{Anatomia}\gdef\@doiabbr{anatomia}\gdef\@ISSN{2813-0545}\gdef\@continuouspages{yes}}
\DeclareOption{animals}{\gdef\@journal{animals}\gdef\@journalfull{Animals}\gdef\@journalshort{Animals}\gdef\@doiabbr{ani}\gdef\@ISSN{2076-2615}}
\DeclareOption{antibiotics}{\gdef\@journal{antibiotics}\gdef\@journalfull{Antibiotics}\gdef\@journalshort{Antibiotics}\gdef\@doiabbr{antibiotics}\gdef\@ISSN{2079-6382}}
\DeclareOption{antibodies}{\gdef\@journal{antibodies}\gdef\@journalfull{Antibodies}\gdef\@journalshort{Antibodies}\gdef\@doiabbr{antib}\gdef\@ISSN{2073-4468}}
\DeclareOption{antioxidants}{\gdef\@journal{antioxidants}\gdef\@journalfull{Antioxidants}\gdef\@journalshort{Antioxidants}\gdef\@doiabbr{antiox}\gdef\@ISSN{2076-3921}}
\DeclareOption{applbiosci}{\gdef\@journal{applbiosci}\gdef\@journalfull{Applied Biosciences}\gdef\@journalshort{Appl. Biosci.}\gdef\@doiabbr{applbiosci}\gdef\@ISSN{2813-0464}\gdef\@continuouspages{yes}}
\DeclareOption{appliedchem}{\gdef\@journal{appliedchem}\gdef\@journalfull{AppliedChem}\gdef\@journalshort{AppliedChem}\gdef\@doiabbr{appliedchem}\gdef\@ISSN{2673-9623}\gdef\@continuouspages{yes}}
\DeclareOption{appliedmath}{\gdef\@journal{appliedmath}\gdef\@journalfull{AppliedMath}\gdef\@journalshort{AppliedMath}\gdef\@doiabbr{appliedmath}\gdef\@ISSN{2673-9909}\gdef\@continuouspages{yes}}
\DeclareOption{applmech}{\gdef\@journal{applmech}\gdef\@journalfull{Applied Mechanics}\gdef\@journalshort{Appl. Mech.}\gdef\@doiabbr{applmech}\gdef\@ISSN{2673-3161}\gdef\@continuouspages{yes}}
\DeclareOption{applmicrobiol}{\gdef\@journal{applmicrobiol}\gdef\@journalfull{Applied Microbiology}\gdef\@journalshort{Appl. Microbiol.}\gdef\@doiabbr{applmicrobiol}\gdef\@ISSN{2673-8007}\gdef\@continuouspages{yes}}
\DeclareOption{applnano}{\gdef\@journal{applnano}\gdef\@journalfull{Applied Nano}\gdef\@journalshort{Appl. Nano}\gdef\@doiabbr{applnano}\gdef\@ISSN{2673-3501}\gdef\@continuouspages{yes}}
\DeclareOption{applsci}{\gdef\@journal{applsci}\gdef\@journalfull{Applied Sciences}\gdef\@journalshort{Appl. Sci.}\gdef\@doiabbr{app}\gdef\@ISSN{2076-3417}}
\DeclareOption{aquacj}{\gdef\@journal{aquacj}\gdef\@journalfull{Aquaculture Journal}\gdef\@journalshort{Aquac. J.}\gdef\@doiabbr{aj}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{architecture}{\gdef\@journal{architecture}\gdef\@journalfull{Architecture}\gdef\@journalshort{Architecture}\gdef\@doiabbr{architecture}\gdef\@ISSN{2673-8945}\gdef\@continuouspages{yes}}
\DeclareOption{arts}{\gdef\@journal{arts}\gdef\@journalfull{Arts}\gdef\@journalshort{Arts}\gdef\@doiabbr{arts}\gdef\@ISSN{2076-0752}}
\DeclareOption{asc}{\gdef\@journal{asc}\gdef\@journalfull{Automatic Systems and Control}\gdef\@journalshort{Autom. Syst. Control}\gdef\@doiabbr{}\gdef\@ISSN{}}
\DeclareOption{asi}{\gdef\@journal{asi}\gdef\@journalfull{Applied System Innovation}\gdef\@journalshort{Appl. Syst. Innov.}\gdef\@doiabbr{asi}\gdef\@ISSN{2571-5577}}
\DeclareOption{astronomy}{\gdef\@journal{astronomy}\gdef\@journalfull{Astronomy}\gdef\@journalshort{Astronomy}\gdef\@doiabbr{astronomy}\gdef\@ISSN{2674-0346}\gdef\@continuouspages{yes}}
\DeclareOption{atmosphere}{\gdef\@journal{atmosphere}\gdef\@journalfull{Atmosphere}\gdef\@journalshort{Atmosphere}\gdef\@doiabbr{atmos}\gdef\@ISSN{2073-4433}}
\DeclareOption{atoms}{\gdef\@journal{atoms}\gdef\@journalfull{Atoms}\gdef\@journalshort{Atoms}\gdef\@doiabbr{atoms}\gdef\@ISSN{2218-2004}}
\DeclareOption{audiolres}{\gdef\@journal{audiolres}\gdef\@journalfull{Audiology Research}\gdef\@journalshort{Audiol. Res.}\gdef\@doiabbr{audiolres}\gdef\@ISSN{2039-4349}\gdef\@continuouspages{yes}}
\DeclareOption{automation}{\gdef\@journal{automation}\gdef\@journalfull{Automation}\gdef\@journalshort{Automation}\gdef\@doiabbr{automation}\gdef\@ISSN{2673-4052}\gdef\@continuouspages{yes}}
\DeclareOption{axioms}{\gdef\@journal{axioms}\gdef\@journalfull{Axioms}\gdef\@journalshort{Axioms}\gdef\@doiabbr{axioms}\gdef\@ISSN{2075-1680}}
\DeclareOption{bacteria}{\gdef\@journal{bacteria}\gdef\@journalfull{Bacteria}\gdef\@journalshort{Bacteria}\gdef\@doiabbr{bacteria}\gdef\@ISSN{2674-1334}\gdef\@continuouspages{yes}}
\DeclareOption{batteries}{\gdef\@journal{batteries}\gdef\@journalfull{Batteries}\gdef\@journalshort{Batteries}\gdef\@doiabbr{batteries}\gdef\@ISSN{2313-0105}}
\DeclareOption{bdcc}{\gdef\@journal{bdcc}\gdef\@journalfull{Big Data and Cognitive Computing}\gdef\@journalshort{Big Data Cogn. Comput.}\gdef\@doiabbr{bdcc}\gdef\@ISSN{2504-2289}}
\DeclareOption{behavsci}{\gdef\@journal{behavsci}\gdef\@journalfull{Behavioral Sciences}\gdef\@journalshort{Behav. Sci.}\gdef\@doiabbr{bs}\gdef\@ISSN{2076-328X}}
\DeclareOption{beverages}{\gdef\@journal{beverages}\gdef\@journalfull{Beverages}\gdef\@journalshort{Beverages}\gdef\@doiabbr{beverages}\gdef\@ISSN{2306-5710}}
\DeclareOption{biochem}{\gdef\@journal{biochem}\gdef\@journalfull{BioChem}\gdef\@journalshort{BioChem}\gdef\@doiabbr{biochem}\gdef\@ISSN{2673-6411}\gdef\@continuouspages{yes}}
\DeclareOption{bioengineering}{\gdef\@journal{bioengineering}\gdef\@journalfull{Bioengineering}\gdef\@journalshort{Bioengineering}\gdef\@doiabbr{bioengineering}\gdef\@ISSN{2306-5354}}
\DeclareOption{biologics}{\gdef\@journal{biologics}\gdef\@journalfull{Biologics}\gdef\@journalshort{Biologics}\gdef\@doiabbr{biologics}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{biology}{\gdef\@journal{biology}\gdef\@journalfull{Biology}\gdef\@journalshort{Biology}\gdef\@doiabbr{biology}\gdef\@ISSN{2079-7737}}
\DeclareOption{biomass}{\gdef\@journal{biomass}\gdef\@journalfull{Biomass}\gdef\@journalshort{Biomass}\gdef\@doiabbr{biomass}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{biomechanics}{\gdef\@journal{biomechanics}\gdef\@journalfull{Biomechanics}\gdef\@journalshort{Biomechanics}\gdef\@doiabbr{biomechanics}\gdef\@ISSN{2673-7078}\gdef\@continuouspages{yes}}
\DeclareOption{biomed}{\gdef\@journal{biomed}\gdef\@journalfull{BioMed}\gdef\@journalshort{BioMed}\gdef\@doiabbr{biomed}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{biomedicines}{\gdef\@journal{biomedicines}\gdef\@journalfull{Biomedicines}\gdef\@journalshort{Biomedicines}\gdef\@doiabbr{biomedicines}\gdef\@ISSN{2227-9059}}
\DeclareOption{biomedinformatics}{\gdef\@journal{biomedinformatics}\gdef\@journalfull{Biomedinformatics}\gdef\@journalshort{Biomedinformatics}\gdef\@doiabbr{biomedinformatics}\gdef\@ISSN{2673-7426}\gdef\@continuouspages{yes}}
\DeclareOption{biomimetics}{\gdef\@journal{biomimetics}\gdef\@journalfull{Biomimetics}\gdef\@journalshort{Biomimetics}\gdef\@doiabbr{biomimetics}\gdef\@ISSN{2313-7673}}
\DeclareOption{biomolecules}{\gdef\@journal{biomolecules}\gdef\@journalfull{Biomolecules}\gdef\@journalshort{Biomolecules}\gdef\@doiabbr{biom}\gdef\@ISSN{2218-273X}}
\DeclareOption{biophysica}{\gdef\@journal{biophysica}\gdef\@journalfull{Biophysica}\gdef\@journalshort{Biophysica}\gdef\@doiabbr{biophysica}\gdef\@ISSN{2673-4125}\gdef\@continuouspages{yes}}
\DeclareOption{biosensors}{\gdef\@journal{biosensors}\gdef\@journalfull{Biosensors}\gdef\@journalshort{Biosensors}\gdef\@doiabbr{bios}\gdef\@ISSN{2079-6374}}
\DeclareOption{biotech}{\gdef\@journal{biotech}\gdef\@journalfull{BioTech}\gdef\@journalshort{BioTech}\gdef\@doiabbr{biotech}\gdef\@ISSN{2673-6284}}
\DeclareOption{birds}{\gdef\@journal{birds}\gdef\@journalfull{Birds}\gdef\@journalshort{Birds}\gdef\@doiabbr{birds}\gdef\@ISSN{2673-6004}\gdef\@continuouspages{yes}}
\DeclareOption{bloods}{\gdef\@journal{bloods}\gdef\@journalfull{Bloods}\gdef\@journalshort{Bloods}\gdef\@doiabbr{bloods}\gdef\@ISSN{2673-415X}}
\DeclareOption{blsf}{\gdef\@journal{blsf}\gdef\@journalfull{Biology and Life Sciences Forum}\gdef\@journalshort{Biol. Life Sci. Forum}\gdef\@doiabbr{blsf	}\gdef\@ISSN{2673-9976}}
\DeclareOption{brainsci}{\gdef\@journal{brainsci}\gdef\@journalfull{Brain Sciences}\gdef\@journalshort{Brain Sci.}\gdef\@doiabbr{brainsci}\gdef\@ISSN{2076-3425}}
\DeclareOption{breath}{\gdef\@journal{breath}\gdef\@journalfull{Breath}\gdef\@journalshort{Breath}\gdef\@doiabbr{breath}\gdef\@ISSN{}}
\DeclareOption{buildings}{\gdef\@journal{buildings}\gdef\@journalfull{Buildings}\gdef\@journalshort{Buildings}\gdef\@doiabbr{buildings}\gdef\@ISSN{2075-5309}}
\DeclareOption{businesses}{\gdef\@journal{businesses}\gdef\@journalfull{Businesses}\gdef\@journalshort{Businesses}\gdef\@doiabbr{businesses}\gdef\@ISSN{2673-7116}\gdef\@continuouspages{yes}}
\DeclareOption{cancers}{\gdef\@journal{cancers}\gdef\@journalfull{Cancers}\gdef\@journalshort{Cancers}\gdef\@doiabbr{cancers}\gdef\@ISSN{2072-6694}}
\DeclareOption{carbon}{\gdef\@journal{carbon}\gdef\@journalfull{C}\gdef\@journalshort{C}\gdef\@doiabbr{c}\gdef\@ISSN{2311-5629}}
\DeclareOption{cardiogenetics}{\gdef\@journal{cardiogenetics}\gdef\@journalfull{Cardiogenetics}\gdef\@journalshort{Cardiogenetics}\gdef\@doiabbr{cardiogenetics}\gdef\@ISSN{2035-8148}\gdef\@continuouspages{yes}}
\DeclareOption{catalysts}{\gdef\@journal{catalysts}\gdef\@journalfull{Catalysts}\gdef\@journalshort{Catalysts}\gdef\@doiabbr{catal}\gdef\@ISSN{2073-4344}}
\DeclareOption{cells}{\gdef\@journal{cells}\gdef\@journalfull{Cells}\gdef\@journalshort{Cells}\gdef\@doiabbr{cells}\gdef\@ISSN{2073-4409}}
\DeclareOption{ceramics}{\gdef\@journal{ceramics}\gdef\@journalfull{Ceramics}\gdef\@journalshort{Ceramics}\gdef\@doiabbr{ceramics}\gdef\@ISSN{2571-6131}\gdef\@continuouspages{yes}}
\DeclareOption{challenges}{\gdef\@journal{challenges}\gdef\@journalfull{Challenges}\gdef\@journalshort{Challenges}\gdef\@doiabbr{challe}\gdef\@ISSN{2078-1547}}
\DeclareOption{chemengineering}{\gdef\@journal{chemengineering}\gdef\@journalfull{ChemEngineering}\gdef\@journalshort{ChemEngineering}\gdef\@doiabbr{chemengineering}\gdef\@ISSN{2305-7084}}
\DeclareOption{chemistry}{\gdef\@journal{chemistry}\gdef\@journalfull{Chemistry}\gdef\@journalshort{Chemistry}\gdef\@doiabbr{chemistry}\gdef\@ISSN{2624-8549}\gdef\@continuouspages{yes}}
\DeclareOption{chemosensors}{\gdef\@journal{chemosensors}\gdef\@journalfull{Chemosensors}\gdef\@journalshort{Chemosensors}\gdef\@doiabbr{chemosensors}\gdef\@ISSN{2227-9040}}
\DeclareOption{chemproc}{\gdef\@journal{chemproc}\gdef\@journalfull{Chemistry Proceedings}\gdef\@journalshort{Chem. Proc.}\gdef\@doiabbr{chemproc}\gdef\@ISSN{2673-4583}}
\DeclareOption{children}{\gdef\@journal{children}\gdef\@journalfull{Children}\gdef\@journalshort{Children}\gdef\@doiabbr{children}\gdef\@ISSN{2227-9067}}
\DeclareOption{chips}{\gdef\@journal{chips}\gdef\@journalfull{Chips}\gdef\@journalshort{Chips}\gdef\@doiabbr{chips}\gdef\@ISSN{2674-0710}\gdef\@continuouspages{yes}}
\DeclareOption{cimb}{\gdef\@journal{cimb}\gdef\@journalfull{Current Issues in Molecular Biology}\gdef\@journalshort{Curr. Issues Mol. Biol.}\gdef\@doiabbr{cimb}\gdef\@ISSN{1467-3045}\gdef\@continuouspages{yes}}
\DeclareOption{civileng}{\gdef\@journal{civileng}\gdef\@journalfull{CivilEng}\gdef\@journalshort{CivilEng}\gdef\@doiabbr{civileng}\gdef\@ISSN{2673-4109}\gdef\@continuouspages{yes}}
\DeclareOption{cleantechnol}{\gdef\@journal{cleantechnol}\gdef\@journalfull{Clean Technologies}\gdef\@journalshort{Clean Technol.}\gdef\@doiabbr{cleantechnol}\gdef\@ISSN{2571-8797}\gdef\@continuouspages{yes}}
\DeclareOption{climate}{\gdef\@journal{climate}\gdef\@journalfull{Climate}\gdef\@journalshort{Climate}\gdef\@doiabbr{cli}\gdef\@ISSN{2225-1154}}
\DeclareOption{clinpract}{\gdef\@journal{clinpract}\gdef\@journalfull{Clinics and Practice}\gdef\@journalshort{Clin. Pract.}\gdef\@doiabbr{clinpract}\gdef\@ISSN{2039-7283}\gdef\@continuouspages{yes}}
\DeclareOption{clockssleep}{\gdef\@journal{clockssleep}\gdef\@journalfull{Clocks \& Sleep}\gdef\@journalshort{Clocks\&Sleep}\gdef\@doiabbr{clockssleep}\gdef\@ISSN{2624-5175}\gdef\@continuouspages{yes}}
\DeclareOption{cmd}{\gdef\@journal{cmd}\gdef\@journalfull{Corrosion and Materials Degradation}\gdef\@journalshort{Corros. Mater. Degrad.}\gdef\@doiabbr{cmd}\gdef\@ISSN{2624-5558}\gdef\@continuouspages{yes}}
\DeclareOption{coasts}{\gdef\@journal{coasts}\gdef\@journalfull{Coasts}\gdef\@journalshort{Coasts}\gdef\@doiabbr{coasts}\gdef\@ISSN{2673-964X}\gdef\@continuouspages{yes}}
\DeclareOption{coatings}{\gdef\@journal{coatings}\gdef\@journalfull{Coatings}\gdef\@journalshort{Coatings}\gdef\@doiabbr{coatings}\gdef\@ISSN{2079-6412}}
\DeclareOption{colloids}{\gdef\@journal{colloids}\gdef\@journalfull{Colloids Interfaces}\gdef\@journalshort{Colloids Interfaces}\gdef\@doiabbr{colloids}\gdef\@ISSN{2504-5377}}
\DeclareOption{colorants}{\gdef\@journal{colorants}\gdef\@journalfull{Colorants}\gdef\@journalshort{Colorants}\gdef\@doiabbr{colorants}\gdef\@ISSN{2079-6447}\gdef\@continuouspages{yes}}
\DeclareOption{commodities}{\gdef\@journal{commodities}\gdef\@journalfull{Commodities}\gdef\@journalshort{Commodities}\gdef\@doiabbr{commodities}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{compounds}{\gdef\@journal{compounds}\gdef\@journalfull{Compounds}\gdef\@journalshort{Compounds}\gdef\@doiabbr{compounds}\gdef\@ISSN{2673-6918}\gdef\@continuouspages{yes}}
\DeclareOption{computation}{\gdef\@journal{computation}\gdef\@journalfull{Computation}\gdef\@journalshort{Computation}\gdef\@doiabbr{computation}\gdef\@ISSN{2079-3197}}
\DeclareOption{computers}{\gdef\@journal{computers}\gdef\@journalfull{Computers}\gdef\@journalshort{Computers}\gdef\@doiabbr{computers}\gdef\@ISSN{2073-431X}}
\DeclareOption{condensedmatter}{\gdef\@journal{condensedmatter}\gdef\@journalfull{Condensed Matter}\gdef\@journalshort{Condens. Matter}\gdef\@doiabbr{condmat}\gdef\@ISSN{2410-3896}}
\DeclareOption{conservation}{\gdef\@journal{conservation}\gdef\@journalfull{Conservation}\gdef\@journalshort{Conservation}\gdef\@doiabbr{conservation}\gdef\@ISSN{2673-7159}\gdef\@continuouspages{yes}}
\DeclareOption{constrmater}{\gdef\@journal{constrmater}\gdef\@journalfull{Construction Materials}\gdef\@journalshort{Constr. Mater.}\gdef\@doiabbr{constrmater}\gdef\@ISSN{2673-7108}\gdef\@continuouspages{yes}}
\DeclareOption{cosmetics}{\gdef\@journal{cosmetics}\gdef\@journalfull{Cosmetics}\gdef\@journalshort{Cosmetics}\gdef\@doiabbr{cosmetics}\gdef\@ISSN{2079-9284}}
\DeclareOption{covid}{\gdef\@journal{covid}\gdef\@journalfull{COVID}\gdef\@journalshort{COVID}\gdef\@doiabbr{covid}\gdef\@ISSN{2673-8112}\gdef\@continuouspages{yes}}
\DeclareOption{crops}{\gdef\@journal{crops}\gdef\@journalfull{Crops}\gdef\@journalshort{Crops}\gdef\@doiabbr{crops}\gdef\@ISSN{2673-7655}\gdef\@continuouspages{yes}}
\DeclareOption{cryptography}{\gdef\@journal{cryptography}\gdef\@journalfull{Cryptography}\gdef\@journalshort{Cryptography}\gdef\@doiabbr{cryptography}\gdef\@ISSN{2410-387X}}
\DeclareOption{crystals}{\gdef\@journal{crystals}\gdef\@journalfull{Crystals}\gdef\@journalshort{Crystals}\gdef\@doiabbr{cryst}\gdef\@ISSN{2073-4352}}
\DeclareOption{csmf}{\gdef\@journal{csmf}\gdef\@journalfull{Computer Sciences \& Mathematics Forum}\gdef\@journalshort{Comput. Sci. Math. Forum}\gdef\@doiabbr{csmf}\gdef\@ISSN{2813-0324}\gdef\@continuouspages{yes}}
\DeclareOption{ctn}{\gdef\@journal{ctn}\gdef\@journalfull{Clinical and Translational Neuroscience}\gdef\@journalshort{CTN}\gdef\@doiabbr{Clin. Transl. Neurosci.}\gdef\@ISSN{2514-183X}}
\DeclareOption{curroncol}{\gdef\@journal{curroncol}\gdef\@journalfull{Current Oncology}\gdef\@journalshort{Curr. Oncol.}\gdef\@doiabbr{curroncol}\gdef\@ISSN{1718-7729}\gdef\@continuouspages{yes}}
\DeclareOption{currophthalmol}{\gdef\@journal{currophthalmol}\gdef\@journalfull{Current Ophthalmology}\gdef\@journalshort{Curr. Ophthalmol.}\gdef\@doiabbr{currophthalmol}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{cyber}{\gdef\@journal{cyber}\gdef\@journalfull{Cyber}\gdef\@journalshort{Cyber}\gdef\@doiabbr{cyber}\gdef\@ISSN{2624-800X}}
\DeclareOption{dairy}{\gdef\@journal{dairy}\gdef\@journalfull{Dairy}\gdef\@journalshort{Dairy}\gdef\@doiabbr{dairy}\gdef\@ISSN{2624-862X}\gdef\@continuouspages{yes}}
\DeclareOption{data}{\gdef\@journal{data}\gdef\@journalfull{Data}\gdef\@journalshort{Data}\gdef\@doiabbr{data}\gdef\@ISSN{2306-5729}}
\DeclareOption{dentistry}{\gdef\@journal{dentistry}\gdef\@journalfull{Dentistry Journal}\gdef\@journalshort{Dent. J.}\gdef\@doiabbr{dj}\gdef\@ISSN{2304-6767}}
\DeclareOption{dermato}{\gdef\@journal{dermato}\gdef\@journalfull{Dermato}\gdef\@journalshort{Dermato}\gdef\@doiabbr{dermato}\gdef\@ISSN{2673-6179}\gdef\@continuouspages{yes}}
\DeclareOption{dermatopathology}{\gdef\@journal{dermatopathology}\gdef\@journalfull{Dermatopathology}\gdef\@journalshort{Dermatopathology}\gdef\@doiabbr{dermatopathology}\gdef\@ISSN{2296-3529}\gdef\@continuouspages{yes}}
\DeclareOption{designs}{\gdef\@journal{designs}\gdef\@journalfull{Designs}\gdef\@journalshort{Designs}\gdef\@doiabbr{designs}\gdef\@ISSN{2411-9660}}
\DeclareOption{diabetology}{\gdef\@journal{diabetology}\gdef\@journalfull{Diabetology}\gdef\@journalshort{Diabetology}\gdef\@doiabbr{diabetology}\gdef\@ISSN{2673-4540}\gdef\@continuouspages{yes}}
\DeclareOption{diagnostics}{\gdef\@journal{diagnostics}\gdef\@journalfull{Diagnostics}\gdef\@journalshort{Diagnostics}\gdef\@doiabbr{diagnostics}\gdef\@ISSN{2075-4418}}
\DeclareOption{dietetics}{\gdef\@journal{dietetics}\gdef\@journalfull{Dietetics}\gdef\@journalshort{Dietetics}\gdef\@doiabbr{dietetics}\gdef\@ISSN{2674-0311}\gdef\@continuouspages{yes}}
\DeclareOption{digital}{\gdef\@journal{digital}\gdef\@journalfull{Digital}\gdef\@journalshort{Digital}\gdef\@doiabbr{digital}\gdef\@ISSN{2673-6470}\gdef\@continuouspages{yes}}
\DeclareOption{disabilities}{\gdef\@journal{disabilities}\gdef\@journalfull{Disabilities}\gdef\@journalshort{Disabilities}\gdef\@doiabbr{disabilities}\gdef\@ISSN{2673-7272}\gdef\@continuouspages{yes}}
\DeclareOption{diseases}{\gdef\@journal{diseases}\gdef\@journalfull{Diseases}\gdef\@journalshort{Diseases}\gdef\@doiabbr{diseases}\gdef\@ISSN{2079-9721}}
\DeclareOption{diversity}{\gdef\@journal{diversity}\gdef\@journalfull{Diversity}\gdef\@journalshort{Diversity}\gdef\@doiabbr{d}\gdef\@ISSN{1424-2818}}
\DeclareOption{dna}{\gdef\@journal{dna}\gdef\@journalfull{DNA}\gdef\@journalshort{DNA}\gdef\@doiabbr{dna}\gdef\@ISSN{2673-8856}\gdef\@continuouspages{yes}}
\DeclareOption{drones}{\gdef\@journal{drones}\gdef\@journalfull{Drones}\gdef\@journalshort{Drones}\gdef\@doiabbr{drones}\gdef\@ISSN{2504-446X}}
\DeclareOption{dynamics}{\gdef\@journal{dynamics}\gdef\@journalfull{Dynamics}\gdef\@journalshort{Dynamics}\gdef\@doiabbr{dynamics}\gdef\@ISSN{2673-8716}\gdef\@continuouspages{yes}}
\DeclareOption{earth}{\gdef\@journal{earth}\gdef\@journalfull{Earth}\gdef\@journalshort{Earth}\gdef\@doiabbr{earth}\gdef\@ISSN{2673-4834}\gdef\@continuouspages{yes}}
\DeclareOption{ebj}{\gdef\@journal{ebj}\gdef\@journalfull{European Burn Journal}\gdef\@journalshort{Eur. Burn J.}\gdef\@doiabbr{ebj}\gdef\@ISSN{2673-1991}\gdef\@continuouspages{yes}}
\DeclareOption{ecologies}{\gdef\@journal{ecologies}\gdef\@journalfull{Ecologies}\gdef\@journalshort{Ecologies}\gdef\@doiabbr{ecologies}\gdef\@ISSN{2673-4133}\gdef\@continuouspages{yes}}
\DeclareOption{econometrics}{\gdef\@journal{econometrics}\gdef\@journalfull{Econometrics}\gdef\@journalshort{Econometrics}\gdef\@doiabbr{econometrics}\gdef\@ISSN{2225-1146}}
\DeclareOption{economies}{\gdef\@journal{economies}\gdef\@journalfull{Economies}\gdef\@journalshort{Economies}\gdef\@doiabbr{economies}\gdef\@ISSN{2227-7099}}
\DeclareOption{education}{\gdef\@journal{education}\gdef\@journalfull{Education Sciences}\gdef\@journalshort{Educ. Sci.}\gdef\@doiabbr{educsci}\gdef\@ISSN{2227-7102}}
\DeclareOption{ejihpe}{\gdef\@journal{ejihpe}\gdef\@journalfull{European Journal of Investigation in Health Psychology and Education}\gdef\@journalshort{Eur. J. Investig. Health Psychol. Educ.}\gdef\@doiabbr{ejihpe}\gdef\@ISSN{2254-9625}\gdef\@continuouspages{yes}}
\DeclareOption{electricity}{\gdef\@journal{electricity}\gdef\@journalfull{Electricity}\gdef\@journalshort{Electricity}\gdef\@doiabbr{electricity}\gdef\@ISSN{2673-4826}\gdef\@continuouspages{yes}}
\DeclareOption{electrochem}{\gdef\@journal{electrochem}\gdef\@journalfull{Electrochem}\gdef\@journalshort{Electrochem}\gdef\@doiabbr{electrochem}\gdef\@ISSN{2673-3293}\gdef\@continuouspages{yes}}
\DeclareOption{electronicmat}{\gdef\@journal{electronicmat}\gdef\@journalfull{Electronic Materials}\gdef\@journalshort{Electron. Mater.}\gdef\@doiabbr{electronicmat}\gdef\@ISSN{2673-3978}\gdef\@continuouspages{yes}}
\DeclareOption{electronics}{\gdef\@journal{electronics}\gdef\@journalfull{Electronics}\gdef\@journalshort{Electronics}\gdef\@doiabbr{electronics}\gdef\@ISSN{2079-9292}}
\DeclareOption{encyclopedia}{\gdef\@journal{encyclopedia}\gdef\@journalfull{Encyclopedia}\gdef\@journalshort{Encyclopedia}\gdef\@doiabbr{encyclopedia}\gdef\@ISSN{2673-8392}\gdef\@continuouspages{yes}}
\DeclareOption{endocrines}{\gdef\@journal{endocrines}\gdef\@journalfull{Endocrines}\gdef\@journalshort{Endocrines}\gdef\@doiabbr{endocrines}\gdef\@ISSN{2673-396X}\gdef\@continuouspages{yes}}
\DeclareOption{energies}{\gdef\@journal{energies}\gdef\@journalfull{Energies}\gdef\@journalshort{Energies}\gdef\@doiabbr{en}\gdef\@ISSN{1996-1073}}
\DeclareOption{eng}{\gdef\@journal{eng}\gdef\@journalfull{Eng-Advances in Engineering}\gdef\@journalshort{Eng}\gdef\@doiabbr{eng}\gdef\@ISSN{2673-4117}\gdef\@continuouspages{yes}}
\DeclareOption{engproc}{\gdef\@journal{engproc}\gdef\@journalfull{Engineering Proceedings}\gdef\@journalshort{Eng. Proc.}\gdef\@doiabbr{engproc}\gdef\@ISSN{2673-4591}}
%\DeclareOption{ent}{\gdef\@journal{ent}\gdef\@journalfull{}\gdef\@journalshort{}\gdef\@doiabbr{}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{entomology}{\gdef\@journal{entomology}\gdef\@journalfull{Entomology}\gdef\@journalshort{Entomology}\gdef\@doiabbr{entomology}\gdef\@ISSN{2813-0502}\gdef\@continuouspages{yes}}	
\DeclareOption{entropy}{\gdef\@journal{entropy}\gdef\@journalfull{Entropy}\gdef\@journalshort{Entropy}\gdef\@doiabbr{e}\gdef\@ISSN{1099-4300}}
\DeclareOption{environments}{\gdef\@journal{environments}\gdef\@journalfull{Environments}\gdef\@journalshort{Environments}\gdef\@doiabbr{environments}\gdef\@ISSN{2076-3298}}
\DeclareOption{environsciproc}{\gdef\@journal{environsciproc}\gdef\@journalfull{Environmental Sciences Proceedings}\gdef\@journalshort{Environ. Sci. Proc.}\gdef\@doiabbr{environsciproc}\gdef\@ISSN{2673-4931}}
\DeclareOption{epidemiologia}{\gdef\@journal{epidemiologia}\gdef\@journalfull{Epidemiologia}\gdef\@journalshort{Epidemiologia}\gdef\@doiabbr{epidemiologia}\gdef\@ISSN{2673-3986}\gdef\@continuouspages{yes}}
\DeclareOption{epigenomes}{\gdef\@journal{epigenomes}\gdef\@journalfull{Epigenomes}\gdef\@journalshort{Epigenomes}\gdef\@doiabbr{epigenomes}\gdef\@ISSN{2075-4655}}
\DeclareOption{est}{\gdef\@journal{est}\gdef\@journalfull{Electrochemical Science and Technology}\gdef\@journalshort{Electrochem. Sci. Technol.}\gdef\@doiabbr{}\gdef\@ISSN{}}
\DeclareOption{fermentation}{\gdef\@journal{fermentation}\gdef\@journalfull{Fermentation}\gdef\@journalshort{Fermentation}\gdef\@doiabbr{fermentation}\gdef\@ISSN{2311-5637}}
\DeclareOption{fibers}{\gdef\@journal{fibers}\gdef\@journalfull{Fibers}\gdef\@journalshort{Fibers}\gdef\@doiabbr{fib}\gdef\@ISSN{2079-6439}}
\DeclareOption{fintech}{\gdef\@journal{fintech}\gdef\@journalfull{FinTech}\gdef\@journalshort{FinTech}\gdef\@doiabbr{fintech}\gdef\@ISSN{2674-1032}\gdef\@continuouspages{yes}}
\DeclareOption{fire}{\gdef\@journal{fire}\gdef\@journalfull{Fire}\gdef\@journalshort{Fire}\gdef\@doiabbr{fire}\gdef\@ISSN{2571-6255}}
\DeclareOption{fishes}{\gdef\@journal{fishes}\gdef\@journalfull{Fishes}\gdef\@journalshort{Fishes}\gdef\@doiabbr{fishes}\gdef\@ISSN{2410-3888}}
\DeclareOption{fluids}{\gdef\@journal{fluids}\gdef\@journalfull{Fluids}\gdef\@journalshort{Fluids}\gdef\@doiabbr{fluids}\gdef\@ISSN{2311-5521}}
\DeclareOption{foods}{\gdef\@journal{foods}\gdef\@journalfull{Foods}\gdef\@journalshort{Foods}\gdef\@doiabbr{foods}\gdef\@ISSN{2304-8158}}
\DeclareOption{forecasting}{\gdef\@journal{forecasting}\gdef\@journalfull{Forecasting}\gdef\@journalshort{Forecasting}\gdef\@doiabbr{forecast}\gdef\@ISSN{2571-9394}\gdef\@continuouspages{yes}}
\DeclareOption{forensicsci}{\gdef\@journal{forensicsci}\gdef\@journalfull{Forensic Sciences}\gdef\@journalshort{Forensic. Sci.}\gdef\@doiabbr{forensicsci}\gdef\@ISSN{2673-6756}\gdef\@continuouspages{yes}}
\DeclareOption{forests}{\gdef\@journal{forests}\gdef\@journalfull{Forests}\gdef\@journalshort{Forests}\gdef\@doiabbr{f}\gdef\@ISSN{1999-4907}}
\DeclareOption{foundations}{\gdef\@journal{foundations}\gdef\@journalfull{Foundations}\gdef\@journalshort{Foundations}\gdef\@doiabbr{foundations}\gdef\@ISSN{2673-9321}\gdef\@continuouspages{yes}}
\DeclareOption{fractalfract}{\gdef\@journal{fractalfract}\gdef\@journalfull{Fractal and Fractional}\gdef\@journalshort{Fractal Fract.}\gdef\@doiabbr{fractalfract}\gdef\@ISSN{2504-3110}}
\DeclareOption{fuels}{\gdef\@journal{fuels}\gdef\@journalfull{Fuels}\gdef\@journalshort{Fuels}\gdef\@doiabbr{fuels}\gdef\@ISSN{2673-3994}\gdef\@continuouspages{yes}}
\DeclareOption{futureinternet}{\gdef\@journal{futureinternet}\gdef\@journalfull{Future Internet}\gdef\@journalshort{Future Internet}\gdef\@doiabbr{fi}\gdef\@ISSN{1999-5903}}
%\DeclareOption{futureparasites}{\gdef\@journal{futureparasites}\gdef\@journalfull{}\gdef\@journalshort{}\gdef\@doiabbr{}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{futurepharmacol}{\gdef\@journal{futurepharmacol}\gdef\@journalfull{Future Pharmacology}\gdef\@journalshort{Future Pharm.}\gdef\@doiabbr{futurepharmacol}\gdef\@ISSN{2673-9879}\gdef\@continuouspages{yes}}
\DeclareOption{futurephys}{\gdef\@journal{futurephys}\gdef\@journalfull{Future Physics}\gdef\@journalshort{Future Phys.}\gdef\@doiabbr{futurephys}\gdef\@ISSN{2624-6503}}
\DeclareOption{futuretransp}{\gdef\@journal{futuretransp}\gdef\@journalfull{Future Transportation}\gdef\@journalshort{Future Transp.}\gdef\@doiabbr{futuretransp}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{galaxies}{\gdef\@journal{galaxies}\gdef\@journalfull{Galaxies}\gdef\@journalshort{Galaxies}\gdef\@doiabbr{galaxies}\gdef\@ISSN{2075-4434}}
\DeclareOption{games}{\gdef\@journal{games}\gdef\@journalfull{Games}\gdef\@journalshort{Games}\gdef\@doiabbr{g}\gdef\@ISSN{2073-4336}}
\DeclareOption{gases}{\gdef\@journal{gases}\gdef\@journalfull{Gases}\gdef\@journalshort{Gases}\gdef\@doiabbr{gases}\gdef\@ISSN{2673-5628}\gdef\@continuouspages{yes}}
\DeclareOption{gastroent}{\gdef\@journal{gastroent}\gdef\@journalfull{Gastroenterology Insights}\gdef\@journalshort{Gastroenterol. Insights}\gdef\@doiabbr{gastroent}\gdef\@ISSN{2036-7422}\gdef\@continuouspages{yes}}
\DeclareOption{gastrointestdisord}{\gdef\@journal{gastrointestdisord}\gdef\@journalfull{Gastrointestinal Disorders}\gdef\@journalshort{Gastrointest. Disord.}\gdef\@doiabbr{gidisord}\gdef\@ISSN{2624-5647}\gdef\@continuouspages{yes}}
\DeclareOption{gels}{\gdef\@journal{gels}\gdef\@journalfull{Gels}\gdef\@journalshort{Gels}\gdef\@doiabbr{gels}\gdef\@ISSN{2310-2861}}
\DeclareOption{genealogy}{\gdef\@journal{genealogy}\gdef\@journalfull{Genealogy}\gdef\@journalshort{Genealogy}\gdef\@doiabbr{genealogy}\gdef\@ISSN{2313-5778}}
\DeclareOption{genes}{\gdef\@journal{genes}\gdef\@journalfull{Genes}\gdef\@journalshort{Genes}\gdef\@doiabbr{genes}\gdef\@ISSN{2073-4425}}
\DeclareOption{geographies}{\gdef\@journal{geographies}\gdef\@journalfull{Geographies}\gdef\@journalshort{Geographies}\gdef\@doiabbr{geographies}\gdef\@ISSN{2673-7086}\gdef\@continuouspages{yes}}
\DeclareOption{geohazards}{\gdef\@journal{geohazards}\gdef\@journalfull{GeoHazards}\gdef\@journalshort{GeoHazards}\gdef\@doiabbr{geohazards}\gdef\@ISSN{2624-795X}\gdef\@continuouspages{yes}}
\DeclareOption{geomatics}{\gdef\@journal{geomatics}\gdef\@journalfull{Geomatics}\gdef\@journalshort{Geomatics}\gdef\@doiabbr{geomatics}\gdef\@ISSN{2673-7418}\gdef\@continuouspages{yes}}
\DeclareOption{geosciences}{\gdef\@journal{geosciences}\gdef\@journalfull{Geosciences}\gdef\@journalshort{Geosciences}\gdef\@doiabbr{geosciences}\gdef\@ISSN{2076-3263}}
\DeclareOption{geotechnics}{\gdef\@journal{geotechnics}\gdef\@journalfull{Geotechnics}\gdef\@journalshort{Geotechnics}\gdef\@doiabbr{geotechnics}\gdef\@ISSN{2673-7094}\gdef\@continuouspages{yes}}
\DeclareOption{geriatrics}{\gdef\@journal{geriatrics}\gdef\@journalfull{Geriatrics}\gdef\@journalshort{Geriatrics}\gdef\@doiabbr{geriatrics}\gdef\@ISSN{2308-3417}}
\DeclareOption{hazardousmatters}{\gdef\@journal{hazardousmatters}\gdef\@journalfull{Hazardous Matters}\gdef\@journalshort{Hazard. Matters}\gdef\@doiabbr{}\gdef\@ISSN{0014-0014}}
\DeclareOption{healthcare}{\gdef\@journal{healthcare}\gdef\@journalfull{Healthcare}\gdef\@journalshort{Healthcare}\gdef\@doiabbr{healthcare}\gdef\@ISSN{2227-9032}}
\DeclareOption{hearts}{\gdef\@journal{hearts}\gdef\@journalfull{Hearts}\gdef\@journalshort{Hearts}\gdef\@doiabbr{hearts}\gdef\@ISSN{2673-3846}\gdef\@continuouspages{yes}}
\DeclareOption{hemato}{\gdef\@journal{hemato}\gdef\@journalfull{Hemato}\gdef\@journalshort{Hemato}\gdef\@doiabbr{hemato}\gdef\@ISSN{2673-6357}\gdef\@continuouspages{yes}}
\DeclareOption{heritage}{\gdef\@journal{heritage}\gdef\@journalfull{Heritage}\gdef\@journalshort{Heritage}\gdef\@doiabbr{heritage}\gdef\@ISSN{2571-9408}\gdef\@continuouspages{yes}}
\DeclareOption{highthroughput}{\gdef\@journal{highthroughput}\gdef\@journalfull{High-Throughput}\gdef\@journalshort{High-Throughput}\gdef\@doiabbr{ht}\gdef\@ISSN{2571-5135}}
\DeclareOption{histories}{\gdef\@journal{histories}\gdef\@journalfull{Histories}\gdef\@journalshort{Histories}\gdef\@doiabbr{histories}\gdef\@ISSN{2409-9252}\gdef\@continuouspages{yes}}
\DeclareOption{horticulturae}{\gdef\@journal{horticulturae}\gdef\@journalfull{Horticulturae}\gdef\@journalshort{Horticulturae}\gdef\@doiabbr{horticulturae}\gdef\@ISSN{2311-7524}}
\DeclareOption{humanities}{\gdef\@journal{humanities}\gdef\@journalfull{Humanities}\gdef\@journalshort{Humanities}\gdef\@doiabbr{h}\gdef\@ISSN{2076-0787}}
\DeclareOption{humans}{\gdef\@journal{humans}\gdef\@journalfull{Humans}\gdef\@journalshort{Humans}\gdef\@doiabbr{humans}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{hydrobiology}{\gdef\@journal{hydrobiology}\gdef\@journalfull{Hydrobiology}\gdef\@journalshort{Hydrobiology	}\gdef\@doiabbr{hydrobiology}\gdef\@ISSN{2673-9917}\gdef\@continuouspages{yes}}
\DeclareOption{hydrogen}{\gdef\@journal{hydrogen}\gdef\@journalfull{Hydrogen}\gdef\@journalshort{Hydrogen}\gdef\@doiabbr{hydrogen}\gdef\@ISSN{2673-4141}\gdef\@continuouspages{yes}}
\DeclareOption{hydrology}{\gdef\@journal{hydrology}\gdef\@journalfull{Hydrology}\gdef\@journalshort{Hydrology}\gdef\@doiabbr{hydrology}\gdef\@ISSN{2306-5338}}
\DeclareOption{hygiene}{\gdef\@journal{hygiene}\gdef\@journalfull{Hygiene}\gdef\@journalshort{Hygiene}\gdef\@doiabbr{hygiene}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{idr}{\gdef\@journal{idr}\gdef\@journalfull{Infectious Disease Reports}\gdef\@journalshort{Infect. Dis. Rep.}\gdef\@doiabbr{idr}\gdef\@ISSN{2036-7449}\gdef\@continuouspages{yes}}
\DeclareOption{ijerph}{\gdef\@journal{ijerph}\gdef\@journalfull{International Journal of Environmental Research and Public Health}\gdef\@journalshort{Int. J. Environ. Res. Public Health}\gdef\@doiabbr{ijerph}\gdef\@ISSN{1660-4601}}
\DeclareOption{ijfs}{\gdef\@journal{ijfs}\gdef\@journalfull{International Journal of Financial Studies}\gdef\@journalshort{Int. J. Financial Stud.}\gdef\@doiabbr{ijfs}\gdef\@ISSN{2227-7072}}
\DeclareOption{ijgi}{\gdef\@journal{ijgi}\gdef\@journalfull{ISPRS International Journal of Geo-Information}\gdef\@journalshort{ISPRS Int. J. Geo-Inf.}\gdef\@doiabbr{ijgi}\gdef\@ISSN{2220-9964}}
\DeclareOption{ijms}{\gdef\@journal{ijms}\gdef\@journalfull{International Journal of Molecular Sciences}\gdef\@journalshort{Int. J. Mol. Sci.}\gdef\@doiabbr{ijms}\gdef\@ISSN{1422-0067}}
\DeclareOption{ijns}{\gdef\@journal{ijns}\gdef\@journalfull{International Journal of Neonatal Screening}\gdef\@journalshort{Int. J. Neonatal Screen.}\gdef\@doiabbr{ijns}\gdef\@ISSN{2409-515X}}
\DeclareOption{ijtm}{\gdef\@journal{ijtm}\gdef\@journalfull{International Journal of Translational Medicine}\gdef\@journalshort{Int. J. Transl. Med.}\gdef\@doiabbr{ijtm}\gdef\@ISSN{2673-8937}\gdef\@continuouspages{yes}}
\DeclareOption{ijtpp}{\gdef\@journal{ijtpp}\gdef\@journalfull{International Journal of Turbomachinery Propulsion and Power}\gdef\@journalshort{Int. J. Turbomach. Propuls. Power}\gdef\@doiabbr{ijtpp}\gdef\@ISSN{2504-186X}}
\DeclareOption{immuno}{\gdef\@journal{immuno}\gdef\@journalfull{Immuno}\gdef\@journalshort{Immuno}\gdef\@doiabbr{immuno}\gdef\@ISSN{2673-5601}\gdef\@continuouspages{yes}}
\DeclareOption{informatics}{\gdef\@journal{informatics}\gdef\@journalfull{Informatics}\gdef\@journalshort{Informatics}\gdef\@doiabbr{informatics}\gdef\@ISSN{2227-9709}}
\DeclareOption{information}{\gdef\@journal{information}\gdef\@journalfull{Information}\gdef\@journalshort{Information}\gdef\@doiabbr{info}\gdef\@ISSN{2078-2489}}
\DeclareOption{infrastructures}{\gdef\@journal{infrastructures}\gdef\@journalfull{Infrastructures}\gdef\@journalshort{Infrastructures}\gdef\@doiabbr{infrastructures}\gdef\@ISSN{2412-3811}}
\DeclareOption{inorganics}{\gdef\@journal{inorganics}\gdef\@journalfull{Inorganics}\gdef\@journalshort{Inorganics}\gdef\@doiabbr{inorganics}\gdef\@ISSN{2304-6740}}
\DeclareOption{insects}{\gdef\@journal{insects}\gdef\@journalfull{Insects}\gdef\@journalshort{Insects}\gdef\@doiabbr{insects}\gdef\@ISSN{2075-4450}}
\DeclareOption{instruments}{\gdef\@journal{instruments}\gdef\@journalfull{Instruments}\gdef\@journalshort{Instruments}\gdef\@doiabbr{instruments}\gdef\@ISSN{2410-390X}}
\DeclareOption{inventions}{\gdef\@journal{inventions}\gdef\@journalfull{Inventions}\gdef\@journalshort{Inventions}\gdef\@doiabbr{inventions}\gdef\@ISSN{2411-5134}}
\DeclareOption{iot}{\gdef\@journal{iot}\gdef\@journalfull{IoT}\gdef\@journalshort{IoT}\gdef\@doiabbr{iot}\gdef\@ISSN{2624-831X}\gdef\@continuouspages{yes}}
\DeclareOption{j}{\gdef\@journal{j}\gdef\@journalfull{J}\gdef\@journalshort{J}\gdef\@doiabbr{j}\gdef\@ISSN{2571-8800}\gdef\@continuouspages{yes}}
\DeclareOption{jal}{\gdef\@journal{jal}\gdef\@journalfull{Journal of Ageing and Longevity}\gdef\@journalshort{J. Ageing Longev.}\gdef\@doiabbr{jal}\gdef\@ISSN{2673-9259}\gdef\@continuouspages{yes}}
\DeclareOption{jcdd}{\gdef\@journal{jcdd}\gdef\@journalfull{Journal of Cardiovascular Development and Disease}\gdef\@journalshort{J. Cardiovasc. Dev. Dis.}\gdef\@doiabbr{jcdd}\gdef\@ISSN{2308-3425}}
\DeclareOption{jcm}{\gdef\@journal{jcm}\gdef\@journalfull{Journal of Clinical Medicine}\gdef\@journalshort{J. Clin. Med.}\gdef\@doiabbr{jcm}\gdef\@ISSN{2077-0383}}
\DeclareOption{jcp}{\gdef\@journal{jcp}\gdef\@journalfull{Journal of Cybersecurity and Privacy}\gdef\@journalshort{J. Cybersecur. Priv.}\gdef\@doiabbr{jcp}\gdef\@ISSN{2624-800X}\gdef\@continuouspages{yes}}
\DeclareOption{jcs}{\gdef\@journal{jcs}\gdef\@journalfull{Journal of Composites Science}\gdef\@journalshort{J. Compos. Sci.}\gdef\@doiabbr{jcs}\gdef\@ISSN{2504-477X}}
\DeclareOption{jdb}{\gdef\@journal{jdb}\gdef\@journalfull{Journal of Developmental Biology}\gdef\@journalshort{J. Dev. Biol.}\gdef\@doiabbr{jdb}\gdef\@ISSN{2221-3759}}
\DeclareOption{jeta}{\gdef\@journal{jeta}\gdef\@journalfull{Journal of Experimental and Theoretical Analyses}\gdef\@journalshort{J. Exp. Theor. Anal.}\gdef\@doiabbr{jeta}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{jfb}{\gdef\@journal{jfb}\gdef\@journalfull{Journal of Functional Biomaterials}\gdef\@journalshort{J. Funct. Biomater.}\gdef\@doiabbr{jfb}\gdef\@ISSN{2079-4983}}
\DeclareOption{jfmk}{\gdef\@journal{jfmk}\gdef\@journalfull{Journal of Functional Morphology and Kinesiology}\gdef\@journalshort{J. Funct. Morphol. Kinesiol.}\gdef\@doiabbr{jfmk}\gdef\@ISSN{2411-5142}}
\DeclareOption{jimaging}{\gdef\@journal{jimaging}\gdef\@journalfull{Journal of Imaging}\gdef\@journalshort{J. Imaging}\gdef\@doiabbr{jimaging}\gdef\@ISSN{2313-433X}}
\DeclareOption{jintelligence}{\gdef\@journal{jintelligence}\gdef\@journalfull{Journal of Intelligence}\gdef\@journalshort{J. Intell.}\gdef\@doiabbr{jintelligence}\gdef\@ISSN{2079-3200}}
\DeclareOption{jlpea}{\gdef\@journal{jlpea}\gdef\@journalfull{Journal of Low Power Electronics and Applications}\gdef\@journalshort{J. Low Power Electron. Appl.}\gdef\@doiabbr{jlpea}\gdef\@ISSN{2079-9268}}
\DeclareOption{jmmp}{\gdef\@journal{jmmp}\gdef\@journalfull{Journal of Manufacturing and Materials Processing}\gdef\@journalshort{J. Manuf. Mater. Process.}\gdef\@doiabbr{jmmp}\gdef\@ISSN{2504-4494}}
\DeclareOption{jmp}{\gdef\@journal{jmp}\gdef\@journalfull{Journal of Molecular Pathology}\gdef\@journalshort{J. Mol. Pathol.}\gdef\@doiabbr{jmp}\gdef\@ISSN{2673-5261}\gdef\@continuouspages{yes}}
\DeclareOption{jmse}{\gdef\@journal{jmse}\gdef\@journalfull{Journal of Marine Science and Engineering}\gdef\@journalshort{J. Mar. Sci. Eng.}\gdef\@doiabbr{jmse}\gdef\@ISSN{2077-1312}}
\DeclareOption{jne}{\gdef\@journal{jne}\gdef\@journalfull{Journal of Nuclear Engineering}\gdef\@journalshort{J. Nucl. Eng.}\gdef\@doiabbr{jne}\gdef\@ISSN{2673-4362}\gdef\@continuouspages{yes}}
\DeclareOption{jnt}{\gdef\@journal{jnt}\gdef\@journalfull{Journal of Nanotheranostics}\gdef\@journalshort{J. Nanotheranostics}\gdef\@doiabbr{jnt}\gdef\@ISSN{2624-845X}\gdef\@continuouspages{yes}}
\DeclareOption{jof}{\gdef\@journal{jof}\gdef\@journalfull{Journal of Fungi}\gdef\@journalshort{J. Fungi}\gdef\@doiabbr{jof}\gdef\@ISSN{2309-608X}}
\DeclareOption{joitmc}{\gdef\@journal{joitmc}\gdef\@journalfull{Journal of Open Innovation: Technology Market and Complexity}\gdef\@journalshort{J. Open Innov. Technol. Mark. Complex.}\gdef\@doiabbr{joitmc}\gdef\@ISSN{2199-8531}}
\DeclareOption{jor}{\gdef\@journal{jor}\gdef\@journalfull{Journal of Respiration}\gdef\@journalshort{J. Respir.}\gdef\@doiabbr{jor}\gdef\@ISSN{2673-527X}\gdef\@continuouspages{yes}}
\DeclareOption{journalmedia}{\gdef\@journal{journalmedia}\gdef\@journalfull{Journalism and Media}\gdef\@journalshort{Journal. Media}\gdef\@doiabbr{journalmedia}\gdef\@ISSN{2673-5172}\gdef\@continuouspages{yes}}
\DeclareOption{jox}{\gdef\@journal{jox}\gdef\@journalfull{Journal of Xenobiotics}\gdef\@journalshort{J. Xenobiot.}\gdef\@doiabbr{jox}\gdef\@ISSN{2039-4713}\gdef\@continuouspages{yes}}
\DeclareOption{jpm}{\gdef\@journal{jpm}\gdef\@journalfull{Journal of Personalized Medicine}\gdef\@journalshort{J. Pers. Med.}\gdef\@doiabbr{jpm}\gdef\@ISSN{2075-4426}}
\DeclareOption{jrfm}{\gdef\@journal{jrfm}\gdef\@journalfull{Journal of Risk and Financial Management}\gdef\@journalshort{J. Risk Financial Manag.}\gdef\@doiabbr{jrfm}\gdef\@ISSN{1911-8074}}
\DeclareOption{jsan}{\gdef\@journal{jsan}\gdef\@journalfull{Journal of Sensor and Actuator Networks}\gdef\@journalshort{J. Sens. Actuator Netw.}\gdef\@doiabbr{jsan}\gdef\@ISSN{2224-2708}}
\DeclareOption{jtaer}{\gdef\@journal{jtaer}\gdef\@journalfull{Journal of Theoretical and Applied Electronic Commerce Research}\gdef\@journalshort{J. Theor. Appl. Electron. Commer. Res.}\gdef\@doiabbr{jtaer}\gdef\@ISSN{0718-1876}\gdef\@continuouspages{yes}}
\DeclareOption{jzbg}{\gdef\@journal{jzbg}\gdef\@journalfull{Journal of Zoological and Botanical Gardens}\gdef\@journalshort{J. Zool. Bot. Gard.}\gdef\@doiabbr{jzbg}\gdef\@ISSN{2673-5636}\gdef\@continuouspages{yes}}
%\DeclareOption{kidney}{\gdef\@journal{kidney}\gdef\@journalfull{}\gdef\@journalshort{}\gdef\@doiabbr{}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{kidneydial}{\gdef\@journal{kidneydial}\gdef\@journalfull{Kidney and Dialysis}\gdef\@journalshort{Kidney Dial.}\gdef\@doiabbr{kidneydial}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{knowledge}{\gdef\@journal{knowledge}\gdef\@journalfull{Knowledge}\gdef\@journalshort{Knowledge}\gdef\@doiabbr{knowledge}\gdef\@ISSN{2673-9585}\gdef\@continuouspages{yes}}
\DeclareOption{land}{\gdef\@journal{land}\gdef\@journalfull{Land}\gdef\@journalshort{Land}\gdef\@doiabbr{land}\gdef\@ISSN{2073-445X}}
\DeclareOption{languages}{\gdef\@journal{languages}\gdef\@journalfull{Languages}\gdef\@journalshort{Languages}\gdef\@doiabbr{languages}\gdef\@ISSN{2226-471X}}
\DeclareOption{laws}{\gdef\@journal{laws}\gdef\@journalfull{Laws}\gdef\@journalshort{Laws}\gdef\@doiabbr{laws}\gdef\@ISSN{2075-471X}}
\DeclareOption{life}{\gdef\@journal{life}\gdef\@journalfull{Life}\gdef\@journalshort{Life}\gdef\@doiabbr{life}\gdef\@ISSN{2075-1729}}
\DeclareOption{liquids}{\gdef\@journal{liquids}\gdef\@journalfull{Liquids}\gdef\@journalshort{Liquids}\gdef\@doiabbr{liquids}\gdef\@ISSN{2673-8015}\gdef\@continuouspages{yes}}
\DeclareOption{literature}{\gdef\@journal{literature}\gdef\@journalfull{Literature}\gdef\@journalshort{Literature}\gdef\@doiabbr{literature}\gdef\@ISSN{2410-9789}\gdef\@continuouspages{yes}}
\DeclareOption{livers}{\gdef\@journal{livers}\gdef\@journalfull{Livers}\gdef\@journalshort{Livers}\gdef\@doiabbr{livers}\gdef\@ISSN{2673-4389}\gdef\@continuouspages{yes}}
\DeclareOption{logics}{\gdef\@journal{logics}\gdef\@journalfull{Logics}\gdef\@journalshort{Logics}\gdef\@doiabbr{logics}\gdef\@ISSN{2813-0405}\gdef\@continuouspages{yes}}
\DeclareOption{logistics}{\gdef\@journal{logistics}\gdef\@journalfull{Logistics}\gdef\@journalshort{Logistics}\gdef\@doiabbr{logistics}\gdef\@ISSN{2305-6290}}
\DeclareOption{lubricants}{\gdef\@journal{lubricants}\gdef\@journalfull{Lubricants}\gdef\@journalshort{Lubricants}\gdef\@doiabbr{lubricants}\gdef\@ISSN{2075-4442}}
\DeclareOption{lymphatics}{\gdef\@journal{lymphatics}\gdef\@journalfull{Lymphatics}\gdef\@journalshort{Lymphatics}\gdef\@doiabbr{lymphatics}\gdef\@ISSN{}\gdef\@continuouspages{yes}}	
\DeclareOption{machines}{\gdef\@journal{machines}\gdef\@journalfull{Machines}\gdef\@journalshort{Machines}\gdef\@doiabbr{machines}\gdef\@ISSN{2075-1702}}
\DeclareOption{macromol}{\gdef\@journal{macromol}\gdef\@journalfull{Macromol}\gdef\@journalshort{Macromol}\gdef\@doiabbr{macromol}\gdef\@ISSN{2673-6209}\gdef\@continuouspages{yes}}
\DeclareOption{magnetism}{\gdef\@journal{magnetism}\gdef\@journalfull{Magnetism}\gdef\@journalshort{Magnetism}\gdef\@doiabbr{magnetism}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{magnetochemistry}{\gdef\@journal{magnetochemistry}\gdef\@journalfull{Magnetochemistry}\gdef\@journalshort{Magnetochemistry}\gdef\@doiabbr{magnetochemistry}\gdef\@ISSN{2312-7481}}
\DeclareOption{make}{\gdef\@journal{make}\gdef\@journalfull{Machine Learning and Knowledge Extraction}\gdef\@journalshort{Mach. Learn. Knowl. Extr.}\gdef\@doiabbr{make}\gdef\@ISSN{2504-4990}\gdef\@continuouspages{yes}}
\DeclareOption{marinedrugs}{\gdef\@journal{marinedrugs}\gdef\@journalfull{Marine Drugs}\gdef\@journalshort{Mar. Drugs}\gdef\@doiabbr{md}\gdef\@ISSN{1660-3397}}
\DeclareOption{materials}{\gdef\@journal{materials}\gdef\@journalfull{Materials}\gdef\@journalshort{Materials}\gdef\@doiabbr{ma}\gdef\@ISSN{1996-1944}}
\DeclareOption{materproc}{\gdef\@journal{materproc}\gdef\@journalfull{Materials Proceedings}\gdef\@journalshort{Mater. Proc.}\gdef\@doiabbr{materproc}\gdef\@ISSN{2673-4605}}
\DeclareOption{mathematics}{\gdef\@journal{mathematics}\gdef\@journalfull{Mathematics}\gdef\@journalshort{Mathematics}\gdef\@doiabbr{math}\gdef\@ISSN{2227-7390}}
\DeclareOption{mca}{\gdef\@journal{mca}\gdef\@journalfull{Mathematical and Computational Applications}\gdef\@journalshort{Math. Comput. Appl.}\gdef\@doiabbr{mca}\gdef\@ISSN{2297-8747}}
\DeclareOption{measurements}{\gdef\@journal{measurements}\gdef\@journalfull{Measurements}\gdef\@journalshort{Measurements}\gdef\@doiabbr{measurements}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{medicina}{\gdef\@journal{medicina}\gdef\@journalfull{Medicina}\gdef\@journalshort{Medicina}\gdef\@doiabbr{medicina}\gdef\@ISSN{1648-9144}}
\DeclareOption{medicines}{\gdef\@journal{medicines}\gdef\@journalfull{Medicines}\gdef\@journalshort{Medicines}\gdef\@doiabbr{medicines}\gdef\@ISSN{2305-6320}}
\DeclareOption{medsci}{\gdef\@journal{medsci}\gdef\@journalfull{Medical Sciences}\gdef\@journalshort{Med. Sci.}\gdef\@doiabbr{medsci}\gdef\@ISSN{2076-3271}}
\DeclareOption{membranes}{\gdef\@journal{membranes}\gdef\@journalfull{Membranes}\gdef\@journalshort{Membranes}\gdef\@doiabbr{membranes}\gdef\@ISSN{2077-0375}}
\DeclareOption{merits}{\gdef\@journal{merits}\gdef\@journalfull{Merits}\gdef\@journalshort{Merits}\gdef\@doiabbr{merits}\gdef\@ISSN{2673-8104}\gdef\@continuouspages{yes}}
\DeclareOption{metabolites}{\gdef\@journal{metabolites}\gdef\@journalfull{Metabolites}\gdef\@journalshort{Metabolites}\gdef\@doiabbr{metabo}\gdef\@ISSN{2218-1989}}
\DeclareOption{metals}{\gdef\@journal{metals}\gdef\@journalfull{Metals}\gdef\@journalshort{Metals}\gdef\@doiabbr{met}\gdef\@ISSN{2075-4701}}
\DeclareOption{meteorology}{\gdef\@journal{meteorology}\gdef\@journalfull{Meteorology}\gdef\@journalshort{Meteorology}\gdef\@doiabbr{meteorology}\gdef\@ISSN{2674-0494}\gdef\@continuouspages{yes}}
\DeclareOption{methane}{\gdef\@journal{methane}\gdef\@journalfull{Methane}\gdef\@journalshort{Methane}\gdef\@doiabbr{methane}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{metrology}{\gdef\@journal{metrology}\gdef\@journalfull{Metrology}\gdef\@journalshort{Metrology}\gdef\@doiabbr{metrology}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{micro}{\gdef\@journal{micro}\gdef\@journalfull{Micro}\gdef\@journalshort{Micro}\gdef\@doiabbr{micro}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{microarrays}{\gdef\@journal{microarrays}\gdef\@journalfull{Microarrays}\gdef\@journalshort{Microarrays}\gdef\@doiabbr{microarrays}\gdef\@ISSN{2076-3905}}
\DeclareOption{microbiolres}{\gdef\@journal{microbiolres}\gdef\@journalfull{Microbiology Research}\gdef\@journalshort{Microbiol. Res.}\gdef\@doiabbr{microbiolres}\gdef\@ISSN{2036-7481}\gdef\@continuouspages{yes}}
\DeclareOption{micromachines}{\gdef\@journal{micromachines}\gdef\@journalfull{Micromachines}\gdef\@journalshort{Micromachines}\gdef\@doiabbr{mi}\gdef\@ISSN{2072-666X}}
\DeclareOption{microorganisms}{\gdef\@journal{microorganisms}\gdef\@journalfull{Microorganisms}\gdef\@journalshort{Microorganisms}\gdef\@doiabbr{microorganisms}\gdef\@ISSN{2076-2607}}
\DeclareOption{microplastics}{\gdef\@journal{microplastics}\gdef\@journalfull{Microplastics}\gdef\@journalshort{Microplastics}\gdef\@doiabbr{microplastics}\gdef\@ISSN{2673-8929}\gdef\@continuouspages{yes}}
\DeclareOption{minerals}{\gdef\@journal{minerals}\gdef\@journalfull{Minerals}\gdef\@journalshort{Minerals}\gdef\@doiabbr{min}\gdef\@ISSN{2075-163X}}
\DeclareOption{mining}{\gdef\@journal{mining}\gdef\@journalfull{Mining}\gdef\@journalshort{Mining}\gdef\@doiabbr{mining}\gdef\@ISSN{2673-6489}\gdef\@continuouspages{yes}}
\DeclareOption{modelling}{\gdef\@journal{modelling}\gdef\@journalfull{Modelling}\gdef\@journalshort{Modelling}\gdef\@doiabbr{modelling}\gdef\@ISSN{2673-3951}\gdef\@continuouspages{yes}}
\DeclareOption{molbank}{\gdef\@journal{molbank}\gdef\@journalfull{Molbank}\gdef\@journalshort{Molbank}\gdef\@doiabbr{M}\gdef\@ISSN{1422-8599}}
\DeclareOption{molecules}{\gdef\@journal{molecules}\gdef\@journalfull{Molecules}\gdef\@journalshort{Molecules}\gdef\@doiabbr{molecules}\gdef\@ISSN{1420-3049}}
\DeclareOption{mps}{\gdef\@journal{mps}\gdef\@journalfull{Methods and Protocols}\gdef\@journalshort{Methods Protoc.}\gdef\@doiabbr{mps}\gdef\@ISSN{2409-9279}}
\DeclareOption{msf}{\gdef\@journal{msf}\gdef\@journalfull{Medical Sciences Forum}\gdef\@journalshort{Med. Sci. Forum}\gdef\@doiabbr{msf}\gdef\@ISSN{2673-9992}}
\DeclareOption{mti}{\gdef\@journal{mti}\gdef\@journalfull{Multimodal Technologies and Interaction}\gdef\@journalshort{Multimodal Technol. Interact.}\gdef\@doiabbr{mti}\gdef\@ISSN{2414-4088}}
\DeclareOption{muscles}{\gdef\@journal{muscles}\gdef\@journalfull{Muscles}\gdef\@journalshort{Muscles}\gdef\@doiabbr{muscles}\gdef\@ISSN{2813-0413}\gdef\@continuouspages{yes}}
\DeclareOption{nanoenergyadv}{\gdef\@journal{nanoenergyadv}\gdef\@journalfull{Nanoenergy Advances}\gdef\@journalshort{Nanoenergy Adv.}\gdef\@doiabbr{nanoenergyadv}\gdef\@ISSN{2673-706X}\gdef\@continuouspages{yes}}
\DeclareOption{nanomanufacturing}{\gdef\@journal{nanomanufacturing}\gdef\@journalfull{Nanomanufacturing}\gdef\@journalshort{Nanomanufacturing}\gdef\@doiabbr{nanomanufacturing}\gdef\@ISSN{2673-687X}\gdef\@continuouspages{yes}}
\DeclareOption{nanomaterials}{\gdef\@journal{nanomaterials}\gdef\@journalfull{Nanomaterials}\gdef\@journalshort{Nanomaterials}\gdef\@doiabbr{nano}\gdef\@ISSN{2079-4991}}
\DeclareOption{ncrna}{\gdef\@journal{ncrna}\gdef\@journalfull{Non-coding RNA}\gdef\@journalshort{Non-coding RNA}\gdef\@doiabbr{ncrna}\gdef\@ISSN{2311-553X}}
\DeclareOption{network}{\gdef\@journal{network}\gdef\@journalfull{Network}\gdef\@journalshort{Network}\gdef\@doiabbr{network}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{neuroglia}{\gdef\@journal{neuroglia}\gdef\@journalfull{Neuroglia}\gdef\@journalshort{Neuroglia}\gdef\@doiabbr{neuroglia}\gdef\@ISSN{2571-6980}\gdef\@continuouspages{yes}}
\DeclareOption{neurolint}{\gdef\@journal{neurolint}\gdef\@journalfull{Neurology International}\gdef\@journalshort{Neurol. Int.}\gdef\@doiabbr{neurolint}\gdef\@ISSN{2035-8377}\gdef\@continuouspages{yes}}
\DeclareOption{neurosci}{\gdef\@journal{neurosci}\gdef\@journalfull{NeuroSci}\gdef\@journalshort{NeuroSci}\gdef\@doiabbr{neurosci}\gdef\@ISSN{2673-4087}\gdef\@continuouspages{yes}}
\DeclareOption{nitrogen}{\gdef\@journal{nitrogen}\gdef\@journalfull{Nitrogen}\gdef\@journalshort{Nitrogen}\gdef\@doiabbr{nitrogen}\gdef\@ISSN{2504-3129}\gdef\@continuouspages{yes}}
\DeclareOption{notspecified}{\gdef\@journal{notspecified}\gdef\@journalfull{Journal Not Specified}\gdef\@journalshort{Journal Not Specified}\gdef\@doiabbr{}\gdef\@ISSN{}}
%\DeclareOption{nri}{\gdef\@journal{nri}\gdef\@journalfull{Natural Resources Informatics}\gdef\@journalshort{Nat. Resour. Inform.}\gdef\@doiabbr{nri}\gdef\@ISSN{2673-981X}\gdef\@continuouspages{yes}}
\DeclareOption{nursrep}{\gdef\@journal{nursrep}\gdef\@journalfull{Nursing Reports}\gdef\@journalshort{Nurs. Rep.}\gdef\@doiabbr{nursrep}\gdef\@ISSN{2039-4403}\gdef\@continuouspages{yes}}
\DeclareOption{nutraceuticals}{\gdef\@journal{nutraceuticals}\gdef\@journalfull{Nutraceuticals}\gdef\@journalshort{Nutraceuticals}\gdef\@doiabbr{nutraceuticals}\gdef\@ISSN{1661-3821}\gdef\@continuouspages{yes}}
\DeclareOption{nutrients}{\gdef\@journal{nutrients}\gdef\@journalfull{Nutrients}\gdef\@journalshort{Nutrients}\gdef\@doiabbr{nu}\gdef\@ISSN{2072-6643}}
\DeclareOption{obesities}{\gdef\@journal{obesities}\gdef\@journalfull{Obesities}\gdef\@journalshort{Obesities}\gdef\@doiabbr{obesities}\gdef\@ISSN{2673-4168}\gdef\@continuouspages{yes}}
\DeclareOption{oceans}{\gdef\@journal{oceans}\gdef\@journalfull{Oceans}\gdef\@journalshort{Oceans}\gdef\@doiabbr{oceans}\gdef\@ISSN{2673-1924}\gdef\@continuouspages{yes}}
\DeclareOption{ohbm}{\gdef\@journal{ohbm}\gdef\@journalfull{Journal of Otorhinolaryngology Hearing and Balance Medicine}\gdef\@journalshort{J. Otorhinolaryngol. Hear. Balance Med.}\gdef\@doiabbr{ohbm}\gdef\@ISSN{2504-463X}}
\DeclareOption{onco}{\gdef\@journal{onco}\gdef\@journalfull{Onco}\gdef\@journalshort{Onco}\gdef\@doiabbr{onco}\gdef\@ISSN{2673-7523}\gdef\@continuouspages{yes}}
%\DeclareOption{oncopathology}{\gdef\@journal{oncopathology}\gdef\@journalfull{}\gdef\@journalshort{}\gdef\@doiabbr{}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{optics}{\gdef\@journal{optics}\gdef\@journalfull{Optics}\gdef\@journalshort{Optics}\gdef\@doiabbr{opt}\gdef\@ISSN{2673-3269}\gdef\@continuouspages{yes}}
\DeclareOption{oral}{\gdef\@journal{oral}\gdef\@journalfull{Oral}\gdef\@journalshort{Oral}\gdef\@doiabbr{oral}\gdef\@ISSN{2673-6373}\gdef\@continuouspages{yes}}
\DeclareOption{organics}{\gdef\@journal{organics}\gdef\@journalfull{Organics}\gdef\@journalshort{Organics}\gdef\@doiabbr{org}\gdef\@ISSN{2673-401X}\gdef\@continuouspages{yes}}
\DeclareOption{organoids}{\gdef\@journal{organoids}\gdef\@journalfull{Organoids}\gdef\@journalshort{Organoids}\gdef\@doiabbr{organoids}\gdef\@ISSN{2674-1172}\gdef\@continuouspages{yes}}
\DeclareOption{osteology}{\gdef\@journal{osteology}\gdef\@journalfull{Osteology}\gdef\@journalshort{Osteology}\gdef\@doiabbr{osteology}\gdef\@ISSN{2673-4036}\gdef\@continuouspages{yes}}
\DeclareOption{oxygen}{\gdef\@journal{oxygen}\gdef\@journalfull{Oxygen}\gdef\@journalshort{Oxygen}\gdef\@doiabbr{oxygen}\gdef\@ISSN{2673-9801}\gdef\@continuouspages{yes}}
\DeclareOption{parasites}{\gdef\@journal{parasites}\gdef\@journalfull{Parasites}\gdef\@journalshort{Parasites}\gdef\@doiabbr{parasites}\gdef\@ISSN{2673-5946}}
\DeclareOption{parasitologia}{\gdef\@journal{parasitologia}\gdef\@journalfull{Parasitologia}\gdef\@journalshort{Parasitologia}\gdef\@doiabbr{parasitologia}\gdef\@ISSN{2673-6772}\gdef\@continuouspages{yes}}
\DeclareOption{particles}{\gdef\@journal{particles}\gdef\@journalfull{Particles}\gdef\@journalshort{Particles}\gdef\@doiabbr{particles}\gdef\@ISSN{2571-712X}\gdef\@continuouspages{yes}}
\DeclareOption{pathogens}{\gdef\@journal{pathogens}\gdef\@journalfull{Pathogens}\gdef\@journalshort{Pathogens}\gdef\@doiabbr{pathogens}\gdef\@ISSN{2076-0817}}
\DeclareOption{pathophysiology}{\gdef\@journal{pathophysiology}\gdef\@journalfull{Pathophysiology}\gdef\@journalshort{Pathophysiology}\gdef\@doiabbr{pathophysiology}\gdef\@ISSN{0928-4680}\gdef\@continuouspages{yes}}
\DeclareOption{pediatrrep}{\gdef\@journal{pediatrrep}\gdef\@journalfull{Pediatric Reports}\gdef\@journalshort{Pediatr. Rep.}\gdef\@doiabbr{pediatric}\gdef\@ISSN{2036-7503}\gdef\@continuouspages{yes}}
\DeclareOption{pharmaceuticals}{\gdef\@journal{pharmaceuticals}\gdef\@journalfull{Pharmaceuticals}\gdef\@journalshort{Pharmaceuticals}\gdef\@doiabbr{ph}\gdef\@ISSN{1424-8247}}
\DeclareOption{pharmaceutics}{\gdef\@journal{pharmaceutics}\gdef\@journalfull{Pharmaceutics}\gdef\@journalshort{Pharmaceutics}\gdef\@doiabbr{pharmaceutics}\gdef\@ISSN{1999-4923}}
\DeclareOption{pharmacoepidemiology}{\gdef\@journal{pharmacoepidemiology}\gdef\@journalfull{Pharmacoepidemiology}\gdef\@journalshort{Pharmacoepidemiology}\gdef\@doiabbr{pharma}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{pharmacy}{\gdef\@journal{pharmacy}\gdef\@journalfull{Pharmacy}\gdef\@journalshort{Pharmacy}\gdef\@doiabbr{pharmacy}\gdef\@ISSN{2226-4787}}
\DeclareOption{philosophies}{\gdef\@journal{philosophies}\gdef\@journalfull{Philosophies}\gdef\@journalshort{Philosophies}\gdef\@doiabbr{philosophies}\gdef\@ISSN{2409-9287}}
\DeclareOption{photochem}{\gdef\@journal{photochem}\gdef\@journalfull{Photochem}\gdef\@journalshort{Photochem}\gdef\@doiabbr{photochem}\gdef\@ISSN{2673-7256}\gdef\@continuouspages{yes}}
\DeclareOption{photonics}{\gdef\@journal{photonics}\gdef\@journalfull{Photonics}\gdef\@journalshort{Photonics}\gdef\@doiabbr{photonics}\gdef\@ISSN{2304-6732}}
\DeclareOption{phycology}{\gdef\@journal{phycology}\gdef\@journalfull{Phycology}\gdef\@journalshort{Phycology}\gdef\@doiabbr{phycology}\gdef\@ISSN{2673-9410}\gdef\@continuouspages{yes}}
\DeclareOption{physchem}{\gdef\@journal{physchem}\gdef\@journalfull{Physchem}\gdef\@journalshort{Physchem}\gdef\@doiabbr{physchem}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{physics}{\gdef\@journal{physics}\gdef\@journalfull{Physics}\gdef\@journalshort{Physics}\gdef\@doiabbr{physics}\gdef\@ISSN{2624-8174}\gdef\@continuouspages{yes}}
\DeclareOption{physiologia}{\gdef\@journal{physiologia}\gdef\@journalfull{Physiologia}\gdef\@journalshort{Physiologia}\gdef\@doiabbr{physiologia}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{plants}{\gdef\@journal{plants}\gdef\@journalfull{Plants}\gdef\@journalshort{Plants}\gdef\@doiabbr{plants}\gdef\@ISSN{2223-7747}}
\DeclareOption{plasma}{\gdef\@journal{plasma}\gdef\@journalfull{Plasma}\gdef\@journalshort{Plasma}\gdef\@doiabbr{plasma}\gdef\@ISSN{2571-6182}\gdef\@continuouspages{yes}}
\DeclareOption{pollutants}{\gdef\@journal{pollutants}\gdef\@journalfull{Pollutants}\gdef\@journalshort{Pollutants}\gdef\@doiabbr{pollutants}\gdef\@ISSN{2673-4672}\gdef\@continuouspages{yes}}
\DeclareOption{polymers}{\gdef\@journal{polymers}\gdef\@journalfull{Polymers}\gdef\@journalshort{Polymers}\gdef\@doiabbr{polym}\gdef\@ISSN{2073-4360}}
\DeclareOption{polysaccharides}{\gdef\@journal{polysaccharides}\gdef\@journalfull{Polysaccharides}\gdef\@journalshort{Polysaccharides}\gdef\@doiabbr{polysaccharides}\gdef\@ISSN{2673-4176}\gdef\@continuouspages{yes}}
\DeclareOption{poultry}{\gdef\@journal{poultry}\gdef\@journalfull{Poultry}\gdef\@journalshort{Poultry}\gdef\@doiabbr{poultry}\gdef\@ISSN{2674-1164}\gdef\@continuouspages{yes}}
\DeclareOption{powders}{\gdef\@journal{powders}\gdef\@journalfull{Powders}\gdef\@journalshort{Powders}\gdef\@doiabbr{powders}\gdef\@ISSN{2674-0516}\gdef\@continuouspages{yes}}
\DeclareOption{preprints}{\gdef\@journal{preprints}\gdef\@journalfull{Preprints}\gdef\@journalshort{Preprints}\gdef\@doiabbr{}\gdef\@ISSN{}}
\DeclareOption{proceedings}{\gdef\@journal{proceedings}\gdef\@journalfull{Proceedings}\gdef\@journalshort{Proceedings}\gdef\@doiabbr{proceedings}\gdef\@ISSN{2504-3900}}
\DeclareOption{processes}{\gdef\@journal{processes}\gdef\@journalfull{Processes}\gdef\@journalshort{Processes}\gdef\@doiabbr{pr}\gdef\@ISSN{2227-9717}}
\DeclareOption{prosthesis}{\gdef\@journal{prosthesis}\gdef\@journalfull{Prosthesis}\gdef\@journalshort{Prosthesis}\gdef\@doiabbr{prosthesis}\gdef\@ISSN{2673-1592}\gdef\@continuouspages{yes}}
\DeclareOption{proteomes}{\gdef\@journal{proteomes}\gdef\@journalfull{Proteomes}\gdef\@journalshort{Proteomes}\gdef\@doiabbr{proteomes}\gdef\@ISSN{2227-7382}}
\DeclareOption{psf}{\gdef\@journal{psf}\gdef\@journalfull{Physical Sciences Forum}\gdef\@journalshort{Phys. Sci. Forum}\gdef\@doiabbr{psf}\gdef\@ISSN{2673-9984}}
\DeclareOption{psych}{\gdef\@journal{psych}\gdef\@journalfull{Psych}\gdef\@journalshort{Psych}\gdef\@doiabbr{psych}\gdef\@ISSN{2624-8611}\gdef\@continuouspages{yes}}
\DeclareOption{psychiatryint}{\gdef\@journal{psychiatryint}\gdef\@journalfull{Psychiatry International}\gdef\@journalshort{Psychiatry Int.}\gdef\@doiabbr{psychiatryint}\gdef\@ISSN{2673-5318}\gdef\@continuouspages{yes}}
\DeclareOption{psychoactives}{\gdef\@journal{psychoactives}\gdef\@journalfull{Psychoactives}\gdef\@journalshort{Psychoactives}\gdef\@doiabbr{psychoactives}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{publications}{\gdef\@journal{publications}\gdef\@journalfull{Publications}\gdef\@journalshort{Publications}\gdef\@doiabbr{publications}\gdef\@ISSN{2304-6775}}
\DeclareOption{quantumrep}{\gdef\@journal{quantumrep}\gdef\@journalfull{Quantum Reports}\gdef\@journalshort{Quantum Rep.}\gdef\@doiabbr{quantum}\gdef\@ISSN{2624-960X}\gdef\@continuouspages{yes}}
\DeclareOption{quaternary}{\gdef\@journal{quaternary}\gdef\@journalfull{Quaternary}\gdef\@journalshort{Quaternary}\gdef\@doiabbr{quat}\gdef\@ISSN{2571-550X}}
\DeclareOption{qubs}{\gdef\@journal{qubs}\gdef\@journalfull{Quantum Beam Science}\gdef\@journalshort{Quantum Beam Sci.}\gdef\@doiabbr{qubs}\gdef\@ISSN{2412-382X}}
\DeclareOption{radiation}{\gdef\@journal{radiation}\gdef\@journalfull{Radiation}\gdef\@journalshort{Radiation}\gdef\@doiabbr{radiation}\gdef\@ISSN{2673-592X}\gdef\@continuouspages{yes}}
\DeclareOption{reactions}{\gdef\@journal{reactions}\gdef\@journalfull{Reactions}\gdef\@journalshort{Reactions}\gdef\@doiabbr{reactions}\gdef\@ISSN{2624-781X}\gdef\@continuouspages{yes}}
\DeclareOption{receptors}{\gdef\@journal{receptors}\gdef\@journalfull{Receptors}\gdef\@journalshort{Receptors}\gdef\@doiabbr{receptors}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{recycling}{\gdef\@journal{recycling}\gdef\@journalfull{Recycling}\gdef\@journalshort{Recycling}\gdef\@doiabbr{recycling}\gdef\@ISSN{2313-4321}}
\DeclareOption{regeneration}{\gdef\@journal{regeneration}\gdef\@journalfull{Regeneration}\gdef\@journalshort{Regeneration}\gdef\@doiabbr{regeneration}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{religions}{\gdef\@journal{religions}\gdef\@journalfull{Religions}\gdef\@journalshort{Religions}\gdef\@doiabbr{rel}\gdef\@ISSN{2077-1444}}
\DeclareOption{remotesensing}{\gdef\@journal{remotesensing}\gdef\@journalfull{Remote Sensing}\gdef\@journalshort{Remote Sens.}\gdef\@doiabbr{rs}\gdef\@ISSN{2072-4292}}
\DeclareOption{reports}{\gdef\@journal{reports}\gdef\@journalfull{Reports}\gdef\@journalshort{Reports}\gdef\@doiabbr{reports}\gdef\@ISSN{2571-841X}}
\DeclareOption{reprodmed}{\gdef\@journal{reprodmed}\gdef\@journalfull{Reproductive Medicine}\gdef\@journalshort{Reprod. Med.}\gdef\@doiabbr{reprodmed}\gdef\@ISSN{2673-3897}\gdef\@continuouspages{yes}}
\DeclareOption{resources}{\gdef\@journal{resources}\gdef\@journalfull{Resources}\gdef\@journalshort{Resources}\gdef\@doiabbr{resources}\gdef\@ISSN{2079-9276}}
\DeclareOption{rheumato}{\gdef\@journal{rheumato}\gdef\@journalfull{Rheumato}\gdef\@journalshort{Rheumato}\gdef\@doiabbr{rheumato}\gdef\@ISSN{2674-0621}\gdef\@continuouspages{yes}}
\DeclareOption{risks}{\gdef\@journal{risks}\gdef\@journalfull{Risks}\gdef\@journalshort{Risks}\gdef\@doiabbr{risks}\gdef\@ISSN{2227-9091}}
\DeclareOption{robotics}{\gdef\@journal{robotics}\gdef\@journalfull{Robotics}\gdef\@journalshort{Robotics}\gdef\@doiabbr{robotics}\gdef\@ISSN{2218-6581}}
\DeclareOption{ruminants}{\gdef\@journal{ruminants}\gdef\@journalfull{Ruminants}\gdef\@journalshort{Ruminants}\gdef\@doiabbr{ruminants}\gdef\@ISSN{2673-933X}\gdef\@continuouspages{yes}}
\DeclareOption{safety}{\gdef\@journal{safety}\gdef\@journalfull{Safety}\gdef\@journalshort{Safety}\gdef\@doiabbr{safety}\gdef\@ISSN{2313-576X}}
\DeclareOption{sci}{\gdef\@journal{sci}\gdef\@journalfull{Sci}\gdef\@journalshort{Sci}\gdef\@doiabbr{sci}\gdef\@ISSN{2413-4155}}
\DeclareOption{scipharm}{\gdef\@journal{scipharm}\gdef\@journalfull{Scientia Pharmaceutica}\gdef\@journalshort{Sci. Pharm.}\gdef\@doiabbr{scipharm}\gdef\@ISSN{2218-0532}}
\DeclareOption{seeds}{\gdef\@journal{seeds}\gdef\@journalfull{Seeds}\gdef\@journalshort{Seeds}\gdef\@doiabbr{seeds}\gdef\@ISSN{2674-1024}\gdef\@continuouspages{yes}}
\DeclareOption{sensors}{\gdef\@journal{sensors}\gdef\@journalfull{Sensors}\gdef\@journalshort{Sensors}\gdef\@doiabbr{s}\gdef\@ISSN{1424-8220}}
\DeclareOption{separations}{\gdef\@journal{separations}\gdef\@journalfull{Separations}\gdef\@journalshort{Separations}\gdef\@doiabbr{separations}\gdef\@ISSN{2297-8739}}
\DeclareOption{sexes}{\gdef\@journal{sexes}\gdef\@journalfull{Sexes}\gdef\@journalshort{Sexes}\gdef\@doiabbr{sexes}\gdef\@ISSN{2411-5118}\gdef\@continuouspages{yes}}
\DeclareOption{signals}{\gdef\@journal{signals}\gdef\@journalfull{Signals}\gdef\@journalshort{Signals}\gdef\@doiabbr{signals}\gdef\@ISSN{2624-6120}\gdef\@continuouspages{yes}}
\DeclareOption{sinusitis}{\gdef\@journal{sinusitis}\gdef\@journalfull{Sinusitis}\gdef\@journalshort{Sinusitis}\gdef\@doiabbr{sinusitis}\gdef\@ISSN{2309-107X}\gdef\@continuouspages{yes}}
\DeclareOption{skins}{\gdef\@journal{skins}\gdef\@journalfull{Skins}\gdef\@journalshort{Skins}\gdef\@doiabbr{skins}\gdef\@ISSN{}}
\DeclareOption{smartcities}{\gdef\@journal{smartcities}\gdef\@journalfull{Smart Cities}\gdef\@journalshort{Smart Cities}\gdef\@doiabbr{smartcities}\gdef\@ISSN{2624-6511}\gdef\@continuouspages{yes}}
\DeclareOption{sna}{\gdef\@journal{sna}\gdef\@journalfull{Sinusitis and Asthma}\gdef\@journalshort{Sinusitis Asthma}\gdef\@doiabbr{sna}\gdef\@ISSN{2624-7003}}
\DeclareOption{societies}{\gdef\@journal{societies}\gdef\@journalfull{Societies}\gdef\@journalshort{Societies}\gdef\@doiabbr{soc}\gdef\@ISSN{2075-4698}}
\DeclareOption{socsci}{\gdef\@journal{socsci}\gdef\@journalfull{Social Sciences}\gdef\@journalshort{Soc. Sci.}\gdef\@doiabbr{socsci}\gdef\@ISSN{2076-0760}}
\DeclareOption{software}{\gdef\@journal{software}\gdef\@journalfull{Software}\gdef\@journalshort{Software}\gdef\@doiabbr{software}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{soilsystems}{\gdef\@journal{soilsystems}\gdef\@journalfull{Soil Systems}\gdef\@journalshort{Soil Syst.}\gdef\@doiabbr{soilsystems}\gdef\@ISSN{2571-8789}}
\DeclareOption{solar}{\gdef\@journal{solar}\gdef\@journalfull{Solar}\gdef\@journalshort{Solar}\gdef\@doiabbr{solar}\gdef\@ISSN{2673-9941}\gdef\@continuouspages{yes}}
\DeclareOption{solids}{\gdef\@journal{solids}\gdef\@journalfull{Solids}\gdef\@journalshort{Solids}\gdef\@doiabbr{solids}\gdef\@ISSN{2673-6497}\gdef\@continuouspages{yes}}
\DeclareOption{sports}{\gdef\@journal{sports}\gdef\@journalfull{Sports}\gdef\@journalshort{Sports}\gdef\@doiabbr{sports}\gdef\@ISSN{2075-4663}}
\DeclareOption{standards}{\gdef\@journal{standards}\gdef\@journalfull{Standards}\gdef\@journalshort{Standards}\gdef\@doiabbr{standards}\gdef\@ISSN{2305-6703}\gdef\@continuouspages{yes}}
\DeclareOption{stats}{\gdef\@journal{stats}\gdef\@journalfull{Stats}\gdef\@journalshort{Stats}\gdef\@doiabbr{stats}\gdef\@ISSN{2571-905X}\gdef\@continuouspages{yes}}
\DeclareOption{stresses}{\gdef\@journal{stresses}\gdef\@journalfull{Stresses}\gdef\@journalshort{Stresses}\gdef\@doiabbr{stresses}\gdef\@ISSN{2673-7140}\gdef\@continuouspages{yes}}
\DeclareOption{surfaces}{\gdef\@journal{surfaces}\gdef\@journalfull{Surfaces}\gdef\@journalshort{Surfaces}\gdef\@doiabbr{surfaces}\gdef\@ISSN{2571-9637}\gdef\@continuouspages{yes}}
\DeclareOption{surgeries}{\gdef\@journal{surgeries}\gdef\@journalfull{Surgeries}\gdef\@journalshort{Surgeries}\gdef\@doiabbr{surgeries}\gdef\@ISSN{2017-2017}\gdef\@continuouspages{yes}}
\DeclareOption{suschem}{\gdef\@journal{suschem}\gdef\@journalfull{Sustainable Chemistry}\gdef\@journalshort{Sustain. Chem.}\gdef\@doiabbr{suschem}\gdef\@ISSN{2673-4079}\gdef\@continuouspages{yes}}
\DeclareOption{sustainability}{\gdef\@journal{sustainability}\gdef\@journalfull{Sustainability}\gdef\@journalshort{Sustainability}\gdef\@doiabbr{su}\gdef\@ISSN{2071-1050}}
\DeclareOption{symmetry}{\gdef\@journal{symmetry}\gdef\@journalfull{Symmetry}\gdef\@journalshort{Symmetry}\gdef\@doiabbr{sym}\gdef\@ISSN{2073-8994}}
\DeclareOption{synbio}{\gdef\@journal{synbio}\gdef\@journalfull{Synbio}\gdef\@journalshort{Synbio}\gdef\@doiabbr{synbio}\gdef\@ISSN{2674-0583}\gdef\@continuouspages{yes}}
\DeclareOption{systems}{\gdef\@journal{systems}\gdef\@journalfull{Systems}\gdef\@journalshort{Systems}\gdef\@doiabbr{systems}\gdef\@ISSN{2079-8954}}
\DeclareOption{taxonomy}{\gdef\@journal{taxonomy}\gdef\@journalfull{Taxonomy}\gdef\@journalshort{Taxonomy}\gdef\@doiabbr{taxonomy}\gdef\@ISSN{2673-6500}\gdef\@continuouspages{yes}}
\DeclareOption{technologies}{\gdef\@journal{technologies}\gdef\@journalfull{Technologies}\gdef\@journalshort{Technologies}\gdef\@doiabbr{technologies}\gdef\@ISSN{2227-7080}}
\DeclareOption{telecom}{\gdef\@journal{telecom}\gdef\@journalfull{Telecom}\gdef\@journalshort{Telecom}\gdef\@doiabbr{telecom}\gdef\@ISSN{2673-4001}\gdef\@continuouspages{yes}}
\DeclareOption{test}{\gdef\@journal{test}\gdef\@journalfull{Test}\gdef\@journalshort{Test}\gdef\@doiabbr{}\gdef\@ISSN{}}
\DeclareOption{textiles}{\gdef\@journal{textiles}\gdef\@journalfull{Textiles}\gdef\@journalshort{Textiles}\gdef\@doiabbr{textiles}\gdef\@ISSN{2673-7248}\gdef\@continuouspages{yes}}
\DeclareOption{thalassrep}{\gdef\@journal{thalassrep}\gdef\@journalfull{Thalassemia Reports}\gdef\@journalshort{Thalass. Rep.}\gdef\@doiabbr{thalassrep}\gdef\@ISSN{2039-4365}\gdef\@continuouspages{yes}}
\DeclareOption{thermo}{\gdef\@journal{thermo}\gdef\@journalfull{Thermo}\gdef\@journalshort{Thermo}\gdef\@doiabbr{thermo}\gdef\@ISSN{2673-7264}\gdef\@continuouspages{yes}}
\DeclareOption{tomography}{\gdef\@journal{tomography}\gdef\@journalfull{Tomography}\gdef\@journalshort{Tomography}\gdef\@doiabbr{tomography}\gdef\@ISSN{2379-139X}\gdef\@continuouspages{yes}}
\DeclareOption{tourismhosp}{\gdef\@journal{tourismhosp}\gdef\@journalfull{Tourism and Hospitality}\gdef\@journalshort{Tour. Hosp.}\gdef\@doiabbr{tourhosp}\gdef\@ISSN{2673-5768}\gdef\@continuouspages{yes}}
\DeclareOption{toxics}{\gdef\@journal{toxics}\gdef\@journalfull{Toxics}\gdef\@journalshort{Toxics}\gdef\@doiabbr{toxics}\gdef\@ISSN{2305-6304}}
\DeclareOption{toxins}{\gdef\@journal{toxins}\gdef\@journalfull{Toxins}\gdef\@journalshort{Toxins}\gdef\@doiabbr{toxins}\gdef\@ISSN{2072-6651}}
\DeclareOption{transplantology}{\gdef\@journal{transplantology}\gdef\@journalfull{Transplantology}\gdef\@journalshort{Transplantology}\gdef\@doiabbr{transplantology}\gdef\@ISSN{2673-3943}\gdef\@continuouspages{yes}}
\DeclareOption{transportation}{\gdef\@journal{transportation}\gdef\@journalfull{Transportation}\gdef\@journalshort{Transportation}\gdef\@doiabbr{transportation}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{traumacare}{\gdef\@journal{traumacare}\gdef\@journalfull{Trauma Care}\gdef\@journalshort{Trauma Care}\gdef\@doiabbr{traumacare}\gdef\@ISSN{2673-866X}\gdef\@continuouspages{yes}}
\DeclareOption{traumas}{\gdef\@journal{traumas}\gdef\@journalfull{Traumas}\gdef\@journalshort{Traumas}\gdef\@doiabbr{traumas}\gdef\@ISSN{2673-7477}\gdef\@continuouspages{yes}}
\DeclareOption{tropicalmed}{\gdef\@journal{tropicalmed}\gdef\@journalfull{Tropical Medicine and Infectious Disease}\gdef\@journalshort{Trop. Med. Infect. Dis.}\gdef\@doiabbr{tropicalmed}\gdef\@ISSN{2414-6366}}
\DeclareOption{universe}{\gdef\@journal{universe}\gdef\@journalfull{Universe}\gdef\@journalshort{Universe}\gdef\@doiabbr{universe}\gdef\@ISSN{2218-1997}}
\DeclareOption{urbansci}{\gdef\@journal{urbansci}\gdef\@journalfull{Urban Science}\gdef\@journalshort{Urban Sci.}\gdef\@doiabbr{urbansci}\gdef\@ISSN{2413-8851}}
\DeclareOption{uro}{\gdef\@journal{uro}\gdef\@journalfull{Uro}\gdef\@journalshort{Uro}\gdef\@doiabbr{uro}\gdef\@ISSN{2673-4397}\gdef\@continuouspages{yes}}
\DeclareOption{vaccines}{\gdef\@journal{vaccines}\gdef\@journalfull{Vaccines}\gdef\@journalshort{Vaccines}\gdef\@doiabbr{vaccines}\gdef\@ISSN{2076-393X}}
\DeclareOption{vehicles}{\gdef\@journal{vehicles}\gdef\@journalfull{Vehicles}\gdef\@journalshort{Vehicles}\gdef\@doiabbr{vehicles}\gdef\@ISSN{2624-8921}\gdef\@continuouspages{yes}}
\DeclareOption{venereology}{\gdef\@journal{venereology}\gdef\@journalfull{Venereology}\gdef\@journalshort{Venereology}\gdef\@doiabbr{venereology}\gdef\@ISSN{2674-0710}\gdef\@continuouspages{yes}}
\DeclareOption{vetsci}{\gdef\@journal{vetsci}\gdef\@journalfull{Veterinary Sciences}\gdef\@journalshort{Vet. Sci.}\gdef\@doiabbr{vetsci}\gdef\@ISSN{2306-7381}}
\DeclareOption{vibration}{\gdef\@journal{vibration}\gdef\@journalfull{Vibration}\gdef\@journalshort{Vibration}\gdef\@doiabbr{vibration}\gdef\@ISSN{2571-631X}\gdef\@continuouspages{yes}}
\DeclareOption{viruses}{\gdef\@journal{viruses}\gdef\@journalfull{Viruses}\gdef\@journalshort{Viruses}\gdef\@doiabbr{v}\gdef\@ISSN{1999-4915}}
\DeclareOption{vision}{\gdef\@journal{vision}\gdef\@journalfull{Vision}\gdef\@journalshort{Vision}\gdef\@doiabbr{vision}\gdef\@ISSN{2411-5150}}
\DeclareOption{waste}{\gdef\@journal{waste}\gdef\@journalfull{Waste}\gdef\@journalshort{Waste}\gdef\@doiabbr{waste}\gdef\@ISSN{2813-0391}\gdef\@continuouspages{yes}}
\DeclareOption{water}{\gdef\@journal{water}\gdef\@journalfull{Water}\gdef\@journalshort{Water}\gdef\@doiabbr{w}\gdef\@ISSN{2073-4441}}
\DeclareOption{wem}{\gdef\@journal{wem}\gdef\@journalfull{Wildlife Ecology and Management}\gdef\@journalshort{Wildl. Ecol. Manag.}\gdef\@doiabbr{}\gdef\@ISSN{1234-4321}}
\DeclareOption{wevj}{\gdef\@journal{wevj}\gdef\@journalfull{World Electric Vehicle Journal}\gdef\@journalshort{World Electr. Veh. J.}\gdef\@doiabbr{wevj}\gdef\@ISSN{2032-6653}}
\DeclareOption{wind}{\gdef\@journal{wind}\gdef\@journalfull{Wind}\gdef\@journalshort{Wind}\gdef\@doiabbr{wind}\gdef\@ISSN{2674-032X}\gdef\@continuouspages{yes}}
\DeclareOption{women}{\gdef\@journal{women}\gdef\@journalfull{Women}\gdef\@journalshort{Women}\gdef\@doiabbr{women}\gdef\@ISSN{2673-4184}\gdef\@continuouspages{yes}}
\DeclareOption{world}{\gdef\@journal{world}\gdef\@journalfull{World}\gdef\@journalshort{World}\gdef\@doiabbr{world}\gdef\@ISSN{2673-4060}\gdef\@continuouspages{yes}}
\DeclareOption{youth}{\gdef\@journal{youth}\gdef\@journalfull{Youth}\gdef\@journalshort{Youth}\gdef\@doiabbr{youth}\gdef\@ISSN{2673-995X}\gdef\@continuouspages{yes}}
\DeclareOption{zoonoticdis}{\gdef\@journal{zoonoticdis}\gdef\@journalfull{Zoonotic Diseases}\gdef\@journalshort{Zoonotic Dis.}\gdef\@doiabbr{zoonoticdis}\gdef\@ISSN{2813-0227}\gdef\@continuouspages{yes}}
